### 2017-12-19 ALL1-backup-2.tex
initial upload - 10 pages

\documentclass{article}

\usepackage{amsmath,amssymb,amsthm}
\usepackage{proof}
\usepackage{stmaryrd}
\usepackage{xargs}

\usepackage{graphicx}

\usepackage{willemtools}
\usepackage{proofnet}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\theoremstyle{plain}
\newtheorem{lemma}[definition]{Lemma}

% ===== Definitions

\newcommand\defn[1]{\textit{\textbf{#1}}}

% ===== General maths

\newcommand\floor[1]{\lfloor#1\rfloor}

% ===== Sets

\newcommand\varA{\textsc{var}^\forall}
\newcommand\varE{\textsc{var}^\exists}
\newcommand\terms{\textsc{term}}
\newcommand\termsA{\textsc{term}^\forall}
\newcommand\atom{\textsc{atom}}
\newcommand\all{\textsc{all}}

\newcommand\subs[1]{\textsc{sub}(#1)}

% ===== Formulas

\newcommand\+{+}
\renewcommand\*{\times}
\newcommand\dual[1]{\overline{#1}}

\newcommand\sub{\leq}
\newcommand\seq[3][]{{\vdash_{#1}}#2,#3}
\newcommand\fv{\textsc{fv}}

% ===== Proofs

\newcommand\prf[3]{#1\vdash\!#2,#3}

% ===== Nets

\newcommand\net[3]{#1\triangleright #2,#3}

\newcommand\deseq[4][\sigma]{[#2]^{#1}_{#3,#4}}
\newcommand\Deseq[4][\sigma]{\left[\vcenter{#2}\right]^{#1}_{#3,#4}}

%\newcommandx\deseq[4][2=\sigma]{\floor{#1}_{#2}^{#3,#4}}
%\newcommandx\Deseq[4][2=\sigma]{\left\lfloor\vcenter{#1}\right\rfloor_{#2}^{#3,#4}}

% ===== Witness maps

\newcommand\join\bowtie

\newcommand\comp\frown
%\newcommand\ubot\sqcup

%\newlength{\cuplength}
%\settowidth{\cuplength}{$\cup$}
%\newcommand\ubot{\mathbin{\ooalign{$\cup$\cr\hss\scalebox{.9}{\raisebox{0.6ex}{\tiny$\mathbf\bot$}}\hss}}}

%\newcommand\inst[1]{\llparenthesis#1\rrparenthesis}

% ===== Slices

% ===== Coalescence

\newcommand\clink[3][\sigma]{(#2,#3)_{#1}}
\newcommand\minus{\mathop{/\mathchoice{\kern-3pt}{\kern-3pt}{\kern-2.5pt}{\kern-2pt}/}}

\newcommand\coals{\rightsquigarrow}
\newcommand\coal{\coals}%{\stackrel1\rightsquigarrow}

\newcommandx\crule[4][1=\sigma,2=\lambda]{#2\coals(#3,#4)_{#1}}

%\newcommandx\xlink[4][1=\sigma,2=\lambda]{#2\triangleright(#3,#4)_{#1}}

\begin{document}

%\end{document}

% ==================================================

\section{Proof nets for first-order additive linear logic}

% ..................................................

\begin{figure}
\hrule
\par\bigskip
\[
	\infer{\seq P{\dual P}}{}
\qquad
	\infer{\seq A{B_0\+B_1}}{\seq A{B_i}}
\qquad
	\infer{\seq A{B\*C}}{\seq AB && \seq AC}
\]
\par
\[
	\infer{\seq A{\exists x.B}}{\seq A{B[t/x]}}
\qquad
	\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]{\seq A{\forall a.B}}{\seq AB}
\]
\par
\[
	\infer{\seq A{\dual A}}{}
\qquad
	\infer{\seq AC}{\seq AB && \seq{\dual B}C}
\]
\par\bigskip\hrule
\caption{A sequent calculus for $\all1$}
\label{fig:sequent calculus}
\end{figure}

% ..................................................

% --------------------------------------------------

\subsection{First-order additive linear logic}

First-order terms and the formulas of first-order $\all$ are generated by the following grammars.
%
\setMidspace{5pt}
\[
\begin{array}{l@{}l}
	t &\Coloneqq a \Mid x \Mid f(t_1,\dots,t_n)
\\[10pt]
	P &\Coloneqq p(t_1,\dots,t_n) \Mid \dual p(t_1,\dots,t_n)
\\[10pt]
	A &\Coloneqq P \Mid A\+A \Mid A\*A \Mid \exists x.A \Mid \forall a.A
\end{array}
\]
%
Negation $(\dual{\,\cdot\,})$ is applied to predicate symbols, $\dual p$, as a matter of convenience. The \defn{dual} $\dual A$ of an arbitrary formula $A$ is given by DeMorgan. We use the following notational conventions.
%
\\[2\itemsep]
%
\begin{tabular}{@{}lll@{}}
	$a,b,c$ & $\in \varA$ 		& universally quantified variables (and free variables)\\
	$x,y,z$ & $\in \varE$		& existentially quantified variables \\
	$f,g,h$ & $\in \Sigma_f$	& $n$-ary $(n\geq 0)$ function symbols from a fixed alphabet $\Sigma_f$\\
	$p,q,r$ & $\in \Sigma_p$	& $n$-ary $(n\geq 0)$ predicate symbols from a fixed alphabet $\Sigma_p$ \\
	$s,t,u$ & $\in \terms$ 		& first-order terms over $\varA$, $\varE$, $\Sigma_f$, and $\Sigma_p$ \\
	$P,Q,R$ & $\in \atom$		& atomic propositions \\
	$A,B,C$ & $\in \all1$		& formulas \\
\end{tabular}
%
\\[2\itemsep]
%
A \defn{sequent} $\seq AB$ is an ordered pair of formulas $A$ and $B$. A sequent calculus for \all1 is given in Figure~\ref{fig:sequent calculus}, where each rule has a symmetric counterpart that applies to the first formula in the sequent. We write $\prf\Pi AB$ for a proof $\Pi$ with conclusion sequent $\seq AB$. Anticipating the requirements of proof nets, we will assume the following convention for \all1 proofs.

\begin{description}
	\item
[\defn{Barendregt's convention}] All quantifiers in a sequent $\seq AB$ have a distinct binding variable, and no bound variable shares a name with a free one.
%	\item
%% ALTERNATIVE: "STATIC WITNESSING"
%[\defn{Universal witnessing}] All existential witnesses in a proof are \defn{universal terms} $\termsA\subset\terms$, generated by the following grammar.
%\[
%	\termsA: \qquad t \Coloneqq a \Mid f(t_1,\dots,t_n)
%\]
\end{description}

% --------------------------------------------------

\subsection{Proof nets}

By a \defn{subformula} we will mean a subformula \defn{occurrence}. For instance, a formula $A\*A$ has two subformulas $A$, one on the left and one on the right. The \defn{subformulas} $\subs A$ of a formula are given by
\[
	\subs A = \{A\} \cup
	\left\{\begin{array}{ll}
		\subs B\uplus\subs C	& \text{if $A=B\+C$ or $A=B\*C$} \\[5pt]
		\subs B					& \text{if $A=\exists x.B$ or $A=\forall a.B$}
	\end{array}\right.
\]
We will write $B\sub A$ if $B$ is a subformula of $A$. In the context of a sequent $\seq AB$, a \defn{link} $(A',B')$ is a pair of subformulas $A'\leq A$ and $B'\leq B$. A link is an \defn{axiom link} if both formulas are atomic propositions. A \defn{linking} $\lambda$ on the sequent $\seq AB$ is a set of links on $\seq AB$. %It is an \defn{axiom linking} if all links are axiom links.

\begin{definition}
A \defn{pre-net} $\net\lambda AB$ is a sequent $\seq AB$ with a linking $\lambda$ on it.
\end{definition}

A \defn{witness map} $\sigma$ is a substitution map
\[
	\sigma\colon \varE \to \terms
\]
which assigns terms to existential variables. We write $\varnothing$ for the empty map (the identity). The map $\sigma[x\mapsto t]$ substitutes $t$ for $x$ and is as $\sigma$ everywhere else, while $\sigma\minus x$ is the identity on $x$ and otherwise as $\sigma$. The application of a witness map $\sigma$ to a formula $A$ is written $A\sigma$.

A \defn{labelled link} $\clink AB$ is a link carrying a witness map $\sigma$. A \defn{labelled linking} respectively a \defn{labelled pre-net} is a linking or pre-net where every link is labelled. A labelled linking $\lambda$ reverts to an unlabelled one, written $\floor\lambda$, by dropping the label of each link.

\begin{definition}
The \defn{labelled de-sequentialization} of a sequent proof $\prf\Pi AB$ is the labelled pre-net $\net{\deseq[\varnothing]\Pi AB} AB$ where $\deseq-AB$ is defined as follows.
%
\[
\begin{array}{ccl}
	\Deseq{\infer{\seq P{\dual P}}{}}QR &=& \{\clink QR\}
\\ \\
	\Deseq{\infer {\seq A {B_0\+B_1}} {\deduce [\rule{0pt}{1pt}] {\seq A{B_i}} \Pi }}
	  {A'}{B_0'\+B'_1} 
	&=& \Deseq{\deduce[\rule{0pt}{1pt}]{\seq A{B_i}}\Pi}{A'}{B_i'}
\\ \\
	\Deseq{\infer{\seq A{B\*C}}{
	  \deduce[\rule{0pt}{1pt}]{\seq AB}\Pi 
	  && 
	  \deduce[\rule{0pt}{1pt}]{\seq AC}\Sigma}}{A'}{B'\*C'}
	&=& \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AB}\Pi}{A'}{B'}
	  \cup
	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AC}\Sigma}{A'}{C'}
\\ \\
	\Deseq{\infer{\seq A{\exists x.B}}{\deduce[\rule{0pt}{1pt}]{\seq A{B[t/x]}}\Pi}}
	  {A'}{\exists x.B'}
	&=&
	 \Deseq[{\sigma[x\mapsto t]}]{\deduce[\rule{0pt}{1pt}]{\seq A{B[t/x]}}\Pi}
	  {A'}{B'}
\\ \\
	\Deseq{\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]
	  {\seq A{\forall a.B}}{\deduce[\rule{0pt}{1pt}]{\seq AB}\Pi}}{A'}{\forall a.B'}
	&=&
	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AB}\Pi}{A'}{B'}
\end{array}
\]
The \defn{(unlabelled) de-sequentialization} of $\Pi$ is $\net{\floor\Pi_{A,B}}AB$ where $\floor\Pi_{A,B}$ is $\floor{\deseq[\varnothing]\Pi AB}$.
\end{definition}

To generate witness maps for an unlabelled linking, we will be using unification. A \defn{unifying} witness map $\sigma$ for formulas $A$ and $B$ is one such that $A\sigma=B\sigma$. Note that these will substitute only the free existential variables, but not bound ones or universal variables. For instance, the only unifying witness map of $p(x,y)$ and $p(a,a)$ is $\{x\mapsto a,y\mapsto a\}$, while $\exists y.p(x,x)$ and $\exists y.p(a,y)$ have no unifier.

A witness map $\sigma$ is \defn{more general} than $\tau$, witten $\sigma\leq\tau$, if there is a $\rho$ such that $(A\sigma)\rho = A\tau$ for any $A$. The \defn{join} $\sigma\join\tau$ of two maps $\sigma$ and $\tau$ is the least map $\rho$ such that $\sigma\leq\rho$ and $\tau\leq\rho$, if it exists. If it does, we call $\sigma$ and $\tau$ \defn{compatible}, written $\sigma\comp\tau$.

The \defn{initial witness map} $\sigma(A,B)$ is the most general unifying witness map for the formulas $A$ and $B$, if it exists; if it does, $A$ and $B$ are \defn{compatible}. An unlabelled axiom link $(P,Q)$ is \defn{compatible} if $P$ and $\dual Q$ are compatible; a labelled one $\clink PQ$ is \defn{compatible} if $\sigma$ is a unifier for $P$ and $\dual Q$. A (labelled) linking or pre-net is \defn{compatible} if all links are compatible axiom links. The \defn{initial labelling} of a compatible linking $\lambda$ or pre-net $\net\lambda AB$ is the labelled linking $\lambda_\star$ or labelled pre-net $\net{\lambda_\star}AB$ given by
\[
	\lambda_\star = \{~\clink[\sigma(P,\dual Q)]PQ~\mid~(P,Q)\in\lambda~\}~.
\]
%Observe that $\floor{\lambda_\star}=\lambda$. We call $\floor\lambda_\star$ the \defn{initial re-labelling} of a labelled linking $\lambda$, and analogously for a pre-net $\net\lambda AB$.

\subsection{Geometric correctness}

For a labelled linking $\lambda$ and an existential variable $x$, write $\lambda(x)\subseteq\terms$ for the \defn{witness set} of $x$, which collects the terms assigned to $x$ by the links in $\lambda$:
\[
	\lambda(x) = \{~t~\mid~\sigma(x) = t~,~\clink AB\in\lambda~\}~.
\]
%
Given a labelled linking $\lambda$, a \defn{slice} $S$ of a formula $A$ is a set of formulas given by: $S=\{A\}\cup S'$ where $S'$ is as follows; if $A$ is of the form
%
\begin{itemize}
	\item
\makebox[40pt][l]{$P$:}				$S'=\varnothing$.
	\item
\makebox[40pt][l]{$B\+C$:} 			$S'=S_B\cup S_C$ where $S_B$ is a slice of $B$ and $S_C$ a slice of $C$.
	\item
\makebox[40pt][l]{$B\*C$:}			$S'$ is a slice of $B$ or a slice of $C$.
	\item
\makebox[40pt][l]{$\exists x.B$:}	$S'$ is a slice of $B$ if the quantifier is vacuous, $x\notin\fv(B)$, and
	\\[\itemsep]
	\hspace*{40pt}					$S'=\uplus_{t\,\in\,\lambda(x)}S_t$ where each $S_t$ is a slice of $B[t/x]$ otherwise.
	\item
\makebox[40pt][l]{$\forall a.B$:}	$S'$ is a slice of $B$.
\end{itemize}
%
A \defn{slice} of a labelled pre-net $\net\lambda AB$ is a set of links
\[
	\{~(C\sigma,D\sigma)~\mid~\clink CD\in \lambda~,~(C\sigma,D\sigma)\in S_A\times S_B~\}
\]
where $S_A$ is a slice of $A$ and $S_B$ a slice of $B$. A labelled pre-net is \defn{correct} if every slice is a singleton. A compatible pre-net $\net\lambda AB$ is \defn{correct} if its initial labelling $\net{\lambda_\star}AB$ is. Observe that for a \emph{labelled} pre-net correctness and compatibility are independent, while a non-labelled pre-net must be compatible to be correct, since $\lambda_\star$ is otherwise not defined.

\begin{definition}
An \all1 \defn{proof net} is a correct pre-net. An \all1 \defn{labelled proof net} is a correct and compatible labelled pre-net.
\end{definition}

% --------------------------------------------------

\subsection{Coalescence}

\begin{definition}
\defn{Coalescence} ($\coals$) is the rewrite relation on labelled pre-nets generated by the following rewrite rules, and their symmetric variants.
%
\renewcommand{\+}{{+}}
\renewcommand{\*}{{\times}}
\begin{align}
  	\net{\{\clink AB\}}A{B\+C} 
& ~\coal~
	\net{\{\clink A{B\+C}\}}A{B\+C}
\tag{$\+_1$}
\\[5pt]
        \net{\{\clink AC\}}A{B\+C}
& ~\coal~  
	\net{\{\clink A{B\+C}\}}A{B\+C}
\tag{$\+_2$}
\\[5pt]
	\net{\{\clink AB,\clink[\tau]AC\}}A{B\*C}
& ~\coal~ 
	\net{\{\clink[\sigma\join\tau]A{B\*C}\}}A{B\*C}\quad\text{if }\sigma\comp\tau
\tag{$\*$}
\\[5pt]	
	\net{\{\clink AB\}}A{\exists x.B}
& ~\coal~ 
	\net{\{\clink[\sigma\!\minus\!x]A{\exists x.B}\}}A{\exists x.B}
\tag{$\exists$}
\\[5pt]
	\net{\{\clink AB\}}A{\forall a.B}
& ~\coal~ 
	\net{\clink A{\forall a.B}}A{\forall a.B} \quad \text{if }a\,\notin\,\fv(A\sigma)
\tag{$\forall$}
\end{align}
%\[
%\renewcommand{\+}{{+}}
%\renewcommand{\*}{{\times}}
%\begin{array}{r@{}c@{\,}c@{\,~}l}
%    \begin{array}{@{}r@{}}
%        \net{\{\clink AB\}}A{B\+C} \\ \\[-5pt]
%        \net{\{\clink AC\}}A{B\+C}
%    \end{array}
%&   \left.\begin{array}{@{}c@{}} 
%		\vphantom\{\\\\[-5pt]\vphantom\{
%	\end{array}\right\}
%& \coal &
%	\net{\{\clink A{B\+C}\}}A{B\+C}
%\\ \\[-5pt]
%	\net{\{\clink AB,\clink[\tau]AC\}}A{B\*C}
%&& \coal &
%	\net{\{\clink[\sigma\join\tau]A{B\*C}\}}A{B\*C}\quad\text{if }\sigma\comp\tau
%\\ \\[-5pt]	
%	\net{\{\clink AB\}}A{\exists x.B}
%&& \coal &
%	\net{\{\clink[\sigma\!\minus\!x]A{\exists x.B}\}}A{\exists x.B}
%\\ \\[-5pt]
%	\net{\{\clink AB\}}A{\forall a.B}
%&& \coal &
%	\net{\clink A{\forall a.B}}A{\forall a.B} \quad \text{if }a\,\notin\,\fv(A\sigma)
%\end{array}
%\]
%\begin{itemize}
%	\item 
%\makebox[40pt][l]{$B\+C$:} 
%Replace a link $\clink AB$ or $\clink AC$ with $\clink A{B\+C}$.
%	\item 
%\makebox[40pt][l]{$B\*C$:} 
%Replace links $\clink AB$ and $\clink[\tau]AC$ with $\clink[\sigma\cup\tau]A{B\*C} $ if $\sigma\comp\tau$.
%	\item
%\makebox[40pt][l]{$\exists x.B$:} 
%Replace a link $\clink AB$ with $\clink[\sigma\minus x]A{\exists x.B}$.
%	\item
%\makebox[40pt][l]{$\forall a.B$:}
%Replace a link $\clink AB$ with $\clink A{\forall a.B}$ if $a\,\notin\,\fv(A\sigma)$.
%\end{itemize}
%
%
%\begin{itemize}
%	\item 
%\makebox[40pt][l]{$B\+C$:} 
%Replace a link $\clink AB$ or $\clink AC$ with $\clink A{B\+C}$.
%	\item 
%\makebox[40pt][l]{$B\*C$:} 
%Replace links $\clink AB$ and $\clink[\tau]AC$ with $\clink[\sigma\cup\tau]A{B\*C} $ if $\sigma\comp\tau$.
%	\item
%\makebox[40pt][l]{$\exists x.B$:} 
%Replace a link $\clink AB$ with $\clink[\sigma\minus x]A{\exists x.B}$.
%	\item
%\makebox[40pt][l]{$\forall a.B$:}
%Replace a link $\clink AB$ with $\clink A{\forall a.B}$ if $a\,\notin\,\fv(A\sigma)$.
%\end{itemize}
%
A labelled pre-net $\net\lambda AB$ \defn{coalesces} if it coalesces to a single link $\clink[\varnothing]AB$. A compatible pre-net \defn{coalesces} if $\net{\lambda_\star}AB$ coalesces. A pre-net \defn{strongly coalesces} if every coalescence sequence terminates at $\clink[\varnothing]AB$.
\end{definition}

To be explicit, generating coalescence as a rewrite relation means the following: $\net\lambda AB\coal \net{\lambda'}AB$ if and only if there is a rewrite rule $\net\kappa CD\coal\net{\kappa'} CD$ such that $C\leq A$, $D\leq B$, $\kappa\subseteq\lambda$, and $\lambda'=\lambda\cup\kappa'-\kappa$.

\begin{lemma}
If a labelled pre-net coalesces, it is correct. 
\end{lemma}

\begin{proof}
By induction on the coalescence path. Let $\net\lambda AB$ coalesce to $\net\kappa AB$ where $\kappa=\{\clink AB\}$. First, we show that the result is correct. For each $x$ the witness set $\kappa(x)$ is $\{\sigma x\}$.  the only slice of $\seq AB$ is $(A,B)$, 
\end{proof}

Coalescence is effectively sequentialization. We will make this explicit by organising the rewrite rules as inference rules.

%
%As an intermediary between the sequent calculus and labelled proof nets, we will introduce a \defn{labelled sequent calculus}. A \defn{labelled sequent}
%\[
%	\xlink AB
%\]
%is a sequent that carries a linking $\lambda$ and a witness map $\sigma$. 
%
%
%for the statement that $\lambda\seq{A\sigma}{B\sigma}$ coalesces to a single labelled 
%

\begin{figure}
\hrule
\par\bigskip
\[
\begin{array}{c@{\hspace{40pt}}ccc}
	\vc{\infer{\crule [\sigma(P,\dual Q)] [\{(P,Q)\}] P Q}{}}
&    
    \vc{\begin{tikzpicture}[net]
    	\formula[y=2]{P}
    	\formula[y=1]{Q}
    	\Vlink[blue]{1,1}
    \end{tikzpicture}}
&\rightsquigarrow&    
    \vc{\begin{tikzpicture}[net]
    	\formula[y=2]{P}
    	\formula[y=1]{Q}
    	\Vlink[red,label={$~\scriptstyle{\sigma(P,\dual Q)}$}]{1,1}
    \end{tikzpicture}}
\\ \\
	\vc{\infer{\crule A {B\+C}} {\crule AB}}
&   
    \vc{\begin{tikzpicture}[net]
    	\formula[y=2]{A}
    	\formula[y=1]{B\+C}
    	\Vlink[red,label={$\scriptstyle\sigma~$},l]{1,1}
    \end{tikzpicture}}
&\rightsquigarrow& 
    \vc{\begin{tikzpicture}[net]
    	\formula[y=2]{A}
    	\formula[y=1]{B\+C}
    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,2}
    \end{tikzpicture}}
\\ \\ 
    \vc{\infer[\!\!\scriptstyle{\sigma\comp\tau}]
    		{\crule [\sigma\cup\tau] [\lambda\cup\kappa] A {B\*C}}
    		{\crule AB && \crule[\tau][\kappa]AC}}
&     
    \vc{\begin{tikzpicture}[net]
    	\formula[y=2]{A}
    	\formula[y=1]{B\*C}
    	\Vlink[red,label={$\scriptstyle\sigma~$},l]{[-1]1,1}
    	\Vlink[red,label={~$\scriptstyle\tau$}]{[1]1,3}
    \end{tikzpicture}}
&\stackrel{\sigma\comp\tau}\rightsquigarrow&   
	\vc{\begin{tikzpicture}[net]
    	\formula[y=2]{A}
    	\formula[y=1]{B\*C}
    	\Vlink[red,label={~$\scriptstyle{\sigma\cup\tau}$}]{1,2}
    \end{tikzpicture}}

\\ \\
    \vc{\infer{\crule[\sigma\minus x]A{\exists x.B}}{\crule AB}}
&
    \vc{\begin{tikzpicture}[net]
    	\formula[y=2]{A}
    	\formula[y=1]{\exists x.B}
    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,4}
    \end{tikzpicture}}
&\rightsquigarrow&
    \vc{\begin{tikzpicture}[net]
    	\formula[y=2]{A}
    	\formula[y=1]{\exists x.B}
    	\Vlink[red,label={~$\scriptstyle{\sigma\!\minus\!x}$}]{1,1}
    \end{tikzpicture}}
\\ \\
    \vc{\infer[\!\!\scriptstyle{a\,\notin\,\fv(A\sigma)}]{\crule A{\forall a.B}}{\crule AB}}
&    
    \vc{\begin{tikzpicture}[net]
    	\formula[y=2]{A}
    	\formula[y=1]{\forall a.B}
    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,4}
    \end{tikzpicture}}
&\stackrel{a\,\notin\,\fv(A\sigma)}\rightsquigarrow&
    \vc{\begin{tikzpicture}[net]
    	\formula[y=2]{A}
    	\formula[y=1]{\forall a.B}
    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,1}
    \end{tikzpicture}}
\end{array}
\]
\par\bigskip\hrule
\caption{Coalescence derivation rules}
\label{fig:coalescence}
\end{figure}

\begin{lemma}
Given a proof $\prf\Pi AB$, formulas $A'$, $B'$, and a witness map $\sigma$ such that $A'\sigma=A$ and $B'\sigma=B$, the de-sequentialization $\net{\deseq\Pi{A'}{B'}}AB$ coalesces to $\net{\{\clink AB\}}AB$. 
\end{lemma}

\begin{lemma}
Given a proof $\prf\Pi AB$ and formulas $A'$ and $B'$, if a smallest witness map $\tau$ exists such that $A=A'\tau$ and $B=B'\tau$, then $\deseq\Pi{A'}{B'}$ coalesces to $\clink{A'}{B'}$ with $\sigma\leq\tau$.
\end{lemma}

\begin{proof}
By induction on $\Pi$.

\newlength\prooftablewidth
\setlength\prooftablewidth{-80pt}
\addtolength\prooftablewidth{\textwidth}

\noindent
\begin{tabular}{@{}p{80pt}@{}p{\prooftablewidth}@{}}
	\hfill \raisebox{-20pt}{\infer{\seq P{\dual P}}{\vphantom B}} \hfill\hfill
&
	Let $A'=Q$ and $B'=R$, and suppose $\tau$ is the smallest witness map such that $Q\tau=P$ and $R\tau=\dual P$. The desequentialization $\deseq\Pi QR$ is the $\net{\{Q,R\}}QR$, which coalesces to $\clink QR$ if $\sigma=\sigma(Q,{\dual R})$ exists. Since $\tau$ is a unifier of $Q$ and $\dual R$, $\sigma\leq\tau$.	
\\ \\
%	$\infer{\seq A{B_0\+B_1}}{\seq A{B_i}}$
%&
%\\ \\
	\hfill \raisebox{-20pt}{\infer{\seq A{B\*C}}{\seq AB && \seq AC}}\hfill\hfill
&
	Let $\seq{\prf\Pi AB}{A'}{B'}$ coalesce to the two subproofs coalesce to $\clink{A'}{B'}$ and $\clink[\rho]{A'}{B'}$ 
%	\infer{\seq A{\exists x.B}}{\seq A{B[t/x]}}
%	\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]{\seq A{\forall a.B}}{\seq AB}
\end{tabular}

\end{proof}

\end{document}

%\[
%	\infer{\xlink [\sigma(P,Q)] [\{(P,Q)\}] P Q}{}
%\]
%\par
%\[
%	\infer{\xlink A {B_0\+B_1}} {\xlink A {B_i}}
%\]
%\par
%\[
%	\infer[\!\!\scriptstyle{\sigma\comp\tau}]
%		{\xlink [\sigma\cup\tau] [\lambda\cup\kappa] A {B\*C}}
%		{\xlink AB && \xlink[\tau][\kappa]AC}
%\]
%\par
%\[
%	\infer{\xlink[\sigma\minus x]A{\exists x.B}}{\xlink AB}
%\]
%\par
%\[
%	\infer[\!\!\scriptstyle{a\,\notin\,\fv(A\sigma)}]{\xlink A{\forall a.B}}{\xlink AB}
%\]

% --------------------------------------------------

%\subsection{Existential witnesses}

%
%
%For two first-order terms $s$ and $t$, and a set of variables $V$, let a $V$-\defn{unifier} be a unifying substitution map
%\[
%	\sigma\colon V\rightharpoonup \terms
%\]
%(that is, $s\sigma=t\sigma$). A $V$-unifier for atomic propositions $P$ and $Q$ is defined analogously. For example, 
%
%
%The \defn{most general $V$-unifier} $\sigma_V(P,Q)$ of $P$ and $Q$ is the most general unifying
%
%let the \defn{initial witness map} $\sigma(P,Q)$ be the most general unifier of $P$ and $Q$, if it exists, where only existential variables can be substituted for, and universal variables are considered constant. That is, the only unifier of $p(x,y)$ and $p(a,a)$ is $\{x\mapsto a,y\mapsto a\}$, while $p(x,x)$ and $p(a,b)$ have no unifier.
%
%Let $\sigma\join\tau$ denote the combination of two witness maps $\sigma$ and $\tau$ as unifiers, if it exists. If it does, we call $\sigma$ and $\tau$ \defn{compatible}, expressed by $\sigma\comp\tau$. The initial witness map $\sigma(A,B)$ of two formulae $A$ and $B$, if it exists, is then given by:
%
%\begin{align}
%	\left.\begin{array}{r}
%		\sigma_V(\,A\+B\,,\,C\+D\,) \\
%		\sigma_V(\,A\*B\,,\,C\*D\,)
%	\end{array}\right\}
%	& = \sigma_V(A,C)\join\sigma_V(B,D)
%\\	
%	\sigma_V(\,\forall a.A\,,\,\forall a.B\,)
%		 \kern12.5pt & = \sigma_V(A,B)
%\\	\sigma_V(\,\exists x.A\,,\,\exists x.B\,)
%		 \kern12.5pt & = \sigma_{V-\{x\}}(A,B)
%\end{align*}
%
%
%Two witness maps $\sigma$ and $\tau$ are \defn{compatible}, written $\sigma\comp\tau$, if they agree wherever they are defined:
%\[
%	\sigma\comp\tau \quad\iff\quad \forall x\in\varE.~\big(\sigma(x)\neq\bot~\wedge~\tau(x)\neq\bot\big)~\Rightarrow~\sigma(x)=\tau(x)~.
%\]
%Two compatible witness maps can be combined into the map $\sigma\cup\tau$ that sends $x$ to $\sigma(x)$ or $\tau(x)$, whichever is defined, and is undefined when both are. To combine witness maps that may not be compatible we will write $\sigma\ubot\tau$, which is $\sigma\cup\tau$ if they are, and undefined ($\bot$) otherwise; if either $\sigma$ or $\tau$ is already undefined, $\sigma\ubot\tau$ also reverts to $\bot$.
%\[
%	\sigma\ubot\tau\quad=\quad
%	\left\{\begin{array}{ll}
%		\sigma\cup\tau	& \text{if $\sigma\neq\bot$, $\tau\neq\bot$, and $\sigma\comp\tau$} \\
%		\bot			& \text{otherwise} \\
%	\end{array}\right.
%\] 
%Note that $\bot$ is not a witness map, and different from the empty substitution map, $\sigma(x)=\bot$ for all $x$. For two atomic formulas $P,Q$ (or terms $s,t$) the \defn{initial witness map} $\sigma(P,Q)$ is the smallest witness map $\sigma$ such that $P\sigma=\dual Q\sigma$ and $P\sigma$ has no free existential variables. If it exists, it is defined inductively as follows (omitting the symmetric case for $\dual p$ and $p$). 
%
%\begin{align*}
%	\left.\begin{array}{r}
%		\sigma(\,x\,,\,t\,) \\
%	 	\sigma(\,t\,,\,x\,)
%	\end{array}\right\}
%	& = \{ x\mapsto t \}\quad \text{if $t\in\termsA$}
% \\
%	\left.\begin{array}{r}
%		\sigma(\,p(s_1,\dots,s_n)\,,\,\dual p(t_1,\dots,t_n)\,) \\
%		\sigma(\,f(s_1,\dots,s_n)\,,\,f(t_1,\dots,t_n)\,)
%	\end{array}\right\}
%	& = \sigma(s_1,t_1)\ubot\dots\ubot\sigma(s_n,t_n)
%\end{align*}
%
%\begin{lemma}
%\label{lem:minimal witness map}
%For first-order terms $s$ and $t$ the witness map $\sigma(s,t)$ is the smallest such that $s\sigma=t\sigma$ and $s\sigma$ contains no existential variables.
%\end{lemma}
%
%\begin{proof}
%By induction on $s$ and $t$. If $s=x$ then $\sigma(x,t)$ exists if and only if $t\in\termsA$, 
%\end{proof}

%\begin{align*}
%	\sigma_V(\,a\,,\,a\,) \kern12.5pt & = \varnothing
%\\	\sigma_V(\,x\,,\,x\,) \kern12.5pt & = \varnothing\quad \text{if $x\in V$}
%\\
%	\left.\begin{array}{r}
%		\sigma_V(\,x\,,\,t\,) \\
%	 	\sigma_V(\,t\,,\,x\,)
%	\end{array}\right\}
%	& = \{ x\mapsto t \}\quad \text{if $x\notin V$ and $t\in\termsA$}
% \\
%	\left.\begin{array}{r}
%		\sigma_V(\,p(s_1,\dots,s_n)\,,\,p(t_1,\dots,t_n)\,) \\
%		\sigma_V(\,f(s_1,\dots,s_n)\,,\,f(t_1,\dots,t_n)\,)
%	\end{array}\right\}
%	& = \sigma_V(s_1,t_1)\ubot\dots\ubot\sigma_V(s_n,t_n)
%\\	
%	\left.\begin{array}{r}
%		\sigma_V(\,A\+B\,,\,C\+D\,) \\
%		\sigma_V(\,A\*B\,,\,C\*D\,)
%	\end{array}\right\}
%	& = \sigma_V(A,C)\ubot\sigma_V(B,D)
%\\	
%	\sigma_V(\,\forall a.A\,,\,\forall a.B\,)
%		 \kern12.5pt & = \sigma_V(A,B)
%\\	\sigma_V(\,\exists x.A\,,\,\exists x.B\,)
%		 \kern12.5pt & = \sigma_{V\cup\{x\}}(A,B)
%\end{align*}
%
%Observe that if the witness map $\sigma=\sigma(A,B)$ exists then $A\sigma=B\sigma$.

% --------------------------------------------------

\begin{lemma}
Given a proof $\prf\Pi AB$ and formulas $A'$ and $B'$, if a smallest witness map $\tau$ exists such that $A=A'\tau$ and $B=B'\tau$, then $\deseq\Pi{A'}{B'}$ coalesces to $\clink{A'}{B'}$ with $\sigma\leq\tau$.
\end{lemma}

\begin{proof}
By induction on $\Pi$.

\newlength\prooftablewidth
\setlength\prooftablewidth{-80pt}
\addtolength\prooftablewidth{\textwidth}

\noindent
\begin{tabular}{@{}p{80pt}@{}p{\prooftablewidth}@{}}
	\hfill \raisebox{-20pt}{\infer{\seq P{\dual P}}{\vphantom B}} \hfill\hfill
&
	Let $A'=Q$ and $B'=R$, and suppose $\tau$ is the smallest witness map such that $Q\tau=P$ and $R\tau=\dual P$. The desequentialization $\deseq\Pi QR$ is the $\net{\{Q,R\}}QR$, which coalesces to $\clink QR$ if $\sigma=\sigma(Q,{\dual R})$ exists. Since $\tau$ is a unifier of $Q$ and $\dual R$, $\sigma\leq\tau$.	
\\ \\
%	$\infer{\seq A{B_0\+B_1}}{\seq A{B_i}}$
%&
%\\ \\
	\hfill \raisebox{-20pt}{\infer{\seq A{B\*C}}{\seq AB && \seq AC}}\hfill\hfill
&
	Let $\seq{\prf\Pi AB}{A'}{B'}$ coalesce to the two subproofs coalesce to $\clink{A'}{B'}$ and $\clink[\rho]{A'}{B'}$ 
%	\infer{\seq A{\exists x.B}}{\seq A{B[t/x]}}
%	\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]{\seq A{\forall a.B}}{\seq AB}
\end{tabular}

\end{proof}

### 2017-12-19 ALL1-backup-3.tex
initial upload - 10 pages

--- 2017-12-19 ALL1-backup-2.tex
@@
 
+\newcommand\mgu{\textsc{mgu}}
+
 %\newcommand\inst[1]{\llparenthesis#1\rrparenthesis}
@@
 
-%\end{document}
+\[
+\begin{tikzpicture}[net]
+\formula[y=1]{\exists x.\forall a.~p(a,x)}
+\formula[y=0]{\exists y.~{\dual p}(y,s)\*{\dual p}(y,t)}
+\Vlink[red,label={$\scriptstyle\sigma~$},l]{[-2]8,5}
+\Vlink[red,label={$~\scriptstyle\tau$}]{[2]8,12}
+\end{tikzpicture}
+\]
+
+\[
+\begin{tikzpicture}[net]
+\formula[y=1]{\exists x.\forall a.~p(a,x)}
+\formula[y=0]{\exists y.~{\dual p}(y,s)\*{\dual p}(y,t)}
+\Vlink[red,label={$~\scriptstyle\upsilon$}]{8,11}
+\end{tikzpicture}
+\]
+
+\[
+\begin{tikzpicture}[net]
+\formula[y=1]{\exists x.\forall a.~p(a,x)}
+\formula[y=0]{\exists y.~{\dual p}(y,s)\*{\dual p}(y,t)}
+\Vlink[red,label={$\quad\scriptstyle{\upsilon\!\minus\!y}$}]{8,1}
+\end{tikzpicture}
+\]
+
+\[
+\begin{tikzpicture}[net]
+\formula[y=1]{\exists x.\forall a.~p(a,x)}
+\formula[y=0]{\exists y.~{\dual p}(y,s)\*{\dual p}(y,t)}
+\Vlink[red,label={$~\scriptstyle{\upsilon\!\minus\!y}$}]{4,1}
+\end{tikzpicture}
+\]
+
+\[
+\begin{tikzpicture}[net]
+\formula[y=1]{\exists x.\forall a.~p(a,x)}
+\formula[y=0]{\exists y.~{\dual p}(y,s)\*{\dual p}(y,t)}
+\Vlink[red,label={$~\scriptstyle{\rho}$}]{1,1}
+\end{tikzpicture}
+\]
+
+\[
+	\sigma = [y\mapsto a, x\mapsto s]
+	\qquad
+	\tau = [y\mapsto a, x\mapsto t]
+\]
+\[
+	\upsilon = \rho[y\mapsto a, x\mapsto u]
+	\qquad
+	\rho = \mgu(s,t)
+	\qquad
+	 u=s\rho=t\rho
+\]
 
@@
 We will write $B\sub A$ if $B$ is a subformula of $A$.
+
 In the context of a sequent $\seq AB$, a \defn{link} $(A',B')$ is a pair of subformulas $A'\leq A$ and $B'\leq B$.
@@
 
-\subsection{Geometric correctness}
-
-For a labelled linking $\lambda$ and an existential variable $x$, write $\lambda(x)\subseteq\terms$ for the \defn{witness set} of $x$, which collects the terms assigned to $x$ by the links in $\lambda$:
-\[
-	\lambda(x) = \{~t~\mid~\sigma(x) = t~,~\clink AB\in\lambda~\}~.
-\]
-%
-Given a labelled linking $\lambda$, a \defn{slice} $S$ of a formula $A$ is a set of formulas given by: $S=\{A\}\cup S'$ where $S'$ is as follows; if $A$ is of the form
-%
-\begin{itemize}
-	\item
-\makebox[40pt][l]{$P$:}				$S'=\varnothing$.
-	\item
-\makebox[40pt][l]{$B\+C$:} 			$S'=S_B\cup S_C$ where $S_B$ is a slice of $B$ and $S_C$ a slice of $C$.
-	\item
-\makebox[40pt][l]{$B\*C$:}			$S'$ is a slice of $B$ or a slice of $C$.
-	\item
-\makebox[40pt][l]{$\exists x.B$:}	$S'$ is a slice of $B$ if the quantifier is vacuous, $x\notin\fv(B)$, and
-	\\[\itemsep]
-	\hspace*{40pt}					$S'=\uplus_{t\,\in\,\lambda(x)}S_t$ where each $S_t$ is a slice of $B[t/x]$ otherwise.
-	\item
-\makebox[40pt][l]{$\forall a.B$:}	$S'$ is a slice of $B$.
-\end{itemize}
-%
-A \defn{slice} of a labelled pre-net $\net\lambda AB$ is a set of links
-\[
-	\{~(C\sigma,D\sigma)~\mid~\clink CD\in \lambda~,~(C\sigma,D\sigma)\in S_A\times S_B~\}
-\]
-where $S_A$ is a slice of $A$ and $S_B$ a slice of $B$.
-A labelled pre-net is \defn{correct} if every slice is a singleton.
-A compatible pre-net $\net\lambda AB$ is \defn{correct} if its initial labelling $\net{\lambda_\star}AB$ is.
-Observe that for a \emph{labelled} pre-net correctness and compatibility are independent, while a non-labelled pre-net must be compatible to be correct, since $\lambda_\star$ is otherwise not defined.
-
-\begin{definition}
-An \all1 \defn{proof net} is a correct pre-net. An \all1 \defn{labelled proof net} is a correct and compatible labelled pre-net.
-\end{definition}
-
 % --------------------------------------------------
@@
 \subsection{Coalescence}
+
+% ..................................................
+
+\begin{figure}
+\hrule
+\par\bigskip
+\[
+\begin{array}{rcl@{\hspace{40pt}}rcl} 
+    \vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{A}
+    	\formula[y=1]{B\+C}
+    	\Vlink[red,label={$\scriptstyle\sigma~$},l]{1,1}
+    \end{tikzpicture}}
+&\rightsquigarrow& 
+    \vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{A}
+    	\formula[y=1]{B\+C}
+    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,2}
+    \end{tikzpicture}}
+&    
+    \vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{A}
+    	\formula[y=1]{\exists x.B}
+    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,4}
+    \end{tikzpicture}}
+&\rightsquigarrow&
+    \vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{A}
+    	\formula[y=1]{\exists x.B}
+    	\Vlink[red,label={~$\scriptstyle{\sigma\!\minus\!x}$}]{1,1}
+    \end{tikzpicture}}
+\\ \\    
+    \vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{A}
+    	\formula[y=1]{B\*C}
+    	\Vlink[red,label={$\scriptstyle\sigma~$},l]{[-1]1,1}
+    	\Vlink[red,label={~$\scriptstyle\tau$}]{[1]1,3}
+    \end{tikzpicture}}
+&\stackrel{\sigma\comp\tau}\rightsquigarrow&   
+	\vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{A}
+    	\formula[y=1]{B\*C}
+    	\Vlink[red,label={~$\scriptstyle{\sigma\cup\tau}$}]{1,2}
+    \end{tikzpicture}}
+&  
+    \vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{A}
+    	\formula[y=1]{\forall a.B}
+    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,4}
+    \end{tikzpicture}}
+&\stackrel{a\,\notin\,\fv(A\sigma)}\rightsquigarrow&
+    \vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{A}
+    	\formula[y=1]{\forall a.B}
+    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,1}
+    \end{tikzpicture}}
+\end{array}
+\]
+\par\bigskip\hrule
+\caption{Coalescence rules}
+\label{fig:coalescence}
+\end{figure}
+
+% ..................................................
 
@@
 
+% --------------------------------------------------
+
+\subsection{Geometric correctness}
+
+For a labelled linking $\lambda$ and an existential variable $x$, write $\lambda(x)\subseteq\terms$ for the \defn{witness set} of $x$, which collects the terms assigned to $x$ by the links in $\lambda$:
+\[
+	\lambda(x) = \{~t~\mid~\sigma(x) = t~,~\clink AB\in\lambda~\}~.
+\]
+%
+Given a labelled linking $\lambda$, a \defn{slice} $S$ of a formula $A$ is a set of formulas given by: $S=\{A\}\cup S'$ where $S'$ is as follows; if $A$ is of the form
+%
+\begin{itemize}
+	\item
+\makebox[40pt][l]{$P$:}				$S'=\varnothing$.
+	\item
+\makebox[40pt][l]{$B\+C$:} 			$S'=S_B\cup S_C$ where $S_B$ is a slice of $B$ and $S_C$ a slice of $C$.
+	\item
+\makebox[40pt][l]{$B\*C$:}			$S'$ is a slice of $B$ or a slice of $C$.
+	\item
+\makebox[40pt][l]{$\exists x.B$:}	$S'$ is a slice of $B$ if the quantifier is vacuous, $x\notin\fv(B)$, and
+	\\[\itemsep]
+	\hspace*{40pt}					$S'=\uplus_{t\,\in\,\lambda(x)}S_t$ where each $S_t$ is a slice of $B[t/x]$ otherwise.
+	\item
+\makebox[40pt][l]{$\forall a.B$:}	$S'$ is a slice of $B$.
+\end{itemize}
+%
+A \defn{slice} of a labelled pre-net $\net\lambda AB$ is a set of links
+\[
+	\{~\clink CD\in \lambda~\mid~(C\sigma,D\sigma)\in S_A\times S_B~\}
+\]
+where $S_A$ is a slice of $A$ and $S_B$ a slice of $B$.
+A labelled pre-net is \defn{correct} if every slice is a singleton.
+A compatible pre-net $\net\lambda AB$ is \defn{correct} if its initial labelling $\net{\lambda_\star}AB$ is.
+Observe that for a \emph{labelled} pre-net correctness and compatibility are independent, while a non-labelled pre-net must be compatible to be correct, since $\lambda_\star$ is otherwise not defined.
+
+\begin{definition}
+An \all1 \defn{proof net} is a correct pre-net. An \all1 \defn{labelled proof net} is a correct and compatible labelled pre-net.
+\end{definition}
+
 \begin{lemma}
@@
 \begin{proof}
-By induction on the coalescence path.
-Let $\net\lambda AB$ coalesce to $\net\kappa AB$ where $\kappa=\{\clink AB\}$.
-First, we show that the result is correct.
-For each $x$ the witness set $\kappa(x)$ is $\{\sigma x\}$.
-the only slice of $\seq AB$ is $(A,B)$,
+By induction on the coalescence path we will show that if $\net\lambda AB$ coalesces to $\net{\{\clink AB\}}AB$ then $\net{\{\clink[\varnothing]{A\sigma}{B\sigma}\}}{A\sigma}{B\sigma}$ is correct.
+The statement is then the special case $\sigma=\varnothing$.
+
+The result $\net{\{\clink[\varnothing]{A\sigma}{B\sigma}\}}{A\sigma}{B\sigma}$ is correct: its only slice is $\{\clink[\varnothing]{A\sigma}{B\sigma}\}$, since $A\sigma$ is in any slice $S_{A\sigma}$ of $A\sigma$, and $B\sigma$ is in any slice $S_{B\sigma}$ of $B\sigma$.
+
+\renewcommand{\+}{{+}}
+\renewcommand{\*}{{\times}}
+\begin{align}
+	\net{\{\clink AB,\clink[\tau]AC\}}A{B\*C}
+& ~\coal~ 
+	\net{\{\clink[\sigma\join\tau]A{B\*C}\}}A{B\*C}\quad\text{if }\sigma\comp\tau
+\tag{$\*$}
+\end{align}
+
+Let $\rho=\sigma\join\tau$, and assume that $\net{\{\clink[\varnothing]{A\rho}{B\rho\*C\rho}\}}{A\rho}{B\rho\*C\rho}$ is correct.
+
 \end{proof}

### 2017-12-19 ALL1-backup-6.tex
initial upload - 10 pages

\documentclass[UKenglish]{lipics-v2016}

\usepackage{amsmath,amssymb,amsthm}
\usepackage{latexsym}
\usepackage{microtype}
\usepackage{proof}
\usepackage{stmaryrd}
\usepackage{xargs}

\usepackage{graphicx}

\usepackage{willemtools}
\usepackage{proofnet}

\bibliographystyle{plainurl}

% ============================== MACROS

\makeatletter

\theoremstyle{plain}
\newtheorem{proposition}[theorem]{Proposition}

% ===== Definitions

\newcommand\defn[1]{\textit{\textbf{#1}}}

% ===== General maths

\newcommand\floor[1]{\lfloor#1\rfloor}

% ===== Sets

\newcommand\varA{\textsc{var}^\forall}
\newcommand\varE{\textsc{var}^\exists}
\newcommand\terms{\textsc{term}}
\newcommand\termsA{\textsc{term}^\forall}
\newcommand\atom{\textsc{atom}}
\newcommand\all{\textsc{all}}

\newcommand\subs[1]{\textsc{sub}(#1)}
\newcommand\dom[1]{\textsc{dom}(#1)}

% ===== Formulas

\newcommand\+{+}
\renewcommand\*{\times}
\newcommand\dual[1]{\overline{#1}}

\newcommand\sub{\leq}
\newcommand\seq[3][]{{\vdash_{#1}}#2,#3}
\newcommand\fv{\textsc{fv}}

% ===== Proofs

\newcommand\prf[3]{#1\vdash\!#2,#3}

% ===== Nets

\newcommand\net[3]{#1\triangleright #2,#3}

\newcommand\deseq[4][\sigma]{[#2]^{#1}_{#3,#4}}
\newcommand\Deseq[4][\sigma]{\left[\vcenter{#2}\right]^{#1}_{#3,#4}}

%\newcommandx\deseq[4][2=\sigma]{\floor{#1}_{#2}^{#3,#4}}
%\newcommandx\Deseq[4][2=\sigma]{\left\lfloor\vcenter{#1}\right\rfloor_{#2}^{#3,#4}}

% ===== Witness maps

\newcommand\mgu{\textsc{mgu}}

\newcommand\gen{\leq}
\newcommand\coh{\smallfrown}
\newcommand\join{\vee}

% ===== Slices

% ===== Coalescence

\newcommand\link[3][\sigma]{(#2,#3)_{#1}}
\newcommand\minus{\mathop{/\mathchoice{\kern-3pt}{\kern-3pt}{\kern-2.5pt}{\kern-2pt}/}}

\newcommand\scoal{\rightarrow} %{\leadsto}
\newcommand\ucoal{\rightsquigarrow}

\newcommand\qrr[1]{
  \ifx#1+\expandafter\@qrr\else
  \ifx#1*\*\mathrm R\else
  \ifx#1!\forall\mathrm R\else
  \ifx#1?\expandafter\@@qrr\else
  \ifx#11\mathrm{ax}\else
  #1\mathrm R
  \fi\fi\fi\fi\fi
}
\newcommand\@qrr[1]{+\mathrm R,#1}
\newcommand\@@qrr[1]{\exists\mathrm R,#1}
\newcommand\srr[1]{
  \ifx#1+\expandafter\@srr\else
  \ifx#1*\*\mathrm S\else
  \ifx#1!\forall\mathrm S\else
  \ifx#1?\exists\mathrm S\else 
  \ifx#11\mathrm{axS}\else
  #1\mathrm S  \fi\fi\fi\fi\fi
}
\newcommand\@srr[1]{+_{#1}\mathrm S}
\newcommand\urr[1]{
  \ifx#1+\expandafter\@urr\else
  \ifx#1*\*\mathrm U\else
  \ifx#1!\forall\mathrm U\else
  \ifx#1?\exists\mathrm U\else 
  \ifx#11\mathrm{axU}\else
  #1\mathrm U
  \fi\fi\fi\fi\fi
}
\newcommand\@urr[1]{+_{#1}\mathrm U}

% ===== Derivations

\newcommand\sdown{\mathrel{\rotatebox[origin=c]{-90}{$\scoal$}\kern1pt}}
\newcommand\udown{\mathrel{\rotatebox[origin=c]{-90}{$\ucoal$}\kern1pt}}

\newcommandx\sdn[4][2=\sigma]{#1\sdown\link[#2]{#3}{#4}}	%{#2\sdown_{#1}{#3}\mathbin,{#4}}
\newcommandx\udn[4][2=\sigma]{#1\udown\link[#2]{#3}{#4}}	%{#2\udown_{#1}{#3}\mathbin,{#4}}

% ===== (De-)Sequentialization

\newcommand\QU{\Leftrightarrow}

\makeatother

% ============================== TITLE & AUTHORS

\title{Proof nets for first-order additive linear logic}
%\titlerunning{Proof nets for ALL1}

\author[1]{Willem B.\ Heijltjes}
\author[2]{Dominic J.D.\ Hughes}
\author[3]{Lutz Stra\ss burger}
\affil[1]{University of Bath, United Kingdom\\
  \texttt{w.b.heijltjes@bath.ac.uk}}
\affil[2]{
  \texttt{}}
\affil[3]{INRIA \&\ \'Ecole Polytechnique, Palaiseau, France\\
  \texttt{lutz.strassburger@inria.fr}}
\authorrunning{W.B.\ Heijltjes, D.J.D.\ Hughes, and L.\ Stra\ss burger}

\Copyright{Willem B.\ Heijltjes, Dominic J.D.\ Hughes, and Lutz Stra\ss burger}

\subjclass{Dummy classification -- please refer to \url{http://www.acm.org/about/class/ccs98-html}}% mandatory: Please choose ACM 1998 classifications from http://www.acm.org/about/class/ccs98-html . E.g., cite as "F.1.1 Models of Computation". 
\keywords{Linear logic, Proof nets}

% ============================== CONTENT

\begin{document}

\maketitle

\begin{abstract}

\end{abstract}

\subsection{Proof identity}

\[
	\infer={\exists x.p(x),\exists y.\dual p(y)}{\infer{p(t),\dual p(t)}{}}
	\quad
	\stackrel?\equiv
	\quad
	\infer={\exists x.P(x),\exists y.\dual p(y)}{\infer{p(s),\dual p(s)}{}}
\]

\[
	\infer{\exists x.p,\dual p}{\infer{p[t/x],\dual p}{}}
	\quad
	\stackrel?\equiv
	\quad	
	\infer{\exists x.p,\dual p}{\infer{p[s/x],\dual p}{}}
\]

\[
	\infer{\exists x.p\+q(x),\dual p}{\infer{p\+q(t)}{\infer{p,\dual p}{}}}
	\quad
	\stackrel?\equiv
	\quad	
	\infer{\exists x.p\+q(x),\dual p}{\infer{p\+q(s)}{\infer{p,\dual p}{}}}
\]

\[
\begin{tikzpicture}[net]
\formula[y=1]{\exists x.\forall a.~p(a,x)}
\formula[y=0]{\exists y.~{\dual p}(y,s)\*{\dual p}(y,t)}
\Vlink[red,label={$\scriptstyle\sigma~$},l]{[-2]8,5}
\Vlink[red,label={$~\scriptstyle\tau$}]{[2]8,12}
\end{tikzpicture}
\]

\[
\begin{tikzpicture}[net]
\formula[y=1]{\exists x.\forall a.~p(a,x)}
\formula[y=0]{\exists y.~{\dual p}(y,s)\*{\dual p}(y,t)}
\Vlink[red,label={$~\scriptstyle\upsilon$}]{8,11}
\end{tikzpicture}
\]

\[
\begin{tikzpicture}[net]
\formula[y=1]{\exists x.\forall a.~p(a,x)}
\formula[y=0]{\exists y.~{\dual p}(y,s)\*{\dual p}(y,t)}
\Vlink[red,label={$\quad\scriptstyle{\upsilon\!\minus\!y}$}]{8,1}
\end{tikzpicture}
\]

\[
\begin{tikzpicture}[net]
\formula[y=1]{\exists x.\forall a.~p(a,x)}
\formula[y=0]{\exists y.~{\dual p}(y,s)\*{\dual p}(y,t)}
\Vlink[red,label={$~\scriptstyle{\upsilon\!\minus\!y}$}]{4,1}
\end{tikzpicture}
\]

\[
\begin{tikzpicture}[net]
\formula[y=1]{\exists x.\forall a.~p(a,x)}
\formula[y=0]{\exists y.~{\dual p}(y,s)\*{\dual p}(y,t)}
\Vlink[red,label={$~\scriptstyle{\rho}$}]{1,1}
\end{tikzpicture}
\]

\[
	\sigma = [a/y, s/x]
	\qquad
	\tau = [a/y, t/x]
\]
\[
	\upsilon = \rho[a/y, u/x]
	\qquad
	\rho = \mgu(s,t)
	\qquad
	 u=s\rho=t\rho
\]

% ==================================================

\section{Proof nets for first-order additive linear logic}

% ..................................................

\begin{figure}
\[
	\infer{\seq P{\dual P}}{}
\qquad
	\infer{\seq A{B_0\+B_1}}{\seq A{B_i}}
\qquad
	\infer{\seq A{B\*C}}{\seq AB && \seq AC}
\qquad
	\infer{\seq A{\exists x.B}}{\seq A{B[t/x]}}
\qquad
	\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]{\seq A{\forall a.B}}{\seq AB}
\]
\caption{A sequent calculus for $\all1$}
\label{fig:sequent calculus}
\end{figure}

\begin{figure}
\noindent\hrule
\[
	\infer[\!\!\scriptstyle{\qrr1}]{\seq P{\dual P}}{}
\quad
	\infer[\!\!\scriptstyle{\qrr+i}]{\seq A{B_0\+B_1}}{\seq A{B_i}}
\quad
	\infer[\!\!\scriptstyle{\qrr*}]{\seq A{B\*C}}{\seq AB & \seq AC}
\quad
	\infer[\!\!\scriptstyle{\qrr?t}]{\seq A{\exists x.B}}{\seq A{B[t/x]}}
\quad
	\infer[\!\!\scriptstyle{\qrr!~(a\,\notin\,\textsc{fv}(A))}]{\seq A{\forall a.B}}{\seq AB}
\]
\caption{A sequent calculus for $\all1$}
\label{fig:sequent calculus}
\end{figure}
%
%\begin{figure}
%\[
%\raisebox{.5ex}{$\qrr1$}\quad
%	\infer{\seq P{\dual P}}{}
%\quad\raisebox{.5ex}{$\qrr+i$}\quad
%	\infer{\seq A{B_0\+B_1}}{\seq A{B_i}}
%\quad\raisebox{.5ex}{$\qrr*$}\quad
%	\infer{\seq A{B\*C}}{\seq AB && \seq AC}
%\quad\raisebox{.5ex}{$\qrr?$}\quad
%	\infer{\seq A{\exists x.B}}{\seq A{B[t/x]}}
%\quad\raisebox{.5ex}{$\qrr!$}\quad
%	\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]{\seq A{\forall a.B}}{\seq AB}
%\]
%\caption{A sequent calculus for $\all1$}
%\label{fig:sequent calculus}
%\end{figure}

% ..................................................

% --------------------------------------------------

\subsection{First-order additive linear logic}

First-order terms and the formulas of first-order $\all$ are generated by the following grammars.
%
\setMidspace{5pt}
\[
\begin{array}{@{}l@{}l}
	t &\Coloneqq a \Mid x \Mid f(t_1,\dots,t_n)
\\[10pt]
	P &\Coloneqq p(t_1,\dots,t_n) \Mid \dual p(t_1,\dots,t_n)
\\[10pt]
	A &\Coloneqq P \Mid A\+A \Mid A\*A \Mid \exists x.A \Mid \forall a.A
\end{array}
\]
%
Negation $(\dual{\,\cdot\,})$ is applied to predicate symbols, $\dual p$, as a matter of convenience. The \defn{dual} $\dual A$ of an arbitrary formula $A$ is given by DeMorgan. We use the following notational conventions.
%
\[
\begin{tabular}{@{}lll@{}}
	$a,b,c$ & $\in \varA$ 		& universally quantified variables (and free variables)\\
	$x,y,z$ & $\in \varE$		& existentially quantified variables \\
	$f,g,h$ & $\in \Sigma_f$	& $n$-ary $(n\geq 0)$ function symbols from a fixed alphabet $\Sigma_f$\\
	$p,q,r$ & $\in \Sigma_p$	& $n$-ary $(n\geq 0)$ predicate symbols from a fixed alphabet $\Sigma_p$ \\
	$s,t,u$ & $\in \terms$ 		& first-order terms over $\varA$, $\varE$, $\Sigma_f$, and $\Sigma_p$ \\
	$P,Q,R$ & $\in \atom$		& atomic propositions \\
	$A,B,C$ & $\in \all1$		& formulas \\
\end{tabular}
\]
%
A \defn{sequent} $\seq AB$ is a pair of formulas $A$ and $B$. A sequent calculus for \all1 is given in Figure~\ref{fig:sequent calculus}, where each rule has a symmetric counterpart that applies to the first formula in the sequent. We write $\prf\Pi AB$ for a proof $\Pi$ with conclusion sequent $\seq AB$. Anticipating the requirements of proof nets, we will assume the following convention for \all1 proofs.

\begin{description}
	\item
[\defn{Barendregt's convention}] All quantifiers in a sequent $\seq AB$ have a distinct binding variable, and no bound variable shares a name with a free one.
%	\item
%% ALTERNATIVE: "STATIC WITNESSING"
%[\defn{Universal witnessing}] All existential witnesses in a proof are \defn{universal terms} $\termsA\subset\terms$, generated by the following grammar.
%\[
%	\termsA: \qquad t \Coloneqq a \Mid f(t_1,\dots,t_n)
%\]
\end{description}

% --------------------------------------------------

\subsection{Pre-nets}

By a \defn{subformula} we will mean a subformula \defn{occurrence}. For instance, a formula $A\*A$ has two subformulas $A$, one on the left and one on the right. The \defn{subformulas} $\subs A$ of a formula are defined as follows; we write $B\sub A$ if $B$ is a subformula of $A$, i.e.\ if $B\in\subs A$.
\[
	\subs A = \{A\} \cup
	\left\{\begin{array}{ll}
		\subs B\uplus\subs C	& \text{if $A=B\+C$ or $A=B\*C$} \\[5pt]
		\subs B					& \text{if $A=\exists x.B$ or $A=\forall a.B$}
	\end{array}\right.
\]

A \defn{witness map} $\sigma\colon \varE \rightharpoonup \terms$ is a substitution map which assigns terms to existential variables, given as a partial function. The \defn{empty} witness map $\varnothing$ is the everywhere undefined partial function, and the map $\sigma[t/x]$ substitutes $t$ for $x$ and is as $\sigma$ everywhere else. We express by $\sigma(x)=\bot$ that $\sigma$ is undefined for $x$.

A \defn{link} $(C,D)$ or $\link CD$ on a sequent $\seq AB$ is a pair of subformulas $C\leq A$ and $D\leq B$, possibly carrying a witness map $\sigma$. We explicitly call a link $(C,D)$ without witness map \defn{clean}; otherwise $\sigma$ is assumed present. We assume the existential variables occurring in the range of $\sigma$ to be fresh, i.e.\ distinct from any existentially quantified variable in $\seq AB$. A \defn{linking} $\lambda$ on the sequent $\seq AB$ is a set of links on it. The clean linking $\floor\lambda$ forgets the witness maps of a linking $\lambda$.

\begin{definition}
A \defn{pre-net} $\net\lambda AB$ is a sequent $\seq AB$ with a linking $\lambda$ on it.
\end{definition}

An \defn{axiom link} is a link $\link PQ$ on two propositional atoms such that $P\sigma=\dual Q\sigma$. A linking consisting of axiom links is an \defn{axiom linking}. For a \emph{clean} axiom link $(P,Q)$ we require that a witness map $\sigma$ exists so that $P\sigma=\dual Q\sigma$.

%A link $\link[\varnothing]CD$ with empty witness map is \defn{clean}; it may then be rendered simply $(C,D)$. A linking or pre-net is \defn{clean} if all its links are. 
%We write $\floor\lambda$ respectively $\floor{\net\lambda AB}$ for the clean version of a linking or pre-net, which forgets the witness map for each link.

\begin{definition}
The \defn{de-sequentialization} $[\Pi]$ of a sequent proof $\prf\Pi AB$ is the pre-net $\net{\deseq[\varnothing]\Pi AB} AB$ where $\deseq-AB$ is defined as follows.
%
\begin{align*}
	\Deseq{\infer{\seq P{\dual P}}{}}QR &\quad=\quad \{\link QR\}
\\ \\
	\Deseq{\infer {\seq A {B_0\+B_1}} {\deduce [\rule{0pt}{1pt}] {\seq A{B_i}} \Pi }}
	  {A'}{B_0'\+B'_1} 
	& \quad=\quad 
	\Deseq{\deduce[\rule{0pt}{1pt}]{\seq A{B_i}}\Pi}{A'}{B_i'}
\\ \\
	\Deseq{\infer{\seq A{B\*C}}{
	  \deduce[\rule{0pt}{1pt}]{\seq AB}\Pi 
	  && 
	  \deduce[\rule{0pt}{1pt}]{\seq AC}\Sigma}}{A'}{B'\*C'}
	& \quad=\quad 
	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AB}\Pi}{A'}{B'}
	  \cup
	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AC}\Sigma}{A'}{C'}
\\ \\
	\Deseq{\infer{\seq A{\exists x.B}}{\deduce[\rule{0pt}{1pt}]{\seq A{B[t/x]}}\Pi}}
	  {A'}{\exists x.B'}
	& \quad=\quad 
	 \Deseq[{\sigma[t/x]}]{\deduce[\rule{0pt}{1pt}]{\seq A{B[t/x]}}\Pi}
	  {A'}{B'}
\\ \\
	\Deseq{\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]
	  {\seq A{\forall a.B}}{\deduce[\rule{0pt}{1pt}]{\seq AB}\Pi}}{A'}{\forall a.B'}
	& \quad=\quad 
	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AB}\Pi}{A'}{B'}
\end{align*}
%
The \defn{clean} de-sequentialization $\floor\Pi$ is $\net{\floor{\deseq[\varnothing]\Pi AB}}AB$:  as $[\Pi]$ but forgetting witness maps.
%
%of $\prf\Pi AB$ is the de-sequentialization $[\Pi]$ which forgets witness maps.
\end{definition}

Observe that the linking of $[\Pi]$ is an axiom linking, and that of $\floor\Pi$ a clean axiom linking.

% --------------------------------------------------

\subsection{Witness maps}

We will write $A\sigma$ for the application of the witness map $\sigma\colon\varE\rightharpoonup\terms$ to the formula $A$ as a substitution map. It is applied to a sequent proof, $\Pi\sigma$, by applying it to each formula in the proof $\Pi$. The \defn{composition} of two maps is written $\sigma\tau$, where $A(\sigma\tau)=(A\sigma)\tau$. The map $\sigma\minus x$ is undefined on $x$ and otherwise as $\sigma$.
%, and $\sigma|X$ is as $\sigma$ on the set of variables $X$ and undefined otherwise. 
We abbreviate the statement that a (universal) variable $a$ occurs free in some term in the range of $\sigma$, $a\in\fv(\sigma(x))$ for some $x$, by $a\in \sigma$. We define the following further operations on witness maps.

\[
\begin{tabular}{@{}lp{.75\textwidth}@{}}
	$\sigma\gen\tau$
&
	A witness map is \defn{more general} than another, 
	$\sigma\gen\tau$, if there is a map $\rho$ such that 
	$\sigma\rho=\tau$.
\\[5pt]	
	$\sigma\coh\tau$
&
	Two witness maps are \defn{coherent}, $\sigma\coh\tau$,
	if there is a map $\rho$ such that $\sigma\rho=\tau\rho$.
\\[5pt]
	$\sigma\join\tau$
&
	The \defn{join} of two witness maps $\sigma\join\tau$ is defined
	if they are coherent, and is the least map $\rho$ such that
	$\sigma\gen\rho$ and $\tau\gen\rho$.
\end{tabular}%
\]

To a clean axiom link $(P,Q)$ we assign an \defn{initial witness map} $\sigma(P,Q)$ as the least witness map $\sigma$ in $(\gen)$ such that $P\sigma=\dual Q\sigma$. In other words, $\sigma(P,Q)$ is the most general unifier ($\textsc{mgu}$) of $P$ and $\dual Q$. The \defn{initial witness assignment} $\lambda_\star$ to a clean axiom linking is:
\[
	\lambda_\star = \{~\link PQ~\mid~(P,Q)\in\lambda~,~\sigma=\sigma(P,Q)~\}~.
\]

% --------------------------------------------------

\subsection{Correctness and sequentialization}

Correctness and sequentialization for \all1 proof nets will be through \defn{coalescence}. This is a simple graph rewriting relation that gives top-down sequentialization, from the axioms to the conclusion of a proof. It is the additive counterpart to Danos \defn{contractibility} for multiplicative linear logic.

We will define two coalescence relations, one \defn{strict} $(\scoal)$ and one \defn{unifying} $(\ucoal)$. In the former, to join two slices the witness assignment must be the same; in the latter, witness assignments must be compatible, so that a common, more general witness map exists.

For sequentialization, the links in a pre-net are labelled with a sequent calculus axiom, and each coalescence rewrite step introduces one proof rule. To this end, let a \defn{labelled link} $\link AB^\Pi$ be a link carrying a sequent proof $\prf\Pi{A\sigma}{B\sigma}$, and a \defn{labelled linking} or \defn{labelled pre-net} one where every link is labelled. The \defn{initial labelling} $\lambda^\star$ of an axiom linking $\lambda$ is:
\[
	\lambda^\star = \{~\link PQ^\Pi~\mid~\link PQ\in\lambda~,~\Pi=~\infer{\seq{P\sigma}{Q\sigma}}{}~\}~.
\]
For correctness we may coalesce a pre-net without constructing a proof.

\begin{definition}
 \defn{Strict sequentialization} ($\scoal$) is the rewrite relation on labelled pre-nets generated by the following rules, which apply symmetrically to the first formula in the sequent. \defn{Strict coalescence} is the same relation ignoring proof labels, on pre-nets.
%
\renewcommand{\+}{{+}}
\renewcommand{\*}{{\times}}
\begin{equation}
  	\net{\{\link A{B_i}^\Pi\}}A{B_0\+B_1} 
 ~\scoal~
	\net{\{\link A{B_0\+B_1} ^\Psi\}}A{B_0\+B_1}
\tag{$\srr+i$}
\end{equation}

\hfill $\text{where}\quad \Psi=~
  \vc{
   \infer  {\seq{A\sigma}{B_0\sigma\,\+\,B_1\sigma}}  {
  	\deduce  [\rule{0pt}{1pt}]  {\seq{A\sigma}{B_i\sigma}}  \Pi
  }}
$ \hspace*{20pt}

\begin{equation}
	\net{\{\link AB^\Pi,\link AC^\Phi\}}A{B\*C}
 ~\scoal~ 
	\net{\{\link A{B\*C}^\Psi\}}A{B\*C}
\tag{$\srr*$}
\end{equation}

\hfill $\text{where}\quad \Psi=~
  \vc{
   \infer  {\seq{A\sigma}{B\sigma\,\*\,C\sigma}}  {
    \deduce  [\rule{0pt}{1pt}]  {\seq{A\sigma}{B\sigma}}  \Pi
    &
    \deduce  [\rule{0pt}{1pt}]  {\seq{A\sigma}{C\sigma}}  \Phi    
  }}$ \hspace*{20pt}

\begin{equation}
	\net{\{\link AB^\Pi\}}A{\exists x.B}
 ~\scoal~ 
	\net{\{\link[\sigma\!\minus\!x]A{\exists x.B}^\Psi\}}A{\exists x.B}
\tag{$\srr?$}
\end{equation}

\hfill $\text{if}\quad\sigma(x)\,\neq\,\bot~,
		\quad
		\text{where}\quad \tau=\sigma\minus x
		\quad
		\text{and}\quad \Psi=~
  \vc{
   \infer  {\seq{A\tau}{\exists x.B\tau}}  {
    \deduce  [\rule{0pt}{1pt}]  {\seq{A\sigma}{B\sigma}}  \Pi  
  }}
$ \hspace*{20pt}

\begin{equation}
	\net{\{\link AB\}}A{\forall a.B}
 ~\scoal~
	\net{\link A{\forall a.B}}A{\forall a.B}
\tag{$\srr!$}
\end{equation}

\hfill $\text{if}\quad a\notin\sigma~,
		\quad
		\text{where}\quad \Psi=~
  \vc{
   \infer  {\seq{A\sigma}{\forall a.B\sigma}}  {
    \deduce  [\rule{0pt}{1pt}]  {\seq{A\sigma}{B\sigma}}  \Pi  
  }}
$ \hspace*{20pt}

\medskip

\noindent
A pre-net $\net\lambda AB$ \defn{strict-coalesces} if it reduces in $(\scoal)$ to a single link $\net{\{\link[\varnothing]AB\}}AB$.
\end{definition}

To be explicit, to generate coalescence as a rewrite relation means the following: a pre-net coalesces to another, $\net\lambda AB\scoal \net{\lambda'}AB$ if and only if there is a rewrite rule $\net\kappa CD\scoal\net{\kappa'} CD$ such that $C\leq A$, $D\leq B$, $\kappa\subseteq\lambda$, $\kappa'\subseteq\lambda'$, and $\lambda-\kappa=\lambda'-\kappa'$.

\begin{definition}
\defn{Unifying coalescence} ($\ucoal$) is the rewrite relation generated by the rules:
\[
	(\urr+i)~,~(\urr?)~,~(\urr!)
	\quad
	\text{are respectively as}
	\quad
	(\srr+i)~,~(\srr?)~,~(\srr!)
\]
except that ($\urr?$) does not require that $\sigma(x)$ is defined, plus the rule
\begin{equation}
	\net{\{\link AB^\Pi,\link[\tau]AC^\Phi\}}A{B\*C}
 ~\ucoal~ 
	\net{\{\link[\sigma\join\tau]A{B\*C}^\Psi\}}A{B\*C}
\tag{$\urr*$}
\end{equation}

\hfill $\text{if}\quad\sigma\coh\tau~,
		\quad
		\text{where}\quad \sigma\join\tau=\sigma\rho=\tau\rho
		\quad
		\text{and}\quad \Psi=~
  \vc{
   \infer  {\seq{A\sigma\rho}{B\sigma\rho\,\*\,C\sigma\rho}}  {
    \left( \vc{\deduce  [\rule{0pt}{2pt}]  {\seq{A\sigma}{B\sigma}}  \Pi} \right)\rho
    &
    \left( \vc{\deduce  [\rule{0pt}{2pt}]  {\seq{A\tau}{C\tau}}  \Phi} \right)\rho   
  }}~.
$ \hspace*{20pt}

\medskip

\noindent
A pre-net $\net\lambda AB$ \defn{unifying-coalesces} if it reduces in $(\ucoal)$ to a single link $\net{\{\link[\varnothing]AB\}}AB$.
\end{definition}

%A pre-net $\net\lambda AB$ \defn{strict-} or \defn{unifying-coalesces} if it reduces in $(\scoal)$ respectively $(\ucoal)$ to a single link $\net{\link[\varnothing]AB}AB$. Here, we ignore the labelling with proofs, which means in particular that we need not instate a labelling to initiate coalescence.

%A pre-net $\net\lambda AB$ \defn{coalesces}, in either relation , if it coalesces to a single clean link $\net{(A,B)^\Pi}AB$. In that case, it \defn{sequentializes} It \defn{strongly coalesces} if every coalescence sequence can be extended to reach $\net{(A,B)}AB$.

\begin{definition}
An \all1 \defn{witnessing proof net} or \defn{witness net} is a pre-net $\net\lambda AB$ with axiom linking $\lambda$ that strict-coalesces. It \defn{sequentializes} to a proof $\Pi$ if its initial labelling $\net{\lambda^\star}AB$ reduces in $(\scoal)$ to $\net{\{\link[\varnothing]AB^\Pi\}}AB$.
\end{definition}

\begin{definition}
An \all1 \defn{unification proof net} or \defn{unification net} is a pre-net $\net\lambda AB$ with clean axiom linking $\lambda$ such that its initial witness assignment $\net{\lambda_\star}AB$ unifying-coalesces. It \defn{sequentializes} to $\Pi$ if the initial labelling $\net{\lambda^\star_\star}AB$ reduces in $(\ucoal)$ to $\net{\{\link[\varnothing]AB^\Pi\}}AB$.
\end{definition}

\begin{theorem}
For any \all1 proof $\Pi$:
\begin{enumerate}
\item the de-sequentialization $[\Pi]$ is a witness net that sequentializes to $\Pi$. 
\item the clean de-sequentialization $\floor\Pi$ is a unification net that sequentializes to a proof $\Phi$ such that $\Pi=\Phi\rho$ for some witness map $\rho$ (where universal variables may be captured).
\end{enumerate}
\end{theorem}

\begin{proof}
By induction on $\prf\Pi AB$, if $\lambda=[\Pi]_{A',B'}^\sigma$ where $A'\sigma=A$ and $B'\sigma=B$, then $\net{\lambda^\star}AB$ reduces in $(\scoal)$ to $\net{\{\link{A'}{B'}^\Pi\}}AB$. Statement 1.\ is the specific case $\sigma=\varnothing$.
%
% Technical note: need to assume $\sigma$ contains no universally quantified variables in $A$ or $B$. 
%
For the second statement, by induction

 on $\prf\Pi AB$, if $\lambda=\floor{\deseq\Pi{A'}{B'}}$ where $A'\sigma=A$ and $B'\sigma=B$, then $\net{\lambda^\star_\star}AB$ reduces in $(\ucoal)$ to $\net{\{\link{A'}{B'}\}}{}{}$
\end{proof}

For two axiom linkings $\lambda$ and $\kappa$,

\begin{lemma}
If $\net\lambda AB$ with axiom linking $\lambda$ unifying-coalesces to $\net{\{\link{A'}{B'}\}}AB$ then $\net{\floor\lambda_\star}AB$ unifying-coalesces to $\net{\{\link[\rho]{A'}{B'}\}}AB$ with $\rho\gen\sigma$.
\end{lemma}

% --------------------------------------------------

\subsection{Geometric correctness}

%\end{document}

A link is \defn{strict} if its domain consists of exactly the existentially quantified variables that its formulas are in scope of. That is, a link $\link CD$ in a pre-net $\net\lambda AB$ is strict if
\[
	\dom\sigma = \{\,x \mid C < \exists x.X \leq A\,\}
			\cup \{\,y \mid D < \exists y.Y \leq B\,\}~.
\]
A linking or pre-net is \defn{strict} if all its links are.

For a labelled linking $\lambda$ and an existential variable $x$, write $\lambda(x)\subseteq\terms$ for the \defn{witness set} of $x$, which collects the terms assigned to $x$ by the links in $\lambda$:
\[
	\lambda(x) = \{~t~\mid~\sigma(x) = t~,~\link AB\in\lambda~\}~.
\]
%
Given a labelled linking $\lambda$, a \defn{slice} $S$ of a formula $A$ is a set of formulas given by: $S=\{A\}\cup S'$ where $S'$ is as follows; if $A$ is of the form
%
\begin{itemize}
	\item
\makebox[40pt][l]{$P$:}				$S'=\varnothing$.
	\item
\makebox[40pt][l]{$B\+C$:} 			$S'=S_B\cup S_C$ where $S_B$ is a slice of $B$ and $S_C$ a slice of $C$.
	\item
\makebox[40pt][l]{$B\*C$:}			$S'$ is a slice of $B$ or a slice of $C$.
	\item
\makebox[40pt][l]{$\exists x.B$:}	$S'$ is a slice of $B$ if the quantifier is vacuous, $x\notin\fv(B)$, and
	\\[\itemsep]
	\hspace*{40pt}					$S'=\uplus_{t\,\in\,\lambda(x)}S_t$ where each $S_t$ is a slice of $B[t/x]$ otherwise.
	\item
\makebox[40pt][l]{$\forall a.B$:}	$S'$ is a slice of $B$.
\end{itemize}
%
A \defn{slice} of a labelled pre-net $\net\lambda AB$ is a set of links
\[
	\{~\link CD\in \lambda~\mid~(C\sigma,D\sigma)\in S_A\times S_B~\}
\]
where $S_A$ is a slice of $A$ and $S_B$ a slice of $B$. A labelled pre-net is \defn{correct} if every slice is a singleton. A coherent pre-net $\net\lambda AB$ is \defn{correct} if its initial labelling $\net{\lambda_\star}AB$ is. Observe that for a \emph{labelled} pre-net correctness and compatibility are independent, while a non-labelled pre-net must be coherent to be correct, since $\lambda_\star$ is otherwise not defined.

\begin{definition}
An \all1 \defn{proof net} is a correct pre-net. An \all1 \defn{labelled proof net} is a correct and coherent labelled pre-net.
\end{definition}

\begin{lemma}
If a labelled pre-net coalesces, it is correct. 
\end{lemma}

\begin{proof}
By induction on the coalescence path we will show that if $\net\lambda AB$ coalesces to $\net{\{\link AB\}}AB$ then $\net{\{\link[\varnothing]{A\sigma}{B\sigma}\}}{A\sigma}{B\sigma}$ is correct. The statement is then the special case $\sigma=\varnothing$.

The result $\net{\{\link[\varnothing]{A\sigma}{B\sigma}\}}{A\sigma}{B\sigma}$ is correct: its only slice is $\{\link[\varnothing]{A\sigma}{B\sigma}\}$, since $A\sigma$ is in any slice $S_{A\sigma}$ of $A\sigma$, and $B\sigma$ is in any slice $S_{B\sigma}$ of $B\sigma$.

\renewcommand{\+}{{+}}
\renewcommand{\*}{{\times}}
\begin{align}
	\net{\{\link AB,\link[\tau]AC\}}A{B\*C}
& ~\scoal~ 
	\net{\{\link[\sigma\join\tau]A{B\*C}\}}A{B\*C}\quad\text{if }\sigma\coh\tau
\tag{$\*$}
\end{align}

Let $\rho=\sigma\join\tau$, and assume that $\net{\{\link[\varnothing]{A\rho}{B\rho\*C\rho}\}}{A\rho}{B\rho\*C\rho}$ is correct.

\end{proof}

\end{document}

Coalescence is effectively sequentialization. We will make this explicit by organising the rewrite rules as inference rules.

%
%As an intermediary between the sequent calculus and labelled proof nets, we will introduce a \defn{labelled sequent calculus}. A \defn{labelled sequent}
%\[
%	\xlink AB
%\]
%is a sequent that carries a linking $\lambda$ and a witness map $\sigma$. 
%
%
%for the statement that $\lambda\seq{A\sigma}{B\sigma}$ coalesces to a single labelled 
%

\begin{figure}
\hrule
\par\bigskip
\[
\begin{array}{c@{\hspace{40pt}}ccc}
	\vc{\infer{\crule [\sigma(P,\dual Q)] [\{(P,Q)\}] P Q}{}}
&    
    \vc{\begin{tikzpicture}[net]
    	\formula[y=2]{P}
    	\formula[y=1]{Q}
    	\Vlink[blue]{1,1}
    \end{tikzpicture}}
&\rightsquigarrow&    
    \vc{\begin{tikzpicture}[net]
    	\formula[y=2]{P}
    	\formula[y=1]{Q}
    	\Vlink[red,label={$~\scriptstyle{\sigma(P,\dual Q)}$}]{1,1}
    \end{tikzpicture}}
\\ \\
	\vc{\infer{\crule A {B\+C}} {\crule AB}}
&   
    \vc{\begin{tikzpicture}[net]
    	\formula[y=2]{A}
    	\formula[y=1]{B\+C}
    	\Vlink[red,label={$\scriptstyle\sigma~$},l]{1,1}
    \end{tikzpicture}}
&\rightsquigarrow& 
    \vc{\begin{tikzpicture}[net]
    	\formula[y=2]{A}
    	\formula[y=1]{B\+C}
    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,2}
    \end{tikzpicture}}
\\ \\ 
    \vc{\infer[\!\!\scriptstyle{\sigma\comp\tau}]
    		{\crule [\sigma\cup\tau] [\lambda\cup\kappa] A {B\*C}}
    		{\crule AB && \crule[\tau][\kappa]AC}}
&     
    \vc{\begin{tikzpicture}[net]
    	\formula[y=2]{A}
    	\formula[y=1]{B\*C}
    	\Vlink[red,label={$\scriptstyle\sigma~$},l]{[-1]1,1}
    	\Vlink[red,label={~$\scriptstyle\tau$}]{[1]1,3}
    \end{tikzpicture}}
&\stackrel{\sigma\comp\tau}\rightsquigarrow&   
	\vc{\begin{tikzpicture}[net]
    	\formula[y=2]{A}
    	\formula[y=1]{B\*C}
    	\Vlink[red,label={~$\scriptstyle{\sigma\cup\tau}$}]{1,2}
    \end{tikzpicture}}

\\ \\
    \vc{\infer{\crule[\sigma\minus x]A{\exists x.B}}{\crule AB}}
&
    \vc{\begin{tikzpicture}[net]
    	\formula[y=2]{A}
    	\formula[y=1]{\exists x.B}
    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,4}
    \end{tikzpicture}}
&\rightsquigarrow&
    \vc{\begin{tikzpicture}[net]
    	\formula[y=2]{A}
    	\formula[y=1]{\exists x.B}
    	\Vlink[red,label={~$\scriptstyle{\sigma\!\minus\!x}$}]{1,1}
    \end{tikzpicture}}
\\ \\
    \vc{\infer[\!\!\scriptstyle{a\,\notin\,\fv(A\sigma)}]{\crule A{\forall a.B}}{\crule AB}}
&    
    \vc{\begin{tikzpicture}[net]
    	\formula[y=2]{A}
    	\formula[y=1]{\forall a.B}
    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,4}
    \end{tikzpicture}}
&\stackrel{a\,\notin\,\fv(A\sigma)}\rightsquigarrow&
    \vc{\begin{tikzpicture}[net]
    	\formula[y=2]{A}
    	\formula[y=1]{\forall a.B}
    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,1}
    \end{tikzpicture}}
\end{array}
\]
\par\bigskip\hrule
\caption{Coalescence derivation rules}
\label{fig:coalescence}
\end{figure}

\begin{lemma}
Given a proof $\prf\Pi AB$, formulas $A'$, $B'$, and a witness map $\sigma$ such that $A'\sigma=A$ and $B'\sigma=B$, the de-sequentialization $\net{\deseq\Pi{A'}{B'}}AB$ coalesces to $\net{\{\link AB\}}AB$. 
\end{lemma}

\begin{lemma}
Given a proof $\prf\Pi AB$ and formulas $A'$ and $B'$, if a smallest witness map $\tau$ exists such that $A=A'\tau$ and $B=B'\tau$, then $\deseq\Pi{A'}{B'}$ coalesces to $\link{A'}{B'}$ with $\sigma\leq\tau$.
\end{lemma}

\begin{proof}
By induction on $\Pi$.

\newlength\prooftablewidth
\setlength\prooftablewidth{-80pt}
\addtolength\prooftablewidth{\textwidth}

\noindent
\begin{tabular}{@{}p{80pt}@{}p{\prooftablewidth}@{}}
	\hfill \raisebox{-20pt}{\infer{\seq P{\dual P}}{\vphantom B}} \hfill\hfill
&
	Let $A'=Q$ and $B'=R$, and suppose $\tau$ is the smallest witness map such that $Q\tau=P$ and $R\tau=\dual P$. The desequentialization $\deseq\Pi QR$ is the $\net{\{Q,R\}}QR$, which coalesces to $\link QR$ if $\sigma=\sigma(Q,{\dual R})$ exists. Since $\tau$ is a unifier of $Q$ and $\dual R$, $\sigma\leq\tau$.	
\\ \\
%	$\infer{\seq A{B_0\+B_1}}{\seq A{B_i}}$
%&
%\\ \\
	\hfill \raisebox{-20pt}{\infer{\seq A{B\*C}}{\seq AB && \seq AC}}\hfill\hfill
&
	Let $\seq{\prf\Pi AB}{A'}{B'}$ coalesce to the two subproofs coalesce to $\link{A'}{B'}$ and $\link[\rho]{A'}{B'}$ 
%	\infer{\seq A{\exists x.B}}{\seq A{B[t/x]}}
%	\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]{\seq A{\forall a.B}}{\seq AB}
\end{tabular}

\end{proof}

\end{document}

%\[
%	\infer{\xlink [\sigma(P,Q)] [\{(P,Q)\}] P Q}{}
%\]
%\par
%\[
%	\infer{\xlink A {B_0\+B_1}} {\xlink A {B_i}}
%\]
%\par
%\[
%	\infer[\!\!\scriptstyle{\sigma\comp\tau}]
%		{\xlink [\sigma\cup\tau] [\lambda\cup\kappa] A {B\*C}}
%		{\xlink AB && \xlink[\tau][\kappa]AC}
%\]
%\par
%\[
%	\infer{\xlink[\sigma\minus x]A{\exists x.B}}{\xlink AB}
%\]
%\par
%\[
%	\infer[\!\!\scriptstyle{a\,\notin\,\fv(A\sigma)}]{\xlink A{\forall a.B}}{\xlink AB}
%\]

% --------------------------------------------------

%\subsection{Existential witnesses}

%
%
%For two first-order terms $s$ and $t$, and a set of variables $V$, let a $V$-\defn{unifier} be a unifying substitution map
%\[
%	\sigma\colon V\rightharpoonup \terms
%\]
%(that is, $s\sigma=t\sigma$). A $V$-unifier for atomic propositions $P$ and $Q$ is defined analogously. For example, 
%
%
%The \defn{most general $V$-unifier} $\sigma_V(P,Q)$ of $P$ and $Q$ is the most general unifying
%
%let the \defn{initial witness map} $\sigma(P,Q)$ be the most general unifier of $P$ and $Q$, if it exists, where only existential variables can be substituted for, and universal variables are considered constant. That is, the only unifier of $p(x,y)$ and $p(a,a)$ is $\{x\mapsto a,y\mapsto a\}$, while $p(x,x)$ and $p(a,b)$ have no unifier.
%
%Let $\sigma\join\tau$ denote the combination of two witness maps $\sigma$ and $\tau$ as unifiers, if it exists. If it does, we call $\sigma$ and $\tau$ \defn{coherent}, expressed by $\sigma\comp\tau$. The initial witness map $\sigma(A,B)$ of two formulae $A$ and $B$, if it exists, is then given by:
%
%\begin{align}
%	\left.\begin{array}{r}
%		\sigma_V(\,A\+B\,,\,C\+D\,) \\
%		\sigma_V(\,A\*B\,,\,C\*D\,)
%	\end{array}\right\}
%	& = \sigma_V(A,C)\join\sigma_V(B,D)
%\\	
%	\sigma_V(\,\forall a.A\,,\,\forall a.B\,)
%		 \kern12.5pt & = \sigma_V(A,B)
%\\	\sigma_V(\,\exists x.A\,,\,\exists x.B\,)
%		 \kern12.5pt & = \sigma_{V-\{x\}}(A,B)
%\end{align*}
%
%
%Two witness maps $\sigma$ and $\tau$ are \defn{coherent}, written $\sigma\comp\tau$, if they agree wherever they are defined:
%\[
%	\sigma\comp\tau \quad\iff\quad \forall x\in\varE.~\big(\sigma(x)\neq\bot~\wedge~\tau(x)\neq\bot\big)~\Rightarrow~\sigma(x)=\tau(x)~.
%\]
%Two coherent witness maps can be combined into the map $\sigma\cup\tau$ that sends $x$ to $\sigma(x)$ or $\tau(x)$, whichever is defined, and is undefined when both are. To combine witness maps that may not be coherent we will write $\sigma\ubot\tau$, which is $\sigma\cup\tau$ if they are, and undefined ($\bot$) otherwise; if either $\sigma$ or $\tau$ is already undefined, $\sigma\ubot\tau$ also reverts to $\bot$.
%\[
%	\sigma\ubot\tau\quad=\quad
%	\left\{\begin{array}{ll}
%		\sigma\cup\tau	& \text{if $\sigma\neq\bot$, $\tau\neq\bot$, and $\sigma\comp\tau$} \\
%		\bot			& \text{otherwise} \\
%	\end{array}\right.
%\] 
%Note that $\bot$ is not a witness map, and different from the empty substitution map, $\sigma(x)=\bot$ for all $x$. For two atomic formulas $P,Q$ (or terms $s,t$) the \defn{initial witness map} $\sigma(P,Q)$ is the smallest witness map $\sigma$ such that $P\sigma=\dual Q\sigma$ and $P\sigma$ has no free existential variables. If it exists, it is defined inductively as follows (omitting the symmetric case for $\dual p$ and $p$). 
%
%\begin{align*}
%	\left.\begin{array}{r}
%		\sigma(\,x\,,\,t\,) \\
%	 	\sigma(\,t\,,\,x\,)
%	\end{array}\right\}
%	& = \{ x\mapsto t \}\quad \text{if $t\in\termsA$}
% \\
%	\left.\begin{array}{r}
%		\sigma(\,p(s_1,\dots,s_n)\,,\,\dual p(t_1,\dots,t_n)\,) \\
%		\sigma(\,f(s_1,\dots,s_n)\,,\,f(t_1,\dots,t_n)\,)
%	\end{array}\right\}
%	& = \sigma(s_1,t_1)\ubot\dots\ubot\sigma(s_n,t_n)
%\end{align*}
%
%\begin{lemma}
%\label{lem:minimal witness map}
%For first-order terms $s$ and $t$ the witness map $\sigma(s,t)$ is the smallest such that $s\sigma=t\sigma$ and $s\sigma$ contains no existential variables.
%\end{lemma}
%
%\begin{proof}
%By induction on $s$ and $t$. If $s=x$ then $\sigma(x,t)$ exists if and only if $t\in\termsA$, 
%\end{proof}

%\begin{align*}
%	\sigma_V(\,a\,,\,a\,) \kern12.5pt & = \varnothing
%\\	\sigma_V(\,x\,,\,x\,) \kern12.5pt & = \varnothing\quad \text{if $x\in V$}
%\\
%	\left.\begin{array}{r}
%		\sigma_V(\,x\,,\,t\,) \\
%	 	\sigma_V(\,t\,,\,x\,)
%	\end{array}\right\}
%	& = \{ x\mapsto t \}\quad \text{if $x\notin V$ and $t\in\termsA$}
% \\
%	\left.\begin{array}{r}
%		\sigma_V(\,p(s_1,\dots,s_n)\,,\,p(t_1,\dots,t_n)\,) \\
%		\sigma_V(\,f(s_1,\dots,s_n)\,,\,f(t_1,\dots,t_n)\,)
%	\end{array}\right\}
%	& = \sigma_V(s_1,t_1)\ubot\dots\ubot\sigma_V(s_n,t_n)
%\\	
%	\left.\begin{array}{r}
%		\sigma_V(\,A\+B\,,\,C\+D\,) \\
%		\sigma_V(\,A\*B\,,\,C\*D\,)
%	\end{array}\right\}
%	& = \sigma_V(A,C)\ubot\sigma_V(B,D)
%\\	
%	\sigma_V(\,\forall a.A\,,\,\forall a.B\,)
%		 \kern12.5pt & = \sigma_V(A,B)
%\\	\sigma_V(\,\exists x.A\,,\,\exists x.B\,)
%		 \kern12.5pt & = \sigma_{V\cup\{x\}}(A,B)
%\end{align*}
%
%Observe that if the witness map $\sigma=\sigma(A,B)$ exists then $A\sigma=B\sigma$.

% --------------------------------------------------

\begin{lemma}
Given a proof $\prf\Pi AB$ and formulas $A'$ and $B'$, if a smallest witness map $\tau$ exists such that $A=A'\tau$ and $B=B'\tau$, then $\deseq\Pi{A'}{B'}$ coalesces to $\link{A'}{B'}$ with $\sigma\leq\tau$.
\end{lemma}

\begin{proof}
By induction on $\Pi$.

\newlength\prooftablewidth
\setlength\prooftablewidth{-80pt}
\addtolength\prooftablewidth{\textwidth}

\noindent
\begin{tabular}{@{}p{80pt}@{}p{\prooftablewidth}@{}}
	\hfill \raisebox{-20pt}{\infer{\seq P{\dual P}}{\vphantom B}} \hfill\hfill
&
	Let $A'=Q$ and $B'=R$, and suppose $\tau$ is the smallest witness map such that $Q\tau=P$ and $R\tau=\dual P$. The desequentialization $\deseq\Pi QR$ is the $\net{\{Q,R\}}QR$, which coalesces to $\link QR$ if $\sigma=\sigma(Q,{\dual R})$ exists. Since $\tau$ is a unifier of $Q$ and $\dual R$, $\sigma\leq\tau$.	
\\ \\
%	$\infer{\seq A{B_0\+B_1}}{\seq A{B_i}}$
%&
%\\ \\
	\hfill \raisebox{-20pt}{\infer{\seq A{B\*C}}{\seq AB && \seq AC}}\hfill\hfill
&
	Let $\seq{\prf\Pi AB}{A'}{B'}$ coalesce to the two subproofs coalesce to $\link{A'}{B'}$ and $\link[\rho]{A'}{B'}$ 
%	\infer{\seq A{\exists x.B}}{\seq A{B[t/x]}}
%	\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]{\seq A{\forall a.B}}{\seq AB}
\end{tabular}

\end{proof}

\begin{description}
	\item[$\sigma\ult\tau$] 
A witness map is \defn{included} in another, $\sigma\ult\tau$, if for every $x\in\varE$, $\sigma(x)=t$ implies $\tau(x)=t$.
	\item[$\sigma\uco\tau$]
Two witness maps are \defn{coherent}, $\sigma\uco\tau$, if for every $x\in\varE$, if $\sigma(x)$ and $\tau(x)$ are both defined then $\sigma(x)=\tau(x)$.
	\item[$\sigma\ujn\tau$]
The \defn{union} of two witness maps $\sigma\ujn\tau$ is defined if they are coherent, and is the map taking $x$ to $\sigma(x)$ or $\tau(x)$ if either is defined.
	\item[$\sigma\gen\tau$]
A witness map is \defn{more general} than another, $\sigma\gen\tau$, if there is a map $\rho$ such that $\sigma\rho=\tau$.
	\item[$\sigma\coh\tau$]
Two witness maps are \defn{coherent}, $\sigma\coh\tau$, if there is a map $\rho$ such that $\sigma\rho=\tau\rho$.
	\item[$\sigma\join\tau$]
The \defn{join} of two witness maps $\sigma\join\tau$ is defined if they are coherent, and is the least map $\rho$ such that $\sigma\gen\rho$ and $\tau\gen\rho$.
\end{description}

The two coalescence relations $(\scoal)$ and $(\ucoal)$ are small-step rewrite relations. We will characterize both as inductive, big-step relations $(\sdown)$ and $(\udown)$. Judgements 
\[
	\sdn\lambda AB
	\qquad\text{and}\qquad
	\udn\lambda AB
\]
will mean that $\net\lambda AB$ strict-coalesces respectively unifying-coalesces to $\net{\link AB}AB$. The relations $(\sdown)$ and $(\udown)$ are defined by the derivation rules given in Figure~\ref{fig:derivations}, where we overload the names of the corresponding rules of $(\scoal)$ and $(\sdown)$, and of $(\ucoal)$ and $(\udown)$.

\begin{proposition}
A pre-net $\net\lambda AB$ is a witness net if and only if $\sdn\lambda[]AB$.
\end{proposition}

%\begin{proof}[Proof sketch]
%
%\end{proof}

\begin{proposition}
A pre-net $\net\lambda AB$ is a unification net if and only if $\udn\lambda[]AB$.
\end{proposition}

We will use both derivation systems to mediate the translation from sequent proofs to proof nets (\defn{de-sequentialization}) and from proof nets to proofs (\defn{sequentialization}). %Firstly, we formalize the isomorphism between sequent proofs and $(\sdown)$-derivations.

\begin{definition}[Witness net (de-)sequentialization]
The relation $\Pi\QU\Sigma$ between sequent proofs $\Pi$ and $(\sdown)$-derivations $\Sigma$ is generated by relating $(\qrr1)$ to $(\srr1)$ and $(\qrr\alpha)$-rules to $(\srr\alpha)$-rules for $\alpha\in\{\,\+_i\,,\,\*\,,\,\exists\,,\,\forall\,\}$. If $\Pi\QU\Sigma$ and $\Sigma$ derives $\sdn\lambda[]AB$ then $\Pi$ \defn{de-sequentializes} to the witness net $\net\lambda AB$ and $\net\lambda AB$ \defn{sequentializes} to $\Pi$.
\end{definition}

\begin{proposition}
The relation $(\QU)$ is an isomorphism.
\end{proposition}

\begin{figure}
\[
\begin{array}{@{}l@{\qquad}c@{\qquad}c@{\qquad}r@{}}
& \textbf{Strict} & \textbf{Unifying}
\\ \\
	(\srr1)
&	\vc{\infer[\!\!\scriptstyle{Q\sigma=\dual R\sigma}]{\sdn{\link QR}QR}{}}
&	\vc{\infer[\!\!\scriptstyle{\sigma\,=\,\sigma(Q,R)}]{\udn{\link[]QR}QR}{}}
&	(\urr1)
\\ \\
	(\srr+i)
&	\vc{\infer{\sdn\lambda A{B_0\+B_1}}{\sdn\lambda A{B_i}}}
&	\vc{\infer{\udn\lambda A{B_0\+B_1}}{\udn\lambda A{B_i}}}
&	(\urr+i)
\\ \\
	(\srr*)
&	\vc{\infer{\sdn{\lambda\cup\kappa}A{B\*C}}{\sdn\lambda AB && \sdn\kappa AC}}
&	\vc{\infer[\!\!\scriptstyle{\sigma\,\coh\,\tau}\vphantom)]{\udn{\lambda\cup\kappa}[\sigma\join\tau]A{B\*C}}{\udn\lambda[\sigma]AB && \udn\kappa[\tau]AC}}
&	(\urr*)
\\ \\
	(\srr?)
&	\vc{\infer[\!\!\scriptstyle{\sigma(x)\,\neq\,\bot}]{\sdn\lambda[\sigma\!\minus\!x]A{\exists x.B}}{\sdn\lambda AB}}
&	\vc{\infer{\udn\lambda[\sigma\!\minus\!x]A{\exists x.B}}{\udn\lambda AB}}
&	(\urr?)
\\ \\
	(\srr!)
&	\vc{\infer[\!\!\scriptstyle{a\,\notin\,\sigma}]{\sdn\lambda A{\forall a.B}}{\sdn\lambda AB}}
&	\vc{\infer[\!\!\scriptstyle{a\,\notin\,\sigma}]{\udn\lambda A{\forall a.B}}{\udn\lambda AB}}
&	(\urr!)
\end{array}
\]
\caption{Derivation rules for (de-)sequentialization}
\label{fig:derivations}
\end{figure}

### 2017-12-19 ALL1-backup-7.tex
initial upload - 10 pages

--- 2017-12-19 ALL1-backup-6.tex
@@
 \newcommand\atom{\textsc{atom}}
+\newcommand\form{\textsc{form}}
+\newcommand\proofs{\textsc{proof}}
 \newcommand\all{\textsc{all}}
@@
 
-\newcommand\deseq[4][\sigma]{[#2]^{#1}_{#3,#4}}
-\newcommand\Deseq[4][\sigma]{\left[\vcenter{#2}\right]^{#1}_{#3,#4}}
+\newcommand\deseq[4][\sigma]{[#2]_{#1}^{#3,#4}}
+\newcommand\Deseq[4][\sigma]{\left[\vcenter{#2}\right]_{#1}^{#3\,,\,#4}}
 
@@
 \newcommand\join{\vee}
+
+\newcommand\init[2]{#1\star #2}
 
@@
 	$P,Q,R$ & $\in \atom$		& atomic propositions \\
-	$A,B,C$ & $\in \all1$		& formulas \\
+	$A,B,C$ & $\in \form$		& \all1 formulas \\
 \end{tabular}
@@
 A sequent calculus for \all1 is given in Figure~\ref{fig:sequent calculus}, where each rule has a symmetric counterpart that applies to the first formula in the sequent.
-We write $\prf\Pi AB$ for a proof $\Pi$ with conclusion sequent $\seq AB$.
+We write $\prf\pi AB$ for a proof $\pi$ with conclusion sequent $\seq AB$.
 Anticipating the requirements of proof nets, we will assume the following convention for \all1 proofs.
@@
 
-% --------------------------------------------------
-
-\subsection{Pre-nets}
-
 By a \defn{subformula} we will mean a subformula \defn{occurrence}.
@@
 
-A \defn{witness map} $\sigma\colon \varE \rightharpoonup \terms$ is a substitution map which assigns terms to existential variables, given as a partial function.
-The \defn{empty} witness map $\varnothing$ is the everywhere undefined partial function, and the map $\sigma[t/x]$ substitutes $t$ for $x$ and is as $\sigma$ everywhere else.
-We express by $\sigma(x)=\bot$ that $\sigma$ is undefined for $x$.
-
-A \defn{link} $(C,D)$ or $\link CD$ on a sequent $\seq AB$ is a pair of subformulas $C\leq A$ and $D\leq B$, possibly carrying a witness map $\sigma$.
-We explicitly call a link $(C,D)$ without witness map \defn{clean}; otherwise $\sigma$ is assumed present.
-We assume the existential variables occurring in the range of $\sigma$ to be fresh, i.e.\ distinct from any existentially quantified variable in $\seq AB$.
+A \defn{link} $(C,D)$ on a sequent $\seq AB$ is a pair of subformulas $C\leq A$ and $D\leq B$. 
 A \defn{linking} $\lambda$ on the sequent $\seq AB$ is a set of links on it.
-The clean linking $\floor\lambda$ forgets the witness maps of a linking $\lambda$.
 
@@
 
-An \defn{axiom link} is a link $\link PQ$ on two propositional atoms such that $P\sigma=\dual Q\sigma$.
-A linking consisting of axiom links is an \defn{axiom linking}.
-For a \emph{clean} axiom link $(P,Q)$ we require that a witness map $\sigma$ exists so that $P\sigma=\dual Q\sigma$.
-
-%A link $\link[\varnothing]CD$ with empty witness map is \defn{clean}; it may then be rendered simply $(C,D)$. A linking or pre-net is \defn{clean} if all its links are. 
-%We write $\floor\lambda$ respectively $\floor{\net\lambda AB}$ for the clean version of a linking or pre-net, which forgets the witness map for each link.
-
-\begin{definition}
-The \defn{de-sequentialization} $[\Pi]$ of a sequent proof $\prf\Pi AB$ is the pre-net $\net{\deseq[\varnothing]\Pi AB} AB$ where $\deseq-AB$ is defined as follows.
-%
-\begin{align*}
-	\Deseq{\infer{\seq P{\dual P}}{}}QR &\quad=\quad \{\link QR\}
-\\ \\
-	\Deseq{\infer {\seq A {B_0\+B_1}} {\deduce [\rule{0pt}{1pt}] {\seq A{B_i}} \Pi }}
-	  {A'}{B_0'\+B'_1} 
-	& \quad=\quad 
-	\Deseq{\deduce[\rule{0pt}{1pt}]{\seq A{B_i}}\Pi}{A'}{B_i'}
-\\ \\
-	\Deseq{\infer{\seq A{B\*C}}{
-	  \deduce[\rule{0pt}{1pt}]{\seq AB}\Pi 
-	  && 
-	  \deduce[\rule{0pt}{1pt}]{\seq AC}\Sigma}}{A'}{B'\*C'}
-	& \quad=\quad 
-	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AB}\Pi}{A'}{B'}
-	  \cup
-	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AC}\Sigma}{A'}{C'}
-\\ \\
-	\Deseq{\infer{\seq A{\exists x.B}}{\deduce[\rule{0pt}{1pt}]{\seq A{B[t/x]}}\Pi}}
-	  {A'}{\exists x.B'}
-	& \quad=\quad 
-	 \Deseq[{\sigma[t/x]}]{\deduce[\rule{0pt}{1pt}]{\seq A{B[t/x]}}\Pi}
-	  {A'}{B'}
-\\ \\
-	\Deseq{\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]
-	  {\seq A{\forall a.B}}{\deduce[\rule{0pt}{1pt}]{\seq AB}\Pi}}{A'}{\forall a.B'}
-	& \quad=\quad 
-	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AB}\Pi}{A'}{B'}
-\end{align*}
-%
-The \defn{clean} de-sequentialization $\floor\Pi$ is $\net{\floor{\deseq[\varnothing]\Pi AB}}AB$:  as $[\Pi]$ but forgetting witness maps.
-%
-%of $\prf\Pi AB$ is the de-sequentialization $[\Pi]$ which forgets witness maps.
-\end{definition}
-
-Observe that the linking of $[\Pi]$ is an axiom linking, and that of $\floor\Pi$ a clean axiom linking.
-
 % --------------------------------------------------
@@
 
+A \defn{witness map} $\sigma\colon \varE \rightharpoonup \terms$ is a substitution map which assigns terms to existential variables, given as a (finite) partial function.
+The \defn{empty} witness map $\varnothing$ is the everywhere undefined partial function, and the map $\sigma[t/x]$ substitutes $t$ for $x$ and is as $\sigma$ everywhere else.
+We express by $\sigma(x)=\bot$ that $\sigma$ is undefined for $x$.
+The map $\sigma\minus x$ is undefined on $x$ and otherwise as $\sigma$.
+
 We will write $A\sigma$ for the application of the witness map $\sigma\colon\varE\rightharpoonup\terms$ to the formula $A$ as a substitution map.
-It is applied to a sequent proof, $\Pi\sigma$, by applying it to each formula in the proof $\Pi$.
+It is applied to a sequent proof, $\pi\sigma$, by applying it to each formula in the proof $\pi$.
 The \defn{composition} of two maps is written $\sigma\tau$, where $A(\sigma\tau)=(A\sigma)\tau$.
-The map $\sigma\minus x$ is undefined on $x$ and otherwise as $\sigma$.
-%, and $\sigma|X$ is as $\sigma$ on the set of variables $X$ and undefined otherwise. 
-We abbreviate the statement that a (universal) variable $a$ occurs free in some term in the range of $\sigma$, $a\in\fv(\sigma(x))$ for some $x$, by $a\in \sigma$.
 We define the following further operations on witness maps.
@@
 
-To a clean axiom link $(P,Q)$ we assign an \defn{initial witness map} $\sigma(P,Q)$ as the least witness map $\sigma$ in $(\gen)$ such that $P\sigma=\dual Q\sigma$.
-In other words, $\sigma(P,Q)$ is the most general unifier ($\textsc{mgu}$) of $P$ and $\dual Q$.
-The \defn{initial witness assignment} $\lambda_\star$ to a clean axiom linking is:
-\[
-	\lambda_\star = \{~\link PQ~\mid~(P,Q)\in\lambda~,~\sigma=\sigma(P,Q)~\}~.
-\]
+A \defn{witness linking} $\lambda_\Sigma$ is a linking $\lambda$ with a \defn{witness labelling}  $\Sigma\colon\lambda\to \varE\rightharpoonup\terms$ that assigns each link $(C,D)$ a witness map. 
+We may use and define $\lambda_\Sigma$ as a set of \defn{witness links} $\link CD$, which indicates the link $(C,D)$ in $\lambda$ where $\Sigma(C,D)=\sigma$.
+
+\begin{definition}
+A \defn{witness pre-net} $\net{\lambda_\Sigma}AB$ is a pre-net with a witness linking $\lambda_\Sigma$.
+\end{definition}
+
+We assume the existential variables occurring in the range of $\Sigma$ to be fresh, i.e.\ distinct from any existentially quantified variable in $\seq AB$.
+We abbreviate by $a\in \sigma$ the statement that a (universal) variable $a$ occurs free in the range of $\sigma$, i.e.\ that $a\in\fv(\sigma(x))$ for some $x$.
+
+\begin{definition}
+The \defn{de-sequentialization} $[\pi]$ of a sequent proof $\prf\pi AB$ is the witness pre-net $\net{\lambda_\Sigma}AB$ where $\lambda_\Sigma=\deseq[\varnothing]\pi AB$ and $\deseq-AB$ is defined as follows.
+%
+\newlength\deseqwidth
+\settowidth\deseqwidth{$\scriptstyle{A'\,,\,B'_0\+B'_1}$}
+\newcommand\XDeseq[4][\sigma]{\left[\vcenter{#2}\right]_{#1}^{\makebox[\deseqwidth][l]{$\scriptstyle{#3\,,\,#4}$}}}
+\begin{align*}
+	\XDeseq{\infer{\seq P{\dual P}}{}}QR &\quad=\quad \{\link QR\}
+\\ \\
+	\XDeseq{\infer {\seq A {B_0\+B_1}} {\deduce [\rule{0pt}{1pt}] {\seq A{B_i}} \pi }}
+	  {A'}{B_0'\+B'_1} 
+	& \quad=\quad 
+	\Deseq{\deduce[\rule{0pt}{1pt}]{\seq A{B_i}}\pi}{A'}{B_i'}
+\\ \\
+	\XDeseq{\infer{\seq A{B\*C}}{
+	  \deduce[\rule{0pt}{1pt}]{\seq AB}\pi 
+	  && 
+	  \deduce[\rule{0pt}{1pt}]{\seq AC}\Sigma}}{A'}{B'\*C'}
+	& \quad=\quad 
+	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AB}\pi}{A'}{B'}
+	  \cup
+	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AC}\Sigma}{A'}{C'}
+\\ \\
+	\XDeseq{\infer{\seq A{\exists x.B}}{\deduce[\rule{0pt}{1pt}]{\seq A{B[t/x]}}\pi}}
+	  {A'}{\exists x.B'}
+	& \quad=\quad 
+	 \Deseq[{\sigma[t/x]}]{\deduce[\rule{0pt}{1pt}]{\seq A{B[t/x]}}\pi}
+	  {A'}{B'}
+\\ \\
+	\XDeseq{\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]
+	  {\seq A{\forall a.B}}{\deduce[\rule{0pt}{1pt}]{\seq AB}\pi}}{A'}{\forall a.B'}
+	& \quad=\quad 
+	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AB}\pi}{A'}{B'}
+\end{align*}
+\end{definition}
+
+A witness link $\link PQ$ or link $(P,Q)$ on two atomic formulas $P$ and $Q$ is an \defn{axiom} link if $P\sigma=\dual Q\sigma$, or respectively, if some $\sigma$ exists such that $P\sigma=\dual Q\sigma$.
+An \defn{axiom} (witness) linking is one consisting only of axiom links.
+Observe that in the de-sequentialization $[\pi]$ the witness linking $\deseq[\varnothing]\pi AB$ is an axiom linking.
+
+To an axiom link $(P,Q)$ we assign an \defn{initial witness map} $\sigma=\init PQ$ as the least witness map in $(\gen)$ such that $P\sigma=\dual Q\sigma$ --- in other words, $\init PQ$ is the most general unifier ($\textsc{mgu}$) of $P$ and $\dual Q$.
+An axiom linking $\lambda$ with the initial witness map assigned to each link will be written $\lambda_\star$:
+\[
+	\lambda_\star = \{~\link PQ~\mid~(P,Q)\in\lambda~,~\sigma=\init PQ~\}~.
+\]
+
+For two witness labellings $\Sigma$ and $\Xi$ on the same linking $\lambda$, one is \defn{more general} than the other, $\Sigma\gen\Xi$, if $\Sigma(C,D)\gen\Xi(C,D)$ for every link $(C,D)\in\lambda$.
+$\lambda_\Sigma\gen\lambda_\Xi$,
+
+Observe that for an axiom linking $\lambda$, the initial linking $\lambda_\star$ is the most general among the witness linkings $\lambda_\Sigma$ for any $\Sigma$.
 
@@
 
-For sequentialization, the links in a pre-net are labelled with a sequent calculus axiom, and each coalescence rewrite step introduces one proof rule.
-To this end, let a \defn{labelled link} $\link AB^\Pi$ be a link carrying a sequent proof $\prf\Pi{A\sigma}{B\sigma}$, and a \defn{labelled linking} or \defn{labelled pre-net} one where every link is labelled.
-The \defn{initial labelling} $\lambda^\star$ of an axiom linking $\lambda$ is:
-\[
-	\lambda^\star = \{~\link PQ^\Pi~\mid~\link PQ\in\lambda~,~\Pi=~\infer{\seq{P\sigma}{Q\sigma}}{}~\}~.
+For sequentialization, the links in a pre-net will be labelled with a sequent proof.
+An axiom link will carry an axiom, and each coalescence step introduces one proof rule.
+A \defn{proof linking} $\lambda_\Sigma^\Pi$ is a witness linking $\lambda_\Sigma$ with a \defn{proof labelling} $\Pi\colon \lambda\to\proofs$ assigning each link a sequent proof.
+We will use and define $\lambda_\Sigma^\Pi$ as a set of \defn{proof links} $\link CD^\pi$, where we assume that $\prf\pi{C\sigma}{D\sigma}$.
+
+Let a \defn{labelled link} $\link AB^\pi$ be a link carrying a sequent proof $\prf\pi{A\sigma}{B\sigma}$, and a \defn{labelled linking} or \defn{labelled pre-net} one where every link is labelled.
+The \defn{initial labelling} $\lambda_\Sigma^\star$ of an axiom linking $\lambda_\Sigma$ is:
+\[
+	\lambda_\Sigma^\star = \{~\link PQ^\pi~\mid~\link PQ\in\lambda_\Sigma~,~\pi=~\infer{\seq{P\sigma}{Q\sigma}}{}~\}~.
 \]
 For correctness we may coalesce a pre-net without constructing a proof. 
+%
+To recap, we have accumulated the following further notational conventions.
+%
+\[
+\begin{tabular}{@{}lcll@{}}
+	$\kappa,\lambda$ 	& $\subset$ & $\form\times\form$ 	& linkings (sets of pairs of formulas)\\
+	$\rho,\sigma,\tau$	& $\colon$  & $\varE\rightharpoonup\terms$ & witness maps\\
+	$\Sigma,\Xi$		& $\colon$  & $(\form\times\form)\rightharpoonup\varE\rightharpoonup\terms$		& witness labellings on a linking \\
+	$\pi,\phi,\psi$		& $\in$ & $\proofs$ & \all1 sequent proofs\\
+	$\Pi,\Phi,\Psi$		& $\colon$  & $(\form\times\form)\rightharpoonup\proofs$		& proof labellings on a linking
+\end{tabular}
+\]
 
@@
  \defn{Strict sequentialization} ($\scoal$) is the rewrite relation on labelled pre-nets generated by the following rules, which apply symmetrically to the first formula in the sequent.
-\defn{Strict coalescence} is the same relation ignoring proof labels, on pre-nets.
+\defn{Strict coalescence} is the same relation ignoring proof labels, on witness pre-nets.
 %
@@
 \begin{equation}
-  	\net{\{\link A{B_i}^\Pi\}}A{B_0\+B_1} 
+  	\net{\{\link A{B_i}^\pi\}}A{B_0\+B_1} 
  ~\scoal~
-	\net{\{\link A{B_0\+B_1} ^\Psi\}}A{B_0\+B_1}
+	\net{\{\link A{B_0\+B_1} ^\psi\}}A{B_0\+B_1}
 \tag{$\srr+i$}
@@
 
-\hfill $\text{where}\quad \Psi=~
+\hfill $\text{where}\quad \psi=~
   \vc{
    \infer  {\seq{A\sigma}{B_0\sigma\,\+\,B_1\sigma}}  {
-  	\deduce  [\rule{0pt}{1pt}]  {\seq{A\sigma}{B_i\sigma}}  \Pi
+  	\deduce  [\rule{0pt}{1pt}]  {\seq{A\sigma}{B_i\sigma}}  \pi
   }}
@@
 \begin{equation}
-	\net{\{\link AB^\Pi,\link AC^\Phi\}}A{B\*C}
+	\net{\{\link AB^\pi,\link AC^\phi\}}A{B\*C}
  ~\scoal~ 
-	\net{\{\link A{B\*C}^\Psi\}}A{B\*C}
+	\net{\{\link A{B\*C}^\psi\}}A{B\*C}
 \tag{$\srr*$}
@@
 
-\hfill $\text{where}\quad \Psi=~
+\hfill $\text{where}\quad \psi=~
   \vc{
    \infer  {\seq{A\sigma}{B\sigma\,\*\,C\sigma}}  {
-    \deduce  [\rule{0pt}{1pt}]  {\seq{A\sigma}{B\sigma}}  \Pi
-    &
-    \deduce  [\rule{0pt}{1pt}]  {\seq{A\sigma}{C\sigma}}  \Phi    
+    \deduce  [\rule{0pt}{1pt}]  {\seq{A\sigma}{B\sigma}}  \pi
+    &
+    \deduce  [\rule{0pt}{1pt}]  {\seq{A\sigma}{C\sigma}}  \phi    
   }}$ \hspace*{20pt}
@@
 \begin{equation}
-	\net{\{\link AB^\Pi\}}A{\exists x.B}
+	\net{\{\link AB^\pi\}}A{\exists x.B}
  ~\scoal~ 
-	\net{\{\link[\sigma\!\minus\!x]A{\exists x.B}^\Psi\}}A{\exists x.B}
+	\net{\{\link[\sigma\!\minus\!x]A{\exists x.B}^\psi\}}A{\exists x.B}
 \tag{$\srr?$}
@@
 		\quad
-		\text{and}\quad \Psi=~
+		\text{and}\quad \psi=~
   \vc{
    \infer  {\seq{A\tau}{\exists x.B\tau}}  {
-    \deduce  [\rule{0pt}{1pt}]  {\seq{A\sigma}{B\sigma}}  \Pi  
+    \deduce  [\rule{0pt}{1pt}]  {\seq{A\sigma}{B\sigma}}  \pi  
   }}
@@
 		\quad
-		\text{where}\quad \Psi=~
+		\text{where}\quad \psi=~
   \vc{
    \infer  {\seq{A\sigma}{\forall a.B\sigma}}  {
-    \deduce  [\rule{0pt}{1pt}]  {\seq{A\sigma}{B\sigma}}  \Pi  
+    \deduce  [\rule{0pt}{1pt}]  {\seq{A\sigma}{B\sigma}}  \pi  
   }}
@@
 \noindent
-A pre-net $\net\lambda AB$ \defn{strict-coalesces} if it reduces in $(\scoal)$ to a single link $\net{\{\link[\varnothing]AB\}}AB$.
+A pre-net $\net{\lambda_\Sigma}AB$ \defn{strict-coalesces} if it reduces in $(\scoal)$ to a single link $\net{\{\link[\varnothing]AB\}}AB$.
 \end{definition}
 
-To be explicit, to generate coalescence as a rewrite relation means the following: a pre-net coalesces to another, $\net\lambda AB\scoal \net{\lambda'}AB$ if and only if there is a rewrite rule $\net\kappa CD\scoal\net{\kappa'} CD$ such that $C\leq A$, $D\leq B$, $\kappa\subseteq\lambda$, $\kappa'\subseteq\lambda'$, and $\lambda-\kappa=\lambda'-\kappa'$.
+To be explicit, to generate coalescence as a rewrite relation means the following: a pre-net coalesces to another, $\net{\lambda_\Sigma} AB\scoal \net{{\lambda'_{\Sigma'}}}AB$ if and only if % there is a rewrite rule $\net{\kappa_\Xi} CD\scoal\net{\kappa'_{\Xi'}} CD$ such that $C\leq A$, $D\leq B$, ${\kappa_\Xi}\subseteq{\lambda_\Sigma}$, $\kappa'_{\Xi'}\subseteq{\lambda'_{\Sigma'}}$, and ${\lambda_\Sigma}-{\kappa_\Xi}={\lambda'_{\Sigma'}}-\kappa'_{\Xi'}$.
+there is a rewrite rule
+\[
+	\net{\kappa_\Xi} CD\scoal\net{\kappa'_{\Xi'}} CD
+\] 
+such that 
+\[
+	C\leq A \qquad
+	D\leq B \qquad
+	\kappa_\Xi\subseteq\lambda_\Sigma \qquad
+	\kappa'_{\Xi'}\subseteq\lambda'_{\Sigma'} \quad
+	\text{and} \quad
+	\lambda_\Sigma-\kappa_\Xi=\lambda'_{\Sigma'}-\kappa'_{\Xi'}~.
+\]
 
@@
 \begin{equation}
-	\net{\{\link AB^\Pi,\link[\tau]AC^\Phi\}}A{B\*C}
+	\net{\{\link AB^\pi,\link[\tau]AC^\phi\}}A{B\*C}
  ~\ucoal~ 
-	\net{\{\link[\sigma\join\tau]A{B\*C}^\Psi\}}A{B\*C}
+	\net{\{\link[\sigma\join\tau]A{B\*C}^\psi\}}A{B\*C}
 \tag{$\urr*$}
@@
 		\quad
-		\text{and}\quad \Psi=~
+		\text{and}\quad \psi=~
   \vc{
    \infer  {\seq{A\sigma\rho}{B\sigma\rho\,\*\,C\sigma\rho}}  {
-    \left( \vc{\deduce  [\rule{0pt}{2pt}]  {\seq{A\sigma}{B\sigma}}  \Pi} \right)\rho
-    &
-    \left( \vc{\deduce  [\rule{0pt}{2pt}]  {\seq{A\tau}{C\tau}}  \Phi} \right)\rho   
+    \left( \vc{\deduce  [\rule{0pt}{2pt}]  {\seq{A\sigma}{B\sigma}}  \pi} \right)\rho
+    &
+    \left( \vc{\deduce  [\rule{0pt}{2pt}]  {\seq{A\tau}{C\tau}}  \phi} \right)\rho   
   }}~.
@@
 
-%A pre-net $\net\lambda AB$ \defn{coalesces}, in either relation , if it coalesces to a single clean link $\net{(A,B)^\Pi}AB$.
+%A pre-net $\net\lambda AB$ \defn{coalesces}, in either relation , if it coalesces to a single clean link $\net{(A,B)^\pi}AB$.
 In that case, it \defn{sequentializes} It \defn{strongly coalesces} if every coalescence sequence can be extended to reach $\net{(A,B)}AB$.
@@
 \begin{definition}
-An \all1 \defn{witnessing proof net} or \defn{witness net} is a pre-net $\net\lambda AB$ with axiom linking $\lambda$ that strict-coalesces.
-It \defn{sequentializes} to a proof $\Pi$ if its initial labelling $\net{\lambda^\star}AB$ reduces in $(\scoal)$ to $\net{\{\link[\varnothing]AB^\Pi\}}AB$.
+An \all1 \defn{witnessing proof net} or \defn{witness net} is a witness pre-net $\net{\lambda_\Sigma}AB$, with $\lambda_\Sigma$ an axiom linking, that strict-coalesces.
+It \defn{sequentializes} to a proof $\pi$ if its initial labelling $\net{\lambda_\Sigma^\star}AB$ reduces in $(\scoal)$ to $\net{\{\link[\varnothing]AB^\pi\}}AB$.
 \end{definition}
@@
 An \all1 \defn{unification proof net} or \defn{unification net} is a pre-net $\net\lambda AB$ with clean axiom linking $\lambda$ such that its initial witness assignment $\net{\lambda_\star}AB$ unifying-coalesces.
-It \defn{sequentializes} to $\Pi$ if the initial labelling $\net{\lambda^\star_\star}AB$ reduces in $(\ucoal)$ to $\net{\{\link[\varnothing]AB^\Pi\}}AB$.
+It \defn{sequentializes} to $\pi$ if the initial labelling $\net{\lambda^\star_\star}AB$ reduces in $(\ucoal)$ to $\net{\{\link[\varnothing]AB^\pi\}}AB$.
 \end{definition}
@@
 \begin{theorem}
-For any \all1 proof $\Pi$:
+For any \all1 proof $\pi$:
 \begin{enumerate}
-\item the de-sequentialization $[\Pi]$ is a witness net that sequentializes to $\Pi$. 
-\item the clean de-sequentialization $\floor\Pi$ is a unification net that sequentializes to a proof $\Phi$ such that $\Pi=\Phi\rho$ for some witness map $\rho$ (where universal variables may be captured).
+\item the de-sequentialization $[\pi]$ is a witness net that sequentializes to $\pi$. 
+\item the clean de-sequentialization $\floor\pi$ is a unification net that sequentializes to a proof $\phi$ such that $\pi=\phi\rho$ for some witness map $\rho$ (where universal variables may be captured).
 \end{enumerate}
@@
 \begin{proof}
-By induction on $\prf\Pi AB$, if $\lambda=[\Pi]_{A',B'}^\sigma$ where $A'\sigma=A$ and $B'\sigma=B$, then $\net{\lambda^\star}AB$ reduces in $(\scoal)$ to $\net{\{\link{A'}{B'}^\Pi\}}AB$.
+By induction on $\prf\pi AB$, if $\lambda=[\pi]_{A',B'}^\sigma$ where $A'\sigma=A$ and $B'\sigma=B$, then $\net{\lambda^\star}AB$ reduces in $(\scoal)$ to $\net{\{\link{A'}{B'}^\pi\}}AB$.
 Statement 1.\ is the specific case $\sigma=\varnothing$.
@@
 
- on $\prf\Pi AB$, if $\lambda=\floor{\deseq\Pi{A'}{B'}}$ where $A'\sigma=A$ and $B'\sigma=B$, then $\net{\lambda^\star_\star}AB$ reduces in $(\ucoal)$ to $\net{\{\link{A'}{B'}\}}{}{}$
+ on $\prf\pi AB$, if $\lambda=\floor{\deseq\pi{A'}{B'}}$ where $A'\sigma=A$ and $B'\sigma=B$, then $\net{\lambda^\star_\star}AB$ reduces in $(\ucoal)$ to $\net{\{\link{A'}{B'}\}}{}{}$
 \end{proof}
@@
 \begin{lemma}
-Given a proof $\prf\Pi AB$, formulas $A'$, $B'$, and a witness map $\sigma$ such that $A'\sigma=A$ and $B'\sigma=B$, the de-sequentialization $\net{\deseq\Pi{A'}{B'}}AB$ coalesces to $\net{\{\link AB\}}AB$.
+Given a proof $\prf\pi AB$, formulas $A'$, $B'$, and a witness map $\sigma$ such that $A'\sigma=A$ and $B'\sigma=B$, the de-sequentialization $\net{\deseq\pi{A'}{B'}}AB$ coalesces to $\net{\{\link AB\}}AB$.
 \end{lemma}
@@
 \begin{lemma}
-Given a proof $\prf\Pi AB$ and formulas $A'$ and $B'$, if a smallest witness map $\tau$ exists such that $A=A'\tau$ and $B=B'\tau$, then $\deseq\Pi{A'}{B'}$ coalesces to $\link{A'}{B'}$ with $\sigma\leq\tau$.
+Given a proof $\prf\pi AB$ and formulas $A'$ and $B'$, if a smallest witness map $\tau$ exists such that $A=A'\tau$ and $B=B'\tau$, then $\deseq\pi{A'}{B'}$ coalesces to $\link{A'}{B'}$ with $\sigma\leq\tau$.
 \end{lemma}
@@
 \begin{proof}
-By induction on $\Pi$.
+By induction on $\pi$.
 
@@
 	Let $A'=Q$ and $B'=R$, and suppose $\tau$ is the smallest witness map such that $Q\tau=P$ and $R\tau=\dual P$.
-The desequentialization $\deseq\Pi QR$ is the $\net{\{Q,R\}}QR$, which coalesces to $\link QR$ if $\sigma=\sigma(Q,{\dual R})$ exists.
+The desequentialization $\deseq\pi QR$ is the $\net{\{Q,R\}}QR$, which coalesces to $\link QR$ if $\sigma=\sigma(Q,{\dual R})$ exists.
 Since $\tau$ is a unifier of $Q$ and $\dual R$, $\sigma\leq\tau$.
@@
 &
-	Let $\seq{\prf\Pi AB}{A'}{B'}$ coalesce to the two subproofs coalesce to $\link{A'}{B'}$ and $\link[\rho]{A'}{B'}$ 
+	Let $\seq{\prf\pi AB}{A'}{B'}$ coalesce to the two subproofs coalesce to $\link{A'}{B'}$ and $\link[\rho]{A'}{B'}$ 
 %	\infer{\seq A{\exists x.B}}{\seq A{B[t/x]}}
@@
 \begin{definition}[Witness net (de-)sequentialization]
-The relation $\Pi\QU\Sigma$ between sequent proofs $\Pi$ and $(\sdown)$-derivations $\Sigma$ is generated by relating $(\qrr1)$ to $(\srr1)$ and $(\qrr\alpha)$-rules to $(\srr\alpha)$-rules for $\alpha\in\{\,\+_i\,,\,\*\,,\,\exists\,,\,\forall\,\}$.
-If $\Pi\QU\Sigma$ and $\Sigma$ derives $\sdn\lambda[]AB$ then $\Pi$ \defn{de-sequentializes} to the witness net $\net\lambda AB$ and $\net\lambda AB$ \defn{sequentializes} to $\Pi$.
+The relation $\pi\QU\Sigma$ between sequent proofs $\pi$ and $(\sdown)$-derivations $\Sigma$ is generated by relating $(\qrr1)$ to $(\srr1)$ and $(\qrr\alpha)$-rules to $(\srr\alpha)$-rules for $\alpha\in\{\,\+_i\,,\,\*\,,\,\exists\,,\,\forall\,\}$.
+If $\pi\QU\Sigma$ and $\Sigma$ derives $\sdn\lambda[]AB$ then $\pi$ \defn{de-sequentializes} to the witness net $\net\lambda AB$ and $\net\lambda AB$ \defn{sequentializes} to $\pi$.
 \end{definition}

### 2017-12-19 ALL1.tex
initial upload - 10 pages

--- 2017-12-19 ALL1-backup-7.tex
@@
 
+\newcommand\ex[2]{\textsc{ex}_{#1}(#2)}
+
 \newcommand\subs[1]{\textsc{sub}(#1)}
+\newcommand\poss[1]{\textsc{pos}(#1)}
 \newcommand\dom[1]{\textsc{dom}(#1)}
@@
 \newcommand\sub{\leq}
+\newcommand\dep{\preccurlyeq}
+%\newcommand\dep{\stackrel\star{\smash\preccurlyeq\rule{0pt}{1ex}}}
+
 \newcommand\seq[3][]{{\vdash_{#1}}#2,#3}
@@
 \newcommand\link[3][\sigma]{(#2,#3)_{#1}}
-\newcommand\minus{\mathop{/\mathchoice{\kern-3pt}{\kern-3pt}{\kern-2.5pt}{\kern-2pt}/}}
+\newcommand\minus{\mathop{\!/\mathchoice{\kern-3pt}{\kern-3pt}{\kern-2.5pt}{\kern-2pt}/\!}}
 
@@
 \formula[y=0]{\exists y.~{\dual p}(y,s)\*{\dual p}(y,t)}
-\Vlink[red,label={$\quad\scriptstyle{\upsilon\!\minus\!y}$}]{8,1}
+\Vlink[red,label={$\quad\scriptstyle{\upsilon\minus y}$}]{8,1}
 \end{tikzpicture}
@@
 \formula[y=0]{\exists y.~{\dual p}(y,s)\*{\dual p}(y,t)}
-\Vlink[red,label={$~\scriptstyle{\upsilon\!\minus\!y}$}]{4,1}
+\Vlink[red,label={$~\scriptstyle{\upsilon\minus y}$}]{4,1}
 \end{tikzpicture}
@@
 
+%\begin{figure}
+%\[
+%	\infer{\seq P{\dual P}}{}
+%\qquad
+%	\infer{\seq A{B_0\+B_1}}{\seq A{B_i}}
+%\qquad
+%	\infer{\seq A{B\*C}}{\seq AB && \seq AC}
+%\qquad
+%	\infer{\seq A{\exists x.B}}{\seq A{B[t/x]}}
+%\qquad
+%	\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]{\seq A{\forall a.B}}{\seq AB}
+%\]
+%\caption{A sequent calculus for $\all1$}
+%\label{fig:sequent calculus}
+%\end{figure}
+
 \begin{figure}
-\[
-	\infer{\seq P{\dual P}}{}
-\qquad
-	\infer{\seq A{B_0\+B_1}}{\seq A{B_i}}
-\qquad
-	\infer{\seq A{B\*C}}{\seq AB && \seq AC}
-\qquad
-	\infer{\seq A{\exists x.B}}{\seq A{B[t/x]}}
-\qquad
-	\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]{\seq A{\forall a.B}}{\seq AB}
-\]
-\caption{A sequent calculus for $\all1$}
-\label{fig:sequent calculus}
-\end{figure}
-
-\begin{figure}
-\noindent\hrule
 \[
@@
 	$a,b,c$ & $\in \varA$ 		& universally quantified variables (and free variables)\\
-	$x,y,z$ & $\in \varE$		& existentially quantified variables \\
+	$x,y,z$ & $\in \varE$		& existentially quantified variables (and term-language variables)\\
 	$f,g,h$ & $\in \Sigma_f$	& $n$-ary $(n\geq 0)$ function symbols from a fixed alphabet $\Sigma_f$\\
@@
 We write $\prf\pi AB$ for a proof $\pi$ with conclusion sequent $\seq AB$.
-Anticipating the requirements of proof nets, we will assume the following convention for \all1 proofs.
+
+By a \defn{subformula} we will mean a subformula \defn{occurrence}.
+For instance, a formula $A\*A$ has two subformulas $A$, one on the left and one on the right.
+The \defn{subformulas} $\subs A$ of a formula are defined as follows; we write $B\sub A$ if $B$ is a subformula of $A$, i.e.\ if $B\in\subs A$.
+\[
+	\subs A = \{A\} \cup
+	\left\{\begin{array}{ll}
+		\subs B\uplus\subs C	& \text{if $A=B\+C$ or $A=B\*C$} \\[5pt]
+		\subs B					& \text{if $A=\exists x.B$ or $A=\forall a.B$}
+	\end{array}\right.
+\]
+
+A \defn{link} $(C,D)$ on a sequent $\seq AB$ is a pair of subformulas $C\leq A$ and $D\leq B$. 
+A \defn{linking} $\lambda$ on the sequent $\seq AB$ is a set of links on it.
+
+\begin{definition}
+A \defn{pre-net} $\net\lambda AB$ is a sequent $\seq AB$ with a linking $\lambda$ on it.
+\end{definition}
+
+% --------------------------------------------------
+
+\subsection{Witness maps}
+
+A \defn{witness map} $\sigma\colon \varE \rightharpoonup \terms$ is a substitution map which assigns terms to existential variables, given as a (finite) partial function.
+Its \defn{domain} $\dom(\sigma)$ are those variables for which it is defined.
+The \defn{empty} witness map $\varnothing$ is the everywhere undefined partial function, and the map $\sigma[t/x]$ substitutes $t$ for $x$ and is as $\sigma$ everywhere else.
+We express by $\sigma(x)=\bot$ that $\sigma$ is undefined for $x$.
+The map $\sigma\minus x$ is undefined on $x$ and otherwise as $\sigma$.
+
+We will write $A\sigma$ for the application of the witness map $\sigma\colon\varE\rightharpoonup\terms$ to the formula $A$ as a substitution map.
+It is applied to a sequent proof, $\pi\sigma$, by applying it to each formula in the proof $\pi$.
+The \defn{composition} of two maps is written $\sigma\tau$, where $A(\sigma\tau)=(A\sigma)\tau$.
+
+A \defn{witness linking} $\lambda_\Sigma$ is a linking $\lambda$ with a \defn{witness labelling} $\Sigma\colon\lambda\to \varE\rightharpoonup\terms$ that assigns each link $(C,D)$ a witness map.
+We may use and define $\lambda_\Sigma$ as a set of \defn{witness links} $\link CD$, where $(C,D)$ in $\lambda$ and $\Sigma(C,D)=\sigma$.
+When link is not a witness link may be emphasized by calling it \defn{clean}.
+
+\begin{definition}
+A \defn{witness pre-net} $\net{\lambda_\Sigma}AB$ is a sequent $\seq AB$ with a witness linking $\lambda_\Sigma$.
+%
+%\begin{description}
+%	\item[Exact coverage]
+%The domain of $\sigma$ is exactly the variables existentially quantified in $\seq AB$ that will be bound in $C$ and $D$, if they occur:
+%\[
+%	\dom\sigma = \{\,x \mid C < \exists x.X \leq A\,\}
+%			\cup \{\,y \mid D < \exists y.Y \leq B\,\}~.
+%\]
+%
+%	\item[Eigenvariables not free]
+%A universal variable $a\in\varA$ quantified in $C$ or $D$ may not occur free in the range of $\sigma$, $a\notin\sigma$.
+%
+%	\item[Freshness]
+%Existential variables in the range of $\sigma$ are fresh, i.e.\ distinct from any existentially quantified variable in $\seq AB$.
+%\end{description}
+\end{definition}
+
+We will assume the following variable naming conventions for \all1 pre-nets.
 
@@
 %\]
+
+	\item[Eigenvariables not free]
+For a link $\link CD$, a universal variable $a\in\varA$ quantified in $C$ or $D$ may not occur free in the range of $\sigma$, $a\notin\sigma$.
+
+	\item[Freshness]
+For a link $\link CD$, existential variables in the range of $\sigma$ are fresh, i.e.\ distinct from any existentially quantified variable in $\seq AB$.
 \end{description}
 
-By a \defn{subformula} we will mean a subformula \defn{occurrence}.
-For instance, a formula $A\*A$ has two subformulas $A$, one on the left and one on the right.
-The \defn{subformulas} $\subs A$ of a formula are defined as follows; we write $B\sub A$ if $B$ is a subformula of $A$, i.e.\ if $B\in\subs A$.
-\[
-	\subs A = \{A\} \cup
-	\left\{\begin{array}{ll}
-		\subs B\uplus\subs C	& \text{if $A=B\+C$ or $A=B\*C$} \\[5pt]
-		\subs B					& \text{if $A=\exists x.B$ or $A=\forall a.B$}
-	\end{array}\right.
-\]
-
-A \defn{link} $(C,D)$ on a sequent $\seq AB$ is a pair of subformulas $C\leq A$ and $D\leq B$. 
-A \defn{linking} $\lambda$ on the sequent $\seq AB$ is a set of links on it.
-
-\begin{definition}
-A \defn{pre-net} $\net\lambda AB$ is a sequent $\seq AB$ with a linking $\lambda$ on it.
-\end{definition}
-
-% --------------------------------------------------
-
-\subsection{Witness maps}
-
-A \defn{witness map} $\sigma\colon \varE \rightharpoonup \terms$ is a substitution map which assigns terms to existential variables, given as a (finite) partial function.
-The \defn{empty} witness map $\varnothing$ is the everywhere undefined partial function, and the map $\sigma[t/x]$ substitutes $t$ for $x$ and is as $\sigma$ everywhere else.
-We express by $\sigma(x)=\bot$ that $\sigma$ is undefined for $x$.
-The map $\sigma\minus x$ is undefined on $x$ and otherwise as $\sigma$.
-
-We will write $A\sigma$ for the application of the witness map $\sigma\colon\varE\rightharpoonup\terms$ to the formula $A$ as a substitution map.
-It is applied to a sequent proof, $\pi\sigma$, by applying it to each formula in the proof $\pi$.
-The \defn{composition} of two maps is written $\sigma\tau$, where $A(\sigma\tau)=(A\sigma)\tau$.
-We define the following further operations on witness maps.
-
-\[
-\begin{tabular}{@{}lp{.75\textwidth}@{}}
-	$\sigma\gen\tau$
-&
-	A witness map is \defn{more general} than another, 
-	$\sigma\gen\tau$, if there is a map $\rho$ such that 
-	$\sigma\rho=\tau$.
-\\[5pt]	
-	$\sigma\coh\tau$
-&
-	Two witness maps are \defn{coherent}, $\sigma\coh\tau$,
-	if there is a map $\rho$ such that $\sigma\rho=\tau\rho$.
-\\[5pt]
-	$\sigma\join\tau$
-&
-	The \defn{join} of two witness maps $\sigma\join\tau$ is defined
-	if they are coherent, and is the least map $\rho$ such that
-	$\sigma\gen\rho$ and $\tau\gen\rho$.
-\end{tabular}%
-\]
-
-A \defn{witness linking} $\lambda_\Sigma$ is a linking $\lambda$ with a \defn{witness labelling}  $\Sigma\colon\lambda\to \varE\rightharpoonup\terms$ that assigns each link $(C,D)$ a witness map. 
-We may use and define $\lambda_\Sigma$ as a set of \defn{witness links} $\link CD$, which indicates the link $(C,D)$ in $\lambda$ where $\Sigma(C,D)=\sigma$.
-
-\begin{definition}
-A \defn{witness pre-net} $\net{\lambda_\Sigma}AB$ is a pre-net with a witness linking $\lambda_\Sigma$.
-\end{definition}
-
-We assume the existential variables occurring in the range of $\Sigma$ to be fresh, i.e.\ distinct from any existentially quantified variable in $\seq AB$.
-We abbreviate by $a\in \sigma$ the statement that a (universal) variable $a$ occurs free in the range of $\sigma$, i.e.\ that $a\in\fv(\sigma(x))$ for some $x$.
+%We assume the existential variables occurring in the range of $\Sigma$ to be fresh, i.e.\ distinct from any existentially quantified variable in $\seq AB$.  
+We abbreviate by $a\in \sigma$ the statement that a variable $a$ occurs free in the range of $\sigma$, i.e.\ that $a\in\fv(\sigma(x))$ for some $x$.
 
@@
 
-A witness link $\link PQ$ or link $(P,Q)$ on two atomic formulas $P$ and $Q$ is an \defn{axiom} link if $P\sigma=\dual Q\sigma$, or respectively, if some $\sigma$ exists such that $P\sigma=\dual Q\sigma$.
-An \defn{axiom} (witness) linking is one consisting only of axiom links.
-Observe that in the de-sequentialization $[\pi]$ the witness linking $\deseq[\varnothing]\pi AB$ is an axiom linking.
-
-To an axiom link $(P,Q)$ we assign an \defn{initial witness map} $\sigma=\init PQ$ as the least witness map in $(\gen)$ such that $P\sigma=\dual Q\sigma$ --- in other words, $\init PQ$ is the most general unifier ($\textsc{mgu}$) of $P$ and $\dual Q$.
-An axiom linking $\lambda$ with the initial witness map assigned to each link will be written $\lambda_\star$:
-\[
-	\lambda_\star = \{~\link PQ~\mid~(P,Q)\in\lambda~,~\sigma=\init PQ~\}~.
-\]
-
-For two witness labellings $\Sigma$ and $\Xi$ on the same linking $\lambda$, one is \defn{more general} than the other, $\Sigma\gen\Xi$, if $\Sigma(C,D)\gen\Xi(C,D)$ for every link $(C,D)\in\lambda$.
-$\lambda_\Sigma\gen\lambda_\Xi$,
-
-Observe that for an axiom linking $\lambda$, the initial linking $\lambda_\star$ is the most general among the witness linkings $\lambda_\Sigma$ for any $\Sigma$.
+A witness link $\link PQ$ on two atomic formulas $P$ and $Q$ is an \defn{axiom} link if $P\sigma=\dual Q\sigma$; a witness \defn{axiom} linking is one where every link is an axiom link.
+Observe that the de-sequentialization $[\pi]$ is a witness pre-net with axiom linking $\deseq[\varnothing]\pi AB$.
 
@@
 
-We will define two coalescence relations, one \defn{strict} $(\scoal)$ and one \defn{unifying} $(\ucoal)$.
+We will define two coalescence relations, one \defn{strict} $(\scoal)$, for witness nets, and one \defn{unifying} $(\ucoal)$, for unification nets, in a later section.
 In the former, to join two slices the witness assignment must be the same; in the latter, witness assignments must be compatible, so that a common, more general witness map exists.
@@
 An axiom link will carry an axiom, and each coalescence step introduces one proof rule.
-A \defn{proof linking} $\lambda_\Sigma^\Pi$ is a witness linking $\lambda_\Sigma$ with a \defn{proof labelling} $\Pi\colon \lambda\to\proofs$ assigning each link a sequent proof.
-We will use and define $\lambda_\Sigma^\Pi$ as a set of \defn{proof links} $\link CD^\pi$, where we assume that $\prf\pi{C\sigma}{D\sigma}$.
-
-Let a \defn{labelled link} $\link AB^\pi$ be a link carrying a sequent proof $\prf\pi{A\sigma}{B\sigma}$, and a \defn{labelled linking} or \defn{labelled pre-net} one where every link is labelled.
-The \defn{initial labelling} $\lambda_\Sigma^\star$ of an axiom linking $\lambda_\Sigma$ is:
+Formalizing this, a \defn{proof linking} $\lambda_\Sigma^\Pi$ is a witness linking $\lambda_\Sigma$ with a \defn{proof labelling} $\Pi\colon \lambda\to\proofs$ assigning each link a sequent proof.
+We will use and define $\lambda_\Sigma^\Pi$ as a set of \defn{proof links} $\link CD^\pi$, where we require that $\prf\pi{C\sigma}{D\sigma}$, i.e.\ that $\pi$ proves the conclusion $\seq{C\sigma}{D\sigma}$.
+A \defn{labelled pre-net} $\net{\lambda_\Sigma^\Pi}AB$ is a witness pre-net $\net{\lambda_\Sigma}AB$ with a proof labelling $\Pi$ on $\lambda_\Sigma$.
+The \defn{initial proof labelling} $\lambda_\Sigma^\star$ of an axiom linking $\lambda_\Sigma$ is:
 \[
@@
 \]
-For correctness we may coalesce a pre-net without constructing a proof. 
-%
+For correctness we may coalesce a pre-net directly, without constructing a proof.
+
 To recap, we have accumulated the following further notational conventions.
@@
 \begin{definition}
- \defn{Strict sequentialization} ($\scoal$) is the rewrite relation on labelled pre-nets generated by the following rules, which apply symmetrically to the first formula in the sequent.
+ \defn{Strict sequentialization} ($\scoal$) is the rewrite relation on witness pre-nets generated by the following rules, which apply symmetrically to the first formula in the sequent.
 \defn{Strict coalescence} is the same relation ignoring proof labels, on witness pre-nets.
@@
  ~\scoal~ 
-	\net{\{\link[\sigma\!\minus\!x]A{\exists x.B}^\psi\}}A{\exists x.B}
+	\net{\{\link[\sigma\minus x]A{\exists x.B}^\psi\}}A{\exists x.B}
 \tag{$\srr?$}
@@
 \noindent
-A pre-net $\net{\lambda_\Sigma}AB$ \defn{strict-coalesces} if it reduces in $(\scoal)$ to a single link $\net{\{\link[\varnothing]AB\}}AB$.
-\end{definition}
-
-To be explicit, to generate coalescence as a rewrite relation means the following: a pre-net coalesces to another, $\net{\lambda_\Sigma} AB\scoal \net{{\lambda'_{\Sigma'}}}AB$ if and only if % there is a rewrite rule $\net{\kappa_\Xi} CD\scoal\net{\kappa'_{\Xi'}} CD$ such that $C\leq A$, $D\leq B$, ${\kappa_\Xi}\subseteq{\lambda_\Sigma}$, $\kappa'_{\Xi'}\subseteq{\lambda'_{\Sigma'}}$, and ${\lambda_\Sigma}-{\kappa_\Xi}={\lambda'_{\Sigma'}}-\kappa'_{\Xi'}$.
-there is a rewrite rule
+A witness pre-net $\net{\lambda_\Sigma}AB$ \defn{strict-coalesces} if it reduces to a single link $\net{\{\link[\varnothing]AB\}}AB$.\end{definition}
+
+To be explicit, to generate coalescence as a rewrite relation means the following: a pre-net coalesces to another, $\net{\lambda_\Sigma} AB\scoal \net{{\lambda'_{\Sigma'}}}AB$ if and only if there is a rewrite rule
 \[
@@
 \]
+
+\begin{definition}
+An \all1 \defn{witnessing proof net} or \defn{witness net} is a witness pre-net $\net{\lambda_\Sigma}AB$, with $\lambda_\Sigma$ an axiom linking, that strict-coalesces.
+It \defn{sequentializes} to a proof $\pi$ if its initial labelling $\net{\lambda_\Sigma^\star}AB$ reduces in $(\scoal)$ to $\net{\{\link[\varnothing]AB^\pi\}}AB$.
+\end{definition}
+
+Two useful properties of witness nets are preserved over a coalescence sequence, captured in the lemma below.
+The first property is formulated the way it is to account for vacuous quantifiers, for which no actual variable occurs in $C$ or $D$, as well as formulas such as $\exists x.C\+C'$ where $x$ occurs in $C'$ but not $C$, where we still would like an explicit witness for $x$ on a link $\link CD$.
+
+\begin{lemma}
+Every pre-net on a coalescence path $\net{\lambda_\Sigma}AB \scoal^* \net{\{\link[\varnothing]AB^\pi\}}AB$ from a witness net satisfies the \defn{exact coverage} property: for any link $\link CD$, the domain of $\sigma$ is exactly the variables existentially quantified in $\seq AB$ thad bind in $C$ and $D$,
+\[
+	\dom\sigma = \{\,x \mid C < \exists x.X \leq A\,\}
+			\cup \{\,y \mid D < \exists y.Y \leq B\,\}~.
+\]
+\end{lemma}
+
+%
+%\begin{lemma}
+%Every pre-net on a coalescence path $\net{\lambda_\Sigma}AB \scoal^* \net{\{\link[\varnothing]AB^\pi\}}AB$ from a witness net satisfies the following properties. 
+%\begin{description}
+%	\item[Eigenvariables not free]
+%For any link $\link CD$, a universal variable $a\in\varA$ quantified in $C$ or $D$ does not occur free in the range of $\sigma$, $a\notin\sigma$.
+%
+%	\item[Exact coverage]
+%For any link $\link CD$, the domain of $\sigma$ is exactly the variables existentially quantified in $\seq AB$ that will be bound in $C$ and $D$, if they occur:
+%\[
+%	\dom\sigma = \{\,x \mid C < \exists x.X \leq A\,\}
+%			\cup \{\,y \mid D < \exists y.Y \leq B\,\}~.
+%\]
+%\end{description}
+%\end{lemma}
+
+\begin{proof}
+By induction on the coalescence path, going forward from $\net{\lambda_\Sigma}AB$ for the first property, and working backward from $\net{\{\link[\varnothing]AB^\pi\}}AB$ for the second.
+\end{proof}
+
+\begin{theorem}
+For any \all1 proof $\pi$, the de-sequentialization $[\pi]$ is a witness net that sequentializes to $\pi$. 
+\end{theorem}
+
+\begin{proof}
+It follows by induction on $\prf\pi AB$ that if $\lambda_\Sigma=[\pi]_{A',B'}^\sigma$ where $A'\sigma=A$ and $B'\sigma=B$, then $\net{\lambda^\star_\Sigma}AB$ reduces in $(\scoal)$ to $\net{\{\link{A'}{B'}^\pi\}}AB$.
+The statement is the specific case $\sigma=\varnothing$.
+\end{proof}
+
+% --------------------------------------------------
+
+\subsection{Geometric correctness}
+
+%A formula $\exists x.A$ has two natural immediate descendants: one \emph{syntactic}, its subformula $A$, and one \emph{semantic}, the premise $A[t/x]$ for its introduction rule, for any given $t$.
+We will define the latter as a tree-order generated from a formula $A$: the \defn{positions} of $A$ are its subformulas under substitution,
+%\[
+%	\poss A~=~\{~B'\sigma~\mid~A=A'\sigma~,~B'\sub A'~,~\sigma\in\varE\rightharpoonup\terms~\}
+%\]
+
+A \defn{slice} is the fraction of a proof that depends on a given choice of one branch (or projection) on each product formula $A\*B$.
+Important to additive proof theory is that many operations can be performed on a per-slice basis, such as normalization, or proof net correctness.
+We will here use slices for the latter purpose.
+
+As in the propositional case, we define a slice of a sequent $\seq AB$ as a set of potential links, of which exactly one must be realized in a proof net $\net{\lambda_\Sigma}AB$.
+
+%In the propositional case, slices are readily defined as sets of subformulas. Here, in the first-order case, we will need to
+
+%The immediate problem is that the number of positions immediately below $\exists x.B$ is infinite, as there is one immediate descendant $B[t/x]$ for every term $t$.
+We reduce it to finite width by restricting a slice to just the terms assigned to $x$ by the witness labelling $\Sigma$ in a pre-net $\net{\lambda_\Sigma}AB$.
+
+For a witness linking $\lambda_\Sigma$ and an existential variable $x$, write $\Sigma(x)\subseteq\terms$ for the \defn{witness set} of $x$, which collects the terms assigned to $x$ by the witness maps in $\Sigma$ for every link in $\lambda$:
+\[
+	\Sigma(x) = \{~\sigma(x)~\mid~\link CD\in\lambda_\Sigma~\}~.
+\]
+%
+Given a witness linking $\lambda_\Sigma$, a \defn{slice} $S$ of a formula $A$ and a witness map $\sigma$ is a set of pairs $(A',\sigma)$ where $A'$ is a subformula of $A$, given by: $S=\{(A,\sigma)\}\cup S'$ where $S'$ is as follows.
+%
+\begin{itemize}
+	\item
+\makebox[70pt][l]{If $A = P$}			then $S'=\varnothing$.
+	\item
+\makebox[70pt][l]{If $A = B\+C$} 		then $S'=S_B\uplus S_C$ where $S_B$ is a slice of $B$ and $\sigma$, and $S_C$ a slice of $C$ and $\sigma$.
+	\item
+\makebox[70pt][l]{If $A = B\*C$}		then $S'$ is a slice of $B$ and $\sigma$ or a slice of $C$ and $\sigma$.
+	\item
+\makebox[70pt][l]{If $A = \exists x.B$}	then $S'=\uplus_{t\,\in\,\Sigma(x)}S_t$ where each $S_t$ is a slice of $B$ and $\sigma[t/x]$.
+	\item
+\makebox[70pt][l]{If $A = \forall a.B$}	then $S'$ is a slice of $B$ and $\sigma$.
+\end{itemize}
+%
+\noindent
+A \defn{slice} of a sequent $\seq AB$ is a set of links
+\[
+	\{~\link[\sigma\cup\tau]CD~\mid~(C,\sigma)\in S_A~,~(D,\tau)\in S_B~\}
+\]
+where $S_A$ is a slice of $A$ and $\varnothing$, and $S_B$ a slice of $B$ and $\varnothing$.
+A \defn{slice} of a witness pre-net $\net{\lambda_\Sigma} AB$ is the intersection $\lambda_\Sigma\cap S$ of $\lambda_\Sigma$ with a slice $S$ of $\seq AB$.
+
+Within a slice, we need to ensure that the order in which quantifiers are instantiated is sound.
+That is, we need to have an analogue of the \emph{eigenvariable condition} on the $\qrr!$-rule of sequent calculus, that the quantified variable $a$ of the primary formula $\forall a.A$ does not occur free in the context.
+We will define a \defn{dependency} condition to this effect.
+
+Since we will require that each slice contains a single link, for simplicity we will define the dependency condition on individual links rather than on slices.
+It is expected that for a more involved logic that includes multiplicative connectives, a dependency condition such as the below one needs to be applied to a slice instead.
+
+For a subformula $C$ of a formula $A$, let the \defn{existential covering} $\ex AC$ of $C$ be the set of variables that are existentially quantified in $A$ dominating $C$:
+\[
+	\ex AC = \{\,x \mid C < \exists x.X \sub A\,\}
+\]
+In a pre-net $\net{\lambda_\Sigma}AB$, let the \defn{column} of a link $\link CD$ be the set of pairs 
+\[
+	\{~(X,\sigma|\ex AX)~\mid~C\sub X\sub A~\}\cup\{~(Y,\sigma|\ex BY)~\mid~D\sub Y\sub B~\}~,
+\]
+with an order $(\dep)$ given by: $(X,\rho)\dep(Y,\tau)$ if $X\leq Y$, or $Y$ occurs as $\forall a.Y$ and $a\in\rho$.
+
+\begin{definition}
+A witness pre-net is \defn{correct} if it is
+\begin{enumerate}
+\item \defn{slice-correct}: every slice is a singleton, and
+\item \defn{dependency-correct}: every column is a partial order (i.e.\ is acyclic/antisymmetric).
+\end{enumerate}
+\end{definition}
+
+\begin{lemma}
+\label{lem:preservation}
+Strict coalescence preserves and reflects correctness: for a strict coalescence step $L\scoal R$, the witness pre-net $L$ is correct if and only if $R$ is.
+\end{lemma}
+
+\begin{proof}
+Let $L=\net{\lambda_\Sigma}AB$ and $R=\net{\kappa_\Xi}AB$.
+We will consider the four coalescence steps as shown below.
+For slice-correctness, we will demonstrate that the left-hand side and right-hand side of each rule belong to the same slice of $\seq AB$, or in the case of $\srr?$, naturally corresponding slices.
+%
+\begin{align}
+  	\net{\{\link C{D_i}\}}C{D_0{\+}D_1} 
+ &~\scoal~
+	\net{\{\link C{D_0{\+}D_1} \}}C{D_0{\+}D_1}
+\tag{$\srr+i$}
+\\	\net{\{\link C{D_0},\link C{D_1}\}}C{D_0{\*}D_1}
+ &~\scoal~ 
+	\net{\{\link C{D_0{\*}D_1}\}}C{D_0{\*}D_1}
+\tag{$\srr*$}
+\\	\net{\{\link CD\}}C{\exists x.D}
+ &~\scoal~ 
+	\net{\{\link[\sigma\minus x]C{\exists x.D}\}}C{\exists x.D}
+\tag{$\srr?$}
+\\	\net{\{\link CD\}}C{\forall a.D}
+ &~\scoal~
+	\net{\{\link C{\forall a.D}\}}C{\forall a.D}
+\tag{$\srr!$}
+\end{align}
+%
+\begin{description}
+	\item[$(\srr+i)$]
+A slice $S_B$ of $B$ and $\varnothing$ containing either of $(D_0,\tau)$, $(D_1,\tau)$, and $(D_0\+D_1,\tau)$ must also contain the other two.
+A slice $S$ of $\seq AB$ then contains all three of $\link C{D_0}$, $\link C{D_1}$, and  $\link C{D_0{\+}D_1}$, or none.
+It follows that $S\cap \lambda_\Sigma$ is a singleton if and only if $S\cap\kappa_\Xi$ is.
+Since other slices are unaffected, $L$ is slice-correct if and only if $R$ is.
+For dependency-correctness, the column of $\link C{D_i}$ is that of $\link C{D_0{\+}D_1}$ plus $(D_i,\sigma|\ex B{D_i})$ itself, which is minimal in the order $\dep$.
+
+	\item[$(\srr*)$]
+A slice $S$ of $\seq AB$ contains $\link C{D_0\+D_1}$ if and only if it contains either of $\link C{D_0}$ or $\link C{D_1}$, and may not contain both.
+Then $S\cap \lambda_\Sigma$ is a singleton if and only if $S\cap\kappa_\Xi$ is.
+Dependency-correctness is immediate, as above.
+
+	\item[$(\srr?)$]
+The witness sets $\Sigma(x)$ and $\Xi(x)$ for $L$ and $R$ need not be the same, since $L$ has $\sigma$ where $R$ has $\sigma\minus x$.
+Let $\Sigma(x)=\{t,t_1,\dots,t_n\}$ and $\Xi(x)=\{t_1,\dots,t_n\}$, where $\sigma(x)=t$.
+For every slice $S_B$ of $B$ over $\Sigma$ there is a corresponding slice $S'_B$ over $\Xi$, both (or neither) containing $(\exists x.D,\tau)$ and $(D,\tau[t_i/x])$ for $i\leq n$, but the former in addition having $(D,\tau[t/x])$.
+Then $S\cap \lambda_\Sigma$ is the singleton $\{\link CD\}$ if and only if $S\cap\kappa_\Xi$ is $\{\link[\sigma\minus x]C{\exists x.D}\}$, where it should be observed that if $t$ is also a witness to $x$ in some other slice of $R$, then $t\in\Xi(x)$ and in fact $S=S'$.
+
+For dependency-correctness, the column of $\link CD$ is that of $\link[\sigma\minus x]C{\exists x.D}$ plus a pair $(D,\tau)$, which is minimal in $(\dep)$.
+
+	\item[$(\srr!)$]
+A slice $S$ of $\seq AB$ contains $\link CD$ if and only if it contains also $\link C{\forall a.D}$, and hence $S\cap\lambda_\Sigma$ is a singleton if and only if $S\cap\kappa_\Xi$ is.
+
+For dependency-correctness, the column of $\link CD$ is that of $\link C{\forall a.D}$ plus a pair $(D,\tau)$.
+The side-condition of the coalescence step is that $a\notin\sigma$; then $a$ does not occur free in any $(X,\rho)$, and $(D,\tau)$ is minimal in $(\dep)$.
+\qedhere
+\end{description}
+\end{proof}
+
+\begin{lemma}
+A witness pre-net is correct if and only if it strict-coalesces. 
+\end{lemma}
+
+\begin{proof}
+From right to left, we proceed by induction on the coalescence path from $\net{\lambda_\Sigma}AB$ to $\net{\{\link[\varnothing]AB\}}AB$, with the end result as the base case.
+It is slice-correct: every slice of $\seq AB$ contains $\link[\varnothing]AB$, so every slice of $\net{\{\link[\varnothing]AB\}}AB$ is the singleton $\{\link[\varnothing]AB\}$.
+It is also dependency-correct: the column of $\link[\varnothing]AB$ is the set $\{(A,\varnothing),(B,\varnothing)\}$, where $A$ and $B$ are unrelated in $(\dep)$.
+For the inductive step, by Lemma~\ref{lem:preservation} coalescence reflects correctness, so that any pre-net along the coalescence path is correct, in particular $\net{\lambda_\Sigma}AB$.
+
+From left to right, let $\net{\lambda_\Sigma}AB$ be correct.
+Let the \defn{depth} of a link $\link CD$ be a pair of integers $(n,m)$, where $n$ is the distance from $C$ to the root of $A$, and $m$ that from $D$ to $B$.
+We order link depth in the product order, $(i,j)\leq(n,m)$ if and only if $i\leq n$ and $j\leq m$.
+We will demonstrate that a link at maximal depth may always be coalesced, unless it is the unique link $\link[\varnothing]AB$ at $(0,0)$.
+By Lemma~\ref{lem:preservation} the result of this coalescence step is again correct, and it follows by induction on the decreasing depth of links that the pre-net $\net{\lambda_\Sigma}AB$ strict-coalesces.
+
+To see that a maximally deep link coalesces, first note that a link $\link C{D_i}$ where $D_i$ occurs in $D_0{\+}D_1$ may always contract, as may a link $\link CD$ where $D$ occurs in $\exists x.D$.
+This leaves the following cases:
+\begin{itemize}
+	\item $\link A{D_i}$ with $D_i$ occurring in $D=D_0\*D_1$; without loss of generality, let $i=0$.
+A slice $S_i$ of $\seq AB$ containing $\link A{D_i}$ has a counterpart $S_j$ containing $\link A{D_j}$ with $j=1-i$.
+The depth of $\link A{D_i}$ is the same as that of $\link A{D_j}$.
+By correctness $S_j\cap \lambda_\Sigma$ is a singleton; by the assumption of maximality it may not contain a deeper link than $\link A{D_j}$; and it may not contain a shallower one since that would be shared with $S_i\cap\lambda_\Sigma$.
+Since $\net{\lambda_\Sigma}AB$ contains both $\link A{D_0}$ and $\link A{D_1}$, these contract by $\srr*$ to $\link AD$.
+
+	\item $\link AD$ with $D$ in $\forall a.D$.
+
+	\item $\link{C_i}{D_j}$ in $C_0\*C_1$ and $D_0\*D_1$.
+
+	\item $\link{C_i}D$ in $C_0\*C_1$ and $\forall a.D$.
+
+	\item $\link CD$ in $\forall a.C$ and $\forall b.D$.
+
+\end{itemize}
+
+\end{proof}
+
+\subsection{Normalization}
+
+\includegraphics[scale=0.4]{normalization.jpg}
+
+\section{Unification nets}
+
+We define the following further operations on witness maps.
+\[
+\begin{tabular}{@{}lp{.75\textwidth}@{}}
+	$\sigma\gen\tau$
+&
+	A witness map is \defn{more general} than another, 
+	$\sigma\gen\tau$, if there is a map $\rho$ such that 
+	$\sigma\rho=\tau$.
+\\[5pt]	
+	$\sigma\coh\tau$
+&
+	Two witness maps are \defn{coherent}, $\sigma\coh\tau$,
+	if there is a map $\rho$ such that $\sigma\rho=\tau\rho$.
+\\[5pt]
+	$\sigma\join\tau$
+&
+	The \defn{join} of two witness maps $\sigma\join\tau$ is defined
+	if they are coherent, and is the least map $\rho$ such that
+	$\sigma\gen\rho$ and $\tau\gen\rho$.
+\end{tabular}%
+\]
+
+A clean link $(P,Q)$ on two atomic formulas $P$ and $Q$ is an \defn{axiom} link if there exists a witness map $\sigma$ such that $P\sigma=\dual Q\sigma$.
+A clean \defn{axiom} linking is one consisting only of axiom links.
+
+The \defn{clean} de-sequentialization $\floor\pi$ of a proof $\pi$ is the pre-net $\net\lambda AB$ where the de-sequentialization $[\pi]=\net{\lambda_\Sigma}AB$.
+Observe that $\lambda$ is then an axiom linking.
+
+To an axiom link $(P,Q)$ we assign an \defn{initial witness map} $\sigma=\init PQ$ as the least witness map in $(\gen)$ such that $P\sigma=\dual Q\sigma$.
+In other words, $\init PQ$ is the most general unifier ($\textsc{mgu}$) of $P$ and $\dual Q$.
+An axiom linking $\lambda$ with the initial witness map assigned to each link will be written $\lambda_\star$:
+\[
+	\lambda_\star = \{~\link PQ~\mid~(P,Q)\in\lambda~,~\sigma=\init PQ~\}~.
+\]
+For a pre-net $\net{\lambda_\star}AB$ we assume the \defn{exact coverage} convention, that the domain of each $\sigma(P,Q)$ is $\ex AP\cup\ex BQ$.
+This means a variable $x\in\varE$ in $P$ or $Q$ will be assigned at least a fresh variable name $y$.
+
+%Together with the convention that existential variables in the range of $\sigma(P,Q)$ are fresh,
+
+For two witness labellings $\Sigma$ and $\Xi$ on the same linking $\lambda$, one is \defn{more general} than the other, $\Sigma\gen\Xi$, if $\Sigma(C,D)\gen\Xi(C,D)$ for every link $(C,D)\in\lambda$.
+We extend this to the linkings themselves: $\lambda_\Sigma\gen\lambda_\Xi$.
+Observe that for an axiom linking $\lambda$, the initial linking $\lambda_\star$ is the most general among the witness linkings $\lambda_\Sigma$ for any $\Sigma$.
+
+We write $\Sigma\tau$ for the composition of every map in $\Sigma$ with $\tau$:	$\Sigma\tau(C,D) = \Sigma(C,D)\tau$.
+Because of the exact coverage convention, we have that, if $\lambda_\star=\lambda_\Sigma\gen\lambda_\Xi$, then $\Xi=\Sigma\tau$ for some $\tau$.
 
@@
 \begin{definition}
-An \all1 \defn{witnessing proof net} or \defn{witness net} is a witness pre-net $\net{\lambda_\Sigma}AB$, with $\lambda_\Sigma$ an axiom linking, that strict-coalesces.
-It \defn{sequentializes} to a proof $\pi$ if its initial labelling $\net{\lambda_\Sigma^\star}AB$ reduces in $(\scoal)$ to $\net{\{\link[\varnothing]AB^\pi\}}AB$.
-\end{definition}
-
-\begin{definition}
 An \all1 \defn{unification proof net} or \defn{unification net} is a pre-net $\net\lambda AB$ with clean axiom linking $\lambda$ such that its initial witness assignment $\net{\lambda_\star}AB$ unifying-coalesces.
@@
 
-\begin{theorem}
-For any \all1 proof $\pi$:
-\begin{enumerate}
-\item the de-sequentialization $[\pi]$ is a witness net that sequentializes to $\pi$. 
-\item the clean de-sequentialization $\floor\pi$ is a unification net that sequentializes to a proof $\phi$ such that $\pi=\phi\rho$ for some witness map $\rho$ (where universal variables may be captured).
-\end{enumerate}
-\end{theorem}
-
-\begin{proof}
-By induction on $\prf\pi AB$, if $\lambda=[\pi]_{A',B'}^\sigma$ where $A'\sigma=A$ and $B'\sigma=B$, then $\net{\lambda^\star}AB$ reduces in $(\scoal)$ to $\net{\{\link{A'}{B'}^\pi\}}AB$.
-Statement 1.\ is the specific case $\sigma=\varnothing$.
-%
-% Technical note: need to assume $\sigma$ contains no universally quantified variables in $A$ or $B$. 
-%
-For the second statement, by induction
-
- on $\prf\pi AB$, if $\lambda=\floor{\deseq\pi{A'}{B'}}$ where $A'\sigma=A$ and $B'\sigma=B$, then $\net{\lambda^\star_\star}AB$ reduces in $(\ucoal)$ to $\net{\{\link{A'}{B'}\}}{}{}$
-\end{proof}
-
-For two axiom linkings $\lambda$ and $\kappa$,
-
-\begin{lemma}
-If $\net\lambda AB$ with axiom linking $\lambda$ unifying-coalesces to $\net{\{\link{A'}{B'}\}}AB$ then $\net{\floor\lambda_\star}AB$ unifying-coalesces to $\net{\{\link[\rho]{A'}{B'}\}}AB$ with $\rho\gen\sigma$.
-\end{lemma}
-
-% --------------------------------------------------
-
-\subsection{Geometric correctness}
-
-%\end{document}
-
-A link is \defn{strict} if its domain consists of exactly the existentially quantified variables that its formulas are in scope of.
-That is, a link $\link CD$ in a pre-net $\net\lambda AB$ is strict if
-\[
-	\dom\sigma = \{\,x \mid C < \exists x.X \leq A\,\}
-			\cup \{\,y \mid D < \exists y.Y \leq B\,\}~.
-\]
-A linking or pre-net is \defn{strict} if all its links are.
-
-For a labelled linking $\lambda$ and an existential variable $x$, write $\lambda(x)\subseteq\terms$ for the \defn{witness set} of $x$, which collects the terms assigned to $x$ by the links in $\lambda$:
-\[
-	\lambda(x) = \{~t~\mid~\sigma(x) = t~,~\link AB\in\lambda~\}~.
-\]
-%
-Given a labelled linking $\lambda$, a \defn{slice} $S$ of a formula $A$ is a set of formulas given by: $S=\{A\}\cup S'$ where $S'$ is as follows; if $A$ is of the form
-%
-\begin{itemize}
-	\item
-\makebox[40pt][l]{$P$:}				$S'=\varnothing$.
-	\item
-\makebox[40pt][l]{$B\+C$:} 			$S'=S_B\cup S_C$ where $S_B$ is a slice of $B$ and $S_C$ a slice of $C$.
-	\item
-\makebox[40pt][l]{$B\*C$:}			$S'$ is a slice of $B$ or a slice of $C$.
-	\item
-\makebox[40pt][l]{$\exists x.B$:}	$S'$ is a slice of $B$ if the quantifier is vacuous, $x\notin\fv(B)$, and
-	\\[\itemsep]
-	\hspace*{40pt}					$S'=\uplus_{t\,\in\,\lambda(x)}S_t$ where each $S_t$ is a slice of $B[t/x]$ otherwise.
-	\item
-\makebox[40pt][l]{$\forall a.B$:}	$S'$ is a slice of $B$.
-\end{itemize}
-%
-A \defn{slice} of a labelled pre-net $\net\lambda AB$ is a set of links
-\[
-	\{~\link CD\in \lambda~\mid~(C\sigma,D\sigma)\in S_A\times S_B~\}
-\]
-where $S_A$ is a slice of $A$ and $S_B$ a slice of $B$.
-A labelled pre-net is \defn{correct} if every slice is a singleton.
-A coherent pre-net $\net\lambda AB$ is \defn{correct} if its initial labelling $\net{\lambda_\star}AB$ is.
-Observe that for a \emph{labelled} pre-net correctness and compatibility are independent, while a non-labelled pre-net must be coherent to be correct, since $\lambda_\star$ is otherwise not defined.
-
-\begin{definition}
-An \all1 \defn{proof net} is a correct pre-net. An \all1 \defn{labelled proof net} is a correct and coherent labelled pre-net.
-\end{definition}
-
-\begin{lemma}
-If a labelled pre-net coalesces, it is correct. 
-\end{lemma}
-
-\begin{proof}
-By induction on the coalescence path we will show that if $\net\lambda AB$ coalesces to $\net{\{\link AB\}}AB$ then $\net{\{\link[\varnothing]{A\sigma}{B\sigma}\}}{A\sigma}{B\sigma}$ is correct.
-The statement is then the special case $\sigma=\varnothing$.
-
-The result $\net{\{\link[\varnothing]{A\sigma}{B\sigma}\}}{A\sigma}{B\sigma}$ is correct: its only slice is $\{\link[\varnothing]{A\sigma}{B\sigma}\}$, since $A\sigma$ is in any slice $S_{A\sigma}$ of $A\sigma$, and $B\sigma$ is in any slice $S_{B\sigma}$ of $B\sigma$.
-
-\renewcommand{\+}{{+}}
-\renewcommand{\*}{{\times}}
-\begin{align}
-	\net{\{\link AB,\link[\tau]AC\}}A{B\*C}
-& ~\scoal~ 
-	\net{\{\link[\sigma\join\tau]A{B\*C}\}}A{B\*C}\quad\text{if }\sigma\coh\tau
-\tag{$\*$}
-\end{align}
-
-Let $\rho=\sigma\join\tau$, and assume that $\net{\{\link[\varnothing]{A\rho}{B\rho\*C\rho}\}}{A\rho}{B\rho\*C\rho}$ is correct.
-
-\end{proof}
-
-\end{document}
-
-Coalescence is effectively sequentialization. We will make this explicit by organising the rewrite rules as inference rules.
-
-%
-%As an intermediary between the sequent calculus and labelled proof nets, we will introduce a \defn{labelled sequent calculus}. A \defn{labelled sequent}
-%\[
-%	\xlink AB
-%\]
-%is a sequent that carries a linking $\lambda$ and a witness map $\sigma$. 
-%
-%
-%for the statement that $\lambda\seq{A\sigma}{B\sigma}$ coalesces to a single labelled 
-%
-
 \begin{figure}
@@
 \[
-\begin{array}{c@{\hspace{40pt}}ccc}
-	\vc{\infer{\crule [\sigma(P,\dual Q)] [\{(P,Q)\}] P Q}{}}
-&    
+\begin{array}{ccc}
     \vc{\begin{tikzpicture}[net]
@@
 \\ \\
-	\vc{\infer{\crule A {B\+C}} {\crule AB}}
-&   
     \vc{\begin{tikzpicture}[net]
@@
 \\ \\   
-    \vc{\infer[\!\!\scriptstyle{\sigma\comp\tau}]
-    		{\crule [\sigma\cup\tau] [\lambda\cup\kappa] A {B\*C}}
-    		{\crule AB && \crule[\tau][\kappa]AC}}
-&     
     \vc{\begin{tikzpicture}[net]
@@
     \end{tikzpicture}}
-&\stackrel{\sigma\comp\tau}\rightsquigarrow&   
+&\stackrel{\sigma\coh\tau}\rightsquigarrow&   
 	\vc{\begin{tikzpicture}[net]
@@
 \\ \\
-    \vc{\infer{\crule[\sigma\minus x]A{\exists x.B}}{\crule AB}}
-&
     \vc{\begin{tikzpicture}[net]
@@
     	\formula[y=1]{\exists x.B}
-    	\Vlink[red,label={~$\scriptstyle{\sigma\!\minus\!x}$}]{1,1}
+    	\Vlink[red,label={~$\scriptstyle{\sigma\minus x}$}]{1,1}
     \end{tikzpicture}}
 \\ \\
-    \vc{\infer[\!\!\scriptstyle{a\,\notin\,\fv(A\sigma)}]{\crule A{\forall a.B}}{\crule AB}}
-&    
     \vc{\begin{tikzpicture}[net]
@@
 \]
-\par\bigskip\hrule
-\caption{Coalescence derivation rules}
+\caption{Coalescence rules}
 \label{fig:coalescence}
@@
 
-\begin{lemma}
-Given a proof $\prf\pi AB$, formulas $A'$, $B'$, and a witness map $\sigma$ such that $A'\sigma=A$ and $B'\sigma=B$, the de-sequentialization $\net{\deseq\pi{A'}{B'}}AB$ coalesces to $\net{\{\link AB\}}AB$.
-\end{lemma}
-
-\begin{lemma}
-Given a proof $\prf\pi AB$ and formulas $A'$ and $B'$, if a smallest witness map $\tau$ exists such that $A=A'\tau$ and $B=B'\tau$, then $\deseq\pi{A'}{B'}$ coalesces to $\link{A'}{B'}$ with $\sigma\leq\tau$.
-\end{lemma}
-
-\begin{proof}
-By induction on $\pi$.
-
-\newlength\prooftablewidth
-\setlength\prooftablewidth{-80pt}
-\addtolength\prooftablewidth{\textwidth}
-
-\noindent
-\begin{tabular}{@{}p{80pt}@{}p{\prooftablewidth}@{}}
-	\hfill \raisebox{-20pt}{\infer{\seq P{\dual P}}{\vphantom B}} \hfill\hfill
-&
-	Let $A'=Q$ and $B'=R$, and suppose $\tau$ is the smallest witness map such that $Q\tau=P$ and $R\tau=\dual P$.
-The desequentialization $\deseq\pi QR$ is the $\net{\{Q,R\}}QR$, which coalesces to $\link QR$ if $\sigma=\sigma(Q,{\dual R})$ exists.
-Since $\tau$ is a unifier of $Q$ and $\dual R$, $\sigma\leq\tau$.
-\\ \\
-%	$\infer{\seq A{B_0\+B_1}}{\seq A{B_i}}$
-%&
-%\\ \\
-	\hfill \raisebox{-20pt}{\infer{\seq A{B\*C}}{\seq AB && \seq AC}}\hfill\hfill
-&
-	Let $\seq{\prf\pi AB}{A'}{B'}$ coalesce to the two subproofs coalesce to $\link{A'}{B'}$ and $\link[\rho]{A'}{B'}$ 
-%	\infer{\seq A{\exists x.B}}{\seq A{B[t/x]}}
-%	\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]{\seq A{\forall a.B}}{\seq AB}
-\end{tabular}
-
-\end{proof}
-
 \end{document}
-
-%\[
-%	\infer{\xlink [\sigma(P,Q)] [\{(P,Q)\}] P Q}{}
-%\]
-%\par
-%\[
-%	\infer{\xlink A {B_0\+B_1}} {\xlink A {B_i}}
-%\]
-%\par
-%\[
-%	\infer[\!\!\scriptstyle{\sigma\comp\tau}]
-%		{\xlink [\sigma\cup\tau] [\lambda\cup\kappa] A {B\*C}}
-%		{\xlink AB && \xlink[\tau][\kappa]AC}
-%\]
-%\par
-%\[
-%	\infer{\xlink[\sigma\minus x]A{\exists x.B}}{\xlink AB}
-%\]
-%\par
-%\[
-%	\infer[\!\!\scriptstyle{a\,\notin\,\fv(A\sigma)}]{\xlink A{\forall a.B}}{\xlink AB}
-%\]
-
-% --------------------------------------------------
-
-%\subsection{Existential witnesses}
-
-%
-%
-%For two first-order terms $s$ and $t$, and a set of variables $V$, let a $V$-\defn{unifier} be a unifying substitution map
-%\[
-%	\sigma\colon V\rightharpoonup \terms
-%\]
-%(that is, $s\sigma=t\sigma$). A $V$-unifier for atomic propositions $P$ and $Q$ is defined analogously. For example, 
-%
-%
-%The \defn{most general $V$-unifier} $\sigma_V(P,Q)$ of $P$ and $Q$ is the most general unifying
-%
-%let the \defn{initial witness map} $\sigma(P,Q)$ be the most general unifier of $P$ and $Q$, if it exists, where only existential variables can be substituted for, and universal variables are considered constant.
-That is, the only unifier of $p(x,y)$ and $p(a,a)$ is $\{x\mapsto a,y\mapsto a\}$, while $p(x,x)$ and $p(a,b)$ have no unifier.
-%
-%Let $\sigma\join\tau$ denote the combination of two witness maps $\sigma$ and $\tau$ as unifiers, if it exists.
-If it does, we call $\sigma$ and $\tau$ \defn{coherent}, expressed by $\sigma\comp\tau$.
-The initial witness map $\sigma(A,B)$ of two formulae $A$ and $B$, if it exists, is then given by:
-%
-%\begin{align}
-%	\left.\begin{array}{r}
-%		\sigma_V(\,A\+B\,,\,C\+D\,) \\
-%		\sigma_V(\,A\*B\,,\,C\*D\,)
-%	\end{array}\right\}
-%	& = \sigma_V(A,C)\join\sigma_V(B,D)
-%\\	
-%	\sigma_V(\,\forall a.A\,,\,\forall a.B\,)
-%		 \kern12.5pt & = \sigma_V(A,B)
-%\\	\sigma_V(\,\exists x.A\,,\,\exists x.B\,)
-%		 \kern12.5pt & = \sigma_{V-\{x\}}(A,B)
-%\end{align*}
-%
-%
-%Two witness maps $\sigma$ and $\tau$ are \defn{coherent}, written $\sigma\comp\tau$, if they agree wherever they are defined:
-%\[
-%	\sigma\comp\tau \quad\iff\quad \forall x\in\varE.~\big(\sigma(x)\neq\bot~\wedge~\tau(x)\neq\bot\big)~\Rightarrow~\sigma(x)=\tau(x)~.
-%\]
-%Two coherent witness maps can be combined into the map $\sigma\cup\tau$ that sends $x$ to $\sigma(x)$ or $\tau(x)$, whichever is defined, and is undefined when both are.
-To combine witness maps that may not be coherent we will write $\sigma\ubot\tau$, which is $\sigma\cup\tau$ if they are, and undefined ($\bot$) otherwise; if either $\sigma$ or $\tau$ is already undefined, $\sigma\ubot\tau$ also reverts to $\bot$.
-%\[
-%	\sigma\ubot\tau\quad=\quad
-%	\left\{\begin{array}{ll}
-%		\sigma\cup\tau	& \text{if $\sigma\neq\bot$, $\tau\neq\bot$, and $\sigma\comp\tau$} \\
-%		\bot			& \text{otherwise} \\
-%	\end{array}\right.
-%\] 
-%Note that $\bot$ is not a witness map, and different from the empty substitution map, $\sigma(x)=\bot$ for all $x$.
-For two atomic formulas $P,Q$ (or terms $s,t$) the \defn{initial witness map} $\sigma(P,Q)$ is the smallest witness map $\sigma$ such that $P\sigma=\dual Q\sigma$ and $P\sigma$ has no free existential variables.
-If it exists, it is defined inductively as follows (omitting the symmetric case for $\dual p$ and $p$).
-%
-%\begin{align*}
-%	\left.\begin{array}{r}
-%		\sigma(\,x\,,\,t\,) \\
-%	 	\sigma(\,t\,,\,x\,)
-%	\end{array}\right\}
-%	& = \{ x\mapsto t \}\quad \text{if $t\in\termsA$}
-% \\
-%	\left.\begin{array}{r}
-%		\sigma(\,p(s_1,\dots,s_n)\,,\,\dual p(t_1,\dots,t_n)\,) \\
-%		\sigma(\,f(s_1,\dots,s_n)\,,\,f(t_1,\dots,t_n)\,)
-%	\end{array}\right\}
-%	& = \sigma(s_1,t_1)\ubot\dots\ubot\sigma(s_n,t_n)
-%\end{align*}
-%
-%\begin{lemma}
-%\label{lem:minimal witness map}
-%For first-order terms $s$ and $t$ the witness map $\sigma(s,t)$ is the smallest such that $s\sigma=t\sigma$ and $s\sigma$ contains no existential variables.
-%\end{lemma}
-%
-%\begin{proof}
-%By induction on $s$ and $t$. If $s=x$ then $\sigma(x,t)$ exists if and only if $t\in\termsA$, 
-%\end{proof}
-
-%\begin{align*}
-%	\sigma_V(\,a\,,\,a\,) \kern12.5pt & = \varnothing
-%\\	\sigma_V(\,x\,,\,x\,) \kern12.5pt & = \varnothing\quad \text{if $x\in V$}
-%\\
-%	\left.\begin{array}{r}
-%		\sigma_V(\,x\,,\,t\,) \\
-%	 	\sigma_V(\,t\,,\,x\,)
-%	\end{array}\right\}
-%	& = \{ x\mapsto t \}\quad \text{if $x\notin V$ and $t\in\termsA$}
-% \\
-%	\left.\begin{array}{r}
-%		\sigma_V(\,p(s_1,\dots,s_n)\,,\,p(t_1,\dots,t_n)\,) \\
-%		\sigma_V(\,f(s_1,\dots,s_n)\,,\,f(t_1,\dots,t_n)\,)
-%	\end{array}\right\}
-%	& = \sigma_V(s_1,t_1)\ubot\dots\ubot\sigma_V(s_n,t_n)
-%\\	
-%	\left.\begin{array}{r}
-%		\sigma_V(\,A\+B\,,\,C\+D\,) \\
-%		\sigma_V(\,A\*B\,,\,C\*D\,)
-%	\end{array}\right\}
-%	& = \sigma_V(A,C)\ubot\sigma_V(B,D)
-%\\	
-%	\sigma_V(\,\forall a.A\,,\,\forall a.B\,)
-%		 \kern12.5pt & = \sigma_V(A,B)
-%\\	\sigma_V(\,\exists x.A\,,\,\exists x.B\,)
-%		 \kern12.5pt & = \sigma_{V\cup\{x\}}(A,B)
-%\end{align*}
-%
-%Observe that if the witness map $\sigma=\sigma(A,B)$ exists then $A\sigma=B\sigma$.
-
-% --------------------------------------------------
-
-\begin{lemma}
-Given a proof $\prf\pi AB$ and formulas $A'$ and $B'$, if a smallest witness map $\tau$ exists such that $A=A'\tau$ and $B=B'\tau$, then $\deseq\pi{A'}{B'}$ coalesces to $\link{A'}{B'}$ with $\sigma\leq\tau$.
-\end{lemma}
-
-\begin{proof}
-By induction on $\pi$.
-
-\newlength\prooftablewidth
-\setlength\prooftablewidth{-80pt}
-\addtolength\prooftablewidth{\textwidth}
-
-\noindent
-\begin{tabular}{@{}p{80pt}@{}p{\prooftablewidth}@{}}
-	\hfill \raisebox{-20pt}{\infer{\seq P{\dual P}}{\vphantom B}} \hfill\hfill
-&
-	Let $A'=Q$ and $B'=R$, and suppose $\tau$ is the smallest witness map such that $Q\tau=P$ and $R\tau=\dual P$.
-The desequentialization $\deseq\pi QR$ is the $\net{\{Q,R\}}QR$, which coalesces to $\link QR$ if $\sigma=\sigma(Q,{\dual R})$ exists.
-Since $\tau$ is a unifier of $Q$ and $\dual R$, $\sigma\leq\tau$.
-\\ \\
-%	$\infer{\seq A{B_0\+B_1}}{\seq A{B_i}}$
-%&
-%\\ \\
-	\hfill \raisebox{-20pt}{\infer{\seq A{B\*C}}{\seq AB && \seq AC}}\hfill\hfill
-&
-	Let $\seq{\prf\pi AB}{A'}{B'}$ coalesce to the two subproofs coalesce to $\link{A'}{B'}$ and $\link[\rho]{A'}{B'}$ 
-%	\infer{\seq A{\exists x.B}}{\seq A{B[t/x]}}
-%	\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]{\seq A{\forall a.B}}{\seq AB}
-\end{tabular}
-
-\end{proof}
-
-\begin{description}
-	\item[$\sigma\ult\tau$] 
-A witness map is \defn{included} in another, $\sigma\ult\tau$, if for every $x\in\varE$, $\sigma(x)=t$ implies $\tau(x)=t$.
-	\item[$\sigma\uco\tau$]
-Two witness maps are \defn{coherent}, $\sigma\uco\tau$, if for every $x\in\varE$, if $\sigma(x)$ and $\tau(x)$ are both defined then $\sigma(x)=\tau(x)$.
-	\item[$\sigma\ujn\tau$]
-The \defn{union} of two witness maps $\sigma\ujn\tau$ is defined if they are coherent, and is the map taking $x$ to $\sigma(x)$ or $\tau(x)$ if either is defined.
-	\item[$\sigma\gen\tau$]
-A witness map is \defn{more general} than another, $\sigma\gen\tau$, if there is a map $\rho$ such that $\sigma\rho=\tau$.
-	\item[$\sigma\coh\tau$]
-Two witness maps are \defn{coherent}, $\sigma\coh\tau$, if there is a map $\rho$ such that $\sigma\rho=\tau\rho$.
-	\item[$\sigma\join\tau$]
-The \defn{join} of two witness maps $\sigma\join\tau$ is defined if they are coherent, and is the least map $\rho$ such that $\sigma\gen\rho$ and $\tau\gen\rho$.
-\end{description}
-
-The two coalescence relations $(\scoal)$ and $(\ucoal)$ are small-step rewrite relations. We will characterize both as inductive, big-step relations $(\sdown)$ and $(\udown)$. Judgements 
-\[
-	\sdn\lambda AB
-	\qquad\text{and}\qquad
-	\udn\lambda AB
-\]
-will mean that $\net\lambda AB$ strict-coalesces respectively unifying-coalesces to $\net{\link AB}AB$.
-The relations $(\sdown)$ and $(\udown)$ are defined by the derivation rules given in Figure~\ref{fig:derivations}, where we overload the names of the corresponding rules of $(\scoal)$ and $(\sdown)$, and of $(\ucoal)$ and $(\udown)$.
-
-\begin{proposition}
-A pre-net $\net\lambda AB$ is a witness net if and only if $\sdn\lambda[]AB$.
-\end{proposition}
-
-%\begin{proof}[Proof sketch]
-%
-%\end{proof}
-
-\begin{proposition}
-A pre-net $\net\lambda AB$ is a unification net if and only if $\udn\lambda[]AB$.
-\end{proposition}
-
-We will use both derivation systems to mediate the translation from sequent proofs to proof nets (\defn{de-sequentialization}) and from proof nets to proofs (\defn{sequentialization}).
-%Firstly, we formalize the isomorphism between sequent proofs and $(\sdown)$-derivations.
-
-\begin{definition}[Witness net (de-)sequentialization]
-The relation $\pi\QU\Sigma$ between sequent proofs $\pi$ and $(\sdown)$-derivations $\Sigma$ is generated by relating $(\qrr1)$ to $(\srr1)$ and $(\qrr\alpha)$-rules to $(\srr\alpha)$-rules for $\alpha\in\{\,\+_i\,,\,\*\,,\,\exists\,,\,\forall\,\}$.
-If $\pi\QU\Sigma$ and $\Sigma$ derives $\sdn\lambda[]AB$ then $\pi$ \defn{de-sequentializes} to the witness net $\net\lambda AB$ and $\net\lambda AB$ \defn{sequentializes} to $\pi$.
-\end{definition}
-
-\begin{proposition}
-The relation $(\QU)$ is an isomorphism.
-\end{proposition}
-
-\begin{figure}
-\[
-\begin{array}{@{}l@{\qquad}c@{\qquad}c@{\qquad}r@{}}
-& \textbf{Strict} & \textbf{Unifying}
-\\ \\
-	(\srr1)
-&	\vc{\infer[\!\!\scriptstyle{Q\sigma=\dual R\sigma}]{\sdn{\link QR}QR}{}}
-&	\vc{\infer[\!\!\scriptstyle{\sigma\,=\,\sigma(Q,R)}]{\udn{\link[]QR}QR}{}}
-&	(\urr1)
-\\ \\
-	(\srr+i)
-&	\vc{\infer{\sdn\lambda A{B_0\+B_1}}{\sdn\lambda A{B_i}}}
-&	\vc{\infer{\udn\lambda A{B_0\+B_1}}{\udn\lambda A{B_i}}}
-&	(\urr+i)
-\\ \\
-	(\srr*)
-&	\vc{\infer{\sdn{\lambda\cup\kappa}A{B\*C}}{\sdn\lambda AB && \sdn\kappa AC}}
-&	\vc{\infer[\!\!\scriptstyle{\sigma\,\coh\,\tau}\vphantom)]{\udn{\lambda\cup\kappa}[\sigma\join\tau]A{B\*C}}{\udn\lambda[\sigma]AB && \udn\kappa[\tau]AC}}
-&	(\urr*)
-\\ \\
-	(\srr?)
-&	\vc{\infer[\!\!\scriptstyle{\sigma(x)\,\neq\,\bot}]{\sdn\lambda[\sigma\!\minus\!x]A{\exists x.B}}{\sdn\lambda AB}}
-&	\vc{\infer{\udn\lambda[\sigma\!\minus\!x]A{\exists x.B}}{\udn\lambda AB}}
-&	(\urr?)
-\\ \\
-	(\srr!)
-&	\vc{\infer[\!\!\scriptstyle{a\,\notin\,\sigma}]{\sdn\lambda A{\forall a.B}}{\sdn\lambda AB}}
-&	\vc{\infer[\!\!\scriptstyle{a\,\notin\,\sigma}]{\udn\lambda A{\forall a.B}}{\udn\lambda AB}}
-&	(\urr!)
-\end{array}
-\]
-\caption{Derivation rules for (de-)sequentialization}
-\label{fig:derivations}
-\end{figure}

### 2017-12-22 ALL1.tex
lutz' comments

@@
 \bibliographystyle{plainurl}
+
+% ============================== FOR COMMENTS
+
+\newcommand{\lutz}[1]{{\color{blue}     \noindent[\![\![{\bf Lutz: }#1]\!]\!]}}
+\newcommand{\todo}[1]{{\color{red}     \noindent[\![\![{\bf TODO: }#1]\!]\!]}}
 
@@
 A \defn{witness map} $\sigma\colon \varE \rightharpoonup \terms$ is a substitution map which assigns terms to existential variables, given as a (finite) partial function.
-Its \defn{domain} $\dom(\sigma)$ are those variables for which it is defined.
+Its \defn{domain} $\dom\sigma$ are those variables for which it is defined.
 The \defn{empty} witness map $\varnothing$ is the everywhere undefined partial function, and the map $\sigma[t/x]$ substitutes $t$ for $x$ and is as $\sigma$ everywhere else.
@@
 We may use and define $\lambda_\Sigma$ as a set of \defn{witness links} $\link CD$, where $(C,D)$ in $\lambda$ and $\Sigma(C,D)=\sigma$.
-When link is not a witness link may be emphasized by calling it \defn{clean}.
+When a link is not a witness link, this may be emphasized by calling it \defn{clean}.
 
@@
 \end{align*}
+\lutz{why the $\Sigma$ in the third equation?}
+
+\lutz{I don't see where the primes come in, i.e, in no equation there is a relation between $A$ and $A'$, etc.}
 \end{definition}
@@
  ~\scoal~
-	\net{\link A{\forall a.B}}A{\forall a.B}
+	\net{\{\link A{\forall a.B}\}}A{\forall a.B}
 \tag{$\srr!$}
@@
 \]
+\lutz{I think a $\Xi$ in the index is just horrible.}
 
@@
 It \defn{sequentializes} to a proof $\pi$ if its initial labelling $\net{\lambda_\Sigma^\star}AB$ reduces in $(\scoal)$ to $\net{\{\link[\varnothing]AB^\pi\}}AB$.
+\lutz{shouldn't we say somewhere that the initial linking is just on atoms?}
 \end{definition}
@@
 \begin{lemma}
-Every pre-net on a coalescence path $\net{\lambda_\Sigma}AB \scoal^* \net{\{\link[\varnothing]AB^\pi\}}AB$ from a witness net satisfies the \defn{exact coverage} property: for any link $\link CD$, the domain of $\sigma$ is exactly the variables existentially quantified in $\seq AB$ thad bind in $C$ and $D$,
+Every pre-net on a coalescence path $\net{\lambda_\Sigma}AB \scoal^* \net{\{\link[\varnothing]AB^\pi\}}AB$ from a witness net satisfies the \defn{exact coverage} property: for any link $\link CD$, the domain of $\sigma$ is exactly the variables existentially quantified in $\seq AB$ thad bind \lutz{???} in $C$ and $D$,
 \[
@@
 \end{proof}
+\lutz{I am missing something here. In the lemma there is only one statement. So, what is the first, and what the second?}
 
@@
 A slice $S_B$ of $B$ and $\varnothing$ containing either of $(D_0,\tau)$, $(D_1,\tau)$, and $(D_0\+D_1,\tau)$ must also contain the other two.
-A slice $S$ of $\seq AB$ then contains all three of $\link C{D_0}$, $\link C{D_1}$, and  $\link C{D_0{\+}D_1}$, or none.
+\lutz{something is confusing here.
+It seems you are using different notions of slice.
+Above it says that correctness means that slices are singletons, and here you imply that slices contain more than one element.} A slice $S$ of $\seq AB$ then contains all three of $\link C{D_0}$, $\link C{D_1}$, and  $\link C{D_0{\+}D_1}$, or none.
 It follows that $S\cap \lambda_\Sigma$ is a singleton if and only if $S\cap\kappa_\Xi$ is.

### 2017-12-22 ALL1.tex
lutz' comments

@@
 
-For two witness labellings $\Sigma$ and $\Xi$ on the same linking $\lambda$, one is \defn{more general} than the other, $\Sigma\gen\Xi$, if $\Sigma(C,D)\gen\Xi(C,D)$ for every link $(C,D)\in\lambda$.
+For two witness labellings $\Sigma$ and $\Xi$ on the same linking $\lambda$, one is \defn{more general} than the other, $\Sigma\gen\Xi$, \lutz{say which one is more general} if $\Sigma(C,D)\gen\Xi(C,D)$ for every link $(C,D)\in\lambda$.
 We extend this to the linkings themselves: $\lambda_\Sigma\gen\lambda_\Xi$.

### 2018-01-04 ALL1.tex
messing around with composition

--- 2017-12-19 ALL1.tex
@@
 
+\newcommand\comp{\mathbin;}
+
 % ===== Witness maps
@@
 \newcommand\join{\vee}
+
+\newcommand\res[1]{|_{#1}}
+\newcommand\fix[1]{\vec{#1}}
+\newcommand\dcom{\mathbin\cdot}
 
@@
 
+% ===== Doubly labeled link
+
+\newcommandx\Wlink[7][1={},4=0,6=0]{
+  \begin{scope}
+    \coordinate (SRC) at ($(\@previousformulaname-#5.south) + (#4pt,0pt)$);
+    \coordinate (TGT) at ($(\@formulaname-#7.north) + (#6pt,0pt)$);
+    \draw[#1,cap=round] 
+      	(SRC) 
+    	--
+      	node[color=black,anchor=east]{$\scriptstyle{#2}$}
+      	node[color=black,anchor=west]{$\scriptstyle{#3}$} 
+    	(TGT) ;
+  \end{scope}
+}
+
 \makeatother
@@
 
+\newcommand\cyc{\mathbin\cdot}
+
 \begin{document}
+
+\subsection{Composition}
+
+For a witness map $\sigma$ and a formula $A$ we abbreviate $\sigma\res{\fv(A)}$ to $\sigma(A)$. The witness map of a link $\link CD$ then has two components, $\sigma_C$ and $\sigma_D$.
+
+The \defn{domain-preserving composition} $\sigma\dcom\tau$ is the map $\sigma\tau\res{\dom\sigma}$.
+
+The \defn{fixpoint} $\fix\sigma$ of a witness map $\sigma$ is the least fixed point of $\sigma$, i.e.\ the least map $\rho$ satisfying $\rho = \rho\sigma$.
+Where it is used, in the composition of the witness maps of two links, we will need to demonstrate that it is well defined.
+
+\begin{definition}
+The \defn{composition} $(\net{\lambda_\Sigma^\Pi}AB)\comp(\net{\kappa_\Theta^\Phi}{\dual B}C)$ of two labelled pre-nets is
+\[
+	\net{\{~l\comp k~\mid~l\in{\lambda_\Sigma^\Pi}~,~k\in\kappa_\Theta^\Phi~\}~}AC
+%	\net{\{~\link XY^\pi\comp\link[\tau]{\dual Y}Z^\phi~\mid~\link XY^\pi\in{\lambda_\Sigma^\Pi}~,~\link[\tau]{\dual Y}Z^\phi\in\kappa_\Theta^\Phi~\}~}AC
+\]
+where the composition of two links is given by
+\[
+	\link XY^\pi\comp\link[\tau]{\dual Y}Z^\phi = \link[\rho]XZ^\psi
+\]
+where
+\[
+	\rho = (\sigma\cyc\tau)\res{\ex AX\,\cup\,\ex CZ}
+\qquad
+	\psi = ~\vcenter{
+	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq {X\rho}{Z\rho}}{
+	 \left(\vcenter{\deduce{\seq{X\sigma}{Y\sigma}\vphantom{\dual Y}}{\pi}}\right)\sigma\cyc\tau
+	&\left(\vcenter{\deduce{\seq{\dual Y\tau}{Z\tau}}{\phi}}\right)\sigma\cyc\tau
+	}}~.
+\]
+\end{definition}
+
+%	\net{\{~\link[\rho]XZ~\mid~\link XY\in{\lambda_\Sigma}~,~\link[\tau]{\dual Y}Z\in\kappa_\Theta~,~\rho = (\sigma\cyc\tau)\res{\ex AX\,\cup\,\ex CZ}~\}~}AC
+%~\rho=\sigma_A\tau_{\smash{\,\dual{\!B}}\vphantom B}\cup\tau_C\sigma_B~
+%(\sigma\res{\ex AX})(\tau\res{\ex{\dual B}{\dual Y}})\cup(\tau\res{\ex CZ})(\sigma\res{\ex BY})
+
+\[
+\begin{array}{ccc}
+    \vc{
+    \begin{tikzpicture}[net]
+        \formula[y=3]{A}
+        \formula[y=1.8]{B\*C}
+        \Vlink[red,label={$\scriptstyle{\pi,\sigma\vphantom)~}$},l]{[-2]1,1}
+        \Vlink[red,label={$\scriptstyle{~\pi'\!,\sigma\vphantom)}$},r]{[2]1,3}
+        \formula[y=1.2]{{\dual B}\+{\dual C}}
+        \formula[y=0]{D}
+        \Vlink[red,label={$\scriptstyle{\phi,\tau\vphantom)~}$},l]{1,1}
+    \end{tikzpicture}}
+    & 
+    \begin{array}{c}\scoal\\[40pt]\scoal\end{array}
+    &
+    \vc{
+    \begin{tikzpicture}[net]
+        \formula[y=3]{A}
+        \formula[y=1.8]{B\*C}
+        \Vlink[red,label={$\scriptstyle{\pi''\!\!,\sigma\vphantom)~}$},l]{1,2}
+        \formula[y=1.2]{{\dual B}\+{\dual C}}
+        \formula[y=0]{D}
+        \Vlink[red,label={$\scriptstyle{\phi'\!,\tau\vphantom)~}$},l]{2,1}
+    \end{tikzpicture}}
+\\\\ \Downarrow && \Downarrow \\\\
+    \vc{
+    \begin{tikzpicture}[net]
+        \formula[y=1.2]{A}
+        \formula[y=0]{D}
+        \Vlink[red,label={\makebox[0pt][r]{$\scriptstyle{\psi,\rho\vphantom)~}$}},l]{1,1}
+    \end{tikzpicture}}
+    &&
+    \vc{
+    \begin{tikzpicture}[net]
+        \formula[y=1.2]{A}
+        \formula[y=0]{D}
+        \Vlink[red,label={\makebox[0pt][r]{$\scriptstyle{\psi',\rho\vphantom)~}$}},l]{1,1}
+    \end{tikzpicture}}
+\end{array}
+\qquad
+\begin{array}{l}
+	\rho = (\sigma\cyc\tau)\res{\ex AX\,\cup\,\ex CZ}
+\\ \\ \\
+	\psi =~\vc{
+	\infer[\!\!\scriptstyle{\mathrm{cut}}\kern5pt]{\seq{A\rho}{D\rho}}{
+	 \left(\vc{
+	  \deduce{\seq{A\sigma}{B\sigma}\vphantom{\dual B}}{\pi\vphantom)}
+	 }\right)\sigma\cyc\tau
+	 &
+	 \left(\vc{
+	  \deduce{\seq{\dual B\tau}{D\tau}}{\phi\vphantom)}
+	 }\right)\makebox[0pt][l]{$\sigma\cyc\tau$}
+	}}
+\\ \\ \\
+	\psi' = 
+\\ \\
+	\vc{
+	\infer[\!\!\scriptstyle{\mathrm{cut}}\kern5pt]{\seq{A\rho}{D\rho}}{
+	 \left(\vc{\infer{\seq{A\sigma}{B\sigma\*C\sigma}\vphantom{\dual B}}{
+	  \deduce{\seq{A\sigma}{B\sigma}\vphantom{\dual B}}{\pi\vphantom)}
+	  &
+	  \deduce{\seq{A\sigma}{C\sigma\vphantom{\dual B}}}{\pi'\vphantom)}
+	 }}\right)\sigma\cyc\tau
+	 &
+	 \left(\vc{\infer{\seq{\dual B\tau\+\dual C\tau}{D\tau}}{
+	  \deduce{\seq{\dual B\tau}{D\tau}}{\phi\vphantom)}
+	 }}\right)\makebox[0pt][l]{$\sigma\cyc\tau$}
+	}}
+\end{array}
+\]
+
+\[
+\begin{array}{ccc}
+    \vc{
+    \begin{tikzpicture}[net]
+        \formula[y=3]{A}
+        \formula[y=1.8]{\exists x.B}
+        \Vlink[red,label={~$\scriptstyle{\pi,\sigma\vphantom)}$},r]{1,4}
+        \formula[y=1.2]{\forall x.{\dual B}}
+        \formula[y=0]{C}
+        \Vlink[red,label={~$\scriptstyle{\phi,\tau\vphantom)}$},r]{4,1}
+    \end{tikzpicture}}
+    & 
+    \begin{array}{c}\scoal\\[40pt]\stackrel{x\,\notin\,\tau\vphantom)}\scoal\end{array}
+    &
+    \vc{
+    \begin{tikzpicture}[net]
+        \formula[y=3]{A}
+        \formula[y=1.8]{\exists x.B}
+        \Vlink[red,label={~$\scriptstyle{\pi,\sigma\minus x\vphantom)}$},r]{1,1}
+        \formula[y=1.2]{\forall x.{\dual B}}
+        \formula[y=0]{C}
+        \Vlink[red,label={~$\scriptstyle{\phi,\tau\vphantom)}$},r]{1,1}
+    \end{tikzpicture}}
+\\\\ \Downarrow~~ && \Downarrow~~ \\\\
+    \vc{ 
+    \begin{tikzpicture}[net]
+        \formula[y=1.2]{A}
+        \formula[y=0]{C}
+        \Vlink[red,label={\makebox[0pt][r]{$\scriptstyle{\psi,\rho\vphantom)~}$}},l]{1,1}
+    \end{tikzpicture}}
+    &&
+    \vc{
+    \begin{tikzpicture}[net]
+        \formula[y=1.2]{A}
+        \formula[y=0]{C}
+        \Vlink[red,label={\makebox[0pt][r]{$\scriptstyle{\psi',\rho'\vphantom)~}$}},l]{1,1}
+    \end{tikzpicture}}
+\end{array}
+%
+\qquad
+%
+\begin{array}{l}
+	\rho = (\sigma\cyc\tau)\res{\ex AX\,\cup\,\ex CZ}
+\\ \\ \\
+	\rho' = (\sigma\minus x\cyc\tau)\res{\ex AX\,\cup\,\ex CZ}
+\\ \\ \\
+	\psi =~\vc{
+	\infer[\!\!\scriptstyle{\mathrm{cut}}\kern5pt]{\seq{A\rho}{C\rho}}{
+	 \left(\vc{
+	  \deduce{\seq{A\sigma}{B\sigma}\vphantom{\dual B}}{\pi\vphantom)}
+	 }\right)\sigma\cyc\tau
+	 &
+	 \left(\vc{
+	  \deduce{\seq{\dual B\tau}{D\tau}}{\phi\vphantom)}
+	 }\right)\makebox[0pt][l]{$\sigma\cyc\tau$}
+	}}
+\\ \\ \\
+	\psi' = 
+\\ \\
+	\vc{
+	\infer[\!\!\scriptstyle{\mathrm{cut}}\kern5pt]{\seq{A\rho}{C\rho}}{
+	 \left(\vc{\infer{\seq{A\sigma}{\exists x.B\sigma\minus x}\vphantom{\dual B}}{
+	  \deduce{\seq{A\sigma}{B\sigma}\vphantom{\dual B}}{\pi\vphantom)}
+	 }}\right)\sigma\cyc\tau
+	 &
+	 \left(\vc{\infer{\seq{\forall x.\dual B\tau}{C\tau}}{
+	  \deduce{\seq{\dual B\tau}{C\tau}}{\phi\vphantom)}
+	 }}\right)\makebox[0pt][l]{$\sigma\cyc\tau$}
+	}}
+\end{array}
+\]
+
+\end{document}
+
+\begin{proposition}
+If $\net{\lambda_\Sigma}AB$ and $\net{\kappa_\Theta}{\dual B}C$ both coalesce, so does their composition.
+\end{proposition}
+
+\begin{proof}
+By induction on both coalescence sequences.
+In the base case, $\lambda_\Sigma=\{\link[\varnothing]AB\}$ and $\kappa_\Theta=\{\link[\varnothing]{\dual B}C\}$, and the composition is $\net{\{\link[\varnothing]AC\}}AC$.
+
+If
+\end{proof}
+
+\begin{proposition}
+If $\net{\lambda_\Sigma}AB$ sequentializes to $\pi$ and $\net{\kappa_\Theta}{\dual B}C$ to $\phi$ then the composition $(\net{\lambda_\Sigma}AB)\comp(\net{\kappa_\Theta}{\dual B}C)$ sequentializes to a normal form $\psi$ of the proof
+\[
+	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq AC}{
+	 %\prf\pi AB & \prf\phi{\dual B}C
+	 \deduce{\seq AB\vphantom{\dual B}}{\pi}
+	&\deduce{\seq{\dual B}C}{\phi}
+	}
+\]
+\end{proposition}
+
+\end{document}
 
@@
 A \defn{witness map} $\sigma\colon \varE \rightharpoonup \terms$ is a substitution map which assigns terms to existential variables, given as a (finite) partial function.
-Its \defn{domain} $\dom(\sigma)$ are those variables for which it is defined.
+Its \defn{domain} $\dom\sigma$ is the set of those variables for which it is defined.
 The \defn{empty} witness map $\varnothing$ is the everywhere undefined partial function, and the map $\sigma[t/x]$ substitutes $t$ for $x$ and is as $\sigma$ everywhere else.
 We express by $\sigma(x)=\bot$ that $\sigma$ is undefined for $x$.
-The map $\sigma\minus x$ is undefined on $x$ and otherwise as $\sigma$.
+The map $\sigma\minus x$ is undefined on $x$ and otherwise as $\sigma$, and $\sigma\res V$ is the restriction of $\sigma$ to a set of variables $V$.
+We abbreviate by $a\in \sigma$ the statement that a variable $a$ occurs free in the range of $\sigma$, i.e.\ that $a\in\fv(\sigma(x))$ for some $x$.
 
@@
 A \defn{witness linking} $\lambda_\Sigma$ is a linking $\lambda$ with a \defn{witness labelling} $\Sigma\colon\lambda\to \varE\rightharpoonup\terms$ that assigns each link $(C,D)$ a witness map.
-We may use and define $\lambda_\Sigma$ as a set of \defn{witness links} $\link CD$, where $(C,D)$ in $\lambda$ and $\Sigma(C,D)=\sigma$.
-When link is not a witness link may be emphasized by calling it \defn{clean}.
+We may use and define $\lambda_\Sigma$ as a set of \defn{witness links} $\link CD$, where $(C,D)\in\lambda$ and $\Sigma(C,D)=\sigma$.
+When a link is not a witness link, this may be emphasized by calling it \defn{clean}.
 
@@
 %We assume the existential variables occurring in the range of $\Sigma$ to be fresh, i.e.\ distinct from any existentially quantified variable in $\seq AB$.
-We abbreviate by $a\in \sigma$ the statement that a variable $a$ occurs free in the range of $\sigma$, i.e.\ that $a\in\fv(\sigma(x))$ for some $x$.
 
 \begin{definition}
-The \defn{de-sequentialization} $[\pi]$ of a sequent proof $\prf\pi AB$ is the witness pre-net $\net{\lambda_\Sigma}AB$ where $\lambda_\Sigma=\deseq[\varnothing]\pi AB$ and $\deseq-AB$ is defined as follows.
+The \defn{de-sequentialization} $[\pi]$ of a sequent proof $\prf\pi AB$ is the witness pre-net $\net{\lambda_\Sigma}AB$ where $\lambda_\Sigma=\deseq[\varnothing]\pi AB$ and the function $\deseq-AB$ is defined as follows.
 %
@@
 	\XDeseq{\infer{\seq A{B\*C}}{
-	  \deduce[\rule{0pt}{1pt}]{\seq AB}\pi 
+	  \deduce[\rule{0pt}{1pt}]{\seq AB}{\pi\vphantom'} 
 	  && 
-	  \deduce[\rule{0pt}{1pt}]{\seq AC}\Sigma}}{A'}{B'\*C'}
+	  \deduce[\rule{0pt}{1pt}]{\seq AC}{\pi'}}}{A'}{B'\*C'}
 	& \quad=\quad 
-	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AB}\pi}{A'}{B'}
+	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AB}{\pi\vphantom'}}{A'}{B'}
 	  \cup
-	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AC}\Sigma}{A'}{C'}
+	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AC}{\pi'}}{A'}{C'}
 \\ \\
@@
 
-A witness link $\link PQ$ on two atomic formulas $P$ and $Q$ is an \defn{axiom} link if $P\sigma=\dual Q\sigma$; a witness \defn{axiom} linking is one where every link is an axiom link.
+A function call $\deseq{\prf\pi AB}{A'}{B'}$ expects that $A=A'\sigma$ and $B=B'\sigma$.
+While a sequent proof instantiates existential witnesses immedately into the premise of the existential quantifier rule, for proof nets we delay the substitutions $\sigma$.
+Hence we need to maintain the separation of the conclusion $\seq AB$ into the substitutions $\sigma$ and the subformulas $A'$ and $B'$ of the conclusion of the proof net.
+
+We will conclude this section by discussing two further essential notions.
+First, a witness link $\link PQ$ on two atomic formulas $P$ and $Q$ is an \defn{axiom} link if $P\sigma=\dual Q\sigma$; a witness \defn{axiom} linking is one where every link is an axiom link.
 Observe that the de-sequentialization $[\pi]$ is a witness pre-net with axiom linking $\deseq[\varnothing]\pi AB$.
+
+Second, given a link $\link CD$ in a pre-net $\net\lambda AB$, we expect the domain of $\sigma$ to be exactly those variables that existentially quantified in $A$ and $B$ dominating $C$ and $D$.
+That is, any variable $x$ such that there is a subformula $\exists x.X$ in $A$ that in turn has $C$ as a subformula, and likewise for $B$ and $D$.
+We will now make this precise.
+For a subformula $C$ of a formula $A$, let the \defn{existential cover} $\ex AC$ of $C$ in $A$ be the following set:
+\[
+	\ex AC = \{\,x \mid C < \exists x.X \sub A\,\}~.
+\]
+
+\begin{definition}
+A witness pre-net $\net{\lambda_\Sigma}AB$ has \defn{exact coverage} if for every link $\link CD$ in $\lambda_\Sigma$ the domain of $\sigma$ is exactly the existential covers of $C$ and $D$:
+\[
+	\dom\sigma = \ex AC\cup\ex BD~.
+\]
+\end{definition}
+
+A de-sequentialization $[\pi]$ has exact coverage.
+Note that the property is carefully formulated, using the \emph{exisential cover} rather than simply the free existential variables in a formula, to account for vacuous quantifiers ($\exists x.C$ where $x$ is not free in $C$).
+The issue becomes even more pertinent for a link $\link CD$ where $C$ occurs in $\exists x.C{\+}C'$ and $x$ is free in $C'$ but not $C$, where we still would like an explicit witness for $x$ in $\sigma$.
 
@@
 A \defn{labelled pre-net} $\net{\lambda_\Sigma^\Pi}AB$ is a witness pre-net $\net{\lambda_\Sigma}AB$ with a proof labelling $\Pi$ on $\lambda_\Sigma$.
-The \defn{initial proof labelling} $\lambda_\Sigma^\star$ of an axiom linking $\lambda_\Sigma$ is:
-\[
-	\lambda_\Sigma^\star = \{~\link PQ^\pi~\mid~\link PQ\in\lambda_\Sigma~,~\pi=~\infer{\seq{P\sigma}{Q\sigma}}{}~\}~.
+If $\lambda_\Sigma$ is an axiom linking, we assign an \defn{initial proof labelling} $\lambda_\Sigma^\star$ as follows.
+\[
+	\lambda_\Sigma^\star = \{~\link PQ^\pi~\mid~\link PQ\in\lambda_\Sigma~,~\pi=~\infer{\seq{P\sigma}{Q\sigma}}{}~\}
 \]
@@
 	$\rho,\sigma,\tau$	& $\colon$  & $\varE\rightharpoonup\terms$ & witness maps\\
-	$\Sigma,\Xi$		& $\colon$  & $(\form\times\form)\rightharpoonup\varE\rightharpoonup\terms$		& witness labellings on a linking \\
+	$\Sigma,\Theta$		& $\colon$  & $(\form\times\form)\rightharpoonup\varE\rightharpoonup\terms$		& witness labellings on a linking \\
 	$\pi,\phi,\psi$		& $\in$ & $\proofs$ & \all1 sequent proofs\\
@@
 \[
-	\net{\kappa_\Xi} CD\scoal\net{\kappa'_{\Xi'}} CD
+	\net{\kappa_\Theta} CD\scoal\net{\kappa'_{\Theta'}} CD
 \] 
@@
 	D\leq B \qquad
-	\kappa_\Xi\subseteq\lambda_\Sigma \qquad
-	\kappa'_{\Xi'}\subseteq\lambda'_{\Sigma'} \quad
+	\kappa_\Theta\subseteq\lambda_\Sigma \qquad
+	\kappa'_{\Theta'}\subseteq\lambda'_{\Sigma'} \quad
 	\text{and} \quad
-	\lambda_\Sigma-\kappa_\Xi=\lambda'_{\Sigma'}-\kappa'_{\Xi'}~.
+	\lambda_\Sigma-\kappa_\Theta=\lambda'_{\Sigma'}-\kappa'_{\Theta'}~.
 \]
@@
 
-Two useful properties of witness nets are preserved over a coalescence sequence, captured in the lemma below.
-The first property is formulated the way it is to account for vacuous quantifiers, for which no actual variable occurs in $C$ or $D$, as well as formulas such as $\exists x.C\+C'$ where $x$ occurs in $C'$ but not $C$, where we still would like an explicit witness for $x$ on a link $\link CD$.
-
-\begin{lemma}
-Every pre-net on a coalescence path $\net{\lambda_\Sigma}AB \scoal^* \net{\{\link[\varnothing]AB^\pi\}}AB$ from a witness net satisfies the \defn{exact coverage} property: for any link $\link CD$, the domain of $\sigma$ is exactly the variables existentially quantified in $\seq AB$ thad bind in $C$ and $D$,
-\[
-	\dom\sigma = \{\,x \mid C < \exists x.X \leq A\,\}
-			\cup \{\,y \mid D < \exists y.Y \leq B\,\}~.
-\]
-\end{lemma}
-
-%
-%\begin{lemma}
-%Every pre-net on a coalescence path $\net{\lambda_\Sigma}AB \scoal^* \net{\{\link[\varnothing]AB^\pi\}}AB$ from a witness net satisfies the following properties. 
-%\begin{description}
-%	\item[Eigenvariables not free]
-%For any link $\link CD$, a universal variable $a\in\varA$ quantified in $C$ or $D$ does not occur free in the range of $\sigma$, $a\notin\sigma$.
-%
-%	\item[Exact coverage]
-%For any link $\link CD$, the domain of $\sigma$ is exactly the variables existentially quantified in $\seq AB$ that will be bound in $C$ and $D$, if they occur:
-%\[
-%	\dom\sigma = \{\,x \mid C < \exists x.X \leq A\,\}
-%			\cup \{\,y \mid D < \exists y.Y \leq B\,\}~.
-%\]
-%\end{description}
-%\end{lemma}
-
-\begin{proof}
-By induction on the coalescence path, going forward from $\net{\lambda_\Sigma}AB$ for the first property, and working backward from $\net{\{\link[\varnothing]AB^\pi\}}AB$ for the second.
-\end{proof}
-
 \begin{theorem}
@@
 
-%A formula $\exists x.A$ has two natural immediate descendants: one \emph{syntactic}, its subformula $A$, and one \emph{semantic}, the premise $A[t/x]$ for its introduction rule, for any given $t$.
-We will define the latter as a tree-order generated from a formula $A$: the \defn{positions} of $A$ are its subformulas under substitution,
-%\[
-%	\poss A~=~\{~B'\sigma~\mid~A=A'\sigma~,~B'\sub A'~,~\sigma\in\varE\rightharpoonup\terms~\}
-%\]
-
 A \defn{slice} is the fraction of a proof that depends on a given choice of one branch (or projection) on each product formula $A\*B$.
@@
 
-%In the propositional case, slices are readily defined as sets of subformulas. Here, in the first-order case, we will need to
-
-%The immediate problem is that the number of positions immediately below $\exists x.B$ is infinite, as there is one immediate descendant $B[t/x]$ for every term $t$.
-We reduce it to finite width by restricting a slice to just the terms assigned to $x$ by the witness labelling $\Sigma$ in a pre-net $\net{\lambda_\Sigma}AB$.
-
 For a witness linking $\lambda_\Sigma$ and an existential variable $x$, write $\Sigma(x)\subseteq\terms$ for the \defn{witness set} of $x$, which collects the terms assigned to $x$ by the witness maps in $\Sigma$ for every link in $\lambda$:
@@
 \]
-%
-Given a witness linking $\lambda_\Sigma$, a \defn{slice} $S$ of a formula $A$ and a witness map $\sigma$ is a set of pairs $(A',\sigma)$ where $A'$ is a subformula of $A$, given by: $S=\{(A,\sigma)\}\cup S'$ where $S'$ is as follows.
+
+\begin{definition}[Slice]
+Given a witness linking $\lambda_\Sigma$, a \defn{slice} $S$ of a formula $A$ and a witness map $\sigma$ is a set of pairs $(A',\sigma')$, where $A'$ is a subformula of $A$ and $\sigma\subseteq\sigma'$, given by: $S=\{(A,\sigma)\}\cup S'$ where $S'$ is as follows.
 %
@@
 	\item
-\makebox[70pt][l]{If $A = P$}			then $S'=\varnothing$.
+\makebox[65pt][l]{If $A = P$}			then $S'=\varnothing$.
 	\item
-\makebox[70pt][l]{If $A = B\+C$} 		then $S'=S_B\uplus S_C$ where $S_B$ is a slice of $B$ and $\sigma$, and $S_C$ a slice of $C$ and $\sigma$.
+\makebox[65pt][l]{If $A = B\+C$} 		then $S'=S_B\uplus S_C$ with $S_B$ a slice of $B$ and $\sigma$, and $S_C$ one of $C$ and $\sigma$.
 	\item
-\makebox[70pt][l]{If $A = B\*C$}		then $S'$ is a slice of $B$ and $\sigma$ or a slice of $C$ and $\sigma$.
+\makebox[65pt][l]{If $A = B\*C$}		then $S'$ is a slice of $B$ and $\sigma$ or a slice of $C$ and $\sigma$.
 	\item
-\makebox[70pt][l]{If $A = \exists x.B$}	then $S'=\uplus_{t\,\in\,\Sigma(x)}S_t$ where each $S_t$ is a slice of $B$ and $\sigma[t/x]$.
+\makebox[65pt][l]{If $A = \exists x.B$}	then $S'=\uplus_{t\,\in\,\Sigma(x)}S_t$ where each $S_t$ is a slice of $B$ and $\sigma[t/x]$.
 	\item
-\makebox[70pt][l]{If $A = \forall a.B$}	then $S'$ is a slice of $B$ and $\sigma$.
+\makebox[65pt][l]{If $A = \forall a.B$}	then $S'$ is a slice of $B$ and $\sigma$.
 \end{itemize}
@@
 A \defn{slice} of a witness pre-net $\net{\lambda_\Sigma} AB$ is the intersection $\lambda_\Sigma\cap S$ of $\lambda_\Sigma$ with a slice $S$ of $\seq AB$.
-
-Within a slice, we need to ensure that the order in which quantifiers are instantiated is sound.
+\end{definition}
+
+As in the propositional case, for correctness we will require that each slice is a singleton.
+In addition, within each slice we need to ensure that the order in which quantifiers are instantiated is sound.
 That is, we need to have an analogue of the \emph{eigenvariable condition} on the $\qrr!$-rule of sequent calculus, that the quantified variable $a$ of the primary formula $\forall a.A$ does not occur free in the context.
 We will define a \defn{dependency} condition to this effect.
-
-Since we will require that each slice contains a single link, for simplicity we will define the dependency condition on individual links rather than on slices.
-It is expected that for a more involved logic that includes multiplicative connectives, a dependency condition such as the below one needs to be applied to a slice instead.
-
-For a subformula $C$ of a formula $A$, let the \defn{existential covering} $\ex AC$ of $C$ be the set of variables that are existentially quantified in $A$ dominating $C$:
-\[
-	\ex AC = \{\,x \mid C < \exists x.X \sub A\,\}
-\]
+For simplicity we will define the dependency condition on individual links rather than on slices (since each slice will be a singleton).
+
 In a pre-net $\net{\lambda_\Sigma}AB$, let the \defn{column} of a link $\link CD$ be the set of pairs 
 \[
-	\{~(X,\sigma|\ex AX)~\mid~C\sub X\sub A~\}\cup\{~(Y,\sigma|\ex BY)~\mid~D\sub Y\sub B~\}~,
-\]
-with an order $(\dep)$ given by: $(X,\rho)\dep(Y,\tau)$ if $X\leq Y$, or $Y$ occurs as $\forall a.Y$ and $a\in\rho$.
-
+	\{~(X,\sigma\res{\ex AX})~\mid~C\sub X\sub A~\}\cup\{~(Y,\sigma\res{\ex BY})~\mid~D\sub Y\sub B~\}~,
+\]
+with an order $(\dep)$ given by: $(X,\rho)\dep(Y,\tau)$ if $X\leq Y$ or $Y$ occurs as $\forall a.Y$ and $a\in\rho$.
+
+%It is expected that for a more involved logic that includes multiplicative connectives, a dependency condition such as the below one needs to be applied to a slice instead.
+%
 \begin{definition}
 A witness pre-net is \defn{correct} if it is
-\begin{enumerate}
+\begin{itemize}
 \item \defn{slice-correct}: every slice is a singleton, and
 \item \defn{dependency-correct}: every column is a partial order (i.e.\ is acyclic/antisymmetric).
-\end{enumerate}
+\end{itemize}
 \end{definition}
+
+\begin{lemma}
+If a pre-net coalesces, it has exact coverage.
+%Every pre-net on a coalescence path $\net{\lambda_\Sigma}AB \scoal^* \net{\{\link[\varnothing]AB^\pi\}}AB$ from a witness net satisfies the exact coverage property.
+\end{lemma}
+
+\begin{proof}
+By induction on the coalescence path. %, working backward from $\net{\{\link[\varnothing]AB^\pi\}}AB$.
+\end{proof}
 
@@
 \begin{proof}
-Let $L=\net{\lambda_\Sigma}AB$ and $R=\net{\kappa_\Xi}AB$.
+Let $L=\net{\lambda_\Sigma}AB$ and $R=\net{\kappa_\Theta}AB$.
 We will consider the four coalescence steps as shown below.
@@
 A slice $S_B$ of $B$ and $\varnothing$ containing either of $(D_0,\tau)$, $(D_1,\tau)$, and $(D_0\+D_1,\tau)$ must also contain the other two. 
+%
+%\lutz{something is confusing here.
+It seems you are using different notions of slice.
+Above it says that correctness means that slices are singletons, and here you imply that slices contain more than one element.}
+%
+% A slice of a NET is singleton; a slice of FORMULA or SEQUENT need not be.
+%
 A slice $S$ of $\seq AB$ then contains all three of $\link C{D_0}$, $\link C{D_1}$, and $\link C{D_0{\+}D_1}$, or none.
-It follows that $S\cap \lambda_\Sigma$ is a singleton if and only if $S\cap\kappa_\Xi$ is.
+It follows that $S\cap \lambda_\Sigma$ is a singleton if and only if $S\cap\kappa_\Theta$ is.
 Since other slices are unaffected, $L$ is slice-correct if and only if $R$ is.
@@
 A slice $S$ of $\seq AB$ contains $\link C{D_0\+D_1}$ if and only if it contains either of $\link C{D_0}$ or $\link C{D_1}$, and may not contain both.
-Then $S\cap \lambda_\Sigma$ is a singleton if and only if $S\cap\kappa_\Xi$ is.
+Then $S\cap \lambda_\Sigma$ is a singleton if and only if $S\cap\kappa_\Theta$ is.
 Dependency-correctness is immediate, as above.
@@
 	\item[$(\srr?)$]
-The witness sets $\Sigma(x)$ and $\Xi(x)$ for $L$ and $R$ need not be the same, since $L$ has $\sigma$ where $R$ has $\sigma\minus x$.
-Let $\Sigma(x)=\{t,t_1,\dots,t_n\}$ and $\Xi(x)=\{t_1,\dots,t_n\}$, where $\sigma(x)=t$.
-For every slice $S_B$ of $B$ over $\Sigma$ there is a corresponding slice $S'_B$ over $\Xi$, both (or neither) containing $(\exists x.D,\tau)$ and $(D,\tau[t_i/x])$ for $i\leq n$, but the former in addition having $(D,\tau[t/x])$.
-Then $S\cap \lambda_\Sigma$ is the singleton $\{\link CD\}$ if and only if $S\cap\kappa_\Xi$ is $\{\link[\sigma\minus x]C{\exists x.D}\}$, where it should be observed that if $t$ is also a witness to $x$ in some other slice of $R$, then $t\in\Xi(x)$ and in fact $S=S'$.
+The witness sets $\Sigma(x)$ and $\Theta(x)$ for $L$ and $R$ need not be the same, since $L$ has $\sigma$ where $R$ has $\sigma\minus x$.
+Let $\Sigma(x)=\{t,t_1,\dots,t_n\}$ and $\Theta(x)=\{t_1,\dots,t_n\}$, where $\sigma(x)=t$.
+For every slice $S_B$ of $B$ over $\Sigma$ there is a corresponding slice $S'_B$ over $\Theta$, both (or neither) containing $(\exists x.D,\tau)$ and $(D,\tau[t_i/x])$ for $i\leq n$, but the former in addition having $(D,\tau[t/x])$.
+Then $S\cap \lambda_\Sigma$ is the singleton $\{\link CD\}$ if and only if $S\cap\kappa_\Theta$ is $\{\link[\sigma\minus x]C{\exists x.D}\}$, where it should be observed that if $t$ is also a witness to $x$ in some other slice of $R$, then $t\in\Theta(x)$ and in fact $S=S'$.
 
@@
 	\item[$(\srr!)$]
-A slice $S$ of $\seq AB$ contains $\link CD$ if and only if it contains also $\link C{\forall a.D}$, and hence $S\cap\lambda_\Sigma$ is a singleton if and only if $S\cap\kappa_\Xi$ is.
+A slice $S$ of $\seq AB$ contains $\link CD$ if and only if it contains also $\link C{\forall a.D}$, and hence $S\cap\lambda_\Sigma$ is a singleton if and only if $S\cap\kappa_\Theta$ is.
 
@@
 
-\subsection{Normalization}
-
-\includegraphics[scale=0.4]{normalization.jpg}
-
 \section{Unification nets}
@@
 
-For two witness labellings $\Sigma$ and $\Xi$ on the same linking $\lambda$, one is \defn{more general} than the other, $\Sigma\gen\Xi$, if $\Sigma(C,D)\gen\Xi(C,D)$ for every link $(C,D)\in\lambda$.
-We extend this to the linkings themselves: $\lambda_\Sigma\gen\lambda_\Xi$.
+For two witness labellings $\Sigma$ and $\Theta$ on the same linking $\lambda$, one is \defn{more general} than the other, $\Sigma\gen\Theta$, \lutz{say which one is more general} if $\Sigma(C,D)\gen\Theta(C,D)$ for every link $(C,D)\in\lambda$.
+We extend this to the linkings themselves: $\lambda_\Sigma\gen\lambda_\Theta$.
 Observe that for an axiom linking $\lambda$, the initial linking $\lambda_\star$ is the most general among the witness linkings $\lambda_\Sigma$ for any $\Sigma$.
@@
 We write $\Sigma\tau$ for the composition of every map in $\Sigma$ with $\tau$:	$\Sigma\tau(C,D) = \Sigma(C,D)\tau$.
-Because of the exact coverage convention, we have that, if $\lambda_\star=\lambda_\Sigma\gen\lambda_\Xi$, then $\Xi=\Sigma\tau$ for some $\tau$.
+Because of the exact coverage convention, we have that, if $\lambda_\star=\lambda_\Sigma\gen\lambda_\Theta$, then $\Theta=\Sigma\tau$ for some $\tau$.
 

### 2018-01-05 ALL1.tex
composition

@@
 \newcommand\join{\vee}
+\newcommand\minus{\mathop{\!/\mathchoice{\kern-3pt}{\kern-3pt}{\kern-2.5pt}{\kern-2pt}/\!}}
 
 \newcommand\res[1]{|_{#1}}
-\newcommand\fix[1]{\vec{#1}}
+\newcommand\fix[1]{\overrightharpoon{#1}}
 \newcommand\dcom{\mathbin\cdot}
@@
 
+\newcommand\subdual[1]{_{\smash{\,\dual{\!#1}}}}
+
 % ===== Slices
@@
 \newcommand\link[3][\sigma]{(#2,#3)_{#1}}
-\newcommand\minus{\mathop{\!/\mathchoice{\kern-3pt}{\kern-3pt}{\kern-2.5pt}{\kern-2pt}/\!}}
 
@@
 
-% ===== Doubly labeled link
-
-\newcommandx\Wlink[7][1={},4=0,6=0]{
-  \begin{scope}
-    \coordinate (SRC) at ($(\@previousformulaname-#5.south) + (#4pt,0pt)$);
-    \coordinate (TGT) at ($(\@formulaname-#7.north) + (#6pt,0pt)$);
-    \draw[#1,cap=round] 
-      	(SRC) 
-    	--
-      	node[color=black,anchor=east]{$\scriptstyle{#2}$}
-      	node[color=black,anchor=west]{$\scriptstyle{#3}$} 
-    	(TGT) ;
-  \end{scope}
-}
+% ===== Overset extensible harpoon
+
+\DeclareFontFamily{U}{MnSymbolA}{}
+\DeclareFontShape{U}{MnSymbolA}{m}{n}{
+    <-6>  MnSymbolA5
+   <6-7>  MnSymbolA6
+   <7-8>  MnSymbolA7
+   <8-9>  MnSymbolA8
+   <9-10> MnSymbolA9
+  <10-12> MnSymbolA10
+  <12->   MnSymbolA12}{}
+\DeclareFontShape{U}{MnSymbolA}{b}{n}{
+    <-6>  MnSymbolA-Bold5
+   <6-7>  MnSymbolA-Bold6
+   <7-8>  MnSymbolA-Bold7
+   <8-9>  MnSymbolA-Bold8
+   <9-10> MnSymbolA-Bold9
+  <10-12> MnSymbolA-Bold10
+  <12->   MnSymbolA-Bold12}{}
+\DeclareSymbolFont{MnSyA}{U}{MnSymbolA}{m}{n}
+\SetSymbolFont{MnSyA}{bold}{U}{MnSymbolA}{b}{n}
+
+\DeclareRobustCommand{\overleftharpoon}{\mathpalette{\overarrow@\leftharpoonfill@}}
+\DeclareRobustCommand{\overrightharpoon}{\mathpalette{\overarrow@\rightharpoonfill@}}
+\def\leftharpoonfill@{\arrowfill@\leftharpoondown\mn@relbar\mn@relbar}
+\def\rightharpoonfill@{\arrowfill@\mn@relbar\mn@relbar\rightharpoonup}
+
+\DeclareMathSymbol{\leftharpoondown}{\mathrel}{MnSyA}{'112}
+\DeclareMathSymbol{\rightharpoonup}{\mathrel}{MnSyA}{'100}
+\DeclareMathSymbol{\mn@relbar}{\mathrel}{MnSyA}{'320}
 
@@
 
-\newcommand\cyc{\mathbin\cdot}
+\newcommand\Seq{\vphantom(\seq}
+\newcommand\Prf[3]{\deduce{\Seq{#2}{#3}}{\vphantom(#1}}
 
 \begin{document}
-
-\subsection{Composition}
-
-For a witness map $\sigma$ and a formula $A$ we abbreviate $\sigma\res{\fv(A)}$ to $\sigma(A)$. The witness map of a link $\link CD$ then has two components, $\sigma_C$ and $\sigma_D$.
-
-The \defn{domain-preserving composition} $\sigma\dcom\tau$ is the map $\sigma\tau\res{\dom\sigma}$.
-
-The \defn{fixpoint} $\fix\sigma$ of a witness map $\sigma$ is the least fixed point of $\sigma$, i.e.\ the least map $\rho$ satisfying $\rho = \rho\sigma$.
-Where it is used, in the composition of the witness maps of two links, we will need to demonstrate that it is well defined.
-
-\begin{definition}
-The \defn{composition} $(\net{\lambda_\Sigma^\Pi}AB)\comp(\net{\kappa_\Theta^\Phi}{\dual B}C)$ of two labelled pre-nets is
-\[
-	\net{\{~l\comp k~\mid~l\in{\lambda_\Sigma^\Pi}~,~k\in\kappa_\Theta^\Phi~\}~}AC
-%	\net{\{~\link XY^\pi\comp\link[\tau]{\dual Y}Z^\phi~\mid~\link XY^\pi\in{\lambda_\Sigma^\Pi}~,~\link[\tau]{\dual Y}Z^\phi\in\kappa_\Theta^\Phi~\}~}AC
-\]
-where the composition of two links is given by
-\[
-	\link XY^\pi\comp\link[\tau]{\dual Y}Z^\phi = \link[\rho]XZ^\psi
-\]
-where
-\[
-	\rho = (\sigma\cyc\tau)\res{\ex AX\,\cup\,\ex CZ}
-\qquad
-	\psi = ~\vcenter{
-	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq {X\rho}{Z\rho}}{
-	 \left(\vcenter{\deduce{\seq{X\sigma}{Y\sigma}\vphantom{\dual Y}}{\pi}}\right)\sigma\cyc\tau
-	&\left(\vcenter{\deduce{\seq{\dual Y\tau}{Z\tau}}{\phi}}\right)\sigma\cyc\tau
-	}}~.
-\]
-\end{definition}
-
-%	\net{\{~\link[\rho]XZ~\mid~\link XY\in{\lambda_\Sigma}~,~\link[\tau]{\dual Y}Z\in\kappa_\Theta~,~\rho = (\sigma\cyc\tau)\res{\ex AX\,\cup\,\ex CZ}~\}~}AC
-%~\rho=\sigma_A\tau_{\smash{\,\dual{\!B}}\vphantom B}\cup\tau_C\sigma_B~
-%(\sigma\res{\ex AX})(\tau\res{\ex{\dual B}{\dual Y}})\cup(\tau\res{\ex CZ})(\sigma\res{\ex BY})
-
-\[
-\begin{array}{ccc}
-    \vc{
-    \begin{tikzpicture}[net]
-        \formula[y=3]{A}
-        \formula[y=1.8]{B\*C}
-        \Vlink[red,label={$\scriptstyle{\pi,\sigma\vphantom)~}$},l]{[-2]1,1}
-        \Vlink[red,label={$\scriptstyle{~\pi'\!,\sigma\vphantom)}$},r]{[2]1,3}
-        \formula[y=1.2]{{\dual B}\+{\dual C}}
-        \formula[y=0]{D}
-        \Vlink[red,label={$\scriptstyle{\phi,\tau\vphantom)~}$},l]{1,1}
-    \end{tikzpicture}}
-    & 
-    \begin{array}{c}\scoal\\[40pt]\scoal\end{array}
-    &
-    \vc{
-    \begin{tikzpicture}[net]
-        \formula[y=3]{A}
-        \formula[y=1.8]{B\*C}
-        \Vlink[red,label={$\scriptstyle{\pi''\!\!,\sigma\vphantom)~}$},l]{1,2}
-        \formula[y=1.2]{{\dual B}\+{\dual C}}
-        \formula[y=0]{D}
-        \Vlink[red,label={$\scriptstyle{\phi'\!,\tau\vphantom)~}$},l]{2,1}
-    \end{tikzpicture}}
-\\\\ \Downarrow && \Downarrow \\\\
-    \vc{
-    \begin{tikzpicture}[net]
-        \formula[y=1.2]{A}
-        \formula[y=0]{D}
-        \Vlink[red,label={\makebox[0pt][r]{$\scriptstyle{\psi,\rho\vphantom)~}$}},l]{1,1}
-    \end{tikzpicture}}
-    &&
-    \vc{
-    \begin{tikzpicture}[net]
-        \formula[y=1.2]{A}
-        \formula[y=0]{D}
-        \Vlink[red,label={\makebox[0pt][r]{$\scriptstyle{\psi',\rho\vphantom)~}$}},l]{1,1}
-    \end{tikzpicture}}
-\end{array}
-\qquad
-\begin{array}{l}
-	\rho = (\sigma\cyc\tau)\res{\ex AX\,\cup\,\ex CZ}
-\\ \\ \\
-	\psi =~\vc{
-	\infer[\!\!\scriptstyle{\mathrm{cut}}\kern5pt]{\seq{A\rho}{D\rho}}{
-	 \left(\vc{
-	  \deduce{\seq{A\sigma}{B\sigma}\vphantom{\dual B}}{\pi\vphantom)}
-	 }\right)\sigma\cyc\tau
-	 &
-	 \left(\vc{
-	  \deduce{\seq{\dual B\tau}{D\tau}}{\phi\vphantom)}
-	 }\right)\makebox[0pt][l]{$\sigma\cyc\tau$}
-	}}
-\\ \\ \\
-	\psi' = 
-\\ \\
-	\vc{
-	\infer[\!\!\scriptstyle{\mathrm{cut}}\kern5pt]{\seq{A\rho}{D\rho}}{
-	 \left(\vc{\infer{\seq{A\sigma}{B\sigma\*C\sigma}\vphantom{\dual B}}{
-	  \deduce{\seq{A\sigma}{B\sigma}\vphantom{\dual B}}{\pi\vphantom)}
-	  &
-	  \deduce{\seq{A\sigma}{C\sigma\vphantom{\dual B}}}{\pi'\vphantom)}
-	 }}\right)\sigma\cyc\tau
-	 &
-	 \left(\vc{\infer{\seq{\dual B\tau\+\dual C\tau}{D\tau}}{
-	  \deduce{\seq{\dual B\tau}{D\tau}}{\phi\vphantom)}
-	 }}\right)\makebox[0pt][l]{$\sigma\cyc\tau$}
-	}}
-\end{array}
-\]
-
-\[
-\begin{array}{ccc}
-    \vc{
-    \begin{tikzpicture}[net]
-        \formula[y=3]{A}
-        \formula[y=1.8]{\exists x.B}
-        \Vlink[red,label={~$\scriptstyle{\pi,\sigma\vphantom)}$},r]{1,4}
-        \formula[y=1.2]{\forall x.{\dual B}}
-        \formula[y=0]{C}
-        \Vlink[red,label={~$\scriptstyle{\phi,\tau\vphantom)}$},r]{4,1}
-    \end{tikzpicture}}
-    & 
-    \begin{array}{c}\scoal\\[40pt]\stackrel{x\,\notin\,\tau\vphantom)}\scoal\end{array}
-    &
-    \vc{
-    \begin{tikzpicture}[net]
-        \formula[y=3]{A}
-        \formula[y=1.8]{\exists x.B}
-        \Vlink[red,label={~$\scriptstyle{\pi,\sigma\minus x\vphantom)}$},r]{1,1}
-        \formula[y=1.2]{\forall x.{\dual B}}
-        \formula[y=0]{C}
-        \Vlink[red,label={~$\scriptstyle{\phi,\tau\vphantom)}$},r]{1,1}
-    \end{tikzpicture}}
-\\\\ \Downarrow~~ && \Downarrow~~ \\\\
-    \vc{ 
-    \begin{tikzpicture}[net]
-        \formula[y=1.2]{A}
-        \formula[y=0]{C}
-        \Vlink[red,label={\makebox[0pt][r]{$\scriptstyle{\psi,\rho\vphantom)~}$}},l]{1,1}
-    \end{tikzpicture}}
-    &&
-    \vc{
-    \begin{tikzpicture}[net]
-        \formula[y=1.2]{A}
-        \formula[y=0]{C}
-        \Vlink[red,label={\makebox[0pt][r]{$\scriptstyle{\psi',\rho'\vphantom)~}$}},l]{1,1}
-    \end{tikzpicture}}
-\end{array}
-%
-\qquad
-%
-\begin{array}{l}
-	\rho = (\sigma\cyc\tau)\res{\ex AX\,\cup\,\ex CZ}
-\\ \\ \\
-	\rho' = (\sigma\minus x\cyc\tau)\res{\ex AX\,\cup\,\ex CZ}
-\\ \\ \\
-	\psi =~\vc{
-	\infer[\!\!\scriptstyle{\mathrm{cut}}\kern5pt]{\seq{A\rho}{C\rho}}{
-	 \left(\vc{
-	  \deduce{\seq{A\sigma}{B\sigma}\vphantom{\dual B}}{\pi\vphantom)}
-	 }\right)\sigma\cyc\tau
-	 &
-	 \left(\vc{
-	  \deduce{\seq{\dual B\tau}{D\tau}}{\phi\vphantom)}
-	 }\right)\makebox[0pt][l]{$\sigma\cyc\tau$}
-	}}
-\\ \\ \\
-	\psi' = 
-\\ \\
-	\vc{
-	\infer[\!\!\scriptstyle{\mathrm{cut}}\kern5pt]{\seq{A\rho}{C\rho}}{
-	 \left(\vc{\infer{\seq{A\sigma}{\exists x.B\sigma\minus x}\vphantom{\dual B}}{
-	  \deduce{\seq{A\sigma}{B\sigma}\vphantom{\dual B}}{\pi\vphantom)}
-	 }}\right)\sigma\cyc\tau
-	 &
-	 \left(\vc{\infer{\seq{\forall x.\dual B\tau}{C\tau}}{
-	  \deduce{\seq{\dual B\tau}{C\tau}}{\phi\vphantom)}
-	 }}\right)\makebox[0pt][l]{$\sigma\cyc\tau$}
-	}}
-\end{array}
-\]
-
-\end{document}
-
-\begin{proposition}
-If $\net{\lambda_\Sigma}AB$ and $\net{\kappa_\Theta}{\dual B}C$ both coalesce, so does their composition.
-\end{proposition}
-
-\begin{proof}
-By induction on both coalescence sequences.
-In the base case, $\lambda_\Sigma=\{\link[\varnothing]AB\}$ and $\kappa_\Theta=\{\link[\varnothing]{\dual B}C\}$, and the composition is $\net{\{\link[\varnothing]AC\}}AC$.
-
-If
-\end{proof}
-
-\begin{proposition}
-If $\net{\lambda_\Sigma}AB$ sequentializes to $\pi$ and $\net{\kappa_\Theta}{\dual B}C$ to $\phi$ then the composition $(\net{\lambda_\Sigma}AB)\comp(\net{\kappa_\Theta}{\dual B}C)$ sequentializes to a normal form $\psi$ of the proof
-\[
-	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq AC}{
-	 %\prf\pi AB & \prf\phi{\dual B}C
-	 \deduce{\seq AB\vphantom{\dual B}}{\pi}
-	&\deduce{\seq{\dual B}C}{\phi}
-	}
-\]
-\end{proposition}
-
-\end{document}
 
@@
 
+\subsection{Composition}
+
+\[
+\begin{array}{ccc}
+	\vc{
+	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\Seq AC}{
+	 \infer[\!\!\scriptstyle{\qrr*}]{\Seq A{B_1\*B_2}\vphantom{\dual B}}{\Prf{\pi_1}A{B_1} & \Prf{\pi_2}A{B_2}}
+	 &&
+	 \infer[\!\!\scriptstyle{\qrr+i}]{\Seq {\dual B_1\+\dual B_2}C}{\Prf\phi{B_i}C}
+	}}
+	&\Rightarrow&
+	\vc{\infer[\!\!\scriptstyle{\mathrm{cut}}]{\Seq AC}{\Prf{\pi_i}A{B_i} && \Prf\phi{\dual B_i}C}}
+\\ \\
+	\vc{
+	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\Seq AC}{
+	 \infer[\!\!\scriptstyle{\qrr?t}]{\Seq A{\exists x.B}}{\Prf\pi A{B[t/x]}}
+	 &&
+	 \infer[\!\!\scriptstyle{\qrr!}]{\Seq {\forall x.\dual B}C}{\Prf\phi{\dual B}C}
+	}}
+	&\Rightarrow&
+	\vc{\infer[\!\!\scriptstyle{\mathrm{cut}}]{\Seq AC}{\Prf\pi A{B[t/x]} && \Prf{\phi[t/x]}{\dual B[t/x]}C}}
+
+\end{array}
+\]
+
+For a witness map $\sigma$ and a formula $B$ that is understood as a subformula of a formula $A$, we abbreviate $\sigma\res{\ex AB}$ to $\sigma_B$.
+A witness map of a link $\link CD$ then has two components, $\sigma_C$ and $\sigma_D$.
+
+The \defn{domain-preserving composition} of two witness maps $\sigma\dcom\tau$ is the map $(\sigma\tau)\res{\dom\sigma}$.
+
+The \defn{least fixed point} $\fix\sigma$ of a witness map $\sigma$ is the least map $\rho$ satisfying $\rho = \rho\sigma$.
+It is the shortest sequence $\fix\sigma=\sigma\sigma\dots\sigma$ such that no variable is both in the domain and range of $\fix\sigma$.
+Where it is used, in the composition of the witness maps of two links, we will need to demonstrate that it is well defined.
+
+\begin{definition}
+The \defn{composition} of two proof links $\link AB^\pi\comp\link[\tau]{\dual B}C^\phi$ is $\link[\rho]AC^\psi$ where
+\[
+	\rho = \sigma_A\tau_C\dcom\fix{\sigma_B\tau\subdual B}
+\qquad\text{and}\qquad
+	\psi = ~\vcenter{
+	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq {A\rho}{B\rho}}{
+	 \left(\vcenter{\deduce{\seq{A\sigma}{B\sigma}\vphantom{\dual B}}{\vphantom\phi\pi}}\right)\fix{\sigma_B\tau\subdual B}
+	&\left(\vcenter{\deduce{\seq{\dual B\tau}{C\tau}}{\phi}}\right)\fix{\sigma_B\tau\subdual B}
+	}}~.
+\]
+The \defn{composition} of two labelled pre-nets $(\net{\lambda_\Sigma^\Pi}AB)\comp(\net{\kappa_\Theta^\Phi}{\dual B}C)$ is then
+\[
+	\net{\{~\link XY^\pi\comp\link[\tau]{\dual Y}Z^\phi
+		~\mid~
+		\link XY^\pi\in{\lambda_\Sigma^\Pi}
+		~,~
+		\link[\tau]{\dual Y}Z^\phi\in\kappa_\Theta^\Phi~\}
+	}AC~.
+\]
+The composition of two witness pre-nets omits the proof annotations.
+\end{definition}
+
+%	\net{\{~\link[\rho]XZ~\mid~\link XY\in{\lambda_\Sigma}~,~\link[\tau]{\dual Y}Z\in\kappa_\Theta~,~\rho = (\sigma\cyc\tau)\res{\ex AX\,\cup\,\ex CZ}~\}~}AC
+%~\rho=\sigma_A\tau_{\smash{\,\dual{\!B}}\vphantom B}\cup\tau_C\sigma_B~
+%(\sigma\res{\ex AX})(\tau\res{\ex{\dual B}{\dual Y}})\cup(\tau\res{\ex CZ})(\sigma\res{\ex BY})
+
+In the following we will demonstrate that composition gives the desired result: if a net $L$ sequentializes to $\pi$ and $R$ to $\phi$, then $L\comp R$ sequentializes to a normal form of the composition of $\pi$ and $\phi$ with a cut.
+To this end we will explore how composition and sequentialization interact.
+We will consider the critical pairs of sequentialization with composition, and demonstrate that how they are resolved.
+
+The first critical pair of composition (downward as $\Rightarrow$) and sequentialization is the following.
+We consider the composition of pre-nets on $\seq AB$ and $\seq{\dual B}C$ where $B=B_1\*B_2$, with a synchronized sequentialization step on both pre-nets.
+\[
+\begin{array}{ccc}
+    \vc{
+    \begin{tikzpicture}[net]
+        \formula[y=3]{A}
+        \formula[y=1.8]{B*{_1}\*B*{_2}}
+        \Vlink[red,label={$\scriptstyle{\pi,\sigma\vphantom)~}$},l]{[-2]1,1}
+        \Vlink[red,label={$\scriptstyle{~\pi'\!,\sigma\vphantom)}$},r]{[2]1,3}
+        \formula[y=1.2]{{\dual B}*{_1}\+{\dual B}*{_2}}
+        \formula[y=0]{C}
+        \Vlink[red,label={$\scriptstyle{\phi,\tau\vphantom)~}$},l]{1,1}
+    \end{tikzpicture}}
+    & 
+    \begin{array}{c}\scoal\\[40pt]\scoal\end{array}
+    &
+    \vc{
+    \begin{tikzpicture}[net]
+        \formula[y=3]{A}
+        \formula[y=1.8]{B*{_1}\*B*{_2}}
+        \Vlink[red,label={$\scriptstyle{\pi''\!\!,\sigma\vphantom)~}$},l]{1,2}
+        \formula[y=1.2]{{\dual B}*{_1}\+{\dual B}*{_2}}
+        \formula[y=0]{C}
+        \Vlink[red,label={$\scriptstyle{\phi'\!,\tau\vphantom)~}$},l]{2,1}
+    \end{tikzpicture}}
+\\\\[-5pt] \Downarrow && \Downarrow \\\\[-5pt]
+    \vc{
+    \begin{tikzpicture}[net]
+        \formula[y=1.2]{A}
+        \formula[y=0]{C}
+        \Vlink[red,label={\makebox[0pt][r]{$\scriptstyle{\psi,\rho\vphantom)~}$}},l]{1,1}
+    \end{tikzpicture}}
+    &&
+    \vc{
+    \begin{tikzpicture}[net]
+        \formula[y=1.2]{A}
+        \formula[y=0]{C}
+        \Vlink[red,label={\makebox[0pt][r]{$\scriptstyle{\psi',\rho'\vphantom)~}$}},l]{1,1}
+    \end{tikzpicture}}
+\end{array}
+\qquad
+\begin{array}{l@{\,}l}
+	\rho  &=~ \sigma_A\tau_C\dcom\fix{\sigma_B\tau\subdual B} 
+\\ \\
+	\rho' &=~ \sigma_A\tau_C\dcom\fix{\sigma_{B_1}\tau\subdual{B_1}}
+\\ \\
+	\psi &=~\vc{
+	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq{A\rho}{C\rho}}{
+	 \left(\vc{
+	  \deduce{\seq{A\sigma}{B_1\sigma}\vphantom{\dual B_1}}{\pi\vphantom)}
+	 }\right)\fix{\sigma_{B_1}\tau\subdual{B_1}}
+	 &
+	 \left(\vc{
+	  \deduce{\seq{\dual B_1\tau}{C\tau}}{\phi\vphantom)}
+	 }\right)\makebox[0pt][l]{$\fix{\sigma_{B_1}\tau\subdual{B_1}}$}
+	}}
+\\ \\ \\
+	\psi' &= ~
+	\vc{\scalebox{0.75}{$
+	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq{A\rho'}{C\rho'}}{
+	 \left(\vc{\infer{\seq{A\sigma}{B_1\sigma\*B_2\sigma}\vphantom{\dual B}}{
+	  \deduce{\seq{A\sigma}{B_1\sigma}\vphantom{\dual B}}{\pi\vphantom)}
+	  &
+	  \deduce{\seq{A\sigma}{B_2\sigma\vphantom{\dual B}}}{\pi'\vphantom)}
+	 }}\right)\fix{\sigma_B\tau\subdual B}
+	 &
+	 \left(\vc{\infer{\seq{\dual B_1\tau\+\dual B_2\tau}{C\tau}}{
+	  \deduce{\seq{\dual B_1\tau}{C\tau}}{\phi\vphantom)}
+	 }}\right)\makebox[0pt][l]{$\fix{\sigma_B\tau\subdual B}$}
+	}$}\kern5pt}
+\end{array}
+\]
+Since the existential covers of $B$ and $B_1$ are the same, $\sigma_B\tau\subdual B = \sigma_{B_1}\tau\subdual{B_1}$ and $\rho=\rho'$.
+It then follows that $\psi'$ cut-eliminates in one step to $\psi$.
+
+The next critical pair is the following.
+\[
+\begin{array}{ccc}
+    \vc{
+    \begin{tikzpicture}[net]
+        \formula[y=3]{A}
+        \formula[y=1.8]{\exists x.B}
+        \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\pi,\sigma\vphantom)}$}},r]{1,4}
+        \formula[y=1.2]{\forall x.{\dual B}}
+        \formula[y=0]{C}
+        \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\phi,\tau\vphantom)}$}},r]{4,1}
+    \end{tikzpicture}}
+    & 
+    \begin{array}{c}\scoal\\[40pt]\stackrel{x\,\notin\,\tau\vphantom)}\scoal\end{array}
+    &
+    \vc{
+    \begin{tikzpicture}[net]
+        \formula[y=3]{A}
+        \formula[y=1.8]{\exists x.B}
+        \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\pi',\sigma\minus x\vphantom)}$}},r]{1,1}
+        \formula[y=1.2]{\forall x.{\dual B}}
+        \formula[y=0]{C}
+        \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\phi',\tau\vphantom)}$}},r]{1,1}
+    \end{tikzpicture}}
+\\\\ \Downarrow && \Downarrow \\\\
+    \vc{ 
+    \begin{tikzpicture}[net]
+        \formula[y=1.2]{A}
+        \formula[y=0]{C}
+        \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\psi,\rho\vphantom)}$}},r]{1,1}
+    \end{tikzpicture}}
+    &&
+    \vc{
+    \begin{tikzpicture}[net]
+        \formula[y=1.2]{A}
+        \formula[y=0]{C}
+        \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\psi',\rho'\vphantom)}$}},r]{1,1}
+    \end{tikzpicture}}
+\end{array}
+%
+\qquad\quad
+%
+\begin{array}{l@{\,}l}
+	\rho  &=~ \sigma_A\tau_C\dcom\fix{\sigma_B\tau\subdual B}
+\\ \\
+	\rho' &=~ \sigma_A\tau_C\dcom\fix{(\sigma_B\minus x)\tau\subdual B}
+\\ \\
+	\psi  &=~
+	\vc{
+	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq{A\rho}{C\rho}}{
+	 \left(\vc{
+	  \deduce{\seq{A\sigma}{B\sigma}\vphantom{\dual B}}{\pi\vphantom)}
+	 }\right)\fix{\sigma_B\tau\subdual B}
+	 &
+	 \left(\vc{
+	  \deduce{\seq{\dual B\tau}{C\tau}}{\phi\vphantom)}
+	 }\right)\makebox[0pt][l]{$\fix{\sigma_B\tau\subdual B}$}
+	}}
+\\ \\ \\
+	\psi' &=~ 
+	\vc{\scalebox{0.8}{$
+	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq{A\rho'}{C\rho'}}{
+	 \left(\vc{\infer{\seq{A\sigma}{\exists x.B\sigma\minus x}\vphantom{\dual B}}{
+	  \deduce{\seq{A\sigma}{B\sigma}\vphantom{\dual B}}{\pi\vphantom)}
+	 }}\right)\fix{(\sigma_B\minus x)\tau\subdual B}
+	 &
+	 \left(\vc{\infer{\seq{\forall x.\dual B\tau}{C\tau}}{
+	  \deduce{\seq{\dual B\tau}{C\tau}}{\phi\vphantom)}
+	 }}\right)\makebox[0pt][l]{$\fix{(\sigma_B\minus x)\tau\subdual B}$}
+	}$}}
+	\rule{25pt}{0pt}
+\end{array}
+\]
+Since $x$ is not free in the range of $\tau$, and (by the freshness convention) nor in the range of $\sigma$, we have that $\fix{\sigma_B\tau\subdual B}$ is $\fix{(\sigma_B\minus x)\tau\subdual B}$ plus the substitution $[\sigma(x)/x]$.
+Then $\rho=\rho'$ (as $x$ does not occur in the range of $\sigma_A\tau_C$) and $\psi'$ reduces to $\psi$ in a single cut-elimination step.
+
+\[
+\begin{array}{ccc}
+    \vc{
+    \begin{tikzpicture}[net]
+        \formula[y=3]{A}
+        \formula[y=1.8]{B}
+        \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\pi,\sigma\vphantom)}$}},r]{1,1}
+        \formula[y=1.2]{{\dual B}}
+        \formula[y=0]{\exists x.C}
+        \Vlink[red,label={\makebox[0pt][r]{~$\scriptstyle{\phi,\tau\vphantom)}$~}},l]{1,4}
+    \end{tikzpicture}}
+    & 
+    \begin{array}{c}\\[45pt]\scoal\end{array}
+    &
+    \vc{
+    \begin{tikzpicture}[net]
+        \formula[y=3]{A}
+        \formula[y=1.8]{B}
+        \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\pi,\sigma\vphantom)}$}},r]{1,1}
+        \formula[y=1.2]{{\dual B}}
+        \formula[y=0]{\exists x.C}
+        \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\phi',\tau\minus x\vphantom)}$}},r]{1,1}
+    \end{tikzpicture}}
+\\\\ \Downarrow && \Downarrow \\\\
+    \vc{ 
+    \begin{tikzpicture}[net]
+        \formula[y=1.2]{A}
+        \formula[y=0]{\exists x.C}
+        \Vlink[red,label={\makebox[0pt][r]{~$\scriptstyle{\psi,\rho\vphantom)}$~}},l]{1,4}
+    \end{tikzpicture}}
+    &&
+    \vc{
+    \begin{tikzpicture}[net]
+        \formula[y=1.2]{A}
+        \formula[y=0]{\exists x.C}
+        \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\psi',\rho'\vphantom)}$}},r]{1,1}
+    \end{tikzpicture}}
+\end{array}
+%
+\qquad\quad
+%
+\begin{array}{l@{\,}l}
+	\rho  &=~ \sigma_A\tau_C\dcom\fix{\sigma_B\tau\subdual B}
+\\ \\
+	\rho' &=~ \sigma_A(\tau_C\minus x)\dcom\fix{\sigma_B\tau\subdual B}
+\\ \\
+	\psi &=~
+	\vc{
+	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq{A\rho}{C\rho}}{
+	 \left(\vc{
+	  \Prf\pi{A\sigma}{B\sigma}
+	 }\right)\fix{\sigma_B\tau\subdual B}
+	 &
+	 \left(\vc{
+	  \Prf\phi{\dual B\tau}{C\tau}
+	 }\right)\fix{\sigma_B\tau\subdual B}
+	}}
+\\ \\
+	\psi' &=~
+	\vc{
+	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq{A\rho'}{C\rho'}}{
+	 \left(\vc{
+	  \Prf\pi{A\sigma}{B\sigma}
+	 }\right)\fix{\sigma_B\tau\subdual B}
+	 &
+	 \left(\vc{
+	  \infer{\Seq{\dual B\tau}{\exists x.C(\tau\minus x)}}{\Prf\phi{\dual B\tau}{C\tau}}
+	 }\right)\fix{\sigma_B\tau\subdual B}
+	}}
+\end{array}
+\]
+Observe that since $x$ occurs in $C$ but not $B$, it is not in the domain of $\tau_B$, so that $\tau_B\minus x$ is just $\tau_B$.
+Then $\rho'=\rho\minus x$, and the diagram is closed by a sequentialization step (from left to right) that extends $\psi$ with an existential introduction rule, to a proof equivalent to $\psi'$:
+\[
+	\infer[\!\!\scriptstyle{\qrr?{\rho(x)}}]{\Seq{A\rho'}{\exists x.C\rho'}}{
+	 \Prf\psi{A\rho}{C\rho}
+	}
+\]
+
+There are three further critical pairs
+
+%\end{document}
+
+\begin{proposition}
+If $\net{\lambda_\Sigma}AB$ and $\net{\kappa_\Theta}{\dual B}C$ both coalesce, so does their composition.
+\end{proposition}
+
+\begin{proof}
+By induction on both coalescence sequences.
+In the base case, $\lambda_\Sigma=\{\link[\varnothing]AB\}$ and $\kappa_\Theta=\{\link[\varnothing]{\dual B}C\}$, and the composition is $\net{\{\link[\varnothing]AC\}}AC$.
+
+If
+\end{proof}
+
+\begin{proposition}
+If $\net{\lambda_\Sigma}AB$ sequentializes to $\pi$ and $\net{\kappa_\Theta}{\dual B}C$ to $\phi$ then the composition $(\net{\lambda_\Sigma}AB)\comp(\net{\kappa_\Theta}{\dual B}C)$ sequentializes to a normal form $\psi$ of the proof
+\[
+	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq AC}{
+	 %\prf\pi AB & \prf\phi{\dual B}C
+	 \deduce{\seq AB\vphantom{\dual B}}{\pi}
+	&\deduce{\seq{\dual B}C}{\phi}
+	}
+\]
+\end{proposition}
+
+%\end{document}
+
 \section{Unification nets}

### 2018-01-05 ALL1.tex
proof identity discussion

@@
 
+\section{Introduction}
+
 \subsection{Proof identity}
 
-\[
-	\infer={\exists x.p(x),\exists y.\dual p(y)}{\infer{p(t),\dual p(t)}{}}
+At the heart of a theory of proof nets is the question of proof identity, of when two proofs should be considered equivalent, and should thus map onto the same proof net. 
+%
+%It can be approached semantically, by asking whether two proofs are identified in every model; 
+%
+The introduction of quantifiers creates an interesting issue: if two proofs differ by an immaterial choice of existential witness, should they be equivalent?
+For example, to prove the sequent $\seq{\exists x.P(x)}{\exists y.\dual P(y)}$ both quantifiers must receive \emph{the same} witness, as in the following two proofs, but any witness will do.
+\[
+	\vc{\infer={\seq{\exists x.P(x)}{\exists y.\dual P(y)}}{\infer{\seq{P(s)}{\dual P(s)}}{}}}
 	\quad
@@
 	\quad
-	\infer={\exists x.P(x),\exists y.\dual p(y)}{\infer{p(s),\dual p(s)}{}}
-\]
-
-\[
-	\infer{\exists x.p,\dual p}{\infer{p[t/x],\dual p}{}}
+	\vc{\infer={\seq{\exists x.P(x)}{\exists y.\dual P(y)}}{\infer{\seq{P(t)}{\dual P(t)}}{}}}
+\]
+The issue is more pronounced where quantifiers are \emph{vacuous}, $\exists x.A$ where $x$ is not free in $A$.
+The proofs below left can only be distinguished even syntactically because the $\exists R$-rule makes the instantiating witness explicit.
+%
+Below right is an interesting intermediate variant: the witness $s$ or $t$ can be observed without explicit annotation in the $\exists R$-rule, but the choice is equally immaterial to the content of the proof as when the quantifier were vacuous.
+\[
+	\vc{\infer[\!\!\scriptstyle{\qrr?s}]{\seq{\exists x.P}{\dual P}}{\infer{\seq P{\dual P}}{}}}
 	\quad
@@
 	\quad	
-	\infer{\exists x.p,\dual p}{\infer{p[s/x],\dual p}{}}
-\]
-
-\[
-	\infer{\exists x.p\+q(x),\dual p}{\infer{p\+q(t)}{\infer{p,\dual p}{}}}
+	\vc{\infer[\!\!\scriptstyle{\qrr?t}]{\seq{\exists x.P}{\dual P}}{\infer{\seq P{\dual P}}{}}}\qquad
+	\vc{
+	 \infer[\!\!\scriptstyle{\qrr?s}]{\seq{\exists x.P\+Q(x)}{\dual P}}{
+	  \infer[\!\!\scriptstyle{\qrr+1}]{\seq{P\+Q(s)}{\dual P}}{\infer{\seq P{\dual P}}{}}
+	}}
 	\quad
@@
 	\quad	
-	\infer{\exists x.p\+q(x),\dual p}{\infer{p\+q(s)}{\infer{p,\dual p}{}}}
-\]
-
-\[
-\begin{tikzpicture}[net]
-\formula[y=1]{\exists x.\forall a.~p(a,x)}
-\formula[y=0]{\exists y.~{\dual p}(y,s)\*{\dual p}(y,t)}
+	\vc{
+	 \infer[\!\!\scriptstyle{\qrr?t}]{\seq{\exists x.P\+Q(x)}{\dual P}}{
+	  \infer[\!\!\scriptstyle{\qrr+1}]{\seq{P\+Q(t)}{\dual P}}{\infer{\seq P{\dual P}}{}}
+	}}
+\]
+In this paper we will not attempt to decisively settle the question of proof identity.
+Rather, we will present two natural and coherent notions of proof net, that represent two extremes.
+One, \defn{witness nets}, takes the choice of existential witnesses to be essential proof content, and rejects all three equivalences above.
+The other, \defn{unification nets}, removes any redundancy by rejecting explicit witnessing information altogether; instead, a most general witness for every quantifier is reconstructed by unification.
+
+\[
+\begin{tikzpicture}[net]
+\formula[y=1.2]{\exists x.\forall y.~{\dual P}(x,y)}
+\formula[y=0]{\exists z.~P(s,z)\*P(t,z)}
 \Vlink[red,label={$\scriptstyle\sigma~$},l]{[-2]8,5}
@@
 \begin{tikzpicture}[net]
-\formula[y=1]{\exists x.\forall a.~p(a,x)}
-\formula[y=0]{\exists y.~{\dual p}(y,s)\*{\dual p}(y,t)}
+\formula[y=1]{\exists x.\forall y.~{\dual P}(x,y)}
+\formula[y=0]{\exists z.~P(s,z)\*P(t,z)}
 \Vlink[red,label={$~\scriptstyle\upsilon$}]{8,11}
@@
 \begin{tikzpicture}[net]
-\formula[y=1]{\exists x.\forall a.~p(a,x)}
-\formula[y=0]{\exists y.~{\dual p}(y,s)\*{\dual p}(y,t)}
+\formula[y=1]{\exists x.\forall y.~{\dual P}(x,y)}
+\formula[y=0]{\exists z.~P(s,z)\*P(t,z)}
 \Vlink[red,label={$\quad\scriptstyle{\upsilon\minus y}$}]{8,1}
@@
 \begin{tikzpicture}[net]
-\formula[y=1]{\exists x.\forall a.~p(a,x)}
-\formula[y=0]{\exists y.~{\dual p}(y,s)\*{\dual p}(y,t)}
+\formula[y=1]{\exists x.\forall y.~{\dual P}(x,y)}
+\formula[y=0]{\exists z.~P(s,z)\*P(t,z)}
 \Vlink[red,label={$~\scriptstyle{\upsilon\minus y}$}]{4,1}
@@
 \begin{tikzpicture}[net]
-\formula[y=1]{\exists x.\forall a.~p(a,x)}
-\formula[y=0]{\exists y.~{\dual p}(y,s)\*{\dual p}(y,t)}
+\formula[y=1]{\exists x.\forall y.~{\dual P}(x,y)}
+\formula[y=0]{\exists z.~P(s,z)\*P(t,z)}
 \Vlink[red,label={$~\scriptstyle{\rho}$}]{1,1}

### 2018-01-05 ALL1.tex
initial bibliography; reworking from start

@@
 
+\newcommand\var{\textsc{var}}
 \newcommand\varA{\textsc{var}^\forall}
@@
 
-\newcommand\ex[2]{\textsc{ex}_{#1}(#2)}
+\newcommand\ex[2][{}]{\textsc{ev}_{#1}(#2)}
 
@@
 \newcommand\dep{\preccurlyeq}
-%\newcommand\dep{\stackrel\star{\smash\preccurlyeq\rule{0pt}{1ex}}}
 
@@
 \newcommand\Deseq[4][\sigma]{\left[\vcenter{#2}\right]_{#1}^{#3\,,\,#4}}
-
-%\newcommandx\deseq[4][2=\sigma]{\floor{#1}_{#2}^{#3,#4}}
-%\newcommandx\Deseq[4][2=\sigma]{\left\lfloor\vcenter{#1}\right\rfloor_{#2}^{#3,#4}}
 
@@
 \newcommand\ucoal{\rightsquigarrow}
+
+\newcommand\Qrr{\!\!\scriptstyle\qrr}
 
@@
 \newcommand\@@qrr[1]{\exists\mathrm R,#1}
+
 \newcommand\srr[1]{
@@
 \newcommand\@srr[1]{+_{#1}\mathrm S}
+
 \newcommand\urr[1]{
@@
 
+% ==================================================
+
 \section{Introduction}
+
+Correctness and sequentialization for \all1 proof nets will be through \defn{coalescence}.
+This is a simple graph rewriting relation that gives top-down sequentialization, from the axioms to the conclusion of a proof.
+It is the additive counterpart to Danos \defn{contractibility} for multiplicative linear logic.
+
+We will define two coalescence relations, one \defn{strict} $(\scoal)$, for witness nets, and one \defn{unifying} $(\ucoal)$, for unification nets, in a later section.
+In the former, to join two slices the witness assignment must be the same; in the latter, witness assignments must be compatible, so that a common, more general witness map exists.
+
+% --------------------------------------------------
 
@@
 
-\[
-\begin{tikzpicture}[net]
-\formula[y=1.2]{\exists x.\forall y.~{\dual P}(x,y)}
-\formula[y=0]{\exists z.~P(s,z)\*P(t,z)}
-\Vlink[red,label={$\scriptstyle\sigma~$},l]{[-2]8,5}
-\Vlink[red,label={$~\scriptstyle\tau$}]{[2]8,12}
-\end{tikzpicture}
-\]
-
-\[
-\begin{tikzpicture}[net]
-\formula[y=1]{\exists x.\forall y.~{\dual P}(x,y)}
-\formula[y=0]{\exists z.~P(s,z)\*P(t,z)}
-\Vlink[red,label={$~\scriptstyle\upsilon$}]{8,11}
-\end{tikzpicture}
-\]
-
-\[
-\begin{tikzpicture}[net]
-\formula[y=1]{\exists x.\forall y.~{\dual P}(x,y)}
-\formula[y=0]{\exists z.~P(s,z)\*P(t,z)}
-\Vlink[red,label={$\quad\scriptstyle{\upsilon\minus y}$}]{8,1}
-\end{tikzpicture}
-\]
-
-\[
-\begin{tikzpicture}[net]
-\formula[y=1]{\exists x.\forall y.~{\dual P}(x,y)}
-\formula[y=0]{\exists z.~P(s,z)\*P(t,z)}
-\Vlink[red,label={$~\scriptstyle{\upsilon\minus y}$}]{4,1}
-\end{tikzpicture}
-\]
-
-\[
-\begin{tikzpicture}[net]
-\formula[y=1]{\exists x.\forall y.~{\dual P}(x,y)}
-\formula[y=0]{\exists z.~P(s,z)\*P(t,z)}
-\Vlink[red,label={$~\scriptstyle{\rho}$}]{1,1}
-\end{tikzpicture}
-\]
-
-\[
-	\sigma = [a/y, s/x]
-	\qquad
-	\tau = [a/y, t/x]
-\]
-\[
-	\upsilon = \rho[a/y, u/x]
-	\qquad
-	\rho = \mgu(s,t)
-	\qquad
-	 u=s\rho=t\rho
-\]
+%$\seq{\,\exists x.P(x,x,s)\,}{\,\exists y.\dual P(t,y,y)}$
+
+% --------------------------------------------------
+
+\subsection{Background and related work}
+
+\cite{Whitman-1941}
+\cite{Girard-1987}
+\cite{Galmiche-Marion-1995} % ALL proof search
+\cite{Girard-1996}
+\cite{Hu-99}
+\cite{Galmiche-2000} % ALL connection net (Def 6.11.)
+\cite{Hughes-VanGlabbeek-2005}
+\cite{Cockett-Santocanale-2009}
+\cite{Heijltjes-2011, Heijltjes-2012}
+\cite{Heijltjes-Hughes-2015}
+
+\cite{Danos-1990}
+\cite{Guerrini-Masini-2001}
+\cite{Guerrini-2011}
+
+\cite{Herbrand-1930}
+\cite{Heijltjes-2010}
 
@@
 
-%\begin{figure}
-%\[
-%	\infer{\seq P{\dual P}}{}
-%\qquad
-%	\infer{\seq A{B_0\+B_1}}{\seq A{B_i}}
-%\qquad
-%	\infer{\seq A{B\*C}}{\seq AB && \seq AC}
-%\qquad
-%	\infer{\seq A{\exists x.B}}{\seq A{B[t/x]}}
-%\qquad
-%	\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]{\seq A{\forall a.B}}{\seq AB}
-%\]
-%\caption{A sequent calculus for $\all1$}
-%\label{fig:sequent calculus}
-%\end{figure}
-
 \begin{figure}
 \[
-	\infer[\!\!\scriptstyle{\qrr1}]{\seq P{\dual P}}{}
-\quad
-	\infer[\!\!\scriptstyle{\qrr+i}]{\seq A{B_0\+B_1}}{\seq A{B_i}}
-\quad
-	\infer[\!\!\scriptstyle{\qrr*}]{\seq A{B\*C}}{\seq AB & \seq AC}
-\quad
-	\infer[\!\!\scriptstyle{\qrr?t}]{\seq A{\exists x.B}}{\seq A{B[t/x]}}
-\quad
-	\infer[\!\!\scriptstyle{\qrr!~(a\,\notin\,\textsc{fv}(A))}]{\seq A{\forall a.B}}{\seq AB}
+	\infer[\Qrr1]{\seq P{\dual P}}{}
+\quad
+	\infer[\Qrr+i]{\seq A{B_1\+B_2}}{\seq A{B_i}}
+\quad
+	\infer[\Qrr*]{\seq A{B\*C}}{\seq AB & \seq AC}
+\quad
+	\infer[\Qrr?t]{\seq A{\exists x.B}}{\seq A{B[t/x]}}
+\quad
+	\infer[\Qrr!~(x\,\notin\,\textsc{fv}(A))]{\seq A{\forall x.B}}{\seq AB}
 \]
@@
 \end{figure}
-%
-%\begin{figure}
-%\[
-%\raisebox{.5ex}{$\qrr1$}\quad
-%	\infer{\seq P{\dual P}}{}
-%\quad\raisebox{.5ex}{$\qrr+i$}\quad
-%	\infer{\seq A{B_0\+B_1}}{\seq A{B_i}}
-%\quad\raisebox{.5ex}{$\qrr*$}\quad
-%	\infer{\seq A{B\*C}}{\seq AB && \seq AC}
-%\quad\raisebox{.5ex}{$\qrr?$}\quad
-%	\infer{\seq A{\exists x.B}}{\seq A{B[t/x]}}
-%\quad\raisebox{.5ex}{$\qrr!$}\quad
-%	\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]{\seq A{\forall a.B}}{\seq AB}
-%\]
-%\caption{A sequent calculus for $\all1$}
-%\label{fig:sequent calculus}
-%\end{figure}
 
@@
 \begin{array}{@{}l@{}l}
-	t &\Coloneqq a \Mid x \Mid f(t_1,\dots,t_n)
+	t &\Coloneqq x \Mid f(t_1,\dots,t_n)
 \\[10pt]
-	P &\Coloneqq p(t_1,\dots,t_n) \Mid \dual p(t_1,\dots,t_n)
+	a &\Coloneqq P(t_1,\dots,t_n) \Mid \dual P(t_1,\dots,t_n)
 \\[10pt]
-	A &\Coloneqq P \Mid A\+A \Mid A\*A \Mid \exists x.A \Mid \forall a.A
+	A &\Coloneqq a \Mid A\+A \Mid A\*A \Mid \exists x.A \Mid \forall x.A
 \end{array}
@@
 %
-Negation $(\dual{\,\cdot\,})$ is applied to predicate symbols, $\dual p$, as a matter of convenience.
+Negation $(\dual{\,\cdot\,})$ is applied to predicate symbols, $\dual P$, as a matter of convenience.
 The \defn{dual} $\dual A$ of an arbitrary formula $A$ is given by DeMorgan.
@@
 \begin{tabular}{@{}lll@{}} 
-	$a,b,c$ & $\in \varA$ 		& universally quantified variables (and free variables)\\
-	$x,y,z$ & $\in \varE$		& existentially quantified variables (and term-language variables)\\
+	$x,y,z$ & $\in \var$		& first-order variables\\
 	$f,g,h$ & $\in \Sigma_f$	& $n$-ary $(n\geq 0)$ function symbols from a fixed alphabet $\Sigma_f$\\
-	$p,q,r$ & $\in \Sigma_p$	& $n$-ary $(n\geq 0)$ predicate symbols from a fixed alphabet $\Sigma_p$ \\
-	$s,t,u$ & $\in \terms$ 		& first-order terms over $\varA$, $\varE$, $\Sigma_f$, and $\Sigma_p$ \\
-	$P,Q,R$ & $\in \atom$		& atomic propositions \\
+	$P,Q,R$ & $\in \Sigma_p$	& $n$-ary $(n\geq 0)$ predicate symbols from a fixed alphabet $\Sigma_p$ \\
+	$s,t,u$ & $\in \terms$ 		& first-order terms over $\var$ and $\Sigma_f$ \\
+	$a,b,c$ & $\in \atom$		& atomic propositions \\
 	$A,B,C$ & $\in \form$		& \all1 formulas \\
@@
 		\subs B\uplus\subs C	& \text{if $A=B\+C$ or $A=B\*C$} \\[5pt]
-		\subs B					& \text{if $A=\exists x.B$ or $A=\forall a.B$}
+		\subs B					& \text{if $A=\exists x.B$ or $A=\forall x.B$}
 	\end{array}\right.
@@
 
-A \defn{witness map} $\sigma\colon \varE \rightharpoonup \terms$ is a substitution map which assigns terms to existential variables, given as a (finite) partial function.
-Its \defn{domain} $\dom\sigma$ is the set of those variables for which it is defined.
-The \defn{empty} witness map $\varnothing$ is the everywhere undefined partial function, and the map $\sigma[t/x]$ substitutes $t$ for $x$ and is as $\sigma$ everywhere else.
-We express by $\sigma(x)=\bot$ that $\sigma$ is undefined for $x$.
-The map $\sigma\minus x$ is undefined on $x$ and otherwise as $\sigma$, and $\sigma\res V$ is the restriction of $\sigma$ to a set of variables $V$.
-We abbreviate by $a\in \sigma$ the statement that a variable $a$ occurs free in the range of $\sigma$, i.e.\ that $a\in\fv(\sigma(x))$ for some $x$.
-
-We will write $A\sigma$ for the application of the witness map $\sigma\colon\varE\rightharpoonup\terms$ to the formula $A$ as a substitution map.
-It is applied to a sequent proof, $\pi\sigma$, by applying it to each formula in the proof $\pi$.
+A \defn{witness map} $\sigma\colon\var\rightharpoonup\terms$ is a substitution map which assigns terms to variables, given as a (finite) partial function.
+We define it as $\sigma=[t_1/x_1,\dots,t_n/x_n]$, where its \defn{domain} $\dom\sigma$ is $\{x_1,\dots,x_n\}$.
+We abbreviate by $y\in\sigma$ that a variable $y$ occurs free in its the range, $y\in\fv(t_i)$ for some $i\leq n$.
+The map $\sigma\minus x$ is undefined on $x$ and otherwise as $\sigma$, we write $\sigma\res V$ for the restriction of $\sigma$ to a set of variables $V$, and $\varnothing$ is the \defn{empty} witness map.
+%
+We write $A\sigma$ for the application of the substitutions in $\sigma$ to the formula $A$, and $\pi\sigma$ for its application to the proof $\pi$, where it is applied to each formula in the proof.
 The \defn{composition} of two maps is written $\sigma\tau$, where $A(\sigma\tau)=(A\sigma)\tau$.
 
-A \defn{witness linking} $\lambda_\Sigma$ is a linking $\lambda$ with a \defn{witness labelling} $\Sigma\colon\lambda\to \varE\rightharpoonup\terms$ that assigns each link $(C,D)$ a witness map.
+%\[
+%\begin{tabular}{@{}ll@{}} 
+%	$\varnothing$ & is the empty witness map \\
+%	$\sigma\minus x$ & is the witness map that is undefined on $x$ and otherwise as $\sigma$ \\
+%	$\sigma\res V$ & is the restriction of $\sigma$ to a set of variables $V$\\
+%	$y\in\sigma$ & abbreviates $y\in\fv(\sigma(x))$ for some $x$ ($y$ occurs in the range of $\sigma$) \\
+%	$A\sigma$ & is the application of $\sigma$ as a substitution map to a formula $A$ \\
+%	$\pi\sigma$ & is the application of $\sigma$ to a proof $\pi$ (applied to all its formulas) \\
+%\end{tabular}
+%\]
+
+A \defn{witness linking} $\lambda_\Sigma$ is a linking $\lambda$ with a \defn{witness labelling} $\Sigma\colon\lambda\to\var\rightharpoonup\terms$ that assigns each link $(C,D)$ a witness map.
 We may use and define $\lambda_\Sigma$ as a set of \defn{witness links} $\link CD$, where $(C,D)\in\lambda$ and $\Sigma(C,D)=\sigma$.
-When a link is not a witness link, this may be emphasized by calling it \defn{clean}.
+% When a link is not a witness link, this may be emphasized by calling it \defn{clean}.
 
@@
 A \defn{witness pre-net} $\net{\lambda_\Sigma}AB$ is a sequent $\seq AB$ with a witness linking $\lambda_\Sigma$.
-%
-%\begin{description}
-%	\item[Exact coverage]
-%The domain of $\sigma$ is exactly the variables existentially quantified in $\seq AB$ that will be bound in $C$ and $D$, if they occur:
-%\[
-%	\dom\sigma = \{\,x \mid C < \exists x.X \leq A\,\}
-%			\cup \{\,y \mid D < \exists y.Y \leq B\,\}~.
-%\]
-%
-%	\item[Eigenvariables not free]
-%A universal variable $a\in\varA$ quantified in $C$ or $D$ may not occur free in the range of $\sigma$, $a\notin\sigma$.
-%
-%	\item[Freshness]
-%Existential variables in the range of $\sigma$ are fresh, i.e.\ distinct from any existentially quantified variable in $\seq AB$.
-%\end{description}
 \end{definition}
 
-We will assume the following variable naming conventions for \all1 pre-nets.
-
+We will assume the following variable naming conventions.
+%
 \begin{description}
 	\item
-[\defn{Barendregt's convention}] All quantifiers in a sequent $\seq AB$ have a distinct binding variable, and no bound variable shares a name with a free one.
-%	\item
-%% ALTERNATIVE: "STATIC WITNESSING"
-%[\defn{Universal witnessing}] All existential witnesses in a proof are \defn{universal terms} $\termsA\subset\terms$, generated by the following grammar.
-%\[
-%	\termsA: \qquad t \Coloneqq a \Mid f(t_1,\dots,t_n)
-%\]
+[Barendregt's convention] All quantifiers in a sequent $\seq AB$ have a distinct binding variable, and no bound variable shares a name with a free one.
 
 	\item[Eigenvariables not free]
-For a link $\link CD$, a universal variable $a\in\varA$ quantified in $C$ or $D$ may not occur free in the range of $\sigma$, $a\notin\sigma$.
+For a link $\link CD$, a universally quantified variable in $C$ or $D$ does not occur free in the range of $\sigma$.
 
 	\item[Freshness]
-For a link $\link CD$, existential variables in the range of $\sigma$ are fresh, i.e.\ distinct from any existentially quantified variable in $\seq AB$.
+For a link $\link CD$ in $\net{\lambda_\Sigma}AB$, variables in the range of $\sigma$ are fresh: distinct from any existentially quantified (as $\exists x$) variable in $\seq AB$.
 \end{description}
 
-%We assume the existential variables occurring in the range of $\Sigma$ to be fresh, i.e.\ distinct from any existentially quantified variable in $\seq AB$.
-
 \begin{definition}
-The \defn{de-sequentialization} $[\pi]$ of a sequent proof $\prf\pi AB$ is the witness pre-net $\net{\lambda_\Sigma}AB$ where $\lambda_\Sigma=\deseq[\varnothing]\pi AB$ and the function $\deseq-AB$ is defined as follows.
-%
-\newlength\deseqwidth
-\settowidth\deseqwidth{$\scriptstyle{A'\,,\,B'_0\+B'_1}$}
-\newcommand\XDeseq[4][\sigma]{\left[\vcenter{#2}\right]_{#1}^{\makebox[\deseqwidth][l]{$\scriptstyle{#3\,,\,#4}$}}}
+The \defn{de-sequentialization} $[\pi]$ of a sequent proof $\prf\pi AB$ is the witness pre-net $\net{\deseq[\varnothing]\pi AB}AB$ where the function $\deseq-AB$ is defined inductively as follows.
+%
+% $\net{\lambda_\Sigma}AB$ where $\lambda_\Sigma=\deseq[\varnothing]\pi AB$ and the function $\deseq-AB$ is defined as follows.
+%
+%\newlength\deseqwidth
+%\settowidth\deseqwidth{$\scriptstyle{A'\,,\,B'_0\+B'_1}$}
+%
+\newcommand\XDeseq[4][\sigma]{
+ \left[\vcenter{#2}\right]%
+ _{\makebox[0pt][l]{$\scriptstyle{#1}$}}%
+ ^{\makebox[0pt][l]{$\scriptstyle{#3\,,\,#4}$}}%
+ \rule{35pt}{0pt}
+}
+%
 \begin{align*}
-	\XDeseq{\infer{\seq P{\dual P}}{}}QR &\quad=\quad \{\link QR\}
-\\ \\
-	\XDeseq{\infer {\seq A {B_0\+B_1}} {\deduce [\rule{0pt}{1pt}] {\seq A{B_i}} \pi }}
-	  {A'}{B_0'\+B'_1} 
+	\XDeseq{\,\infer[\Qrr1]{\seq a{\dual a}}{}}bc &\quad=\quad \{\link bc\}
+\\ \\[-5pt]
+	\XDeseq{\infer[\Qrr+i]{\seq A {B_1\+B_2}}{\Prf \pi A{B_i}}} {A'} {B_1'\+B'_2} 
 	& \quad=\quad 
-	\Deseq{\deduce[\rule{0pt}{1pt}]{\seq A{B_i}}\pi}{A'}{B_i'}
-\\ \\
-	\XDeseq{\infer{\seq A{B\*C}}{
-	  \deduce[\rule{0pt}{1pt}]{\seq AB}{\pi\vphantom'} 
-	  && 
-	  \deduce[\rule{0pt}{1pt}]{\seq AC}{\pi'}}}{A'}{B'\*C'}
+	\Deseq{\Prf\pi A{B_i}} {A'} {B_i'}
+\\ \\[-5pt]
+	\XDeseq{\infer[\Qrr*]{\seq A{B\*C}}{
+	 \Prf\pi AB && \Prf{\pi'}AC 
+	}}{A'}{B'\*C'}
 	& \quad=\quad 
-	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AB}{\pi\vphantom'}}{A'}{B'}
+	  \Deseq{\Prf\pi AB}{A'}{B'}
 	  \cup
-	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AC}{\pi'}}{A'}{C'}
-\\ \\
-	\XDeseq{\infer{\seq A{\exists x.B}}{\deduce[\rule{0pt}{1pt}]{\seq A{B[t/x]}}\pi}}
-	  {A'}{\exists x.B'}
+	  \Deseq{\Prf{\pi'}AC}{A'}{C'}
+\\ \\[-5pt]
+	\XDeseq{\infer[\Qrr?t]{\seq A{\exists x.B}}{\Prf\pi A{B[t/x]}}}{A'}{\exists x.B'}
 	& \quad=\quad 
-	 \Deseq[{\sigma[t/x]}]{\deduce[\rule{0pt}{1pt}]{\seq A{B[t/x]}}\pi}
-	  {A'}{B'}
-\\ \\
-	\XDeseq{\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]
-	  {\seq A{\forall a.B}}{\deduce[\rule{0pt}{1pt}]{\seq AB}\pi}}{A'}{\forall a.B'}
+	 \Deseq[{\sigma[t/x]}]{\Prf\pi A{B[t/x]}} {A'} {B'}
+\\ \\[-5pt]
+	\XDeseq{\infer[\Qrr!]
+	  {\seq A{\forall x.B}}{\Prf\pi AB}} {A'} {\forall x.B'}
 	& \quad=\quad 
-	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AB}\pi}{A'}{B'}
+	  \Deseq{\Prf\pi AB}{A'}{B'}
 \end{align*}
@@
 
-A function call $\deseq{\prf\pi AB}{A'}{B'}$ expects that $A=A'\sigma$ and $B=B'\sigma$.
-While a sequent proof instantiates existential witnesses immedately into the premise of the existential quantifier rule, for proof nets we delay the substitutions $\sigma$.
+A function call $\deseq{\prf\pi AB}{A'}{B'}$ expects that $A=A'\sigma$ and $B=B'\sigma$: the translation separates a sequent $\seq AB$ into subformulas $A'$, $B'$ of the ultimate conclusion of the proof, and the accumulated existential witnesses $\sigma$.
+%While a sequent proof instantiates existential witnesses immedately into the premise of the existential quantifier rule, for proof nets we delay the substitutions $\sigma$.
 Hence we need to maintain the separation of the conclusion $\seq AB$ into the substitutions $\sigma$ and the subformulas $A'$ and $B'$ of the conclusion of the proof net.
@@
 We will conclude this section by discussing two further essential notions.
-First, a witness link $\link PQ$ on two atomic formulas $P$ and $Q$ is an \defn{axiom} link if $P\sigma=\dual Q\sigma$; a witness \defn{axiom} linking is one where every link is an axiom link.
+First, a witness link $\link ab$ on two atomic formulas $a$ and $b$ is an \defn{axiom} link if $a\sigma=\dual b\sigma$.
+A witness \defn{axiom} linking is one where every link is an axiom link.
 Observe that the de-sequentialization $[\pi]$ is a witness pre-net with axiom linking $\deseq[\varnothing]\pi AB$.
 
-Second, given a link $\link CD$ in a pre-net $\net\lambda AB$, we expect the domain of $\sigma$ to be exactly those variables that existentially quantified in $A$ and $B$ dominating $C$ and $D$.
-That is, any variable $x$ such that there is a subformula $\exists x.X$ in $A$ that in turn has $C$ as a subformula, and likewise for $B$ and $D$.
-We will now make this precise.
-For a subformula $C$ of a formula $A$, let the \defn{existential cover} $\ex AC$ of $C$ in $A$ be the following set:
-\[
-	\ex AC = \{\,x \mid C < \exists x.X \sub A\,\}~.
+Second, given a link $\link CD$ in a pre-net $\net\lambda AB$, we expect the domain of $\sigma$ to be exactly the existentially quantified variables in $A$ and $B$ in whose scope $C$ and $D$ occur. 
+%That is, any variable $x$ such that there is a subformula $\exists x.X$ in $A$ that in turn has $C$ as a subformula, and likewise for $B$ and $D$. We will now make this precise. 
+For a subformula $C$ of $A$, let the \defn{existential variables} $\ex[A]C$ of $C$ in $A$ be the set
+\[
+	\ex[A]C = \{\,x \mid C < \exists x.X \sub A\,\}~.
 \]
@@
 \begin{definition}
-A witness pre-net $\net{\lambda_\Sigma}AB$ has \defn{exact coverage} if for every link $\link CD$ in $\lambda_\Sigma$ the domain of $\sigma$ is exactly the existential covers of $C$ and $D$:
-\[
-	\dom\sigma = \ex AC\cup\ex BD~.
+A witness pre-net $\net{\lambda_\Sigma}AB$ has \defn{exact coverage} if for every link $\link CD$ in $\lambda_\Sigma$ the domain of $\sigma$ is exactly the existential variables of $C$ and $D$:
+\[
+	\dom\sigma = \ex[A]C\cup\ex[B]D~.
 \]
 \end{definition}
-
-A de-sequentialization $[\pi]$ has exact coverage.
-Note that the property is carefully formulated, using the \emph{exisential cover} rather than simply the free existential variables in a formula, to account for vacuous quantifiers ($\exists x.C$ where $x$ is not free in $C$).
+%
+The witness map $\sigma$ of a link $\link CD$ then has two natural components, $\sigma\res{\ex[A]C}$ and $\sigma\res{\ex[B]D}$, which we will abbreviate by $\sigma_C$ and $\sigma_D$ respectively.
+
+Finally, note that a de-sequentialization $[\pi]$ has exact coverage.
+
+%Note that the property is carefully formulated, using the \emph{exisential cover} rather than simply the free existential variables in a formula, to account for vacuous quantifiers.
+% ($\exists x.C$ where $x$ is not free in $C$).
 The issue becomes even more pertinent for a link $\link CD$ where $C$ occurs in $\exists x.C{\+}C'$ and $x$ is free in $C'$ but not $C$, where we still would like an explicit witness for $x$ in $\sigma$.
@@
 \subsection{Correctness and sequentialization}
-
-Correctness and sequentialization for \all1 proof nets will be through \defn{coalescence}.
-This is a simple graph rewriting relation that gives top-down sequentialization, from the axioms to the conclusion of a proof.
-It is the additive counterpart to Danos \defn{contractibility} for multiplicative linear logic.
-
-We will define two coalescence relations, one \defn{strict} $(\scoal)$, for witness nets, and one \defn{unifying} $(\ucoal)$, for unification nets, in a later section.
-In the former, to join two slices the witness assignment must be the same; in the latter, witness assignments must be compatible, so that a common, more general witness map exists.
 
@@
 An axiom link will carry an axiom, and each coalescence step introduces one proof rule.
-Formalizing this, a \defn{proof linking} $\lambda_\Sigma^\Pi$ is a witness linking $\lambda_\Sigma$ with a \defn{proof labelling} $\Pi\colon \lambda\to\proofs$ assigning each link a sequent proof.
+Formalizing this, a \defn{proof linking} $\lambda_\Sigma^\Pi$ is a witness linking $\lambda_\Sigma$ with a \defn{proof labelling} $\Pi\colon \lambda\to\proofs$ assigning a sequent proof to each link.
 We will use and define $\lambda_\Sigma^\Pi$ as a set of \defn{proof links} $\link CD^\pi$, where we require that $\prf\pi{C\sigma}{D\sigma}$, i.e.\ that $\pi$ proves the conclusion $\seq{C\sigma}{D\sigma}$.
@@
 \[
-	\lambda_\Sigma^\star = \{~\link PQ^\pi~\mid~\link PQ\in\lambda_\Sigma~,~\pi=~\infer{\seq{P\sigma}{Q\sigma}}{}~\}
+	\lambda_\Sigma^\star = \{~\link ab^\pi~\mid~\link ab\in\lambda_\Sigma~,~\pi=~\infer{\seq{a\sigma}{b\sigma}}{}~\}
 \]
 For correctness we may coalesce a pre-net directly, without constructing a proof. 
-
-To recap, we have accumulated the following further notational conventions.
+%
+Then to recap, we have accumulated the following further notational conventions.
 %
@@
 \begin{tabular}{@{}lcll@{}}
+	$\pi,\phi,\psi$		& $\in$ & $\proofs$ & \all1 sequent proofs\\
 	$\kappa,\lambda$ 	& $\subset$ & $\form\times\form$ 	& linkings (sets of pairs of formulas)\\
@@
 	$\Sigma,\Theta$		& $\colon$  & $(\form\times\form)\rightharpoonup\varE\rightharpoonup\terms$		& witness labellings on a linking \\
-	$\pi,\phi,\psi$		& $\in$ & $\proofs$ & \all1 sequent proofs\\
 	$\Pi,\Phi,\Psi$		& $\colon$  & $(\form\times\form)\rightharpoonup\proofs$		& proof labellings on a linking
@@
 \begin{definition}
- \defn{Strict sequentialization} ($\scoal$) is the rewrite relation on witness pre-nets generated by the following rules, which apply symmetrically to the first formula in the sequent.
-\defn{Strict coalescence} is the same relation ignoring proof labels, on witness pre-nets.
+ \defn{Strict sequentialization} ($\scoal$) is the rewrite relation on labelled pre-nets generated by the following rules.
+\defn{Strict coalescence} is the same relation ignoring proof labels, on witness pre-nets, illustrated in Figure~\ref{fig:coalescence}.
 %
@@
 \begin{equation}
-  	\net{\{\link A{B_i}^\pi\}}A{B_0\+B_1} 
+  	\net{\{\link A{B_i}^\pi\}}A{B_1\+B_2} 
  ~\scoal~
-	\net{\{\link A{B_0\+B_1} ^\psi\}}A{B_0\+B_1}
+	\net{\{\link A{B_1\+B_2} ^\psi\}}A{B_1\+B_2}
 \tag{$\srr+i$}
@@
 \hfill $\text{where}\quad \psi=~
-  \vc{
-   \infer  {\seq{A\sigma}{B_0\sigma\,\+\,B_1\sigma}}  {
-  	\deduce  [\rule{0pt}{1pt}]  {\seq{A\sigma}{B_i\sigma}}  \pi
-  }}
+  \vc{\infer  {\seq{A\sigma}{B_1\sigma\,\+\,B_2\sigma}}  {\Prf \pi {A\sigma} {B_i\sigma}}}
 $ \hspace*{20pt}
@@
    \infer  {\seq{A\sigma}{B\sigma\,\*\,C\sigma}}  {
-    \deduce  [\rule{0pt}{1pt}]  {\seq{A\sigma}{B\sigma}}  \pi
-    &
-    \deduce  [\rule{0pt}{1pt}]  {\seq{A\sigma}{C\sigma}}  \phi    
+    \Prf \pi {A\sigma} {B\sigma}
+    &
+    \Prf \phi {A\sigma} {C\sigma}    
   }}$ \hspace*{20pt}
@@
    \infer  {\seq{A\tau}{\exists x.B\tau}}  {
-    \deduce  [\rule{0pt}{1pt}]  {\seq{A\sigma}{B\sigma}}  \pi  
+    \Prf \pi {A\sigma} {B\sigma}
   }}
@@
    \infer  {\seq{A\sigma}{\forall a.B\sigma}}  {
-    \deduce  [\rule{0pt}{1pt}]  {\seq{A\sigma}{B\sigma}}  \pi  
+    \Prf \pi {A\sigma} {B\sigma}
   }}
@@
 \end{proof}
+
+\end{document}
 
@@
 
-For a witness map $\sigma$ and a formula $B$ that is understood as a subformula of a formula $A$, we abbreviate $\sigma\res{\ex AB}$ to $\sigma_B$.
-A witness map of a link $\link CD$ then has two components, $\sigma_C$ and $\sigma_D$.
-
 The \defn{domain-preserving composition} of two witness maps $\sigma\dcom\tau$ is the map $(\sigma\tau)\res{\dom\sigma}$.
@@
 
+\[
+\begin{tikzpicture}[net]
+\formula[y=1.2]{\exists x.\forall y.~{\dual P}(x,y)}
+\formula[y=0]{\exists z.~P(s,z)\*P(t,z)}
+\Vlink[red,label={$\scriptstyle{[y/z,s/x]}~~$},l]{[-2]8,5}
+\Vlink[red,label={$~\scriptstyle{[y/z,t/x]}$}]{[2]8,12}
+\end{tikzpicture}
+\]
+
+\[
+\begin{tikzpicture}[net]
+\formula[y=1]{\exists x.\forall y.~{\dual P}(x,y)}
+\formula[y=0]{\exists z.~P(s,z)\*P(t,z)}
+\Vlink[red,label={$~\scriptstyle{[y/z,s/x]\mgu(s,t)}$}]{8,11}
+\end{tikzpicture}
+\]
+
+\[
+\begin{tikzpicture}[net]
+\formula[y=1]{\exists x.\forall y.~{\dual P}(x,y)}
+\formula[y=0]{\exists z.~P(s,z)\*P(t,z)}
+\Vlink[red,label={$\quad\scriptstyle{[s/x]\mgu(s,t)}$}]{8,1}
+\end{tikzpicture}
+\]
+
+\[
+\begin{tikzpicture}[net]
+\formula[y=1]{\exists x.\forall y.~{\dual P}(x,y)}
+\formula[y=0]{\exists z.~P(s,z)\*P(t,z)}
+\Vlink[red,label={$~~\scriptstyle{[s/x]\mgu(s,t)}$}]{4,1}
+\end{tikzpicture}
+\]
+
+\[
+\begin{tikzpicture}[net]
+\formula[y=1]{\exists x.\forall y.~{\dual P}(x,y)}
+\formula[y=0]{\exists z.~P(s,z)\*P(t,z)}
+\Vlink[red,label={$~\scriptstyle{\mgu(s,t)}$}]{1,1}
+\end{tikzpicture}
+\]
+
+\bibliography{ALL1}
+
 \end{document}

### 2018-01-09 ALL1.tex
finished correctness proof YAY

@@
 \newcommand{\todo}[1]{{\color{red}     \noindent[\![\![{\bf TODO: }#1]\!]\!]}}
+\newcommand{\willem}[1]{{\color{green!50!black}     \noindent[\![\![{\bf Willem: }#1]\!]\!]}}
 
@@
 }
-\newcommand\@srr[1]{+_{#1}\mathrm S}
+\newcommand\@srr[1]{+\mathrm S,{#1}}
 
@@
 \[
-	\infer[\Qrr1]{\seq P{\dual P}}{}
+	\infer[\Qrr1]{\vphantom B\seq a{\dual a}}{}
 \quad
@@
 	\item[Freshness]
-For a link $\link CD$ in $\net{\lambda_\Sigma}AB$, variables in the range of $\sigma$ are fresh: distinct from any existentially quantified (as $\exists x$) variable in $\seq AB$.
+For a link $\link CD$ in $\net{\lambda_\Sigma}AB$, variables in the range of $\sigma$ are fresh: distinct from any existentially quantified variable in $\seq AB$.
 \end{description}
@@
 	$\kappa,\lambda$ 	& $\subset$ & $\form\times\form$ 	& linkings (sets of pairs of formulas)\\
-	$\rho,\sigma,\tau$	& $\colon$  & $\varE\rightharpoonup\terms$ & witness maps\\
-	$\Sigma,\Theta$		& $\colon$  & $(\form\times\form)\rightharpoonup\varE\rightharpoonup\terms$		& witness labellings on a linking \\
-	$\Pi,\Phi,\Psi$		& $\colon$  & $(\form\times\form)\rightharpoonup\proofs$		& proof labellings on a linking
+	$\rho,\sigma,\tau$	& $\colon$  & $\var\rightharpoonup\terms$ & witness maps\\
+	$\Sigma,\Theta$		& $\colon$  & $\lambda\to\var\rightharpoonup\terms$		& witness labellings on a linking $\lambda$ \\
+	$\Pi,\Phi,\Psi$		& $\colon$  & $\lambda\to\proofs$		& proof labellings on a linking $\lambda$
 \end{tabular}
@@
 
+% ..................................................
+
+\begin{figure}
+\[
+\begin{array}{ccc@{\hspace{50pt}}ccc}
+    \vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{C}
+    	\formula[y=1]{D*{_1}{{\+}}D*{_2}}
+    	\Vlink[red,label={$\scriptstyle\sigma~$},l]{1,1}
+    \end{tikzpicture}}
+&\scoal& 
+    \vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{C}
+    	\formula[y=1]{D*{_1}{{\+}}D*{_2}}
+    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,2}
+    \end{tikzpicture}}
+&
+    \vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{C}
+    	\formula[y=1]{\exists x.D}
+    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,4}
+    \end{tikzpicture}}
+&\stackrel{x\,\in\,\dom\sigma}\scoal&
+    \vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{C}
+    	\formula[y=1]{\exists x.D}
+    	\Vlink[red,label={~$\scriptstyle{\sigma\minus x}$}]{1,1}
+    \end{tikzpicture}}   
+\\ \\   
+    \vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{C}
+    	\formula[y=1]{D*{_1}{{\*}}D*{_2}}
+    	\Vlink[red,label={$\scriptstyle\sigma~$},l]{[-1]1,1}
+    	\Vlink[red,label={~$\scriptstyle\sigma$}]{[1]1,3}
+    \end{tikzpicture}}
+&\scoal&
+	\vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{C}
+    	\formula[y=1]{D*{_1}{{\*}}D*{_2}}
+    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,2}
+    \end{tikzpicture}}   
+&
+    \vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{C}
+    	\formula[y=1]{\forall x.D}
+    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,4}
+    \end{tikzpicture}}
+&\stackrel{x\,\notin\,\sigma}\scoal&
+    \vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{C}
+    	\formula[y=1]{\forall x.D}
+    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,1}
+    \end{tikzpicture}}
+\end{array}
+\]
+\caption{Coalescence rules}
+\label{fig:coalescence}
+\end{figure}
+
+%\begin{figure}
+%\[
+%    \vc{\begin{tikzpicture}[net]
+%    	\formula[y=2]{C}
+%    	\formula[y=1]{D*{_1}{{\+}}D*{_2}}
+%    	\Vlink[red,label={$\scriptstyle\sigma~$},l]{1,1}
+%    \end{tikzpicture}}
+%\scoal 
+%    \vc{\begin{tikzpicture}[net]
+%    	\formula[y=2]{C}
+%    	\formula[y=1]{D*{_1}{{\+}}D*{_2}}
+%    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,2}
+%    \end{tikzpicture}}
+%\hfill% 
+%    \vc{\begin{tikzpicture}[net]
+%    	\formula[y=2]{C}
+%    	\formula[y=1]{D*{_1}{{\*}}D*{_2}}
+%    	\Vlink[red,label={$\scriptstyle\sigma~$},l]{[-1]1,1}
+%    	\Vlink[red,label={~$\scriptstyle\sigma$}]{[1]1,3}
+%    \end{tikzpicture}}
+%\scoal
+%	\vc{\begin{tikzpicture}[net]
+%    	\formula[y=2]{C}
+%    	\formula[y=1]{D*{_1}{{\*}}D*{_2}}
+%    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,2}
+%    \end{tikzpicture}} 
+%\hfill%    
+%    \vc{\begin{tikzpicture}[net]
+%    	\formula[y=2]{C}
+%    	\formula[y=1]{\exists x.D}
+%    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,4}
+%    \end{tikzpicture}}
+%\stackrel{\begin{array}{@{}c@{}}\scriptstyle x\,\in\\[-1ex]\scriptstyle\dom\sigma\end{array}}\scoal
+%    \vc{\begin{tikzpicture}[net]
+%    	\formula[y=2]{C}
+%    	\formula[y=1]{\exists x.D}
+%    	\Vlink[red,label={~$\scriptstyle{\sigma\minus x}$}]{1,1}
+%    \end{tikzpicture}}   
+%\hfill%
+%    \vc{\begin{tikzpicture}[net]
+%    	\formula[y=2]{C}
+%    	\formula[y=1]{\forall x.D}
+%    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,4}
+%    \end{tikzpicture}}
+%\stackrel{x\,\notin\,\sigma}\scoal
+%    \vc{\begin{tikzpicture}[net]
+%    	\formula[y=2]{C}
+%    	\formula[y=1]{\forall x.D}
+%    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,1}
+%    \end{tikzpicture}}
+%\]
+%\caption{Coalescence rules}
+%\label{fig:coalescence}
+%\end{figure}
+
+% ..................................................
+
 \begin{definition}
- \defn{Strict sequentialization} ($\scoal$) is the rewrite relation on labelled pre-nets generated by the following rules.
-\defn{Strict coalescence} is the same relation ignoring proof labels, on witness pre-nets, illustrated in Figure~\ref{fig:coalescence}.
 %
@@
 \renewcommand{\*}{{\times}}
-\begin{equation}
-  	\net{\{\link A{B_i}^\pi\}}A{B_1\+B_2} 
- ~\scoal~
-	\net{\{\link A{B_1\+B_2} ^\psi\}}A{B_1\+B_2}
-\tag{$\srr+i$}
-\end{equation}
-
-\hfill $\text{where}\quad \psi=~
-  \vc{\infer  {\seq{A\sigma}{B_1\sigma\,\+\,B_2\sigma}}  {\Prf \pi {A\sigma} {B_i\sigma}}}
-$ \hspace*{20pt}
-
-\begin{equation}
-	\net{\{\link AB^\pi,\link AC^\phi\}}A{B\*C}
- ~\scoal~ 
-	\net{\{\link A{B\*C}^\psi\}}A{B\*C}
-\tag{$\srr*$}
-\end{equation}
-
-\hfill $\text{where}\quad \psi=~
-  \vc{
-   \infer  {\seq{A\sigma}{B\sigma\,\*\,C\sigma}}  {
-    \Prf \pi {A\sigma} {B\sigma}
-    &
-    \Prf \phi {A\sigma} {C\sigma}    
-  }}$ \hspace*{20pt}
-
-\begin{equation}
-	\net{\{\link AB^\pi\}}A{\exists x.B}
- ~\scoal~ 
-	\net{\{\link[\sigma\minus x]A{\exists x.B}^\psi\}}A{\exists x.B}
-\tag{$\srr?$}
-\end{equation}
-
-\hfill $\text{if}\quad\sigma(x)\,\neq\,\bot~,
-		\quad
-		\text{where}\quad \tau=\sigma\minus x
-		\quad
-		\text{and}\quad \psi=~
-  \vc{
-   \infer  {\seq{A\tau}{\exists x.B\tau}}  {
-    \Prf \pi {A\sigma} {B\sigma}
+%
+\defn{Strict sequentialization} ($\scoal$) is the rewrite relation on labelled pre-nets generated by the following rules, that replace one or two links by another in a pre-net $\net{\lambda_\Sigma^\Pi}AB$ (where $B$ has a subformula $D_1\+D_2$, $D_1\*D_2$, $\exists x.D$, and $\forall x.D$ respectively).
+%
+\begin{align*}
+%\tag{$\srr+i$}
+	\link C{D_i}^\pi
+	& \scoal
+	\link C{D_1\+D_2}^\psi
+	&& 
+ 	\psi=~\vc{\infer[\Qrr+i]{\seq{C\sigma}{D_1\sigma\,\+\,D_2\sigma}}  {\Prf \pi {C\sigma} {D_i\sigma}}}
+\\ \\[-8pt]
+%\tag{$\srr*$}
+	%\{\link C{D_1}^\pi\,,\,\link C{D_2}^\phi\}
+	\left.\begin{array}{@{}l@{\,}}\link C{D_1}^\pi \\ \link C{D_2}^\phi\end{array}\right\}
+	& \scoal
+	\link C{D_1\*D_2}^\psi
+	&&
+	\psi=~\vc{\infer[\Qrr*]{\seq{C\sigma}{D_1\sigma\,\*\,D_2\sigma}}  {
+      \Prf \pi {C\sigma} {D_1\sigma} & \Prf \phi {C\sigma} {D_2\sigma}    
 	}}
-$ \hspace*{20pt}
-
-\begin{equation}
-	\net{\{\link AB\}}A{\forall a.B}
- ~\scoal~
-	\net{\{\link A{\forall a.B}\}}A{\forall a.B}
-\tag{$\srr!$}
-\end{equation}
-
-\hfill $\text{if}\quad a\notin\sigma~,
-		\quad
-		\text{where}\quad \psi=~
-  \vc{
-   \infer  {\seq{A\sigma}{\forall a.B\sigma}}  {
-    \Prf \pi {A\sigma} {B\sigma}
-  }}
-$ \hspace*{20pt}
-
-\medskip
-
-\noindent
-A witness pre-net $\net{\lambda_\Sigma}AB$ \defn{strict-coalesces} if it reduces to a single link $\net{\{\link[\varnothing]AB\}}AB$.\end{definition}
-
-To be explicit, to generate coalescence as a rewrite relation means the following: a pre-net coalesces to another, $\net{\lambda_\Sigma} AB\scoal \net{{\lambda'_{\Sigma'}}}AB$ if and only if there is a rewrite rule
-\[
-	\net{\kappa_\Theta} CD\scoal\net{\kappa'_{\Theta'}} CD
-\] 
-such that 
-\[
-	C\leq A \qquad
-	D\leq B \qquad
-	\kappa_\Theta\subseteq\lambda_\Sigma \qquad
-	\kappa'_{\Theta'}\subseteq\lambda'_{\Sigma'} \quad
-	\text{and} \quad
-	\lambda_\Sigma-\kappa_\Theta=\lambda'_{\Sigma'}-\kappa'_{\Theta'}~.
-\]
+\\ \\[-8pt]
+%\tag{$\srr?$}
+	\link CD^\pi
+	& \scoal
+	\link[\sigma\minus x]C{\exists x.D}^\psi
+	\quad{\scriptstyle(x\,\in\,\dom\sigma)}
+	&&
+	\psi=~\vc{\infer[\Qrr?{\sigma(x)}]{\seq{C(\sigma\minus x)}{\exists x.D(\sigma\minus x)}} {\Prf \pi {C\sigma} {D\sigma} }}	
+\\ \\[-8pt]
+%\tag{$\srr!$}
+	\link CD^\pi
+	& \scoal
+	\link C{\forall x.D}^\psi
+	\quad{\scriptstyle\phantom{\minus x}(x\,\notin\,\sigma)}
+	&&
+	\psi=~\vc{\infer[\Qrr!]{\seq{C\sigma}{\forall x.D\sigma}} {\Prf \pi {C\sigma} {D\sigma}}}
+\end{align*}
+%
+\defn{Strict coalescence} is the same relation on witness pre-nets, ignoring proof labels, illustrated in Figure~\ref{fig:coalescence}.
+A witness pre-net $\net{\lambda_\Sigma}AB$ \defn{strict-coalesces} if it reduces to $\net{\{\link[\varnothing]AB\}}AB$.
+It \defn{strongly} strict-coalesces if any coalescence path terminates at $\net{\{\link[\varnothing]AB\}}AB$.
+\end{definition}
 
 \begin{definition}
-An \all1 \defn{witnessing proof net} or \defn{witness net} is a witness pre-net $\net{\lambda_\Sigma}AB$, with $\lambda_\Sigma$ an axiom linking, that strict-coalesces.
+An \all1 \defn{witness proof net} or \defn{witness net} is a witness pre-net $\net{\lambda_\Sigma}AB$ with $\lambda_\Sigma$ an axiom linking, that strict-coalesces.
 It \defn{sequentializes} to a proof $\pi$ if its initial labelling $\net{\lambda_\Sigma^\star}AB$ reduces in $(\scoal)$ to $\net{\{\link[\varnothing]AB^\pi\}}AB$.
@@
 \begin{proof}
-It follows by induction on $\prf\pi AB$ that if $\lambda_\Sigma=[\pi]_{A',B'}^\sigma$ where $A'\sigma=A$ and $B'\sigma=B$, then $\net{\lambda^\star_\Sigma}AB$ reduces in $(\scoal)$ to $\net{\{\link{A'}{B'}^\pi\}}AB$.
-The statement is the specific case $\sigma=\varnothing$.
+It follows by induction on $\pi$ that if $\lambda_\Sigma=\deseq{\prf\pi AB}{A'}{B'}$ where $A'\sigma=A$ and $B'\sigma=B$, then $\net{\lambda^\star_\Sigma}AB$ reduces in $(\scoal)$ to $\net{\{\link{A'}{B'}^\pi\}}AB$.
+The statement is the case $\sigma=\varnothing$.
 \end{proof}
-
-\end{document}
 
@@
 As in the propositional case, we define a slice of a sequent $\seq AB$ as a set of potential links, of which exactly one must be realized in a proof net $\net{\lambda_\Sigma}AB$.
-
-For a witness linking $\lambda_\Sigma$ and an existential variable $x$, write $\Sigma(x)\subseteq\terms$ for the \defn{witness set} of $x$, which collects the terms assigned to $x$ by the witness maps in $\Sigma$ for every link in $\lambda$:
+For a witness linking $\lambda_\Sigma$ and variable $x$, write $\Sigma(x)\subseteq\terms$ for the \defn{witness set} of $x$, which collects the terms assigned to $x$ by the witness maps in $\Sigma$ for every link in $\lambda$:
 \[
@@
 \begin{definition}[Slice]
-Given a witness linking $\lambda_\Sigma$, a \defn{slice} $S$ of a formula $A$ and a witness map $\sigma$ is a set of pairs $(A',\sigma')$, where $A'$ is a subformula of $A$ and $\sigma\subseteq\sigma'$, given by: $S=\{(A,\sigma)\}\cup S'$ where $S'$ is as follows.
+Given a witness linking $\lambda_\Sigma$, a \defn{slice} $S$ of a formula $A$ and a witness map $\sigma$ is a set of pairs $(A',\sigma')$, where $A'\leq A$ and $\sigma'\supseteq\sigma$, given by $S=\{(A,\sigma)\}\cup S'$ where:
 %
@@
 	\item
-\makebox[65pt][l]{If $A = P$}			then $S'=\varnothing$.
+\makebox[65pt][l]{If $A = a$}			then $S'=\varnothing$.
 	\item
@@
 	\item
-\makebox[65pt][l]{If $A = \forall a.B$}	then $S'$ is a slice of $B$ and $\sigma$.
+\makebox[65pt][l]{If $A = \forall x.B$}	then $S'$ is a slice of $B$ and $\sigma$.
 \end{itemize}
@@
 In addition, within each slice we need to ensure that the order in which quantifiers are instantiated is sound.
-That is, we need to have an analogue of the \emph{eigenvariable condition} on the $\qrr!$-rule of sequent calculus, that the quantified variable $a$ of the primary formula $\forall a.A$ does not occur free in the context.
+That is, we need to have an analogue of the \emph{eigenvariable condition} on the $\qrr!$-rule of sequent calculus, that the quantified variable $x$ of the formula $\forall x.A$ does not occur free in the context.
 We will define a \defn{dependency} condition to this effect.
-For simplicity we will define the dependency condition on individual links rather than on slices (since each slice will be a singleton).
+For simplicity we will define the dependency condition on individual links rather than on slices.
+% (since each slice will be a singleton).
 
@@
 \[
-	\{~(X,\sigma\res{\ex AX})~\mid~C\sub X\sub A~\}\cup\{~(Y,\sigma\res{\ex BY})~\mid~D\sub Y\sub B~\}~,
-\]
-with an order $(\dep)$ given by: $(X,\rho)\dep(Y,\tau)$ if $X\leq Y$ or $Y$ occurs as $\forall a.Y$ and $a\in\rho$.
+	\{~(X,\sigma\res{\ex[A]X})~\mid~C\sub X\sub A~\}\cup\{~(Y,\sigma\res{\ex[B]Y})~\mid~D\sub Y\sub B~\}~,
+\]
+with an order $(\dep)$ given by: $(X,\rho)\dep(Y,\tau)$ if $X\leq Y$ or $Y$ occurs as $\forall x.Y$ and $x\in\rho$.
 
@@
 \begin{definition}
-A witness pre-net is \defn{correct} if it is
+A witness pre-net is \defn{correct} if
 \begin{itemize}
-\item \defn{slice-correct}: every slice is a singleton, and
-\item \defn{dependency-correct}: every column is a partial order (i.e.\ is acyclic/antisymmetric).
+\item it has exact coverage,
+\item it is \defn{slice-correct}: every slice is a singleton, and
+\item it is \defn{dependency-correct}: every column is a partial order (i.e.\ is acyclic/antisymmetric).
 \end{itemize}
@@
 \label{lem:preservation}
-Strict coalescence preserves and reflects correctness: for a strict coalescence step $L\scoal R$, the witness pre-net $L$ is correct if and only if $R$ is.
+Strict coalescence preserves and reflects slice- and dependency-correctness.
 \end{lemma}
 
+\willem{It looks like this can be split into separate lemmas for slice-correctness and dependency-correctness. Better?}
+
 \begin{proof}
+For a strict coalescence step $L\scoal R$, we will show that the witness pre-net $L$ is slice- or dependency-correct if and only if $R$ is.
+%
 Let $L=\net{\lambda_\Sigma}AB$ and $R=\net{\kappa_\Theta}AB$.
-We will consider the four coalescence steps as shown below.
 For slice-correctness, we will demonstrate that the left-hand side and right-hand side of each rule belong to the same slice of $\seq AB$, or in the case of $\srr?$, naturally corresponding slices.
 %
-\begin{align}
-  	\net{\{\link C{D_i}\}}C{D_0{\+}D_1} 
- &~\scoal~
-	\net{\{\link C{D_0{\+}D_1} \}}C{D_0{\+}D_1}
-\tag{$\srr+i$}
-\\	\net{\{\link C{D_0},\link C{D_1}\}}C{D_0{\*}D_1}
- &~\scoal~ 
-	\net{\{\link C{D_0{\*}D_1}\}}C{D_0{\*}D_1}
-\tag{$\srr*$}
-\\	\net{\{\link CD\}}C{\exists x.D}
- &~\scoal~ 
-	\net{\{\link[\sigma\minus x]C{\exists x.D}\}}C{\exists x.D}
-\tag{$\srr?$}
-\\	\net{\{\link CD\}}C{\forall a.D}
- &~\scoal~
-	\net{\{\link C{\forall a.D}\}}C{\forall a.D}
-\tag{$\srr!$}
-\end{align}
-%
-\begin{description}
-	\item[$(\srr+i)$]
-A slice $S_B$ of $B$ and $\varnothing$ containing either of $(D_0,\tau)$, $(D_1,\tau)$, and $(D_0\+D_1,\tau)$ must also contain the other two. 
-%
-%\lutz{something is confusing here.
+%\begin{align}
+%  	\net{\{\link C{D_i}\}}C{D_0{\+}D_1} 
+% &~\scoal~
+%	\net{\{\link C{D_0{\+}D_1} \}}C{D_0{\+}D_1}
+%\tag{$\srr+i$}
+%\\	\net{\{\link C{D_0},\link C{D_1}\}}C{D_0{\*}D_1}
+% &~\scoal~ 
+%	\net{\{\link C{D_0{\*}D_1}\}}C{D_0{\*}D_1}
+%\tag{$\srr*$}
+%\\	\net{\{\link CD\}}C{\exists x.D}
+% &~\scoal~ 
+%	\net{\{\link[\sigma\minus x]C{\exists x.D}\}}C{\exists x.D}
+%\tag{$\srr?$}
+%\\	\net{\{\link CD\}}C{\forall a.D}
+% &~\scoal~
+%	\net{\{\link C{\forall a.D}\}}C{\forall a.D}
+%\tag{$\srr!$}
+%\end{align}
+%
+\begin{itemize}
+	\item
+$\link C{D_i}\scoal\link C{D_1{\+}D_2}$
+\\
+A slice $S_B$ of $B$ and $\varnothing$ containing one of $(D_1,\tau)$, $(D_2,\tau)$, and $(D_1\+D_2,\tau)$ must also contain the other two. 
+%
+\lutz{something is confusing here.
 It seems you are using different notions of slice.
@@
 %
-% A slice of a NET is singleton; a slice of FORMULA or SEQUENT need not be.
-%
-A slice $S$ of $\seq AB$ then contains all three of $\link C{D_0}$, $\link C{D_1}$, and $\link C{D_0{\+}D_1}$, or none.
+\willem{Indeed. A slice of a NET is singleton; a slice of FORMULA or SEQUENT need not be.}
+%
+A slice $S$ of $\seq AB$ then contains all three of $\link C{D_1}$, $\link C{D_2}$, and $\link C{D_1{\+}D_2}$, or none.
 It follows that $S\cap \lambda_\Sigma$ is a singleton if and only if $S\cap\kappa_\Theta$ is.
 Since other slices are unaffected, $L$ is slice-correct if and only if $R$ is.
-For dependency-correctness, the column of $\link C{D_i}$ is that of $\link C{D_0{\+}D_1}$ plus $(D_i,\sigma|\ex B{D_i})$ itself, which is minimal in the order $\dep$.
-
-	\item[$(\srr*)$]
-A slice $S$ of $\seq AB$ contains $\link C{D_0\+D_1}$ if and only if it contains either of $\link C{D_0}$ or $\link C{D_1}$, and may not contain both.
+For dependency-correctness, the column of $\link C{D_i}$ is that of $\link C{D_1{\+}D_2}$ plus $(D_i,\sigma\res{\ex[B]{D_i}})$ itself, which is minimal in the order $\dep$.
+
+	\item
+$\link C{D_1},\link C{D_2}\scoal\link C{D_1{\*}D_2}$
+\\
+A slice $S$ of $\seq AB$ contains $\link C{D_1{\*}D_2}$ if and only if it contains either of $\link C{D_1}$ or $\link C{D_2}$, and may not contain both.
 Then $S\cap \lambda_\Sigma$ is a singleton if and only if $S\cap\kappa_\Theta$ is.
@@
 
-	\item[$(\srr?)$]
+	\item
+$\link CD\scoal\link[\sigma\minus x]C{\exists x.D}$
+\\
 The witness sets $\Sigma(x)$ and $\Theta(x)$ for $L$ and $R$ need not be the same, since $L$ has $\sigma$ where $R$ has $\sigma\minus x$.
@@
 
-	\item[$(\srr!)$]
-A slice $S$ of $\seq AB$ contains $\link CD$ if and only if it contains also $\link C{\forall a.D}$, and hence $S\cap\lambda_\Sigma$ is a singleton if and only if $S\cap\kappa_\Theta$ is.
-
-For dependency-correctness, the column of $\link CD$ is that of $\link C{\forall a.D}$ plus a pair $(D,\tau)$.
-The side-condition of the coalescence step is that $a\notin\sigma$; then $a$ does not occur free in any $(X,\rho)$, and $(D,\tau)$ is minimal in $(\dep)$.
+	\item
+$\link CD\scoal\link C{\forall x.D}$
+\\
+A slice $S$ of $\seq AB$ contains $\link CD$ if and only if it contains also $\link C{\forall x.D}$, and hence $S\cap\lambda_\Sigma$ is a singleton if and only if $S\cap\kappa_\Theta$ is.
+
+For dependency-correctness, the column of $\link CD$ is that of $\link C{\forall x.D}$ plus a pair $(D,\tau)$.
+The side-condition of the coalescence step is that $x\notin\sigma$; then $x$ does not occur free in any $(X,\rho)$, and $(D,\tau)$ is minimal in $(\dep)$.
 \qedhere
-\end{description}
+\end{itemize}
 \end{proof}
@@
 \begin{lemma}
+\label{lem:coalescence applies}
+In a correct witness pre-net a coalescence step applies, unless it has already been coalesced.
+\end{lemma}
+
+\begin{proof}
+
+\end{proof}
+
+\begin{theorem}
 A witness pre-net is correct if and only if it strict-coalesces. 
-\end{lemma}
+\end{theorem}
 
@@
 Let the \defn{depth} of a link $\link CD$ be a pair of integers $(n,m)$, where $n$ is the distance from $C$ to the root of $A$, and $m$ that from $D$ to $B$.
-We order link depth in the product order, $(i,j)\leq(n,m)$ if and only if $i\leq n$ and $j\leq m$.
+We order link depth in the product order: $(i,j)\leq(n,m)$ if and only if $i\leq n$ and $j\leq m$.
 We will demonstrate that a link at maximal depth may always be coalesced, unless it is the unique link $\link[\varnothing]AB$ at $(0,0)$.
@@
 \begin{itemize}
-	\item $\link A{D_i}$ with $D_i$ occurring in $D=D_0\*D_1$; without loss of generality, let $i=0$.
-A slice $S_i$ of $\seq AB$ containing $\link A{D_i}$ has a counterpart $S_j$ containing $\link A{D_j}$ with $j=1-i$.
-The depth of $\link A{D_i}$ is the same as that of $\link A{D_j}$.
-By correctness $S_j\cap \lambda_\Sigma$ is a singleton; by the assumption of maximality it may not contain a deeper link than $\link A{D_j}$; and it may not contain a shallower one since that would be shared with $S_i\cap\lambda_\Sigma$.
-Since $\net{\lambda_\Sigma}AB$ contains both $\link A{D_0}$ and $\link A{D_1}$, these contract by $\srr*$ to $\link AD$.
-
-	\item $\link AD$ with $D$ in $\forall a.D$.
-
-	\item $\link{C_i}{D_j}$ in $C_0\*C_1$ and $D_0\*D_1$.
-
-	\item $\link{C_i}D$ in $C_0\*C_1$ and $\forall a.D$.
-
-	\item $\link CD$ in $\forall a.C$ and $\forall b.D$.
-
+	\item 
+$\link A{D_i}$ with $D_i$ occurring in $D=D_1\*D_2$.
+\\ 
+Without loss of generality, let $i=1$.
+A slice $S_1$ of $\seq AB$ containing $\link A{D_1}$ has a counterpart $S_2$ containing $\link A{D_2}$.
+The depth of $\link A{D_2}$ is the same as that of $\link A{D_1}$.
+By correctness $S_2\cap \lambda_\Sigma$ is a singleton; by the assumption of maximality it may not contain a deeper link than $\link A{D_2}$; and it may not contain a shallower one since that would be shared with $S_1\cap\lambda_\Sigma$.
+Then $\net{\lambda_\Sigma}AB$ contains both $\link A{D_1}$ and $\link A{D_2}$, and these contract to $\link AD$.
+
+	\item 
+$\link AD$ with $D$ in $\forall x.D$. 
+\\
+The step $\link AD\scoal\link A{\forall x.D}$ applies if $x\notin\sigma$.
+The column of $\link AD$ contains $(D,\sigma_D)$ and $(\forall x.D,\tau)$ where $\tau=\sigma\res{\ex[B]{\forall x.D}}$.
+By the exact coverage condition, $\sigma=\sigma_A\cup\sigma_D$, and since the existential variables in $D$ and $\forall x.D$ are the same, $\ex[B]D=\ex[B]{\forall x.D}$, so that $\tau=\sigma_D$.
+(Note that since $\sigma_A=\varnothing$, we get $\sigma=\sigma_D=\tau$, but this is not essential to the argument.) If $x\in\sigma$ then $x\in\tau$, and in the column of $\link AD$ we would have $(\forall x.D,\tau)\dep(D,\tau)$ since $D$ occurs as $\forall x.D$.
+But we already have $(D,\tau)\dep(\forall x.D,\tau)$ because $D\sub\forall x.D$, contradicting antisymmetry of $(\dep)$.
+Then $x\notin\sigma$, and the step $\link AD\scoal\link A{\forall x.D}$ applies.
+
+	\item
+$\link{C_i}{D_j}$ in $C=C_1\*C_2$ and $D=D_1\*D_2$.
+\\
+Without loss of generality, let $i=j=1$. By minimal depth and using similar reasoning to the first case above, the pre-net must contain one of the following three configurations.\\
+\begin{tabular}[c]{ll}
+	1. & $\link{C_1}{D_1},\link{C_1}{D_2},\link{C_2}{D_1},\link{C_2}{D_2}$
+\\	2. & $\link{C_1}{D_1},\link{C_1}{D_2},\link{C_2}{D}$
+\\	3. & $\link{C_1}{D_1},\link{C_2}{D_1},\link{C}{D_2}$
+\end{tabular}
+\hfill
+$
+\scriptstyle
+1:~\vc{
+\begin{tikzpicture}[net]
+	\formula[y=1]{C*{_1}{{\*}}C*{_2}}
+	\formula[y=0]{D*{_1}{{\*}}D*{_2}}
+	\Vlink[red]{[-2]1,[-2]1}\Vlink[red]{[2]1,[-2]3}\Vlink[red]{[-2]3,[2]1}\Vlink[red]{[2]3,[2]3}
+\end{tikzpicture}}
+\qquad
+2:~\vc{
+\begin{tikzpicture}[net]
+	\formula[y=1]{C*{_1}{{\*}}C*{_2}}
+	\formula[y=0]{D*{_1}{{\*}}D*{_2}}
+	\Vlink[red]{[-2]1,[-2]1}\Vlink[red]{[2]1,[-2]3}\Vlink[red]{3,2}
+\end{tikzpicture}}
+\qquad
+3:~\vc{
+\begin{tikzpicture}[net]
+	\formula[y=1]{C*{_1}{{\*}}C*{_2}}
+	\formula[y=0]{D*{_1}{{\*}}D*{_2}}
+	\Vlink[red]{[-2]1,[-2]1}\Vlink[red]{[-2]3,[2]1}\Vlink[red]{2,3}
+\end{tikzpicture}}
+\qquad
+$
+In the second case, the step $\link{C_1}{D_1},\link{C_1}{D_2}\scoal\link{C_1}D$ applies; in the third case, $\link{C_1}{D_1},\link{C_2}{D_1}\scoal\link C{D_1}$; and in the first case, both.
+
+	\item 
+$\link{C_i}D$ in $C=C_1\*C_2$ and $\forall x.D$.
+\\
+Without loss of generality let $i=1$.
+If $x\notin\sigma$ the rewrite step $\link{C_1}D\scoal\link{C_1}{\forall x.D}$ applies.
+Otherwise, let $x\in\sigma$.
+The slice $S_1$ of $\seq AB$ containing $\link{C_1}D$ has a counterpart $S_2$ containing $\link{C_2}D$, which must include exactly one link of $\lambda_\Sigma$.
+By the assumption of minimal depth, it cannot have greater depth than $\link{C_2}D$.
+It cannot be $\link CD$ or any shallower link, since that would be shared with the slice $S_1$ which already contains $\link{C_1}D$.
+It cannot be $\link{C_2}{\forall x.D}$ or any shallower link $\link[\tau]{C_2}{X}$ (i.e.\ with $\forall x.D\leq X$) because $x\in\sigma$.
+This would mean either $x\in\tau$ which contradicts the \emph{eigenvariables not free} convention, or $x\in\fv(\sigma(y))$ where $\forall x.D<\exists y.Y\leq X$ which creates a cyclic column, as in the second case above.
+It follows that $S_2\cap\lambda_\Sigma=\{\link{C_2}{D}\}$, so that the rewrite step $\link{C_1}D,\link{C_2}D\scoal\link CD$ applies.
+
+	\item 
+$\link CD$ in $\forall x.C$ and $\forall y.D$.
+\\
+A rewrite step $\link CD\scoal\link{\forall x.C}D$ or $\link CD\scoal\link C{\forall y.D}$ applies unless $x,y\in\sigma$.
+But that would generate a cycle in the column of $\link CD$, in one of three ways.
+If $x\in\sigma_C$ or $y\in\sigma_D$ then, since $\sigma_C=\sigma_{\forall x.C}$ and $\sigma_D=\sigma_{\forall y.D}$, respectively:
+\[
+	(C,\sigma_C)\dep(\forall x.C,\sigma_C)\dep(C,\sigma_C)
+\qquad\quad
+	(D,\sigma_D)\dep(\forall y.D,\sigma_D)\dep(D,\sigma_D)~.
+\]
+Otherwise, if $x\in\sigma_D$ and $y\in\sigma_C$ then
+\[
+	(C,\sigma_C)\dep(\forall x.C,\sigma_C)\dep(D,\sigma_D)\dep(\forall x.D,\sigma_D)\dep(C,\sigma_C)~.
+\qedhere
+\]
 \end{itemize}
-
 \end{proof}
+
+\begin{corollary}
+A correct witness pre-net with axiom linking is a witness proof net.
+\end{corollary}
+
+\begin{theorem}
+A correct witness pre-net strongly strict-coalesces.
+\end{theorem}
+
+\begin{
+
+\end{document}
 
@@
 \end{document}
+
+\begin{equation}
+  	\net{\{\link A{B_i}^\pi\}}A{B_1\+B_2} 
+ ~\scoal~
+	\net{\{\link A{B_1\+B_2} ^\psi\}}A{B_1\+B_2}
+\tag{$\srr+i$}
+\end{equation}
+
+\hfill $\text{where}\quad \psi=~
+  \vc{\infer  {\seq{A\sigma}{B_1\sigma\,\+\,B_2\sigma}}  {\Prf \pi {A\sigma} {B_i\sigma}}}
+$ \hspace*{20pt}
+
+\begin{equation}
+	\net{\{\link AB^\pi,\link AC^\phi\}}A{B\*C}
+ ~\scoal~ 
+	\net{\{\link A{B\*C}^\psi\}}A{B\*C}
+\tag{$\srr*$}
+\end{equation}
+
+\hfill $\text{where}\quad \psi=~
+  \vc{
+   \infer  {\seq{A\sigma}{B\sigma\,\*\,C\sigma}}  {
+    \Prf \pi {A\sigma} {B\sigma}
+    &
+    \Prf \phi {A\sigma} {C\sigma}    
+  }}$ \hspace*{20pt}
+
+\begin{equation}
+	\net{\{\link AB^\pi\}}A{\exists x.B}
+ ~\scoal~ 
+	\net{\{\link[\sigma\minus x]A{\exists x.B}^\psi\}}A{\exists x.B}
+\tag{$\srr?$}
+\end{equation}
+
+\hfill $\text{if}\quad\sigma(x)\,\neq\,\bot~,
+		\quad
+		\text{where}\quad \tau=\sigma\minus x
+		\quad
+		\text{and}\quad \psi=~
+  \vc{
+   \infer  {\seq{A\tau}{\exists x.B\tau}}  {
+    \Prf \pi {A\sigma} {B\sigma}
+  }}
+$ \hspace*{20pt}
+
+\begin{equation}
+	\net{\{\link AB\}}A{\forall a.B}
+ ~\scoal~
+	\net{\{\link A{\forall a.B}\}}A{\forall a.B}
+\tag{$\srr!$}
+\end{equation}
+
+\hfill $\text{if}\quad a\notin\sigma~,
+		\quad
+		\text{where}\quad \psi=~
+  \vc{
+   \infer  {\seq{A\sigma}{\forall a.B\sigma}}  {
+    \Prf \pi {A\sigma} {B\sigma}
+  }}
+$ \hspace*{20pt}

### 2018-01-09 ALL1.tex
re-organised proofs - still not happy

@@
 If a pre-net coalesces, it has exact coverage.
-%Every pre-net on a coalescence path $\net{\lambda_\Sigma}AB \scoal^* \net{\{\link[\varnothing]AB^\pi\}}AB$ from a witness net satisfies the exact coverage property.
 \end{lemma}
@@
 \begin{proof}
-By induction on the coalescence path. %, working backward from $\net{\{\link[\varnothing]AB^\pi\}}AB$.
+By induction on the coalescence path.
 \end{proof}
 
+\newcounter{lemslicecorrect}
+\setcounter{lemslicecorrect}{\thetheorem}
 \begin{lemma}
-\label{lem:preservation}
-Strict coalescence preserves and reflects slice- and dependency-correctness.
+\label{lem:slice-correct}
+Strict coalescence preserves and reflects slice-correctness.
 \end{lemma}
 
-\willem{It looks like this can be split into separate lemmas for slice-correctness and dependency-correctness. Better?}
-
 \begin{proof}
-For a strict coalescence step $L\scoal R$, we will show that the witness pre-net $L$ is slice- or dependency-correct if and only if $R$ is.
-%
+See appendix.
+\end{proof}
+
+\newcounter{lemdependencycorrect}
+\setcounter{lemdependencycorrect}{\thetheorem}
+\begin{lemma}
+\label{lem:dependency-correct}
+Strict coalescence preserves and reflects dependency-correctness.
+\end{lemma}
+
+\begin{proof}
+See appendix.
+\end{proof}
+
+\newcounter{lemcoalescenceapplies}
+\setcounter{lemcoalescenceapplies}{\thetheorem}
+\begin{lemma}
+\label{lem:coalescence applies}
+In a correct witness pre-net a coalescence step applies, unless it has already been coalesced.
+\end{lemma}
+
+\begin{proof}
+See appendix.
+\end{proof}
+
+\begin{theorem}
+\label{thm:correctness}
+A witness pre-net is correct if and only if it strict-coalesces. 
+\end{theorem}
+
+\begin{proof}
+From right to left, we proceed by induction on the coalescence path from $\net{\lambda_\Sigma}AB$ to $\net{\{\link[\varnothing]AB\}}AB$, with the end result as the base case.
+It is slice-correct: every slice of $\seq AB$ contains $\link[\varnothing]AB$, so every slice of $\net{\{\link[\varnothing]AB\}}AB$ is the singleton $\{\link[\varnothing]AB\}$.
+It is also dependency-correct: the column of $\link[\varnothing]AB$ is the set $\{(A,\varnothing),(B,\varnothing)\}$, where $A$ and $B$ are unrelated in $(\dep)$.
+For the inductive step, by Lemma~\ref{lem:preservation} coalescence reflects correctness, so that any pre-net along the coalescence path is correct, in particular $\net{\lambda_\Sigma}AB$.
+
+From left to right, let $\net{\lambda_\Sigma}AB$ be correct.
+By Lemma~\ref{lem:coalescence applies} either the net has coalesced, or a coalescence step applies.
+By Lemma~\ref{lem:slice-correct} and Lemma~\ref{lem:dependency-correct} the result of this coalescence step is again correct.
+It follows that the pre-net $\net{\lambda_\Sigma}AB$ strict-coalesces.
+\end{proof}
+
+\begin{corollary}
+A correct witness pre-net with axiom linking is a witness proof net.
+\end{corollary}
+
+\begin{corollary}
+A correct witness pre-net strongly strict-coalesces.
+\end{corollary}
+
+\begin{proof}
+By Theorem~\ref{thm:correctness} a correct pre-net coalesces, and by Lemma~\ref{lem:slice-correct} and Lemma~\ref{lem:dependency-correct} any coalescence step preserves correctness.
+\end{proof}
+
+\appendix
+
+\section{Postponed proofs}
+
+% ..................................................
+
+\setcounter{theorem}{\thelemslicecorrect}
+\begin{lemma}[Restatement]
+Strict coalescence preserves and reflects slice-correctness.
+\end{lemma}
+
+\begin{proof}
+For a strict coalescence step $L\scoal R$, we will show that the witness pre-net $L$ is slice-correct if and only if $R$ is.
 Let $L=\net{\lambda_\Sigma}AB$ and $R=\net{\kappa_\Theta}AB$.
-For slice-correctness, we will demonstrate that the left-hand side and right-hand side of each rule belong to the same slice of $\seq AB$, or in the case of $\srr?$, naturally corresponding slices.
-%
-%\begin{align}
-%  	\net{\{\link C{D_i}\}}C{D_0{\+}D_1} 
-% &~\scoal~
-%	\net{\{\link C{D_0{\+}D_1} \}}C{D_0{\+}D_1}
-%\tag{$\srr+i$}
-%\\	\net{\{\link C{D_0},\link C{D_1}\}}C{D_0{\*}D_1}
-% &~\scoal~ 
-%	\net{\{\link C{D_0{\*}D_1}\}}C{D_0{\*}D_1}
-%\tag{$\srr*$}
-%\\	\net{\{\link CD\}}C{\exists x.D}
-% &~\scoal~ 
-%	\net{\{\link[\sigma\minus x]C{\exists x.D}\}}C{\exists x.D}
-%\tag{$\srr?$}
-%\\	\net{\{\link CD\}}C{\forall a.D}
-% &~\scoal~
-%	\net{\{\link C{\forall a.D}\}}C{\forall a.D}
-%\tag{$\srr!$}
-%\end{align}
-%
+We will demonstrate that the left-hand side and right-hand side of each rule belong to the same slice of $\seq AB$, or in the case of $\srr?$, naturally corresponding slices.
+
 \begin{itemize}
@@
 Since other slices are unaffected, $L$ is slice-correct if and only if $R$ is.
-For dependency-correctness, the column of $\link C{D_i}$ is that of $\link C{D_1{\+}D_2}$ plus $(D_i,\sigma\res{\ex[B]{D_i}})$ itself, which is minimal in the order $\dep$.
 
@@
 Then $S\cap \lambda_\Sigma$ is a singleton if and only if $S\cap\kappa_\Theta$ is.
-Dependency-correctness is immediate, as above.
 
@@
 
-For dependency-correctness, the column of $\link CD$ is that of $\link[\sigma\minus x]C{\exists x.D}$ plus a pair $(D,\tau)$, which is minimal in $(\dep)$.
-
 	\item
@@
 A slice $S$ of $\seq AB$ contains $\link CD$ if and only if it contains also $\link C{\forall x.D}$, and hence $S\cap\lambda_\Sigma$ is a singleton if and only if $S\cap\kappa_\Theta$ is. 
-
-For dependency-correctness, the column of $\link CD$ is that of $\link C{\forall x.D}$ plus a pair $(D,\tau)$.
+\qedhere
+\end{itemize}
+\end{proof}
+
+% ..................................................
+
+\setcounter{theorem}{\thelemdependencycorrect}
+\begin{lemma}[Restatement]
+Strict coalescence preserves and reflects dependency-correctness.
+\end{lemma}
+
+\begin{proof}
+For a strict coalescence step $L\scoal R$, we will show that the witness pre-net $L$ is dependency-correct if and only if $R$ is. Again let $L=\net{\lambda_\Sigma}AB$ and $R=\net{\kappa_\Theta}AB$.
+
+\begin{itemize}
+	\item
+$\link C{D_i}\scoal\link C{D_1{\+}D_2}$
+\\
+The column of $\link C{D_i}$ is that of $\link C{D_1{\+}D_2}$ plus $(D_i,\sigma\res{\ex[B]{D_i}})$ itself, which is minimal in the order $\dep$.
+
+	\item
+$\link C{D_1},\link C{D_2}\scoal\link C{D_1{\*}D_2}$
+\\
+Immediate, as above.
+
+	\item
+$\link CD\scoal\link[\sigma\minus x]C{\exists x.D}$
+\\
+The column of $\link CD$ is that of $\link[\sigma\minus x]C{\exists x.D}$ plus a pair $(D,\tau)$, which is minimal in $(\dep)$.
+
+	\item
+$\link CD\scoal\link C{\forall x.D}$
+\\
+The column of $\link CD$ is that of $\link C{\forall x.D}$ plus a pair $(D,\tau)$.
 The side-condition of the coalescence step is that $x\notin\sigma$; then $x$ does not occur free in any $(X,\rho)$, and $(D,\tau)$ is minimal in $(\dep)$.
@@
 
-\begin{lemma}
-\label{lem:coalescence applies}
+% ..................................................
+
+\setcounter{theorem}{\thelemcoalescenceapplies}
+\begin{lemma}[Restatement]
 In a correct witness pre-net a coalescence step applies, unless it has already been coalesced.
@@
 \begin{proof}
-
-\end{proof}
-
-\begin{theorem}
-A witness pre-net is correct if and only if it strict-coalesces. 
-\end{theorem}
-
-\begin{proof}
-From right to left, we proceed by induction on the coalescence path from $\net{\lambda_\Sigma}AB$ to $\net{\{\link[\varnothing]AB\}}AB$, with the end result as the base case.
-It is slice-correct: every slice of $\seq AB$ contains $\link[\varnothing]AB$, so every slice of $\net{\{\link[\varnothing]AB\}}AB$ is the singleton $\{\link[\varnothing]AB\}$.
-It is also dependency-correct: the column of $\link[\varnothing]AB$ is the set $\{(A,\varnothing),(B,\varnothing)\}$, where $A$ and $B$ are unrelated in $(\dep)$.
-For the inductive step, by Lemma~\ref{lem:preservation} coalescence reflects correctness, so that any pre-net along the coalescence path is correct, in particular $\net{\lambda_\Sigma}AB$.
-
-From left to right, let $\net{\lambda_\Sigma}AB$ be correct.
 Let the \defn{depth} of a link $\link CD$ be a pair of integers $(n,m)$, where $n$ is the distance from $C$ to the root of $A$, and $m$ that from $D$ to $B$.
@@
 We will demonstrate that a link at maximal depth may always be coalesced, unless it is the unique link $\link[\varnothing]AB$ at $(0,0)$.
-By Lemma~\ref{lem:preservation} the result of this coalescence step is again correct, and it follows by induction on the decreasing depth of links that the pre-net $\net{\lambda_\Sigma}AB$ strict-coalesces.
-
-To see that a maximally deep link coalesces, first note that a link $\link C{D_i}$ where $D_i$ occurs in $D_0{\+}D_1$ may always contract, as may a link $\link CD$ where $D$ occurs in $\exists x.D$.
+
+To see that a maximally deep link coalesces, first note that a link $\link C{D_i}$ where $D_i$ occurs in $D_0{\+}D_1$ may always coalesce, as may a link $\link CD$ where $D$ occurs in $\exists x.D$.
 This leaves the following cases:
@@
 
-\begin{corollary}
-A correct witness pre-net with axiom linking is a witness proof net.
-\end{corollary}
-
-\begin{theorem}
-A correct witness pre-net strongly strict-coalesces.
-\end{theorem}
-
-\begin{
+% ..................................................
 

### 2018-01-09 ALL1.tex
re-re-organised proofs, put back composition

@@
 
+\newcounter{lemcorrectness}
+\setcounter{lemcorrectness}{\thetheorem}
 \begin{lemma}
-If a pre-net coalesces, it has exact coverage.
-\end{lemma}
-
-\begin{proof}
-By induction on the coalescence path.
-\end{proof}
-
-\newcounter{lemslicecorrect}
-\setcounter{lemslicecorrect}{\thetheorem}
-\begin{lemma}
-\label{lem:slice-correct}
-Strict coalescence preserves and reflects slice-correctness.
-\end{lemma}
-
-\begin{proof}
-See appendix.
-\end{proof}
-
-\newcounter{lemdependencycorrect}
-\setcounter{lemdependencycorrect}{\thetheorem}
-\begin{lemma}
-\label{lem:dependency-correct}
-Strict coalescence preserves and reflects dependency-correctness.
+\label{lem:correctness}
+Strict coalescence preserves and reflects correctness.
 \end{lemma}
@@
 By Lemma~\ref{lem:coalescence applies} either the net has coalesced, or a coalescence step applies.
-By Lemma~\ref{lem:slice-correct} and Lemma~\ref{lem:dependency-correct} the result of this coalescence step is again correct.
+By Lemma~\ref{lem:correct} the result of this coalescence step is again correct.
 It follows that the pre-net $\net{\lambda_\Sigma}AB$ strict-coalesces.
@@
 \begin{proof}
-By Theorem~\ref{thm:correctness} a correct pre-net coalesces, and by Lemma~\ref{lem:slice-correct} and Lemma~\ref{lem:dependency-correct} any coalescence step preserves correctness.
+By Theorem~\ref{thm:correctness} a correct pre-net coalesces, and by Lemma~\ref{lem:correct} any coalescence step preserves correctness.
 \end{proof}
 
+% --------------------------------------------------
+
+\subsection{Composition}
+
+\[
+\begin{array}{ccc}
+	\vc{
+	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\Seq AC}{
+	 \infer[\!\!\scriptstyle{\qrr*}]{\Seq A{B_1\*B_2}\vphantom{\dual B}}{\Prf{\pi_1}A{B_1} & \Prf{\pi_2}A{B_2}}
+	 &&
+	 \infer[\!\!\scriptstyle{\qrr+i}]{\Seq {\dual B_1\+\dual B_2}C}{\Prf\phi{B_i}C}
+	}}
+	&\Rightarrow&
+	\vc{\infer[\!\!\scriptstyle{\mathrm{cut}}]{\Seq AC}{\Prf{\pi_i}A{B_i} && \Prf\phi{\dual B_i}C}}
+\\ \\
+	\vc{
+	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\Seq AC}{
+	 \infer[\!\!\scriptstyle{\qrr?t}]{\Seq A{\exists x.B}}{\Prf\pi A{B[t/x]}}
+	 &&
+	 \infer[\!\!\scriptstyle{\qrr!}]{\Seq {\forall x.\dual B}C}{\Prf\phi{\dual B}C}
+	}}
+	&\Rightarrow&
+	\vc{\infer[\!\!\scriptstyle{\mathrm{cut}}]{\Seq AC}{\Prf\pi A{B[t/x]} && \Prf{\phi[t/x]}{\dual B[t/x]}C}}
+
+\end{array}
+\]
+
+The \defn{domain-preserving composition} of two witness maps $\sigma\dcom\tau$ is the map $(\sigma\tau)\res{\dom\sigma}$.
+
+The \defn{least fixed point} $\fix\sigma$ of a witness map $\sigma$ is the least map $\rho$ satisfying $\rho = \rho\sigma$.
+It is the shortest sequence $\fix\sigma=\sigma\sigma\dots\sigma$ such that no variable is both in the domain and range of $\fix\sigma$.
+Where it is used, in the composition of the witness maps of two links, we will need to demonstrate that it is well defined.
+
+\begin{definition}
+The \defn{composition} of two proof links $\link AB^\pi\comp\link[\tau]{\dual B}C^\phi$ is $\link[\rho]AC^\psi$ where
+\[
+	\rho = \sigma_A\tau_C\dcom\fix{\sigma_B\tau\subdual B}
+\qquad\text{and}\qquad
+	\psi = ~\vcenter{
+	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq {A\rho}{B\rho}}{
+	 \left(\vcenter{\deduce{\seq{A\sigma}{B\sigma}\vphantom{\dual B}}{\vphantom\phi\pi}}\right)\fix{\sigma_B\tau\subdual B}
+	&\left(\vcenter{\deduce{\seq{\dual B\tau}{C\tau}}{\phi}}\right)\fix{\sigma_B\tau\subdual B}
+	}}~.
+\]
+The \defn{composition} of two labelled pre-nets $(\net{\lambda_\Sigma^\Pi}AB)\comp(\net{\kappa_\Theta^\Phi}{\dual B}C)$ is then
+\[
+	\net{\{~\link XY^\pi\comp\link[\tau]{\dual Y}Z^\phi
+		~\mid~
+		\link XY^\pi\in{\lambda_\Sigma^\Pi}
+		~,~
+		\link[\tau]{\dual Y}Z^\phi\in\kappa_\Theta^\Phi~\}
+	}AC~.
+\]
+The composition of two witness pre-nets omits the proof annotations.
+\end{definition}
+
+%	\net{\{~\link[\rho]XZ~\mid~\link XY\in{\lambda_\Sigma}~,~\link[\tau]{\dual Y}Z\in\kappa_\Theta~,~\rho = (\sigma\cyc\tau)\res{\ex AX\,\cup\,\ex CZ}~\}~}AC
+%~\rho=\sigma_A\tau_{\smash{\,\dual{\!B}}\vphantom B}\cup\tau_C\sigma_B~
+%(\sigma\res{\ex AX})(\tau\res{\ex{\dual B}{\dual Y}})\cup(\tau\res{\ex CZ})(\sigma\res{\ex BY})
+
+In the following we will demonstrate that composition gives the desired result: if a net $L$ sequentializes to $\pi$ and $R$ to $\phi$, then $L\comp R$ sequentializes to a normal form of the composition of $\pi$ and $\phi$ with a cut.
+To this end we will explore how composition and sequentialization interact.
+We will consider the critical pairs of sequentialization with composition, and demonstrate that how they are resolved.
+
+The first critical pair of composition (downward as $\Rightarrow$) and sequentialization is the following.
+We consider the composition of pre-nets on $\seq AB$ and $\seq{\dual B}C$ where $B=B_1\*B_2$, with a synchronized sequentialization step on both pre-nets.
+\[
+\begin{array}{ccc}
+    \vc{
+    \begin{tikzpicture}[net]
+        \formula[y=3]{A}
+        \formula[y=1.8]{B*{_1}\*B*{_2}}
+        \Vlink[red,label={$\scriptstyle{\pi,\sigma\vphantom)~}$},l]{[-2]1,1}
+        \Vlink[red,label={$\scriptstyle{~\pi'\!,\sigma\vphantom)}$},r]{[2]1,3}
+        \formula[y=1.2]{{\dual B}*{_1}\+{\dual B}*{_2}}
+        \formula[y=0]{C}
+        \Vlink[red,label={$\scriptstyle{\phi,\tau\vphantom)~}$},l]{1,1}
+    \end{tikzpicture}}
+    & 
+    \begin{array}{c}\scoal\\[40pt]\scoal\end{array}
+    &
+    \vc{
+    \begin{tikzpicture}[net]
+        \formula[y=3]{A}
+        \formula[y=1.8]{B*{_1}\*B*{_2}}
+        \Vlink[red,label={$\scriptstyle{\pi''\!\!,\sigma\vphantom)~}$},l]{1,2}
+        \formula[y=1.2]{{\dual B}*{_1}\+{\dual B}*{_2}}
+        \formula[y=0]{C}
+        \Vlink[red,label={$\scriptstyle{\phi'\!,\tau\vphantom)~}$},l]{2,1}
+    \end{tikzpicture}}
+\\\\[-5pt] \Downarrow && \Downarrow \\\\[-5pt]
+    \vc{
+    \begin{tikzpicture}[net]
+        \formula[y=1.2]{A}
+        \formula[y=0]{C}
+        \Vlink[red,label={\makebox[0pt][r]{$\scriptstyle{\psi,\rho\vphantom)~}$}},l]{1,1}
+    \end{tikzpicture}}
+    &&
+    \vc{
+    \begin{tikzpicture}[net]
+        \formula[y=1.2]{A}
+        \formula[y=0]{C}
+        \Vlink[red,label={\makebox[0pt][r]{$\scriptstyle{\psi',\rho'\vphantom)~}$}},l]{1,1}
+    \end{tikzpicture}}
+\end{array}
+\qquad
+\begin{array}{l@{\,}l}
+	\rho  &=~ \sigma_A\tau_C\dcom\fix{\sigma_B\tau\subdual B} 
+\\ \\
+	\rho' &=~ \sigma_A\tau_C\dcom\fix{\sigma_{B_1}\tau\subdual{B_1}}
+\\ \\
+	\psi &=~\vc{
+	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq{A\rho}{C\rho}}{
+	 \left(\vc{
+	  \deduce{\seq{A\sigma}{B_1\sigma}\vphantom{\dual B_1}}{\pi\vphantom)}
+	 }\right)\fix{\sigma_{B_1}\tau\subdual{B_1}}
+	 &
+	 \left(\vc{
+	  \deduce{\seq{\dual B_1\tau}{C\tau}}{\phi\vphantom)}
+	 }\right)\makebox[0pt][l]{$\fix{\sigma_{B_1}\tau\subdual{B_1}}$}
+	}}
+\\ \\ \\
+	\psi' &= ~
+	\vc{\scalebox{0.75}{$
+	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq{A\rho'}{C\rho'}}{
+	 \left(\vc{\infer{\seq{A\sigma}{B_1\sigma\*B_2\sigma}\vphantom{\dual B}}{
+	  \deduce{\seq{A\sigma}{B_1\sigma}\vphantom{\dual B}}{\pi\vphantom)}
+	  &
+	  \deduce{\seq{A\sigma}{B_2\sigma\vphantom{\dual B}}}{\pi'\vphantom)}
+	 }}\right)\fix{\sigma_B\tau\subdual B}
+	 &
+	 \left(\vc{\infer{\seq{\dual B_1\tau\+\dual B_2\tau}{C\tau}}{
+	  \deduce{\seq{\dual B_1\tau}{C\tau}}{\phi\vphantom)}
+	 }}\right)\makebox[0pt][l]{$\fix{\sigma_B\tau\subdual B}$}
+	}$}\kern5pt}
+\end{array}
+\]
+Since the existential covers of $B$ and $B_1$ are the same, $\sigma_B\tau\subdual B = \sigma_{B_1}\tau\subdual{B_1}$ and $\rho=\rho'$.
+It then follows that $\psi'$ cut-eliminates in one step to $\psi$.
+
+The next critical pair is the following.
+\[
+\begin{array}{ccc}
+    \vc{
+    \begin{tikzpicture}[net]
+        \formula[y=3]{A}
+        \formula[y=1.8]{\exists x.B}
+        \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\pi,\sigma\vphantom)}$}},r]{1,4}
+        \formula[y=1.2]{\forall x.{\dual B}}
+        \formula[y=0]{C}
+        \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\phi,\tau\vphantom)}$}},r]{4,1}
+    \end{tikzpicture}}
+    & 
+    \begin{array}{c}\scoal\\[40pt]\stackrel{x\,\notin\,\tau\vphantom)}\scoal\end{array}
+    &
+    \vc{
+    \begin{tikzpicture}[net]
+        \formula[y=3]{A}
+        \formula[y=1.8]{\exists x.B}
+        \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\pi',\sigma\minus x\vphantom)}$}},r]{1,1}
+        \formula[y=1.2]{\forall x.{\dual B}}
+        \formula[y=0]{C}
+        \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\phi',\tau\vphantom)}$}},r]{1,1}
+    \end{tikzpicture}}
+\\\\ \Downarrow && \Downarrow \\\\
+    \vc{ 
+    \begin{tikzpicture}[net]
+        \formula[y=1.2]{A}
+        \formula[y=0]{C}
+        \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\psi,\rho\vphantom)}$}},r]{1,1}
+    \end{tikzpicture}}
+    &&
+    \vc{
+    \begin{tikzpicture}[net]
+        \formula[y=1.2]{A}
+        \formula[y=0]{C}
+        \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\psi',\rho'\vphantom)}$}},r]{1,1}
+    \end{tikzpicture}}
+\end{array}
+%
+\qquad\quad
+%
+\begin{array}{l@{\,}l}
+	\rho  &=~ \sigma_A\tau_C\dcom\fix{\sigma_B\tau\subdual B}
+\\ \\
+	\rho' &=~ \sigma_A\tau_C\dcom\fix{(\sigma_B\minus x)\tau\subdual B}
+\\ \\
+	\psi  &=~
+	\vc{
+	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq{A\rho}{C\rho}}{
+	 \left(\vc{
+	  \deduce{\seq{A\sigma}{B\sigma}\vphantom{\dual B}}{\pi\vphantom)}
+	 }\right)\fix{\sigma_B\tau\subdual B}
+	 &
+	 \left(\vc{
+	  \deduce{\seq{\dual B\tau}{C\tau}}{\phi\vphantom)}
+	 }\right)\makebox[0pt][l]{$\fix{\sigma_B\tau\subdual B}$}
+	}}
+\\ \\ \\
+	\psi' &=~ 
+	\vc{\scalebox{0.8}{$
+	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq{A\rho'}{C\rho'}}{
+	 \left(\vc{\infer{\seq{A\sigma}{\exists x.B\sigma\minus x}\vphantom{\dual B}}{
+	  \deduce{\seq{A\sigma}{B\sigma}\vphantom{\dual B}}{\pi\vphantom)}
+	 }}\right)\fix{(\sigma_B\minus x)\tau\subdual B}
+	 &
+	 \left(\vc{\infer{\seq{\forall x.\dual B\tau}{C\tau}}{
+	  \deduce{\seq{\dual B\tau}{C\tau}}{\phi\vphantom)}
+	 }}\right)\makebox[0pt][l]{$\fix{(\sigma_B\minus x)\tau\subdual B}$}
+	}$}}
+	\rule{25pt}{0pt}
+\end{array}
+\]
+Since $x$ is not free in the range of $\tau$, and (by the freshness convention) nor in the range of $\sigma$, we have that $\fix{\sigma_B\tau\subdual B}$ is $\fix{(\sigma_B\minus x)\tau\subdual B}$ plus the substitution $[\sigma(x)/x]$.
+Then $\rho=\rho'$ (as $x$ does not occur in the range of $\sigma_A\tau_C$) and $\psi'$ reduces to $\psi$ in a single cut-elimination step.
+
+\[
+\begin{array}{ccc}
+    \vc{
+    \begin{tikzpicture}[net]
+        \formula[y=3]{A}
+        \formula[y=1.8]{B}
+        \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\pi,\sigma\vphantom)}$}},r]{1,1}
+        \formula[y=1.2]{{\dual B}}
+        \formula[y=0]{\exists x.C}
+        \Vlink[red,label={\makebox[0pt][r]{~$\scriptstyle{\phi,\tau\vphantom)}$~}},l]{1,4}
+    \end{tikzpicture}}
+    & 
+    \begin{array}{c}\\[45pt]\scoal\end{array}
+    &
+    \vc{
+    \begin{tikzpicture}[net]
+        \formula[y=3]{A}
+        \formula[y=1.8]{B}
+        \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\pi,\sigma\vphantom)}$}},r]{1,1}
+        \formula[y=1.2]{{\dual B}}
+        \formula[y=0]{\exists x.C}
+        \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\phi',\tau\minus x\vphantom)}$}},r]{1,1}
+    \end{tikzpicture}}
+\\\\ \Downarrow && \Downarrow \\\\
+    \vc{ 
+    \begin{tikzpicture}[net]
+        \formula[y=1.2]{A}
+        \formula[y=0]{\exists x.C}
+        \Vlink[red,label={\makebox[0pt][r]{~$\scriptstyle{\psi,\rho\vphantom)}$~}},l]{1,4}
+    \end{tikzpicture}}
+    &&
+    \vc{
+    \begin{tikzpicture}[net]
+        \formula[y=1.2]{A}
+        \formula[y=0]{\exists x.C}
+        \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\psi',\rho'\vphantom)}$}},r]{1,1}
+    \end{tikzpicture}}
+\end{array}
+%
+\qquad\quad
+%
+\begin{array}{l@{\,}l}
+	\rho  &=~ \sigma_A\tau_C\dcom\fix{\sigma_B\tau\subdual B}
+\\ \\
+	\rho' &=~ \sigma_A(\tau_C\minus x)\dcom\fix{\sigma_B\tau\subdual B}
+\\ \\
+	\psi &=~
+	\vc{
+	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq{A\rho}{C\rho}}{
+	 \left(\vc{
+	  \Prf\pi{A\sigma}{B\sigma}
+	 }\right)\fix{\sigma_B\tau\subdual B}
+	 &
+	 \left(\vc{
+	  \Prf\phi{\dual B\tau}{C\tau}
+	 }\right)\fix{\sigma_B\tau\subdual B}
+	}}
+\\ \\
+	\psi' &=~
+	\vc{
+	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq{A\rho'}{C\rho'}}{
+	 \left(\vc{
+	  \Prf\pi{A\sigma}{B\sigma}
+	 }\right)\fix{\sigma_B\tau\subdual B}
+	 &
+	 \left(\vc{
+	  \infer{\Seq{\dual B\tau}{\exists x.C(\tau\minus x)}}{\Prf\phi{\dual B\tau}{C\tau}}
+	 }\right)\fix{\sigma_B\tau\subdual B}
+	}}
+\end{array}
+\]
+Observe that since $x$ occurs in $C$ but not $B$, it is not in the domain of $\tau_B$, so that $\tau_B\minus x$ is just $\tau_B$.
+Then $\rho'=\rho\minus x$, and the diagram is closed by a sequentialization step (from left to right) that extends $\psi$ with an existential introduction rule, to a proof equivalent to $\psi'$:
+\[
+	\infer[\!\!\scriptstyle{\qrr?{\rho(x)}}]{\Seq{A\rho'}{\exists x.C\rho'}}{
+	 \Prf\psi{A\rho}{C\rho}
+	}
+\]
+
+There are three further critical pairs
+
+%\end{document}
+
+\begin{proposition}
+If $\net{\lambda_\Sigma}AB$ and $\net{\kappa_\Theta}{\dual B}C$ both coalesce, so does their composition.
+\end{proposition}
+
+\begin{proof}
+By induction on both coalescence sequences.
+In the base case, $\lambda_\Sigma=\{\link[\varnothing]AB\}$ and $\kappa_\Theta=\{\link[\varnothing]{\dual B}C\}$, and the composition is $\net{\{\link[\varnothing]AC\}}AC$.
+
+If
+\end{proof}
+
+\begin{proposition}
+If $\net{\lambda_\Sigma}AB$ sequentializes to $\pi$ and $\net{\kappa_\Theta}{\dual B}C$ to $\phi$ then the composition $(\net{\lambda_\Sigma}AB)\comp(\net{\kappa_\Theta}{\dual B}C)$ sequentializes to a normal form $\psi$ of the proof
+\[
+	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq AC}{
+	 %\prf\pi AB & \prf\phi{\dual B}C
+	 \deduce{\seq AB\vphantom{\dual B}}{\pi}
+	&\deduce{\seq{\dual B}C}{\phi}
+	}
+\]
+\end{proposition}
+
+% --------------------------------------------------
+
+% ==================================================
+
+\newpage
 \appendix
@@
 
-\setcounter{theorem}{\thelemslicecorrect}
+\setcounter{theorem}{\thelemcorrectness}
 \begin{lemma}[Restatement]
-Strict coalescence preserves and reflects slice-correctness.
+Strict coalescence preserves and reflects correctness.
 \end{lemma}
@@
 \begin{proof}
-For a strict coalescence step $L\scoal R$, we will show that the witness pre-net $L$ is slice-correct if and only if $R$ is.
+For a strict coalescence step $L\scoal R$, we will show that the witness pre-net $L$ is correct if and only if $R$ is.
 Let $L=\net{\lambda_\Sigma}AB$ and $R=\net{\kappa_\Theta}AB$.
-We will demonstrate that the left-hand side and right-hand side of each rule belong to the same slice of $\seq AB$, or in the case of $\srr?$, naturally corresponding slices.
+In each case, exact coverage is immediately preserved and reflected.
+For slice-correctness, we will demonstrate that the left-hand side and right-hand side of each rule belong to the same slice of $\seq AB$, or in the case of $\srr?$, naturally corresponding slices.
+For dependency-correctness, we will briefly show how acyclicity of the columns of the involved links is preserved.
 
@@
 
+For dependency-correctness, the column of $\link C{D_i}$ is that of $\link C{D_1{\+}D_2}$ plus $(D_i,\sigma\res{\ex[B]{D_i}})$ itself, which is minimal in the order $\dep$.
+
 	\item
@@
 Then $S\cap \lambda_\Sigma$ is a singleton if and only if $S\cap\kappa_\Theta$ is.
+
+Dependency-correctness is immediate, as above.
 
@@
 
+For dependency-correctness, the column of $\link CD$ is that of $\link[\sigma\minus x]C{\exists x.D}$ plus a pair $(D,\tau)$, which is minimal in $(\dep)$.
+
 	\item
@@
 A slice $S$ of $\seq AB$ contains $\link CD$ if and only if it contains also $\link C{\forall x.D}$, and hence $S\cap\lambda_\Sigma$ is a singleton if and only if $S\cap\kappa_\Theta$ is.
-\qedhere
-\end{itemize}
-\end{proof}
-
-% ..................................................
-
-\setcounter{theorem}{\thelemdependencycorrect}
-\begin{lemma}[Restatement]
-Strict coalescence preserves and reflects dependency-correctness.
-\end{lemma}
-
-\begin{proof}
-For a strict coalescence step $L\scoal R$, we will show that the witness pre-net $L$ is dependency-correct if and only if $R$ is. Again let $L=\net{\lambda_\Sigma}AB$ and $R=\net{\kappa_\Theta}AB$.
-
-\begin{itemize}
-	\item
-$\link C{D_i}\scoal\link C{D_1{\+}D_2}$
-\\
-The column of $\link C{D_i}$ is that of $\link C{D_1{\+}D_2}$ plus $(D_i,\sigma\res{\ex[B]{D_i}})$ itself, which is minimal in the order $\dep$.
-
-	\item
-$\link C{D_1},\link C{D_2}\scoal\link C{D_1{\*}D_2}$
-\\
-Immediate, as above.
-
-	\item
-$\link CD\scoal\link[\sigma\minus x]C{\exists x.D}$
-\\
-The column of $\link CD$ is that of $\link[\sigma\minus x]C{\exists x.D}$ plus a pair $(D,\tau)$, which is minimal in $(\dep)$.
-
-	\item
-$\link CD\scoal\link C{\forall x.D}$
-\\
-The column of $\link CD$ is that of $\link C{\forall x.D}$ plus a pair $(D,\tau)$.
+
+For dependency-correctness, the column of $\link CD$ is that of $\link C{\forall x.D}$ plus a pair $(D,\tau)$.
 The side-condition of the coalescence step is that $x\notin\sigma$; then $x$ does not occur free in any $(X,\rho)$, and $(D,\tau)$ is minimal in $(\dep)$.
@@
 
-\subsection{Composition}
-
-\[
-\begin{array}{ccc}
-	\vc{
-	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\Seq AC}{
-	 \infer[\!\!\scriptstyle{\qrr*}]{\Seq A{B_1\*B_2}\vphantom{\dual B}}{\Prf{\pi_1}A{B_1} & \Prf{\pi_2}A{B_2}}
-	 &&
-	 \infer[\!\!\scriptstyle{\qrr+i}]{\Seq {\dual B_1\+\dual B_2}C}{\Prf\phi{B_i}C}
-	}}
-	&\Rightarrow&
-	\vc{\infer[\!\!\scriptstyle{\mathrm{cut}}]{\Seq AC}{\Prf{\pi_i}A{B_i} && \Prf\phi{\dual B_i}C}}
-\\ \\
-	\vc{
-	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\Seq AC}{
-	 \infer[\!\!\scriptstyle{\qrr?t}]{\Seq A{\exists x.B}}{\Prf\pi A{B[t/x]}}
-	 &&
-	 \infer[\!\!\scriptstyle{\qrr!}]{\Seq {\forall x.\dual B}C}{\Prf\phi{\dual B}C}
-	}}
-	&\Rightarrow&
-	\vc{\infer[\!\!\scriptstyle{\mathrm{cut}}]{\Seq AC}{\Prf\pi A{B[t/x]} && \Prf{\phi[t/x]}{\dual B[t/x]}C}}
-
-\end{array}
-\]
-
-The \defn{domain-preserving composition} of two witness maps $\sigma\dcom\tau$ is the map $(\sigma\tau)\res{\dom\sigma}$.
-
-The \defn{least fixed point} $\fix\sigma$ of a witness map $\sigma$ is the least map $\rho$ satisfying $\rho = \rho\sigma$.
-It is the shortest sequence $\fix\sigma=\sigma\sigma\dots\sigma$ such that no variable is both in the domain and range of $\fix\sigma$.
-Where it is used, in the composition of the witness maps of two links, we will need to demonstrate that it is well defined.
-
-\begin{definition}
-The \defn{composition} of two proof links $\link AB^\pi\comp\link[\tau]{\dual B}C^\phi$ is $\link[\rho]AC^\psi$ where
-\[
-	\rho = \sigma_A\tau_C\dcom\fix{\sigma_B\tau\subdual B}
-\qquad\text{and}\qquad
-	\psi = ~\vcenter{
-	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq {A\rho}{B\rho}}{
-	 \left(\vcenter{\deduce{\seq{A\sigma}{B\sigma}\vphantom{\dual B}}{\vphantom\phi\pi}}\right)\fix{\sigma_B\tau\subdual B}
-	&\left(\vcenter{\deduce{\seq{\dual B\tau}{C\tau}}{\phi}}\right)\fix{\sigma_B\tau\subdual B}
-	}}~.
-\]
-The \defn{composition} of two labelled pre-nets $(\net{\lambda_\Sigma^\Pi}AB)\comp(\net{\kappa_\Theta^\Phi}{\dual B}C)$ is then
-\[
-	\net{\{~\link XY^\pi\comp\link[\tau]{\dual Y}Z^\phi
-		~\mid~
-		\link XY^\pi\in{\lambda_\Sigma^\Pi}
-		~,~
-		\link[\tau]{\dual Y}Z^\phi\in\kappa_\Theta^\Phi~\}
-	}AC~.
-\]
-The composition of two witness pre-nets omits the proof annotations.
-\end{definition}
-
-%	\net{\{~\link[\rho]XZ~\mid~\link XY\in{\lambda_\Sigma}~,~\link[\tau]{\dual Y}Z\in\kappa_\Theta~,~\rho = (\sigma\cyc\tau)\res{\ex AX\,\cup\,\ex CZ}~\}~}AC
-%~\rho=\sigma_A\tau_{\smash{\,\dual{\!B}}\vphantom B}\cup\tau_C\sigma_B~
-%(\sigma\res{\ex AX})(\tau\res{\ex{\dual B}{\dual Y}})\cup(\tau\res{\ex CZ})(\sigma\res{\ex BY})
-
-In the following we will demonstrate that composition gives the desired result: if a net $L$ sequentializes to $\pi$ and $R$ to $\phi$, then $L\comp R$ sequentializes to a normal form of the composition of $\pi$ and $\phi$ with a cut.
-To this end we will explore how composition and sequentialization interact.
-We will consider the critical pairs of sequentialization with composition, and demonstrate that how they are resolved.
-
-The first critical pair of composition (downward as $\Rightarrow$) and sequentialization is the following.
-We consider the composition of pre-nets on $\seq AB$ and $\seq{\dual B}C$ where $B=B_1\*B_2$, with a synchronized sequentialization step on both pre-nets.
-\[
-\begin{array}{ccc}
-    \vc{
-    \begin{tikzpicture}[net]
-        \formula[y=3]{A}
-        \formula[y=1.8]{B*{_1}\*B*{_2}}
-        \Vlink[red,label={$\scriptstyle{\pi,\sigma\vphantom)~}$},l]{[-2]1,1}
-        \Vlink[red,label={$\scriptstyle{~\pi'\!,\sigma\vphantom)}$},r]{[2]1,3}
-        \formula[y=1.2]{{\dual B}*{_1}\+{\dual B}*{_2}}
-        \formula[y=0]{C}
-        \Vlink[red,label={$\scriptstyle{\phi,\tau\vphantom)~}$},l]{1,1}
-    \end{tikzpicture}}
-    & 
-    \begin{array}{c}\scoal\\[40pt]\scoal\end{array}
-    &
-    \vc{
-    \begin{tikzpicture}[net]
-        \formula[y=3]{A}
-        \formula[y=1.8]{B*{_1}\*B*{_2}}
-        \Vlink[red,label={$\scriptstyle{\pi''\!\!,\sigma\vphantom)~}$},l]{1,2}
-        \formula[y=1.2]{{\dual B}*{_1}\+{\dual B}*{_2}}
-        \formula[y=0]{C}
-        \Vlink[red,label={$\scriptstyle{\phi'\!,\tau\vphantom)~}$},l]{2,1}
-    \end{tikzpicture}}
-\\\\[-5pt] \Downarrow && \Downarrow \\\\[-5pt]
-    \vc{
-    \begin{tikzpicture}[net]
-        \formula[y=1.2]{A}
-        \formula[y=0]{C}
-        \Vlink[red,label={\makebox[0pt][r]{$\scriptstyle{\psi,\rho\vphantom)~}$}},l]{1,1}
-    \end{tikzpicture}}
-    &&
-    \vc{
-    \begin{tikzpicture}[net]
-        \formula[y=1.2]{A}
-        \formula[y=0]{C}
-        \Vlink[red,label={\makebox[0pt][r]{$\scriptstyle{\psi',\rho'\vphantom)~}$}},l]{1,1}
-    \end{tikzpicture}}
-\end{array}
-\qquad
-\begin{array}{l@{\,}l}
-	\rho  &=~ \sigma_A\tau_C\dcom\fix{\sigma_B\tau\subdual B} 
-\\ \\
-	\rho' &=~ \sigma_A\tau_C\dcom\fix{\sigma_{B_1}\tau\subdual{B_1}}
-\\ \\
-	\psi &=~\vc{
-	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq{A\rho}{C\rho}}{
-	 \left(\vc{
-	  \deduce{\seq{A\sigma}{B_1\sigma}\vphantom{\dual B_1}}{\pi\vphantom)}
-	 }\right)\fix{\sigma_{B_1}\tau\subdual{B_1}}
-	 &
-	 \left(\vc{
-	  \deduce{\seq{\dual B_1\tau}{C\tau}}{\phi\vphantom)}
-	 }\right)\makebox[0pt][l]{$\fix{\sigma_{B_1}\tau\subdual{B_1}}$}
-	}}
-\\ \\ \\
-	\psi' &= ~
-	\vc{\scalebox{0.75}{$
-	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq{A\rho'}{C\rho'}}{
-	 \left(\vc{\infer{\seq{A\sigma}{B_1\sigma\*B_2\sigma}\vphantom{\dual B}}{
-	  \deduce{\seq{A\sigma}{B_1\sigma}\vphantom{\dual B}}{\pi\vphantom)}
-	  &
-	  \deduce{\seq{A\sigma}{B_2\sigma\vphantom{\dual B}}}{\pi'\vphantom)}
-	 }}\right)\fix{\sigma_B\tau\subdual B}
-	 &
-	 \left(\vc{\infer{\seq{\dual B_1\tau\+\dual B_2\tau}{C\tau}}{
-	  \deduce{\seq{\dual B_1\tau}{C\tau}}{\phi\vphantom)}
-	 }}\right)\makebox[0pt][l]{$\fix{\sigma_B\tau\subdual B}$}
-	}$}\kern5pt}
-\end{array}
-\]
-Since the existential covers of $B$ and $B_1$ are the same, $\sigma_B\tau\subdual B = \sigma_{B_1}\tau\subdual{B_1}$ and $\rho=\rho'$.
-It then follows that $\psi'$ cut-eliminates in one step to $\psi$.
-
-The next critical pair is the following.
-\[
-\begin{array}{ccc}
-    \vc{
-    \begin{tikzpicture}[net]
-        \formula[y=3]{A}
-        \formula[y=1.8]{\exists x.B}
-        \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\pi,\sigma\vphantom)}$}},r]{1,4}
-        \formula[y=1.2]{\forall x.{\dual B}}
-        \formula[y=0]{C}
-        \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\phi,\tau\vphantom)}$}},r]{4,1}
-    \end{tikzpicture}}
-    & 
-    \begin{array}{c}\scoal\\[40pt]\stackrel{x\,\notin\,\tau\vphantom)}\scoal\end{array}
-    &
-    \vc{
-    \begin{tikzpicture}[net]
-        \formula[y=3]{A}
-        \formula[y=1.8]{\exists x.B}
-        \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\pi',\sigma\minus x\vphantom)}$}},r]{1,1}
-        \formula[y=1.2]{\forall x.{\dual B}}
-        \formula[y=0]{C}
-        \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\phi',\tau\vphantom)}$}},r]{1,1}
-    \end{tikzpicture}}
-\\\\ \Downarrow && \Downarrow \\\\
-    \vc{ 
-    \begin{tikzpicture}[net]
-        \formula[y=1.2]{A}
-        \formula[y=0]{C}
-        \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\psi,\rho\vphantom)}$}},r]{1,1}
-    \end{tikzpicture}}
-    &&
-    \vc{
-    \begin{tikzpicture}[net]
-        \formula[y=1.2]{A}
-        \formula[y=0]{C}
-        \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\psi',\rho'\vphantom)}$}},r]{1,1}
-    \end{tikzpicture}}
-\end{array}
-%
-\qquad\quad
-%
-\begin{array}{l@{\,}l}
-	\rho  &=~ \sigma_A\tau_C\dcom\fix{\sigma_B\tau\subdual B}
-\\ \\
-	\rho' &=~ \sigma_A\tau_C\dcom\fix{(\sigma_B\minus x)\tau\subdual B}
-\\ \\
-	\psi  &=~
-	\vc{
-	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq{A\rho}{C\rho}}{
-	 \left(\vc{
-	  \deduce{\seq{A\sigma}{B\sigma}\vphantom{\dual B}}{\pi\vphantom)}
-	 }\right)\fix{\sigma_B\tau\subdual B}
-	 &
-	 \left(\vc{
-	  \deduce{\seq{\dual B\tau}{C\tau}}{\phi\vphantom)}
-	 }\right)\makebox[0pt][l]{$\fix{\sigma_B\tau\subdual B}$}
-	}}
-\\ \\ \\
-	\psi' &=~ 
-	\vc{\scalebox{0.8}{$
-	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq{A\rho'}{C\rho'}}{
-	 \left(\vc{\infer{\seq{A\sigma}{\exists x.B\sigma\minus x}\vphantom{\dual B}}{
-	  \deduce{\seq{A\sigma}{B\sigma}\vphantom{\dual B}}{\pi\vphantom)}
-	 }}\right)\fix{(\sigma_B\minus x)\tau\subdual B}
-	 &
-	 \left(\vc{\infer{\seq{\forall x.\dual B\tau}{C\tau}}{
-	  \deduce{\seq{\dual B\tau}{C\tau}}{\phi\vphantom)}
-	 }}\right)\makebox[0pt][l]{$\fix{(\sigma_B\minus x)\tau\subdual B}$}
-	}$}}
-	\rule{25pt}{0pt}
-\end{array}
-\]
-Since $x$ is not free in the range of $\tau$, and (by the freshness convention) nor in the range of $\sigma$, we have that $\fix{\sigma_B\tau\subdual B}$ is $\fix{(\sigma_B\minus x)\tau\subdual B}$ plus the substitution $[\sigma(x)/x]$.
-Then $\rho=\rho'$ (as $x$ does not occur in the range of $\sigma_A\tau_C$) and $\psi'$ reduces to $\psi$ in a single cut-elimination step.
-
-\[
-\begin{array}{ccc}
-    \vc{
-    \begin{tikzpicture}[net]
-        \formula[y=3]{A}
-        \formula[y=1.8]{B}
-        \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\pi,\sigma\vphantom)}$}},r]{1,1}
-        \formula[y=1.2]{{\dual B}}
-        \formula[y=0]{\exists x.C}
-        \Vlink[red,label={\makebox[0pt][r]{~$\scriptstyle{\phi,\tau\vphantom)}$~}},l]{1,4}
-    \end{tikzpicture}}
-    & 
-    \begin{array}{c}\\[45pt]\scoal\end{array}
-    &
-    \vc{
-    \begin{tikzpicture}[net]
-        \formula[y=3]{A}
-        \formula[y=1.8]{B}
-        \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\pi,\sigma\vphantom)}$}},r]{1,1}
-        \formula[y=1.2]{{\dual B}}
-        \formula[y=0]{\exists x.C}
-        \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\phi',\tau\minus x\vphantom)}$}},r]{1,1}
-    \end{tikzpicture}}
-\\\\ \Downarrow && \Downarrow \\\\
-    \vc{ 
-    \begin{tikzpicture}[net]
-        \formula[y=1.2]{A}
-        \formula[y=0]{\exists x.C}
-        \Vlink[red,label={\makebox[0pt][r]{~$\scriptstyle{\psi,\rho\vphantom)}$~}},l]{1,4}
-    \end{tikzpicture}}
-    &&
-    \vc{
-    \begin{tikzpicture}[net]
-        \formula[y=1.2]{A}
-        \formula[y=0]{\exists x.C}
-        \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\psi',\rho'\vphantom)}$}},r]{1,1}
-    \end{tikzpicture}}
-\end{array}
-%
-\qquad\quad
-%
-\begin{array}{l@{\,}l}
-	\rho  &=~ \sigma_A\tau_C\dcom\fix{\sigma_B\tau\subdual B}
-\\ \\
-	\rho' &=~ \sigma_A(\tau_C\minus x)\dcom\fix{\sigma_B\tau\subdual B}
-\\ \\
-	\psi &=~
-	\vc{
-	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq{A\rho}{C\rho}}{
-	 \left(\vc{
-	  \Prf\pi{A\sigma}{B\sigma}
-	 }\right)\fix{\sigma_B\tau\subdual B}
-	 &
-	 \left(\vc{
-	  \Prf\phi{\dual B\tau}{C\tau}
-	 }\right)\fix{\sigma_B\tau\subdual B}
-	}}
-\\ \\
-	\psi' &=~
-	\vc{
-	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq{A\rho'}{C\rho'}}{
-	 \left(\vc{
-	  \Prf\pi{A\sigma}{B\sigma}
-	 }\right)\fix{\sigma_B\tau\subdual B}
-	 &
-	 \left(\vc{
-	  \infer{\Seq{\dual B\tau}{\exists x.C(\tau\minus x)}}{\Prf\phi{\dual B\tau}{C\tau}}
-	 }\right)\fix{\sigma_B\tau\subdual B}
-	}}
-\end{array}
-\]
-Observe that since $x$ occurs in $C$ but not $B$, it is not in the domain of $\tau_B$, so that $\tau_B\minus x$ is just $\tau_B$.
-Then $\rho'=\rho\minus x$, and the diagram is closed by a sequentialization step (from left to right) that extends $\psi$ with an existential introduction rule, to a proof equivalent to $\psi'$:
-\[
-	\infer[\!\!\scriptstyle{\qrr?{\rho(x)}}]{\Seq{A\rho'}{\exists x.C\rho'}}{
-	 \Prf\psi{A\rho}{C\rho}
-	}
-\]
-
-There are three further critical pairs
-
-%\end{document}
-
-\begin{proposition}
-If $\net{\lambda_\Sigma}AB$ and $\net{\kappa_\Theta}{\dual B}C$ both coalesce, so does their composition.
-\end{proposition}
-
-\begin{proof}
-By induction on both coalescence sequences.
-In the base case, $\lambda_\Sigma=\{\link[\varnothing]AB\}$ and $\kappa_\Theta=\{\link[\varnothing]{\dual B}C\}$, and the composition is $\net{\{\link[\varnothing]AC\}}AC$.
-
-If
-\end{proof}
-
-\begin{proposition}
-If $\net{\lambda_\Sigma}AB$ sequentializes to $\pi$ and $\net{\kappa_\Theta}{\dual B}C$ to $\phi$ then the composition $(\net{\lambda_\Sigma}AB)\comp(\net{\kappa_\Theta}{\dual B}C)$ sequentializes to a normal form $\psi$ of the proof
-\[
-	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq AC}{
-	 %\prf\pi AB & \prf\phi{\dual B}C
-	 \deduce{\seq AB\vphantom{\dual B}}{\pi}
-	&\deduce{\seq{\dual B}C}{\phi}
-	}
-\]
-\end{proposition}
-
 %\end{document}

### 2018-01-10 ALL1.tex
new overrightharpoon

@@
 \usepackage{graphicx}
+
+\usepackage{tikz}
+\usetikzlibrary{arrows}
 
@@
 
+\newcommand\Seq{\vphantom(\seq}
+\newcommand\Prf[3]{\deduce{\Seq{#2}{#3}}{\vphantom(#1}}
+
 % ===== Nets
@@
 \newcommand\res[1]{|_{#1}}
-\newcommand\fix[1]{\overrightharpoon{#1}}
+\newcommand\fix[2][2pt]{\overrightharpoon[#1]{#2}}
 \newcommand\dcom{\mathbin\cdot}
@@
 
+\renewcommand\overrightharpoon[2][2pt]{
+\begin{tikzpicture}[baseline=0]
+	\node[inner sep=0pt,outer sep=0pt,anchor=base] (x) at (0,0) {$#2$};
+	\draw[-left to] ($(x.north west) + (0pt,#1)$) -- ($(x.north east) + (0pt,#1)$);
+\end{tikzpicture}}
+
 \makeatother
@@
 % ============================== CONTENT
-
-\newcommand\Seq{\vphantom(\seq}
-\newcommand\Prf[3]{\deduce{\Seq{#2}{#3}}{\vphantom(#1}}
 
@@
 
-\newcounter{lemcorrectness}
-\setcounter{lemcorrectness}{\thetheorem}
+\newcounter{lemcorrect}
+\setcounter{lemcorrect}{\thetheorem}
 \begin{lemma}
-\label{lem:correctness}
+\label{lem:correct}
 Strict coalescence preserves and reflects correctness.
@@
 \label{lem:coalescence applies}
-In a correct witness pre-net a coalescence step applies, unless it has already been coalesced.
+To a correct witness pre-net a coalescence step applies, unless it has already been coalesced.
 \end{lemma}
@@
 It is also dependency-correct: the column of $\link[\varnothing]AB$ is the set $\{(A,\varnothing),(B,\varnothing)\}$, where $A$ and $B$ are unrelated in $(\dep)$.
-For the inductive step, by Lemma~\ref{lem:preservation} coalescence reflects correctness, so that any pre-net along the coalescence path is correct, in particular $\net{\lambda_\Sigma}AB$.
+For the inductive step, by Lemma~\ref{lem:correct} coalescence reflects correctness, so that any pre-net along the coalescence path is correct, in particular $\net{\lambda_\Sigma}AB$.
 
@@
 
+\begin{figure}
 \[
@@
 	\vc{\infer[\!\!\scriptstyle{\mathrm{cut}}]{\Seq AC}{\Prf\pi A{B[t/x]} && \Prf{\phi[t/x]}{\dual B[t/x]}C}}
-
 \end{array}
 \]
+\caption{\all1 cut-elimination steps}
+\label{fig:cut-elim}
+\end{figure}
 
@@
 \begin{definition}
-The \defn{composition} of two proof links $\link AB^\pi\comp\link[\tau]{\dual B}C^\phi$ is $\link[\rho]AC^\psi$ where
+The \defn{composition} $\link AB^\pi\comp\link[\tau]{\dual B}C^\phi$ of two proof links is $\link[\rho]AC^\psi$ where
 \[
@@
 \end{definition}
+
+The composition of two links is strongly related to composition of strategies in game semantics.
+There, two strategies on $\seq AB$ and $\seq{\dual B}C$ are composed by \emph{interaction} on the interface of $B$ and $\dual B$, and subsequently \emph{hiding} that interaction.
 
@@
 \]
-Since $x$ is not free in the range of $\tau$, and (by the freshness convention) nor in the range of $\sigma$, we have that $\fix{\sigma_B\tau\subdual B}$ is $\fix{(\sigma_B\minus x)\tau\subdual B}$ plus the substitution $[\sigma(x)/x]$.
+Since $x$ is not free in the range of $\tau$, and (by the freshness convention) nor in the range of $\sigma$, we have that $\fix{\sigma_B\tau\subdual B}$ is $\fix[1pt]{(\sigma_B\minus x)\tau\subdual B}$ plus the substitution $[\sigma(x)/x]$.
 Then $\rho=\rho'$ (as $x$ does not occur in the range of $\sigma_A\tau_C$) and $\psi'$ reduces to $\psi$ in a single cut-elimination step.
@@
 
-\setcounter{theorem}{\thelemcorrectness}
+\setcounter{theorem}{\thelemcorrect}
 \begin{lemma}[Restatement]

### 2018-01-10 ALL1.tex
lutz comments

--- 2018-01-09 ALL1.tex
@@
 We define it as $\sigma=[t_1/x_1,\dots,t_n/x_n]$, where its \defn{domain} $\dom\sigma$ is $\{x_1,\dots,x_n\}$.
-We abbreviate by $y\in\sigma$ that a variable $y$ occurs free in its the range, $y\in\fv(t_i)$ for some $i\leq n$.
-The map $\sigma\minus x$ is undefined on $x$ and otherwise as $\sigma$, we write $\sigma\res V$ for the restriction of $\sigma$ to a set of variables $V$, and $\varnothing$ is the \defn{empty} witness map.
-%
-We write $A\sigma$ for the application of the substitutions in $\sigma$ to the formula $A$, and $\pi\sigma$ for its application to the proof $\pi$, where it is applied to each formula in the proof.
+We abbreviate by $y\in\sigma$ that a variable $y$ occurs free in the range of~$\sigma$, i.e., $y\in\fv(t_i)$ for some $i\leq n$.
+The map $\sigma\minus x$ is undefined on $x$ and otherwise as $\sigma$, we write $\sigma\res V$ for the restriction of $\sigma$ to a set of variables $V$, and $\varnothing$ for the \defn{empty} witness map.
+%
+We write $A\sigma$ for the application of the substitutions in $\sigma$ to the formula $A$, and $\pi\sigma$ for its application to the proof $\pi$, where it is applied to each formula in the proof \lutz{also to the existential witnesses?}.
 The \defn{composition} of two maps is written $\sigma\tau$, where $A(\sigma\tau)=(A\sigma)\tau$.
@@
 Hence we need to maintain the separation of the conclusion $\seq AB$ into the substitutions $\sigma$ and the subformulas $A'$ and $B'$ of the conclusion of the proof net.
+\lutz{every referee will ask for an example here.}
 
@@
 
+\lutz{I guess there should be an example here.}
+
 \begin{definition}
@@
 
+\lutz{why in the appendix? is it too long such that it does not fit in the page limit?}
+
 \newcounter{lemcoalescenceapplies}
@@
 
+\lutz{that statement is not clear?}
+
 \begin{proof}
@@
 \end{proof}
+
+\lutz{labels: preservation and correctness one or two lemmas?}
 
@@
 
+\lutz{why the fixpoint?}
+
 In the following we will demonstrate that composition gives the desired result: if a net $L$ sequentializes to $\pi$ and $R$ to $\phi$, then $L\comp R$ sequentializes to a normal form of the composition of $\pi$ and $\phi$ with a cut.
@@
 We will consider the critical pairs of sequentialization with composition, and demonstrate that how they are resolved.
+
+\lutz{some itemizing environment?}
 
@@
 \]
-Since $x$ is not free in the range of $\tau$, and (by the freshness convention) nor in the range of $\sigma$, we have that $\fix{\sigma_B\tau\subdual B}$ is $\fix{(\sigma_B\minus x)\tau\subdual B}$ plus the substitution $[\sigma(x)/x]$.
+Since $x$ is not free in the range of $\tau$, and (by the freshness convention) nor \lutz{not?} in the range of $\sigma$, we have that $\fix{\sigma_B\tau\subdual B}$ is $\fix{(\sigma_B\minus x)\tau\subdual B}$ plus the substitution $[\sigma(x)/x]$.
 Then $\rho=\rho'$ (as $x$ does not occur in the range of $\sigma_A\tau_C$) and $\psi'$ reduces to $\psi$ in a single cut-elimination step.
@@
 
+\todo{add them}
+
 %\end{document}
@@
 If
+\todo{}
 \end{proof}
@@
 
+\
+\begin{proof}
+  \todo{}
+\end{proof}
 % --------------------------------------------------
@@
 %
-\lutz{something is confusing here.
+%% \lutz{something is confusing here.
 It seems you are using different notions of slice.
 Above it says that correctness means that slices are singletons, and here you imply that slices contain more than one element.}
-%
-\willem{Indeed. A slice of a NET is singleton; a slice of FORMULA or SEQUENT need not be.}
+%% %
+%% \willem{Indeed. A slice of a NET is singleton; a slice of FORMULA or SEQUENT need not be.}
 %
@@
 \\
-A slice $S$ of $\seq AB$ contains $\link C{D_1{\*}D_2}$ if and only if it contains either of $\link C{D_1}$ or $\link C{D_2}$, and may not contain both.
+A slice $S$ of $\seq AB$ contains $\link C{D_1{\*}D_2}$ if and only if it contains either of $\link C{D_1}$ or $\link C{D_2}$, and may not\lutz{may not or cannot?} contain both.
 Then $S\cap \lambda_\Sigma$ is a singleton if and only if $S\cap\kappa_\Theta$ is.
@@
 Then $S\cap \lambda_\Sigma$ is the singleton $\{\link CD\}$ if and only if $S\cap\kappa_\Theta$ is $\{\link[\sigma\minus x]C{\exists x.D}\}$, where it should be observed that if $t$ is also a witness to $x$ in some other slice of $R$, then $t\in\Theta(x)$ and in fact $S=S'$.
+\lutz{?}
 

### 2018-01-11 ALL1.tex
bib + some stuff
small fixes

--- 2018-01-10 ALL1.tex
@@
 \cite{Girard-1996}
-\cite{Hu-99}
+\cite{Hu-1999}
 \cite{Galmiche-2000} % ALL connection net (Def 6.11.)
@@
 We define it as $\sigma=[t_1/x_1,\dots,t_n/x_n]$, where its \defn{domain} $\dom\sigma$ is $\{x_1,\dots,x_n\}$.
-We abbreviate by $y\in\sigma$ that a variable $y$ occurs free in its the range, $y\in\fv(t_i)$ for some $i\leq n$.
-The map $\sigma\minus x$ is undefined on $x$ and otherwise as $\sigma$, we write $\sigma\res V$ for the restriction of $\sigma$ to a set of variables $V$, and $\varnothing$ is the \defn{empty} witness map.
-%
-We write $A\sigma$ for the application of the substitutions in $\sigma$ to the formula $A$, and $\pi\sigma$ for its application to the proof $\pi$, where it is applied to each formula in the proof.
+We abbreviate by $y\in\sigma$ that a variable $y$ occurs free in the range of~$\sigma$, i.e., $y\in\fv(t_i)$ for some $i\leq n$.
+The map $\sigma\minus x$ is undefined on $x$ and otherwise as $\sigma$, we write $\sigma\res V$ for the restriction of $\sigma$ to a set of variables $V$, and $\varnothing$ for the \defn{empty} witness map.
+%
+We write $A\sigma$ for the application of the substitutions in $\sigma$ to the formula $A$, and $\pi\sigma$ for its application to the proof $\pi$, where it is applied to each formula in the proof, and to each existential witness $t$ recorded with a rule $\qrr?t$.
 The \defn{composition} of two maps is written $\sigma\tau$, where $A(\sigma\tau)=(A\sigma)\tau$.
@@
 \label{lem:coalescence applies}
-To a correct witness pre-net a coalescence step applies, unless it has already been coalesced.
+To a correct witness pre-net $\net{\lambda_\Sigma}AB$ a coalescence step applies, unless it is fully coalesced already, $\lambda_\Sigma=\{\link[\varnothing]AB\}$.
 \end{lemma}
+
+\lutz{that statement is not clear?}
 
@@
 
+\cite{Mimram-2011}
+
+\lutz{why the fixpoint?}
+
+\todo{example: $\forall x.\exists y.\forall z.P$ with $[f(x)/y]$ cut against $\exists x.\forall y.\exists z.\dual P$ with $[a/x,g(y)/z]$.}
+
 In the following we will demonstrate that composition gives the desired result: if a net $L$ sequentializes to $\pi$ and $R$ to $\phi$, then $L\comp R$ sequentializes to a normal form of the composition of $\pi$ and $\phi$ with a cut.
@@
 \]
+
 Since $x$ is not free in the range of $\tau$, and (by the freshness convention) nor in the range of $\sigma$, we have that $\fix{\sigma_B\tau\subdual B}$ is $\fix[1pt]{(\sigma_B\minus x)\tau\subdual B}$ plus the substitution $[\sigma(x)/x]$.
 Then $\rho=\rho'$ (as $x$ does not occur in the range of $\sigma_A\tau_C$) and $\psi'$ reduces to $\psi$ in a single cut-elimination step.
+
+\willem{Dominic:plz check grammar above.}
 
@@
 
+\
+\begin{proof}
+  \todo{}
+\end{proof}
 % --------------------------------------------------
+
+\bibliography{ALL1}
 
@@
 \\
-A slice $S$ of $\seq AB$ contains $\link C{D_1{\*}D_2}$ if and only if it contains either of $\link C{D_1}$ or $\link C{D_2}$, and may not contain both.
+A slice $S$ of $\seq AB$ contains $\link C{D_1{\*}D_2}$ if and only if it contains either of $\link C{D_1}$ or $\link C{D_2}$, and cannot contain both.
 Then $S\cap \lambda_\Sigma$ is a singleton if and only if $S\cap\kappa_\Theta$ is.
@@
 Then $S\cap \lambda_\Sigma$ is the singleton $\{\link CD\}$ if and only if $S\cap\kappa_\Theta$ is $\{\link[\sigma\minus x]C{\exists x.D}\}$, where it should be observed that if $t$ is also a witness to $x$ in some other slice of $R$, then $t\in\Theta(x)$ and in fact $S=S'$.
+\lutz{?}
+\todo{Explain the witness sets better; refer to 1st case above; }
 
@@
 The step $\link AD\scoal\link A{\forall x.D}$ applies if $x\notin\sigma$.
+By way of contradiction, assume $x\in\sigma$.
 The column of $\link AD$ contains $(D,\sigma_D)$ and $(\forall x.D,\tau)$ where $\tau=\sigma\res{\ex[B]{\forall x.D}}$.
 By the exact coverage condition, $\sigma=\sigma_A\cup\sigma_D$, and since the existential variables in $D$ and $\forall x.D$ are the same, $\ex[B]D=\ex[B]{\forall x.D}$, so that $\tau=\sigma_D$.
-(Note that since $\sigma_A=\varnothing$, we get $\sigma=\sigma_D=\tau$, but this is not essential to the argument.) If $x\in\sigma$ then $x\in\tau$, and in the column of $\link AD$ we would have $(\forall x.D,\tau)\dep(D,\tau)$ since $D$ occurs as $\forall x.D$.
+(Note that since $\sigma_A=\varnothing$, we get $\sigma=\sigma_D=\tau$, but this is not essential to the argument.) Since $x\in\sigma$ we have $x\in\tau$, and in the column of $\link AD$ we have $(\forall x.D,\tau)\dep(D,\tau)$ since $D$ occurs as $\forall x.D$.
 But we already have $(D,\tau)\dep(\forall x.D,\tau)$ because $D\sub\forall x.D$, contradicting antisymmetry of $(\dep)$.
@@
 
-\bibliography{ALL1}
-
 \end{document}

### 2018-01-13 ALL1.tex
composition finalised

@@
 
-\subjclass{Dummy classification -- please refer to \url{http://www.acm.org/about/class/ccs98-html}}% mandatory: Please choose ACM 1998 classifications from http://www.acm.org/about/class/ccs98-html .
-E.g., cite as "F.1.1 Models of Computation".
-\keywords{Linear logic, Proof nets}
+\subjclass{F.4.1 [Mathematical logic and formal languages]: Mathematical logic--Proof theory}
+\keywords{Linear logic, First-order logic, Proof nets}
 
@@
 \begin{abstract}
-
+We extend proof nets for additive linear logic with first-order quantification.
+
+We present two versions of our proof nets.
+One, called witness nets, retains explicit witnessing information to existential quantification.
+For the other, called unification nets, this information is absent but can be reconstructed through unification.
+Unification nets embody a main contribution of the paper: the observation that first-order witnessing information can be left implicit, and reconstructed effectively.
+
+Witness nets are canonical for first-order additive sequent calculus. Unification nets in addition factor out any inessential choice for existential witnesses. 
+Both notions of proof net are defined through coalescence (the additive version of multiplicative contractibility), and for witness nets a geometric correctness criterion is provided.
+Both feature a global, one-shot composition operation.
 \end{abstract}
@@
 
-\lutz{that statement is not clear?}
-
 \begin{proof}
@@
 \begin{corollary}
+\label{cor:strong coalescence}
 A correct witness pre-net strongly strict-coalesces.
@@
 To this end we will explore how composition and sequentialization interact.
-We will consider the critical pairs of sequentialization with composition, and demonstrate that how they are resolved.
+We will consider the critical pairs of sequentialization with composition, and demonstrate how they are resolved.
 
@@
 
-\willem{Dominic:plz check grammar above.}
+\willem{Dominic: plz check grammar above.}
 
@@
 
-There are three further critical pairs
-
-\todo{add them}
-
-%\end{document}
+There are three further critical pairs, for a proof net on $\seq AB$ composed with one on $\seq {\dual B}{C_1{\+}C_2}$, one on $\seq {\dual B}{C_1{\*}C_2}$, and one on $\seq {\dual B}{\forall x.C}$.
+These converge as the one above.
 
 \begin{proposition}
-If $\net{\lambda_\Sigma}AB$ and $\net{\kappa_\Theta}{\dual B}C$ both coalesce, so does their composition.
+If proof nets $\net{\lambda_\Sigma}AB$ and $\net{\kappa_\Theta}{\dual B}C$ sequentialize to $\pi$ and $\phi$ respectively, then their composition $(\net{\lambda_\Sigma}AB)\comp(\net{\kappa_\Theta}{\dual B}C)$ sequentializes to a normal form $\psi$ of the proof
+\[
+	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq AC}{
+	 \Prf\pi AB & \Prf\phi{\dual B}C
+	}
+\]
 \end{proposition}
@@
 \begin{proof}
-By induction on both coalescence sequences.
-In the base case, $\lambda_\Sigma=\{\link[\varnothing]AB\}$ and $\kappa_\Theta=\{\link[\varnothing]{\dual B}C\}$, and the composition is $\net{\{\link[\varnothing]AC\}}AC$.
-
-If
-\todo{}
+By Corollary~\ref{cor:strong coalescence} the proof nets $L=\net{\lambda_\Sigma}AB$ and $R=\net{\kappa_\Theta}{\dual B}C$ strongly coalesce.
+We may then interleave their coalescence sequences as follows: if a synchronized step in $L$ and $R$ on the interface $B$ and $\dual B$ is available, apply it; otherwise perform steps in $L$ on $A$ and in $R$ on $C$ until it is.
+This gives the following combined sequence.
+\[
+\begin{array}{c@{~}c@{~}c@{~}l@{~}c@{~}l@{~}c@{~}l@{~}c}
+	L &{}={}& L_1 & ~\scoal^?~ & L_2 & ~\scoal^?~ & \dots & ~\scoal^?~ & L_n 
+\\
+	R &{}={}& R_1 & ~\scoal^?~ & R_2 & ~\scoal^?~ & \dots & ~\scoal^?~ & R_n 
+\\[5pt]
+	\Downarrow && \Downarrow && \Downarrow &&&& \Downarrow 
+\\[5pt]
+	L\comp R & = & L_1\comp R_1 & ~\scoal~ & L_2\comp R_2 & ~\scoal~ & \dots & ~\scoal~ & L_n\comp R_n
+\end{array}
+\]
+(Here, $(\scoal^?)$ is the relation $(\scoal)\cup(=)$, but we assume that at least $L_i\scoal L_{i+1}$ or $R_i\scoal R_{i+1}$.)
+%
+The path along the top and right of this diagram sequentializes $L$ to $\pi'$ and $R$ to $\phi'$ (equivalent to $\pi$ and $\phi$ respectively), and then composes to $L_n\comp R_n = \net{\{\link[\varnothing]AC^{\psi'}\}}AC$ with
+%
+\[
+	\psi' = \vc{\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq AC}{\Prf{\pi'}AB & \Prf{\phi'}{\dual B}C}}~.
+\]
+
+Each square of the diagram converges as one of the critical pairs of sequentialization and composition discussed above.
+Then each path along the diagram from top left ($L$ and $R$) to bottom right $(L_n\comp R_n)$ gives a sequentialization, with cuts, of $L_n\comp R_n$.
+Let the path taking the vertical step from $L_i$ and $R_i$ to $L_i\comp R_i$ sequentialize to $\psi_i$, so that $\psi_n=\psi'$.
+By the way each square converges, we have that $\psi_i$ is reached from $\psi_{i+1}$ by a cut-elimination or permutation step.
+
+Finally, in $L$ and $R$ every link is an axiom link.
+Any link in $L\comp R$ is composed from two links $\link ab$ in $L$ and $\link[\tau]{\dual b}c$ in $R$, which yields $\link[\rho]ac$ where $\rho = \sigma_a\tau_c\dcom\fix{\sigma_b\tau\subdual b}$.
+This sequentializes to the axiom $\infer{\seq{a\rho}{c\rho}}{}$, which is in normal form.
+Then $L\comp R$ is a proof net (it has an axiom linking and it coalesces), and it sequentializes to a proof in normal form which sequentializes (up to permutations) to $\psi'$.
+%
+%which sequentialize respectively to. 
+%\[
+%	\infer{\seq{a\sigma}{b\sigma}}{} 
+%	\qquad\text{and}\qquad
+%	\infer{\seq{\dual b\tau}{c\tau}}{}~.
+%\]
+%We have the link 
 \end{proof}
 
-\begin{proposition}
-If $\net{\lambda_\Sigma}AB$ sequentializes to $\pi$ and $\net{\kappa_\Theta}{\dual B}C$ to $\phi$ then the composition $(\net{\lambda_\Sigma}AB)\comp(\net{\kappa_\Theta}{\dual B}C)$ sequentializes to a normal form $\psi$ of the proof
-\[
-	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq AC}{
-	 %\prf\pi AB & \prf\phi{\dual B}C
-	 \deduce{\seq AB\vphantom{\dual B}}{\pi}
-	&\deduce{\seq{\dual B}C}{\phi}
-	}
-\]
-\end{proposition}
-
-\
-\begin{proof}
-  \todo{}
-\end{proof}
 % --------------------------------------------------
@@
 \begin{lemma}[Restatement]
-In a correct witness pre-net a coalescence step applies, unless it has already been coalesced.
+To a correct witness pre-net $\net{\lambda_\Sigma}AB$ a coalescence step applies, unless it is fully coalesced already, $\lambda_\Sigma=\{\link[\varnothing]AB\}$.
 \end{lemma}
@@
 $ \hspace*{20pt}
+
+\begin{proposition}
+If $\net{\lambda_\Sigma}AB$ and $\net{\kappa_\Theta}{\dual B}C$ both coalesce, so does their composition.
+\end{proposition}
+
+\begin{proof}
+By induction on both coalescence sequences.
+In the base case, $\lambda_\Sigma=\{\link[\varnothing]AB\}$ and $\kappa_\Theta=\{\link[\varnothing]{\dual B}C\}$, and the composition is $\net{\{\link[\varnothing]AC\}}AC$.
+
+If
+\todo{}
+\end{proof}

### 2018-01-15 ALL1.tex
minor fixes - put back "unification nets" draft

@@
 \cite{Galmiche-2000} % ALL connection net (Def 6.11.)
+\cite{Cockett-Seely-2001}
 \cite{Hughes-VanGlabbeek-2005}
-\cite{Cockett-Santocanale-2009}
+%\cite{Cockett-Santocanale-2009}
 \cite{Heijltjes-2011, Heijltjes-2012}
@@
 
+	\item[Freshness]
+For a link $\link CD$ over $\seq AB$, variables in the range of $\sigma$ are \emph{fresh}: distinct from any existentially quantified variable in $\seq AB$.
+
 	\item[Eigenvariables not free]
-For a link $\link CD$, a universally quantified variable in $C$ or $D$ does not occur free in the range of $\sigma$.
-
-	\item[Freshness]
-For a link $\link CD$ in $\net{\lambda_\Sigma}AB$, variables in the range of $\sigma$ are fresh: distinct from any existentially quantified variable in $\seq AB$.
+For a link $\link CD$ over $\seq AB$, if a variable $x$ in the range of $\sigma$ is universally quantified as $\forall x.X$ in $\seq AB$ (an \emph{eigenvariable}), then $C\leq X$ or $D\leq X$.
 \end{description}
@@
 This sequentializes to the axiom $\infer{\seq{a\rho}{c\rho}}{}$, which is in normal form.
-Then $L\comp R$ is a proof net (it has an axiom linking and it coalesces), and it sequentializes to a proof in normal form which sequentializes (up to permutations) to $\psi'$.
+Then $L\comp R$ is a proof net (it has an axiom linking and it coalesces), and it sequentializes to a normal form of $\psi$.
 %
@@
 \end{proof}
+
+% --------------------------------------------------
+
+\section{Unification nets}
+
+We define the following further operations on witness maps.
+\[
+\begin{tabular}{@{}lp{.75\textwidth}@{}}
+	$\sigma\gen\tau$
+&
+	A witness map is \defn{more general} than another, 
+	$\sigma\gen\tau$, if there is a map $\rho$ such that 
+	$\sigma\rho=\tau$.
+\\[5pt]	
+	$\sigma\coh\tau$
+&
+	Two witness maps are \defn{coherent}, $\sigma\coh\tau$,
+	if there is a map $\rho$ such that $\sigma\rho=\tau\rho$.
+\\[5pt]
+	$\sigma\join\tau$
+&
+	The \defn{join} of two witness maps $\sigma\join\tau$ is defined
+	if they are coherent, and is the least map $\rho$ such that
+	$\sigma\gen\rho$ and $\tau\gen\rho$.
+\end{tabular}%
+\]
+
+A clean link $(P,Q)$ on two atomic formulas $P$ and $Q$ is an \defn{axiom} link if there exists a witness map $\sigma$ such that $P\sigma=\dual Q\sigma$.
+A clean \defn{axiom} linking is one consisting only of axiom links.
+
+The \defn{clean} de-sequentialization $\floor\pi$ of a proof $\pi$ is the pre-net $\net\lambda AB$ where the de-sequentialization $[\pi]=\net{\lambda_\Sigma}AB$.
+Observe that $\lambda$ is then an axiom linking.
+
+To an axiom link $(P,Q)$ we assign an \defn{initial witness map} $\sigma=\init PQ$ as the least witness map in $(\gen)$ such that $P\sigma=\dual Q\sigma$.
+In other words, $\init PQ$ is the most general unifier ($\textsc{mgu}$) of $P$ and $\dual Q$.
+An axiom linking $\lambda$ with the initial witness map assigned to each link will be written $\lambda_\star$:
+\[
+	\lambda_\star = \{~\link PQ~\mid~(P,Q)\in\lambda~,~\sigma=\init PQ~\}~.
+\]
+For a pre-net $\net{\lambda_\star}AB$ we assume the \defn{exact coverage} convention, that the domain of each $\sigma(P,Q)$ is $\ex AP\cup\ex BQ$.
+This means a variable $x\in\varE$ in $P$ or $Q$ will be assigned at least a fresh variable name $y$.
+
+%Together with the convention that existential variables in the range of $\sigma(P,Q)$ are fresh,
+
+For two witness labellings $\Sigma$ and $\Theta$ on the same linking $\lambda$, one is \defn{more general} than the other, $\Sigma\gen\Theta$, \lutz{say which one is more general} if $\Sigma(C,D)\gen\Theta(C,D)$ for every link $(C,D)\in\lambda$.
+We extend this to the linkings themselves: $\lambda_\Sigma\gen\lambda_\Theta$.
+Observe that for an axiom linking $\lambda$, the initial linking $\lambda_\star$ is the most general among the witness linkings $\lambda_\Sigma$ for any $\Sigma$.
+
+We write $\Sigma\tau$ for the composition of every map in $\Sigma$ with $\tau$:	$\Sigma\tau(C,D) = \Sigma(C,D)\tau$.
+Because of the exact coverage convention, we have that, if $\lambda_\star=\lambda_\Sigma\gen\lambda_\Theta$, then $\Theta=\Sigma\tau$ for some $\tau$.
+
+\begin{definition}
+\defn{Unifying coalescence} ($\ucoal$) is the rewrite relation generated by the rules:
+\[
+	(\urr+i)~,~(\urr?)~,~(\urr!)
+	\quad
+	\text{are respectively as}
+	\quad
+	(\srr+i)~,~(\srr?)~,~(\srr!)
+\]
+except that ($\urr?$) does not require that $\sigma(x)$ is defined, plus the rule
+\begin{equation}
+	\net{\{\link AB^\pi,\link[\tau]AC^\phi\}}A{B\*C}
+ ~\ucoal~ 
+	\net{\{\link[\sigma\join\tau]A{B\*C}^\psi\}}A{B\*C}
+\tag{$\urr*$}
+\end{equation}
+
+\hfill $\text{if}\quad\sigma\coh\tau~,
+		\quad
+		\text{where}\quad \sigma\join\tau=\sigma\rho=\tau\rho
+		\quad
+		\text{and}\quad \psi=~
+  \vc{
+   \infer  {\seq{A\sigma\rho}{B\sigma\rho\,\*\,C\sigma\rho}}  {
+    \left( \vc{\deduce  [\rule{0pt}{2pt}]  {\seq{A\sigma}{B\sigma}}  \pi} \right)\rho
+    &
+    \left( \vc{\deduce  [\rule{0pt}{2pt}]  {\seq{A\tau}{C\tau}}  \phi} \right)\rho   
+  }}~.
+$ \hspace*{20pt}
+
+\medskip
+
+\noindent
+A pre-net $\net\lambda AB$ \defn{unifying-coalesces} if it reduces in $(\ucoal)$ to a single link $\net{\{\link[\varnothing]AB\}}AB$.
+\end{definition}
+
+%A pre-net $\net\lambda AB$ \defn{strict-} or \defn{unifying-coalesces} if it reduces in $(\scoal)$ respectively $(\ucoal)$ to a single link $\net{\link[\varnothing]AB}AB$.
+Here, we ignore the labelling with proofs, which means in particular that we need not instate a labelling to initiate coalescence.
+
+%A pre-net $\net\lambda AB$ \defn{coalesces}, in either relation , if it coalesces to a single clean link $\net{(A,B)^\pi}AB$.
+In that case, it \defn{sequentializes} It \defn{strongly coalesces} if every coalescence sequence can be extended to reach $\net{(A,B)}AB$.
+
+\begin{definition}
+An \all1 \defn{unification proof net} or \defn{unification net} is a pre-net $\net\lambda AB$ with clean axiom linking $\lambda$ such that its initial witness assignment $\net{\lambda_\star}AB$ unifying-coalesces.
+It \defn{sequentializes} to $\pi$ if the initial labelling $\net{\lambda^\star_\star}AB$ reduces in $(\ucoal)$ to $\net{\{\link[\varnothing]AB^\pi\}}AB$.
+\end{definition}
 
@@
 
-\section{Unification nets}
-
-We define the following further operations on witness maps.
-\[
-\begin{tabular}{@{}lp{.75\textwidth}@{}}
-	$\sigma\gen\tau$
-&
-	A witness map is \defn{more general} than another, 
-	$\sigma\gen\tau$, if there is a map $\rho$ such that 
-	$\sigma\rho=\tau$.
-\\[5pt]	
-	$\sigma\coh\tau$
-&
-	Two witness maps are \defn{coherent}, $\sigma\coh\tau$,
-	if there is a map $\rho$ such that $\sigma\rho=\tau\rho$.
-\\[5pt]
-	$\sigma\join\tau$
-&
-	The \defn{join} of two witness maps $\sigma\join\tau$ is defined
-	if they are coherent, and is the least map $\rho$ such that
-	$\sigma\gen\rho$ and $\tau\gen\rho$.
-\end{tabular}%
-\]
-
-A clean link $(P,Q)$ on two atomic formulas $P$ and $Q$ is an \defn{axiom} link if there exists a witness map $\sigma$ such that $P\sigma=\dual Q\sigma$.
-A clean \defn{axiom} linking is one consisting only of axiom links.
-
-The \defn{clean} de-sequentialization $\floor\pi$ of a proof $\pi$ is the pre-net $\net\lambda AB$ where the de-sequentialization $[\pi]=\net{\lambda_\Sigma}AB$.
-Observe that $\lambda$ is then an axiom linking.
-
-To an axiom link $(P,Q)$ we assign an \defn{initial witness map} $\sigma=\init PQ$ as the least witness map in $(\gen)$ such that $P\sigma=\dual Q\sigma$.
-In other words, $\init PQ$ is the most general unifier ($\textsc{mgu}$) of $P$ and $\dual Q$.
-An axiom linking $\lambda$ with the initial witness map assigned to each link will be written $\lambda_\star$:
-\[
-	\lambda_\star = \{~\link PQ~\mid~(P,Q)\in\lambda~,~\sigma=\init PQ~\}~.
-\]
-For a pre-net $\net{\lambda_\star}AB$ we assume the \defn{exact coverage} convention, that the domain of each $\sigma(P,Q)$ is $\ex AP\cup\ex BQ$.
-This means a variable $x\in\varE$ in $P$ or $Q$ will be assigned at least a fresh variable name $y$.
-
-%Together with the convention that existential variables in the range of $\sigma(P,Q)$ are fresh,
-
-For two witness labellings $\Sigma$ and $\Theta$ on the same linking $\lambda$, one is \defn{more general} than the other, $\Sigma\gen\Theta$, \lutz{say which one is more general} if $\Sigma(C,D)\gen\Theta(C,D)$ for every link $(C,D)\in\lambda$.
-We extend this to the linkings themselves: $\lambda_\Sigma\gen\lambda_\Theta$.
-Observe that for an axiom linking $\lambda$, the initial linking $\lambda_\star$ is the most general among the witness linkings $\lambda_\Sigma$ for any $\Sigma$.
-
-We write $\Sigma\tau$ for the composition of every map in $\Sigma$ with $\tau$:	$\Sigma\tau(C,D) = \Sigma(C,D)\tau$.
-Because of the exact coverage convention, we have that, if $\lambda_\star=\lambda_\Sigma\gen\lambda_\Theta$, then $\Theta=\Sigma\tau$ for some $\tau$.
-
-\begin{definition}
-\defn{Unifying coalescence} ($\ucoal$) is the rewrite relation generated by the rules:
-\[
-	(\urr+i)~,~(\urr?)~,~(\urr!)
-	\quad
-	\text{are respectively as}
-	\quad
-	(\srr+i)~,~(\srr?)~,~(\srr!)
-\]
-except that ($\urr?$) does not require that $\sigma(x)$ is defined, plus the rule
-\begin{equation}
-	\net{\{\link AB^\pi,\link[\tau]AC^\phi\}}A{B\*C}
- ~\ucoal~ 
-	\net{\{\link[\sigma\join\tau]A{B\*C}^\psi\}}A{B\*C}
-\tag{$\urr*$}
-\end{equation}
-
-\hfill $\text{if}\quad\sigma\coh\tau~,
-		\quad
-		\text{where}\quad \sigma\join\tau=\sigma\rho=\tau\rho
-		\quad
-		\text{and}\quad \psi=~
-  \vc{
-   \infer  {\seq{A\sigma\rho}{B\sigma\rho\,\*\,C\sigma\rho}}  {
-    \left( \vc{\deduce  [\rule{0pt}{2pt}]  {\seq{A\sigma}{B\sigma}}  \pi} \right)\rho
-    &
-    \left( \vc{\deduce  [\rule{0pt}{2pt}]  {\seq{A\tau}{C\tau}}  \phi} \right)\rho   
-  }}~.
-$ \hspace*{20pt}
-
-\medskip
-
-\noindent
-A pre-net $\net\lambda AB$ \defn{unifying-coalesces} if it reduces in $(\ucoal)$ to a single link $\net{\{\link[\varnothing]AB\}}AB$.
-\end{definition}
-
-%A pre-net $\net\lambda AB$ \defn{strict-} or \defn{unifying-coalesces} if it reduces in $(\scoal)$ respectively $(\ucoal)$ to a single link $\net{\link[\varnothing]AB}AB$.
-Here, we ignore the labelling with proofs, which means in particular that we need not instate a labelling to initiate coalescence.
-
-%A pre-net $\net\lambda AB$ \defn{coalesces}, in either relation , if it coalesces to a single clean link $\net{(A,B)^\pi}AB$.
-In that case, it \defn{sequentializes} It \defn{strongly coalesces} if every coalescence sequence can be extended to reach $\net{(A,B)}AB$.
-
-\begin{definition}
-An \all1 \defn{unification proof net} or \defn{unification net} is a pre-net $\net\lambda AB$ with clean axiom linking $\lambda$ such that its initial witness assignment $\net{\lambda_\star}AB$ unifying-coalesces.
-It \defn{sequentializes} to $\pi$ if the initial labelling $\net{\lambda^\star_\star}AB$ reduces in $(\ucoal)$ to $\net{\{\link[\varnothing]AB^\pi\}}AB$.
-\end{definition}
-
 \begin{figure}

### 2018-01-17 ALL1.tex
stuff

@@
 
-\newcommand\seq[3][]{{\vdash_{#1}}#2,#3}
+\newcommand\seq[2]{{\vdash}#1,#2}
 \newcommand\fv{\textsc{fv}}
@@
 
-\newcommand\init[2]{#1\star #2}
+\newcommand\init[2]{\mgu(#1,#2)}
 
@@
   \ifx#11\mathrm{ax}\else
+  \ifx#1.\mathrm{cut}\else
   #1\mathrm R
-  \fi\fi\fi\fi\fi
+  \fi\fi\fi\fi\fi\fi
 }
@@
 }
-\newcommand\@urr[1]{+_{#1}\mathrm U}
+\newcommand\@urr[1]{+\mathrm U,{#1}}
 
@@
 
+% ===== Permutations
+
+\newcommand\downperm{\sim\rule[-8pt]{0pt}{22pt}}
+
+\newcommand\permAB{
+ \infer[\Qrr!]{\Seq{\forall x.A}{\forall y.B}}{
+  \infer[\Qrr!]{\Seq A{\forall y.B}}{
+   \Seq AB
+}}}
+\newcommand\permBA{
+ \infer[\Qrr!]{\Seq{\forall x.A}{\forall y.B}}{
+  \infer[\Qrr!]{\Seq{\forall x.A}B}{
+   \Seq AB
+}}}
+\newcommand\permAE{
+ \infer[\Qrr!]{\Seq{\forall x.A}{\exists y.B}}{
+  \infer[\Qrr?t]{\Seq A{\exists y.B}}{
+   \Seq A{B[t/y]}
+}}}
+\newcommand\permEA{
+ \infer[\Qrr?t]{\Seq{\forall x.A}{\forall y.B}}{
+  \infer[\Qrr!]{\Seq{\forall x.A}{B[t/y]}}{
+   \Seq A{B[t/y]}
+}}}
+\newcommand\permEF{
+ \infer[\Qrr?s]{\Seq{\exists x.A}{\exists y.B}}{
+  \infer[\Qrr?t]{\Seq{A[s/x]}{\exists y.B}}{
+   \Seq{A[s/x]}{B[t/y]}
+}}}
+\newcommand\permFE{
+ \infer[\Qrr?t]{\Seq{\exists x.A}{\exists y.B}}{
+  \infer[\Qrr?s]{\Seq{\exists x.A}B[t/y]}{
+   \Seq{A[s/x]}{B[t/y]}
+}}}
+\newcommand\permAP{
+ \infer[\Qrr!]{\Seq{\forall x.A}{B_1\+B_2}}{
+  \infer[\Qrr+i]{\Seq A{B_1\+B_2}}{
+   \Seq A{B_i}
+}}}
+\newcommand\permPA{
+ \infer[\Qrr+i]{\Seq{\forall x.A}{B_1\+B_2}}{
+  \infer[\Qrr!]{\Seq{\forall x.A}{B_i}}{
+   \Seq A{B_i}
+}}}
+\newcommand\permEP{
+ \infer[\Qrr?t]{\Seq{\exists x.A}{B_1\+B_2}}{
+  \infer[\Qrr+i]{\Seq{A[t/x]}{B_1\+B_2}}{
+   \Seq{A[t/x]}{B_i}
+}}}
+\newcommand\permPE{
+ \infer[\Qrr+i]{\Seq{\exists x.A}{B_1\+B_2}}{
+  \infer[\Qrr?t]{\Seq{\exists x.A}{B_i}}{
+   \Seq{A[t/x]}{B_i}
+}}}
+\newcommand\permPQ{
+ \infer[\Qrr+i]{\Seq{A_1\+A_2}{B_1\+B_2}}{
+  \infer[\Qrr+j]{\Seq{A_i}{B_1\+B_2}}{
+   \Seq{A_i}{B_j}
+}}}
+\newcommand\permQP{
+ \infer[\Qrr+j]{\Seq{A_1\+A_2}{B_1\+B_2}}{
+  \infer[\Qrr+i]{\Seq{A_1\+A_2}{B_j}}{
+   \Seq{A_i}{B_j}
+}}}
+\newcommand\permAX{
+ \infer[\Qrr!]{\Seq{\forall x.A}{B\*C}}{
+  \infer[\Qrr*]{\Seq A{B\*C}}{
+   \Seq AB & \Seq AC
+}}}
+\newcommand\permXA{
+ \infer[\Qrr*]{\Seq{\forall x.A}{B\*C}}{
+  \infer[\Qrr!]{\Seq{\forall x.A}B}{
+   \Seq AB 
+  }& 
+  \infer[\Qrr!]{\Seq{\forall x.A}C}{
+   \Seq AC
+}}}
+\newcommand\permEX{
+ \infer[\Qrr?t]{\Seq{\exists x.A}{B\*C}}{
+  \infer[\Qrr*]{\Seq{A[t/x]}{B\*C}}{
+   \Seq{A[t/x]}B & \Seq{A[t/x]}C
+}}}
+\newcommand\permXE{
+ \infer[\Qrr*]{\Seq{\exists x.A}{B\*C}}{
+  \infer[\Qrr?t]{\Seq{\exists x.A}B}{
+   \Seq{A[t/x]}B 
+  }& 
+  \infer[\Qrr?t]{\Seq{\exists x.A}C}{
+   \Seq{A[t/x]}C
+}}}
+\newcommand\permPX{
+ \infer[\Qrr+i]{\Seq{A_1\+A_2}{B\*C}}{
+  \infer[\Qrr*]{\Seq{A_i}{B\*C}}{
+   \Seq{A_i}B & \Seq{A_i}C
+}}}
+\newcommand\permXP{
+ \infer[\Qrr*]{\Seq{A_1\+A_2}{B\*C}}{
+  \infer[\Qrr+i]{\Seq{A_1\+A_2}B}{
+   \Seq{A_i}B 
+  }& 
+  \infer[\Qrr+i]{\Seq{A_1\+A_2}C}{
+   \Seq{A_i}C
+}}}
+\newcommand\permXY{
+ \infer[\Qrr*]{\Seq{A\*B}{C\*D}}{
+  \infer[\Qrr*]{\Seq A{C\*D}}{
+   \Seq AC & \Seq AD
+  }&
+  \infer[\Qrr*]{\Seq B{C\*D}}{
+   \Seq BC & \Seq BD
+}}}
+\newcommand\permYX{
+ \infer[\Qrr*]{\Seq{A\*B}{C\*D}}{
+  \infer[\Qrr*]{\Seq{A\*B}C}{
+   \Seq AC & \Seq BC
+  }&
+  \infer[\Qrr*]{\Seq{A\*B}D}{
+   \Seq AD & \Seq BD
+}}}
+
+% ===== Cut-permutations
+
+\newcommand\permAC{
+ \infer[\Qrr.]{\Seq{\forall x.A}C}{
+  \infer[\Qrr!]{\Seq{\forall x.A}B}{
+   \Seq AB 
+  }& 
+  \Seq{\dual B}C
+}}
+\newcommand\permCA{
+ \infer[\Qrr!]{\Seq{\forall x.A}C}{
+  \infer[\Qrr.]{\Seq AC}{
+   \Seq AB & \Seq{\dual B}C
+}}}
+\newcommand\permEC{
+ \infer[\Qrr.]{\Seq{\exists x.A}C}{
+  \infer[\Qrr?t]{\Seq{\exists x.A}B}{
+   \Seq{A[t/x]}B 
+  }& 
+  \Seq{\dual B}C
+}}
+\newcommand\permCE{
+ \infer[\Qrr?t]{\Seq{\exists x.A}C}{
+  \infer[\Qrr.]{\Seq{A[t/x]}C}{
+   \Seq{A[t/x]}B & \Seq{\dual B}C
+}}}
+\newcommand\permPC{
+ \infer[\Qrr.]{\Seq{{A_1\+A_2}}C}{
+  \infer[\Qrr+i]{\Seq{{A_1\+A_2}}B}{
+   \Seq {A_i}B 
+  }& 
+  \Seq{\dual B}C
+}}
+\newcommand\permCP{
+ \infer[\Qrr+i]{\Seq{{A_1\+A_2}}C}{
+  \infer[\Qrr.]{\Seq {A_i}C}{
+   \Seq {A_i}B & \Seq{\dual B}C
+}}}
+\newcommand\permXC{
+ \infer[\Qrr.]{\Seq{{A_1\*A_2}}C}{
+  \infer[\Qrr*]{\Seq{{A_1\*A_2}}B}{
+   \Seq {A_1}B & \Seq{A_2}B
+  }& 
+  \Seq{\dual B}C
+}}
+\newcommand\permCX{
+ \infer[\Qrr*]{\Seq{{A_1\*A_2}}C}{
+  \infer[\Qrr.]{\Seq {A_i}C}{
+   \Seq {A_1}B & \Seq{\dual B}C
+  }&
+  \infer[\Qrr.]{\Seq {A_i}C}{
+   \Seq {A_2}B & \Seq{\dual B}C
+}}}
+\newcommand\permCD{
+ \infer[\Qrr.]{\Seq AD}{
+  \infer[\Qrr.]{\Seq AC}{
+   \Seq AB & \Seq{\dual B}C
+  }& 
+  \Seq{\dual C}D
+}}
+\newcommand\permDC{
+ \infer[\Qrr.]{\Seq{{A_1\*A_2}}C}{
+  \Seq A{\dual B}
+  &
+  \infer[\Qrr.]{\Seq BD}{
+   \Seq B{\dual C} & \Seq CD
+}}}
+
 \makeatother
@@
 \begin{document}
+
+\begin{lemma}
+For $\link ab$ in a proof net $\net{\lambda_\star}AB$ and $\link[\tau]{\dual b}c$ in $\net{\kappa_\star}{\dual B}C$ the composition $\sigma_a\tau_c\dcom\fix{\sigma_b\tau\subdual b}=\mgu(a,c)$.
+\end{lemma}
+
+\begin{proof}
+Let $\rho=\mgu(a,c)$ and $\rho'=\sigma_a\tau_c\dcom\fix{\sigma_b\tau\subdual b}$.
+Define the \defn{basis} $\floor{s,t}$ of the $\mgu$ of $s$ and $t$ to be the substitution map defined by $\floor{x,t}=\floor{t,x} = [t/x]$ and
+\[
+	\floor{P(s_1,\dots,s_n),P(t_1,\dots,t_n)} =
+	\floor{f(s_1,\dots,s_n),f(t_1,\dots,t_n)} =
+	\floor{s_1,t_1}\dots\floor{s_n,t_n}~.
+\]
+Write $\floor\sigma$ for the basis $\floor{a,b}$ of $\sigma$, $\floor\tau$ for that of $\tau$, and $\floor\rho$ for that of $\rho$.
+\end{proof}
+
+\end{document}
 
@@
 We write $\prf\pi AB$ for a proof $\pi$ with conclusion sequent $\seq AB$.
+Two proofs are \defn{equivalent} $\pi\sim\pi'$ if one is obtained from the other by rule permutations (Appendix, Figure~\ref{fig:permutations}.
 
@@
 A \defn{linking} $\lambda$ on the sequent $\seq AB$ is a set of links on it.
+
+% ..................................................
 
@@
 We may use and define $\lambda_\Sigma$ as a set of \defn{witness links} $\link CD$, where $(C,D)\in\lambda$ and $\Sigma(C,D)=\sigma$.
-% When a link is not a witness link, this may be emphasized by calling it \defn{clean}.
+
+% ..................................................
 
@@
 
+% ..................................................
+
 We will assume the following variable naming conventions.
@@
 
-	\item[Freshness]
-For a link $\link CD$ over $\seq AB$, variables in the range of $\sigma$ are \emph{fresh}: distinct from any existentially quantified variable in $\seq AB$.
-
 	\item[Eigenvariables not free]
 For a link $\link CD$ over $\seq AB$, if a variable $x$ in the range of $\sigma$ is universally quantified as $\forall x.X$ in $\seq AB$ (an \emph{eigenvariable}), then $C\leq X$ or $D\leq X$.
+
+	\item[Freshness]
+For a link $\link CD$ over $\seq AB$, other variables in the range of $\sigma$ are \emph{fresh}: distinct from any existentially quantified variable in $\seq AB$.
 \end{description}
+
+% ..................................................
 
@@
 The \defn{de-sequentialization} $[\pi]$ of a sequent proof $\prf\pi AB$ is the witness pre-net $\net{\deseq[\varnothing]\pi AB}AB$ where the function $\deseq-AB$ is defined inductively as follows.
-%
-% $\net{\lambda_\Sigma}AB$ where $\lambda_\Sigma=\deseq[\varnothing]\pi AB$ and the function $\deseq-AB$ is defined as follows.
-%
-%\newlength\deseqwidth
-%\settowidth\deseqwidth{$\scriptstyle{A'\,,\,B'_0\+B'_1}$}
 %
@@
 
+% ..................................................
+
 A function call $\deseq{\prf\pi AB}{A'}{B'}$ expects that $A=A'\sigma$ and $B=B'\sigma$: the translation separates a sequent $\seq AB$ into subformulas $A'$, $B'$ of the ultimate conclusion of the proof, and the accumulated existential witnesses $\sigma$.
@@
 
+% ..................................................
+
 \begin{definition}
@@
 \end{definition}
+%
+% ..................................................
 %
@@
 
-%\begin{figure}
-%\[
-%    \vc{\begin{tikzpicture}[net]
-%    	\formula[y=2]{C}
-%    	\formula[y=1]{D*{_1}{{\+}}D*{_2}}
-%    	\Vlink[red,label={$\scriptstyle\sigma~$},l]{1,1}
-%    \end{tikzpicture}}
-%\scoal 
-%    \vc{\begin{tikzpicture}[net]
-%    	\formula[y=2]{C}
-%    	\formula[y=1]{D*{_1}{{\+}}D*{_2}}
-%    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,2}
-%    \end{tikzpicture}}
-%\hfill% 
-%    \vc{\begin{tikzpicture}[net]
-%    	\formula[y=2]{C}
-%    	\formula[y=1]{D*{_1}{{\*}}D*{_2}}
-%    	\Vlink[red,label={$\scriptstyle\sigma~$},l]{[-1]1,1}
-%    	\Vlink[red,label={~$\scriptstyle\sigma$}]{[1]1,3}
-%    \end{tikzpicture}}
-%\scoal
-%	\vc{\begin{tikzpicture}[net]
-%    	\formula[y=2]{C}
-%    	\formula[y=1]{D*{_1}{{\*}}D*{_2}}
-%    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,2}
-%    \end{tikzpicture}} 
-%\hfill%    
-%    \vc{\begin{tikzpicture}[net]
-%    	\formula[y=2]{C}
-%    	\formula[y=1]{\exists x.D}
-%    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,4}
-%    \end{tikzpicture}}
-%\stackrel{\begin{array}{@{}c@{}}\scriptstyle x\,\in\\[-1ex]\scriptstyle\dom\sigma\end{array}}\scoal
-%    \vc{\begin{tikzpicture}[net]
-%    	\formula[y=2]{C}
-%    	\formula[y=1]{\exists x.D}
-%    	\Vlink[red,label={~$\scriptstyle{\sigma\minus x}$}]{1,1}
-%    \end{tikzpicture}}   
-%\hfill%
-%    \vc{\begin{tikzpicture}[net]
-%    	\formula[y=2]{C}
-%    	\formula[y=1]{\forall x.D}
-%    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,4}
-%    \end{tikzpicture}}
-%\stackrel{x\,\notin\,\sigma}\scoal
-%    \vc{\begin{tikzpicture}[net]
-%    	\formula[y=2]{C}
-%    	\formula[y=1]{\forall x.D}
-%    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,1}
-%    \end{tikzpicture}}
-%\]
-%\caption{Coalescence rules}
-%\label{fig:coalescence}
-%\end{figure}
-
 % ..................................................
@@
 \begin{align*}
-%\tag{$\srr+i$}
+\tag{$\srr+i$}
 	\link C{D_i}^\pi
@@
 \\ \\[-8pt]
-%\tag{$\srr*$}
+\tag{$\srr*$}
 	%\{\link C{D_1}^\pi\,,\,\link C{D_2}^\phi\}
@@
 \\ \\[-8pt]
-%\tag{$\srr?$}
+\tag{$\srr?$}
 	\link CD^\pi
@@
 \\ \\[-8pt]
-%\tag{$\srr!$}
+\tag{$\srr!$}
 	\link CD^\pi
@@
 
+% ..................................................
+
 \lutz{I guess there should be an example here.}
@@
 
+% ..................................................
+
 \begin{theorem}
-For any \all1 proof $\pi$, the de-sequentialization $[\pi]$ is a witness net that sequentializes to $\pi$. 
+\label{thm:proof->net->proof}
+For any \all1 proof $\pi$, the witness net $[\pi]$ sequentializes to $\pi$. 
 \end{theorem}
@@
 
+% ..................................................
+
+\begin{theorem}
+\label{thm:net->proof->net}
+If $\net{\lambda_\Sigma}AB$ sequentializes to $\pi$, then $[\pi]$ is $\net{\lambda_\Sigma}AB$. 
+\end{theorem}
+
+\begin{proof}
+By induction on the sequentialization path 
+$\net{\lambda_\Sigma^\star}AB\scoal^*\net{\{\link[\varnothing]AB^\pi\}}AB$
+it follows that in every pre-net $\net{\kappa_\Theta^\Phi}AB$ on this path, $\lambda_\Sigma$ is equal to the union over the de-sequentialization of all proof labels $\phi$ in $\Phi$:
+\[
+	\lambda_\Sigma=\bigcup~\{\,\deseq\phi CD \mid \link CD^\phi \in \kappa_\Theta^\Phi\,\}~.
+\]
+The statement is then the case $\kappa_\Theta^\Phi=\{\link[\varnothing]AB^\pi\}$.
+\end{proof}
+
 % --------------------------------------------------
@@
 \]
+
+% ..................................................
 
@@
 
+% ..................................................
+
 As in the propositional case, for correctness we will require that each slice is a singleton.
@@
 %
+
+% ..................................................
+
 \begin{definition}
@@
 
+% ..................................................
+
 \newcounter{lemcorrect}
@@
 
+% ..................................................
+
 \newcounter{lemcoalescenceapplies}
@@
 
+% ..................................................
+
 \begin{theorem}
@@
 
+% ..................................................
+
 \begin{corollary}
@@
 \end{corollary}
+
+% ..................................................
 
@@
 
+% ..................................................
+
+\begin{theorem}
+Proof nets are canonical: $[\pi]=[\phi]$ if and only if $\pi\sim\phi$.
+\end{theorem}
+
+\begin{proof}
+From left to right is by inspection of the critical pairs of sequentialization ($\scoal$).
+From right to left is by inspection of the rule permutations in Figure~\ref{fig:permutations} in the Appendix.
+\end{proof}
+
 % --------------------------------------------------
@@
 
+% ..................................................
 \begin{figure}
@@
 \end{figure}
+% ..................................................
 
@@
 
+% ..................................................
 \begin{definition}
@@
 \end{definition}
+% ..................................................
 
@@
 
-\begin{proposition}
+% ..................................................
+\begin{theorem}
 If proof nets $\net{\lambda_\Sigma}AB$ and $\net{\kappa_\Theta}{\dual B}C$ sequentialize to $\pi$ and $\phi$ respectively, then their composition $(\net{\lambda_\Sigma}AB)\comp(\net{\kappa_\Theta}{\dual B}C)$ sequentializes to a normal form $\psi$ of the proof
@@
 \]
-\end{proposition}
+\end{theorem}
 
@@
 The path along the top and right of this diagram sequentializes $L$ to $\pi'$ and $R$ to $\phi'$ (equivalent to $\pi$ and $\phi$ respectively), and then composes to $L_n\comp R_n = \net{\{\link[\varnothing]AC^{\psi'}\}}AC$ with
-%
 \[
@@
 
+%\[
+%	\vc{
+%	 \infer[\Qrr*]{\seq{A\*B}{\exists x.C}}{
+%	  \infer[\Qrr?y]{\seq A{\exists x.C}}{\seq AC}
+%	  &
+%	  \infer[\Qrr?z]{\seq B{\exists x.C}}{\seq BC}
+%	}}
+%	\quad\sim\quad
+%	\vc{
+%	 \infer[\Qrr?y]{\seq{A\*B}C}{
+%	  \infer[\Qrr*]{\seq{A\*B}{\exists x.C}}{
+%	   \seq AC
+%	   &
+%	   \seq BC
+%	}}}
+%\]
+
+A proof $\pi$ is \defn{more general} than $\pi'$, written $\pi\leq\pi'$, if there is a substitution map $\rho$ such that $\pi\rho=\pi'$.
+
+\[
+	\vc{
+	 \infer[\Qrr*]{\seq{A\*B}{\exists x.C}}{
+	  \infer[\Qrr?s]{\seq A{\exists x.C}}{\seq AC}
+	  &
+	  \infer[\Qrr?t]{\seq B{\exists x.C}}{\seq BC}
+	}}
+	\quad\sim\quad
+	\vc{
+	 \infer[\Qrr?u]{\seq{A\*B}C}{
+	  \infer[\Qrr*]{\seq{A\*B}{\exists x.C}}{
+	   \seq AC
+	   &
+	   \seq BC
+	}}}
+\]
+
 We define the following further operations on witness maps.
 \[
-\begin{tabular}{@{}lp{.75\textwidth}@{}}
-	$\sigma\gen\tau$
-&
-	A witness map is \defn{more general} than another, 
+\begin{tabular}{@{}p{.10\textwidth}@{}p{.90\textwidth}@{}}
+	\quad$\sigma\gen\tau$
+&
+	A witness map $\sigma$ is \defn{more general} than $\tau$,  
 	$\sigma\gen\tau$, if there is a map $\rho$ such that 
 	$\sigma\rho=\tau$.
-\\[5pt]	
-	$\sigma\coh\tau$
-&
-	Two witness maps are \defn{coherent}, $\sigma\coh\tau$,
+\\[4pt]	
+	\quad$\sigma\coh\tau$
+&
+	Two witness maps $\sigma$ and $\tau$ are \defn{coherent}, $\sigma\coh\tau$,
 	if there is a map $\rho$ such that $\sigma\rho=\tau\rho$.
-\\[5pt]
-	$\sigma\join\tau$
-&
-	The \defn{join} of two witness maps $\sigma\join\tau$ is defined
-	if they are coherent, and is the least map $\rho$ such that
-	$\sigma\gen\rho$ and $\tau\gen\rho$.
+\\[4pt]
+	\quad$\sigma\join\tau$
+&
+	The \defn{join} $\sigma\join\tau$ of two coherent witness maps is the least map $\rho$ such that $\sigma\gen\rho$ and $\tau\gen\rho$.
 \end{tabular}%
 \]
-
-A clean link $(P,Q)$ on two atomic formulas $P$ and $Q$ is an \defn{axiom} link if there exists a witness map $\sigma$ such that $P\sigma=\dual Q\sigma$.
-A clean \defn{axiom} linking is one consisting only of axiom links.
-
-The \defn{clean} de-sequentialization $\floor\pi$ of a proof $\pi$ is the pre-net $\net\lambda AB$ where the de-sequentialization $[\pi]=\net{\lambda_\Sigma}AB$.
-Observe that $\lambda$ is then an axiom linking.
-
-To an axiom link $(P,Q)$ we assign an \defn{initial witness map} $\sigma=\init PQ$ as the least witness map in $(\gen)$ such that $P\sigma=\dual Q\sigma$.
-In other words, $\init PQ$ is the most general unifier ($\textsc{mgu}$) of $P$ and $\dual Q$.
-An axiom linking $\lambda$ with the initial witness map assigned to each link will be written $\lambda_\star$:
-\[
-	\lambda_\star = \{~\link PQ~\mid~(P,Q)\in\lambda~,~\sigma=\init PQ~\}~.
-\]
-For a pre-net $\net{\lambda_\star}AB$ we assume the \defn{exact coverage} convention, that the domain of each $\sigma(P,Q)$ is $\ex AP\cup\ex BQ$.
-This means a variable $x\in\varE$ in $P$ or $Q$ will be assigned at least a fresh variable name $y$.
-
-%Together with the convention that existential variables in the range of $\sigma(P,Q)$ are fresh,
-
-For two witness labellings $\Sigma$ and $\Theta$ on the same linking $\lambda$, one is \defn{more general} than the other, $\Sigma\gen\Theta$, \lutz{say which one is more general} if $\Sigma(C,D)\gen\Theta(C,D)$ for every link $(C,D)\in\lambda$.
-We extend this to the linkings themselves: $\lambda_\Sigma\gen\lambda_\Theta$.
-Observe that for an axiom linking $\lambda$, the initial linking $\lambda_\star$ is the most general among the witness linkings $\lambda_\Sigma$ for any $\Sigma$.
-
-We write $\Sigma\tau$ for the composition of every map in $\Sigma$ with $\tau$:	$\Sigma\tau(C,D) = \Sigma(C,D)\tau$.
-Because of the exact coverage convention, we have that, if $\lambda_\star=\lambda_\Sigma\gen\lambda_\Theta$, then $\Theta=\Sigma\tau$ for some $\tau$.
-
+%
+A link $\link[]ab$ on two atomic formulas is an \defn{axiom} link if there exists a witness map $\sigma$ such that $a\sigma=\dual b\sigma$.
+To an axiom link $\link[]ab$ over $\seq AB$ we assign an \defn{initial witness map}, which is the least witness map $\sigma$ over the domain $\ex[\!A]a\cup\ex[\!B]b$ such that $a\sigma=\dual b\sigma$.
+In other words, $\sigma$ is the most general unifier of $a$ and $\dual b$, over the given domain, written $\init ab$.
+For an axiom linking $\lambda$ over $\seq AB$ the \defn{initial witness pre-net} $\net{\lambda_\star}AB$ is given by
+\[
+	\lambda_\star = \{~\link ab~\mid~\link[]ab\in\lambda~,~\sigma=\init ab~\}~.
+\]
+Observe that the initial witness pre-net satisfies the \emph{exact coverage} condition.
+
+% ..................................................
 \begin{definition}
-\defn{Unifying coalescence} ($\ucoal$) is the rewrite relation generated by the rules:
-\[
-	(\urr+i)~,~(\urr?)~,~(\urr!)
-	\quad
-	\text{are respectively as}
-	\quad
-	(\srr+i)~,~(\srr?)~,~(\srr!)
-\]
-except that ($\urr?$) does not require that $\sigma(x)$ is defined, plus the rule
+%
+\renewcommand{\+}{{+}}
+\renewcommand{\*}{{\times}}
+%
+\defn{Unifying sequentialization} ($\ucoal$) is the rewrite relation on labelled pre-nets generated by the rules
+$(\urr+i)$, $(\urr?)$, $(\urr!)$, which are respectively as $(\srr+i)$, $(\srr?)$, and $(\srr!)$, and the rule
 \begin{equation}
-	\net{\{\link AB^\pi,\link[\tau]AC^\phi\}}A{B\*C}
- ~\ucoal~ 
-	\net{\{\link[\sigma\join\tau]A{B\*C}^\psi\}}A{B\*C}
 \tag{$\urr*$}
+	\left.\begin{array}{@{}l@{\,}}\link C{D_1}^\pi \\ \link[\tau]C{D_2}^\phi\end{array}\right\}
+	\ucoal
+	\link[\sigma\join\tau\,=\,\sigma\rho\,=\,\tau\rho]C{D_1\*D_2}^\psi
+	\quad~
+	{\scriptstyle(\sigma\coh\tau)}
+	\quad~
+	\psi=~
+  \vc{\scalebox{0.9}{$
+   \infer  {\seq{A(\sigma{\join}\tau)}{B\sigma\rho\,\*\,C\tau\rho}}  {
+    \left( \vc{\Prf \pi {A\sigma} {B\sigma}} \right)\rho
+    &
+    \left( \vc{\Prf \phi {A\tau} {C\tau}} \right)\rho   
+  }$}}
 \end{equation} 
-
-\hfill $\text{if}\quad\sigma\coh\tau~,
-		\quad
-		\text{where}\quad \sigma\join\tau=\sigma\rho=\tau\rho
-		\quad
-		\text{and}\quad \psi=~
-  \vc{
-   \infer  {\seq{A\sigma\rho}{B\sigma\rho\,\*\,C\sigma\rho}}  {
-    \left( \vc{\deduce  [\rule{0pt}{2pt}]  {\seq{A\sigma}{B\sigma}}  \pi} \right)\rho
-    &
-    \left( \vc{\deduce  [\rule{0pt}{2pt}]  {\seq{A\tau}{C\tau}}  \phi} \right)\rho   
-  }}~.
-$ \hspace*{20pt}
-
-\medskip
-
-\noindent
-A pre-net $\net\lambda AB$ \defn{unifying-coalesces} if it reduces in $(\ucoal)$ to a single link $\net{\{\link[\varnothing]AB\}}AB$.
+%
+\defn{Unifying coalescence} is the relation ($\ucoal$) on witness pre-nets, ignoring proof labels.
+A witness pre-net $\net{\lambda_\Sigma}AB$ \defn{unifying-coalesces} if it reduces to $\net{\{\link[\varnothing]AB\}}AB$ and \defn{strongly} unifying-coalesces if any coalescence path terminates at $\net{\{\link[\varnothing]AB\}}AB$.
 \end{definition}
-
-%A pre-net $\net\lambda AB$ \defn{strict-} or \defn{unifying-coalesces} if it reduces in $(\scoal)$ respectively $(\ucoal)$ to a single link $\net{\link[\varnothing]AB}AB$.
-Here, we ignore the labelling with proofs, which means in particular that we need not instate a labelling to initiate coalescence.
-
-%A pre-net $\net\lambda AB$ \defn{coalesces}, in either relation , if it coalesces to a single clean link $\net{(A,B)^\pi}AB$.
-In that case, it \defn{sequentializes} It \defn{strongly coalesces} if every coalescence sequence can be extended to reach $\net{(A,B)}AB$.
-
+% ..................................................
+
+Observe that unifying coalescence includes strict coalescence, $(\scoal)\subseteq(\ucoal)$.
+
+% ..................................................
 \begin{definition}
-An \all1 \defn{unification proof net} or \defn{unification net} is a pre-net $\net\lambda AB$ with clean axiom linking $\lambda$ such that its initial witness assignment $\net{\lambda_\star}AB$ unifying-coalesces.
-It \defn{sequentializes} to $\pi$ if the initial labelling $\net{\lambda^\star_\star}AB$ reduces in $(\ucoal)$ to $\net{\{\link[\varnothing]AB^\pi\}}AB$.
+An \all1 \defn{unification proof net} or \defn{unification net} is a pre-net $\net\lambda AB$ with axiom linking $\lambda$ such that the initial witness pre-net $\net{\lambda_\star}AB$ unifying-coalesces.
+It \defn{sequentializes} to $\pi$ if $\net{\lambda^\star_\star}AB$ reduces in $(\ucoal)$ to $\net{\{\link[\varnothing]AB^\pi\}}AB$.
 \end{definition}
-
-% --------------------------------------------------
+% ..................................................
+
+In the above definition, note that $\lambda_\star^\star=(\lambda_\star)^*$ is the initial proof labelling of $\lambda_\star$, which assigns an axiom rule to each axiom link.
+
+% ..................................................
+\begin{lemma}
+\label{lem:ucoal generality}
+In ($\ucoal$), if $\net{\lambda_\Sigma}AB$ sequentializes to $\pi$ then $\net{\lambda_\star}AB$ sequentializes to $\pi'\leq\pi$.
+\end{lemma}
+
+\begin{proof}
+The sequentialization path
+$
+	\net{\lambda_\Sigma^\star}AB = 
+	L_1 \ucoal L_2 \ucoal \dots \ucoal L_n = 
+	\net{\link[\varnothing]AB^\pi}AB
+$
+has a corresponding path
+$
+	\net{\lambda_\star^\star}AB = 
+	R_1 \ucoal R_2 \ucoal \dots \ucoal R_n =
+	\net{\link[\varnothing]AB^{\pi'}}AB
+$
+where the same links (but with potentially different witness maps) are coalesced.
+It follows by induction on this path (where the base case is $L_1$ and $R_1$) that for every corresponding pair of links $\link CD^\phi$ in $L_i$ and $\link[\tau]CD^\psi$ in $R_i$ we have $\tau\leq\sigma$ and $\psi\leq\phi$.
+\end{proof}
+% ..................................................
+
+% ..................................................
+\begin{theorem}
+If $[\prf\pi AB]$ is $\net{\lambda_\Sigma}AB$ then $\net\lambda AB$ unifying-sequentializes to $\pi'\leq \pi$.
+\end{theorem}
+
+\begin{proof}
+By Theorem~\ref{thm:proof->net->proof}, $\net{\lambda_\Sigma}AB$ sequentializes to $\pi$ in $(\scoal)$, and hence also in $(\ucoal)$.
+Then by Lemma~\ref{lem:ucoal generality} $\net{\lambda_\star}AB$ sequentializes to $\pi'\leq\pi$.
+\end{proof}
+% ..................................................
+
+\begin{theorem}
+If $\net\lambda AB$ sequentializes to $\pi$, then $[\pi]=\net{\lambda_\Sigma} AB$ for some $\Sigma$.
+\end{theorem}
+
+% ..................................................
+\begin{lemma}
+If $\net{\lambda_\star}AB$ unifying-sequentializes to $\pi$ then there exists a witness assignment $\Sigma$ and substitution $\rho$ such that $\net{\lambda_\Sigma}AB$ strict-sequentializes to $\pi$ and $\lambda_\Sigma=\lambda_\star\rho$.
+\end{lemma}
+
+\begin{proof}
+By induction on the sequentialization path $\net{\lambda_\star}AB\ucoal^*\net{\link[\varnothing]AB^\pi}AB$.
+For the end result, the statement holds with $\rho=\varnothing$.
+For the inductive step, consider a step $L\ucoal R$.
+We show the case ($\urr*$); the other cases are immediate.
+%
+\begin{itemize}
+	\item
+$\link C{D_1},\link[\tau]C{D_2}\ucoal\link[\sigma\join\tau]C{D_1{\*}D_2}$
+\\
+By the inductive hypothesis, $R\rho'$ strict-sequentializes to $\pi$. Let $\sigma\join\tau=\sigma\rho''=\tau\rho''$ and let $\rho=\rho''\rho'$. Then $L\rho$ strict-sequentializes to $\pi$ by 
+\[
+	\link[\sigma\rho]C{D_1},\link[\tau\rho]C{D_2}\scoal\link[(\sigma\join\tau)\rho']C{D_1{\*}D_2}~.
+\qedhere
+\]
+\end{itemize}
+\end{proof}
+
+% ..................................................
+
+\begin{lemma}
+If a labelled pre-net $\net{\lambda_\Sigma^\Pi}AB$ strict-sequentializes to $\pi$, then $(\net{\lambda_\Sigma^\Pi}AB)\rho$ strict-sequentializes to $\pi\rho$.
+\end{lemma}
+
+\begin{proof}
+By induction on the sequentialization sequence.
+\end{proof}
 
@@
 
-For dependency-correctness, the column of $\link C{D_i}$ is that of $\link C{D_1{\+}D_2}$ plus $(D_i,\sigma\res{\ex[B]{D_i}})$ itself, which is minimal in the order $\dep$.
+For dependency-correctness, the column of $\link C{D_i}$ is that of $\link C{D_1{\+}D_2}$ plus the pair $(D_i,\sigma\res{\ex[B]{D_i}})$ itself, which is minimal in the order $\dep$.
 
@@
 \end{tikzpicture}}
-\qquad
+\quad
 $
@@
 
-% ..................................................
+% --------------------------------------------------
+
+\newpage
+\section{Permutations}
+
+% ..................................................
+
+\begin{figure}[h!]
+\[
+\renewcommand\+{{+}}
+\renewcommand\*{{\times}}
+\scalebox{0.85}{$
+\begin{array}{@{}c@{\qquad}c@{\qquad}c@{\qquad}c@{}}
+	\permAB   & \permAE   & \permAP   & \permAX 
+\\	\downperm & \downperm & \downperm & \downperm \\
+	\permBA   & \permEA   & \permPA   & \permXA
+\\ \\[20pt]
+ 			  & \permEF   & \permEP   & \permEX
+\\			  & \downperm & \downperm & \downperm \\
+ 			  & \permFE   & \permPE   & \permXE
+\\ \\[20pt]
+ 			  &			  & \permPQ   & \permPX
+\\			  &			  & \downperm & \downperm \\
+ 			  &			  & \permQP   & \permXP
+\\ \\[20pt]
+ 			  &			  &			  & \permPX
+\\			  &			  &			  & \downperm \\
+ 			  &			  &			  & \permXP
+\end{array}$}
+\]
+\caption{Cut-free rule permutations}
+\label{fig:permutations}
+\end{figure}
+
+% ..................................................
+
+\begin{figure}
+\[
+\renewcommand\+{{+}}
+\renewcommand\*{{\times}}
+\scalebox{0.85}{$
+\begin{array}{c@{\qquad}c}
+	\permAC   & \permEC   
+\\	\downperm & \downperm \\
+	\permCA   & \permCE
+\\ \\[20pt]
+	\permPC   & \permXC 
+\\	\downperm & \downperm \\
+	\permCP   & \permCX
+\end{array}
+\begin{array}{c}
+	\permCD \\ \downperm \\ \permDC
+\end{array}
+$}
+\]
+\caption{Cut-permutations}
+\end{figure}
 

### 2018-01-17 ALL1.tex
aargh try again

@@
 \begin{document}
-
-\begin{lemma}
-For $\link ab$ in a proof net $\net{\lambda_\star}AB$ and $\link[\tau]{\dual b}c$ in $\net{\kappa_\star}{\dual B}C$ the composition $\sigma_a\tau_c\dcom\fix{\sigma_b\tau\subdual b}=\mgu(a,c)$.
-\end{lemma}
-
-\begin{proof}
-Let $\rho=\mgu(a,c)$ and $\rho'=\sigma_a\tau_c\dcom\fix{\sigma_b\tau\subdual b}$.
+%
+%\begin{lemma}
+%For $\link ab$ in a proof net $\net{\lambda_\star}AB$ and $\link[\tau]{\dual b}c$ in $\net{\kappa_\star}{\dual B}C$ the composition $\sigma_a\tau_c\dcom\fix{\sigma_b\tau\subdual b}=\mgu(a,c)$.
+%\end{lemma}
+%
+%\begin{proof}
+%Let $\rho=\mgu(a,c)$ and $\rho'=\sigma_a\tau_c\dcom\fix{\sigma_b\tau\subdual b}$.
 Define the \defn{basis} $\floor{s,t}$ of the $\mgu$ of $s$ and $t$ to be the substitution map defined by $\floor{x,t}=\floor{t,x} = [t/x]$ and
-\[
-	\floor{P(s_1,\dots,s_n),P(t_1,\dots,t_n)} =
-	\floor{f(s_1,\dots,s_n),f(t_1,\dots,t_n)} =
-	\floor{s_1,t_1}\dots\floor{s_n,t_n}~.
-\]
-Write $\floor\sigma$ for the basis $\floor{a,b}$ of $\sigma$, $\floor\tau$ for that of $\tau$, and $\floor\rho$ for that of $\rho$.
-\end{proof}
-
-\end{document}
+%\[
+%	\floor{P(s_1,\dots,s_n),P(t_1,\dots,t_n)} =
+%	\floor{f(s_1,\dots,s_n),f(t_1,\dots,t_n)} =
+%	\floor{s_1,t_1}\dots\floor{s_n,t_n}~.
+%\]
+%Write $\floor\sigma$ for the basis $\floor{a,b}$ of $\sigma$, $\floor\tau$ for that of $\tau$, and $\floor\rho$ for that of $\rho$.
+%\end{proof}
+%
+%\end{document}
+%
 

### 2018-01-19 ALL1.tex
normalisation problem
intro eating space ...

@@
 % ===== General maths
+
+\newcommand\zeroleft[1]{\makebox[0pt][r]{$#1$}}
+\newcommand\zeroright[1]{\makebox[0pt][l]{$#1$}}
 
@@
 \begin{document}
-%
-%\begin{lemma}
-%For $\link ab$ in a proof net $\net{\lambda_\star}AB$ and $\link[\tau]{\dual b}c$ in $\net{\kappa_\star}{\dual B}C$ the composition $\sigma_a\tau_c\dcom\fix{\sigma_b\tau\subdual b}=\mgu(a,c)$.
-%\end{lemma}
-%
-%\begin{proof}
-%Let $\rho=\mgu(a,c)$ and $\rho'=\sigma_a\tau_c\dcom\fix{\sigma_b\tau\subdual b}$.
-Define the \defn{basis} $\floor{s,t}$ of the $\mgu$ of $s$ and $t$ to be the substitution map defined by $\floor{x,t}=\floor{t,x} = [t/x]$ and
-%\[
-%	\floor{P(s_1,\dots,s_n),P(t_1,\dots,t_n)} =
-%	\floor{f(s_1,\dots,s_n),f(t_1,\dots,t_n)} =
-%	\floor{s_1,t_1}\dots\floor{s_n,t_n}~.
-%\]
-%Write $\floor\sigma$ for the basis $\floor{a,b}$ of $\sigma$, $\floor\tau$ for that of $\tau$, and $\floor\rho$ for that of $\rho$.
-%\end{proof}
-%
-%\end{document}
-%
 
@@
 \section{Introduction}
+
+%Proof nets aim to be canonical representations of proofs. As graphs, they abstract away from the rule commutations of the sequent calculus. 
+%
+%In the study of \emph{proof nets} \cite{Girard-1987}, canonical graphical representations of proofs, the additive fragment of linear logic provides several interesting challenges.
+At the propositional level, the challenge is to capture the merging of the contexts $\Gamma$ in the additive product rule:
+%\[
+%	\vc{\infer[\Qrr*]{\seq\Gamma{A\*B}}{\seq\Gamma A & \seq\Gamma B}}~.
+%\]
+%One approach, perfect for the multiplicative fragment, is to create proof nets from sequent proofs by separating rules from their context: each sequent rule becomes a node in the graph, connected only to the primary formulas of the rule, in this case $A$, $B$, and $A\*B$.
+The benefit is a direct interpretation from sequent calculus;
+
+Additive linear logic is the logic of product $(\*)$ and sum $(\+)$.
+Proofs, over a sequent $A\vdash B$ or, here, $\seq{\dual A}B$, are built from the canonical morphisms: projections, injections, and diagonals.
+These are captured naturally in \emph{proof nets}, which consist of a set of \emph{links} between subformulas in $\dual A$ and in $B$, satisfying a simple geometric correctness condition.
+\[
+\begin{array}{c@{\qquad}c@{\qquad}c@{\qquad}c}
+	\begin{tikzpicture}[net]
+		\formula[y=1.2]{{\dual a}}
+		\formula[y=0]{a\*a}
+		\Vlink[red]{[-2]1,1}
+		\Vlink[red]{[2]1,3}
+	\end{tikzpicture}
+&
+	\begin{tikzpicture}[net]
+		\formula[y=1.2]{{\dual a}}
+		\formula[y=0]{a\+b}
+		\Vlink[red]{1,1}
+	\end{tikzpicture}
+&
+	\begin{tikzpicture}[net]
+		\formula[y=1.2]{{\dual a}\+{\dual b}}
+		\formula[y=0]{b\*a}
+		\Vlink[red]{1,3}
+		\Vlink[red]{3,1}
+	\end{tikzpicture}
+&
+	\begin{tikzpicture}[net]
+		\formula[y=1.2]{*{\phantom(}{\dual a}*{\phantom)}
+		 {{\+}}*({\dual b}*{\phantom)}
+		 {{\+}}*{\phantom(}{\dual c}*)}
+		\formula[y=0]{*(a*{\phantom)}
+		{{\*}}*{\phantom(}b*)
+		{{\*}}*{\phantom(}c*{\phantom)}}
+		\Vlink[red]{1,1}
+		\Vlink[red]{3,3}
+		\Vlink[red]{5,5}
+	\end{tikzpicture}
+\\
+	\text{\small diagonal}
+&	\text{\small injection}
+&	\text{\small symmetry}
+&	\text{\small associativity}
+\end{array}
+\]
+
+The logic is combinatorially rich, yet well-behaved and tractable: proof search \cite{} and proof net correctness \cite{} are linear in $|A|\times|B|$ (where $|A|$ is the size of the syntax tree of $A$); proof nets remain canonical and equally tractable when extended with the two units \cite{,}; and the first-order case is merely NP-complete \cite{}.
+
+At the same time, the ubiquity of its main operations, product and sum, mean the ideas and results it garners are widely applicable.
+It serves as a microcosmos for important ideas and observations: it fostered the \emph{connections method} of proof search \cite{}; it demonstrated the \emph{Blass problem} \cite{Abramsky} of game semantics, that sequential strategies do not in general have associative composition; and it is at the root of the study of fixed points in linear logic \cite{Santocanale}.
+
+The logic is of course part of MALL (multiplicative-additive linear logic), and its lessons are clearly visible in the second author's canonical proof nets \cite{Hughes-vanGlabbeek} for that fragment, as well as the first and second author's locally canonical \emph{conflict nets} \cite{Hughes-Heijltjes-2016}.
+But its proof nets also appear as the \emph{skew fibrations} in the second author's \emph{combinatorial proofs} for classical logic \cite{Hughes-}.
+To prepare the ground for the extension of the latter to first-order classical logic is one motivation for the current presentation.
+
+The main content of first-order proof, and the central challenge for first-order additive proof nets, is the \emph{witness assignment} to existential quantifiers.
+There are two, related obstacles in particular.
+First, the standard approach to evaluate a formula $\exists x.A$ is by a substitution $A[t/x]$, which destroys the subformula $A$.%
+%
+\footnote{Given $A[t/x]$ and $t$, it is not possible to unambiguously recover $A$, which may contain other occurrences of $t$ not originating in the substitution $[t/x]$.}
+%
+But the current, successful formulation of proof nets, as a set of links over a two-formula sequent, requires subformulas to remain intact.
+
+Second, the same existential quantification $\exists x.A$ may occur in different \emph{slices} (branches of a proof above a product), with different witnesses, as in the below proof.
+But the formulas--plus--links design has exactly one instance of $\exists x.A$.
+\[
+\vc{
+	\infer[\Qrr*]{\Seq{\exists x.A}{B\*C}}{
+	 \infer[\Qrr?s]{\Seq{\exists x.A}B}{\Seq{A[s/x]}B}
+	 &
+	 \infer[\Qrr?t]{\Seq{\exists x.A}C}{\Seq{A[t/x]}C}
+   }}
+~.
+\]
+
+We advance two solutions, both simple and radical.
+\defn{Witness nets} replace the \emph{implicit} substitutions of sequent proofs with \emph{explicit} substitutions, recorded at each link.
+An example is given below left.
+Second, \defn{unification nets} omit existential witnesses altogether, and reconstruct them by unification.
+
+* EXAMPLE *
+
+\subsection{Expansion trees}
+
+We observe that the presented solution is not the only one possible.
+In fact, a reasonable alternative could be the approach of \emph{expansion tree proofs} for higher-order classical logic \cite{Miller}.
+In this formulation, a formula $\exists x.A$ is interpreted, effectively, as the sum over all its instantiations $A[t/x]$ in the proof; e.g.\ $A[s/x]\+A[t/x]$ for the above proof fragment.
+
+We will use this approach implicitly to define a geometric correctness condition, in Section~\ref{sec:correctness}.
+The idea is as follows: for an existential formula $\exists x.A$ we collect all witnesses $t$ to $x$ present in the links of the proof, and then interpret $\exists x.A$ as the sum of all $A[t/x]$ to generate the \emph{slices} on which the criterion is based.
+
+The idea is closely related to Herbrand's Theorem \cite{Herbrand} and the \emph{compactness theorem}: semantically, $\exists x.A$ is equivalent to the infinite sum over all $A[t/x]$ for all terms $t$ in the language, or all elements $t$ of a model; for any individual proof, a finite set of terms (or finitely generated set of elements) suffices.
+
+For the definition of proof nets, we did not pursue this direction, and consider the present choice preferable for the following reasons.
+They retain the original structure of links between formulas, without requiring expansion trees.
+More importantly, as in the propositional case, they enable direct (non-inductive) composition by a relational composition of links.
+
+\[
+\begin{tikzpicture}[net]
+\formula[y=1.2]{\exists x.\forall y.~{\dual P}(x,y)}
+\formula[y=0]{\exists z.~P(s,z)\*P(t,z)}
+\Vlink[red,label={$\scriptstyle{[y/z,s/x]}~~$},l]{[-2]8,5}
+\Vlink[red,label={$~\scriptstyle{[y/z,t/x]}$}]{[2]8,12}
+\end{tikzpicture}
+\]
+
+\[
+\begin{tikzpicture}[net]
+\formula[y=1]{\exists x.\forall y.~{\dual P}(x,y)}
+\formula[y=0]{\exists z.~P(s,z)\*P(t,z)}
+\Vlink[red,label={$~\scriptstyle{[y/z,s/x]\mgu(s,t)}$}]{8,11}
+\end{tikzpicture}
+\]
+
+\[
+\begin{tikzpicture}[net]
+\formula[y=1]{\exists x.\forall y.~{\dual P}(x,y)}
+\formula[y=0]{\exists z.~P(s,z)\*P(t,z)}
+\Vlink[red,label={$\quad\scriptstyle{[s/x]\mgu(s,t)}$}]{8,1}
+\end{tikzpicture}
+\]
+
+\[
+\begin{tikzpicture}[net]
+\formula[y=1]{\exists x.\forall y.~{\dual P}(x,y)}
+\formula[y=0]{\exists z.~P(s,z)\*P(t,z)}
+\Vlink[red,label={$~~\scriptstyle{[s/x]\mgu(s,t)}$}]{4,1}
+\end{tikzpicture}
+\]
+
+\[
+\begin{tikzpicture}[net]
+\formula[y=1]{\exists x.\forall y.~{\dual P}(x,y)}
+\formula[y=0]{\exists z.~P(s,z)\*P(t,z)}
+\Vlink[red,label={$~\scriptstyle{\mgu(s,t)}$}]{1,1}
+\end{tikzpicture}
+\]
 
@@
 
-\subsection{Geometric correctness}
+\section{Geometric correctness}
 
@@
 
-\subsection{Composition}
+\section{Composition}
 
@@
 \]
-The \defn{composition} of two labelled pre-nets $(\net{\lambda_\Sigma^\Pi}AB)\comp(\net{\kappa_\Theta^\Phi}{\dual B}C)$ is then
-\[
-	\net{\{~\link XY^\pi\comp\link[\tau]{\dual Y}Z^\phi
+The \defn{composition} $\lambda_\Sigma^\Pi\comp\kappa_\Theta^\Phi$ of two linkings is the linking
+\[
+	\{~\link XY^\pi\comp\link[\tau]{\dual Y}Z^\phi
 		~\mid~
@@
 		\link[\tau]{\dual Y}Z^\phi\in\kappa_\Theta^\Phi~\}
-	}AC~.
-\]
-The composition of two witness pre-nets omits the proof annotations.
+\]
+The \defn{composition} $(\net{\lambda_\Sigma^\Pi}AB)\comp(\net{\kappa_\Theta^\Phi}{\dual B}C)$ of two pre-nets is the pre-net $\net{(\lambda_\Sigma^\Pi\comp\kappa_\Theta^\Phi)}AC$.
 \end{definition}
 % ..................................................
+
+These compositions may omit proof annotations and witness annotations.
 
@@
 \begin{theorem}
+\label{thm:composition}
 If proof nets $\net{\lambda_\Sigma}AB$ and $\net{\kappa_\Theta}{\dual B}C$ sequentialize to $\pi$ and $\phi$ respectively, then their composition $(\net{\lambda_\Sigma}AB)\comp(\net{\kappa_\Theta}{\dual B}C)$ sequentializes to a normal form $\psi$ of the proof
 \[
-	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq AC}{
+	\infer[\Qrr.]{\seq AC}{
 	 \Prf\pi AB & \Prf\phi{\dual B}C
@@
 % ..................................................
-\begin{theorem}
-If $[\prf\pi AB]$ is $\net{\lambda_\Sigma}AB$ then $\net\lambda AB$ unifying-sequentializes to $\pi'\leq \pi$.
-\end{theorem}
-
-\begin{proof}
-By Theorem~\ref{thm:proof->net->proof}, $\net{\lambda_\Sigma}AB$ sequentializes to $\pi$ in $(\scoal)$, and hence also in $(\ucoal)$.
-Then by Lemma~\ref{lem:ucoal generality} $\net{\lambda_\star}AB$ sequentializes to $\pi'\leq\pi$.
-\end{proof}
-% ..................................................
-
-\begin{theorem}
-If $\net\lambda AB$ sequentializes to $\pi$, then $[\pi]=\net{\lambda_\Sigma} AB$ for some $\Sigma$.
-\end{theorem}
-
-% ..................................................
 \begin{lemma}
+\label{lem:unifying implies strict coalescence}
 If $\net{\lambda_\star}AB$ unifying-sequentializes to $\pi$ then there exists a witness assignment $\Sigma$ and substitution $\rho$ such that $\net{\lambda_\Sigma}AB$ strict-sequentializes to $\pi$ and $\lambda_\Sigma=\lambda_\star\rho$.
@@
 \end{proof}
-
-% ..................................................
-
-\begin{lemma}
-If a labelled pre-net $\net{\lambda_\Sigma^\Pi}AB$ strict-sequentializes to $\pi$, then $(\net{\lambda_\Sigma^\Pi}AB)\rho$ strict-sequentializes to $\pi\rho$.
-\end{lemma}
+% ..................................................
+
+% ..................................................
+\begin{theorem}
+If $[\prf\pi AB]$ is $\net{\lambda_\Sigma}AB$ then $\net\lambda AB$ unifying-sequentializes to $\pi'\leq \pi$.
+\end{theorem}
 
 \begin{proof}
-By induction on the sequentialization sequence.
+By Theorem~\ref{thm:proof->net->proof}, $\net{\lambda_\Sigma}AB$ sequentializes to $\pi$ in $(\scoal)$, and hence also in $(\ucoal)$.
+Then by Lemma~\ref{lem:ucoal generality} $\net{\lambda_\star}AB$ sequentializes to $\pi'\leq\pi$.
+\end{proof}
+% ..................................................
+
+% ..................................................
+\begin{theorem}
+If $\net\lambda AB$ sequentializes to $\pi$, then $[\pi]=\net{\lambda_\Sigma} AB$ for some $\Sigma$.
+\end{theorem}
+
+\begin{proof}
+By Lemma~\ref{lem:unifying implies strict coalescence}, since $\net\lambda AB$ sequentializes to $\pi$ there is a net $\net{\lambda_\Sigma} AB$ that sequentializes to $\pi$.
+By Theorem~\ref{thm:net->proof->net}, $[\pi]=\net{\lambda_\Sigma} AB$.
+\end{proof}
+% ..................................................
+
+% ..................................................
+\begin{theorem}
+If $\net\lambda AB$ sequentializes to $\pi$ and $\net\kappa{\dual B}C$ to $\phi$ then their composition $\net{\lambda\comp\kappa}AC$ sequentializes to a proof $\psi''\leq\psi'$ where $\psi'$ is a normal form of the proof
+\[
+	\psi~=~
+	\vc{\infer[\Qrr.]{\seq AC}{
+	 \Prf\pi AB & \Prf\phi{\dual B}C
+	}}~.
+\]
+\end{theorem}
+
+\begin{proof}
+By Lemma~\ref{lem:unifying implies strict coalescence} there are witness labellings $\Sigma$ and $\Theta$ such that $\net{\lambda_\Sigma}AB$ strict-sequentializes to $\pi$ and $\net{\kappa_\Theta}{\dual B}C$ to $\phi$.
+By Theorem~\ref{thm:composition} their composition $(\net{\lambda_\Sigma\comp\kappa_\Theta)}AC$ strict-sequentializes to a normal form $\psi'$ of $\psi$.
+By Lemma~\ref{lem:ucoal generality} the net $\net{(\lambda\comp\kappa)_\star}AC$ unifying-sequentializes to $\psi''\leq\psi'$.
 \end{proof}
@@
 
+\begin{lemma}
+If a labelled pre-net $\net{\lambda_\Sigma^\Pi}AB$ strict-sequentializes to $\pi$, then $(\net{\lambda_\Sigma^\Pi}AB)\rho$ strict-sequentializes to $\pi\rho$.
+\end{lemma}
+
+\begin{proof}
+By induction on the sequentialization sequence.
+\end{proof}
+
+NORMALIZATION PROBLEM
+
+\begin{lemma}
+For $\link ab$ with $\sigma=\mgu(a,\dual b)$ in a proof net $\net{\lambda_\star}AB$ and $\link[\tau]{\dual b}c$ with $\tau=\mgu(b,c)$ in $\net{\kappa_\star}{\dual B}C$ the composition $\sigma_a\tau_c\dcom\fix{\sigma_b\tau\subdual b}$ is $\mgu(a,\dual c)$.
+\end{lemma}
+
+%
+%\begin{lemma}
+%For $\link ab$ in a proof net $\net{\lambda_\star}AB$ and $\link[\tau]{\dual b}c$ in $\net{\kappa_\star}{\dual B}C$ the composition $\sigma_a\tau_c\dcom\fix{\sigma_b\tau\subdual b}=\mgu(a,c)$.
+%\end{lemma}
+%
+%\begin{proof}
+%Let $\rho=\mgu(a,c)$ and $\rho'=\sigma_a\tau_c\dcom\fix{\sigma_b\tau\subdual b}$.
+Define the \defn{basis} $\floor{s,t}$ of the $\mgu$ of $s$ and $t$ to be the substitution map defined by $\floor{x,t}=\floor{t,x} = [t/x]$ and
+%\[
+%	\floor{P(s_1,\dots,s_n),P(t_1,\dots,t_n)} =
+%	\floor{f(s_1,\dots,s_n),f(t_1,\dots,t_n)} =
+%	\floor{s_1,t_1}\dots\floor{s_n,t_n}~.
+%\]
+%Write $\floor\sigma$ for the basis $\floor{a,b}$ of $\sigma$, $\floor\tau$ for that of $\tau$, and $\floor\rho$ for that of $\rho$.
+%\end{proof}
+%
 %\end{document}
+%
 
@@
 
-\[
-\begin{tikzpicture}[net]
-\formula[y=1.2]{\exists x.\forall y.~{\dual P}(x,y)}
-\formula[y=0]{\exists z.~P(s,z)\*P(t,z)}
-\Vlink[red,label={$\scriptstyle{[y/z,s/x]}~~$},l]{[-2]8,5}
-\Vlink[red,label={$~\scriptstyle{[y/z,t/x]}$}]{[2]8,12}
-\end{tikzpicture}
-\]
-
-\[
-\begin{tikzpicture}[net]
-\formula[y=1]{\exists x.\forall y.~{\dual P}(x,y)}
-\formula[y=0]{\exists z.~P(s,z)\*P(t,z)}
-\Vlink[red,label={$~\scriptstyle{[y/z,s/x]\mgu(s,t)}$}]{8,11}
-\end{tikzpicture}
-\]
-
-\[
-\begin{tikzpicture}[net]
-\formula[y=1]{\exists x.\forall y.~{\dual P}(x,y)}
-\formula[y=0]{\exists z.~P(s,z)\*P(t,z)}
-\Vlink[red,label={$\quad\scriptstyle{[s/x]\mgu(s,t)}$}]{8,1}
-\end{tikzpicture}
-\]
-
-\[
-\begin{tikzpicture}[net]
-\formula[y=1]{\exists x.\forall y.~{\dual P}(x,y)}
-\formula[y=0]{\exists z.~P(s,z)\*P(t,z)}
-\Vlink[red,label={$~~\scriptstyle{[s/x]\mgu(s,t)}$}]{4,1}
-\end{tikzpicture}
-\]
-
-\[
-\begin{tikzpicture}[net]
-\formula[y=1]{\exists x.\forall y.~{\dual P}(x,y)}
-\formula[y=0]{\exists z.~P(s,z)\*P(t,z)}
-\Vlink[red,label={$~\scriptstyle{\mgu(s,t)}$}]{1,1}
-\end{tikzpicture}
-\]
-
-\end{document}
-
 \begin{equation}

### 2018-01-19 ALL1.tex
added reference

@@
 The logic is of course part of MALL (multiplicative-additive linear logic), and its lessons are clearly visible in the second author's canonical proof nets \cite{Hughes-vanGlabbeek} for that fragment, as well as the first and second author's locally canonical \emph{conflict nets} \cite{Hughes-Heijltjes-2016}.
-But its proof nets also appear as the \emph{skew fibrations} in the second author's \emph{combinatorial proofs} for classical logic \cite{Hughes-}.
-To prepare the ground for the extension of the latter to first-order classical logic is one motivation for the current presentation.
+But its proof nets also appear as the \emph{skew fibrations} in the second author's \emph{combinatorial proofs} for classical logic \cite{Hughes-}, and in the third authors study of the \emph{medial rule} for classical logic~\cite{str:RTA07}.
+To prepare the ground for the extension of \emph{combinatorial proofs} to first-order classical logic is one motivation for the current presentation.
 

### 2018-01-19 ALL1.tex
main example
more intro, references

@@
 \newcommand\all{\textsc{all}}
+\newcommand\mall{\textsc{mall}}
 
@@
 
-Additive linear logic is the logic of product $(\*)$ and sum $(\+)$.
+Additive linear logic $(\all)$ is the logic of product $(\*)$ and sum $(\+)$.
 Proofs, over a sequent $A\vdash B$ or, here, $\seq{\dual A}B$, are built from the canonical morphisms: projections, injections, and diagonals.
-These are captured naturally in \emph{proof nets}, which consist of a set of \emph{links} between subformulas in $\dual A$ and in $B$, satisfying a simple geometric correctness condition.
+These are captured naturally in \emph{proof nets} \cite{Girard-1987,Hughes-vanGlabbeek-2005}, which consist of a set of \emph{links} between subformulas in $\dual A$ and in $B$, satisfying a simple geometric correctness condition.
 \[
@@
 
-The logic is combinatorially rich, yet well-behaved and tractable: proof search \cite{} and proof net correctness \cite{} are linear in $|A|\times|B|$ (where $|A|$ is the size of the syntax tree of $A$); proof nets remain canonical and equally tractable when extended with the two units \cite{,}; and the first-order case is merely NP-complete \cite{}.
+The logic is combinatorially rich, yet well-behaved and tractable: proof search \cite{Galmiche-Marion-1995,Galmiche-2000} and proof net correctness \cite{Heijltjes-Hughes-2015} are linear in $|A|\times|B|$ (with $|A|$ the size of the syntax tree of $A$); proof nets remain canonical and equally tractable when extended with the two units \cite{Heijltjes-2011,Heijltjes-Hughes-2015}; and the first-order case is merely NP-complete \cite{Heijltjes-Hughes-2015}.
 
 At the same time, the ubiquity of its main operations, product and sum, mean the ideas and results it garners are widely applicable.
-It serves as a microcosmos for important ideas and observations: it fostered the \emph{connections method} of proof search \cite{}; it demonstrated the \emph{Blass problem} \cite{Abramsky} of game semantics, that sequential strategies do not in general have associative composition; and it is at the root of the study of fixed points in linear logic \cite{Santocanale}.
-
-The logic is of course part of MALL (multiplicative-additive linear logic), and its lessons are clearly visible in the second author's canonical proof nets \cite{Hughes-vanGlabbeek} for that fragment, as well as the first and second author's locally canonical \emph{conflict nets} \cite{Hughes-Heijltjes-2016}.
-But its proof nets also appear as the \emph{skew fibrations} in the second author's \emph{combinatorial proofs} for classical logic \cite{Hughes-}, and in the third authors study of the \emph{medial rule} for classical logic~\cite{str:RTA07}.
+It serves as a microcosmos for important ideas and observations: it fostered the \emph{connections method} of proof search \cite{Galmiche-2000}; it demonstrated the \emph{Blass problem} \cite{Abramsky-2003} of game semantics, that sequential strategies do not in general have associative composition; and it is at the root of the study of fixed points in linear logic \cite{Santocanale-2002a}.
+The logic describes two-way communication~\cite{Cockett-Santocanale-2009}, and as such is a core part of \emph{session types}~\cite{Honda-1993}.
+
+{\all} is of course part of {\mall} (multiplicative-additive linear logic), and its lessons are clearly visible in the second author's canonical proof nets \cite{Hughes-vanGlabbeek-2005} for that fragment, as well as the first and second author's locally canonical \emph{conflict nets}~\cite{Hughes-Heijltjes-2016}.
+But its proof nets also appear as the \emph{skew fibrations} in the second author's \emph{combinatorial proofs} for classical logic~\cite{Hughes-2006-proofs}, and in the third authors study of the \emph{medial rule} for classical logic~\cite{str:RTA07}.
 To prepare the ground for the extension of \emph{combinatorial proofs} to first-order classical logic is one motivation for the current presentation.
@@
 Second, \defn{unification nets} omit existential witnesses altogether, and reconstruct them by unification.
-
-* EXAMPLE *
-
-\subsection{Expansion trees}
-
-We observe that the presented solution is not the only one possible.
-In fact, a reasonable alternative could be the approach of \emph{expansion tree proofs} for higher-order classical logic \cite{Miller}.
-In this formulation, a formula $\exists x.A$ is interpreted, effectively, as the sum over all its instantiations $A[t/x]$ in the proof; e.g.\ $A[s/x]\+A[t/x]$ for the above proof fragment.
-
-We will use this approach implicitly to define a geometric correctness condition, in Section~\ref{sec:correctness}.
-The idea is as follows: for an existential formula $\exists x.A$ we collect all witnesses $t$ to $x$ present in the links of the proof, and then interpret $\exists x.A$ as the sum of all $A[t/x]$ to generate the \emph{slices} on which the criterion is based.
-
-The idea is closely related to Herbrand's Theorem \cite{Herbrand} and the \emph{compactness theorem}: semantically, $\exists x.A$ is equivalent to the infinite sum over all $A[t/x]$ for all terms $t$ in the language, or all elements $t$ of a model; for any individual proof, a finite set of terms (or finitely generated set of elements) suffices.
-
-For the definition of proof nets, we did not pursue this direction, and consider the present choice preferable for the following reasons.
-They retain the original structure of links between formulas, without requiring expansion trees.
-More importantly, as in the propositional case, they enable direct (non-inductive) composition by a relational composition of links.
-
-\[
-\begin{tikzpicture}[net]
-\formula[y=1.2]{\exists x.\forall y.~{\dual P}(x,y)}
-\formula[y=0]{\exists z.~P(s,z)\*P(t,z)}
-\Vlink[red,label={$\scriptstyle{[y/z,s/x]}~~$},l]{[-2]8,5}
-\Vlink[red,label={$~\scriptstyle{[y/z,t/x]}$}]{[2]8,12}
+The example is below right.
+\[
+\begin{tikzpicture}[net]
+	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+	\Vlink[red,l,label={$\scriptstyle[f(x)/y\,,\,x/z]$~~}]{3,2}
+	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
 \end{tikzpicture}
-\]
-
-\[
-\begin{tikzpicture}[net]
-\formula[y=1]{\exists x.\forall y.~{\dual P}(x,y)}
-\formula[y=0]{\exists z.~P(s,z)\*P(t,z)}
-\Vlink[red,label={$~\scriptstyle{[y/z,s/x]\mgu(s,t)}$}]{8,11}
+\qquad\qquad
+\begin{tikzpicture}[net]
+	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+	\Vlink[red]{3,2}
+	\Vlink[blue]{5,4}
 \end{tikzpicture}
@@
 
-\[
-\begin{tikzpicture}[net]
-\formula[y=1]{\exists x.\forall y.~{\dual P}(x,y)}
-\formula[y=0]{\exists z.~P(s,z)\*P(t,z)}
-\Vlink[red,label={$\quad\scriptstyle{[s/x]\mgu(s,t)}$}]{8,1}
-\end{tikzpicture}
-\]
-
-\[
-\begin{tikzpicture}[net]
-\formula[y=1]{\exists x.\forall y.~{\dual P}(x,y)}
-\formula[y=0]{\exists z.~P(s,z)\*P(t,z)}
-\Vlink[red,label={$~~\scriptstyle{[s/x]\mgu(s,t)}$}]{4,1}
-\end{tikzpicture}
-\]
-
-\[
-\begin{tikzpicture}[net]
-\formula[y=1]{\exists x.\forall y.~{\dual P}(x,y)}
-\formula[y=0]{\exists z.~P(s,z)\*P(t,z)}
-\Vlink[red,label={$~\scriptstyle{\mgu(s,t)}$}]{1,1}
-\end{tikzpicture}
-\]
-
-Correctness and sequentialization for \all1 proof nets will be through \defn{coalescence}.
-This is a simple graph rewriting relation that gives top-down sequentialization, from the axioms to the conclusion of a proof.
-It is the additive counterpart to Danos \defn{contractibility} for multiplicative linear logic.
-
-We will define two coalescence relations, one \defn{strict} $(\scoal)$, for witness nets, and one \defn{unifying} $(\ucoal)$, for unification nets, in a later section.
-In the former, to join two slices the witness assignment must be the same; in the latter, witness assignments must be compatible, so that a common, more general witness map exists.
+Correctness and sequentialization for \all1 proof nets will be through \defn{coalescence}~\cite{Heijltjes-Hughes-2015,Hughes-Heijltjes-2016}, the additive counterpart to \defn{contractibility} for multiplicative linear logic~\cite{Danos-1990}.
+It is a simple graph rewrite relation that pushes links from the leaves towards the roots of a sequent, that is effectively top-down sequentialization (like its multiplicative counterpart~\cite{Guerrini-Masini-2001}).
+Figure~\ref{fig:main example} illustrates the process for the witness net above.
+In the example, a link between subformulas $A$ and $B$ carrying a substitution map $\sigma$ represents a sequent $\seq{A\sigma}{B\sigma}$.
+Each step (labelled $\star S$) corresponds to a proof rule (labelled $\star R$), by which the coalescence sequence generates the sequent proof.
+
+In addition, we will present a geometric correctness condition for witness nets, and define composition as direct,
+
+%In the former, to join two slices the witness assignment must be the same; in the latter, witness assignments must be compatible, so that a common, more general witness map exists.
+
+\begin{figure}
+\[
+\begin{array}{c}
+\begin{array}{@{}c@{~}c@{\qquad}c@{}}
+  \vc{
+  \begin{tikzpicture}[net]
+	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+	\Vlink[red,l,label={$\scriptstyle[f(x)/y\,,\,x/z]$~~}]{3,2}
+	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
+  \end{tikzpicture}}
+&&
+  \vc{
+  \begin{tikzpicture}[net]
+	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+	\Vlink[violet,l,label={$\scriptstyle\varnothing$~~}]{2,1}
+  \end{tikzpicture}}
+\\ \\[-5pt] \downarrow\scriptstyle{\srr+1} && \uparrow\scriptstyle\srr! \\ \\[-5pt]
+  \vc{
+  \begin{tikzpicture}[net]
+	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+	\Vlink[red,l,label={$\scriptstyle[f(x)/y\,,\,x/z]$~~~}]{4,2}
+	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
+  \end{tikzpicture}}
+&&
+  \vc{
+  \begin{tikzpicture}[net]
+	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+	\Vlink[violet,l,label={$\scriptstyle\varnothing$~~}]{1,1}
+  \end{tikzpicture}}  
+\\ \\[-5pt] \downarrow\scriptstyle\srr?,f(x) && \uparrow\scriptstyle\srr?,x \\ \\[-5pt]  
+  \vc{
+  \begin{tikzpicture}[net]
+	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+	\Vlink[red,l,label={$\scriptstyle[x/z]$~~}]{2,2}
+	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
+  \end{tikzpicture}} 
+&&  
+  \vc{
+  \begin{tikzpicture}[net]
+	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+	\Vlink[violet,l,label={$\scriptstyle[x/z]$~~~}]{[2]2,3}
+  \end{tikzpicture}}
+\\ \\[-5pt] \downarrow\scriptstyle{\srr+2} && \uparrow\scriptstyle\srr* \\ \\[-5pt]
+  \vc{
+  \begin{tikzpicture}[net]
+	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+	\Vlink[red,l,label={$\scriptstyle[x/z]$~~}]{2,2}
+	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{4,4}
+  \end{tikzpicture}}
+& \stackrel{\srr?,t}\scoal & 
+  \vc{
+  \begin{tikzpicture}[net]
+	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+	\Vlink[red,l,label={$\scriptstyle[x/z]$~~}]{2,2}
+	\Vlink[blue,r,label={~~~$\scriptstyle[x/z]$}]{[4]2,4}
+  \end{tikzpicture}}
+\end{array}
+\\ \\[20pt]
+	\color{violet}\infer[\color{black}\Qrr!]{\color{black}\Seq{\forall x.\exists y.\dual P(y)\+\dual Q(x,y)}{\exists z.P(f(z))\*Q(z,t)}}{
+	 \color{violet}\infer[\color{black}\Qrr?,x]{\color{black}\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{\exists z.P(f(z))\*Q(z,t)}}{
+	  \color{violet}\infer[\color{black}\Qrr*]{\color{black}\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{P(f(x))\*Q(x,t)}}{
+	   \color{red}\infer[\color{black}\Qrr?{f(x)}]{\color{black}\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{P(f(x))}}{
+	    \color{red}\infer[\color{black}\Qrr+1]{\color{black}\Seq{\dual P(f(x))\+\dual Q(x,f(x))}{P(f(x))}}{
+	     \color{red}\infer[\color{black}\Qrr1]{\color{black}\Seq{\dual P(f(x))}{P(f(x))}}{}
+	   }}&
+	   \color{blue}\infer[\color{black}\Qrr?t]{\color{black}\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{Q(x,t)}}{
+	    \color{blue}\infer[\color{black}\Qrr+2]{\color{black}\Seq{\dual P(t)\+\dual Q(x,t)}{Q(x,t)}}{
+	     \color{blue}\infer[\color{black}\Qrr1]{\color{black}\Seq{\dual Q(x,t)}{Q(x,t)}}{}
+	}}}}}
+\end{array}
+\]
+\caption{A coalescence and sequentialization example}
+\label{fig:example}
+\end{figure}
 
@@
 
+\subsection{Expansion trees}
+
+We observe that the presented solution is not the only one possible.
+In fact, a reasonable alternative could be the approach of \emph{expansion tree proofs} for higher-order classical logic \cite{Miller}.
+In this formulation, a formula $\exists x.A$ is interpreted, effectively, as the sum over all its instantiations $A[t/x]$ in the proof; e.g.\ $A[s/x]\+A[t/x]$ for the above proof fragment.
+
+We will use this approach implicitly to define a geometric correctness condition, in Section~\ref{sec:correctness}.
+The idea is as follows: for an existential formula $\exists x.A$ we collect all witnesses $t$ to $x$ present in the links of the proof, and then interpret $\exists x.A$ as the sum of all $A[t/x]$ to generate the \emph{slices} on which the criterion is based.
+
+The idea is closely related to Herbrand's Theorem \cite{Herbrand} and the \emph{compactness theorem}: semantically, $\exists x.A$ is equivalent to the infinite sum over all $A[t/x]$ for all terms $t$ in the language, or all elements $t$ of a model; for any individual proof, a finite set of terms (or finitely generated set of elements) suffices.
+
+For the definition of proof nets, we did not pursue this direction, and consider the present choice preferable for the following reasons.
+They retain the original structure of links between formulas, without requiring expansion trees.
+More importantly, as in the propositional case, they enable direct (non-inductive) composition by a relational composition of links.
+
 %$\seq{\,\exists x.P(x,x,s)\,}{\,\exists y.\dual P(t,y,y)}$
@@
 
-\subsection{Background and related work}
-
-\cite{Whitman-1941}
-\cite{Girard-1987}
-\cite{Galmiche-Marion-1995} % ALL proof search
-\cite{Girard-1996}
-\cite{Hu-1999}
-\cite{Galmiche-2000} % ALL connection net (Def 6.11.)
-\cite{Cockett-Seely-2001}
-\cite{Hughes-VanGlabbeek-2005}
-%\cite{Cockett-Santocanale-2009}
-\cite{Heijltjes-2011, Heijltjes-2012}
-\cite{Heijltjes-Hughes-2015}
-
-\cite{Danos-1990}
-\cite{Guerrini-Masini-2001}
-\cite{Guerrini-2011}
-
-\cite{Herbrand-1930}
-\cite{Heijltjes-2010}
+%\subsection{Background and related work}
+
+%
+%\cite{Whitman-1941}
+%\cite{Girard-1987}
+%\cite{Galmiche-Marion-1995} % ALL proof search
+%\cite{Girard-1996}
+%\cite{Hu-1999}
+%\cite{Galmiche-2000} % ALL connection net (Def 6.11.)
+%\cite{Cockett-Seely-2001}
+%\cite{Hughes-VanGlabbeek-2005}
+%%\cite{Cockett-Santocanale-2009}
+%\cite{Heijltjes-2011, Heijltjes-2012}
+%\cite{Heijltjes-Hughes-2015}
+%
+%\cite{Danos-1990}
+%\cite{Guerrini-Masini-2001}
+%\cite{Guerrini-2011}
+%
+%\cite{Herbrand-1930}
+%\cite{Heijltjes-2010}
 
@@
 \end{proof}
+
+\[
+\begin{array}{@{}ccccc@{}}
+  \vc{
+  \begin{tikzpicture}[net]
+	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+	\Vlink[red,l,label={$\scriptstyle[f(x)/y\,,\,x/z]$~~}]{3,2}
+	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
+  \end{tikzpicture}}
+& \scoal &
+  \vc{
+  \begin{tikzpicture}[net]
+	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+	\Vlink[red,l,label={$\scriptstyle[f(x)/y\,,\,x/z]$~~~}]{4,2}
+	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
+  \end{tikzpicture}}
+& \scoal &
+  \vc{
+  \begin{tikzpicture}[net]
+	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+	\Vlink[red,l,label={$\scriptstyle[x/z]$~~}]{2,2}
+	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
+  \end{tikzpicture}}
+\\ \\[-10pt] &&&& \downarrow \\ \\[-10pt]
+  \vc{
+  \begin{tikzpicture}[net]
+	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+	\Vlink[violet,l,label={$\scriptstyle[x/z]$~~~}]{[2]2,3}
+  \end{tikzpicture}}
+& \leftarrow &
+  \vc{
+  \begin{tikzpicture}[net]
+	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+	\Vlink[red,l,label={$\scriptstyle[x/z]$~~}]{2,2}
+	\Vlink[blue,r,label={~~~$\scriptstyle[x/z]$}]{[4]2,4}
+  \end{tikzpicture}}
+& \leftarrow &
+  \vc{
+  \begin{tikzpicture}[net]
+	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+	\Vlink[red,l,label={$\scriptstyle[x/z]$~~}]{2,2}
+	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{4,4}
+  \end{tikzpicture}}
+\\ \\[-10pt] \downarrow &&&& \\ \\[-10pt]
+  \vc{
+  \begin{tikzpicture}[net]
+	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+	\Vlink[violet,l,label={$\scriptstyle\varnothing$~~}]{2,1}
+  \end{tikzpicture}}
+& \scoal &
+  \vc{
+  \begin{tikzpicture}[net]
+	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+	\Vlink[violet,l,label={$\scriptstyle\varnothing$~~}]{1,1}
+  \end{tikzpicture}}
+\end{array}
+\]
+
+%\vc{\scalebox{0.5}{$
+%	\infer[\Qrr!]{\Seq{\forall x.\exists y.\dual P(y)\+\dual Q(x,y)}{\exists z.P(f(z))\*Q(z,t)}}{
+%	 \infer[\Qrr?,x]{\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{\exists z.P(f(z))\*Q(z,t)}}{
+%	  \infer[\Qrr*]{\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{P(f(x))\*Q(x,t)}}{
+%	   \infer[\Qrr?{f(x)}]{\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{P(f(x))}}{
+%	    \infer[\Qrr+1]{\Seq{\dual P(f(x))\+\dual Q(x,f(x))}{P(f(x))}}{
+%	     \infer[\Qrr1]{\Seq{\dual P(f(x))}{P(f(x))}}{}
+%	   }}&
+%	   \infer[\Qrr?t]{\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{Q(x,t)}}{
+%	    \infer[\Qrr+2]{\Seq{\dual P(t)\+\dual Q(x,t)}{Q(x,t)}}{
+%	     \infer[\Qrr1]{\Seq{\dual Q(x,t)}{Q(x,t)}}{}
+%	}}}}}
+
+%
+%\[
+%\begin{array}{@{}ccc@{}}
+%  \vc{
+%  \begin{tikzpicture}[net]
+%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+%	\Vlink[red,l,label={$\scriptstyle[f(x)/y\,,\,x/z]$~~}]{3,2}
+%	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
+%  \end{tikzpicture}}
+%& \stackrel{\srr+1}\scoal &
+%  \vc{
+%  \begin{tikzpicture}[net]
+%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+%	\Vlink[red,l,label={$\scriptstyle[f(x)/y\,,\,x/z]$~~~}]{4,2}
+%	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
+%  \end{tikzpicture}}
+%\\ \\[-5pt] && \downarrow\scriptstyle\srr?,f(x) \\ \\[-5pt]
+%  \vc{
+%  \begin{tikzpicture}[net]
+%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+%	\Vlink[red,l,label={$\scriptstyle[x/z]$~~}]{2,2}
+%	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{4,4}
+%  \end{tikzpicture}}
+%& \stackrel{\srr+2}\leftarrow &
+%  \vc{
+%  \begin{tikzpicture}[net]
+%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+%	\Vlink[red,l,label={$\scriptstyle[x/z]$~~}]{2,2}
+%	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
+%  \end{tikzpicture}}
+%\\ \\[-5pt] \downarrow\scriptstyle\srr?,t \\ \\[-5pt]  
+%  \vc{
+%  \begin{tikzpicture}[net]
+%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+%	\Vlink[red,l,label={$\scriptstyle[x/z]$~~}]{2,2}
+%	\Vlink[blue,r,label={~~~$\scriptstyle[x/z]$}]{[4]2,4}
+%  \end{tikzpicture}}
+%& \stackrel{\srr*}\scoal & 
+%  \vc{
+%  \begin{tikzpicture}[net]
+%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+%	\Vlink[violet,l,label={$\scriptstyle[x/z]$~~~}]{[2]2,3}
+%  \end{tikzpicture}}
+%\\ \\[-5pt] && \downarrow\scriptstyle\srr?,x \\ \\[-5pt]
+%  \vc{
+%  \begin{tikzpicture}[net]
+%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+%	\Vlink[violet,l,label={$\scriptstyle\varnothing$~~}]{1,1}
+%  \end{tikzpicture}}
+%& \stackrel{\srr!}\leftarrow &
+%  \vc{
+%  \begin{tikzpicture}[net]
+%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+%	\Vlink[violet,l,label={$\scriptstyle\varnothing$~~}]{2,1}
+%  \end{tikzpicture}}
+%\end{array}
+%\]

### 2018-01-20 ALL1.tex
prose up to page 10

@@
 
-\subjclass{F.4.1 [Mathematical logic and formal languages]: Mathematical logic--Proof theory}
+\subjclass{F.4.1: Mathematical logic--Proof theory}
 \keywords{Linear logic, First-order logic, Proof nets}
@@
 Both notions of proof net are defined through coalescence (the additive version of multiplicative contractibility), and for witness nets a geometric correctness criterion is provided.
-Both feature a global, one-shot composition operation.
+Both feature a global composition operation.
 \end{abstract}
@@
 \]
-
+%
 The logic is combinatorially rich, yet well-behaved and tractable: proof search \cite{Galmiche-Marion-1995,Galmiche-2000} and proof net correctness \cite{Heijltjes-Hughes-2015} are linear in $|A|\times|B|$ (with $|A|$ the size of the syntax tree of $A$); proof nets remain canonical and equally tractable when extended with the two units \cite{Heijltjes-2011,Heijltjes-Hughes-2015}; and the first-order case is merely NP-complete \cite{Heijltjes-Hughes-2015}.
@@
 It serves as a microcosmos for important ideas and observations: it fostered the \emph{connections method} of proof search \cite{Galmiche-2000}; it demonstrated the \emph{Blass problem} \cite{Abramsky-2003} of game semantics, that sequential strategies do not in general have associative composition; and it is at the root of the study of fixed points in linear logic \cite{Santocanale-2002a}.
-The logic describes two-way communication~\cite{Cockett-Santocanale-2009}, and as such is a core part of \emph{session types}~\cite{Honda-1993}.
+The logic describes two-way communication~\cite{Cockett-Santocanale-2009}, and is a core part of \emph{session types}~\cite{Honda-1993}.
 
@@
 But its proof nets also appear as the \emph{skew fibrations} in the second author's \emph{combinatorial proofs} for classical logic~\cite{Hughes-2006-proofs}, and in the third authors study of the \emph{medial rule} for classical logic~\cite{str:RTA07}.
-To prepare the ground for the extension of \emph{combinatorial proofs} to first-order classical logic is one motivation for the current presentation.
-
-The main content of first-order proof, and the central challenge for first-order additive proof nets, is the \emph{witness assignment} to existential quantifiers.
-There are two, related obstacles in particular.
-First, the standard approach to evaluate a formula $\exists x.A$ is by a substitution $A[t/x]$, which destroys the subformula $A$.%
+To prepare the ground for the extension of \emph{combinatorial proofs} to first-order classical logic is one motivation for the% current presentation.
+
+We present proof nets for first-order additive linear logic (\all1). The main content of first-order proof, and our central challenge, is the \emph{witness assignment} to existential quantifiers. 
+%
+The standard approach to evaluate a formula $\exists x.A$ is by a substitution $A[t/x]$, which destroys the subformula $A$.%
 %
@@
 %
-But the current, successful formulation of proof nets, as a set of links over a two-formula sequent, requires subformulas to remain intact.
-
-Second, the same existential quantification $\exists x.A$ may occur in different \emph{slices} (branches of a proof above a product), with different witnesses, as in the below proof.
-But the formulas--plus--links design has exactly one instance of $\exists x.A$.
+But the current, successful formulation of additive proof nets, as a set of links over a two-formula sequent, requires subformulas to remain intact.
+%
+Moreover, the same quantification $\exists x.A$ may occur in different \emph{slices} (branches of a proof above a product), with different witnesses, as below.
+But the \emph{formulas + links} design has only one instance of $\exists x.A$.
 \[
@@
 \]
-
-We advance two solutions, both simple and radical.
+%
+We advance two solutions.
 \defn{Witness nets} replace the \emph{implicit} substitutions of sequent proofs with \emph{explicit} substitutions, recorded at each link.
-An example is given below left.
-Second, \defn{unification nets} omit existential witnesses altogether, and reconstruct them by unification.
-The example is below right.
+\defn{Unification nets} omit existential witnesses altogether, and reconstruct them by unification.
+Respective examples are below.
 \[
@@
 \]
-
+%
 Correctness and sequentialization for \all1 proof nets will be through \defn{coalescence}~\cite{Heijltjes-Hughes-2015,Hughes-Heijltjes-2016}, the additive counterpart to \defn{contractibility} for multiplicative linear logic~\cite{Danos-1990}.
@@
 In the example, a link between subformulas $A$ and $B$ carrying a substitution map $\sigma$ represents a sequent $\seq{A\sigma}{B\sigma}$.
-Each step (labelled $\star S$) corresponds to a proof rule (labelled $\star R$), by which the coalescence sequence generates the sequent proof.
-
-In addition, we will present a geometric correctness condition for witness nets, and define composition as direct,
-
-%In the former, to join two slices the witness assignment must be the same; in the latter, witness assignments must be compatible, so that a common, more general witness map exists.
+Each coalescence step ($\star S$) corresponds to a proof rule ($\star R$), by which the sequence generates the sequent proof.
+
+In unification nets, existential witnesses are reconstructed during coalescence.
+The initial substitution map assigned to a link on atomic formulas $a=P(s_1,\dots,s_n)$ and $b=\dual P(t_1,\dots,t_n)$ is the most general unifier (\mgu) of $a$ and $\dual b$ (the first step in Figure~\ref{fig:unification example}).
+Coalescence then proceeds as for witness nets, except when joining two links from different slices with a product step, ($\urr*$) in Figure~\ref{fig:unification example}.
+Here, witness nets require both links to carry the same substitution map, while for unification nets a common, more general map is generated by unification.
+
+We include the following results for our \all1 proof nets.
+Witness nets are \emph{canonical} for the permutations of the sequent calculus, and we provide a geometric correctness condition.
+\emph{Composition} of unification nets (over $\seq AB$ and $\seq{\dual BC}$ into one over $\seq AC$) is remarkedly simple, as the relational composition of both sets of links.
+For composition of witness nets, in addition the witness assignments of links must be composed, which is done through a simple process of \emph{interaction + hiding} similar to those of game semantics \cite{Mimram-2011}.
+
+A companion paper \cite{Hughes-2018} explores unification nets for first-order \emph{multiplicative} linear logic, reporting drastic complexity improvements and equally straightforward proof net composition.
+
+% Hyland-Ong-2000,Abramsky-Jagadeesan-Malacaria-2000
+
+% ..................................................
 
@@
 	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-	\Vlink[violet,l,label={$\scriptstyle\varnothing$~~}]{2,1}
+	\Vlink[violet,l,label={$\scriptstyle\varnothing$~~}]{1,1}
   \end{tikzpicture}} 
@@
 	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-	\Vlink[violet,l,label={$\scriptstyle\varnothing$~~}]{1,1}
+	\Vlink[violet,l,label={$\scriptstyle\varnothing$~~}]{2,1}
   \end{tikzpicture}} 
@@
 \caption{A coalescence and sequentialization example}
-\label{fig:example}
+\label{fig:main example}
 \end{figure}
 
+% ..................................................
+
+\begin{figure}
+\[
+\vc{\begin{tikzpicture}[net]
+	\formula[y=1.2]{{\dual P}*{(x,x)}}
+	\formula[y=0]{P*{(y,s)}\*P*{(t,z)}}
+	\Vlink[red]{[-2]1,1}
+	\Vlink[blue]{[2]1,3}
+\end{tikzpicture}}
+\quad\ucoal\quad
+\vc{\begin{tikzpicture}[net]
+	\formula[y=1.2]{{\dual P}*{(x,x)}}
+	\formula[y=0]{P*{(y,s)}\*P*{(t,z)}}
+	\Vlink[red,l,label={$\scriptstyle[s/y,s/x]$~~}]{[-2]1,1}
+	\Vlink[blue,r,label={~~$\scriptstyle[t/z,t/x]$}]{[2]1,3}
+\end{tikzpicture}}
+\quad\stackrel{\urr*}\ucoal\quad
+\vc{\begin{tikzpicture}[net]
+	\formula[y=1.2]{{\dual P}*{(x,x)}}
+	\formula[y=0]{P*{(y,s)}\*P*{(t,z)}}
+	\Vlink[violet,r,label={~~$\scriptstyle[u/z,u/y,u/x]$}]{1,2}
+\end{tikzpicture}}
+\]
+\caption{Coalescence with unification; $u$ is the smallest term unifying $s$ and $t$} 
+\label{fig:unification example}
+\end{figure}
+
+% ..................................................
+
 % --------------------------------------------------
@@
 
-At the heart of a theory of proof nets is the question of proof identity, of when two proofs should be considered equivalent, and should thus map onto the same proof net. 
-%
-%It can be approached semantically, by asking whether two proofs are identified in every model; 
-%
+At the heart of a theory of proof nets is the question of \emph{proof identity}: when are two proofs equivalent?
+The answer determines which proofs should map onto the same proof net.
 The introduction of quantifiers creates an interesting issue: if two proofs differ by an immaterial choice of existential witness, should they be equivalent?
@@
 The proofs below left can only be distinguished even syntactically because the $\exists R$-rule makes the instantiating witness explicit.
-%
 Below right is an interesting intermediate variant: the witness $s$ or $t$ can be observed without explicit annotation in the $\exists R$-rule, but the choice is equally immaterial to the content of the proof as when the quantifier were vacuous.
@@
 \]
-In this paper we will not attempt to decisively settle the question of proof identity.
-Rather, we will present two natural and coherent notions of proof net, that represent two extremes.
-One, \defn{witness nets}, takes the choice of existential witnesses to be essential proof content, and rejects all three equivalences above.
-The other, \defn{unification nets}, removes any redundancy by rejecting explicit witnessing information altogether; instead, a most general witness for every quantifier is reconstructed by unification.
-
-\subsection{Expansion trees}
-
-We observe that the presented solution is not the only one possible.
-In fact, a reasonable alternative could be the approach of \emph{expansion tree proofs} for higher-order classical logic \cite{Miller}.
-In this formulation, a formula $\exists x.A$ is interpreted, effectively, as the sum over all its instantiations $A[t/x]$ in the proof; e.g.\ $A[s/x]\+A[t/x]$ for the above proof fragment.
-
-We will use this approach implicitly to define a geometric correctness condition, in Section~\ref{sec:correctness}.
-The idea is as follows: for an existential formula $\exists x.A$ we collect all witnesses $t$ to $x$ present in the links of the proof, and then interpret $\exists x.A$ as the sum of all $A[t/x]$ to generate the \emph{slices} on which the criterion is based.
-
-The idea is closely related to Herbrand's Theorem \cite{Herbrand} and the \emph{compactness theorem}: semantically, $\exists x.A$ is equivalent to the infinite sum over all $A[t/x]$ for all terms $t$ in the language, or all elements $t$ of a model; for any individual proof, a finite set of terms (or finitely generated set of elements) suffices.
-
-For the definition of proof nets, we did not pursue this direction, and consider the present choice preferable for the following reasons.
-They retain the original structure of links between formulas, without requiring expansion trees.
+In this paper we will not attempt to settle the question of proof identity.
+Rather, our two notions of proof net each represent a natural and coherent perspective, at either end of the spectrum.
+\emph{Witness nets} make all existential witnesses explicit, including those to vacuous quantifiers, rejecting all three equivalences above.
+\emph{Unification nets} leave all witnesses implicit, thus identifying all proofs modulo witness assignment, and validating all three equivalences.
+
+\subsection{Monomial nets and Expansion Trees}
+
+Proof nets with additives and quantifiers exist as \emph{monomial nets} \cite{Girard-1996}, where slices are managed explicitly with \emph{monomial weights}.
+These nets are not generally canonical: they admit the permutation (and duplication) of proof rules past implicit \emph{contractions}.
+We believe (though have not technically verified) that additive monomial nets include, and could be restricted to, canonical forms.
+These would be equivalent to the following approach.
+
+\emph{Expansion tree proofs} for classical logic \cite{Miller-1987,Heijltjes-2010} provide another approach to canonicity for first-order quantification.
+In this formulation, a formula $\exists x.A$ is interpreted as the sum (or classically, \emph{disjunction}) over a fixed number of instantiations $A[t_1/x]\+\dots\+A[t_n/x]$.
+The idea can be traced to Herbrand's Theorem \cite{Herbrand-1930}: $\exists x.A$ is equivalent to the infinite sum over $A[t/x]$ for all terms $t$ in the language, but for any given proof a finite set of terms suffices.
+
+We use this approach implicitly for our geometric correctness condition for witness nets (Section~\ref{sec:correctness}), which generalizes the existing \emph{slice-based} criterion for additive proof nets \cite{Hughes-vanGlabbeek-2005}.
+In constructing the slices over a formula, we interpret $\exists x.A$ by an \emph{expansion} $A[t_1/x]\+\dots\+A[t_n/x]$, where the witnesses $t_1$ through $t_n$ are collected from the substitution maps of the links in the proof net.
+
+For the definition of proof nets, we did not pursue this direction, and consider the present choice preferable.
+Witness nets and unification nets retain the original structure of \emph{formulas + links}, without requiring expansion trees.
 More importantly, as in the propositional case, they enable direct (non-inductive) composition by a relational composition of links.
+Finally, available space does not permit a detailed exposition, which we defer to a journal version.
 
@@
 %
-Negation $(\dual{\,\cdot\,})$ is applied to predicate symbols, $\dual P$, as a matter of convenience.
+Negation $(\dual{\,\cdot\,})$ is applied to predicate symbols, $\dual P$ as a matter of convenience.
 The \defn{dual} $\dual A$ of an arbitrary formula $A$ is given by DeMorgan.
@@
 A \defn{sequent} $\seq AB$ is a pair of formulas $A$ and $B$.
-A sequent calculus for \all1 is given in Figure~\ref{fig:sequent calculus}, where each rule has a symmetric counterpart that applies to the first formula in the sequent.
+A sequent calculus for \all1 is given in Figure~\ref{fig:sequent calculus}, where each rule has a symmetric counterpart for the first formula in the sequent.
 We write $\prf\pi AB$ for a proof $\pi$ with conclusion sequent $\seq AB$.
@@
 We abbreviate by $y\in\sigma$ that a variable $y$ occurs free in the range of~$\sigma$, i.e., $y\in\fv(t_i)$ for some $i\leq n$.
-The map $\sigma\minus x$ is undefined on $x$ and otherwise as $\sigma$, we write $\sigma\res V$ for the restriction of $\sigma$ to a set of variables $V$, and $\varnothing$ for the \defn{empty} witness map.
+The map $\sigma\minus x$ is undefined on $x$ and otherwise as $\sigma$, we write $\sigma\res V$ for the restriction of $\sigma$ to a set of variables $V$, and $\varnothing$ for the empty witness map.
 %
@@
 	\item[Freshness]
-For a link $\link CD$ over $\seq AB$, other variables in the range of $\sigma$ are \emph{fresh}: distinct from any existentially quantified variable in $\seq AB$.
+For a link $\link CD$ over $\seq AB$, other variables in the range of $\sigma$ are \emph{fresh}: distinct from existentially quantified variables in $\seq AB$, and from those of other links.
 \end{description}
@@
 Hence we need to maintain the separation of the conclusion $\seq AB$ into the substitutions $\sigma$ and the subformulas $A'$ and $B'$ of the conclusion of the proof net.
-\lutz{every referee will ask for an example here.}
+%
+For an example, we refer to Figure~\ref{fig:main example}: the de-sequentialization of the sequent proof is the first pre-net of the coalescence sequence.
 
@@
 \]
-
-% ..................................................
-
-\begin{figure}
-\[
-\begin{array}{ccc@{\hspace{50pt}}ccc}
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{C}
-    	\formula[y=1]{D*{_1}{{\+}}D*{_2}}
-    	\Vlink[red,label={$\scriptstyle\sigma~$},l]{1,1}
-    \end{tikzpicture}}
-&\scoal& 
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{C}
-    	\formula[y=1]{D*{_1}{{\+}}D*{_2}}
-    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,2}
-    \end{tikzpicture}}
-&
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{C}
-    	\formula[y=1]{\exists x.D}
-    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,4}
-    \end{tikzpicture}}
-&\stackrel{x\,\in\,\dom\sigma}\scoal&
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{C}
-    	\formula[y=1]{\exists x.D}
-    	\Vlink[red,label={~$\scriptstyle{\sigma\minus x}$}]{1,1}
-    \end{tikzpicture}}   
-\\ \\   
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{C}
-    	\formula[y=1]{D*{_1}{{\*}}D*{_2}}
-    	\Vlink[red,label={$\scriptstyle\sigma~$},l]{[-1]1,1}
-    	\Vlink[red,label={~$\scriptstyle\sigma$}]{[1]1,3}
-    \end{tikzpicture}}
-&\scoal&
-	\vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{C}
-    	\formula[y=1]{D*{_1}{{\*}}D*{_2}}
-    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,2}
-    \end{tikzpicture}}   
-&
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{C}
-    	\formula[y=1]{\forall x.D}
-    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,4}
-    \end{tikzpicture}}
-&\stackrel{x\,\notin\,\sigma}\scoal&
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{C}
-    	\formula[y=1]{\forall x.D}
-    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,1}
-    \end{tikzpicture}}
-\end{array}
-\]
-\caption{Coalescence rules}
-\label{fig:coalescence}
-\end{figure}
-
-% ..................................................
-
 \begin{definition}
@@
 \end{definition}
-
-% ..................................................
-
-\lutz{I guess there should be an example here.}
-
+% ..................................................
+
+For an example of coalescence, see Figure~\ref{fig:main example} in the introduction.
+
+% ..................................................
 \begin{definition}
@@
 \end{definition}
-
-% ..................................................
-
+% ..................................................
+
+We conclude this section by establishing that sequentialization and de-sequentialization for witness nets are inverses.
+
+% ..................................................
 \begin{theorem}
@@
 \end{proof}
-
-% ..................................................
-
+% ..................................................
+
+% ..................................................
 \begin{theorem}
@@
 \end{proof}
+% ..................................................
+
+% ..................................................
+\begin{figure}
+\[
+\begin{array}{ccc@{\hspace{50pt}}ccc}
+    \vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{C}
+    	\formula[y=1]{D*{_1}{{\+}}D*{_2}}
+    	\Vlink[red,label={$\scriptstyle\sigma~$},l]{1,1}
+    \end{tikzpicture}}
+&\scoal& 
+    \vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{C}
+    	\formula[y=1]{D*{_1}{{\+}}D*{_2}}
+    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,2}
+    \end{tikzpicture}}
+&
+    \vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{C}
+    	\formula[y=1]{\exists x.D}
+    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,4}
+    \end{tikzpicture}}
+&\stackrel{x\,\in\,\dom\sigma}\scoal&
+    \vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{C}
+    	\formula[y=1]{\exists x.D}
+    	\Vlink[red,label={~$\scriptstyle{\sigma\minus x}$}]{1,1}
+    \end{tikzpicture}}   
+\\ \\   
+    \vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{C}
+    	\formula[y=1]{D*{_1}{{\*}}D*{_2}}
+    	\Vlink[red,label={$\scriptstyle\sigma~$},l]{[-1]1,1}
+    	\Vlink[red,label={~$\scriptstyle\sigma$}]{[1]1,3}
+    \end{tikzpicture}}
+&\scoal&
+	\vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{C}
+    	\formula[y=1]{D*{_1}{{\*}}D*{_2}}
+    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,2}
+    \end{tikzpicture}}   
+&
+    \vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{C}
+    	\formula[y=1]{\forall x.D}
+    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,4}
+    \end{tikzpicture}}
+&\stackrel{x\,\notin\,\sigma}\scoal&
+    \vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{C}
+    	\formula[y=1]{\forall x.D}
+    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,1}
+    \end{tikzpicture}}
+\end{array}
+\]
+\caption{Coalescence rules}
+\label{fig:coalescence}
+\end{figure}
+% ..................................................
 
@@
 \section{Geometric correctness}
+\label{sec:correctness}
 
@@
 
-As in the propositional case, we define a slice of a sequent $\seq AB$ as a set of potential links, of which exactly one must be realized in a proof net $\net{\lambda_\Sigma}AB$.
+As in the propositional case \cite{Hughes-vanGlabbeek-2005}, we define a \defn{slice} of a sequent $\seq AB$ as a set of potential links, of which exactly one must be realized in a proof net $\net{\lambda_\Sigma}AB$.
+We extend the propositional criterion in two ways:
+\begin{itemize}
+	\item
+When defining slices, we interpret an existential quantification $\exists x.A$ as a sum over all witnesses $t_i$ to $x$ that occur in the pre-net,  $A[t_1/x]\+\dots\+A[t_n/x]$.
+This captures the non-permutability of a product rule over distinct existential instantiations, as below left.
+
+	\item
+We define a \defn{dependency} relation between a universal quantification $\forall x.A$ and an instantiation $B[t/y]$ of $\exists x.B$ where the \defn{eigenvariable} $x$ occurs free in $t$ (a standard approach to first-order quantification \cite{Miller-1987,Girard-1996,Heijltjes-2010,Mimram-2011}).
+For each link, we require the dependency to be \emph{acyclic}, which amounts to \emph{slice-wise} first-order correctness.
+It captures the non-permutability of universal and existential sequent rules due to the \emph{eigenvariable condition} of the former, as below right.
+\end{itemize}
+
+\[
+\vc{
+	\infer[\Qrr*]{\Seq{\exists x.A}{B\*C}}{
+	 \infer[\Qrr?s]{\Seq{\exists x.A}B}{\Seq{A[s/x]}B}
+	 &
+	 \infer[\Qrr?t]{\Seq{\exists x.A}C}{\Seq{A[t/x]}C}
+   }}
+\qquad\qquad
+\vc{
+	\infer[\Qrr!]{\Seq{\forall x.A}{\exists y.B}}{
+	 \infer[\Qrr?t]{\Seq A{\exists x.B}}{\Seq AB[t/y]}
+   }}
+   \quad\text{where }x\in\fv(t)
+\]
+
 For a witness linking $\lambda_\Sigma$ and variable $x$, write $\Sigma(x)\subseteq\terms$ for the \defn{witness set} of $x$, which collects the terms assigned to $x$ by the witness maps in $\Sigma$ for every link in $\lambda$:
@@
 % ..................................................
-
 \begin{definition}[Slice]
@@
 \end{definition}
-
 % ..................................................
@@
 As in the propositional case, for correctness we will require that each slice is a singleton.
+We will further define a \defn{dependency} condition to ensure that the order in which quantifiers are instantiated is sound, corresponding to the \emph{eigenvariable condition} on the $\qrr!$-rule of sequent calculus.
+For simplicity, we define the condition on individual links rather than slices.
+
+%As in the propositional case, for correctness we will require that each slice is a singleton.
 In addition, within each slice we need to ensure that the order in which quantifiers are instantiated is sound.
@@
 For simplicity we will define the dependency condition on individual links rather than on slices.
-% (since each slice will be a singleton).
-
+
+\begin{definition}
 In a pre-net $\net{\lambda_\Sigma}AB$, let the \defn{column} of a link $\link CD$ be the set of pairs 
@@
 \]
-with an order $(\dep)$ given by: $(X,\rho)\dep(Y,\tau)$ if $X\leq Y$ or $Y$ occurs as $\forall x.Y$ and $x\in\rho$.
-
-%It is expected that for a more involved logic that includes multiplicative connectives, a dependency condition such as the below one needs to be applied to a slice instead.
-%
-
-% ..................................................
-
+with a \defn{dependency} order $(\dep)$: $(X,\rho)\dep(Y,\tau)$ if $X\leq Y$ or $Y$ occurs as $\forall x.Y$ and $x\in\rho$.
+\end{definition}
+
+% ..................................................
 \begin{definition}
@@
 \end{definition}
-
-% ..................................................
-
+% ..................................................
+
+In the remainder of this section we will establish that the two correctness conditions, by coalescence and by slicing, are equivalent.
+The geometric condition further gives \emph{strong} coalescence: since it is preserved, no coalescence step yields an incorrect, and thus non-coalescing, pre-net.
+Finally, canonicity follows by inspecting the critical pairs of sequentialization.
+
+% ..................................................
 \newcounter{lemcorrect}
@@
 \section{Composition}
+
+In this section we will describe the composition of two witness nets by a global operation.
+It consists of the relational composition of both linkings, as in the propositional case, where for each pair of links that are being connected, their witness maps are composed.
+Since each link corresponds to a slice, the operation is effectively first-order composition \cite{Mimram-2011} applied slice-wise.
+
+\[
+\begin{tikzpicture}[net]
+	\formula[right,y=1.2]{\exists v.A}
+	\formula[right,y=0]{*{\forall x.\exists y.\forall z.\,}P}
+	\Vlink[red,l,label={$\scriptstyle[v/z,f(x)/y]$~~}]{1,1}
+	\formula[right,y=-.5]{*{\exists x.\forall y.\exists z.\,}{\dual P}}
+	\formula[right,y=-1.7]{C}
+	\Vlink[blue,l,label={$\scriptstyle[t/x,g(y)/z]$~~}]{1,1}
+\end{tikzpicture}
+\qquad
+\Rightarrow
+\qquad
+\begin{tikzpicture}[net]
+	\formula[right,y=1.2]{A}
+	\formula[right,y=-1.7]{C}
+	\Vlink[blue,l,label={$\scriptstyle[t/x,g(y)/z]$~~}]{1,1}
+\end{tikzpicture}
+\]
+
+To compose two links $\link ab$ and $\link[\tau]{\dual b}c$, the substitutions on the  $\sigma_b$ and $\tau\subdual b$
+
+\todo{example: $\forall x.\exists y.\forall z.P$ with $[f(x)/y]$ cut against $\exists x.\forall y.\exists z.\dual P$ with $[a/x,g(y)/z]$.}
+
+The \defn{domain-preserving composition} of two witness maps $\sigma\dcom\tau$ is the map $(\sigma\tau)\res{\dom\sigma}$.
+
+The \defn{least fixed point} $\fix\sigma$ of a witness map $\sigma$ is the least map $\rho$ satisfying $\rho = \rho\sigma$.
+It is the shortest sequence $\fix\sigma=\sigma\sigma\dots\sigma$ such that no variable is both in the domain and range of $\fix\sigma$.
+Where it is used, in the composition of the witness maps of two links, we will need to demonstrate that it is well defined.
+
+% ..................................................
+\begin{definition}
+The \defn{composition} $\link AB^\pi\comp\link[\tau]{\dual B}C^\phi$ of two proof links is $\link[\rho]AC^\psi$ where
+\[
+	\rho = \sigma_A\tau_C\dcom\fix{\sigma_B\tau\subdual B}
+\qquad\text{and}\qquad
+	\psi = ~\vcenter{
+	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq {A\rho}{B\rho}}{
+	 \left(\vcenter{\deduce{\seq{A\sigma}{B\sigma}\vphantom{\dual B}}{\vphantom\phi\pi}}\right)\fix{\sigma_B\tau\subdual B}
+	&\left(\vcenter{\deduce{\seq{\dual B\tau}{C\tau}}{\phi}}\right)\fix{\sigma_B\tau\subdual B}
+	}}~.
+\]
+The \defn{composition} $\lambda_\Sigma^\Pi\comp\kappa_\Theta^\Phi$ of two linkings is the linking
+\[
+	\{~\link XY^\pi\comp\link[\tau]{\dual Y}Z^\phi
+		~\mid~
+		\link XY^\pi\in{\lambda_\Sigma^\Pi}
+		~,~
+		\link[\tau]{\dual Y}Z^\phi\in\kappa_\Theta^\Phi~\}
+\]
+The \defn{composition} $(\net{\lambda_\Sigma^\Pi}AB)\comp(\net{\kappa_\Theta^\Phi}{\dual B}C)$ of two pre-nets is the pre-net $\net{(\lambda_\Sigma^\Pi\comp\kappa_\Theta^\Phi)}AC$.
+\end{definition}
+% ..................................................
 
@@
 
-The \defn{domain-preserving composition} of two witness maps $\sigma\dcom\tau$ is the map $(\sigma\tau)\res{\dom\sigma}$.
-
-The \defn{least fixed point} $\fix\sigma$ of a witness map $\sigma$ is the least map $\rho$ satisfying $\rho = \rho\sigma$.
-It is the shortest sequence $\fix\sigma=\sigma\sigma\dots\sigma$ such that no variable is both in the domain and range of $\fix\sigma$.
-Where it is used, in the composition of the witness maps of two links, we will need to demonstrate that it is well defined.
-
-% ..................................................
-\begin{definition}
-The \defn{composition} $\link AB^\pi\comp\link[\tau]{\dual B}C^\phi$ of two proof links is $\link[\rho]AC^\psi$ where
-\[
-	\rho = \sigma_A\tau_C\dcom\fix{\sigma_B\tau\subdual B}
-\qquad\text{and}\qquad
-	\psi = ~\vcenter{
-	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq {A\rho}{B\rho}}{
-	 \left(\vcenter{\deduce{\seq{A\sigma}{B\sigma}\vphantom{\dual B}}{\vphantom\phi\pi}}\right)\fix{\sigma_B\tau\subdual B}
-	&\left(\vcenter{\deduce{\seq{\dual B\tau}{C\tau}}{\phi}}\right)\fix{\sigma_B\tau\subdual B}
-	}}~.
-\]
-The \defn{composition} $\lambda_\Sigma^\Pi\comp\kappa_\Theta^\Phi$ of two linkings is the linking
-\[
-	\{~\link XY^\pi\comp\link[\tau]{\dual Y}Z^\phi
-		~\mid~
-		\link XY^\pi\in{\lambda_\Sigma^\Pi}
-		~,~
-		\link[\tau]{\dual Y}Z^\phi\in\kappa_\Theta^\Phi~\}
-\]
-The \defn{composition} $(\net{\lambda_\Sigma^\Pi}AB)\comp(\net{\kappa_\Theta^\Phi}{\dual B}C)$ of two pre-nets is the pre-net $\net{(\lambda_\Sigma^\Pi\comp\kappa_\Theta^\Phi)}AC$.
-\end{definition}
-% ..................................................
-
 These compositions may omit proof annotations and witness annotations.
@@
 \lutz{why the fixpoint?}
-
-\todo{example: $\forall x.\exists y.\forall z.P$ with $[f(x)/y]$ cut against $\exists x.\forall y.\exists z.\dual P$ with $[a/x,g(y)/z]$.}
 

### 2018-01-21 ALL1.tex
Composition prose

@@
 
-In this section we will describe the composition of two witness nets by a global operation.
+\newlength\seriously
+\setlength\seriously\parindent
+\parbox[b]{.6\columnwidth}{
+We will describe the composition of two witness nets by a global operation.
 It consists of the relational composition of both linkings, as in the propositional case, where for each pair of links that are being connected, their witness maps are composed.
-Since each link corresponds to a slice, the operation is effectively first-order composition \cite{Mimram-2011} applied slice-wise.
-
-\[
-\begin{tikzpicture}[net]
-	\formula[right,y=1.2]{\exists v.A}
+As links correspond to slices, the operation is effectively first-order composition~\cite{Mimram-2011} applied slice-wise.
+
+\setlength\parindent\seriously
+\indent
+Cut-elimination rules for \all1 are given in Figure~\ref{fig:cut-elim}; the needed permutations are in the Appendix, Figure~\ref{fig:cut-permutations}.
+}
+\quad
+\begin{tikzpicture}[net]
+	\formula[right,y=1.2]{*{\exists v.}{\dual P}}
 	\formula[right,y=0]{*{\forall x.\exists y.\forall z.\,}P}
@@
 	\formula[right,y=-.5]{*{\exists x.\forall y.\exists z.\,}{\dual P}}
-	\formula[right,y=-1.7]{C}
+	\formula[right,y=-1.7]{P}
 	\Vlink[blue,l,label={$\scriptstyle[t/x,g(y)/z]$~~}]{1,1}
+	\path(0,-2)--(1,-2);
 \end{tikzpicture}
-\qquad
-\Rightarrow
-\qquad
-\begin{tikzpicture}[net]
-	\formula[right,y=1.2]{A}
-	\formula[right,y=-1.7]{C}
-	\Vlink[blue,l,label={$\scriptstyle[t/x,g(y)/z]$~~}]{1,1}
+\quad
+\begin{tikzpicture}[net]
+	\formula[right,y=1.2]{*{\exists v.}{\dual P}}
+	\formula[right,y=-1.7]{P}
+	\Vlink[violet,l,label={$\Rightarrow\quad\scriptstyle[g(f(t))/v]$~~}]{1,1}
+	\path(0,-2)--(1,-2);
 \end{tikzpicture}
-\]
-
-To compose two links $\link ab$ and $\link[\tau]{\dual b}c$, the substitutions on the  $\sigma_b$ and $\tau\subdual b$
-
-\todo{example: $\forall x.\exists y.\forall z.P$ with $[f(x)/y]$ cut against $\exists x.\forall y.\exists z.\dual P$ with $[a/x,g(y)/z]$.}
-
+
+We use the example on the right to illustrate the composition of links.
+To eliminate the central cut, on $\forall x.\exists y.\forall z.P$ and $\exists x.\forall y.\exists z.\dual P$, the explicit substitutions for both formulas must be effectuated.
+An inductive procedure, as in sequent calculus, could apply them from outside in: first $[t/x]$, then $[f(t)/y]$ (previously $[f(x)/y]$), then $[g(f(t))/z]$ (previously $[g(y)/z]$).
+
+For a direct definition, to compose two links $\link ab$ and $\link[\tau]{\dual b}c$, the substitutions into the cut-formula $\sigma_b$ and $\tau\subdual b$ must be applied as often as needed, up to the depth of quantifiers above $b$, to the terms in the range of the remaining substitutions, $\sigma_a$ and $\tau_c$.
+To formalize this, we will use the following notions:
+%
+\begin{itemize}
+	\item
 The \defn{domain-preserving composition} of two witness maps $\sigma\dcom\tau$ is the map $(\sigma\tau)\res{\dom\sigma}$.
-
+	\item
 The \defn{least fixed point} $\fix\sigma$ of a witness map $\sigma$ is the least map $\rho$ satisfying $\rho = \rho\sigma$. 
-It is the shortest sequence $\fix\sigma=\sigma\sigma\dots\sigma$ such that no variable is both in the domain and range of $\fix\sigma$.
-Where it is used, in the composition of the witness maps of two links, we will need to demonstrate that it is well defined.
+\end{itemize}
+%
+The latter is the shortest sequence $\fix\sigma=\sigma\sigma\dots\sigma$ such that no variable is both in the domain and range of $\fix\sigma$.
+This is not necessarily finite; in our composition operations, finiteness is ensured by the correctness conditions on proof nets.
 
@@
 The \defn{composition} $(\net{\lambda_\Sigma^\Pi}AB)\comp(\net{\kappa_\Theta^\Phi}{\dual B}C)$ of two pre-nets is the pre-net $\net{(\lambda_\Sigma^\Pi\comp\kappa_\Theta^\Phi)}AC$.
+These compositions may omit proof annotations and witness annotations.
 \end{definition}
@@
 
-These compositions may omit proof annotations and witness annotations.
-
 The composition of two links is strongly related to composition of strategies in game semantics.
@@
 
-%	\net{\{~\link[\rho]XZ~\mid~\link XY\in{\lambda_\Sigma}~,~\link[\tau]{\dual Y}Z\in\kappa_\Theta~,~\rho = (\sigma\cyc\tau)\res{\ex AX\,\cup\,\ex CZ}~\}~}AC
-%~\rho=\sigma_A\tau_{\smash{\,\dual{\!B}}\vphantom B}\cup\tau_C\sigma_B~
-%(\sigma\res{\ex AX})(\tau\res{\ex{\dual B}{\dual Y}})\cup(\tau\res{\ex CZ})(\sigma\res{\ex BY})
-
-\cite{Mimram-2011}
-
-\lutz{why the fixpoint?}
-
 In the following we will demonstrate that composition gives the desired result: if a net $L$ sequentializes to $\pi$ and $R$ to $\phi$, then $L\comp R$ sequentializes to a normal form of the composition of $\pi$ and $\phi$ with a cut.
 To this end we will explore how composition and sequentialization interact.
-We will consider the critical pairs of sequentialization with composition, and demonstrate how they are resolved.
-
-\lutz{some itemizing environment?}
-
-The first critical pair of composition (downward as $\Rightarrow$) and sequentialization is the following.
-We consider the composition of pre-nets on $\seq AB$ and $\seq{\dual B}C$ where $B=B_1\*B_2$, with a synchronized sequentialization step on both pre-nets.
+We will consider the critical pairs of sequentialization $(\scoal)$ with composition $(\Rightarrow)$ given in Figures~\ref{fig:crit1}--\ref{fig:crit3}, and demonstrate how they are resolved.
+
+\begin{itemize}
+	\item 
+$\seq A{B_1{\*}B_2}$ ; $\seq{\dual B_1{\+}\dual B_2}C$\quad (Figure~\ref{fig:crit1})
+\\
+Since the existential covers of $B$ and $B_1$ are the same, $\sigma_B\tau\subdual B = \sigma_{B_1}\tau\subdual{B_1}$ and $\rho=\rho'$.
+It then follows that $\psi'$ cut-eliminates in one step to $\psi$.
+
+	\item
+$\seq A{\exists x.B}$ ; $\seq{\forall x.\dual B}C$\quad (Figure~\ref{fig:crit2})
+\\	
+Since $x$ is not free in the range of $\tau$, and (by the freshness convention) nor in the range of $\sigma$, we have that $\fix{\sigma_B\tau\subdual B}$ is $\fix[1pt]{(\sigma_B\minus x)\tau\subdual B}$ plus the substitution $[\sigma(x)/x]$.
+Then $\rho=\rho'$ (as $x$ does not occur in the range of $\sigma_A\tau_C$) and $\psi'$ reduces to $\psi$ in a single cut-elimination step.
+
+	\item
+$\seq AB$ ; $\seq{\dual B}{\exists x.C}$\quad (Figure~\ref{fig:crit3})
+\\
+Observe that since $x$ occurs in $C$ but not $B$, it is not in the domain of $\tau_B$, so that $\tau_B\minus x$ is just $\tau_B$.
+Then $\rho'=\rho\minus x$, and the diagram is closed by a sequentialization step (from left to right) that extends $\psi$ with an existential introduction rule, to a proof equivalent to $\psi'$:
+\[
+	\infer[\!\!\scriptstyle{\qrr?{\rho(x)}}]{\Seq{A\rho'}{\exists x.C\rho'}}{
+	 \Prf\psi{A\rho}{C\rho}
+	}
+\]
+\end{itemize}
+
+% ..................................................
+\begin{figure}
 \[
@@
 \]
-Since the existential covers of $B$ and $B_1$ are the same, $\sigma_B\tau\subdual B = \sigma_{B_1}\tau\subdual{B_1}$ and $\rho=\rho'$.
-It then follows that $\psi'$ cut-eliminates in one step to $\psi$.
-
-The next critical pair is the following.
+\caption{The critical pair $\seq A{B_1{\*}B_2}$ ; $\seq{\dual B_1{\+}\dual B_2}C$}
+\label{fig:crit1}
+\end{figure}
+% ..................................................
+\begin{figure}
 \[
@@
 \]
-
-Since $x$ is not free in the range of $\tau$, and (by the freshness convention) nor in the range of $\sigma$, we have that $\fix{\sigma_B\tau\subdual B}$ is $\fix[1pt]{(\sigma_B\minus x)\tau\subdual B}$ plus the substitution $[\sigma(x)/x]$.
-Then $\rho=\rho'$ (as $x$ does not occur in the range of $\sigma_A\tau_C$) and $\psi'$ reduces to $\psi$ in a single cut-elimination step.
-
-\willem{Dominic: plz check grammar above.}
-
+\caption{The critical pair $\seq A{\exists x.B}$ ; $\seq{\forall x.\dual B}C$}
+\label{fig:crit2}
+\end{figure}
+% ..................................................
+\begin{figure}
 \[
@@
 \]
-Observe that since $x$ occurs in $C$ but not $B$, it is not in the domain of $\tau_B$, so that $\tau_B\minus x$ is just $\tau_B$.
-Then $\rho'=\rho\minus x$, and the diagram is closed by a sequentialization step (from left to right) that extends $\psi$ with an existential introduction rule, to a proof equivalent to $\psi'$:
-\[
-	\infer[\!\!\scriptstyle{\qrr?{\rho(x)}}]{\Seq{A\rho'}{\exists x.C\rho'}}{
-	 \Prf\psi{A\rho}{C\rho}
-	}
-\]
+\caption{The critical pair $\seq AB$ ; $\seq{\dual B}{\exists x.C}$}
+\label{fig:crit3}
+\end{figure}
+% ..................................................
 

### 2018-01-21 ALL1.tex
done. W out.

@@
   \texttt{w.b.heijltjes@bath.ac.uk}}
-\affil[2]{
-  \texttt{}}
+\affil[2]{Apple, Inc.\\
+  \texttt{dominich@gmail.com}}
 \affil[3]{INRIA \&\ \'Ecole Polytechnique, Palaiseau, France\\
@@
 We present two versions of our proof nets.
-One, called witness nets, retains explicit witnessing information to existential quantification.
-For the other, called unification nets, this information is absent but can be reconstructed through unification.
-Unification nets embody a main contribution of the paper: the observation that first-order witnessing information can be left implicit, and reconstructed effectively.
+One, witness nets, retains explicit witnessing information to existential quantification.
+For the other, unification nets, this information is absent but can be reconstructed through unification.
+Unification nets embody a main contribution of the paper: first-order witness information can be left implicit, and reconstructed effectively.
 
@@
 \begin{proof}
-See appendix.
+See the appendix.
 \end{proof}
@@
 From left to right is by inspection of the critical pairs of sequentialization ($\scoal$).
-From right to left is by inspection of the rule permutations in Figure~\ref{fig:permutations} in the Appendix.
+From right to left is by inspection of the rule permutations in Figure~\ref{fig:permutations} in the appendix.
 \end{proof}
@@
 \indent
-Cut-elimination rules for \all1 are given in Figure~\ref{fig:cut-elim}; the needed permutations are in the Appendix, Figure~\ref{fig:cut-permutations}.
+Cut-elimination rules for \all1 are given in Figure~\ref{fig:cut-elim}; the needed permutations are in the appendix, Figure~\ref{fig:cut-permutations}.
 }
@@
 \end{tikzpicture}
-\quad
 \begin{tikzpicture}[net]
@@
 	\psi = ~\vcenter{
-	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq {A\rho}{B\rho}}{
+	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq {A\rho}{C\rho}}{
 	 \left(\vcenter{\deduce{\seq{A\sigma}{B\sigma}\vphantom{\dual B}}{\vphantom\phi\pi}}\right)\fix{\sigma_B\tau\subdual B}
@@
 
-\begin{itemize}
-	\item 
-$\seq A{B_1{\*}B_2}$ ; $\seq{\dual B_1{\+}\dual B_2}C$\quad (Figure~\ref{fig:crit1})
-\\
-Since the existential covers of $B$ and $B_1$ are the same, $\sigma_B\tau\subdual B = \sigma_{B_1}\tau\subdual{B_1}$ and $\rho=\rho'$.
-It then follows that $\psi'$ cut-eliminates in one step to $\psi$.
-
-	\item
-$\seq A{\exists x.B}$ ; $\seq{\forall x.\dual B}C$\quad (Figure~\ref{fig:crit2})
-\\	
-Since $x$ is not free in the range of $\tau$, and (by the freshness convention) nor in the range of $\sigma$, we have that $\fix{\sigma_B\tau\subdual B}$ is $\fix[1pt]{(\sigma_B\minus x)\tau\subdual B}$ plus the substitution $[\sigma(x)/x]$.
-Then $\rho=\rho'$ (as $x$ does not occur in the range of $\sigma_A\tau_C$) and $\psi'$ reduces to $\psi$ in a single cut-elimination step.
-
-	\item
-$\seq AB$ ; $\seq{\dual B}{\exists x.C}$\quad (Figure~\ref{fig:crit3})
-\\
-Observe that since $x$ occurs in $C$ but not $B$, it is not in the domain of $\tau_B$, so that $\tau_B\minus x$ is just $\tau_B$.
-Then $\rho'=\rho\minus x$, and the diagram is closed by a sequentialization step (from left to right) that extends $\psi$ with an existential introduction rule, to a proof equivalent to $\psi'$:
-\[
-	\infer[\!\!\scriptstyle{\qrr?{\rho(x)}}]{\Seq{A\rho'}{\exists x.C\rho'}}{
-	 \Prf\psi{A\rho}{C\rho}
-	}
-\]
-\end{itemize}
-
-% ..................................................
-\begin{figure}
+\newcommand\yA{2.7}
+\newcommand\yB{1.65}
+\newcommand\yC{1.05}
+
+% ..................................................
+\begin{figure}[p]
 \[
@@
     \begin{tikzpicture}[net]
-        \formula[y=3]{A}
-        \formula[y=1.8]{B*{_1}\*B*{_2}}
+        \formula[y=\yA]{A}
+        \formula[y=\yB]{B*{_1}\*B*{_2}}
         \Vlink[red,label={$\scriptstyle{\pi,\sigma\vphantom)~}$},l]{[-2]1,1}
         \Vlink[red,label={$\scriptstyle{~\pi'\!,\sigma\vphantom)}$},r]{[2]1,3}
-        \formula[y=1.2]{{\dual B}*{_1}\+{\dual B}*{_2}}
+        \formula[y=\yC]{{\dual B}*{_1}\+{\dual B}*{_2}}
         \formula[y=0]{C}
@@
     & 
-    \begin{array}{c}\scoal\\[40pt]\scoal\end{array}
+    \begin{array}{c}\scoal\\[36pt]\scoal\end{array}
     &
@@
     \begin{tikzpicture}[net]
-        \formula[y=3]{A}
-        \formula[y=1.8]{B*{_1}\*B*{_2}}
+        \formula[y=\yA]{A}
+        \formula[y=\yB]{B*{_1}\*B*{_2}}
         \Vlink[red,label={$\scriptstyle{\pi''\!\!,\sigma\vphantom)~}$},l]{1,2}
-        \formula[y=1.2]{{\dual B}*{_1}\+{\dual B}*{_2}}
+        \formula[y=\yC]{{\dual B}*{_1}\+{\dual B}*{_2}}
         \formula[y=0]{C}
@@
     \end{tikzpicture}}
-\\\\[-5pt] \Downarrow && \Downarrow \\\\[-5pt]
-    \vc{
-    \begin{tikzpicture}[net]
-        \formula[y=1.2]{A}
+\\\\[-7pt] \Downarrow && \Downarrow \\\\[-7pt]
+    \vc{
+    \begin{tikzpicture}[net]
+        \formula[y=\yC]{A}
         \formula[y=0]{C}
@@
     \begin{tikzpicture}[net]
-        \formula[y=1.2]{A}
+        \formula[y=\yC]{A}
         \formula[y=0]{C}
@@
 % ..................................................
-\begin{figure}
+\begin{figure}[p]
 \[
@@
     \begin{tikzpicture}[net]
-        \formula[y=3]{A}
-        \formula[y=1.8]{\exists x.B}
+        \formula[y=\yA]{A}
+        \formula[y=\yB]{\exists x.B}
         \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\pi,\sigma\vphantom)}$}},r]{1,4}
-        \formula[y=1.2]{\forall x.{\dual B}}
+        \formula[y=\yC]{\forall x.{\dual B}}
         \formula[y=0]{C}
@@
     & 
-    \begin{array}{c}\scoal\\[40pt]\stackrel{x\,\notin\,\tau\vphantom)}\scoal\end{array}
+    \begin{array}{c}\scoal\\[36pt]\stackrel{x\,\notin\,\tau\vphantom)}\scoal\end{array}
     &
@@
     \begin{tikzpicture}[net]
-        \formula[y=3]{A}
-        \formula[y=1.8]{\exists x.B}
+        \formula[y=\yA]{A}
+        \formula[y=\yB]{\exists x.B}
         \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\pi',\sigma\minus x\vphantom)}$}},r]{1,1}
-        \formula[y=1.2]{\forall x.{\dual B}}
+        \formula[y=\yC]{\forall x.{\dual B}}
         \formula[y=0]{C}
@@
     \end{tikzpicture}}
-\\\\ \Downarrow && \Downarrow \\\\
-    \vc{ 
-    \begin{tikzpicture}[net]
-        \formula[y=1.2]{A}
+\\\\[-7pt] \Downarrow && \Downarrow \\\\[-7pt]
+    \vc{ 
+    \begin{tikzpicture}[net]
+        \formula[y=\yC]{A}
         \formula[y=0]{C}
@@
     \begin{tikzpicture}[net]
-        \formula[y=3]{A}
-        \formula[y=1.8]{B}
+        \formula[y=\yA]{A}
+        \formula[y=\yB]{B}
         \Vlink[red,label={\makebox[0pt][l]{~$\scriptstyle{\pi,\sigma\vphantom)}$}},r]{1,1}
-        \formula[y=1.2]{{\dual B}}
+        \formula[y=\yC]{{\dual B}}
         \formula[y=0]{\exists x.C}
@@
     & 
-    \begin{array}{c}\\[45pt]\scoal\end{array}
+    \begin{array}{c}\\[36pt]\scoal\end{array}
     &
@@
     \end{tikzpicture}}
-\\\\ \Downarrow && \Downarrow \\\\
-    \vc{ 
-    \begin{tikzpicture}[net]
-        \formula[y=1.2]{A}
+\\\\[-7pt] \Downarrow && \Downarrow \\\\[-7pt]
+    \vc{ 
+    \begin{tikzpicture}[net]
+        \formula[y=\yC]{A}
         \formula[y=0]{\exists x.C}
@@
     \begin{tikzpicture}[net]
-        \formula[y=1.2]{A}
+        \formula[y=\yC]{A}
         \formula[y=0]{\exists x.C}
@@
 
+\begin{itemize}
+	\item 
+$\seq A{B_1{\*}B_2}$ ; $\seq{\dual B_1{\+}\dual B_2}C$\quad (Figure~\ref{fig:crit1})
+\\
+Since the existential covers of $B$ and $B_1$ are the same, $\sigma_B\tau\subdual B = \sigma_{B_1}\tau\subdual{B_1}$ and $\rho=\rho'$.
+It then follows that $\psi'$ cut-eliminates in one step to $\psi$.
+
+	\item
+$\seq A{\exists x.B}$ ; $\seq{\forall x.\dual B}C$\quad (Figure~\ref{fig:crit2})
+\\	
+Since $x$ is not free in the range of $\tau$, and (by the freshness convention) nor in the range of $\sigma$, we have that $\fix{\sigma_B\tau\subdual B}$ is $\fix[1pt]{(\sigma_B\minus x)\tau\subdual B}$ plus the substitution $[\sigma(x)/x]$.
+Then $\rho=\rho'$ (as $x$ does not occur in the range of $\sigma_A\tau_C$) and $\psi'$ reduces to $\psi$ in a single cut-elimination step.
+
+	\item
+$\seq AB$ ; $\seq{\dual B}{\exists x.C}$\quad (Figure~\ref{fig:crit3})
+\\
+Observe that since $x$ occurs in $C$ but not $B$, it is not in the domain of $\tau_B$, so that $\tau_B\minus x$ is just $\tau_B$.
+Then $\rho'=\rho\minus x$, and the diagram is closed by a sequentialization step (from left to right) that extends $\psi$ with an existential introduction rule, to a proof equivalent to $\psi'$:
+\[
+	\infer[\!\!\scriptstyle{\qrr?{\rho(x)}}]{\Seq{A\rho'}{\exists x.C\rho'}}{
+	 \Prf\psi{A\rho}{C\rho}
+	}
+\]
+\end{itemize}
 There are three further critical pairs, for a proof net on $\seq AB$ composed with one on $\seq {\dual B}{C_1{\+}C_2}$, one on $\seq {\dual B}{C_1{\*}C_2}$, and one on $\seq {\dual B}{\forall x.C}$.
@@
 
-% ..................................................
+Resolving these critical pairs gives the soundness of the composition operation, per the following theorem. We abbreviate a cut on proofs $\prf\pi AB$ and $\prf\phi{\dual B}C$ by $\pi\comp\phi$.
+
+% ..................................................
+\newcounter{thmcomposition}
+\setcounter{thmcomposition}{\thetheorem}
 \begin{theorem}
 \label{thm:composition}
-If proof nets $\net{\lambda_\Sigma}AB$ and $\net{\kappa_\Theta}{\dual B}C$ sequentialize to $\pi$ and $\phi$ respectively, then their composition $(\net{\lambda_\Sigma}AB)\comp(\net{\kappa_\Theta}{\dual B}C)$ sequentializes to a normal form $\psi$ of the proof
-\[
-	\infer[\Qrr.]{\seq AC}{
-	 \Prf\pi AB & \Prf\phi{\dual B}C
-	}
-\]
+If proof nets $\net{\lambda_\Sigma}AB$ and $\net{\kappa_\Theta}{\dual B}C$ sequentialize to $\pi$ and $\phi$ respectively, then their composition $(\net{\lambda_\Sigma}AB)\comp(\net{\kappa_\Theta}{\dual B}C)$ sequentializes to a normal form $\psi$ of $\pi\comp\phi$.
+%the proof
+%\[
+%	\infer[\Qrr.]{\seq AC}{
+%	 \Prf\pi AB & \Prf\phi{\dual B}C
+%	}
+%\]
 \end{theorem}
@@
 \begin{proof}
-By Corollary~\ref{cor:strong coalescence} the proof nets $L=\net{\lambda_\Sigma}AB$ and $R=\net{\kappa_\Theta}{\dual B}C$ strongly coalesce.
-We may then interleave their coalescence sequences as follows: if a synchronized step in $L$ and $R$ on the interface $B$ and $\dual B$ is available, apply it; otherwise perform steps in $L$ on $A$ and in $R$ on $C$ until it is.
-This gives the following combined sequence.
-\[
-\begin{array}{c@{~}c@{~}c@{~}l@{~}c@{~}l@{~}c@{~}l@{~}c}
-	L &{}={}& L_1 & ~\scoal^?~ & L_2 & ~\scoal^?~ & \dots & ~\scoal^?~ & L_n 
-\\
-	R &{}={}& R_1 & ~\scoal^?~ & R_2 & ~\scoal^?~ & \dots & ~\scoal^?~ & R_n 
-\\[5pt]
-	\Downarrow && \Downarrow && \Downarrow &&&& \Downarrow 
-\\[5pt]
-	L\comp R & = & L_1\comp R_1 & ~\scoal~ & L_2\comp R_2 & ~\scoal~ & \dots & ~\scoal~ & L_n\comp R_n
-\end{array}
-\]
-(Here, $(\scoal^?)$ is the relation $(\scoal)\cup(=)$, but we assume that at least $L_i\scoal L_{i+1}$ or $R_i\scoal R_{i+1}$.)
-%
-The path along the top and right of this diagram sequentializes $L$ to $\pi'$ and $R$ to $\phi'$ (equivalent to $\pi$ and $\phi$ respectively), and then composes to $L_n\comp R_n = \net{\{\link[\varnothing]AC^{\psi'}\}}AC$ with
-\[
-	\psi' = \vc{\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq AC}{\Prf{\pi'}AB & \Prf{\phi'}{\dual B}C}}~.
-\]
-
-Each square of the diagram converges as one of the critical pairs of sequentialization and composition discussed above.
-Then each path along the diagram from top left ($L$ and $R$) to bottom right $(L_n\comp R_n)$ gives a sequentialization, with cuts, of $L_n\comp R_n$.
-Let the path taking the vertical step from $L_i$ and $R_i$ to $L_i\comp R_i$ sequentialize to $\psi_i$, so that $\psi_n=\psi'$.
-By the way each square converges, we have that $\psi_i$ is reached from $\psi_{i+1}$ by a cut-elimination or permutation step.
-
-Finally, in $L$ and $R$ every link is an axiom link.
-Any link in $L\comp R$ is composed from two links $\link ab$ in $L$ and $\link[\tau]{\dual b}c$ in $R$, which yields $\link[\rho]ac$ where $\rho = \sigma_a\tau_c\dcom\fix{\sigma_b\tau\subdual b}$.
-This sequentializes to the axiom $\infer{\seq{a\rho}{c\rho}}{}$, which is in normal form.
-Then $L\comp R$ is a proof net (it has an axiom linking and it coalesces), and it sequentializes to a normal form of $\psi$.
-%
-%which sequentialize respectively to. 
-%\[
-%	\infer{\seq{a\sigma}{b\sigma}}{} 
-%	\qquad\text{and}\qquad
-%	\infer{\seq{\dual b\tau}{c\tau}}{}~.
-%\]
-%We have the link 
+See the appendix.
 \end{proof}
@@
 
-%\[
-%	\vc{
-%	 \infer[\Qrr*]{\seq{A\*B}{\exists x.C}}{
-%	  \infer[\Qrr?y]{\seq A{\exists x.C}}{\seq AC}
-%	  &
-%	  \infer[\Qrr?z]{\seq B{\exists x.C}}{\seq BC}
-%	}}
-%	\quad\sim\quad
-%	\vc{
-%	 \infer[\Qrr?y]{\seq{A\*B}C}{
-%	  \infer[\Qrr*]{\seq{A\*B}{\exists x.C}}{
-%	   \seq AC
-%	   &
-%	   \seq BC
-%	}}}
-%\]
-
-A proof $\pi$ is \defn{more general} than $\pi'$, written $\pi\leq\pi'$, if there is a substitution map $\rho$ such that $\pi\rho=\pi'$.
-
+In this final section we explore a second notion of \all1 proof net: \defn{unification nets} omit any witness information, which is then reconstructed by coalescence.
+This yields a natural notion of \emph{most general} proof net, where every other proof net is obtained by introducing more witness information.
+Conversely, every witness net has an underlying unification net, that sequentializes to a \emph{most general} proof.
+
+We consider a proof $\prf\pi AB$ \defn{more general} than $\prf{\pi'}AB$, written $\pi\leq\pi'$, if there is a substitution map $\rho$ such that $\pi\rho=\pi'$.
+Unlike for proof nets, this notion is not so natural for sequent proofs: in the permutation of existential and product rules below, from left to right $u$ must be generated as the least term more general than $s$ and $t$; from right to left, $s$ and $t$ cannot be reconstructed from $u$, and must be retrieved from their respective subproofs.
 \[
@@
 
-We define the following further operations on witness maps.
-\[
-\begin{tabular}{@{}p{.10\textwidth}@{}p{.90\textwidth}@{}}
-	\quad$\sigma\gen\tau$
-&
-	A witness map $\sigma$ is \defn{more general} than $\tau$,  
-	$\sigma\gen\tau$, if there is a map $\rho$ such that 
-	$\sigma\rho=\tau$.
-\\[4pt]	
-	\quad$\sigma\coh\tau$
-&
-	Two witness maps $\sigma$ and $\tau$ are \defn{coherent}, $\sigma\coh\tau$,
-	if there is a map $\rho$ such that $\sigma\rho=\tau\rho$.
-\\[4pt]
-	\quad$\sigma\join\tau$
-&
-	The \defn{join} $\sigma\join\tau$ of two coherent witness maps is the least map $\rho$ such that $\sigma\gen\rho$ and $\tau\gen\rho$.
-\end{tabular}%
-\]
+To reconstruct witnesses by unification, we define the following operations.
+\\
+\makebox[28pt][l]{$\sigma\gen\tau$}:\quad
+	A witness map $\sigma$ is \defn{more general} than $\tau$ if there is a map $\rho$ such that $\sigma\rho=\tau$.
+\\
+\makebox[28pt][l]{$\sigma\coh\tau$}:\quad
+	Two witness maps $\sigma$ and $\tau$ are \defn{coherent} if there is a map $\rho$ such that $\sigma\rho=\tau\rho$.
+\\
+\makebox[28pt][l]{$\sigma\join\tau$}:\quad
+	The \defn{join} of coherent witness maps is the least map $\rho$ such that $\sigma\gen\rho$ and $\tau\gen\rho$.
+
+%\[
+%\begin{tabular}{@{}p{.08\textwidth}@{}p{.92\textwidth}@{}}
+%	$\sigma\gen\tau$
+%&
+%	A witness map $\sigma$ is \defn{more general} than $\tau$,  
+%	$\sigma\gen\tau$, if there is a map $\rho$ such that 
+%	$\sigma\rho=\tau$.
+%\\%[4pt]	
+%	$\sigma\coh\tau$
+%&
+%	Two witness maps $\sigma$ and $\tau$ are \defn{coherent}, $\sigma\coh\tau$,
+%	if there is a map $\rho$ such that $\sigma\rho=\tau\rho$.
+%\\%[4pt]
+%	$\sigma\join\tau$
+%&
+%	The \defn{join} $\sigma\join\tau$ of two coherent witness maps is the least map $\rho$ such that $\sigma\gen\rho$ and $\tau\gen\rho$.
+%\end{tabular}%
+%\]
+
 %
@@
 
-Observe that unifying coalescence includes strict coalescence, $(\scoal)\subseteq(\ucoal)$.
-
 % ..................................................
@@
 In the above definition, note that $\lambda_\star^\star=(\lambda_\star)^*$ is the initial proof labelling of $\lambda_\star$, which assigns an axiom rule to each axiom link.
+For a minimal example, see Figure~\ref{fig:unification example} in the introduction.
+Observe also that unifying coalescence includes strict coalescence, $(\scoal)\subseteq(\ucoal)$.
+The following two lemmata relate sequentialization for witness nets and unification nets.
 
@@
 
+We can then show that sequentialization and de-sequentialization for unification nets are inverses up to generality, and that composition is sound.
+
 % ..................................................
@@
 \begin{theorem}
-If $\net\lambda AB$ sequentializes to $\pi$ and $\net\kappa{\dual B}C$ to $\phi$ then their composition $\net{\lambda\comp\kappa}AC$ sequentializes to a proof $\psi''\leq\psi'$ where $\psi'$ is a normal form of the proof
-\[
-	\psi~=~
-	\vc{\infer[\Qrr.]{\seq AC}{
-	 \Prf\pi AB & \Prf\phi{\dual B}C
-	}}~.
-\]
+If $\net\lambda AB$ sequentializes to $\pi$ and $\net\kappa{\dual B}C$ to $\phi$ then their composition $\net{\lambda\comp\kappa}AC$ sequentializes to a proof $\psi'\leq\psi$ where $\psi$ is a normal form of $\pi\comp\phi$.
+%\[
+%	\psi~=~
+%	\vc{\infer[\Qrr.]{\seq AC}{
+%	 \Prf\pi AB & \Prf\phi{\dual B}C
+%	}}~.
+%\]
 \end{theorem}
@@
 By Lemma~\ref{lem:unifying implies strict coalescence} there are witness labellings $\Sigma$ and $\Theta$ such that $\net{\lambda_\Sigma}AB$ strict-sequentializes to $\pi$ and $\net{\kappa_\Theta}{\dual B}C$ to $\phi$.
-By Theorem~\ref{thm:composition} their composition $(\net{\lambda_\Sigma\comp\kappa_\Theta)}AC$ strict-sequentializes to a normal form $\psi'$ of $\psi$.
-By Lemma~\ref{lem:ucoal generality} the net $\net{(\lambda\comp\kappa)_\star}AC$ unifying-sequentializes to $\psi''\leq\psi'$.
+By Theorem~\ref{thm:composition} their composition $(\net{\lambda_\Sigma\comp\kappa_\Theta)}AC$ strict-sequentializes to a normal form $\psi$ of $\pi\comp\phi$.
+By Lemma~\ref{lem:ucoal generality} the net $\net{(\lambda\comp\kappa)_\star}AC$ unifying-sequentializes to $\psi'\leq\psi$.
 \end{proof}
@@
 A slice $S_B$ of $B$ and $\varnothing$ containing one of $(D_1,\tau)$, $(D_2,\tau)$, and $(D_1\+D_2,\tau)$ must also contain the other two.
-%
-%% \lutz{something is confusing here.
-It seems you are using different notions of slice.
-Above it says that correctness means that slices are singletons, and here you imply that slices contain more than one element.}
-%% %
-%% \willem{Indeed. A slice of a NET is singleton; a slice of FORMULA or SEQUENT need not be.}
-%
 A slice $S$ of $\seq AB$ then contains all three of $\link C{D_1}$, $\link C{D_2}$, and $\link C{D_1{\+}D_2}$, or none.
@@
 Then $S\cap \lambda_\Sigma$ is the singleton $\{\link CD\}$ if and only if $S\cap\kappa_\Theta$ is $\{\link[\sigma\minus x]C{\exists x.D}\}$, where it should be observed that if $t$ is also a witness to $x$ in some other slice of $R$, then $t\in\Theta(x)$ and in fact $S=S'$.
-\lutz{?}
-\todo{Explain the witness sets better; refer to 1st case above; }
+
+%\lutz{?}
+%\todo{Explain the witness sets better; refer to 1st case above; }
 
@@
 
+% ..................................................
+
+\setcounter{theorem}{\thethmcomposition}
+\begin{theorem}[Restatement]
+If proof nets $\net{\lambda_\Sigma}AB$ and $\net{\kappa_\Theta}{\dual B}C$ sequentialize to $\pi$ and $\phi$ respectively, then their composition $(\net{\lambda_\Sigma}AB)\comp(\net{\kappa_\Theta}{\dual B}C)$ sequentializes to a normal form $\psi$ of $\pi\comp\phi$.
+\end{theorem}
+
+\begin{proof}
+By Corollary~\ref{cor:strong coalescence} the proof nets $L=\net{\lambda_\Sigma}AB$ and $R=\net{\kappa_\Theta}{\dual B}C$ strongly coalesce.
+We may then interleave their coalescence sequences as follows: if a synchronized step in $L$ and $R$ on the interface $B$ and $\dual B$ is available, apply it; otherwise perform steps in $L$ on $A$ and in $R$ on $C$ until it is.
+This gives the following combined sequence.
+\[
+\begin{array}{c@{~}c@{~}c@{~}l@{~}c@{~}l@{~}c@{~}l@{~}c}
+	L &{}={}& L_1 & ~\scoal^?~ & L_2 & ~\scoal^?~ & \dots & ~\scoal^?~ & L_n 
+\\
+	R &{}={}& R_1 & ~\scoal^?~ & R_2 & ~\scoal^?~ & \dots & ~\scoal^?~ & R_n 
+\\[5pt]
+	\Downarrow && \Downarrow && \Downarrow &&&& \Downarrow 
+\\[5pt]
+	L\comp R & = & L_1\comp R_1 & ~\scoal~ & L_2\comp R_2 & ~\scoal~ & \dots & ~\scoal~ & L_n\comp R_n
+\end{array}
+\]
+(Here, $(\scoal^?)$ is the relation $(\scoal)\cup(=)$, but we assume that at least $L_i\scoal L_{i+1}$ or $R_i\scoal R_{i+1}$.)
+%
+The path along the top and right of this diagram sequentializes $L$ to $\pi'$ and $R$ to $\phi'$ (equivalent to $\pi$ and $\phi$ respectively), and then composes to $L_n\comp R_n = \net{\{\link[\varnothing]AC^{\pi'\comp\phi'}\}}AC$.
+%with
+%\[
+%	\psi' = \vc{\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq AC}{\Prf{\pi'}AB & \Prf{\phi'}{\dual B}C}}~.
+%\]
+
+Each square of the diagram converges as one of the critical pairs of sequentialization and composition discussed above.
+Then each path along the diagram from top left ($L$ and $R$) to bottom right $(L_n\comp R_n)$ gives a sequentialization, with cuts, of $L_n\comp R_n$.
+Let the path taking the vertical step from $L_i$ and $R_i$ to $L_i\comp R_i$ sequentialize to $\psi_i$, so that $\psi_n=\psi'$.
+By the way each square converges, we have that $\psi_i$ is reached from $\psi_{i+1}$ by a cut-elimination or permutation step.
+
+Finally, in $L$ and $R$ every link is an axiom link.
+Any link in $L\comp R$ is composed from two links $\link ab$ in $L$ and $\link[\tau]{\dual b}c$ in $R$, which yields $\link[\rho]ac$ where $\rho = \sigma_a\tau_c\dcom\fix{\sigma_b\tau\subdual b}$.
+This sequentializes to the axiom $\infer{\seq{a\rho}{c\rho}}{}$, which is in normal form.
+Then $L\comp R$ is a proof net (it has an axiom linking and it coalesces), and it sequentializes to a normal form of $\psi$.
+%
+%which sequentialize respectively to. 
+%\[
+%	\infer{\seq{a\sigma}{b\sigma}}{} 
+%	\qquad\text{and}\qquad
+%	\infer{\seq{\dual b\tau}{c\tau}}{}~.
+%\]
+%We have the link 
+\end{proof}
+
 % --------------------------------------------------
 
-\newpage
 \section{Permutations}
@@
 
-\begin{figure}[h!]
+\begin{figure}[!ht]
+\[
+\renewcommand\+{{+}}
+\renewcommand\*{{\times}}
+\scalebox{0.85}{$
+\begin{array}{c@{\qquad}c}
+	\permAC   & \permEC   
+\\	\downperm & \downperm \\
+	\permCA   & \permCE
+\\ \\[20pt]
+	\permPC   & \permXC 
+\\	\downperm & \downperm \\
+	\permCP   & \permCX
+\end{array}
+\begin{array}{c}
+	\permCD \\ \downperm \\ \permDC
+\end{array}
+$}
+\]
+\caption{Cut-permutations}
+\label{fig:cut-permutations}
+\end{figure}
+
+% ..................................................
+
+\begin{figure}[!ht]
 \[
@@
 \label{fig:permutations}
-\end{figure}
-
-% ..................................................
-
-\begin{figure}
-\[
-\renewcommand\+{{+}}
-\renewcommand\*{{\times}}
-\scalebox{0.85}{$
-\begin{array}{c@{\qquad}c}
-	\permAC   & \permEC   
-\\	\downperm & \downperm \\
-	\permCA   & \permCE
-\\ \\[20pt]
-	\permPC   & \permXC 
-\\	\downperm & \downperm \\
-	\permCP   & \permCX
-\end{array}
-\begin{array}{c}
-	\permCD \\ \downperm \\ \permDC
-\end{array}
-$}
-\]
-\caption{Cut-permutations}
 \end{figure}
@@
 %\]
+
+%\[
+%	\vc{
+%	 \infer[\Qrr*]{\seq{A\*B}{\exists x.C}}{
+%	  \infer[\Qrr?y]{\seq A{\exists x.C}}{\seq AC}
+%	  &
+%	  \infer[\Qrr?z]{\seq B{\exists x.C}}{\seq BC}
+%	}}
+%	\quad\sim\quad
+%	\vc{
+%	 \infer[\Qrr?y]{\seq{A\*B}C}{
+%	  \infer[\Qrr*]{\seq{A\*B}{\exists x.C}}{
+%	   \seq AC
+%	   &
+%	   \seq BC
+%	}}}
+%\]

### 2018-01-21 ALL1.tex
ACKs section
Dominic's affiliation
stuff
MLL1 unification net reference; centered page 1&2 figures

@@
 \newcommand\mall{\textsc{mall}}
+\newcommand\mll{\textsc{mll}}
 
@@
   \texttt{w.b.heijltjes@bath.ac.uk}}
-\affil[2]{Apple, Inc.\\
-  \texttt{dominich@gmail.com}}
+\affil[2]{Logic Group, UC Berkeley, USA\\
+  \texttt{dominich@theory.stanford.edu}}
 \affil[3]{INRIA \&\ \'Ecole Polytechnique, Palaiseau, France\\
@@
 These are captured naturally in \emph{proof nets} \cite{Girard-1987,Hughes-vanGlabbeek-2005}, which consist of a set of \emph{links} between subformulas in $\dual A$ and in $B$, satisfying a simple geometric correctness condition.
-\[
-\begin{array}{c@{\qquad}c@{\qquad}c@{\qquad}c}
+\[\hspace*{9ex}% spacing hack to achieve central horizontal alignment
+\begin{array}{c@{\qquad\qquad}c@{\qquad\qquad}c@{\qquad\qquad}c}
 	\begin{tikzpicture}[net]
@@
 But the \emph{formulas + links} design has only one instance of $\exists x.A$.
-\[
+\[\hspace*{26ex}% spacing hack to achieve central horizontal alignment
 \vc{
@@
    }}
-~.
+%~.
 \]
@@
 \defn{Witness nets} replace the \emph{implicit} substitutions of sequent proofs with \emph{explicit} substitutions, recorded at each link.
-\defn{Unification nets} omit existential witnesses altogether, and reconstruct them by unification.
+\defn{Unification nets}, introduced by the second author in \cite{Hughes-2018} for first-order multiplicative linear logic, omit existential witnesses and reconstruct them by unification; we extend them to \all1.
 Respective examples are below.
 \[
+\hspace*{8ex}% spacing hack to achieve central horizontal alignment
 \begin{tikzpicture}[net]
@@
 \end{tikzpicture}
-\qquad\qquad
+\hspace*{16ex}
 \begin{tikzpicture}[net]
@@
 
-A companion paper \cite{Hughes-2018} explores unification nets for first-order \emph{multiplicative} linear logic, reporting drastic complexity improvements and equally straightforward proof net composition.
+%A companion paper \cite{Hughes-2018} explores unification nets for first-order \emph{multiplicative} linear logic, reporting drastic complexity improvements and equally straightforward proof net composition.
 
@@
 \end{proof}
+
+% --------------------------------------------------
+
+\subsection*{Acknowledgements}
+
+Dominic would like to thank his host, Wes Holliday, at the UC Berkeley Logic Group.
 

### 2018-01-21 ALL1.tex
typo fix third authors -> third author's

@@
 {\all} is of course part of {\mall} (multiplicative-additive linear logic), and its lessons are clearly visible in the second author's canonical proof nets \cite{Hughes-vanGlabbeek-2005} for that fragment, as well as the first and second author's locally canonical \emph{conflict nets}~\cite{Hughes-Heijltjes-2016}.
-But its proof nets also appear as the \emph{skew fibrations} in the second author's \emph{combinatorial proofs} for classical logic~\cite{Hughes-2006-proofs}, and in the third authors study of the \emph{medial rule} for classical logic~\cite{str:RTA07}.
+But its proof nets also appear as the \emph{skew fibrations} in the second author's \emph{combinatorial proofs} for classical logic~\cite{Hughes-2006-proofs}, and in the third author's study of the \emph{medial rule} for classical logic~\cite{str:RTA07}.
 To prepare the ground for the extension of \emph{combinatorial proofs} to first-order classical logic is one motivation for the% current presentation.

### 2018-01-21 ALL1.tex
fixed bug where '... current presentation' was cut from end of first paragraph of page 2; had to shorten some sentences to avoid an extra line

--- 2018-01-21 ALL1.tex
@@
 
-{\all} is of course part of {\mall} (multiplicative-additive linear logic), and its lessons are clearly visible in the second author's canonical proof nets \cite{Hughes-vanGlabbeek-2005} for that fragment, as well as the first and second author's locally canonical \emph{conflict nets}~\cite{Hughes-Heijltjes-2016}.
-But its proof nets also appear as the \emph{skew fibrations} in the second author's \emph{combinatorial proofs} for classical logic~\cite{Hughes-2006-proofs}, and in the third authors study of the \emph{medial rule} for classical logic~\cite{str:RTA07}.
-To prepare the ground for the extension of \emph{combinatorial proofs} to first-order classical logic is one motivation for the% current presentation.
+{\all} is of course part of {\mall} (multiplicative-additive linear logic), and its lessons are clearly visible in the second author's canonical proof nets \cite{Hughes-vanGlabbeek-2005} for {\mall}, as well as the first and second author's locally canonical \emph{conflict nets}~\cite{Hughes-Heijltjes-2016}.
+Its proof nets also appear as the \emph{skew fibrations} in the second author's \emph{combinatorial proofs} for classical logic~\cite{Hughes-2006-proofs}, and in the third author's study of the \emph{medial rule} for classical logic~\cite{str:RTA07}.
+To prepare the ground for the cut elimination of first-order \emph{combinatorial proofs} is one motivation for the current presentation.
 

### 2018-01-21 ALL1.tex
fixed some refs to figs 9 and 10 in Appdx B

@@
 We write $\prf\pi AB$ for a proof $\pi$ with conclusion sequent $\seq AB$.
-Two proofs are \defn{equivalent} $\pi\sim\pi'$ if one is obtained from the other by rule permutations (Appendix, Figure~\ref{fig:permutations}.
+Two proofs are \defn{equivalent} $\pi\sim\pi'$ if one is obtained from the other by rule permutations (Appendix~\ref{sec:permutations}, Figure~\ref{fig:permutations}).
 
@@
 From left to right is by inspection of the critical pairs of sequentialization ($\scoal$).
-From right to left is by inspection of the rule permutations in Figure~\ref{fig:permutations} in the appendix.
+From right to left is by inspection of the rule permutations in Figure~\ref{fig:permutations} in Appendix~\ref{sec:permutations}.
 \end{proof}
@@
 \indent
-Cut-elimination rules for \all1 are given in Figure~\ref{fig:cut-elim}; the needed permutations are in the appendix, Figure~\ref{fig:cut-permutations}.
+Cut-elimination rules for \all1 are given in Figure~\ref{fig:cut-elim}; the needed permutations are in Appendix~\ref{sec:permutations}, Figure~\ref{fig:cut-permutations}.
 }
@@
 
-\section{Permutations}
+\section{Permutations}\label{sec:permutations}
 

### 2018-01-22 ALL1.tex
Changed 'embody a main contribution' to 'embody a central contribution' since the former doesn't sound right in English. Also changed 'reconstructed effectively' to 'reconstructed when needed' because 'effectively' isn't actually true, because it takes exponential time.
bugfixes

@@
 \newcommand\permEA{
- \infer[\Qrr?t]{\Seq{\forall x.A}{\forall y.B}}{
+ \infer[\Qrr?t]{\Seq{\forall x.A}{\exists y.B}}{
   \infer[\Qrr!]{\Seq{\forall x.A}{B[t/y]}}{
@@
  \infer[\Qrr*]{\Seq{{A_1\*A_2}}C}{
-  \infer[\Qrr.]{\Seq {A_i}C}{
+  \infer[\Qrr.]{\Seq {A_1}C}{
    \Seq {A_1}B & \Seq{\dual B}C
   }&
-  \infer[\Qrr.]{\Seq {A_i}C}{
+  \infer[\Qrr.]{\Seq {A_2}C}{
    \Seq {A_2}B & \Seq{\dual B}C
@@
 \newcommand\permDC{
- \infer[\Qrr.]{\Seq{{A_1\*A_2}}C}{
-  \Seq A{\dual B}
+ \infer[\Qrr.]{\Seq{A}D}{
+  \Seq A{B}
   &
-  \infer[\Qrr.]{\Seq BD}{
-   \Seq B{\dual C} & \Seq CD
+  \infer[\Qrr.]{\Seq {\dual B}D}{
+   \Seq {\dual B}{C} & \Seq {\dual C}D
 }}}
@@
 \affil[1]{University of Bath, United Kingdom\\
-  \texttt{w.b.heijltjes@bath.ac.uk}}
+  \texttt{http://www.cs.bath.ac.uk/~wbh22/}} %%w.b.heijltjes@bath.ac.uk}}
 \affil[2]{Logic Group, UC Berkeley, USA\\
-  \texttt{dominich@theory.stanford.edu}}
-\affil[3]{INRIA \&\ \'Ecole Polytechnique, Palaiseau, France\\
-  \texttt{lutz.strassburger@inria.fr}}
+  \texttt{http://boole.stanford.edu/~dominic/}} %%dominich@theory.stanford.edu}}
+\affil[3]{Inria Saclay \&\ LIX/\'Ecole Polytechnique, Palaiseau, France\\
+  \texttt{http://www.lix.polytechnique.fr/Labo/Lutz.Strassburger/}} %%lutz.strassburger@inria.fr}}
 \authorrunning{W.B.\ Heijltjes, D.J.D.\ Hughes, and L.\ Stra\ss burger}
@@
 For the other, unification nets, this information is absent but can be reconstructed through unification.
-Unification nets embody a main contribution of the paper: first-order witness information can be left implicit, and reconstructed effectively.
+Unification nets embody a central contribution of the paper: first-order witness information can be left implicit, and reconstructed as needed.
 
@@
 	\color{violet}\infer[\color{black}\Qrr!]{\color{black}\Seq{\forall x.\exists y.\dual P(y)\+\dual Q(x,y)}{\exists z.P(f(z))\*Q(z,t)}}{
-	 \color{violet}\infer[\color{black}\Qrr?,x]{\color{black}\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{\exists z.P(f(z))\*Q(z,t)}}{
+	 \color{violet}\infer[\color{black}\Qrr?x]{\color{black}\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{\exists z.P(f(z))\*Q(z,t)}}{
 	  \color{violet}\infer[\color{black}\Qrr*]{\color{black}\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{P(f(x))\*Q(x,t)}}{
@@
 %
-The witness map $\sigma$ of a link $\link CD$ then has two natural components, $\sigma\res{\ex[A]C}$ and $\sigma\res{\ex[B]D}$, which we will abbreviate by $\sigma_C$ and $\sigma_D$ respectively.
+The witness map $\sigma$ of a link $\link CD$ then has two natural \lutz{disjoint?} components, $\sigma\res{\ex[A]C}$ and $\sigma\res{\ex[B]D}$, which we will abbreviate by $\sigma_C$ and $\sigma_D$ respectively.
 
@@
 	\infer[\Qrr!]{\Seq{\forall x.A}{\exists y.B}}{
-	 \infer[\Qrr?t]{\Seq A{\exists x.B}}{\Seq AB[t/y]}
+	 \infer[\Qrr?t]{\Seq A{\exists y.B}}{\Seq AB[t/y]}
    }}
@@
 \\ \\[20pt]
- 			  &			  &			  & \permPX
+ 			  &			  &			  & \permXY
 \\			  &			  &			  & \downperm \\
- 			  &			  &			  & \permXP
+ 			  &			  &			  & \permYX
 \end{array}$}

### 2018-01-22 ALL1.tex
fixed url

@@
 \affil[1]{University of Bath, United Kingdom\\
-  \texttt{http://www.cs.bath.ac.uk/~wbh22/}} %%w.b.heijltjes@bath.ac.uk}}
+  \url{http://www.cs.bath.ac.uk/~wbh22/}} %%\texttt{w.b.heijltjes@bath.ac.uk}}
 \affil[2]{Logic Group, UC Berkeley, USA\\
-  \texttt{http://boole.stanford.edu/~dominic/}} %%dominich@theory.stanford.edu}}
+  \url{http://boole.stanford.edu/~dominic/}} %%\texttt{dominich@theory.stanford.edu}}
 \affil[3]{Inria Saclay \&\ LIX/\'Ecole Polytechnique, Palaiseau, France\\
-  \texttt{http://www.lix.polytechnique.fr/Labo/Lutz.Strassburger/}} %%lutz.strassburger@inria.fr}}
+  \url{http://www.lix.polytechnique.fr/Labo/Lutz.Strassburger/}} %%\texttt{lutz.strassburger@inria.fr}}
 \authorrunning{W.B.\ Heijltjes, D.J.D.\ Hughes, and L.\ Stra\ss burger}

### 2018-01-22 ALL1.tex
accept suggestion

@@
 \affil[1]{University of Bath, United Kingdom\\
-  \url{http://www.cs.bath.ac.uk/~wbh22/}} %%\texttt{w.b.heijltjes@bath.ac.uk}}
+  \url{http://willem.heijltj.es/}} %%\texttt{w.b.heijltjes@bath.ac.uk}}
 \affil[2]{Logic Group, UC Berkeley, USA\\
@@
 %
-The witness map $\sigma$ of a link $\link CD$ then has two natural \lutz{disjoint?} components, $\sigma\res{\ex[A]C}$ and $\sigma\res{\ex[B]D}$, which we will abbreviate by $\sigma_C$ and $\sigma_D$ respectively.
+The witness map $\sigma$ of a link $\link CD$ then has two natural, disjoint components, $\sigma\res{\ex[A]C}$ and $\sigma\res{\ex[B]D}$, which we will abbreviate by $\sigma_C$ and $\sigma_D$ respectively.
 

### 2018-03-23 Archive/ALL1-backup-1.tex
some cleanup

--- 2017-12-19 ALL1-backup-2.tex
@@
 
-\newcommand\deseq[4][\sigma]{[#2]^{#1}_{#3,#4}}
-\newcommand\Deseq[4][\sigma]{\left[\vcenter{#2}\right]^{#1}_{#3,#4}}
+\newcommandx\deseq[3]{\floor{#1}_{#2,#3}}
+\newcommandx\Deseq[3]{\left\lfloor\vcenter{#1}\right\rfloor_{#2,#3}}
 
@@
 
-\newcommand\join\bowtie
-
 \newcommand\comp\frown
-%\newcommand\ubot\sqcup
+\newcommand\ubot\sqcup
 
@@
 \newcommand\coals{\rightsquigarrow}
-\newcommand\coal{\coals}%{\stackrel1\rightsquigarrow}
+\newcommand\coal{\stackrel1\rightsquigarrow}
 
@@
 We write $\prf\Pi AB$ for a proof $\Pi$ with conclusion sequent $\seq AB$.
-Anticipating the requirements of proof nets, we will assume the following convention for \all1 proofs.
+Anticipating the requirements of proof nets, we will assume the following conventions for \all1 proofs.
 
@@
 [\defn{Barendregt's convention}] All quantifiers in a sequent $\seq AB$ have a distinct binding variable, and no bound variable shares a name with a free one.
-%	\item
-%% ALTERNATIVE: "STATIC WITNESSING"
-%[\defn{Universal witnessing}] All existential witnesses in a proof are \defn{universal terms} $\termsA\subset\terms$, generated by the following grammar.
-%\[
-%	\termsA: \qquad t \Coloneqq a \Mid f(t_1,\dots,t_n)
-%\]
+	\item
+% ALTERNATIVE: "STATIC WITNESSING"
+[\defn{Universal witnessing}] All existential witnesses in a proof are \defn{universal terms} $\termsA\subset\terms$, generated by the following grammar.
+\[
+	\termsA: \qquad t \Coloneqq a \Mid f(t_1,\dots,t_n)
+\]
 \end{description}
@@
 A \defn{linking} $\lambda$ on the sequent $\seq AB$ is a set of links on $\seq AB$.
-%It is an \defn{axiom linking} if all links are axiom links.
+It is an \defn{axiom linking} if all links are axiom links.
 
@@
 
-A \defn{witness map} $\sigma$ is a substitution map
-\[
-	\sigma\colon \varE \to \terms
-\]
-which assigns terms to existential variables.
-We write $\varnothing$ for the empty map (the identity).
-The map $\sigma[x\mapsto t]$ substitutes $t$ for $x$ and is as $\sigma$ everywhere else, while $\sigma\minus x$ is the identity on $x$ and otherwise as $\sigma$.
-The application of a witness map $\sigma$ to a formula $A$ is written $A\sigma$.
-
-A \defn{labelled link} $\clink AB$ is a link carrying a witness map $\sigma$.
-A \defn{labelled linking} respectively a \defn{labelled pre-net} is a linking or pre-net where every link is labelled.
-A labelled linking $\lambda$ reverts to an unlabelled one, written $\floor\lambda$, by dropping the label of each link.
-
-\begin{definition}
-The \defn{labelled de-sequentialization} of a sequent proof $\prf\Pi AB$ is the labelled pre-net $\net{\deseq[\varnothing]\Pi AB} AB$ where $\deseq-AB$ is defined as follows.
+The \defn{de-sequentialization} of a sequent proof $\prf\Pi AB$ is the labelled pre-net $\net\lambda AB$ where $\lambda=\deseq\Pi AB$ and $\deseq-AB$ is defined as follows.
 %
@@
 \begin{array}{ccl}
-	\Deseq{\infer{\seq P{\dual P}}{}}QR &=& \{\clink QR\}
+	\Deseq{\infer{\seq P{\dual P}}{}}QR &=& \{(Q,R)\}
 \\ \\
@@
 	&=&
-	 \Deseq[{\sigma[x\mapsto t]}]{\deduce[\rule{0pt}{1pt}]{\seq A{B[t/x]}}\Pi}
+	 \Deseq{\deduce[\rule{0pt}{1pt}]{\seq A{B[t/x]}}\Pi}
 	  {A'}{B'}
@@
 \]
-The \defn{(unlabelled) de-sequentialization} of $\Pi$ is $\net{\floor\Pi_{A,B}}AB$ where $\floor\Pi_{A,B}$ is $\floor{\deseq[\varnothing]\Pi AB}$.
-\end{definition}
 
-To generate witness maps for an unlabelled linking, we will be using unification.
-A \defn{unifying} witness map $\sigma$ for formulas $A$ and $B$ is one such that $A\sigma=B\sigma$.
-Note that these will substitute only the free existential variables, but not bound ones or universal variables.
-For instance, the only unifying witness map of $p(x,y)$ and $p(a,a)$ is $\{x\mapsto a,y\mapsto a\}$, while $\exists y.p(x,x)$ and $\exists y.p(a,y)$ have no unifier.
+% --------------------------------------------------
 
-A witness map $\sigma$ is \defn{more general} than $\tau$, witten $\sigma\leq\tau$, if there is a $\rho$ such that $(A\sigma)\rho = A\tau$ for any $A$.
-The \defn{join} $\sigma\join\tau$ of two maps $\sigma$ and $\tau$ is the least map $\rho$ such that $\sigma\leq\rho$ and $\tau\leq\rho$, if it exists.
-If it does, we call $\sigma$ and $\tau$ \defn{compatible}, written $\sigma\comp\tau$.
+\subsection{Existential witnesses}
 
-The \defn{initial witness map} $\sigma(A,B)$ is the most general unifying witness map for the formulas $A$ and $B$, if it exists; if it does, $A$ and $B$ are \defn{compatible}.
-An unlabelled axiom link $(P,Q)$ is \defn{compatible} if $P$ and $\dual Q$ are compatible; a labelled one $\clink PQ$ is \defn{compatible} if $\sigma$ is a unifier for $P$ and $\dual Q$.
-A (labelled) linking or pre-net is \defn{compatible} if all links are compatible axiom links.
-The \defn{initial labelling} of a compatible linking $\lambda$ or pre-net $\net\lambda AB$ is the labelled linking $\lambda_\star$ or labelled pre-net $\net{\lambda_\star}AB$ given by
+A \defn{witness map} $\sigma$ is a substitution map
 \[
-	\lambda_\star = \{~\clink[\sigma(P,\dual Q)]PQ~\mid~(P,Q)\in\lambda~\}~.
+	\sigma\colon \varE \rightharpoonup \termsA
 \]
-%Observe that $\floor{\lambda_\star}=\lambda$. We call $\floor\lambda_\star$ the \defn{initial re-labelling} of a labelled linking $\lambda$, and analogously for a pre-net $\net\lambda AB$.
+which assigns universal terms to existential variables, given by a partial function.
+We write $\sigma(x)=\bot$ to indicate that $\sigma$ is undefined for $x$.
+The map $\sigma\minus x$ is undefined for $x$ and as $\sigma$ everywhere else.
+The application of a witness map $\sigma$ to a formula $A$ is written $A\sigma$.
+Two witness maps $\sigma$ and $\tau$ are \defn{compatible}, written $\sigma\comp\tau$, if they agree wherever they are defined:
+\[
+	\sigma\comp\tau \quad\iff\quad \forall x\in\varE.~\big(\sigma(x)\neq\bot~\wedge~\tau(x)\neq\bot\big)~\Rightarrow~\sigma(x)=\tau(x)~.
+\]
+Two compatible witness maps can be combined into the map $\sigma\cup\tau$ that sends $x$ to $\sigma(x)$ or $\tau(x)$, whichever is defined, and is undefined when both are.
+To combine witness maps that may not be compatible we will write $\sigma\ubot\tau$, which is $\sigma\cup\tau$ if they are, and undefined ($\bot$) otherwise; if either $\sigma$ or $\tau$ is already undefined, $\sigma\ubot\tau$ also reverts to $\bot$.
+\[
+	\sigma\ubot\tau\quad=\quad
+	\left\{\begin{array}{ll}
+		\sigma\cup\tau	& \text{if $\sigma\neq\bot$, $\tau\neq\bot$, and $\sigma\comp\tau$} \\
+		\bot			& \text{otherwise} \\
+	\end{array}\right.
+\] 
+Note that $\bot$ is not a witness map, and different from the empty substitution map, $\sigma(x)=\bot$ for all $x$.
+For two atomic formulas $P,Q$ (or terms $s,t$) the \defn{initial witness map} $\sigma(P,Q)$ is the smallest witness map $\sigma$ such that $P\sigma=\dual Q\sigma$ and $P\sigma$ has no free existential variables.
+If it exists, it is defined inductively as follows (omitting the symmetric case for $\dual p$ and $p$).
+
+\begin{align*}
+	\left.\begin{array}{r}
+		\sigma(\,x\,,\,t\,) \\
+	 	\sigma(\,t\,,\,x\,)
+	\end{array}\right\}
+	& = \{ x\mapsto t \}\quad \text{if $t\in\termsA$}
+ \\
+	\left.\begin{array}{r}
+		\sigma(\,p(s_1,\dots,s_n)\,,\,\dual p(t_1,\dots,t_n)\,) \\
+		\sigma(\,f(s_1,\dots,s_n)\,,\,f(t_1,\dots,t_n)\,)
+	\end{array}\right\}
+	& = \sigma(s_1,t_1)\ubot\dots\ubot\sigma(s_n,t_n)
+\end{align*}
+
+\begin{lemma}
+\label{lem:minimal witness map}
+For first-order terms $s$ and $t$ the witness map $\sigma(s,t)$ is the smallest such that $s\sigma=t\sigma$ and $s\sigma$ contains no existential variables.
+\end{lemma}
+
+\begin{proof}
+By induction on $s$ and $t$. If $s=x$ then $\sigma(x,t)$ exists if and only if $t\in\termsA$, 
+\end{proof}
+
+%\begin{align*}
+%	\sigma_V(\,a\,,\,a\,) \kern12.5pt & = \varnothing
+%\\	\sigma_V(\,x\,,\,x\,) \kern12.5pt & = \varnothing\quad \text{if $x\in V$}
+%\\
+%	\left.\begin{array}{r}
+%		\sigma_V(\,x\,,\,t\,) \\
+%	 	\sigma_V(\,t\,,\,x\,)
+%	\end{array}\right\}
+%	& = \{ x\mapsto t \}\quad \text{if $x\notin V$ and $t\in\termsA$}
+% \\
+%	\left.\begin{array}{r}
+%		\sigma_V(\,p(s_1,\dots,s_n)\,,\,p(t_1,\dots,t_n)\,) \\
+%		\sigma_V(\,f(s_1,\dots,s_n)\,,\,f(t_1,\dots,t_n)\,)
+%	\end{array}\right\}
+%	& = \sigma_V(s_1,t_1)\ubot\dots\ubot\sigma_V(s_n,t_n)
+%\\	
+%	\left.\begin{array}{r}
+%		\sigma_V(\,A\+B\,,\,C\+D\,) \\
+%		\sigma_V(\,A\*B\,,\,C\*D\,)
+%	\end{array}\right\}
+%	& = \sigma_V(A,C)\ubot\sigma_V(B,D)
+%\\	
+%	\sigma_V(\,\forall a.A\,,\,\forall a.B\,)
+%		 \kern12.5pt & = \sigma_V(A,B)
+%\\	\sigma_V(\,\exists x.A\,,\,\exists x.B\,)
+%		 \kern12.5pt & = \sigma_{V\cup\{x\}}(A,B)
+%\end{align*}
+%
+%Observe that if the witness map $\sigma=\sigma(A,B)$ exists then $A\sigma=B\sigma$.
+
+% --------------------------------------------------
 
@@
 
-For a labelled linking $\lambda$ and an existential variable $x$, write $\lambda(x)\subseteq\terms$ for the \defn{witness set} of $x$, which collects the terms assigned to $x$ by the links in $\lambda$:
+A \defn{labelled link} $\clink AB$ is a link carrying a witness map $\sigma$. A \defn{labelled linking} respectively \defn{labelled pre-net} is a linking or pre-net where every link is labelled.
+%
+For a labelled pre-net $\net\lambda AB$ and an existential variable $x\in\varE$, write $\lambda(x)\subseteq\termsA$ for the \defn{witness set} of $x$, which collects the terms assigned to $x$ by the links in $\lambda$:
 \[
@@
 where $S_A$ is a slice of $A$ and $S_B$ a slice of $B$.
-A labelled pre-net is \defn{correct} if every slice is a singleton.
-A compatible pre-net $\net\lambda AB$ is \defn{correct} if its initial labelling $\net{\lambda_\star}AB$ is.
-Observe that for a \emph{labelled} pre-net correctness and compatibility are independent, while a non-labelled pre-net must be compatible to be correct, since $\lambda_\star$ is otherwise not defined.
 
 \begin{definition}
-An \all1 \defn{proof net} is a correct pre-net. An \all1 \defn{labelled proof net} is a correct and compatible labelled pre-net.
+A labelled pre-net is \defn{correct} if every slice is a singleton.
+\end{definition}
+
+A pre-net is \defn{compatible} if every link is an axiom link $(P,Q)$ such that $\sigma(P,Q)$ exists.
+A compatible pre-net $\net\lambda AB$ is \defn{correct} if its \defn{labelling} $\net{\lambda_\star}AB$ is correct, where $\lambda_\star$ is defined as follows.
+\[
+	\lambda_\star=\{~\clink PQ~\mid~(P,Q)\in\lambda~,~\sigma=\sigma(P,Q)~\}
+\]
+
+\begin{definition}
+An \all1 \defn{proof net} is a correct pre-net.
 \end{definition}
@@
 %
-\renewcommand{\+}{{+}}
-\renewcommand{\*}{{\times}}
-\begin{align}
-  	\net{\{\clink AB\}}A{B\+C} 
-& ~\coal~
-	\net{\{\clink A{B\+C}\}}A{B\+C}
-\tag{$\+_1$}
-\\[5pt]
-        \net{\{\clink AC\}}A{B\+C}
-& ~\coal~  
-	\net{\{\clink A{B\+C}\}}A{B\+C}
-\tag{$\+_2$}
-\\[5pt]
-	\net{\{\clink AB,\clink[\tau]AC\}}A{B\*C}
-& ~\coal~ 
-	\net{\{\clink[\sigma\join\tau]A{B\*C}\}}A{B\*C}\quad\text{if }\sigma\comp\tau
-\tag{$\*$}
-\\[5pt]	
-	\net{\{\clink AB\}}A{\exists x.B}
-& ~\coal~ 
-	\net{\{\clink[\sigma\!\minus\!x]A{\exists x.B}\}}A{\exists x.B}
-\tag{$\exists$}
-\\[5pt]
-	\net{\{\clink AB\}}A{\forall a.B}
-& ~\coal~ 
-	\net{\clink A{\forall a.B}}A{\forall a.B} \quad \text{if }a\,\notin\,\fv(A\sigma)
-\tag{$\forall$}
-\end{align}
-%\[
-%\renewcommand{\+}{{+}}
-%\renewcommand{\*}{{\times}}
-%\begin{array}{r@{}c@{\,}c@{\,~}l}
-%    \begin{array}{@{}r@{}}
-%        \net{\{\clink AB\}}A{B\+C} \\ \\[-5pt]
-%        \net{\{\clink AC\}}A{B\+C}
-%    \end{array}
-%&   \left.\begin{array}{@{}c@{}} 
-%		\vphantom\{\\\\[-5pt]\vphantom\{
-%	\end{array}\right\}
-%& \coal &
-%	\net{\{\clink A{B\+C}\}}A{B\+C}
-%\\ \\[-5pt]
-%	\net{\{\clink AB,\clink[\tau]AC\}}A{B\*C}
-%&& \coal &
-%	\net{\{\clink[\sigma\join\tau]A{B\*C}\}}A{B\*C}\quad\text{if }\sigma\comp\tau
-%\\ \\[-5pt]	
-%	\net{\{\clink AB\}}A{\exists x.B}
-%&& \coal &
-%	\net{\{\clink[\sigma\!\minus\!x]A{\exists x.B}\}}A{\exists x.B}
-%\\ \\[-5pt]
-%	\net{\{\clink AB\}}A{\forall a.B}
-%&& \coal &
-%	\net{\clink A{\forall a.B}}A{\forall a.B} \quad \text{if }a\,\notin\,\fv(A\sigma)
-%\end{array}
-%\]
-%\begin{itemize}
-%	\item 
-%\makebox[40pt][l]{$B\+C$:} 
-%Replace a link $\clink AB$ or $\clink AC$ with $\clink A{B\+C}$.
-%	\item 
-%\makebox[40pt][l]{$B\*C$:} 
-%Replace links $\clink AB$ and $\clink[\tau]AC$ with $\clink[\sigma\cup\tau]A{B\*C} $ if $\sigma\comp\tau$.
-%	\item
-%\makebox[40pt][l]{$\exists x.B$:} 
-%Replace a link $\clink AB$ with $\clink[\sigma\minus x]A{\exists x.B}$.
-%	\item
-%\makebox[40pt][l]{$\forall a.B$:}
-%Replace a link $\clink AB$ with $\clink A{\forall a.B}$ if $a\,\notin\,\fv(A\sigma)$.
-%\end{itemize}
+%
+\begin{itemize}
+	\item 
+\makebox[40pt][l]{$B\+C$:} 
+Replace a link $\clink AB$ or $\clink AC$ with $\clink A{B\+C}$.
+	\item 
+\makebox[40pt][l]{$B\*C$:} 
+Replace links $\clink AB$ and $\clink[\tau]AC$ with $\clink[\sigma\cup\tau]A{B\*C} $ if $\sigma\comp\tau$.
+	\item
+\makebox[40pt][l]{$\exists x.B$:} 
+Replace a link $\clink AB$ with $\clink[\sigma\minus x]A{\exists x.B}$.
+	\item
+\makebox[40pt][l]{$\forall a.B$:}
+Replace a link $\clink AB$ with $\clink A{\forall a.B}$ if $a\,\notin\,\fv(A\sigma)$.
+\end{itemize}
 %
@@
 
-To be explicit, generating coalescence as a rewrite relation means the following: $\net\lambda AB\coal \net{\lambda'}AB$ if and only if there is a rewrite rule $\net\kappa CD\coal\net{\kappa'} CD$ such that $C\leq A$, $D\leq B$, $\kappa\subseteq\lambda$, and $\lambda'=\lambda\cup\kappa'-\kappa$.
+Coalescence is effectively sequentialization. We will make this explicit by organising the rewrite rules as inference rules.
 
 \begin{lemma}
-If a labelled pre-net coalesces, it is correct. 
+Given a proof $\prf\Pi AB$ and formulas $A'$ and $B'$, if a smallest witness map $\sigma$ exists such that $A=A'\sigma$ and $B=B'\sigma$, then $\deseq\Pi{A'}{B'}$ coalesces to $\clink{A'}{B'}$.
 \end{lemma}
@@
 \begin{proof}
-By induction on the coalescence path.
-Let $\net\lambda AB$ coalesce to $\net\kappa AB$ where $\kappa=\{\clink AB\}$.
-First, we show that the result is correct.
-For each $x$ the witness set $\kappa(x)$ is $\{\sigma x\}$.
-the only slice of $\seq AB$ is $(A,B)$,
+By induction on $\Pi$.
+
+\newlength\prooftablewidth
+\setlength\prooftablewidth{-40pt}
+\addtolength\prooftablewidth{\textwidth}
+
+\noindent
+\begin{tabular}{@{}p{40pt}@{}p{\prooftablewidth}@{}}
+	$\infer{\seq P{\dual P}}{}$
+&
+	Let $A'=Q$ and $B'=R$. Then $\sigma$ is the smallest witness map such that $R\sigma=P$ and $Q\sigma=\dual P$.
+
+		\left.\begin{array}{r}
+		\sigma(\,x\,,\,t\,) \\
+	 	\sigma(\,t\,,\,x\,)
+	\end{array}\right\}
+	& = \{ x\mapsto t \}\quad \text{if $t\in\termsA$}
+ \\
+	\left.\begin{array}{r}
+		\sigma(\,p(s_1,\dots,s_n)\,,\,\dual p(t_1,\dots,t_n)\,) \\
+		\sigma(\,f(s_1,\dots,s_n)\,,\,f(t_1,\dots,t_n)\,)
+	\end{array}\right\}
+	& = \sigma(s_1,t_1)\ubot\dots\ubot\sigma(s_n,t_n)
+
+\\ \\
+	$\infer{\seq A{B_0\+B_1}}{\seq A{B_i}}$
+&
+\\ \\
+	$\infer{\seq A{B\*C}}{\seq AB && \seq AC}$
+%\]
+%\[
+%	\infer{\seq A{\exists x.B}}{\seq A{B[t/x]}}
+%\]
+%\[
+%	\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]{\seq A{\forall a.B}}{\seq AB}
+%\]
+\end{tabular}
+
 \end{proof}
-
-Coalescence is effectively sequentialization. We will make this explicit by organising the rewrite rules as inference rules.
 
@@
 \\ \\
-	\vc{\infer{\crule A {B\+C}} {\crule AB}}
+	\vc{\infer{\crule A {B_0\+B_1}} {\crule A {B_i}}}
 &   
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{A}
-    	\formula[y=1]{B\+C}
-    	\Vlink[red,label={$\scriptstyle\sigma~$},l]{1,1}
-    \end{tikzpicture}}
-&\rightsquigarrow& 
     \vc{\begin{tikzpicture}[net]
@@
     \end{tikzpicture}}
+&\rightsquigarrow& 
 \\ \\ 
@@
 
-\begin{lemma}
-Given a proof $\prf\Pi AB$, formulas $A'$, $B'$, and a witness map $\sigma$ such that $A'\sigma=A$ and $B'\sigma=B$, the de-sequentialization $\net{\deseq\Pi{A'}{B'}}AB$ coalesces to $\net{\{\clink AB\}}AB$.
-\end{lemma}
-
-\begin{lemma}
-Given a proof $\prf\Pi AB$ and formulas $A'$ and $B'$, if a smallest witness map $\tau$ exists such that $A=A'\tau$ and $B=B'\tau$, then $\deseq\Pi{A'}{B'}$ coalesces to $\clink{A'}{B'}$ with $\sigma\leq\tau$.
-\end{lemma}
-
-\begin{proof}
-By induction on $\Pi$.
-
-\newlength\prooftablewidth
-\setlength\prooftablewidth{-80pt}
-\addtolength\prooftablewidth{\textwidth}
-
-\noindent
-\begin{tabular}{@{}p{80pt}@{}p{\prooftablewidth}@{}}
-	\hfill \raisebox{-20pt}{\infer{\seq P{\dual P}}{\vphantom B}} \hfill\hfill
-&
-	Let $A'=Q$ and $B'=R$, and suppose $\tau$ is the smallest witness map such that $Q\tau=P$ and $R\tau=\dual P$.
-The desequentialization $\deseq\Pi QR$ is the $\net{\{Q,R\}}QR$, which coalesces to $\clink QR$ if $\sigma=\sigma(Q,{\dual R})$ exists.
-Since $\tau$ is a unifier of $Q$ and $\dual R$, $\sigma\leq\tau$.
-\\ \\
-%	$\infer{\seq A{B_0\+B_1}}{\seq A{B_i}}$
-%&
-%\\ \\
-	\hfill \raisebox{-20pt}{\infer{\seq A{B\*C}}{\seq AB && \seq AC}}\hfill\hfill
-&
-	Let $\seq{\prf\Pi AB}{A'}{B'}$ coalesce to the two subproofs coalesce to $\clink{A'}{B'}$ and $\clink[\rho]{A'}{B'}$ 
-%	\infer{\seq A{\exists x.B}}{\seq A{B[t/x]}}
-%	\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]{\seq A{\forall a.B}}{\seq AB}
-\end{tabular}
-
-\end{proof}
-
 \end{document}
@@
 %\]
-
-% --------------------------------------------------
-
-%\subsection{Existential witnesses}
-
-%
-%
-%For two first-order terms $s$ and $t$, and a set of variables $V$, let a $V$-\defn{unifier} be a unifying substitution map
-%\[
-%	\sigma\colon V\rightharpoonup \terms
-%\]
-%(that is, $s\sigma=t\sigma$). A $V$-unifier for atomic propositions $P$ and $Q$ is defined analogously. For example, 
-%
-%
-%The \defn{most general $V$-unifier} $\sigma_V(P,Q)$ of $P$ and $Q$ is the most general unifying
-%
-%let the \defn{initial witness map} $\sigma(P,Q)$ be the most general unifier of $P$ and $Q$, if it exists, where only existential variables can be substituted for, and universal variables are considered constant.
-That is, the only unifier of $p(x,y)$ and $p(a,a)$ is $\{x\mapsto a,y\mapsto a\}$, while $p(x,x)$ and $p(a,b)$ have no unifier.
-%
-%Let $\sigma\join\tau$ denote the combination of two witness maps $\sigma$ and $\tau$ as unifiers, if it exists.
-If it does, we call $\sigma$ and $\tau$ \defn{compatible}, expressed by $\sigma\comp\tau$.
-The initial witness map $\sigma(A,B)$ of two formulae $A$ and $B$, if it exists, is then given by:
-%
-%\begin{align}
-%	\left.\begin{array}{r}
-%		\sigma_V(\,A\+B\,,\,C\+D\,) \\
-%		\sigma_V(\,A\*B\,,\,C\*D\,)
-%	\end{array}\right\}
-%	& = \sigma_V(A,C)\join\sigma_V(B,D)
-%\\	
-%	\sigma_V(\,\forall a.A\,,\,\forall a.B\,)
-%		 \kern12.5pt & = \sigma_V(A,B)
-%\\	\sigma_V(\,\exists x.A\,,\,\exists x.B\,)
-%		 \kern12.5pt & = \sigma_{V-\{x\}}(A,B)
-%\end{align*}
-%
-%
-%Two witness maps $\sigma$ and $\tau$ are \defn{compatible}, written $\sigma\comp\tau$, if they agree wherever they are defined:
-%\[
-%	\sigma\comp\tau \quad\iff\quad \forall x\in\varE.~\big(\sigma(x)\neq\bot~\wedge~\tau(x)\neq\bot\big)~\Rightarrow~\sigma(x)=\tau(x)~.
-%\]
-%Two compatible witness maps can be combined into the map $\sigma\cup\tau$ that sends $x$ to $\sigma(x)$ or $\tau(x)$, whichever is defined, and is undefined when both are.
-To combine witness maps that may not be compatible we will write $\sigma\ubot\tau$, which is $\sigma\cup\tau$ if they are, and undefined ($\bot$) otherwise; if either $\sigma$ or $\tau$ is already undefined, $\sigma\ubot\tau$ also reverts to $\bot$.
-%\[
-%	\sigma\ubot\tau\quad=\quad
-%	\left\{\begin{array}{ll}
-%		\sigma\cup\tau	& \text{if $\sigma\neq\bot$, $\tau\neq\bot$, and $\sigma\comp\tau$} \\
-%		\bot			& \text{otherwise} \\
-%	\end{array}\right.
-%\] 
-%Note that $\bot$ is not a witness map, and different from the empty substitution map, $\sigma(x)=\bot$ for all $x$.
-For two atomic formulas $P,Q$ (or terms $s,t$) the \defn{initial witness map} $\sigma(P,Q)$ is the smallest witness map $\sigma$ such that $P\sigma=\dual Q\sigma$ and $P\sigma$ has no free existential variables.
-If it exists, it is defined inductively as follows (omitting the symmetric case for $\dual p$ and $p$).
-%
-%\begin{align*}
-%	\left.\begin{array}{r}
-%		\sigma(\,x\,,\,t\,) \\
-%	 	\sigma(\,t\,,\,x\,)
-%	\end{array}\right\}
-%	& = \{ x\mapsto t \}\quad \text{if $t\in\termsA$}
-% \\
-%	\left.\begin{array}{r}
-%		\sigma(\,p(s_1,\dots,s_n)\,,\,\dual p(t_1,\dots,t_n)\,) \\
-%		\sigma(\,f(s_1,\dots,s_n)\,,\,f(t_1,\dots,t_n)\,)
-%	\end{array}\right\}
-%	& = \sigma(s_1,t_1)\ubot\dots\ubot\sigma(s_n,t_n)
-%\end{align*}
-%
-%\begin{lemma}
-%\label{lem:minimal witness map}
-%For first-order terms $s$ and $t$ the witness map $\sigma(s,t)$ is the smallest such that $s\sigma=t\sigma$ and $s\sigma$ contains no existential variables.
-%\end{lemma}
-%
-%\begin{proof}
-%By induction on $s$ and $t$. If $s=x$ then $\sigma(x,t)$ exists if and only if $t\in\termsA$, 
-%\end{proof}
-
-%\begin{align*}
-%	\sigma_V(\,a\,,\,a\,) \kern12.5pt & = \varnothing
-%\\	\sigma_V(\,x\,,\,x\,) \kern12.5pt & = \varnothing\quad \text{if $x\in V$}
-%\\
-%	\left.\begin{array}{r}
-%		\sigma_V(\,x\,,\,t\,) \\
-%	 	\sigma_V(\,t\,,\,x\,)
-%	\end{array}\right\}
-%	& = \{ x\mapsto t \}\quad \text{if $x\notin V$ and $t\in\termsA$}
-% \\
-%	\left.\begin{array}{r}
-%		\sigma_V(\,p(s_1,\dots,s_n)\,,\,p(t_1,\dots,t_n)\,) \\
-%		\sigma_V(\,f(s_1,\dots,s_n)\,,\,f(t_1,\dots,t_n)\,)
-%	\end{array}\right\}
-%	& = \sigma_V(s_1,t_1)\ubot\dots\ubot\sigma_V(s_n,t_n)
-%\\	
-%	\left.\begin{array}{r}
-%		\sigma_V(\,A\+B\,,\,C\+D\,) \\
-%		\sigma_V(\,A\*B\,,\,C\*D\,)
-%	\end{array}\right\}
-%	& = \sigma_V(A,C)\ubot\sigma_V(B,D)
-%\\	
-%	\sigma_V(\,\forall a.A\,,\,\forall a.B\,)
-%		 \kern12.5pt & = \sigma_V(A,B)
-%\\	\sigma_V(\,\exists x.A\,,\,\exists x.B\,)
-%		 \kern12.5pt & = \sigma_{V\cup\{x\}}(A,B)
-%\end{align*}
-%
-%Observe that if the witness map $\sigma=\sigma(A,B)$ exists then $A\sigma=B\sigma$.
-
-% --------------------------------------------------
-
-\begin{lemma}
-Given a proof $\prf\Pi AB$ and formulas $A'$ and $B'$, if a smallest witness map $\tau$ exists such that $A=A'\tau$ and $B=B'\tau$, then $\deseq\Pi{A'}{B'}$ coalesces to $\clink{A'}{B'}$ with $\sigma\leq\tau$.
-\end{lemma}
-
-\begin{proof}
-By induction on $\Pi$.
-
-\newlength\prooftablewidth
-\setlength\prooftablewidth{-80pt}
-\addtolength\prooftablewidth{\textwidth}
-
-\noindent
-\begin{tabular}{@{}p{80pt}@{}p{\prooftablewidth}@{}}
-	\hfill \raisebox{-20pt}{\infer{\seq P{\dual P}}{\vphantom B}} \hfill\hfill
-&
-	Let $A'=Q$ and $B'=R$, and suppose $\tau$ is the smallest witness map such that $Q\tau=P$ and $R\tau=\dual P$.
-The desequentialization $\deseq\Pi QR$ is the $\net{\{Q,R\}}QR$, which coalesces to $\clink QR$ if $\sigma=\sigma(Q,{\dual R})$ exists.
-Since $\tau$ is a unifier of $Q$ and $\dual R$, $\sigma\leq\tau$.
-\\ \\
-%	$\infer{\seq A{B_0\+B_1}}{\seq A{B_i}}$
-%&
-%\\ \\
-	\hfill \raisebox{-20pt}{\infer{\seq A{B\*C}}{\seq AB && \seq AC}}\hfill\hfill
-&
-	Let $\seq{\prf\Pi AB}{A'}{B'}$ coalesce to the two subproofs coalesce to $\clink{A'}{B'}$ and $\clink[\rho]{A'}{B'}$ 
-%	\infer{\seq A{\exists x.B}}{\seq A{B[t/x]}}
-%	\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]{\seq A{\forall a.B}}{\seq AB}
-\end{tabular}
-
-\end{proof}

### 2018-03-23 Archive/ALL1-backup-4.tex
some cleanup

--- 2017-12-19 ALL1-backup-3.tex
@@
-\documentclass{article}
+\documentclass[UKenglish]{lipics-v2016}
 
 \usepackage{amsmath,amssymb,amsthm}
+\usepackage{latexsym}
+\usepackage{microtype}
 \usepackage{proof}
@@
 
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
-\theoremstyle{plain}
-\newtheorem{lemma}[definition]{Lemma}
+\bibliographystyle{plainurl}
+
+% ============================== MACROS
+
+\makeatletter
 
@@
 \newcommand\subs[1]{\textsc{sub}(#1)}
+\newcommand\dom[1]{\textsc{dom}(#1)}
 
@@
 
+\newcommand\mgu{\textsc{mgu}}
+
+\newcommand\ult{\subseteq}
+\newcommand\uco{\smallfrown}
+\newcommand\ujn{\cup}
+
+\newcommand\vlt{\le}
+\newcommand\vco{\mathrel{\makebox[5pt][c]{\raisebox{-1ex}{$\widehat{}$}}}}
+\newcommand\vjn{\vee}
+
 \newcommand\join\bowtie
@@
 %\newcommand\ubot{\mathbin{\ooalign{$\cup$\cr\hss\scalebox{.9}{\raisebox{0.6ex}{\tiny$\mathbf\bot$}}\hss}}}
-
-\newcommand\mgu{\textsc{mgu}}
 
@@
 
+\newcommand\ucoal{\leadsto}
+\newcommand\vcoal{\rightsquigarrow}
+
+\newcommand\urr[1]{
+  \ifx#1+\expandafter\@urr\else
+  \ifx#1*(\*)\else
+  \ifx#1!(\forall)\else
+  \ifx#1?(\exists)\else
+  (#1)
+  \fi\fi\fi\fi
+}
+\newcommand\@urr[1]{(+_{#1})}
+\newcommand\vrr[1]{
+  \ifx#1+\expandafter\@vrr\else
+  \ifx#1*\langle\*\rangle\else
+  \ifx#1!\langle\forall\rangle\else
+  \ifx#1?\langle\exists\rangle\else
+  \langle#1\rangle
+  \fi\fi\fi\fi
+}
+\newcommand\@vrr[1]{\langle+_{#1}\rangle}
+
 \newcommand\coals{\rightsquigarrow}
@@
 
+% ===== Derivations
+
+\newcommand\udn{\mathrel{\rotatebox[origin=c]{-90}{$\ucoal$}\kern1pt}}
+\newcommand\vdn{\mathrel{\rotatebox[origin=c]{-90}{$\vcoal$}}}
+
+\newcommandx\ujg[4][2=\sigma]{#1\udn\clink[#2]{#3}{#4}}	%{#2\udn_{#1}{#3}\mathbin,{#4}}
+\newcommandx\vjg[4][2=\sigma]{#1\vdn\clink[#2]{#3}{#4}}	%{#2\vdn_{#1}{#3}\mathbin,{#4}}
+
+\makeatother
+
+% ============================== TITLE & AUTHORS
+
+\title{Proof nets for first-order additive linear logic}
+%\titlerunning{Proof nets for ALL1}
+
+\author[1]{Willem B.\ Heijltjes}
+\author[2]{Dominic J.D.\ Hughes}
+\author[3]{Lutz Stra\ss burger}
+\affil[1]{University of Bath, United Kingdom\\
+  \texttt{w.b.heijltjes@bath.ac.uk}}
+\affil[2]{
+  \texttt{}}
+\affil[3]{INRIA \&\ \'Ecole Polytechnique, Palaiseau, France\\
+  \texttt{lutz.strassburger@inria.fr}}
+\authorrunning{W.B.\ Heijltjes, D.J.D.\ Hughes, and L.\ Stra\ss burger}
+
+\Copyright{Willem B.\ Heijltjes, Dominic J.D.\ Hughes, and Lutz Stra\ss burger}
+
+\subjclass{Dummy classification -- please refer to \url{http://www.acm.org/about/class/ccs98-html}}% mandatory: Please choose ACM 1998 classifications from http://www.acm.org/about/class/ccs98-html .
+E.g., cite as "F.1.1 Models of Computation".
+\keywords{Linear logic, Proof nets}
+
+% ============================== CONTENT
+
 \begin{document}
+
+% --------------------------------------------------
+
+\subsection{Sequentialization}
+
+\[
+	\infer{\seq P{\dual P}}{}
+\qquad
+	\infer{\seq A{B_0\+B_1}}{\seq A{B_i}}
+\qquad
+	\infer{\seq A{B\*C}}{\seq AB && \seq AC}
+\qquad
+	\infer{\seq A{\exists x.B}}{\seq A{B[t/x]}}
+\qquad
+	\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]{\seq A{\forall a.B}}{\seq AB}
+\]
+
+\[
+	\infer[\!\!\scriptstyle{Q\sigma=\dual R\sigma}]{\ujg{\clink QR}QR}{}
+\]
+
+\[
+	\infer[\!\!\scriptstyle{\sigma\,=\,\sigma(Q,R)}]{\vjg{\clink[]QR}QR}{}
+\]
+
+\[
+	\infer{\ujg\lambda A{B_0\+B_1}}{\ujg\lambda A{B_i}}
+\]
+
+\[
+	\infer{\vjg\lambda A{B_0\+B_1}}{\vjg\lambda A{B_i}}
+\]
+
+\[
+	\infer[\!\!\scriptstyle{\sigma\,\uco\,\tau}\vphantom)]{\ujg{\lambda\cup\kappa}[\sigma\ujn\tau]A{B\*C}}{\ujg\lambda[\sigma]AB && \ujg\kappa[\tau]AC}
+\]
+
+\[
+	\infer[\!\!\scriptstyle{\sigma\,\vco\,\tau}\vphantom)]{\vjg{\lambda\cup\kappa}[\sigma\vjn\tau]A{B\*C}}{\vjg\lambda[\sigma]AB && \vjg\kappa[\tau]AC}
+\]
+
+\[
+	\infer{\ujg\lambda[\sigma\!\minus\!x]A{\exists x.B}}{\ujg\lambda AB}
+\]
+
+\[
+	\infer{\vjg\lambda[\sigma\!\minus\!x]A{\exists x.B}}{\vjg\lambda AB}
+\]
+
+\end{document}
+
+\maketitle
+
+\begin{abstract}
+
+\end{abstract}
+
+\subsection{Proof identity}
+
+\[
+	\infer={\exists x.p(x),\exists y.\dual p(y)}{\infer{p(t),\dual p(t)}{}}
+	\quad
+	\stackrel?\equiv
+	\quad
+	\infer={\exists x.P(x),\exists y.\dual p(y)}{\infer{p(s),\dual p(s)}{}}
+\]
+
+\[
+	\infer{\exists x.p,\dual p}{\infer{p[t/x],\dual p}{}}
+	\quad
+	\stackrel?\equiv
+	\quad	
+	\infer{\exists x.p,\dual p}{\infer{p[s/x],\dual p}{}}
+\]
+
+\[
+	\infer{\exists x.p\+q(x),\dual p}{\infer{p\+q(t)}{\infer{p,\dual p}{}}}
+	\quad
+	\stackrel?\equiv
+	\quad	
+	\infer{\exists x.p\+q(x),\dual p}{\infer{p\+q(s)}{\infer{p,\dual p}{}}}
+\]
 
@@
 \begin{figure}
-\hrule
-\par\bigskip
 \[
@@
 	\infer{\seq A{B\*C}}{\seq AB && \seq AC}
-\]
-\par
-\[
+\qquad
 	\infer{\seq A{\exists x.B}}{\seq A{B[t/x]}}
@@
 \]
-\par
-\[
-	\infer{\seq A{\dual A}}{}
-\qquad
-	\infer{\seq AC}{\seq AB && \seq{\dual B}C}
-\]
-\par\bigskip\hrule
 \caption{A sequent calculus for $\all1$}
@@
 \[
-\begin{array}{l@{}l}
+\begin{array}{@{}l@{}l}
 	t &\Coloneqq a \Mid x \Mid f(t_1,\dots,t_n)
@@
 %
-\\[2\itemsep]
-%
+\[
 \begin{tabular}{@{}lll@{}}
@@
 \end{tabular}
+\]
 %
-\\[2\itemsep]
-%
-A \defn{sequent} $\seq AB$ is an ordered pair of formulas $A$ and $B$.
+A \defn{sequent} $\seq AB$ is a pair of formulas $A$ and $B$.
 A sequent calculus for \all1 is given in Figure~\ref{fig:sequent calculus}, where each rule has a symmetric counterpart that applies to the first formula in the sequent.
@@
 For instance, a formula $A\*A$ has two subformulas $A$, one on the left and one on the right.
-The \defn{subformulas} $\subs A$ of a formula are given by
+The \defn{subformulas} $\subs A$ of a formula are defined as follows; we write $B\sub A$ if $B$ is a subformula of $A$, i.e.\ if $B\in\subs A$.
 \[
@@
 \]
-We will write $B\sub A$ if $B$ is a subformula of $A$.
 
-In the context of a sequent $\seq AB$, a \defn{link} $(A',B')$ is a pair of subformulas $A'\leq A$ and $B'\leq B$.
-A link is an \defn{axiom link} if both formulas are atomic propositions.
-A \defn{linking} $\lambda$ on the sequent $\seq AB$ is a set of links on $\seq AB$.
-%It is an \defn{axiom linking} if all links are axiom links.
+A \defn{witness map} $\sigma\colon \varE \rightharpoonup \terms$ is a substitution map which assigns terms to existential variables, given as a partial function.
+The \defn{empty} witness map $\varnothing$ is the everywhere undefined partial function.
+The map $\sigma[x\mapsto t]$ substitutes $t$ for $x$ and is as $\sigma$ everywhere else.
+
+A \defn{link} $\clink CD$ on a sequent $\seq AB$ is a pair of subformulas $C\leq A$ and $D\leq B$ along with a witness map $\sigma$.
+We assume the existential variables occurring in the range of $\sigma$ to be fresh, i.e.\ distinct from any existentially quantified variable in $\seq AB$.
+A \defn{linking} $\lambda$ on the sequent $\seq AB$ is a set of links on it.% $\seq AB$.
 
@@
 
-A \defn{witness map} $\sigma$ is a substitution map
+An \defn{axiom} link is a link $\clink PQ$, and a linking consisting of only axiom links an \defn{axiom linking}.
+%
+A link is \defn{clean} if its witness map is empty, $\clink[\varnothing]CD$; it may then be rendered simply $(C,D)$.
+A linking or pre-net is \defn{clean} if all its links are.
+We write $\floor\lambda$ respectively $\floor{\net\lambda AB}$ for the clean version of a linking or pre-net, which forgets the witness map for each link.
+%
+A link is \defn{strict} if its domain consists of exactly the existentially quantified variables that its formulas are in scope of.
+That is, a link $\clink CD$ in a pre-net $\net\lambda AB$ is strict if
 \[
-	\sigma\colon \varE \to \terms
+	\dom\sigma = \{\,x \mid C < \exists x.X \leq A\,\}
+			\cup \{\,y \mid D < \exists y.Y \leq B\,\}~.
 \]
-which assigns terms to existential variables.
-We write $\varnothing$ for the empty map (the identity).
-The map $\sigma[x\mapsto t]$ substitutes $t$ for $x$ and is as $\sigma$ everywhere else, while $\sigma\minus x$ is the identity on $x$ and otherwise as $\sigma$.
-The application of a witness map $\sigma$ to a formula $A$ is written $A\sigma$.
-
-A \defn{labelled link} $\clink AB$ is a link carrying a witness map $\sigma$.
-A \defn{labelled linking} respectively a \defn{labelled pre-net} is a linking or pre-net where every link is labelled.
-A labelled linking $\lambda$ reverts to an unlabelled one, written $\floor\lambda$, by dropping the label of each link.
+A linking or pre-net is \defn{strict} if all its links are.
 
 \begin{definition}
-The \defn{labelled de-sequentialization} of a sequent proof $\prf\Pi AB$ is the labelled pre-net $\net{\deseq[\varnothing]\Pi AB} AB$ where $\deseq-AB$ is defined as follows.
+The \defn{de-sequentialization} $[\Pi]$ of a sequent proof $\prf\Pi AB$ is the pre-net $\net{\deseq[\varnothing]\Pi AB} AB$ where $\deseq-AB$ is defined as follows.
 %
@@
 \]
-The \defn{(unlabelled) de-sequentialization} of $\Pi$ is $\net{\floor\Pi_{A,B}}AB$ where $\floor\Pi_{A,B}$ is $\floor{\deseq[\varnothing]\Pi AB}$.
+The \defn{clean} de-sequentialization $\floor\Pi$ of $\prf\Pi AB$ is $\floor{[\Pi]}$.
 \end{definition}
 
-To generate witness maps for an unlabelled linking, we will be using unification.
-A \defn{unifying} witness map $\sigma$ for formulas $A$ and $B$ is one such that $A\sigma=B\sigma$.
-Note that these will substitute only the free existential variables, but not bound ones or universal variables.
-For instance, the only unifying witness map of $p(x,y)$ and $p(a,a)$ is $\{x\mapsto a,y\mapsto a\}$, while $\exists y.p(x,x)$ and $\exists y.p(a,y)$ have no unifier.
+Observe that the pre-net $[\Pi]$ has a strict axiom linking and $\floor\Pi$ a clean axiom linking.
 
-A witness map $\sigma$ is \defn{more general} than $\tau$, witten $\sigma\leq\tau$, if there is a $\rho$ such that $(A\sigma)\rho = A\tau$ for any $A$.
-The \defn{join} $\sigma\join\tau$ of two maps $\sigma$ and $\tau$ is the least map $\rho$ such that $\sigma\leq\rho$ and $\tau\leq\rho$, if it exists.
-If it does, we call $\sigma$ and $\tau$ \defn{compatible}, written $\sigma\comp\tau$.
+\subsection{Witness maps}
 
-The \defn{initial witness map} $\sigma(A,B)$ is the most general unifying witness map for the formulas $A$ and $B$, if it exists; if it does, $A$ and $B$ are \defn{compatible}.
-An unlabelled axiom link $(P,Q)$ is \defn{compatible} if $P$ and $\dual Q$ are compatible; a labelled one $\clink PQ$ is \defn{compatible} if $\sigma$ is a unifier for $P$ and $\dual Q$.
-A (labelled) linking or pre-net is \defn{compatible} if all links are compatible axiom links.
-The \defn{initial labelling} of a compatible linking $\lambda$ or pre-net $\net\lambda AB$ is the labelled linking $\lambda_\star$ or labelled pre-net $\net{\lambda_\star}AB$ given by
+We will write $A\sigma$ for the application of the witness map $\sigma\colon\varE\rightharpoonup\terms$ to the formula $A$ as a substitution map.
+The \defn{composition} of two maps is written $\sigma\tau$, where $A(\sigma\tau)=(A\sigma)\tau$.
+The map $\sigma\minus x$ is undefined on $x$ and otherwise as $\sigma$, and $\sigma|X$ is as $\sigma$ on the set of variables $X$ and undefined otherwise.
+We define the following further operations on witness maps.
+
 \[
-	\lambda_\star = \{~\clink[\sigma(P,\dual Q)]PQ~\mid~(P,Q)\in\lambda~\}~.
+\begin{tabular}{@{}lp{.75\textwidth}@{}}
+	$\sigma\ult\tau$
+&
+	A witness map is \defn{included} in another, $\sigma\ult\tau$,
+	if for every $x\in\varE$, $\sigma(x)=t$ implies $\tau(x)=t$.
+\\[5pt]	
+	$\sigma\uco\tau$
+&
+	Two witness maps are \defn{coherent}, $\sigma\uco\tau$,
+	if for every $x\in\varE$, if $\sigma(x)$ and $\tau(x)$
+	are both defined then $\sigma(x)=\tau(x)$.
+\\[5pt]
+	$\sigma\ujn\tau$
+&
+	The \defn{union} of two witness maps $\sigma\ujn\tau$
+	is defined if they are coherent, and is the map taking
+	$x$ to $\sigma(x)$ or $\tau(x)$ if either is defined.
+\\[5pt]
+	$\sigma\vlt\tau$
+&
+	A witness map is \defn{more general} than another, 
+	$\sigma\vlt\tau$, if there is a map $\rho$ such that 
+	$\sigma\rho=\tau$.
+\\[5pt]	
+	$\sigma\vco\tau$
+&
+	Two witness maps are \defn{compatible}, $\sigma\vco\tau$,
+	if there is a map $\rho$ such that $\sigma\rho=\tau\rho$.
+\\[5pt]
+	$\sigma\vjn\tau$
+&
+	The \defn{join} of two witness maps $\sigma\vjn\tau$ is defined
+	if they are compatible, and is the least map $\rho$ such that
+	$\sigma\vlt\rho$ and $\tau\vlt\rho$.
+\end{tabular}%
 \]
-%Observe that $\floor{\lambda_\star}=\lambda$. We call $\floor\lambda_\star$ the \defn{initial re-labelling} of a labelled linking $\lambda$, and analogously for a pre-net $\net\lambda AB$.
 
@@
 
-% ..................................................
-
-\begin{figure}
-\hrule
-\par\bigskip
-\[
-\begin{array}{rcl@{\hspace{40pt}}rcl} 
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{A}
-    	\formula[y=1]{B\+C}
-    	\Vlink[red,label={$\scriptstyle\sigma~$},l]{1,1}
-    \end{tikzpicture}}
-&\rightsquigarrow& 
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{A}
-    	\formula[y=1]{B\+C}
-    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,2}
-    \end{tikzpicture}}
-&    
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{A}
-    	\formula[y=1]{\exists x.B}
-    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,4}
-    \end{tikzpicture}}
-&\rightsquigarrow&
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{A}
-    	\formula[y=1]{\exists x.B}
-    	\Vlink[red,label={~$\scriptstyle{\sigma\!\minus\!x}$}]{1,1}
-    \end{tikzpicture}}
-\\ \\    
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{A}
-    	\formula[y=1]{B\*C}
-    	\Vlink[red,label={$\scriptstyle\sigma~$},l]{[-1]1,1}
-    	\Vlink[red,label={~$\scriptstyle\tau$}]{[1]1,3}
-    \end{tikzpicture}}
-&\stackrel{\sigma\comp\tau}\rightsquigarrow&   
-	\vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{A}
-    	\formula[y=1]{B\*C}
-    	\Vlink[red,label={~$\scriptstyle{\sigma\cup\tau}$}]{1,2}
-    \end{tikzpicture}}
-&  
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{A}
-    	\formula[y=1]{\forall a.B}
-    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,4}
-    \end{tikzpicture}}
-&\stackrel{a\,\notin\,\fv(A\sigma)}\rightsquigarrow&
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{A}
-    	\formula[y=1]{\forall a.B}
-    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,1}
-    \end{tikzpicture}}
-\end{array}
-\]
-\par\bigskip\hrule
-\caption{Coalescence rules}
-\label{fig:coalescence}
-\end{figure}
-
-% ..................................................
+We will define two \defn{coalescence} relations, one \defn{compounding} $(\ucoal)$ and one \defn{unifying} $(\vcoal)$.
 
 \begin{definition}
-\defn{Coalescence} ($\coals$) is the rewrite relation on labelled pre-nets generated by the following rewrite rules, and their symmetric variants.
+\defn{Compounding coalescence} ($\ucoal$) is the rewrite relation on pre-nets generated by the following rules, which apply symmetrically to the first formula in the sequent.
 %
@@
   	\net{\{\clink AB\}}A{B\+C} 
-& ~\coal~
+& ~\ucoal~
 	\net{\{\clink A{B\+C}\}}A{B\+C}
@@
         \net{\{\clink AC\}}A{B\+C}
-& ~\coal~  
+& ~\ucoal~  
 	\net{\{\clink A{B\+C}\}}A{B\+C}
@@
 	\net{\{\clink AB,\clink[\tau]AC\}}A{B\*C}
-& ~\coal~ 
-	\net{\{\clink[\sigma\join\tau]A{B\*C}\}}A{B\*C}\quad\text{if }\sigma\comp\tau
+& ~\ucoal~ 
+	\net{\{\clink[\sigma\ujn\tau]A{B\*C}\}}A{B\*C}\quad\text{if }\sigma\uco\tau
 \tag{$\*$}
@@
 	\net{\{\clink AB\}}A{\exists x.B}
-& ~\coal~ 
+& ~\ucoal~ 
 	\net{\{\clink[\sigma\!\minus\!x]A{\exists x.B}\}}A{\exists x.B}
@@
 	\net{\{\clink AB\}}A{\forall a.B}
-& ~\coal~ 
+& ~\ucoal~ 
 	\net{\clink A{\forall a.B}}A{\forall a.B} \quad \text{if }a\,\notin\,\fv(A\sigma)
@@
 \end{align}
-%\[
-%\renewcommand{\+}{{+}}
-%\renewcommand{\*}{{\times}}
-%\begin{array}{r@{}c@{\,}c@{\,~}l}
-%    \begin{array}{@{}r@{}}
-%        \net{\{\clink AB\}}A{B\+C} \\ \\[-5pt]
-%        \net{\{\clink AC\}}A{B\+C}
-%    \end{array}
-%&   \left.\begin{array}{@{}c@{}} 
-%		\vphantom\{\\\\[-5pt]\vphantom\{
-%	\end{array}\right\}
-%& \coal &
-%	\net{\{\clink A{B\+C}\}}A{B\+C}
-%\\ \\[-5pt]
-%	\net{\{\clink AB,\clink[\tau]AC\}}A{B\*C}
-%&& \coal &
-%	\net{\{\clink[\sigma\join\tau]A{B\*C}\}}A{B\*C}\quad\text{if }\sigma\comp\tau
-%\\ \\[-5pt]	
-%	\net{\{\clink AB\}}A{\exists x.B}
-%&& \coal &
-%	\net{\{\clink[\sigma\!\minus\!x]A{\exists x.B}\}}A{\exists x.B}
-%\\ \\[-5pt]
-%	\net{\{\clink AB\}}A{\forall a.B}
-%&& \coal &
-%	\net{\clink A{\forall a.B}}A{\forall a.B} \quad \text{if }a\,\notin\,\fv(A\sigma)
-%\end{array}
-%\]
-%\begin{itemize}
-%	\item 
-%\makebox[40pt][l]{$B\+C$:} 
-%Replace a link $\clink AB$ or $\clink AC$ with $\clink A{B\+C}$.
-%	\item 
-%\makebox[40pt][l]{$B\*C$:} 
-%Replace links $\clink AB$ and $\clink[\tau]AC$ with $\clink[\sigma\cup\tau]A{B\*C} $ if $\sigma\comp\tau$.
-%	\item
-%\makebox[40pt][l]{$\exists x.B$:} 
-%Replace a link $\clink AB$ with $\clink[\sigma\minus x]A{\exists x.B}$.
-%	\item
-%\makebox[40pt][l]{$\forall a.B$:}
-%Replace a link $\clink AB$ with $\clink A{\forall a.B}$ if $a\,\notin\,\fv(A\sigma)$.
-%\end{itemize}
 %
+\defn{Unifying coalescence} ($\vcoal$) is the rewrite relation generated by the following rules:
+\[
+	\vrr+1~,~\vrr+2~,~\vrr?~,~\vrr!
+	\quad
+	\text{are respectively as}
+	\quad
+	\urr+1~,~\urr+2~,~\urr?~,~\urr!
+\]
+plus the rule
+\renewcommand{\+}{{+}}
+\renewcommand{\*}{{\times}}
+\begin{align}
+	\net{\{\clink AB,\clink[\tau]AC\}}A{B\*C}
+& ~\vcoal~ 
+	\net{\{\clink[\sigma\vjn\tau]A{B\*C}\}}A{B\*C}\quad\text{if }\sigma\vco\tau~.
+\tag*{$\vrr*$}
+\end{align}
 %
-%\begin{itemize}
-%	\item 
-%\makebox[40pt][l]{$B\+C$:} 
-%Replace a link $\clink AB$ or $\clink AC$ with $\clink A{B\+C}$.
-%	\item 
-%\makebox[40pt][l]{$B\*C$:} 
-%Replace links $\clink AB$ and $\clink[\tau]AC$ with $\clink[\sigma\cup\tau]A{B\*C} $ if $\sigma\comp\tau$.
-%	\item
-%\makebox[40pt][l]{$\exists x.B$:} 
-%Replace a link $\clink AB$ with $\clink[\sigma\minus x]A{\exists x.B}$.
-%	\item
-%\makebox[40pt][l]{$\forall a.B$:}
-%Replace a link $\clink AB$ with $\clink A{\forall a.B}$ if $a\,\notin\,\fv(A\sigma)$.
-%\end{itemize}
-%
-A labelled pre-net $\net\lambda AB$ \defn{coalesces} if it coalesces to a single link $\clink[\varnothing]AB$.
-A compatible pre-net \defn{coalesces} if $\net{\lambda_\star}AB$ coalesces.
-A pre-net \defn{strongly coalesces} if every coalescence sequence terminates at $\clink[\varnothing]AB$.
+A pre-net $\net\lambda AB$ \defn{coalesces}, in either relation $(\ucoal)$ or $(\vcoal)$, if it coalesces to a single clean link $\net{(A,B)}AB$.
+It \defn{strongly coalesces} if every coalescence sequence terminates at $\net{(A,B)}AB$.
 \end{definition}
 
-To be explicit, generating coalescence as a rewrite relation means the following: $\net\lambda AB\coal \net{\lambda'}AB$ if and only if there is a rewrite rule $\net\kappa CD\coal\net{\kappa'} CD$ such that $C\leq A$, $D\leq B$, $\kappa\subseteq\lambda$, and $\lambda'=\lambda\cup\kappa'-\kappa$.
+To be explicit, to generate coalescence as a rewrite relation means the following: a pre-net coalesces to another, $\net\lambda AB\ucoal \net{\lambda'}AB$ if and only if there is a rewrite rule $\net\kappa CD\ucoal\net{\kappa'} CD$ such that $C\leq A$, $D\leq B$, $\kappa\subseteq\lambda$, $\kappa'\subseteq\lambda'$, and $\lambda-\kappa=\lambda'-\kappa'$; and likewise for $(\vcoal)$.
+
+\begin{definition}
+An \all1 \defn{witnessing proof net} or \defn{witness net} is a pre-net $\net\lambda AB$ with a strict axiom linking $\lambda$, that compounding-coalesces.
+\end{definition}
+
+Coalescence on a clean axiom linking is initiated by assigning each link $(P,Q)$ an \defn{initial witness map} $\sigma(P,Q)$ which, if it exists, is the most general witness map $\sigma$ such that $P\sigma=\dual Q\sigma$.
+In other words, $\sigma(P,Q)$ is the most general unifier ($\textsc{mgu}$) of $P$ and $\dual Q$.
+If it exists, we call the link $(P,Q)$ \defn{compatible}, and a linking is \defn{compatible} if all its links are.
+For a compatible axiom linking $\lambda$ we define the \defn{initial witness assignment} $\lambda_\star$ to be:
+\[
+	\lambda_\star = \{~\clink PQ~\mid~(P,Q)\in\lambda~,~\sigma=\sigma(P,Q)~\}~.
+\]
+
+\begin{definition}
+An \all1 \defn{unification proof net} or \defn{unification net} is a pre-net $\net\lambda AB$ with a clean, compatible axiom linking $\lambda$, such that $\net{\lambda_\star}AB$ unifying-coalesces.
+\end{definition}
+
+% --------------------------------------------------
+
+\subsection{Sequentialization}
+
+\end{document}
 
@@
 \end{proof}
+
+\begin{description}
+	\item[$\sigma\ult\tau$] 
+A witness map is \defn{included} in another, $\sigma\ult\tau$, if for every $x\in\varE$, $\sigma(x)=t$ implies $\tau(x)=t$.
+	\item[$\sigma\uco\tau$]
+Two witness maps are \defn{coherent}, $\sigma\uco\tau$, if for every $x\in\varE$, if $\sigma(x)$ and $\tau(x)$ are both defined then $\sigma(x)=\tau(x)$.
+	\item[$\sigma\ujn\tau$]
+The \defn{union} of two witness maps $\sigma\ujn\tau$ is defined if they are coherent, and is the map taking $x$ to $\sigma(x)$ or $\tau(x)$ if either is defined.
+	\item[$\sigma\vlt\tau$]
+A witness map is \defn{more general} than another, $\sigma\vlt\tau$, if there is a map $\rho$ such that $\sigma\rho=\tau$.
+	\item[$\sigma\vco\tau$]
+Two witness maps are \defn{compatible}, $\sigma\vco\tau$, if there is a map $\rho$ such that $\sigma\rho=\tau\rho$.
+	\item[$\sigma\vjn\tau$]
+The \defn{join} of two witness maps $\sigma\vjn\tau$ is defined if they are compatible, and is the least map $\rho$ such that $\sigma\vlt\rho$ and $\tau\vlt\rho$.
+\end{description}

### 2018-03-23 Archive/ALL1-backup-5.tex
some cleanup

--- 2017-12-19 ALL1-backup-6.tex
@@
   \ifx#1!\forall\mathrm R\else
-  \ifx#1?\expandafter\@@qrr\else
+  \ifx#1?\exists\mathrm R\else 
   \ifx#11\mathrm{ax}\else
@@
 }
-\newcommand\@qrr[1]{+\mathrm R,#1}
-\newcommand\@@qrr[1]{\exists\mathrm R,#1}
+\newcommand\@qrr[1]{+_{#1}\mathrm R}
 \newcommand\srr[1]{
@@
 \[
-	\sigma = [a/y, s/x]
+	\sigma = [y\mapsto a, x\mapsto s]
 	\qquad
-	\tau = [a/y, t/x]
-\]
-\[
-	\upsilon = \rho[a/y, u/x]
+	\tau = [y\mapsto a, x\mapsto t]
+\]
+\[
+	\upsilon = \rho[y\mapsto a, x\mapsto u]
 	\qquad
@@
 \quad
-	\infer[\!\!\scriptstyle{\qrr*}]{\seq A{B\*C}}{\seq AB & \seq AC}
-\quad
-	\infer[\!\!\scriptstyle{\qrr?t}]{\seq A{\exists x.B}}{\seq A{B[t/x]}}
+	\infer[\!\!\scriptstyle{\qrr*}]{\seq A{B\*C}}{\seq AB && \seq AC}
+\quad
+	\infer[\!\!\scriptstyle{\qrr?}]{\seq A{\exists x.B}}{\seq A{B[t/x]}}
 \quad
@@
 A \defn{witness map} $\sigma\colon \varE \rightharpoonup \terms$ is a substitution map which assigns terms to existential variables, given as a partial function.
-The \defn{empty} witness map $\varnothing$ is the everywhere undefined partial function, and the map $\sigma[t/x]$ substitutes $t$ for $x$ and is as $\sigma$ everywhere else.
+The \defn{empty} witness map $\varnothing$ is the everywhere undefined partial function, and the map $\sigma[x\mapsto t]$ substitutes $t$ for $x$ and is as $\sigma$ everywhere else.
 We express by $\sigma(x)=\bot$ that $\sigma$ is undefined for $x$.
 
-A \defn{link} $(C,D)$ or $\link CD$ on a sequent $\seq AB$ is a pair of subformulas $C\leq A$ and $D\leq B$, possibly carrying a witness map $\sigma$.
-We explicitly call a link $(C,D)$ without witness map \defn{clean}; otherwise $\sigma$ is assumed present.
+A \defn{link} $\link CD$ on a sequent $\seq AB$ is a pair of subformulas $C\leq A$ and $D\leq B$ along with a witness map $\sigma$.
 We assume the existential variables occurring in the range of $\sigma$ to be fresh, i.e.\ distinct from any existentially quantified variable in $\seq AB$.
-A \defn{linking} $\lambda$ on the sequent $\seq AB$ is a set of links on it.
-The clean linking $\floor\lambda$ forgets the witness maps of a linking $\lambda$.
+A \defn{linking} $\lambda$ on the sequent $\seq AB$ is a set of links on it.% $\seq AB$.
 
@@
 
-An \defn{axiom link} is a link $\link PQ$ on two propositional atoms such that $P\sigma=\dual Q\sigma$.
+An \defn{axiom} link is a link $\link PQ$ on two propositional atoms.
 A linking consisting of axiom links is an \defn{axiom linking}.
-For a \emph{clean} axiom link $(P,Q)$ we require that a witness map $\sigma$ exists so that $P\sigma=\dual Q\sigma$.
-
-%A link $\link[\varnothing]CD$ with empty witness map is \defn{clean}; it may then be rendered simply $(C,D)$. A linking or pre-net is \defn{clean} if all its links are. 
-%We write $\floor\lambda$ respectively $\floor{\net\lambda AB}$ for the clean version of a linking or pre-net, which forgets the witness map for each link.
-
-\begin{definition}
-The \defn{de-sequentialization} $[\Pi]$ of a sequent proof $\prf\Pi AB$ is the pre-net $\net{\deseq[\varnothing]\Pi AB} AB$ where $\deseq-AB$ is defined as follows.
-%
-\begin{align*}
-	\Deseq{\infer{\seq P{\dual P}}{}}QR &\quad=\quad \{\link QR\}
-\\ \\
-	\Deseq{\infer {\seq A {B_0\+B_1}} {\deduce [\rule{0pt}{1pt}] {\seq A{B_i}} \Pi }}
-	  {A'}{B_0'\+B'_1} 
-	& \quad=\quad 
-	\Deseq{\deduce[\rule{0pt}{1pt}]{\seq A{B_i}}\Pi}{A'}{B_i'}
-\\ \\
-	\Deseq{\infer{\seq A{B\*C}}{
-	  \deduce[\rule{0pt}{1pt}]{\seq AB}\Pi 
-	  && 
-	  \deduce[\rule{0pt}{1pt}]{\seq AC}\Sigma}}{A'}{B'\*C'}
-	& \quad=\quad 
-	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AB}\Pi}{A'}{B'}
-	  \cup
-	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AC}\Sigma}{A'}{C'}
-\\ \\
-	\Deseq{\infer{\seq A{\exists x.B}}{\deduce[\rule{0pt}{1pt}]{\seq A{B[t/x]}}\Pi}}
-	  {A'}{\exists x.B'}
-	& \quad=\quad 
-	 \Deseq[{\sigma[t/x]}]{\deduce[\rule{0pt}{1pt}]{\seq A{B[t/x]}}\Pi}
-	  {A'}{B'}
-\\ \\
-	\Deseq{\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]
-	  {\seq A{\forall a.B}}{\deduce[\rule{0pt}{1pt}]{\seq AB}\Pi}}{A'}{\forall a.B'}
-	& \quad=\quad 
-	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AB}\Pi}{A'}{B'}
-\end{align*}
-%
-The \defn{clean} de-sequentialization $\floor\Pi$ is $\net{\floor{\deseq[\varnothing]\Pi AB}}AB$:  as $[\Pi]$ but forgetting witness maps.
-%
-%of $\prf\Pi AB$ is the de-sequentialization $[\Pi]$ which forgets witness maps.
-\end{definition}
-
-Observe that the linking of $[\Pi]$ is an axiom linking, and that of $\floor\Pi$ a clean axiom linking.
+A link $\link[\varnothing]CD$ with empty witness map is \defn{clean}; it may then be rendered simply $(C,D)$.
+A linking or pre-net is \defn{clean} if all its links are.
 
@@
 We will write $A\sigma$ for the application of the witness map $\sigma\colon\varE\rightharpoonup\terms$ to the formula $A$ as a substitution map.
-It is applied to a sequent proof, $\Pi\sigma$, by applying it to each formula in the proof $\Pi$.
 The \defn{composition} of two maps is written $\sigma\tau$, where $A(\sigma\tau)=(A\sigma)\tau$.
@@
 
-To a clean axiom link $(P,Q)$ we assign an \defn{initial witness map} $\sigma(P,Q)$ as the least witness map $\sigma$ in $(\gen)$ such that $P\sigma=\dual Q\sigma$.
-In other words, $\sigma(P,Q)$ is the most general unifier ($\textsc{mgu}$) of $P$ and $\dual Q$.
-The \defn{initial witness assignment} $\lambda_\star$ to a clean axiom linking is:
-\[
-	\lambda_\star = \{~\link PQ~\mid~(P,Q)\in\lambda~,~\sigma=\sigma(P,Q)~\}~.
-\]
-
 % --------------------------------------------------
 
-\subsection{Correctness and sequentialization}
-
-Correctness and sequentialization for \all1 proof nets will be through \defn{coalescence}.
-This is a simple graph rewriting relation that gives top-down sequentialization, from the axioms to the conclusion of a proof.
-It is the additive counterpart to Danos \defn{contractibility} for multiplicative linear logic.
-
-We will define two coalescence relations, one \defn{strict} $(\scoal)$ and one \defn{unifying} $(\ucoal)$.
-In the former, to join two slices the witness assignment must be the same; in the latter, witness assignments must be compatible, so that a common, more general witness map exists.
-
-For sequentialization, the links in a pre-net are labelled with a sequent calculus axiom, and each coalescence rewrite step introduces one proof rule.
-To this end, let a \defn{labelled link} $\link AB^\Pi$ be a link carrying a sequent proof $\prf\Pi{A\sigma}{B\sigma}$, and a \defn{labelled linking} or \defn{labelled pre-net} one where every link is labelled.
-The \defn{initial labelling} $\lambda^\star$ of an axiom linking $\lambda$ is:
-\[
-	\lambda^\star = \{~\link PQ^\Pi~\mid~\link PQ\in\lambda~,~\Pi=~\infer{\seq{P\sigma}{Q\sigma}}{}~\}~.
-\]
-For correctness we may coalesce a pre-net without constructing a proof.
+\subsection{Coalescence}
+
+We will define two \defn{coalescence} relations, one \defn{strict} $(\scoal)$ and one \defn{unifying} $(\ucoal)$.
 
 \begin{definition}
- \defn{Strict sequentialization} ($\scoal$) is the rewrite relation on labelled pre-nets generated by the following rules, which apply symmetrically to the first formula in the sequent.
-\defn{Strict coalescence} is the same relation ignoring proof labels, on pre-nets.
+\defn{Strict coalescence} ($\scoal$) is the rewrite relation on pre-nets generated by the following rules, which apply symmetrically to the first formula in the sequent.
 %
@@
 \renewcommand{\*}{{\times}}
-\begin{equation}
-  	\net{\{\link A{B_i}^\Pi\}}A{B_0\+B_1} 
- ~\scoal~
-	\net{\{\link A{B_0\+B_1} ^\Psi\}}A{B_0\+B_1}
-\tag{$\srr+i$}
-\end{equation}
-
-\hfill $\text{where}\quad \Psi=~
-  \vc{
-   \infer  {\seq{A\sigma}{B_0\sigma\,\+\,B_1\sigma}}  {
-  	\deduce  [\rule{0pt}{1pt}]  {\seq{A\sigma}{B_i\sigma}}  \Pi
-  }}
-$ \hspace*{20pt}
-
-\begin{equation}
-	\net{\{\link AB^\Pi,\link AC^\Phi\}}A{B\*C}
- ~\scoal~ 
-	\net{\{\link A{B\*C}^\Psi\}}A{B\*C}
+\begin{align}
+  	\net{\{\link AB\}}A{B\+C} 
+& ~\scoal~
+	\net{\{\link A{B\+C}\}}A{B\+C}
+\tag{$\srr+1$}
+\\[5pt]
+        \net{\{\link AC\}}A{B\+C}
+& ~\scoal~  
+	\net{\{\link A{B\+C}\}}A{B\+C}
+\tag{$\srr+2$}
+\\[5pt]
+	\net{\{\link AB,\link AC\}}A{B\*C}
+& ~\scoal~ 
+	\net{\{\link A{B\*C}\}}A{B\*C}
 \tag{$\srr*$}
-\end{equation}
-
-\hfill $\text{where}\quad \Psi=~
-  \vc{
-   \infer  {\seq{A\sigma}{B\sigma\,\*\,C\sigma}}  {
-    \deduce  [\rule{0pt}{1pt}]  {\seq{A\sigma}{B\sigma}}  \Pi
-    &
-    \deduce  [\rule{0pt}{1pt}]  {\seq{A\sigma}{C\sigma}}  \Phi    
-  }}$ \hspace*{20pt}
-
-\begin{equation}
-	\net{\{\link AB^\Pi\}}A{\exists x.B}
- ~\scoal~ 
-	\net{\{\link[\sigma\!\minus\!x]A{\exists x.B}^\Psi\}}A{\exists x.B}
+\\[5pt]	
+	\net{\{\link AB\}}A{\exists x.B}
+& ~\scoal~ 
+	\net{\{\link[\sigma\!\minus\!x]A{\exists x.B}\}}A{\exists x.B} \quad \text{if }\sigma(x)\,\neq\,\bot
 \tag{$\srr?$}
-\end{equation}
-
-\hfill $\text{if}\quad\sigma(x)\,\neq\,\bot~,
-		\quad
-		\text{where}\quad \tau=\sigma\minus x
-		\quad
-		\text{and}\quad \Psi=~
-  \vc{
-   \infer  {\seq{A\tau}{\exists x.B\tau}}  {
-    \deduce  [\rule{0pt}{1pt}]  {\seq{A\sigma}{B\sigma}}  \Pi  
-  }}
-$ \hspace*{20pt}
-
-\begin{equation}
+\\[5pt]
 	\net{\{\link AB\}}A{\forall a.B}
- ~\scoal~
-	\net{\link A{\forall a.B}}A{\forall a.B}
+& ~\scoal~ 
+	\net{\link A{\forall a.B}}A{\forall a.B} \quad \text{if }a\notin\sigma
 \tag{$\srr!$}
-\end{equation}
-
-\hfill $\text{if}\quad a\notin\sigma~,
-		\quad
-		\text{where}\quad \Psi=~
-  \vc{
-   \infer  {\seq{A\sigma}{\forall a.B\sigma}}  {
-    \deduce  [\rule{0pt}{1pt}]  {\seq{A\sigma}{B\sigma}}  \Pi  
-  }}
-$ \hspace*{20pt}
-
-\medskip
-
-\noindent
-A pre-net $\net\lambda AB$ \defn{strict-coalesces} if it reduces in $(\scoal)$ to a single link $\net{\{\link[\varnothing]AB\}}AB$.
+\end{align}
+%
+\defn{Unifying coalescence} ($\ucoal$) is the rewrite relation generated by the following rules:
+\[
+	(\urr+i)~,~(\urr?)~,~(\urr!)
+	\quad
+	\text{are respectively as}
+	\quad
+	(\srr+i)~,~(\srr?)~,~(\srr!)
+\]
+except $\urr?$ does not require that $\sigma(x)$ is defined, plus the rule
+\renewcommand{\+}{{+}}
+\renewcommand{\*}{{\times}}
+\begin{align}
+	\net{\{\link AB,\link[\tau]AC\}}A{B\*C}
+& ~\ucoal~ 
+	\net{\{\link[\sigma\join\tau]A{B\*C}\}}A{B\*C}\quad\text{if }\sigma\coh\tau~.
+\tag{$\urr*$}
+\end{align}
+%
+A pre-net $\net\lambda AB$ \defn{coalesces}, in either relation $(\scoal)$ or $(\ucoal)$, if it coalesces to a single clean link $\net{(A,B)}AB$.
+It \defn{strongly coalesces} if every coalescence sequence can be extended to reach $\net{(A,B)}AB$.
 \end{definition}
 
-To be explicit, to generate coalescence as a rewrite relation means the following: a pre-net coalesces to another, $\net\lambda AB\scoal \net{\lambda'}AB$ if and only if there is a rewrite rule $\net\kappa CD\scoal\net{\kappa'} CD$ such that $C\leq A$, $D\leq B$, $\kappa\subseteq\lambda$, $\kappa'\subseteq\lambda'$, and $\lambda-\kappa=\lambda'-\kappa'$.
+To be explicit, to generate coalescence as a rewrite relation means the following: a pre-net coalesces to another, $\net\lambda AB\scoal \net{\lambda'}AB$ if and only if there is a rewrite rule $\net\kappa CD\scoal\net{\kappa'} CD$ such that $C\leq A$, $D\leq B$, $\kappa\subseteq\lambda$, $\kappa'\subseteq\lambda'$, and $\lambda-\kappa=\lambda'-\kappa'$; and likewise for $(\ucoal)$.
 
 \begin{definition}
-\defn{Unifying coalescence} ($\ucoal$) is the rewrite relation generated by the rules:
-\[
-	(\urr+i)~,~(\urr?)~,~(\urr!)
-	\quad
-	\text{are respectively as}
-	\quad
-	(\srr+i)~,~(\srr?)~,~(\srr!)
-\]
-except that ($\urr?$) does not require that $\sigma(x)$ is defined, plus the rule
-\begin{equation}
-	\net{\{\link AB^\Pi,\link[\tau]AC^\Phi\}}A{B\*C}
- ~\ucoal~ 
-	\net{\{\link[\sigma\join\tau]A{B\*C}^\Psi\}}A{B\*C}
-\tag{$\urr*$}
-\end{equation}
-
-\hfill $\text{if}\quad\sigma\coh\tau~,
-		\quad
-		\text{where}\quad \sigma\join\tau=\sigma\rho=\tau\rho
-		\quad
-		\text{and}\quad \Psi=~
-  \vc{
-   \infer  {\seq{A\sigma\rho}{B\sigma\rho\,\*\,C\sigma\rho}}  {
-    \left( \vc{\deduce  [\rule{0pt}{2pt}]  {\seq{A\sigma}{B\sigma}}  \Pi} \right)\rho
-    &
-    \left( \vc{\deduce  [\rule{0pt}{2pt}]  {\seq{A\tau}{C\tau}}  \Phi} \right)\rho   
-  }}~.
-$ \hspace*{20pt}
-
-\medskip
-
-\noindent
-A pre-net $\net\lambda AB$ \defn{unifying-coalesces} if it reduces in $(\ucoal)$ to a single link $\net{\{\link[\varnothing]AB\}}AB$.
+An \all1 \defn{witnessing proof net} or \defn{witness net} is a pre-net $\net\lambda AB$ with $\lambda$ an axiom linking, that strict-coalesces.
 \end{definition}
 
-%A pre-net $\net\lambda AB$ \defn{strict-} or \defn{unifying-coalesces} if it reduces in $(\scoal)$ respectively $(\ucoal)$ to a single link $\net{\link[\varnothing]AB}AB$.
-Here, we ignore the labelling with proofs, which means in particular that we need not instate a labelling to initiate coalescence.
-
-%A pre-net $\net\lambda AB$ \defn{coalesces}, in either relation , if it coalesces to a single clean link $\net{(A,B)^\Pi}AB$.
-In that case, it \defn{sequentializes} It \defn{strongly coalesces} if every coalescence sequence can be extended to reach $\net{(A,B)}AB$.
+Coalescence on a clean axiom linking is initiated by assigning each link $(P,Q)$ an \defn{initial witness map} $\sigma(P,Q)$ which, if it exists, is the most general witness map $\sigma$ such that $P\sigma=\dual Q\sigma$.
+In other words, $\sigma(P,Q)$ is the most general unifier ($\textsc{mgu}$) of $P$ and $\dual Q$.
+If it exists, we call the link $(P,Q)$ \defn{coherent}; a linking is \defn{coherent} if all its links are.
+For a coherent axiom linking $\lambda$ we define the \defn{initial witness assignment} $\lambda_\star$ to be:
+\[
+	\lambda_\star = \{~\link PQ~\mid~(P,Q)\in\lambda~,~\sigma=\sigma(P,Q)~\}~.
+\]
 
 \begin{definition}
-An \all1 \defn{witnessing proof net} or \defn{witness net} is a pre-net $\net\lambda AB$ with axiom linking $\lambda$ that strict-coalesces.
-It \defn{sequentializes} to a proof $\Pi$ if its initial labelling $\net{\lambda^\star}AB$ reduces in $(\scoal)$ to $\net{\{\link[\varnothing]AB^\Pi\}}AB$.
+An \all1 \defn{unification proof net} or \defn{unification net} is a pre-net $\net\lambda AB$ with a clean, coherent axiom linking $\lambda$, such that $\net{\lambda_\star}AB$ unifying-coalesces.
 \end{definition}
 
-\begin{definition}
-An \all1 \defn{unification proof net} or \defn{unification net} is a pre-net $\net\lambda AB$ with clean axiom linking $\lambda$ such that its initial witness assignment $\net{\lambda_\star}AB$ unifying-coalesces.
-It \defn{sequentializes} to $\Pi$ if the initial labelling $\net{\lambda^\star_\star}AB$ reduces in $(\ucoal)$ to $\net{\{\link[\varnothing]AB^\Pi\}}AB$.
+% --------------------------------------------------
+
+\subsection{(De-)Sequentialization}
+
+The two coalescence relations $(\scoal)$ and $(\ucoal)$ are small-step rewrite relations. We will characterize both as inductive, big-step relations $(\sdown)$ and $(\udown)$. Judgements 
+\[
+	\sdn\lambda AB
+	\qquad\text{and}\qquad
+	\udn\lambda AB
+\]
+will mean that $\net\lambda AB$ strict-coalesces respectively unifying-coalesces to $\net{\link AB}AB$.
+The relations $(\sdown)$ and $(\udown)$ are defined by the derivation rules given in Figure~\ref{fig:derivations}, where we overload the names of the corresponding rules of $(\scoal)$ and $(\sdown)$, and of $(\ucoal)$ and $(\udown)$.
+
+\begin{proposition}
+A pre-net $\net\lambda AB$ is a witness net if and only if $\sdn\lambda[]AB$.
+\end{proposition}
+
+%\begin{proof}[Proof sketch]
+%
+%\end{proof}
+
+\begin{proposition}
+A pre-net $\net\lambda AB$ is a unification net if and only if $\udn\lambda[]AB$.
+\end{proposition}
+
+We will use both derivation systems to mediate the translation from sequent proofs to proof nets (\defn{de-sequentialization}) and from proof nets to proofs (\defn{sequentialization}).
+%Firstly, we formalize the isomorphism between sequent proofs and $(\sdown)$-derivations.
+
+\begin{definition}[Witness net (de-)sequentialization]
+The relation $\Pi\QU\Sigma$ between sequent proofs $\Pi$ and $(\sdown)$-derivations $\Sigma$ is generated by relating $(\qrr1)$ to $(\srr1)$ and $(\qrr\alpha)$-rules to $(\srr\alpha)$-rules for $\alpha\in\{\,\+_i\,,\,\*\,,\,\exists\,,\,\forall\,\}$.
+If $\Pi\QU\Sigma$ and $\Sigma$ derives $\sdn\lambda[]AB$ then $\Pi$ \defn{de-sequentializes} to the witness net $\net\lambda AB$ and $\net\lambda AB$ \defn{sequentializes} to $\Pi$.
 \end{definition}
 
-\begin{theorem}
-For any \all1 proof $\Pi$:
-\begin{enumerate}
-\item the de-sequentialization $[\Pi]$ is a witness net that sequentializes to $\Pi$. 
-\item the clean de-sequentialization $\floor\Pi$ is a unification net that sequentializes to a proof $\Phi$ such that $\Pi=\Phi\rho$ for some witness map $\rho$ (where universal variables may be captured).
-\end{enumerate}
-\end{theorem}
-
-\begin{proof}
-By induction on $\prf\Pi AB$, if $\lambda=[\Pi]_{A',B'}^\sigma$ where $A'\sigma=A$ and $B'\sigma=B$, then $\net{\lambda^\star}AB$ reduces in $(\scoal)$ to $\net{\{\link{A'}{B'}^\Pi\}}AB$.
-Statement 1.\ is the specific case $\sigma=\varnothing$.
-%
-% Technical note: need to assume $\sigma$ contains no universally quantified variables in $A$ or $B$. 
-%
-For the second statement, by induction
-
- on $\prf\Pi AB$, if $\lambda=\floor{\deseq\Pi{A'}{B'}}$ where $A'\sigma=A$ and $B'\sigma=B$, then $\net{\lambda^\star_\star}AB$ reduces in $(\ucoal)$ to $\net{\{\link{A'}{B'}\}}{}{}$
-\end{proof}
-
-For two axiom linkings $\lambda$ and $\kappa$,
-
-\begin{lemma}
-If $\net\lambda AB$ with axiom linking $\lambda$ unifying-coalesces to $\net{\{\link{A'}{B'}\}}AB$ then $\net{\floor\lambda_\star}AB$ unifying-coalesces to $\net{\{\link[\rho]{A'}{B'}\}}AB$ with $\rho\gen\sigma$.
-\end{lemma}
-
-% --------------------------------------------------
-
-\subsection{Geometric correctness}
-
-%\end{document}
+\begin{proposition}
+The relation $(\QU)$ is an isomorphism.
+\end{proposition}
+
+\begin{figure}
+\[
+\begin{array}{@{}l@{\qquad}c@{\qquad}c@{\qquad}r@{}}
+& \textbf{Strict} & \textbf{Unifying}
+\\ \\
+	(\srr1)
+&	\vc{\infer[\!\!\scriptstyle{Q\sigma=\dual R\sigma}]{\sdn{\link QR}QR}{}}
+&	\vc{\infer[\!\!\scriptstyle{\sigma\,=\,\sigma(Q,R)}]{\udn{\link[]QR}QR}{}}
+&	(\urr1)
+\\ \\
+	(\srr+i)
+&	\vc{\infer{\sdn\lambda A{B_0\+B_1}}{\sdn\lambda A{B_i}}}
+&	\vc{\infer{\udn\lambda A{B_0\+B_1}}{\udn\lambda A{B_i}}}
+&	(\urr+i)
+\\ \\
+	(\srr*)
+&	\vc{\infer{\sdn{\lambda\cup\kappa}A{B\*C}}{\sdn\lambda AB && \sdn\kappa AC}}
+&	\vc{\infer[\!\!\scriptstyle{\sigma\,\coh\,\tau}\vphantom)]{\udn{\lambda\cup\kappa}[\sigma\join\tau]A{B\*C}}{\udn\lambda[\sigma]AB && \udn\kappa[\tau]AC}}
+&	(\urr*)
+\\ \\
+	(\srr?)
+&	\vc{\infer[\!\!\scriptstyle{\sigma(x)\,\neq\,\bot}]{\sdn\lambda[\sigma\!\minus\!x]A{\exists x.B}}{\sdn\lambda AB}}
+&	\vc{\infer{\udn\lambda[\sigma\!\minus\!x]A{\exists x.B}}{\udn\lambda AB}}
+&	(\urr?)
+\\ \\
+	(\srr!)
+&	\vc{\infer[\!\!\scriptstyle{a\,\notin\,\sigma}]{\sdn\lambda A{\forall a.B}}{\sdn\lambda AB}}
+&	\vc{\infer[\!\!\scriptstyle{a\,\notin\,\sigma}]{\udn\lambda A{\forall a.B}}{\udn\lambda AB}}
+&	(\urr!)
+\end{array}
+\]
+\caption{Derivation rules for (de-)sequentialization}
+\label{fig:derivations}
+\end{figure}
+
+\end{document}
 
@@
 A linking or pre-net is \defn{strict} if all its links are.
+
+ We write $\floor\lambda$ respectively $\floor{\net\lambda AB}$ for the clean version of a linking or pre-net, which forgets the witness map for each link.
+%
+
+\begin{definition}
+The \defn{de-sequentialization} $[\Pi]$ of a sequent proof $\prf\Pi AB$ is the pre-net $\net{\deseq[\varnothing]\Pi AB} AB$ where $\deseq-AB$ is defined as follows.
+%
+\[
+\begin{array}{ccl}
+	\Deseq{\infer{\seq P{\dual P}}{}}QR &=& \{\link QR\}
+\\ \\
+	\Deseq{\infer {\seq A {B_0\+B_1}} {\deduce [\rule{0pt}{1pt}] {\seq A{B_i}} \Pi }}
+	  {A'}{B_0'\+B'_1} 
+	&=& \Deseq{\deduce[\rule{0pt}{1pt}]{\seq A{B_i}}\Pi}{A'}{B_i'}
+\\ \\
+	\Deseq{\infer{\seq A{B\*C}}{
+	  \deduce[\rule{0pt}{1pt}]{\seq AB}\Pi 
+	  && 
+	  \deduce[\rule{0pt}{1pt}]{\seq AC}\Sigma}}{A'}{B'\*C'}
+	&=& \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AB}\Pi}{A'}{B'}
+	  \cup
+	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AC}\Sigma}{A'}{C'}
+\\ \\
+	\Deseq{\infer{\seq A{\exists x.B}}{\deduce[\rule{0pt}{1pt}]{\seq A{B[t/x]}}\Pi}}
+	  {A'}{\exists x.B'}
+	&=&
+	 \Deseq[{\sigma[x\mapsto t]}]{\deduce[\rule{0pt}{1pt}]{\seq A{B[t/x]}}\Pi}
+	  {A'}{B'}
+\\ \\
+	\Deseq{\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]
+	  {\seq A{\forall a.B}}{\deduce[\rule{0pt}{1pt}]{\seq AB}\Pi}}{A'}{\forall a.B'}
+	&=&
+	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AB}\Pi}{A'}{B'}
+\end{array}
+\]
+The \defn{clean} de-sequentialization $\floor\Pi$ of $\prf\Pi AB$ is $\floor{[\Pi]}$.
+\end{definition}
+
+Observe that the pre-net $[\Pi]$ has a strict axiom linking and $\floor\Pi$ a clean axiom linking.
+
+% --------------------------------------------------
+
+\subsection{Geometric correctness}
 
@@
 	\net{\{\link AB,\link[\tau]AC\}}A{B\*C}
-& ~\scoal~ 
-	\net{\{\link[\sigma\join\tau]A{B\*C}\}}A{B\*C}\quad\text{if }\sigma\coh\tau
+& ~\coal~ 
+	\net{\{\link[\sigma\join\tau]A{B\*C}\}}A{B\*C}\quad\text{if }\sigma\comp\tau
 \tag{$\*$}
@@
 \end{proof}
-
-\end{document}
 
@@
 \end{description}
-
-The two coalescence relations $(\scoal)$ and $(\ucoal)$ are small-step rewrite relations. We will characterize both as inductive, big-step relations $(\sdown)$ and $(\udown)$. Judgements 
-\[
-	\sdn\lambda AB
-	\qquad\text{and}\qquad
-	\udn\lambda AB
-\]
-will mean that $\net\lambda AB$ strict-coalesces respectively unifying-coalesces to $\net{\link AB}AB$.
-The relations $(\sdown)$ and $(\udown)$ are defined by the derivation rules given in Figure~\ref{fig:derivations}, where we overload the names of the corresponding rules of $(\scoal)$ and $(\sdown)$, and of $(\ucoal)$ and $(\udown)$.
-
-\begin{proposition}
-A pre-net $\net\lambda AB$ is a witness net if and only if $\sdn\lambda[]AB$.
-\end{proposition}
-
-%\begin{proof}[Proof sketch]
-%
-%\end{proof}
-
-\begin{proposition}
-A pre-net $\net\lambda AB$ is a unification net if and only if $\udn\lambda[]AB$.
-\end{proposition}
-
-We will use both derivation systems to mediate the translation from sequent proofs to proof nets (\defn{de-sequentialization}) and from proof nets to proofs (\defn{sequentialization}).
-%Firstly, we formalize the isomorphism between sequent proofs and $(\sdown)$-derivations.
-
-\begin{definition}[Witness net (de-)sequentialization]
-The relation $\Pi\QU\Sigma$ between sequent proofs $\Pi$ and $(\sdown)$-derivations $\Sigma$ is generated by relating $(\qrr1)$ to $(\srr1)$ and $(\qrr\alpha)$-rules to $(\srr\alpha)$-rules for $\alpha\in\{\,\+_i\,,\,\*\,,\,\exists\,,\,\forall\,\}$.
-If $\Pi\QU\Sigma$ and $\Sigma$ derives $\sdn\lambda[]AB$ then $\Pi$ \defn{de-sequentializes} to the witness net $\net\lambda AB$ and $\net\lambda AB$ \defn{sequentializes} to $\Pi$.
-\end{definition}
-
-\begin{proposition}
-The relation $(\QU)$ is an isomorphism.
-\end{proposition}
-
-\begin{figure}
-\[
-\begin{array}{@{}l@{\qquad}c@{\qquad}c@{\qquad}r@{}}
-& \textbf{Strict} & \textbf{Unifying}
-\\ \\
-	(\srr1)
-&	\vc{\infer[\!\!\scriptstyle{Q\sigma=\dual R\sigma}]{\sdn{\link QR}QR}{}}
-&	\vc{\infer[\!\!\scriptstyle{\sigma\,=\,\sigma(Q,R)}]{\udn{\link[]QR}QR}{}}
-&	(\urr1)
-\\ \\
-	(\srr+i)
-&	\vc{\infer{\sdn\lambda A{B_0\+B_1}}{\sdn\lambda A{B_i}}}
-&	\vc{\infer{\udn\lambda A{B_0\+B_1}}{\udn\lambda A{B_i}}}
-&	(\urr+i)
-\\ \\
-	(\srr*)
-&	\vc{\infer{\sdn{\lambda\cup\kappa}A{B\*C}}{\sdn\lambda AB && \sdn\kappa AC}}
-&	\vc{\infer[\!\!\scriptstyle{\sigma\,\coh\,\tau}\vphantom)]{\udn{\lambda\cup\kappa}[\sigma\join\tau]A{B\*C}}{\udn\lambda[\sigma]AB && \udn\kappa[\tau]AC}}
-&	(\urr*)
-\\ \\
-	(\srr?)
-&	\vc{\infer[\!\!\scriptstyle{\sigma(x)\,\neq\,\bot}]{\sdn\lambda[\sigma\!\minus\!x]A{\exists x.B}}{\sdn\lambda AB}}
-&	\vc{\infer{\udn\lambda[\sigma\!\minus\!x]A{\exists x.B}}{\udn\lambda AB}}
-&	(\urr?)
-\\ \\
-	(\srr!)
-&	\vc{\infer[\!\!\scriptstyle{a\,\notin\,\sigma}]{\sdn\lambda A{\forall a.B}}{\sdn\lambda AB}}
-&	\vc{\infer[\!\!\scriptstyle{a\,\notin\,\sigma}]{\udn\lambda A{\forall a.B}}{\udn\lambda AB}}
-&	(\urr!)
-\end{array}
-\]
-\caption{Derivation rules for (de-)sequentialization}
-\label{fig:derivations}
-\end{figure}

### 2018-03-23 Archive/ALL1-backup-8.tex
some cleanup

--- 2017-12-19 ALL1-backup-7.tex
@@
 \newcommand\subs[1]{\textsc{sub}(#1)}
+\newcommand\poss[1]{\textsc{pos}(#1)}
 \newcommand\dom[1]{\textsc{dom}(#1)}
@@
 A \defn{witness map} $\sigma\colon \varE \rightharpoonup \terms$ is a substitution map which assigns terms to existential variables, given as a (finite) partial function.
+Its \defn{domain} $\dom(\sigma)$ are those variables for which it is defined.
 The \defn{empty} witness map $\varnothing$ is the everywhere undefined partial function, and the map $\sigma[t/x]$ substitutes $t$ for $x$ and is as $\sigma$ everywhere else.
@@
 The \defn{composition} of two maps is written $\sigma\tau$, where $A(\sigma\tau)=(A\sigma)\tau$.
-We define the following further operations on witness maps.
-
-\[
-\begin{tabular}{@{}lp{.75\textwidth}@{}}
-	$\sigma\gen\tau$
-&
-	A witness map is \defn{more general} than another, 
-	$\sigma\gen\tau$, if there is a map $\rho$ such that 
-	$\sigma\rho=\tau$.
-\\[5pt]	
-	$\sigma\coh\tau$
-&
-	Two witness maps are \defn{coherent}, $\sigma\coh\tau$,
-	if there is a map $\rho$ such that $\sigma\rho=\tau\rho$.
-\\[5pt]
-	$\sigma\join\tau$
-&
-	The \defn{join} of two witness maps $\sigma\join\tau$ is defined
-	if they are coherent, and is the least map $\rho$ such that
-	$\sigma\gen\rho$ and $\tau\gen\rho$.
-\end{tabular}%
-\]
 
 A \defn{witness linking} $\lambda_\Sigma$ is a linking $\lambda$ with a \defn{witness labelling} $\Sigma\colon\lambda\to \varE\rightharpoonup\terms$ that assigns each link $(C,D)$ a witness map.
-We may use and define $\lambda_\Sigma$ as a set of \defn{witness links} $\link CD$, which indicates the link $(C,D)$ in $\lambda$ where $\Sigma(C,D)=\sigma$.
+We may use and define $\lambda_\Sigma$ as a set of \defn{witness links} $\link CD$, where $(C,D)$ in $\lambda$ and $\Sigma(C,D)=\sigma$.
 
 \begin{definition}
-A \defn{witness pre-net} $\net{\lambda_\Sigma}AB$ is a pre-net with a witness linking $\lambda_\Sigma$.
+A \defn{witness pre-net} $\net{\lambda_\Sigma}AB$ is a sequent $\seq AB$ with a witness linking $\lambda_\Sigma$.
+%
+%\begin{description}
+%	\item[Exact coverage]
+%The domain of $\sigma$ is exactly the variables existentially quantified in $\seq AB$ that will be bound in $C$ and $D$, if they occur:
+%\[
+%	\dom\sigma = \{\,x \mid C < \exists x.X \leq A\,\}
+%			\cup \{\,y \mid D < \exists y.Y \leq B\,\}~.
+%\]
+%
+%	\item[Eigenvariables not free]
+%A universal variable $a\in\varA$ quantified in $C$ or $D$ may not occur free in the range of $\sigma$, $a\notin\sigma$.
+%
+%	\item[Freshness]
+%Existential variables in the range of $\sigma$ are fresh, i.e.\ distinct from any existentially quantified variable in $\seq AB$.
+%\end{description}
 \end{definition}
@@
 We assume the existential variables occurring in the range of $\Sigma$ to be fresh, i.e.\ distinct from any existentially quantified variable in $\seq AB$.
-We abbreviate by $a\in \sigma$ the statement that a (universal) variable $a$ occurs free in the range of $\sigma$, i.e.\ that $a\in\fv(\sigma(x))$ for some $x$.
+We abbreviate by $a\in \sigma$ the statement that a variable $a$ occurs free in the range of $\sigma$, i.e.\ that $a\in\fv(\sigma(x))$ for some $x$.
 
@@
 \]
+
+\begin{definition}
+An \all1 \defn{witnessing proof net} or \defn{witness net} is a witness pre-net $\net{\lambda_\Sigma}AB$, with $\lambda_\Sigma$ an axiom linking, that strict-coalesces.
+It \defn{sequentializes} to a proof $\pi$ if its initial labelling $\net{\lambda_\Sigma^\star}AB$ reduces in $(\scoal)$ to $\net{\{\link[\varnothing]AB^\pi\}}AB$.
+\end{definition}
+
+Two useful properties of witness nets are preserved over a coalescence sequence, captured in the lemma below.
+The first property is formulated the way it is to account for vacuous quantifiers, for which no actual variable occurs in $C$ or $D$, as well as formulas such as $\exists x.C\+C'$ where $x$ occurs in $C'$ but not $C$, where we still would like an explicit witness for $x$ on a link $\link CD$.
+
+\begin{lemma}
+Every pre-net on a coalescence path $\net{\lambda_\Sigma}AB \scoal^* \net{\{\link[\varnothing]AB^\pi\}}AB$ from a witness net satisfies the following properties. 
+\begin{description}
+	\item[Eigenvariables not free]
+For any link $\link CD$, a universal variable $a\in\varA$ quantified in $C$ or $D$ does not occur free in the range of $\sigma$, $a\notin\sigma$.
+
+	\item[Exact coverage]
+For any link $\link CD$, the domain of $\sigma$ is exactly the variables existentially quantified in $\seq AB$ that will be bound in $C$ and $D$, if they occur:
+\[
+	\dom\sigma = \{\,x \mid C < \exists x.X \leq A\,\}
+			\cup \{\,y \mid D < \exists y.Y \leq B\,\}~.
+\]
+\end{description}
+\end{lemma}
+
+\begin{proof}
+By induction on the coalescence path, going forward from $\net{\lambda_\Sigma}AB$ for the first property, and working backward from $\net{\{\link[\varnothing]AB^\pi\}}AB$ for the second.
+\end{proof}
+
+\begin{theorem}
+For any \all1 proof $\pi$, the de-sequentialization $[\pi]$ is a witness net that sequentializes to $\pi$. 
+\end{theorem}
+
+\begin{proof}
+It follows by induction on $\prf\pi AB$ that if $\lambda_\Sigma=[\pi]_{A',B'}^\sigma$ where $A'\sigma=A$ and $B'\sigma=B$, then $\net{\lambda^\star_\Sigma}AB$ reduces in $(\scoal)$ to $\net{\{\link{A'}{B'}^\pi\}}AB$.
+The statement is the specific case $\sigma=\varnothing$.
+\end{proof}
+
+% --------------------------------------------------
+
+\subsection{Geometric correctness}
+
+A formula $\exists x.A$ has two natural immediate descendants: one \emph{syntactic}, its subformula $A$, and one \emph{semantic}, the premise $A[t/x]$ for its introduction rule, for any given $t$.
+We will define the latter as a tree-order generated from a formula $A$: the \defn{positions} of $A$ are its subformulas under substitution,
+\[
+	\poss A~=~\{~B'\sigma~\mid~A=A'\sigma~,~B'\sub A'~,~\sigma\in\varE\rightharpoonup\terms~\}
+\]
+
+The notion of a \defn{slice} is central to additive proof theory.
+{\color{red}[TO DO: say what it is]} In the propositional case, slices are readily defined as sets of subformulas.
+Here, in the first-order case, we will work analogously on the set of positions.
+
+The immediate problem is that the number of positions immediately below $\exists x.B$ is infinite, as there is one immediate descendant $B[t/x]$ for every term $t$.
+We reduce it to finite width by restricting a slice to just the terms assigned to $x$ by the witness labelling $\Sigma$ in a pre-net $\net{\lambda_\Sigma}AB$.
+
+For a witness linking $\lambda_\Sigma$ and an existential variable $x$, write $\Sigma(x)\subseteq\terms$ for the \defn{witness set} of $x$, which collects the terms assigned to $x$ by the witness maps in $\Sigma$ for every link in $\lambda$:
+\[
+	\Sigma(x) = \{~\sigma(x)~\mid~\link CD\in\lambda_\Sigma~\}~.
+\]
+%
+Given a witness linking $\lambda_\Sigma$, a \defn{slice} $S$ of a formula $A$ is a set of positions of $A$ given by: $S=\{A\}\cup S'$ where $S'$ is as follows.
+
+\begin{itemize}
+	\item
+\makebox[70pt][l]{If $A = P$}			then $S'=\varnothing$.
+	\item
+\makebox[70pt][l]{If $A = B\+C$} 		then $S'=S_B\uplus S_C$ where $S_B$ is a slice of $B$ and $S_C$ a slice of $C$.
+	\item
+\makebox[70pt][l]{If $A = B\*C$}		then $S'$ is a slice of $B$ or a slice of $C$.
+	\item
+\makebox[70pt][l]{If $A = \exists x.B$}	then $S'=\uplus_{t\,\in\,\Sigma(x)}S_t$ where each $S_t$ is a slice of $B[t/x]$.
+	\item
+\makebox[70pt][l]{If $A = \forall a.B$}	then $S'$ is a slice of $B$.
+\end{itemize}
+% Note: careful with multiple identical terms t! It should always be safe to have more...
+
+\noindent
+A \defn{slice} of a sequent $\seq AB$ is the product $S_A\times S_B$ of a slice of each formula.
+A \defn{slice} of a witness pre-net $\net{\lambda_\Sigma} AB$ over a slice $S_A\times S_B$ of $\seq AB$ is the set of links
+\[
+	\{~\link CD\in \lambda_\Sigma~\mid~(C\sigma,D\sigma)\in S_A\times S_B~\}~.
+\]
+
+Within a slice, we need to ensure that the order in which quantifiers are instantiated is sound.
+That is, we need to have an analogue of the \emph{eigenvariable condition} on the $\qrr!$-rule of sequent calculus, that the quantified variable $a$ of the primary formula $\forall a.A$ does not occur free in the context.
+We will define a \defn{dependency} condition to this effect.
+
+Rather than define the condition on slices, since we will require that each slice contains a single link, we will define it for individual links.
+It is expected that for a more involved logic that includes multiplicative connectives, a dependency condition such as the below one needs to be applied to a slice instead.
+
+In a pre-net $\net{\lambda_\Sigma}AB$, let the \defn{column} of a link $\link CD$ be the set of positions of $A\sigma$ and $B\sigma$ that have $C\sigma$ respectively $D\sigma$ as a descendant,
+\[
+	\{~X~\mid~C\sigma\sub X\sub A\sigma~\}\cup\{~Y~\mid~D\sigma\leq Y\leq B\sigma~\}~,
+\]
+with an order $(\dep)$ given by: $X\dep Y$ if $X\leq Y$, and $\exists x.X\dep \forall a.Y$ if $a\in\fv(\sigma(x))$.
+We will have $X\dep\forall a.Y$ whenever $a$ is free in $X$, plus when $X$ occurs under a vacuous existential quantifier $\exists x$ with $a\in\fv(\sigma(x))$.
+
+\begin{definition}
+A witness pre-net is \defn{correct} if it is
+\begin{enumerate}
+\item \defn{slice-correct}: every slice is a singleton, and
+\item \defn{dependency-correct}: every column is a partial order (i.e.\ is acyclic/antisymmetric).
+\end{enumerate}
+\end{definition}
+
+\begin{lemma}
+\label{lem:preservation}
+Strict coalescence preserves and reflects correctness: for a strict coalescence step $L\scoal R$, the witness pre-net $L$ is correct if and only if $R$ is.
+\end{lemma}
+
+\begin{proof}
+Let $L=\net{\lambda_\Sigma}AB$ and $R=\net{\kappa_\Xi}AB$. We will consider the four coalescence steps.
+%
+\begin{align}
+  	\net{\{\link C{D_i}\}}C{D_0{\+}D_1} 
+ &~\scoal~
+	\net{\{\link C{D_0{\+}D_1} \}}C{D_0{\+}D_1}
+\tag{$\srr+i$}
+\\	\net{\{\link C{D_0},\link C{D_1}\}}C{D_0{\*}D_1}
+ &~\scoal~ 
+	\net{\{\link C{D_0{\*}D_1}\}}C{D_0{\*}D_1}
+\tag{$\srr*$}
+\\	\net{\{\link CD\}}C{\exists x.D}
+ &~\scoal~ 
+	\net{\{\link[\sigma\minus x]C{\exists x.D}\}}C{\exists x.D}
+\tag{$\srr?$}
+\\	\net{\{\link CD\}}C{\forall a.D}
+ &~\scoal~
+	\net{\{\link C{\forall a.D}\}}C{\forall a.D}
+\tag{$\srr!$}
+\end{align}
+%
+\begin{description}
+	\item[$(\srr+i)$]
+Let $S_A$  contain $C\sigma$ and $S_B$ contain $D_0\sigma\+D_1\sigma$.
+Then $S_B$ contains also $D_0\sigma$ and $D_1\sigma$.
+If the slice of $L$ over $S_A$ and $S_B$ is $\{\link C{D_i}\}$, then that of $R$ over $S_A$ and $S_B$ is $\{\link C{D_0{\+}D_1}\}$, and vice versa.
+Since other slices are unaffected, $L$ is slice-correct if and only if $R$ is.
+For dependency-correctness, the column of $\link C{D_i}$ is that of $\link C{D_0{\+}D_1}$ plus $D_i\sigma$ itself, which is minimal in the order $\dep$.
+
+	\item[$(\srr*)$]
+Let $S_A$ contain $C\sigma$, and $S_B$ contain $D_0\sigma\+D_1\sigma$ and either $D_0\sigma$ or $D_1\sigma$.
+Then the slice of $L$ over $S_A$ and $S_B$ is $\{\link C{D_0}\}$ respectively $\{\link C{D_1}\}$ if and only if that of $R$ is $\{\link C{D_0{\*}D_1}\}$.
+Dependency-correctness is immediate, as above.
+
+	\item[$(\srr?)$]
+The witness sets $\Sigma(x)$ and $\Xi(x)$ for $L$ and $R$ need not be the same, since $L$ has $\sigma$ where $R$ has $\sigma\minus x$.
+Let $\Sigma(x)=\{t,t_1,\dots,t_n\}$ and $\Xi(x)=\{t_1,\dots,t_n\}$, where $\sigma(x)=t$.
+Let $S_A$ contain $C\sigma$.
+Let $S_B$ be a slice of $B$ for $\lambda_\Sigma$  and let $S'_B$ be a corresponding slice of $B$ for $\lambda_\Xi$, both containing $(\exists x.D)\sigma=\exists x.D(\sigma\minus x)$.
+Then $S_B$ contains $D[t/x],D[t_1/x],\dots,D[t_n/x]$ where $S'_B$ has $D[t_1/x],\dots,D[t_n/x]$.
+It follows that the slice of $L$ over $S_A$ and $S_B$ is $\{\link CD\}$ if and only if that of $R$ over $S_A$ and $S'_B$ is $\{\link[\sigma\minus x]C{\exists x.D}\}$.
+% Note that if $t=t_i$ for some $i$ then still the slice over $C$ and $D[t_i/x]$ in $L$ must be empty.
+
+The column of $\link CD$ is that of $\link[\sigma\minus x]C{\exists x.D}$ plus the formula $D\sigma$ itself.
+In addition, in the former the order $(\dep)$ is augmented with $(\exists x.D)\sigma\dep\forall a.X$ whenever $a\in\fv(\sigma(x))$.
+Since $D\sigma$ is the only element smaller than $(\exists x.D)\sigma$, this may only create a cycle in $(\dep)$ if $D=\forall b.Y$; but in that case, $b$ is not free in $\sigma$ (by the ``Eigenvariables not free'' condition on pre-nets), and so cannot create a cycle.
+It follows that $L$ is dependency-correct if and only if $R$ is.
+
+	\item[$(\srr!)$]
+Let $S_A$ contain $C\sigma$, and $S_B$ contain $\forall a.D\sigma$ and $D\sigma$.
+The slice of $L$ over $S_A$ and $S_B$ is $\{\link CD\}$ if and only if that of $R$ is $\{\link C{\forall a.D}\}$.
+Dependency-correctness is immediate by the observation that $D\sigma$ is minimal in the column of $\link CD$.
+
+\qedhere
+\end{description}
+\end{proof}
+
+\begin{lemma}
+A witness pre-net $\net{\lambda_\Sigma}AB$ is correct if and only if it strict-coalesces to $\net{\{\link{A'}{B'}\}}AB$ where $A=A'\sigma$ and $B=B'\sigma$. 
+\end{lemma}
+
+\begin{proof}
+From right to left, we proceed by induction on the coalescence path, with the end result as the base case.
+It is slice-correct: every slice of $\seq AB$ contains $(A,B)$, and since $(A,B)=(A'\sigma,B'\sigma)$ every slice of $\net{\{\link{A'}{B'}\}}AB$ is the singleton $\{\link{A'}{B'}\}$.
+It is also dependency-correct: the column of $\link{A'}{B'}$ is the set $\{A,B\}$, where $A$ and $B$ are unrelated in $(\dep)$ (note that even if one is $\exists x.C$, still $x$ is not in the domain of $\sigma$, which covers the existential variables quantified by successors of $A'$ and $B'$ but not $A'$ and $B'$ themselves).
+By Lemma~\ref{lem:preservation}, coalescence reflects correctness, so that any pre-net along the coalescence path is correct, in particular $\net{\lambda_\Sigma}AB$.
+
+From left to right, let $\net{\lambda_\Sigma}AB$ be correct.
+Let the \defn{depth} of a link $\link CD$ be the distance from $C$ and $D$ to the root of $A$ respectively $B$, given by a pair of integers $(n,m)$.
+We will demonstrate that a link at maximal depth in the product order, $(i,j)\leq(n,m)$ if and only if $i\leq n$ and $j\leq m$, may always be coalesced, unless it is the unique link $\link{A'}{B'}$ at $(0,0)$.
+By Lemma~\ref{lem:preservation} the result of this coalescence step is again correct, and it follows by induction on the decreasing depth of links that the pre-net strict-coalesces to $\net{\{\link{A'}{B'}\}}AB$.
+
+To see that a maximally deep link coalesces, first note that a link $\link C{D_i}$ where $D_i$ occurs in $D_0{\+}D_1$ may always contract, as may a link $\link CD$ where $D$ occurs in $\exists x.D$.
+This leaves the following cases:
+\begin{itemize}
+	\item $\link A{D_i}$ with $D_i$ in $D=D_0\*D_1$; without loss of generality, let $i=0$.
+A slice $S_B$ of $B$ containing $D$ also contains either $D_0$ or $D_1$.
+If the former, the corresponding slice of $\net{\lambda_\Sigma}AB$ is $\{\link A{D_0}\}$.
+
+	\item  $\link{C_i}{D_j}$ in $C_0\*C_1$ and $D_0\*D_j$
+
+\end{itemize}
+
+\end{proof}
+
+\end{document}
 
@@
 
-% --------------------------------------------------
-
-\subsection{Geometric correctness}
-
-%\end{document}
-
-A link is \defn{strict} if its domain consists of exactly the existentially quantified variables that its formulas are in scope of.
-That is, a link $\link CD$ in a pre-net $\net\lambda AB$ is strict if
-\[
-	\dom\sigma = \{\,x \mid C < \exists x.X \leq A\,\}
-			\cup \{\,y \mid D < \exists y.Y \leq B\,\}~.
-\]
-A linking or pre-net is \defn{strict} if all its links are.
-
-For a labelled linking $\lambda$ and an existential variable $x$, write $\lambda(x)\subseteq\terms$ for the \defn{witness set} of $x$, which collects the terms assigned to $x$ by the links in $\lambda$:
-\[
-	\lambda(x) = \{~t~\mid~\sigma(x) = t~,~\link AB\in\lambda~\}~.
-\]
-%
-Given a labelled linking $\lambda$, a \defn{slice} $S$ of a formula $A$ is a set of formulas given by: $S=\{A\}\cup S'$ where $S'$ is as follows; if $A$ is of the form
-%
-\begin{itemize}
-	\item
-\makebox[40pt][l]{$P$:}				$S'=\varnothing$.
-	\item
-\makebox[40pt][l]{$B\+C$:} 			$S'=S_B\cup S_C$ where $S_B$ is a slice of $B$ and $S_C$ a slice of $C$.
-	\item
-\makebox[40pt][l]{$B\*C$:}			$S'$ is a slice of $B$ or a slice of $C$.
-	\item
-\makebox[40pt][l]{$\exists x.B$:}	$S'$ is a slice of $B$ if the quantifier is vacuous, $x\notin\fv(B)$, and
-	\\[\itemsep]
-	\hspace*{40pt}					$S'=\uplus_{t\,\in\,\lambda(x)}S_t$ where each $S_t$ is a slice of $B[t/x]$ otherwise.
-	\item
-\makebox[40pt][l]{$\forall a.B$:}	$S'$ is a slice of $B$.
-\end{itemize}
-%
-A \defn{slice} of a labelled pre-net $\net\lambda AB$ is a set of links
-\[
-	\{~\link CD\in \lambda~\mid~(C\sigma,D\sigma)\in S_A\times S_B~\}
-\]
-where $S_A$ is a slice of $A$ and $S_B$ a slice of $B$.
-A labelled pre-net is \defn{correct} if every slice is a singleton.
-A coherent pre-net $\net\lambda AB$ is \defn{correct} if its initial labelling $\net{\lambda_\star}AB$ is.
-Observe that for a \emph{labelled} pre-net correctness and compatibility are independent, while a non-labelled pre-net must be coherent to be correct, since $\lambda_\star$ is otherwise not defined.
-
-\begin{definition}
-An \all1 \defn{proof net} is a correct pre-net. An \all1 \defn{labelled proof net} is a correct and coherent labelled pre-net.
-\end{definition}
-
-\begin{lemma}
-If a labelled pre-net coalesces, it is correct. 
-\end{lemma}
-
-\begin{proof}
-By induction on the coalescence path we will show that if $\net\lambda AB$ coalesces to $\net{\{\link AB\}}AB$ then $\net{\{\link[\varnothing]{A\sigma}{B\sigma}\}}{A\sigma}{B\sigma}$ is correct.
-The statement is then the special case $\sigma=\varnothing$.
-
-The result $\net{\{\link[\varnothing]{A\sigma}{B\sigma}\}}{A\sigma}{B\sigma}$ is correct: its only slice is $\{\link[\varnothing]{A\sigma}{B\sigma}\}$, since $A\sigma$ is in any slice $S_{A\sigma}$ of $A\sigma$, and $B\sigma$ is in any slice $S_{B\sigma}$ of $B\sigma$.
-
-\renewcommand{\+}{{+}}
-\renewcommand{\*}{{\times}}
-\begin{align}
-	\net{\{\link AB,\link[\tau]AC\}}A{B\*C}
-& ~\scoal~ 
-	\net{\{\link[\sigma\join\tau]A{B\*C}\}}A{B\*C}\quad\text{if }\sigma\coh\tau
-\tag{$\*$}
-\end{align}
-
-Let $\rho=\sigma\join\tau$, and assume that $\net{\{\link[\varnothing]{A\rho}{B\rho\*C\rho}\}}{A\rho}{B\rho\*C\rho}$ is correct.
-
-\end{proof}
-
-\end{document}
+We define the following further operations on witness maps.
+\[
+\begin{tabular}{@{}lp{.75\textwidth}@{}}
+	$\sigma\gen\tau$
+&
+	A witness map is \defn{more general} than another, 
+	$\sigma\gen\tau$, if there is a map $\rho$ such that 
+	$\sigma\rho=\tau$.
+\\[5pt]	
+	$\sigma\coh\tau$
+&
+	Two witness maps are \defn{coherent}, $\sigma\coh\tau$,
+	if there is a map $\rho$ such that $\sigma\rho=\tau\rho$.
+\\[5pt]
+	$\sigma\join\tau$
+&
+	The \defn{join} of two witness maps $\sigma\join\tau$ is defined
+	if they are coherent, and is the least map $\rho$ such that
+	$\sigma\gen\rho$ and $\tau\gen\rho$.
+\end{tabular}%
+\]
+
+A witness link $\link PQ$ or link $(P,Q)$ on two atomic formulas $P$ and $Q$ is an \defn{axiom} link if $P\sigma=\dual Q\sigma$, or respectively, if some $\sigma$ exists such that $P\sigma=\dual Q\sigma$.
+An \defn{axiom} (witness) linking is one consisting only of axiom links.
+Observe that in the de-sequentialization $[\pi]$ the witness linking $\deseq[\varnothing]\pi AB$ is an axiom linking.
+
+To an axiom link $(P,Q)$ we assign an \defn{initial witness map} $\sigma=\init PQ$ as the least witness map in $(\gen)$ such that $P\sigma=\dual Q\sigma$.
+In other words, $\init PQ$ is the most general unifier ($\textsc{mgu}$) of $P$ and $\dual Q$.
+An axiom linking $\lambda$ with the initial witness map assigned to each link will be written $\lambda_\star$:
+\[
+	\lambda_\star = \{~\link PQ~\mid~(P,Q)\in\lambda~,~\sigma=\init PQ~\}~.
+\]
+For two witness labellings $\Sigma$ and $\Xi$ on the same linking $\lambda$, one is \defn{more general} than the other, $\Sigma\gen\Xi$, if $\Sigma(C,D)\gen\Xi(C,D)$ for every link $(C,D)\in\lambda$.
+We extend this to the linkings themselves: $\lambda_\Sigma\gen\lambda_\Xi$.
+Observe that for an axiom linking $\lambda$, the initial linking $\lambda_\star$ is the most general among the witness linkings $\lambda_\Sigma$ for any $\Sigma$.
 
@@
     	\formula[y=1]{\exists x.B}
-    	\Vlink[red,label={~$\scriptstyle{\sigma\!\minus\!x}$}]{1,1}
+    	\Vlink[red,label={~$\scriptstyle{\sigma\minus x}$}]{1,1}
     \end{tikzpicture}}
@@
 	(\srr?)
-&	\vc{\infer[\!\!\scriptstyle{\sigma(x)\,\neq\,\bot}]{\sdn\lambda[\sigma\!\minus\!x]A{\exists x.B}}{\sdn\lambda AB}}
-&	\vc{\infer{\udn\lambda[\sigma\!\minus\!x]A{\exists x.B}}{\udn\lambda AB}}
+&	\vc{\infer[\!\!\scriptstyle{\sigma(x)\,\neq\,\bot}]{\sdn\lambda[\sigma\minus x]A{\exists x.B}}{\sdn\lambda AB}}
+&	\vc{\infer{\udn\lambda[\sigma\minus x]A{\exists x.B}}{\udn\lambda AB}}
 &	(\urr?)

### 2018-04-17 ALL1.tex
CSL revision

@@
-\documentclass[UKenglish]{lipics-v2016}
+\documentclass[UKenglish]{lipics-v2018}
 
@@
 \newcommand\floor[1]{\lfloor#1\rfloor}
+
+% ===== Check mark symbols
+\usepackage{pifont}
+	\newcommand\xmark{{\red\ding{54}}}
+	\newcommand\vmark{{\color{green}\ding{51}}}
 
@@
 
-\author[1]{Willem B.\ Heijltjes}
-\author[2]{Dominic J.D.\ Hughes}
-\author[3]{Lutz Stra\ss burger}
-\affil[1]{University of Bath, United Kingdom\\
-  \url{http://willem.heijltj.es/}} %%\texttt{w.b.heijltjes@bath.ac.uk}}
-\affil[2]{Logic Group, UC Berkeley, USA\\
-  \url{http://boole.stanford.edu/~dominic/}} %%\texttt{dominich@theory.stanford.edu}}
-\affil[3]{Inria Saclay \&\ LIX/\'Ecole Polytechnique, Palaiseau, France\\
-  \url{http://www.lix.polytechnique.fr/Labo/Lutz.Strassburger/}} %%\texttt{lutz.strassburger@inria.fr}}
+\author
+ {Willem B.\ Heijltjes}
+ {University of Bath, United Kingdom}
+ {http://willem.heijltj.es/} %{w.b.heijltjes@bath.ac.uk}
+ {}
+ {}
+\author
+ {Dominic J.D.\ Hughes}
+ {Logic Group, UC Berkeley, USA}
+ {http://boole.stanford.edu/\textasciitilde dominic/} %{dominich@theory.stanford.edu}
+ {}
+ {} 
+\author
+ {Lutz Stra\ss burger}
+ {Inria Saclay \&\ LIX/\'Ecole Polytechnique, Palaiseau, France}
+ {http://www.lix.polytechnique.fr/Labo/Lutz.Strassburger/} %{lutz.strassburger@inria.fr}
+ {}
+ {}
+
 \authorrunning{W.B.\ Heijltjes, D.J.D.\ Hughes, and L.\ Stra\ss burger}
@@
 \subjclass{F.4.1: Mathematical logic--Proof theory}
-\keywords{Linear logic, First-order logic, Proof nets}
+\keywords{Linear logic, First-order logic, Proof nets, Herbrand's Theorem}
 
@@
 \begin{abstract}
-We extend proof nets for additive linear logic with first-order quantification.
+We present canonical proof nets for first-order additive linear logic, the fragment of linear logic with sum, product, and first-order universal and existential quantification.
 
@@
 
-Witness nets are canonical for first-order additive sequent calculus. Unification nets in addition factor out any inessential choice for existential witnesses. 
-Both notions of proof net are defined through coalescence (the additive version of multiplicative contractibility), and for witness nets a geometric correctness criterion is provided.
+Witness nets are canonical for first-order additive sequent calculus.
+Unification nets in addition factor out any inessential choice for existential witnesses.
+Both notions of proof net are defined through coalescence, the additive version of multiplicative contractibility, and for witness nets a geometric correctness criterion is provided.
 Both feature a global composition operation.
@@
 
-%Proof nets aim to be canonical representations of proofs. As graphs, they abstract away from the rule commutations of the sequent calculus. 
-%
-%In the study of \emph{proof nets} \cite{Girard-1987}, canonical graphical representations of proofs, the additive fragment of linear logic provides several interesting challenges.
-At the propositional level, the challenge is to capture the merging of the contexts $\Gamma$ in the additive product rule:
-%\[
-%	\vc{\infer[\Qrr*]{\seq\Gamma{A\*B}}{\seq\Gamma A & \seq\Gamma B}}~.
-%\]
-%One approach, perfect for the multiplicative fragment, is to create proof nets from sequent proofs by separating rules from their context: each sequent rule becomes a node in the graph, connected only to the primary formulas of the rule, in this case $A$, $B$, and $A\*B$.
-The benefit is a direct interpretation from sequent calculus;
-
-Additive linear logic $(\all)$ is the logic of product $(\*)$ and sum $(\+)$.
-Proofs, over a sequent $A\vdash B$ or, here, $\seq{\dual A}B$, are built from the canonical morphisms: projections, injections, and diagonals.
-These are captured naturally in \emph{proof nets} \cite{Girard-1987,Hughes-vanGlabbeek-2005}, which consist of a set of \emph{links} between subformulas in $\dual A$ and in $B$, satisfying a simple geometric correctness condition.
-\[\hspace*{9ex}% spacing hack to achieve central horizontal alignment
-\begin{array}{c@{\qquad\qquad}c@{\qquad\qquad}c@{\qquad\qquad}c}
-	\begin{tikzpicture}[net]
-		\formula[y=1.2]{{\dual a}}
+Additive linear logic $(\all)$ is the logic of product $(\*)$, sum $(\+)$, and their canonical morphisms: projections, injections, and diagonals.
+It is naturally captured in \defn{proof nets} \cite{Girard-1987,Hughes-vanGlabbeek-2005}, which describe a morphism $A\to B$ by a sequent $\seq{\dual A}B$ plus a \defn{linking}, a relation between the propositional atoms of $\dual A$ and those of $B$.
+%
+Additive proof nets are \defn{canonical}: they factor out the permutations of sequent calculus, and correspond 1--1 to morphisms of the free category.
+%
+%Additive linear logic $(\all)$ is the logic of product $(\*)$, sum $(\+)$, and their canonical morphisms: projections, injections, and diagonals.
+It is naturally captured in \defn{proof nets} \cite{Girard-1987,Hughes-vanGlabbeek-2005}, which describe a morphism $A\mathbin{\shortrightarrow}B$ by a sequent $\seq{\dual A}B$ plus a \defn{linking}, a relation between subformulas in $\dual A$ and in $B$.
+Proof nets are \defn{canonical}, factoring out the permutations of sequent calculus.
+%
+%Additive linear logic $(\all)$ is the logic of product $(\*)$ and sum $(\+)$.
+Proofs, over a two-sided sequent $A\vdash B$ or, here, a one-sided sequent $\seq{\dual A}B$, are built from the canonical morphisms: projections, injections, and diagonals.
+These are captured naturally in \emph{proof nets} \cite{Girard-1987,Hughes-vanGlabbeek-2005}, which consist of a set of \emph{links} between subformulas in $\dual A$ and in $B$, as illustrated below left.
+\[
+%\hspace*{9ex}% spacing hack to achieve central horizontal alignment
+\hspace*{-\parindent}%
+\hspace*{\fill}%
+% Behold my better spacing hack to achieve central horizontal alignment :)
+\begin{array}{c@{\qquad\qquad}c}
+	\begin{tikzpicture}[net]
+		\formula[y=1]{{\dual a}}
 		\formula[y=0]{a\*a}
@@
 	\begin{tikzpicture}[net]
-		\formula[y=1.2]{{\dual a}}
+		\formula[y=1]{{\dual a}}
 		\formula[y=0]{a\+b}
@@
 	\end{tikzpicture}
-&
-	\begin{tikzpicture}[net]
-		\formula[y=1.2]{{\dual a}\+{\dual b}}
+\\
+	\text{\small diagonal}
+&	\text{\small injection}	
+\\ \\ \\[-10pt]
+	\begin{tikzpicture}[net]
+		\formula[y=1]{{\dual a}\+{\dual b}}
 		\formula[y=0]{b\*a}
@@
 	\begin{tikzpicture}[net]
-		\formula[y=1.2]{*{\phantom(}{\dual a}*{\phantom)}
+		\formula[y=1]{*{\phantom(}{\dual a}*{\phantom)}
 		 {{\+}}*({\dual b}*{\phantom)}
@@
 \\
-	\text{\small diagonal}
-&	\text{\small injection}
-&	\text{\small symmetry}
+	\text{\small symmetry}
 &	\text{\small associativity}
 \end{array}
-\]
-%
-The logic is combinatorially rich, yet well-behaved and tractable: proof search \cite{Galmiche-Marion-1995,Galmiche-2000} and proof net correctness \cite{Heijltjes-Hughes-2015} are linear in $|A|\times|B|$ (with $|A|$ the size of the syntax tree of $A$); proof nets remain canonical and equally tractable when extended with the two units \cite{Heijltjes-2011,Heijltjes-Hughes-2015}; and the first-order case is merely NP-complete \cite{Heijltjes-Hughes-2015}.
-
-At the same time, the ubiquity of its main operations, product and sum, mean the ideas and results it garners are widely applicable.
-It serves as a microcosmos for important ideas and observations: it fostered the \emph{connections method} of proof search \cite{Galmiche-2000}; it demonstrated the \emph{Blass problem} \cite{Abramsky-2003} of game semantics, that sequential strategies do not in general have associative composition; and it is at the root of the study of fixed points in linear logic \cite{Santocanale-2002a}.
-The logic describes two-way communication~\cite{Cockett-Santocanale-2009}, and is a core part of \emph{session types}~\cite{Honda-1993}.
-
-{\all} is of course part of {\mall} (multiplicative-additive linear logic), and its lessons are clearly visible in the second author's canonical proof nets \cite{Hughes-vanGlabbeek-2005} for {\mall}, as well as the first and second author's locally canonical \emph{conflict nets}~\cite{Hughes-Heijltjes-2016}.
-Its proof nets also appear as the \emph{skew fibrations} in the second author's \emph{combinatorial proofs} for classical logic~\cite{Hughes-2006-proofs}, and in the third author's study of the \emph{medial rule} for classical logic~\cite{str:RTA07}.
-To prepare the ground for the cut elimination of first-order \emph{combinatorial proofs} is one motivation for the current presentation.
-
-We present proof nets for first-order additive linear logic (\all1). The main content of first-order proof, and our central challenge, is the \emph{witness assignment} to existential quantifiers. 
-%
-The standard approach to evaluate a formula $\exists x.A$ is by a substitution $A[t/x]$, which destroys the subformula $A$.%
-%
-\footnote{Given $A[t/x]$ and $t$, it is not possible to unambiguously recover $A$, which may contain other occurrences of $t$ not originating in the substitution $[t/x]$.}
-%
-But the current, successful formulation of additive proof nets, as a set of links over a two-formula sequent, requires subformulas to remain intact.
-%
-Moreover, the same quantification $\exists x.A$ may occur in different \emph{slices} (branches of a proof above a product), with different witnesses, as below.
-But the \emph{formulas + links} design has only one instance of $\exists x.A$.
-\[\hspace*{26ex}% spacing hack to achieve central horizontal alignment
-\vc{
-	\infer[\Qrr*]{\Seq{\exists x.A}{B\*C}}{
-	 \infer[\Qrr?s]{\Seq{\exists x.A}B}{\Seq{A[s/x]}B}
+\qquad\qquad\qquad
+\begin{array}{c}
+    \vc{\begin{tikzpicture}[net]
+        \formula[y=2.5]{{\dual b}*\+{\dual a}}
+        \formula[y=1.5]{a*\**(b*\+b*)}
+            \Vlink[red]{1,2}
+            \Vlink[red]{2,1}
+        \formula[y=1]{{\dual a}*\+*({\dual b}*\*{\dual b}*)}
+        \formula[y=0]{b*\*b}
+            \Vlink[blue]{[-1]2,[-1]1}
+            \Vlink[blue]{[1]2,[-1]2}
+            \Vlink[blue]{[-1]3,[1]1}
+            \Vlink[blue]{[1]3,[1]2}
+    \end{tikzpicture}}
+\quad\Rightarrow\quad
+    \vc{\begin{tikzpicture}[net]
+        \formula[y=2.5]{{\dual b}*\+{\dual a}}
+        \formula[y=0]{b*\*b}
+            \Vlink[violet]{[-1]1,1}
+            \Vlink[violet]{[1]1,2}
+    \end{tikzpicture}}
+\\ \\[-5pt]
+	\text{\small composition}
+\end{array}
+\hfill
+\]
+\defn{Composition}, of proof nets over $\seq{\dual A}B$ and $\seq{\dual B}C$ to one over $\seq{\dual A}C$, is by the relational composition of their linkings along the dual formulas $B$ and $\dual B$, as illustrated above right.
+
+Additive proof nets have two natural correctness criteria.
+\defn{Coalescence} \cite{Heijltjes-Hughes-2015,Hughes-Heijltjes-2016}, a counterpart to multiplicative \emph{contractibility} \cite{Danos-1990}, provides efficient correctness and sequentialization via local rewriting: it asks that the steps below left result in a single link, connecting both formulas.
+\defn{Slicing} \cite{Hughes-vanGlabbeek-2005} is a global, geometric criterion: it asks that each \defn{slice}, a choice to remove one subformula of each product along with all connected links, retains a single link.
+%
+\[
+\hspace*{-\parindent}
+\hspace*{\fill}
+\begin{array}{c@{\qquad\qquad\qquad}c}
+	\vc{\begin{tikzpicture}[net]
+		\formula[y=1]{A}
+		\formula[y=0]{B\*C}
+		\Vlink[red]{[-2]1,1}
+		\Vlink[red]{[2]1,3}
+	\end{tikzpicture}}
+~\scoal~
+	\vc{\begin{tikzpicture}[net]
+		\formula[y=1]{A}
+		\formula[y=0]{B\*C}
+		\Vlink[red]{1,2}
+	\end{tikzpicture}}
+\qquad\quad
+	\vc{\begin{tikzpicture}[net]
+		\formula[y=1]{A}
+		\formula[y=0]{B\+C}
+		\Vlink[red]{1,1}
+	\end{tikzpicture}}
+~\scoal~
+	\vc{\begin{tikzpicture}[net]
+		\formula[y=1]{A}
+		\formula[y=0]{B\+C}
+		\Vlink[red]{1,2}
+	\end{tikzpicture}}
 &	
-	 \infer[\Qrr?t]{\Seq{\exists x.A}C}{\Seq{A[t/x]}C}
+	\vc{\begin{tikzpicture}[net]
+		\formula[y=1]{A}
+		\begin{scope}[black!40]
+		\formula[y=0]{B\*C}
+		\Vlink[red]{[-1]1,1}
+		\Vlink{[1]1,3}
+		\end{scope}
+		\formula[y=0]{B{\phantom{{}\*{}}}{\phantom C}}
+	\end{tikzpicture}}
+\qquad
+	\vc{\begin{tikzpicture}[net]
+		\formula[y=1]{A}
+		\begin{scope}[black!40]
+		\formula[y=0]{B\*C}
+		\Vlink{[-1]1,1}
+		\Vlink[red]{[1]1,3}
+		\end{scope}
+		\formula[y=0]{{\phantom B}{\phantom{{}\*{}}}C}
+	\end{tikzpicture}}
+\\
+	\text{\small coalescence}
+&	\text{\small slicing}
+\end{array}	
+\hfill
+\]
+
+%In this paper we extend additive proof nets with first-order quantification. 
+In this paper we present proof nets for first-order additive linear logic (\all1).
+Our central challenge is to incorporate the essential content of first-order proof, the \defn{witness assignment} to existential quantifiers, into additive proof nets, while retaining their features and tools: canonicity, direct (relational) composition, coalescence, and slicing.
+
+In a standard approach, as in the sequent calculus rules below left, a witness to $\exists x.B$ is assigned by an immediate substitution $B[t/x]$.
+To assign different witnesses in different slices, the subformula may be duplicated first, giving $B[s/x]$ and $B[t/x]$, as below right.
+%
+\[
+\hspace*{\fill}
+\hspace*{-\parindent}
+	\vc{\infer[\Qrr?t]{\seq A{\exists x.B}}{\seq A{B[t/x]}}}
+\qquad
+	\vc{\infer[\Qrr!]{\seq A{\forall x.B}}{\seq AB}}
+\qquad\qquad
+\vc{
+	\infer[\Qrr*]{\Seq{\exists x.\dual P(x)}{P(s)\*P(t)}}{
+	 \infer[\Qrr?s]{\Seq{\exists x.\dual P(x)}{P(s)}}{\infer{\Seq{\dual P(s)}{P(s)}}{}}
+	 &&
+	 \infer[\Qrr?t]{\Seq{\exists x.\dual P(x)}{P(t)}}{\infer{\Seq{\dual P(t)}{P(t)}}{}}
    }}
-%~.
-\]
-%
-We advance two solutions.
-\defn{Witness nets} replace the \emph{implicit} substitutions of sequent proofs with \emph{explicit} substitutions, recorded at each link.
-\defn{Unification nets}, introduced by the second author in \cite{Hughes-2018} for first-order multiplicative linear logic, omit existential witnesses and reconstruct them by unification; we extend them to \all1.
-Respective examples are below.
-\[
-\hspace*{8ex}% spacing hack to achieve central horizontal alignment
-\begin{tikzpicture}[net]
-	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-	\Vlink[red,l,label={$\scriptstyle[f(x)/y\,,\,x/z]$~~}]{3,2}
-	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
-\end{tikzpicture}
-\hspace*{16ex}
-\begin{tikzpicture}[net]
-	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-	\Vlink[red]{3,2}
-	\Vlink[blue]{5,4}
-\end{tikzpicture}
-\]
-%
-Correctness and sequentialization for \all1 proof nets will be through \defn{coalescence}~\cite{Heijltjes-Hughes-2015,Hughes-Heijltjes-2016}, the additive counterpart to \defn{contractibility} for multiplicative linear logic~\cite{Danos-1990}.
-It is a simple graph rewrite relation that pushes links from the leaves towards the roots of a sequent, that is effectively top-down sequentialization (like its multiplicative counterpart~\cite{Guerrini-Masini-2001}).
-Figure~\ref{fig:main example} illustrates the process for the witness net above.
+\hfill
+\]
+%
+This is incompatible with a \defn{sequent + links} proof net design, where the conclusion sequent remains intact, and a subformula $B$ cannot be the subject of substitution or duplication.
+Instead, we propose two alternative treatments of witnessing terms, embodied in two notions of proof net: \defn{witness nets} and \defn{unification nets}.
+% irrecoverably alters the subformula $B$ (since $B[t/x]$ may contain other occurrences of $t$, it is not possible to recover $B$)
+%
+Our solutions are based on the second author's recent \defn{unification nets} for first-order multiplicative linear logic \cite{Hughes-2018}.
+Their main feature is to omit existential witnesses altogether, and reconstruct them by unification.
+%
+\[
+\hspace*{\fill}
+\hspace*{-\parindent}
+\begin{array}{c@{\qquad\qquad\qquad}c}
+	\vc{\begin{tikzpicture}[net]
+		\formula[y=1.2]{\exists x.{\dual P}(x)}
+		\formula[y=0]{P(s)\*P(t)}
+		\Vlink[red,l,label={$\scriptstyle[s/x]~~$}]{[-3]4,1}
+		\Vlink[red,r,label={$~\scriptstyle[t/x]$}]{[1]4,6}
+	\end{tikzpicture}}
+&
+	\vc{\begin{tikzpicture}[net]
+		\formula[y=1.2]{\exists x.{\dual P}(x)}
+		\formula[y=0]{P(s)\*P(t)}
+		\Vlink[red]{[-3]4,1}
+		\Vlink[red]{[1]4,6}
+	\end{tikzpicture}}
+\\ \\[-5pt]
+	\text{\small a witness net}
+&	\text{\small a unification net}
+\end{array}
+\hfill
+\]
+
+\defn{Witness nets} record witness assignment in substitution maps attached to each link.
+The example above left shows the net corresponding to the sequent proof above.
+(We will assume a different variable for each quantifier, and we attach links to predicate letters, as the root connective of a propositional atom.) Witness nets are canonical for \all1 sequent calculus permutations, and we give both correctness criteria,  coalescence and slicing.
+Composition is direct, where the witness assignments of links must be composed, which is done through a simple process of \emph{interaction + hiding} similar to that of game semantics \cite{Mimram-2011}.
+
+\defn{Unification nets} omit any witness information, as illustrated above right.
+In addition to canonicity, they embody a notion of \defn{generality}: where more than one witness could be assigned, unification nets do not require a definite choice, while witness nets do.
+Composition remains by relational composition, and correctness is by coalescence, during which process witnesses are reconstructed by first-order unification.
+
+Coalescence~\cite{Heijltjes-Hughes-2015,Hughes-Heijltjes-2016}, like multiplicative contractibility, \cite{Danos-1990,Guerrini-Masini-2001} is effectively top-down sequentialization.
+Figure~\ref{fig:main example} illustrates the process.
 In the example, a link between subformulas $A$ and $B$ carrying a substitution map $\sigma$ represents a sequent $\seq{A\sigma}{B\sigma}$.
-Each coalescence step ($\star S$) corresponds to a proof rule ($\star R$), by which the sequence generates the sequent proof.
+Each coalescence step ($\star S$) corresponds to a proof rule ($\star R$), by which the coalescence sequence generates the sequent proof from the axioms down to the conclusion.
 
@@
 
-We include the following results for our \all1 proof nets.
+%As illustrated by Herbrand's Theorem \cite{Herbrand-1930},
+
+%\[
+%\hspace*{\fill}%
+%\hspace*{-\parindent}%\hspace*{8ex}% spacing hack to achieve central horizontal alignment
+%\begin{tikzpicture}[net]
+%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+%	\Vlink[red,l,label={$\scriptstyle[f(x)/y\,,\,x/z]$~~}]{3,2}
+%	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
+%\end{tikzpicture}
+%\hspace*{16ex}
+%\begin{tikzpicture}[net]
+%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+%	\Vlink[red]{3,2}
+%	\Vlink[blue]{5,4}
+%\end{tikzpicture}
+%\hfill
+%\]
+%
+%Correctness and sequentialization for \all1 proof nets will be through \defn{coalescence}~\cite{Heijltjes-Hughes-2015,Hughes-Heijltjes-2016}, the additive counterpart to \defn{contractibility} for multiplicative linear logic~\cite{Danos-1990}.
+It is a simple graph rewrite relation that pushes links from the leaves towards the roots of a sequent,
+
+%We include the following results for our \all1 proof nets.
 Witness nets are \emph{canonical} for the permutations of the sequent calculus, and we provide a geometric correctness condition.
 \emph{Composition} of unification nets (over $\seq AB$ and $\seq{\dual BC}$ into one over $\seq AC$) is remarkedly simple, as the relational composition of both sets of links.
-For composition of witness nets, in addition the witness assignments of links must be composed, which is done through a simple process of \emph{interaction + hiding} similar to those of game semantics \cite{Mimram-2011}.
+For composition of witness nets, in addition
+%\end{document}
+
+\subsection{Background}
+
+Additive linear logic is combinatorially rich, yet well-behaved and tractable: proof search \cite{Galmiche-Marion-1995,Galmiche-2000} and proof net correctness \cite{Heijltjes-Hughes-2015} are linear in $|A|\times|B|$ (with $|A|$ the size of the syntax tree of $A$); proof nets remain canonical and equally tractable when extended with the two units \cite{Heijltjes-2011,Heijltjes-Hughes-2015}; and the first-order case is merely NP-complete \cite{Heijltjes-Hughes-2015}.
+
+At the same time, the ubiquity of its main operations, product and sum, mean the ideas and results it garners are widely applicable.
+It serves as a microcosmos for important ideas and observations: it fostered the \emph{connections method} of proof search \cite{Galmiche-2000}; it demonstrated the \emph{Blass problem} \cite{Abramsky-2003} of game semantics, that sequential strategies do not in general have associative composition; and it is at the root of the study of fixed points in linear logic \cite{Santocanale-2002a}.
+The logic describes two-way communication~\cite{Cockett-Santocanale-2009}, and is a core part of \emph{session types}~\cite{Honda-1993}.
+
+{\all} is of course part of {\mall} (multiplicative-additive linear logic), and its lessons are clearly visible in the second author's canonical proof nets \cite{Hughes-vanGlabbeek-2005} for {\mall}, as well as the first and second author's locally canonical \emph{conflict nets}~\cite{Hughes-Heijltjes-2016}.
+Its proof nets also appear as the \emph{skew fibrations} in the second author's \emph{combinatorial proofs} for classical logic~\cite{Hughes-2006-proofs}, and in the third author's study of the \emph{medial rule} for classical logic~\cite{str:RTA07}.
+To prepare the ground for the cut elimination of first-order \emph{combinatorial proofs} is one motivation for the current presentation.
+
+%Additive linear logic $(\all)$ is the logic of product $(\*)$ and sum $(\+)$, and their canonical morphisms: projections, injections, and diagonals.
+It is captured naturally in \defn{additive proof nets} \cite{Girard-1987,Hughes-vanGlabbeek-2005}, consisting of a two-sided sequent $A\vdash B$ or, here, a one-sided sequent $\seq{\dual A}B$ plus a \defn{linking}, a relation between subformulas in $\dual A$ and in $B$.
+
+%\[
+%%\hspace*{9ex}% spacing hack to achieve central horizontal alignment
+%\hspace*{-\parindent}%
+%\hspace*{\fill}%
+%% Behold my better spacing hack to achieve central horizontal alignment :)
+%\begin{array}{c@{\qquad\qquad}c@{\qquad\qquad}c@{\qquad\qquad}c}
+%	\begin{tikzpicture}[net]
+%		\formula[y=1]{{\dual a}}
+%		\formula[y=0]{a\*a}
+%		\Vlink[red]{[-2]1,1}
+%		\Vlink[red]{[2]1,3}
+%	\end{tikzpicture}
+%&
+%	\begin{tikzpicture}[net]
+%		\formula[y=1]{{\dual a}}
+%		\formula[y=0]{a\+b}
+%		\Vlink[red]{1,1}
+%	\end{tikzpicture}
+%&
+%	\begin{tikzpicture}[net]
+%		\formula[y=1]{{\dual a}\+{\dual b}}
+%		\formula[y=0]{b\*a}
+%		\Vlink[red]{1,3}
+%		\Vlink[red]{3,1}
+%	\end{tikzpicture}
+%&
+%	\begin{tikzpicture}[net]
+%		\formula[y=1]{*{\phantom(}{\dual a}*{\phantom)}
+%		 {{\+}}*({\dual b}*{\phantom)}
+%		 {{\+}}*{\phantom(}{\dual c}*)}
+%		\formula[y=0]{*(a*{\phantom)}
+%		{{\*}}*{\phantom(}b*)
+%		{{\*}}*{\phantom(}c*{\phantom)}}
+%		\Vlink[red]{1,1}
+%		\Vlink[red]{3,3}
+%		\Vlink[red]{5,5}
+%	\end{tikzpicture}
+%\\
+%	\text{\small diagonal}
+%&	\text{\small injection}
+%&	\text{\small symmetry}
+%&	\text{\small associativity}
+%\end{array}
+%\hfill
+%\]
 
@@
 These nets are not generally canonical: they admit the permutation (and duplication) of proof rules past implicit \emph{contractions}.
-We believe (though have not technically verified) that additive monomial nets include, and could be restricted to, canonical forms.
+We believe that additive monomial nets include, and could be restricted to, canonical forms.
 These would be equivalent to the following approach.
@@
 
+% --------------------------------------------------
+
+\subsection{First-order additive linear logic}
+
+First-order terms and the formulas of first-order $\all$ are generated by the following grammars.
+%
+\setMidspace{5pt}
+\[
+\begin{array}{@{}l@{}l}
+	t &\Coloneqq x \Mid f(t_1,\dots,t_n)
+\\[10pt]
+	a &\Coloneqq P(t_1,\dots,t_n) \Mid \dual P(t_1,\dots,t_n)
+\\[10pt]
+	A &\Coloneqq a \Mid A\+A \Mid A\*A \Mid \exists x.A \Mid \forall x.A
+\end{array}
+\]
+%
+Negation $(\dual{\,\cdot\,})$ is applied to predicate symbols, $\dual P$ as a matter of convenience.
+The \defn{dual} $\dual A$ of an arbitrary formula $A$ is given by DeMorgan.
+We use the following notational conventions.
+%
+\[
+\begin{tabular}{@{}lll@{}} 
+	$x,y,z$ & $\in \var$		& first-order variables\\
+	$f,g,h$ & $\in \Sigma_f$	& $n$-ary $(n\geq 0)$ function symbols from a fixed alphabet $\Sigma_f$\\
+	$P,Q,R$ & $\in \Sigma_p$	& $n$-ary $(n\geq 0)$ predicate symbols from a fixed alphabet $\Sigma_p$ \\
+	$s,t,u$ & $\in \terms$ 		& first-order terms over $\var$ and $\Sigma_f$ \\
+	$a,b,c$ & $\in \atom$		& atomic propositions \\
+	$A,B,C$ & $\in \form$		& \all1 formulas \\
+\end{tabular}
+\]
+%
+A \defn{sequent} $\seq AB$ is a pair of formulas $A$ and $B$.
+A sequent calculus for \all1 is given in Figure~\ref{fig:sequent calculus}, where each rule has a symmetric counterpart for the first formula in the sequent.
+We write $\prf\pi AB$ for a proof $\pi$ with conclusion sequent $\seq AB$.
+Two proofs are \defn{equivalent} $\pi\sim\pi'$ if one is obtained from the other by rule permutations (Appendix~\ref{sec:permutations}, Figure~\ref{fig:permutations}).
+
 % ..................................................
@@
 % ..................................................
-
-% --------------------------------------------------
-
-\subsection{First-order additive linear logic}
-
-First-order terms and the formulas of first-order $\all$ are generated by the following grammars.
-%
-\setMidspace{5pt}
-\[
-\begin{array}{@{}l@{}l}
-	t &\Coloneqq x \Mid f(t_1,\dots,t_n)
-\\[10pt]
-	a &\Coloneqq P(t_1,\dots,t_n) \Mid \dual P(t_1,\dots,t_n)
-\\[10pt]
-	A &\Coloneqq a \Mid A\+A \Mid A\*A \Mid \exists x.A \Mid \forall x.A
-\end{array}
-\]
-%
-Negation $(\dual{\,\cdot\,})$ is applied to predicate symbols, $\dual P$ as a matter of convenience.
-The \defn{dual} $\dual A$ of an arbitrary formula $A$ is given by DeMorgan.
-We use the following notational conventions.
-%
-\[
-\begin{tabular}{@{}lll@{}} 
-	$x,y,z$ & $\in \var$		& first-order variables\\
-	$f,g,h$ & $\in \Sigma_f$	& $n$-ary $(n\geq 0)$ function symbols from a fixed alphabet $\Sigma_f$\\
-	$P,Q,R$ & $\in \Sigma_p$	& $n$-ary $(n\geq 0)$ predicate symbols from a fixed alphabet $\Sigma_p$ \\
-	$s,t,u$ & $\in \terms$ 		& first-order terms over $\var$ and $\Sigma_f$ \\
-	$a,b,c$ & $\in \atom$		& atomic propositions \\
-	$A,B,C$ & $\in \form$		& \all1 formulas \\
-\end{tabular}
-\]
-%
-A \defn{sequent} $\seq AB$ is a pair of formulas $A$ and $B$.
-A sequent calculus for \all1 is given in Figure~\ref{fig:sequent calculus}, where each rule has a symmetric counterpart for the first formula in the sequent.
-We write $\prf\pi AB$ for a proof $\pi$ with conclusion sequent $\seq AB$.
-Two proofs are \defn{equivalent} $\pi\sim\pi'$ if one is obtained from the other by rule permutations (Appendix~\ref{sec:permutations}, Figure~\ref{fig:permutations}).
 
@@
 
+\section{Conclusion}
+
+We have presented two notions of first-order additive proof net, witness nets and unification nets, to canonically capture the two natural notions of proof identity for first-order additive linear logic.
+We conclude with a quick table surveying our results.
+
+\begin{center}
+\begin{tabular}{lcc}
+\vphantom)	& Witness nets & Unification nets
+\\\hline
+   Canonicity & \vmark & \vmark
+\\ Generality && \vmark
+\\ Direct composition & \vmark & \vmark
+\\ Coalescence & \vmark & \vmark
+\\ Slicing & \vmark &
+\end{tabular}
+\end{center}
+
+% --------------------------------------------------
+
 \subsection*{Acknowledgements}
 
-Dominic would like to thank his host, Wes Holliday, at the UC Berkeley Logic Group.
+We would like to thank the anonymous referees for their constructive feedback. Dominic would like to thank his host, Wes Holliday, at the UC Berkeley Logic Group.
 

### 2018-04-17 ALL1.tex
improved intro and moved 1.3 to conclusion

@@
 \documentclass[UKenglish]{lipics-v2018}
+
+%\usepackage {etex}
 
@@
 \usepackage{pifont}
-	\newcommand\xmark{{\red\ding{54}}}
+	\newcommand\xmark{{\color{red}\ding{55}}}
 	\newcommand\vmark{{\color{green}\ding{51}}}
@@
  {University of Bath, United Kingdom}
- {http://willem.heijltj.es/} %{w.b.heijltjes@bath.ac.uk}
+ {{http://willem.heijltj.es/}} %{w.b.heijltjes@bath.ac.uk}
  {}
@@
  {Logic Group, UC Berkeley, USA}
- {http://boole.stanford.edu/\textasciitilde dominic/} %{dominich@theory.stanford.edu}
+ {{http://boole.stanford.edu/\textasciitilde dominic/}} %{dominich@theory.stanford.edu}
  {}
@@
  {Inria Saclay \&\ LIX/\'Ecole Polytechnique, Palaiseau, France}
- {http://www.lix.polytechnique.fr/Labo/Lutz.Strassburger/} %{lutz.strassburger@inria.fr}
+ {{http://www.lix.polytechnique.fr/Labo/Lutz.Strassburger/}} %{lutz.strassburger@inria.fr}
  {}
@@
 We present canonical proof nets for first-order additive linear logic, the fragment of linear logic with sum, product, and first-order universal and existential quantification. 
-
+%
 We present two versions of our proof nets.
-One, witness nets, retains explicit witnessing information to existential quantification.
-For the other, unification nets, this information is absent but can be reconstructed through unification.
+One, \emph{witness nets}, retains explicit witnessing information to existential quantification.
+For the other, \emph{unification nets}, this information is absent but can be reconstructed through unification.
 Unification nets embody a central contribution of the paper: first-order witness information can be left implicit, and reconstructed as needed.
-
+%
 Witness nets are canonical for first-order additive sequent calculus.
 Unification nets in addition factor out any inessential choice for existential witnesses.
-Both notions of proof net are defined through coalescence, the additive version of multiplicative contractibility, and for witness nets a geometric correctness criterion is provided.
+Both notions of proof net are defined through coalescence, the additive version of multiplicative contractibility, and for witness nets an additional geometric correctness criterion is provided.
 Both feature a global composition operation.
@@
 \hspace*{-\parindent}
-\begin{array}{c@{\qquad\qquad\qquad}c}
+\begin{array}{c@{\qquad\qquad\qquad\qquad\qquad}c}
 	\vc{\begin{tikzpicture}[net]
@@
 The example above left shows the net corresponding to the sequent proof above.
-(We will assume a different variable for each quantifier, and we attach links to predicate letters, as the root connective of a propositional atom.) Witness nets are canonical for \all1 sequent calculus permutations, and we give both correctness criteria,  coalescence and slicing.
+(We will assume a different variable for each quantifier, and we attach links to predicate letters, as the root connective of a propositional atom.) Witness nets are canonical for \all1 sequent calculus permutations, and we give two correctness criteria, one via coalescence and one via slicing.
 Composition is direct, where the witness assignments of links must be composed, which is done through a simple process of \emph{interaction + hiding} similar to that of game semantics \cite{Mimram-2011}.
@@
 In addition to canonicity, they embody a notion of \defn{generality}: where more than one witness could be assigned, unification nets do not require a definite choice, while witness nets do.
-Composition remains by relational composition, and correctness is by coalescence, during which process witnesses are reconstructed by first-order unification.
+Composition remains by relational composition, and correctness is by coalescence.
+During this process witnesses are reconstructed by first-order unification.
+
+% ..................................................
+
+\begin{figure}[!t]
+\[
+\begin{array}{c}
+\begin{array}{@{}c@{~}c@{\qquad}c@{}}
+  \vc{
+  \begin{tikzpicture}[net]
+	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+	\Vlink[red,l,label={$\scriptstyle[f(x)/y\,,\,x/z]$~~}]{3,2}
+	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
+  \end{tikzpicture}}
+&&
+  \vc{
+  \begin{tikzpicture}[net]
+	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+	\Vlink[violet,l,label={$\scriptstyle\varnothing$~~}]{1,1}
+  \end{tikzpicture}} 
+\\ \\[-5pt] \downarrow\scriptstyle{\srr+1} && \uparrow\scriptstyle\srr! \\ \\[-5pt]
+  \vc{
+  \begin{tikzpicture}[net]
+	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+	\Vlink[red,l,label={$\scriptstyle[f(x)/y\,,\,x/z]$~~~}]{4,2}
+	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
+  \end{tikzpicture}}
+&&
+  \vc{
+  \begin{tikzpicture}[net]
+	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+	\Vlink[violet,l,label={$\scriptstyle\varnothing$~~}]{2,1}
+  \end{tikzpicture}} 
+\\ \\[-5pt] \downarrow\scriptstyle\srr?,f(x) && \uparrow\scriptstyle\srr?,x \\ \\[-5pt]  
+  \vc{
+  \begin{tikzpicture}[net]
+	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+	\Vlink[red,l,label={$\scriptstyle[x/z]$~~}]{2,2}
+	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
+  \end{tikzpicture}} 
+&&  
+  \vc{
+  \begin{tikzpicture}[net]
+	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+	\Vlink[violet,l,label={$\scriptstyle[x/z]$~~~}]{[2]2,3}
+  \end{tikzpicture}}
+\\ \\[-5pt] \downarrow\scriptstyle{\srr+2} && \uparrow\scriptstyle\srr* \\ \\[-5pt]
+  \vc{
+  \begin{tikzpicture}[net]
+	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+	\Vlink[red,l,label={$\scriptstyle[x/z]$~~}]{2,2}
+	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{4,4}
+  \end{tikzpicture}}
+& \stackrel{\srr?,t}\scoal & 
+  \vc{
+  \begin{tikzpicture}[net]
+	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+	\Vlink[red,l,label={$\scriptstyle[x/z]$~~}]{2,2}
+	\Vlink[blue,r,label={~~~$\scriptstyle[x/z]$}]{[4]2,4}
+  \end{tikzpicture}}
+\end{array}
+\\ \\[20pt]
+	\color{violet}\infer[\color{black}\Qrr!]{\color{black}\Seq{\forall x.\exists y.\dual P(y)\+\dual Q(x,y)}{\exists z.P(f(z))\*Q(z,t)}}{
+	 \color{violet}\infer[\color{black}\Qrr?x]{\color{black}\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{\exists z.P(f(z))\*Q(z,t)}}{
+	  \color{violet}\infer[\color{black}\Qrr*]{\color{black}\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{P(f(x))\*Q(x,t)}}{
+	   \color{red}\infer[\color{black}\Qrr?{f(x)}]{\color{black}\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{P(f(x))}}{
+	    \color{red}\infer[\color{black}\Qrr+1]{\color{black}\Seq{\dual P(f(x))\+\dual Q(x,f(x))}{P(f(x))}}{
+	     \color{red}\infer[\color{black}\Qrr1]{\color{black}\Seq{\dual P(f(x))}{P(f(x))}}{}
+	   }}&
+	   \color{blue}\infer[\color{black}\Qrr?t]{\color{black}\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{Q(x,t)}}{
+	    \color{blue}\infer[\color{black}\Qrr+2]{\color{black}\Seq{\dual P(t)\+\dual Q(x,t)}{Q(x,t)}}{
+	     \color{blue}\infer[\color{black}\Qrr1]{\color{black}\Seq{\dual Q(x,t)}{Q(x,t)}}{}
+	}}}}}
+\end{array}
+\]
+\caption{A coalescence and sequentialization example}
+\label{fig:main example}
+\end{figure}
+
+% ..................................................
+% ..................................................
+
+\begin{figure}[!t]
+\[
+\vc{\begin{tikzpicture}[net]
+	\formula[y=1.2]{{\dual P}*{(x,x)}}
+	\formula[y=0]{P*{(y,s)}\*P*{(t,z)}}
+	\Vlink[red]{[-2]1,1}
+	\Vlink[blue]{[2]1,3}
+\end{tikzpicture}}
+\quad\ucoal\quad
+\vc{\begin{tikzpicture}[net]
+	\formula[y=1.2]{{\dual P}*{(x,x)}}
+	\formula[y=0]{P*{(y,s)}\*P*{(t,z)}}
+	\Vlink[red,l,label={$\scriptstyle[s/y,s/x]$~~}]{[-2]1,1}
+	\Vlink[blue,r,label={~~$\scriptstyle[t/z,t/x]$}]{[2]1,3}
+\end{tikzpicture}}
+\quad\stackrel{\urr*}\ucoal\quad
+\vc{\begin{tikzpicture}[net]
+	\formula[y=1.2]{{\dual P}*{(x,x)}}
+	\formula[y=0]{P*{(y,s)}\*P*{(t,z)}}
+	\Vlink[violet,r,label={~~$\scriptstyle[u/z,u/y,u/x]$}]{1,2}
+\end{tikzpicture}}
+\]
+\caption{Coalescence with unification; $u$ is the smallest term unifying $s$ and $t$} 
+\label{fig:unification example}
+\end{figure}
+
+% ..................................................
 
@@
 Figure~\ref{fig:main example} illustrates the process.
-In the example, a link between subformulas $A$ and $B$ carrying a substitution map $\sigma$ represents a sequent $\seq{A\sigma}{B\sigma}$.
+In the example, a link between subformulas $A$ and $B$ carrying a substitution $\sigma$ represents a sequent $\seq{A\sigma}{B\sigma}$.
 Each coalescence step ($\star S$) corresponds to a proof rule ($\star R$), by which the coalescence sequence generates the sequent proof from the axioms down to the conclusion.
@@
 The initial substitution map assigned to a link on atomic formulas $a=P(s_1,\dots,s_n)$ and $b=\dual P(t_1,\dots,t_n)$ is the most general unifier (\mgu) of $a$ and $\dual b$ (the first step in Figure~\ref{fig:unification example}).
-Coalescence then proceeds as for witness nets, except when joining two links from different slices with a product step, ($\urr*$) in Figure~\ref{fig:unification example}.
-Here, witness nets require both links to carry the same substitution map, while for unification nets a common, more general map is generated by unification.
+Coalescence then proceeds as for witness nets, except when joining two links from different slices with a product step (marked \hbox{\small$\;\urr*\;$} in Figure~\ref{fig:unification example}).
+Here, witness nets require both links to carry the same substitution, while for unification nets a common, more general map is generated by unification.\looseness=-1
 
@@
 
-% ..................................................
-
-\begin{figure}
-\[
-\begin{array}{c}
-\begin{array}{@{}c@{~}c@{\qquad}c@{}}
-  \vc{
-  \begin{tikzpicture}[net]
-	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-	\Vlink[red,l,label={$\scriptstyle[f(x)/y\,,\,x/z]$~~}]{3,2}
-	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
-  \end{tikzpicture}}
-&&
-  \vc{
-  \begin{tikzpicture}[net]
-	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-	\Vlink[violet,l,label={$\scriptstyle\varnothing$~~}]{1,1}
-  \end{tikzpicture}} 
-\\ \\[-5pt] \downarrow\scriptstyle{\srr+1} && \uparrow\scriptstyle\srr! \\ \\[-5pt]
-  \vc{
-  \begin{tikzpicture}[net]
-	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-	\Vlink[red,l,label={$\scriptstyle[f(x)/y\,,\,x/z]$~~~}]{4,2}
-	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
-  \end{tikzpicture}}
-&&
-  \vc{
-  \begin{tikzpicture}[net]
-	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-	\Vlink[violet,l,label={$\scriptstyle\varnothing$~~}]{2,1}
-  \end{tikzpicture}} 
-\\ \\[-5pt] \downarrow\scriptstyle\srr?,f(x) && \uparrow\scriptstyle\srr?,x \\ \\[-5pt]  
-  \vc{
-  \begin{tikzpicture}[net]
-	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-	\Vlink[red,l,label={$\scriptstyle[x/z]$~~}]{2,2}
-	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
-  \end{tikzpicture}} 
-&&  
-  \vc{
-  \begin{tikzpicture}[net]
-	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-	\Vlink[violet,l,label={$\scriptstyle[x/z]$~~~}]{[2]2,3}
-  \end{tikzpicture}}
-\\ \\[-5pt] \downarrow\scriptstyle{\srr+2} && \uparrow\scriptstyle\srr* \\ \\[-5pt]
-  \vc{
-  \begin{tikzpicture}[net]
-	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-	\Vlink[red,l,label={$\scriptstyle[x/z]$~~}]{2,2}
-	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{4,4}
-  \end{tikzpicture}}
-& \stackrel{\srr?,t}\scoal & 
-  \vc{
-  \begin{tikzpicture}[net]
-	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-	\Vlink[red,l,label={$\scriptstyle[x/z]$~~}]{2,2}
-	\Vlink[blue,r,label={~~~$\scriptstyle[x/z]$}]{[4]2,4}
-  \end{tikzpicture}}
-\end{array}
-\\ \\[20pt]
-	\color{violet}\infer[\color{black}\Qrr!]{\color{black}\Seq{\forall x.\exists y.\dual P(y)\+\dual Q(x,y)}{\exists z.P(f(z))\*Q(z,t)}}{
-	 \color{violet}\infer[\color{black}\Qrr?x]{\color{black}\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{\exists z.P(f(z))\*Q(z,t)}}{
-	  \color{violet}\infer[\color{black}\Qrr*]{\color{black}\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{P(f(x))\*Q(x,t)}}{
-	   \color{red}\infer[\color{black}\Qrr?{f(x)}]{\color{black}\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{P(f(x))}}{
-	    \color{red}\infer[\color{black}\Qrr+1]{\color{black}\Seq{\dual P(f(x))\+\dual Q(x,f(x))}{P(f(x))}}{
-	     \color{red}\infer[\color{black}\Qrr1]{\color{black}\Seq{\dual P(f(x))}{P(f(x))}}{}
-	   }}&
-	   \color{blue}\infer[\color{black}\Qrr?t]{\color{black}\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{Q(x,t)}}{
-	    \color{blue}\infer[\color{black}\Qrr+2]{\color{black}\Seq{\dual P(t)\+\dual Q(x,t)}{Q(x,t)}}{
-	     \color{blue}\infer[\color{black}\Qrr1]{\color{black}\Seq{\dual Q(x,t)}{Q(x,t)}}{}
-	}}}}}
-\end{array}
-\]
-\caption{A coalescence and sequentialization example}
-\label{fig:main example}
-\end{figure}
-
-% ..................................................
-
-\begin{figure}
-\[
-\vc{\begin{tikzpicture}[net]
-	\formula[y=1.2]{{\dual P}*{(x,x)}}
-	\formula[y=0]{P*{(y,s)}\*P*{(t,z)}}
-	\Vlink[red]{[-2]1,1}
-	\Vlink[blue]{[2]1,3}
-\end{tikzpicture}}
-\quad\ucoal\quad
-\vc{\begin{tikzpicture}[net]
-	\formula[y=1.2]{{\dual P}*{(x,x)}}
-	\formula[y=0]{P*{(y,s)}\*P*{(t,z)}}
-	\Vlink[red,l,label={$\scriptstyle[s/y,s/x]$~~}]{[-2]1,1}
-	\Vlink[blue,r,label={~~$\scriptstyle[t/z,t/x]$}]{[2]1,3}
-\end{tikzpicture}}
-\quad\stackrel{\urr*}\ucoal\quad
-\vc{\begin{tikzpicture}[net]
-	\formula[y=1.2]{{\dual P}*{(x,x)}}
-	\formula[y=0]{P*{(y,s)}\*P*{(t,z)}}
-	\Vlink[violet,r,label={~~$\scriptstyle[u/z,u/y,u/x]$}]{1,2}
-\end{tikzpicture}}
-\]
-\caption{Coalescence with unification; $u$ is the smallest term unifying $s$ and $t$} 
-\label{fig:unification example}
-\end{figure}
-
-% ..................................................
-
 % --------------------------------------------------
@@
 \emph{Unification nets} leave all witnesses implicit, thus identifying all proofs modulo witness assignment, and validating all three equivalences.
-
-\subsection{Monomial nets and Expansion Trees}
-
-Proof nets with additives and quantifiers exist as \emph{monomial nets} \cite{Girard-1996}, where slices are managed explicitly with \emph{monomial weights}.
-These nets are not generally canonical: they admit the permutation (and duplication) of proof rules past implicit \emph{contractions}.
-We believe that additive monomial nets include, and could be restricted to, canonical forms.
-These would be equivalent to the following approach.
-
-\emph{Expansion tree proofs} for classical logic \cite{Miller-1987,Heijltjes-2010} provide another approach to canonicity for first-order quantification.
-In this formulation, a formula $\exists x.A$ is interpreted as the sum (or classically, \emph{disjunction}) over a fixed number of instantiations $A[t_1/x]\+\dots\+A[t_n/x]$.
-The idea can be traced to Herbrand's Theorem \cite{Herbrand-1930}: $\exists x.A$ is equivalent to the infinite sum over $A[t/x]$ for all terms $t$ in the language, but for any given proof a finite set of terms suffices.
-
-We use this approach implicitly for our geometric correctness condition for witness nets (Section~\ref{sec:correctness}), which generalizes the existing \emph{slice-based} criterion for additive proof nets \cite{Hughes-vanGlabbeek-2005}.
-In constructing the slices over a formula, we interpret $\exists x.A$ by an \emph{expansion} $A[t_1/x]\+\dots\+A[t_n/x]$, where the witnesses $t_1$ through $t_n$ are collected from the substitution maps of the links in the proof net.
-
-For the definition of proof nets, we did not pursue this direction, and consider the present choice preferable.
-Witness nets and unification nets retain the original structure of \emph{formulas + links}, without requiring expansion trees.
-More importantly, as in the propositional case, they enable direct (non-inductive) composition by a relational composition of links.
-Finally, available space does not permit a detailed exposition, which we defer to a journal version.
 
@@
 
-\begin{figure}
+\begin{figure}[!t]
 \[
@@
 	}}
-\\ \\[-8pt]
+\end{align*}
+%\\ \\[-8pt]
+\begin{align*}
 \tag{$\srr?$}
@@
 % ..................................................
-\begin{figure}
+\begin{figure}[!t]
 \[
@@
 % ..................................................
-\begin{figure}[p]
+\begin{figure}[!tp]
 \[
@@
 
-\section{Conclusion}
-
+\begin{figure}[!t]
+\begin{center}
+\begin{tabular}{lcccc}
+ &	Monomial nets & Expansion trees & Witness nets & Unification nets
+\\\hline
+   Canonicity & \xmark & \vmark & \vmark & \vmark
+\\ Generality & \xmark &\xmark&\xmark& \vmark
+\\ Direct composition &(\vmark) &\xmark& \vmark & \vmark
+\\ Coalescence & ? & ? & \vmark & \vmark
+\\ Slicing &\vmark &\xmark& \vmark &\xmark
+\end{tabular}  
+  \caption{Comparison of different notions of proof nets for quantifiers and additive connectives}
+  \label{fig:results}
+\end{center}
+\end{figure}
+
+% --------------------------------------------------
+
+\section{Conclusion and related work}
+
+%\subsection{Alternative approaches: monomial nets and expansion trees}
 We have presented two notions of first-order additive proof net, witness nets and unification nets, to canonically capture the two natural notions of proof identity for first-order additive linear logic.
-We conclude with a quick table surveying our results.
-
-\begin{center}
-\begin{tabular}{lcc}
-\vphantom)	& Witness nets & Unification nets
-\\\hline
-   Canonicity & \vmark & \vmark
-\\ Generality && \vmark
-\\ Direct composition & \vmark & \vmark
-\\ Coalescence & \vmark & \vmark
-\\ Slicing & \vmark &
-\end{tabular}
-\end{center}
+%
+Proof nets with additives and quantifiers existed before as \emph{monomial nets} \cite{Girard-1996}, where slices are managed explicitly with \emph{monomial weights}.
+These nets are not generally canonical: they admit the permutation (and duplication) of proof rules past implicit \emph{contractions}.
+%
+However, we do conjecture that additive monomial nets could be restricted to some notion of canonical form, which would be equivalent to the notion induced by \emph{expansion tree proofs}, provide another approach to canonicity for first-order quantification for classical logic \cite{Miller-1987,Heijltjes-2010}.
+%
+But the details of this relation are clearly beyond the scope of our paper.
+
+%%\emph{Expansion trees} provide another approach to canonicity for first-order quantification for classical logic \cite{Miller-1987,Heijltjes-2010}.
+
+In the formulation of expansion trees, a formula $\exists x.A$ is interpreted as the sum (or classically, the \emph{disjunction}) over a fixed number of instantiations $A[t_1/x]\+\dots\+A[t_n/x]$.
+This can be traced back to Herbrand's Theorem \cite{Herbrand-1930}: $\exists x.A$ is equivalent to the infinite sum over $A[t/x]$ for all terms $t$ in the language, but for any given proof a finite set of terms suffices.
+%
+We used this idea implicitly for our geometric correctness condition for witness nets (Section~\ref{sec:correctness}), which generalizes the existing \emph{slice-based} criterion for multiplicative-additive proof nets \cite{Hughes-vanGlabbeek-2005}.
+In constructing the slices over a formula, we interpreted $\exists x.A$ by an \emph{expansion} $A[t_1/x]\+\dots\+A[t_n/x]$, where the witnesses $t_1$ through $t_n$ are collected from the substitution maps of the links in the proof net.
+
+However, for our definition of proof nets, we did not pursue this direction, and consider the choices made in this paper preferable.
+Witness nets and unification nets retain the original structure of \emph{formulas + links}, without requiring expansion trees.
+More importantly, as in the propositional case, they enable direct (non-inductive) composition by a relational composition of links.
+%
+%%Finally, available space does not permit a detailed exposition, which we defer to a journal version.
+%
+%We have presented two notions of first-order additive proof net, witness nets and unification nets, to canonically capture the two natural notions of proof identity for first-order additive linear logic.
+%
+The table in Figure~\ref{fig:results} summarizes the results of our paper and the observations in this section.
 

### 2018-04-17 ALL1.tex
discussion on table

@@
 \begin{tabular}{lcccc}
- &	Monomial nets & Expansion trees & Witness nets & Unification nets
+ &	Monomial nets & Expansion trees$^\ast$ & Witness nets & Unification nets
 \\\hline
-   Canonicity & \xmark & \vmark & \vmark & \vmark
+   Canonicity & \xmark & \vmark^\ast & \vmark & \vmark
 \\ Generality & \xmark &\xmark&\xmark& \vmark
@@
 \\ Coalescence & ? & ? & \vmark & \vmark
-\\ Slicing &\vmark &\xmark& \vmark &\xmark
+\\ Slicing &\vmark &\vmark^\ast& \vmark & ?
 \end{tabular}  
@@
 %
-However, we do conjecture that additive monomial nets could be restricted to some notion of canonical form, which would be equivalent to the notion induced by \emph{expansion tree proofs}, provide another approach to canonicity for first-order quantification for classical logic \cite{Miller-1987,Heijltjes-2010}.
+However, we do conjecture that additive monomial nets could be restricted to some notion of canonical form, which would be equivalent to the notion induced by \emph{expansion tree proofs}, provide another approach to first-order quantification for classical logic \cite{Miller-1987,Heijltjes-2010}.
 %
@@
 %
-The table in Figure~\ref{fig:results} summarizes the results of our paper and the observations in this section.
+The table in Figure~\ref{fig:results} summarizes the results of our paper and the observations in this section, where the column on expansion trees is speculative since they only exist for classical logic, and not (yet) exist for $\all$.
 

### 2018-04-20 ALL1.tex
new introduction

@@
 \qquad
-	\vc{\infer[\Qrr!]{\seq A{\forall x.B}}{\seq AB}}
-\qquad\qquad
+	\vc{\infer[\Qrr!~(x\,\notin\,\fv(A))]{\seq A{\forall x.B}}{\seq AB}}
+\qquad\quad
 \vc{
@@
 (We will assume a different variable for each quantifier, and we attach links to predicate letters, as the root connective of a propositional atom.) Witness nets are canonical for \all1 sequent calculus permutations, and we give two correctness criteria, one via coalescence and one via slicing.
-Composition is direct, where the witness assignments of links must be composed, which is done through a simple process of \emph{interaction + hiding} similar to that of game semantics \cite{Mimram-2011}.
+Composition is direct, where the witness assignments of links are composed through a simple process of \emph{interaction + hiding} similar to that of game semantics \cite{Mimram-2011}.
 
@@
 
-% ..................................................
-
-\begin{figure}[!t]
-\[
-\begin{array}{c}
-\begin{array}{@{}c@{~}c@{\qquad}c@{}}
-  \vc{
-  \begin{tikzpicture}[net]
-	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-	\Vlink[red,l,label={$\scriptstyle[f(x)/y\,,\,x/z]$~~}]{3,2}
-	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
-  \end{tikzpicture}}
+\defn{Coalescence}~\cite{Heijltjes-Hughes-2015,Hughes-Heijltjes-2016}, like multiplicative contractibility \cite{Danos-1990,Guerrini-Masini-2001}, is effectively top-down sequentialization.
+We will distinguish \defn{strict coalescence} ($\scoal$) for witness nets and \defn{unifying coalescence} ($\ucoal$) for unification nets.
+We first give an example of the former (writing $Pxy$ for $P(x,y)$ to conserve space).
+In the initial witness net, below left, each link corresponds to a sequent calculus axiom between both linked subformulas, with the substitutions applied.
+%
+\newcommand\xs{xs} %{(\kern-1ptx\kern-1pt,\kern-2pts\kern-1pt)}
+\newcommand\xt{xt} %{(\kern-1ptx\kern-1pt,\kern-2ptt\kern-1pt)}
+\newcommand\xy{xy} %(\kern-1ptx\kern-1pt,\kern-2pty\kern-1pt)}
+\newcommand\zs{zs}
+\newcommand\zt{zt}
+\[
+\begin{array}{@{}c@{}c@{}c@{}c@{}c@{}}
+	\vc{\begin{tikzpicture}[net]
+		\formula[y=1]{\forall*{x.}\exists*{y.}{\dual P}*\xy}
+		\formula[y=0]{\exists*{z.}P*\zs\*P*\zt}
+		\Vlink[red,l,label={$\scriptstyle[x/z,s/y]~~$}]{[-3]3,2}
+		\Vlink[blue,r,label={$~~\scriptstyle[x/z,s/y]$}]{[1]3,4}
+	\end{tikzpicture}}
+& \quad\scoal &
+	\vc{\begin{tikzpicture}[net]
+		\formula[y=1]{\forall*{x.}\exists*{y.}{\dual P}*\xy}
+		\formula[y=0]{\exists*{z.}P*\zs\*P*\zt}
+		\Vlink[red,l,label={$\scriptstyle[x/z]~$}]{[-2]2,2}
+		\Vlink[blue,r,label={$~~\scriptstyle[x/z,s/y]$}]{[1]3,4}
+	\end{tikzpicture}}
+& \scoal &
+\hfill
+	\vc{\begin{tikzpicture}[net]
+		\formula[y=1]{\forall*{x.}\exists*{y.}{\dual P}*\xy}
+		\formula[y=0]{\exists*{z.}P*\zs\*P*\zt}
+		\Vlink[red,l,label={$\scriptstyle[x/z]~$}]{[-2]2,2}
+		\Vlink[blue,r,label={$~~\scriptstyle[x/z]$}]{[2]2,4}
+	\end{tikzpicture}}
+\hfill
+\scoal\cdots
+\\ \\
+\scriptsize
+	\color{white}
+	 \infer{\vphantom{\dual P}}{
+	  \color{red}\infer{\seq{\dual P\xs}{P\xs}}{}
        &&
-  \vc{
-  \begin{tikzpicture}[net]
-	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-	\Vlink[violet,l,label={$\scriptstyle\varnothing$~~}]{1,1}
-  \end{tikzpicture}} 
-\\ \\[-5pt] \downarrow\scriptstyle{\srr+1} && \uparrow\scriptstyle\srr! \\ \\[-5pt]
-  \vc{
-  \begin{tikzpicture}[net]
-	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-	\Vlink[red,l,label={$\scriptstyle[f(x)/y\,,\,x/z]$~~~}]{4,2}
-	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
-  \end{tikzpicture}}
-&&
-  \vc{
-  \begin{tikzpicture}[net]
-	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-	\Vlink[violet,l,label={$\scriptstyle\varnothing$~~}]{2,1}
-  \end{tikzpicture}} 
-\\ \\[-5pt] \downarrow\scriptstyle\srr?,f(x) && \uparrow\scriptstyle\srr?,x \\ \\[-5pt]  
-  \vc{
-  \begin{tikzpicture}[net]
-	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-	\Vlink[red,l,label={$\scriptstyle[x/z]$~~}]{2,2}
-	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
-  \end{tikzpicture}} 
-&&  
-  \vc{
-  \begin{tikzpicture}[net]
-	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-	\Vlink[violet,l,label={$\scriptstyle[x/z]$~~~}]{[2]2,3}
-  \end{tikzpicture}}
-\\ \\[-5pt] \downarrow\scriptstyle{\srr+2} && \uparrow\scriptstyle\srr* \\ \\[-5pt]
-  \vc{
-  \begin{tikzpicture}[net]
-	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-	\Vlink[red,l,label={$\scriptstyle[x/z]$~~}]{2,2}
-	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{4,4}
-  \end{tikzpicture}}
-& \stackrel{\srr?,t}\scoal & 
-  \vc{
-  \begin{tikzpicture}[net]
-	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-	\Vlink[red,l,label={$\scriptstyle[x/z]$~~}]{2,2}
-	\Vlink[blue,r,label={~~~$\scriptstyle[x/z]$}]{[4]2,4}
-  \end{tikzpicture}}
+	  \color{blue}\infer{\seq{\dual P\xt}{P\xt}}{}
+	 }
+& \hspace*{32pt} &
+\scriptsize
+	\color{red}\infer[\!\Qrr?s]{\seq{\exists y.\dual P\xy}{P\xs}}{\color{black}\infer{\seq{\dual P\xs}{P\xs}}{}}
+~~
+	\color{white}\infer{\vphantom{\dual P}}{\color{blue}\infer{\seq{\dual P\xt}{P\xt}}{}}
+& \hspace*{32pt} &
+\scriptsize
+	\color{red}\infer[\!\Qrr?s]{\seq{\exists y.\dual P\xy}{P\xs}}{\color{black}\infer{\seq{\dual P\xs}{P\xs}}{}}
+~~
+	\color{blue}\infer[\!\Qrr?t]{\seq{\exists y.\dual P\xy}{P\xt}}{\color{black}\infer{\seq{\dual P\xt}{P\xt}}{}}
 \end{array}
-\\ \\[20pt]
-	\color{violet}\infer[\color{black}\Qrr!]{\color{black}\Seq{\forall x.\exists y.\dual P(y)\+\dual Q(x,y)}{\exists z.P(f(z))\*Q(z,t)}}{
-	 \color{violet}\infer[\color{black}\Qrr?x]{\color{black}\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{\exists z.P(f(z))\*Q(z,t)}}{
-	  \color{violet}\infer[\color{black}\Qrr*]{\color{black}\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{P(f(x))\*Q(x,t)}}{
-	   \color{red}\infer[\color{black}\Qrr?{f(x)}]{\color{black}\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{P(f(x))}}{
-	    \color{red}\infer[\color{black}\Qrr+1]{\color{black}\Seq{\dual P(f(x))\+\dual Q(x,f(x))}{P(f(x))}}{
-	     \color{red}\infer[\color{black}\Qrr1]{\color{black}\Seq{\dual P(f(x))}{P(f(x))}}{}
-	   }}&
-	   \color{blue}\infer[\color{black}\Qrr?t]{\color{black}\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{Q(x,t)}}{
-	    \color{blue}\infer[\color{black}\Qrr+2]{\color{black}\Seq{\dual P(t)\+\dual Q(x,t)}{Q(x,t)}}{
-	     \color{blue}\infer[\color{black}\Qrr1]{\color{black}\Seq{\dual Q(x,t)}{Q(x,t)}}{}
-	}}}}}
+\]
+The first two steps (above middle and right) move both links from the subformula $\dual Pxy$ to $\exists y.\dual Pxy$, removing the substitutions $[s/y]$ and $[t/y]$ on $y$, and corresponding to sequent rules $\exists R,s$ and $\exists R,t$.
+Observe that we maintain the domain of the substitutions on a link as the variables of those existential quantifiers that either linked subformula is (strictly) in scope of.
+
+The next step, from above right to below left, combines both links, and corresponds to an additive conjunction rule.
+We require that both substitutions agree (their domains are the same by the above observation); hence this step could not have been performed before the previous two, corresponding to the non-permutability of the generated inference rules.
+\[
+\begin{array}{@{}c@{}c@{}c@{}c@{}c@{}}
+\cdots\scoal\quad
+	\vc{\begin{tikzpicture}[net]
+		\formula[y=1]{\forall*{x.}\exists*{y.}{\dual P}*\xy}
+		\formula[y=0]{\exists*{z.}P*\zs\*P*\zt}
+		\Vlink[violet,r,label={$~~\scriptstyle[x/z]$}]{2,3}
+	\end{tikzpicture}}
+	\hfill\hfill
+& \scoal &
+	\vc{\begin{tikzpicture}[net]
+		\formula[y=1]{\forall*{x.}\exists*{y.}{\dual P}*\xy}
+		\formula[y=0]{\exists*{z.}P*\zs\*P*\zt}
+		\Vlink[violet]{2,1}
+	\end{tikzpicture}}
+& \scoal &
+	\vc{\begin{tikzpicture}[net]
+		\formula[y=1]{\forall*{x.}\exists*{y.}{\dual P}*\xy}
+		\formula[y=0]{\exists*{z.}P*\zs\*P*\zt}
+		\Vlink[violet]{1,1}
+	\end{tikzpicture}}
+\\ \\
+\scriptsize
+	\color{white}\infer{\dual P}{\infer{\dual P}{
+	\color{violet}
+	 \infer[\Qrr*]{\seq{\exists y.\dual P\xy}{P\xs\*P\xt}}{
+	  \color{black}\infer{\seq{\exists y.\dual P\xy}{P\xs}}{\infer{\seq{\dual P\xs}{P\xs}}{}}
+	  &
+	  \color{black}\infer{\seq{\exists y.\dual P\xy}{P\xt}}{\infer{\seq{\dual P\xt}{P\xt}}{}}
+	 }
+	}}
+& \hspace*{28pt} &
+\scriptsize
+	\color{white}\infer{\dual P}{
+	\color{violet}
+ 	\infer[\Qrr?x]{\seq{\exists y.\dual P\xy}{\exists z.P\zs\*P\zt}}{
+	 \color{black}
+	 \infer{\seq{\exists y.\dual P\xy}{P\xs\*P\xt}}{
+	  \infer{\seq{\exists y.\dual P\xy}{P\xs}}{\infer{\seq{\dual P\xs}{P\xs}}{}}
+	  &
+	  \infer{\seq{\exists y.\dual P\xy}{P\xt}}{\infer{\seq{\dual P\xt}{P\xt}}{}}
+	}}
+	}
+& \hspace*{28pt} &
+\scriptsize
+	\color{violet}
+	\infer[\Qrr!]{\seq{\forall x.\exists y.\dual P\xy}{\exists z.P\zs\*P\zt}}{
+	 \color{black}
+ 	 \infer{\seq{\exists y.\dual P\xy}{\exists z.P\zs\*P\zt}}{
+	  \infer{\seq{\exists y.\dual P\xy}{P\xs\*P\xt}}{
+	   \infer{\seq{\exists y.\dual P\xy}{P\xs}}{\infer{\seq{\dual P\xs}{P\xs}}{}}
+	   &
+	   \infer{\seq{\exists y.\dual P\xy}{P\xt}}{\infer{\seq{\dual P\xt}{P\xt}}{}}
+	}}}
 \end{array}
 \]
-\caption{A coalescence and sequentialization example}
-\label{fig:main example}
-\end{figure}
-
-% ..................................................
-% ..................................................
-
-\begin{figure}[!t]
-\[
-\vc{\begin{tikzpicture}[net]
-	\formula[y=1.2]{{\dual P}*{(x,x)}}
-	\formula[y=0]{P*{(y,s)}\*P*{(t,z)}}
+The final steps introduce an inference $\exists R,x$ and one $\forall R$.
+For the latter, we require that the \emph{eigenvariable} $x$ of the universal quantification does not occur in the range of the substitution of the link, as in $[x/z]$ in the net above left---hence the two steps could not be interchanged.
+It corresponds to the \emph{eigenvariable condition} on the $\forall R$ rule that $x$ is not free in the context.
+
+Unifying coalescence, for unification nets, is similar to strict coalescence; two differences allow it to reconstruct witnesses by unification, which we illustrate.
+To initialize coalescence, the links in the net below left are given, as a substitution map, the \defn{most general unifier} of the two propositions connected by the link.
+Both links now correspond to sequent axioms.
+\[
+\hspace*{-\parindent}
+\hspace*{\fill}
+\begin{array}{@{}ccccc@{}}
+    \vc{\begin{tikzpicture}[net]
+    	\formula[y=1]{{\dual P}*{xx}}
+    	\formula[y=0]{P*{ys}\*P*{tz}}
     	\Vlink[red]{[-2]1,1}
@@
     \end{tikzpicture}}
-\quad\ucoal\quad
-\vc{\begin{tikzpicture}[net]
-	\formula[y=1.2]{{\dual P}*{(x,x)}}
-	\formula[y=0]{P*{(y,s)}\*P*{(t,z)}}
+&\ucoal& 
+    \vc{\begin{tikzpicture}[net]
+    	\formula[y=1]{{\dual P}*{xx}}
+    	\formula[y=0]{P*{ys}\*P*{tz}}
     	\Vlink[red,l,label={$\scriptstyle[s/y,s/x]$~~}]{[-2]1,1}
@@
     \end{tikzpicture}}
-\quad\stackrel{\urr*}\ucoal\quad
-\vc{\begin{tikzpicture}[net]
-	\formula[y=1.2]{{\dual P}*{(x,x)}}
-	\formula[y=0]{P*{(y,s)}\*P*{(t,z)}}
+&\ucoal& 
+    \vc{\begin{tikzpicture}[net]
+    	\formula[y=1]{{\dual P}*{xx}}
+    	\formula[y=0]{P*{ys}\*P*{tz}}
     	\Vlink[violet,r,label={~~$\scriptstyle[u/z,u/y,u/x]$}]{1,2}
     \end{tikzpicture}}
-\]
-\caption{Coalescence with unification; $u$ is the smallest term unifying $s$ and $t$} 
-\label{fig:unification example}
-\end{figure}
-
-% ..................................................
-
-Coalescence~\cite{Heijltjes-Hughes-2015,Hughes-Heijltjes-2016}, like multiplicative contractibility, \cite{Danos-1990,Guerrini-Masini-2001} is effectively top-down sequentialization.
-Figure~\ref{fig:main example} illustrates the process.
-In the example, a link between subformulas $A$ and $B$ carrying a substitution $\sigma$ represents a sequent $\seq{A\sigma}{B\sigma}$.
-Each coalescence step ($\star S$) corresponds to a proof rule ($\star R$), by which the coalescence sequence generates the sequent proof from the axioms down to the conclusion.
-
-In unification nets, existential witnesses are reconstructed during coalescence.
-The initial substitution map assigned to a link on atomic formulas $a=P(s_1,\dots,s_n)$ and $b=\dual P(t_1,\dots,t_n)$ is the most general unifier (\mgu) of $a$ and $\dual b$ (the first step in Figure~\ref{fig:unification example}).
-Coalescence then proceeds as for witness nets, except when joining two links from different slices with a product step (marked \hbox{\small$\;\urr*\;$} in Figure~\ref{fig:unification example}).
-Here, witness nets require both links to carry the same substitution, while for unification nets a common, more general map is generated by unification.\looseness=-1
+\\ \\
+&\qquad\qquad&
+\scriptsize
+	\color{white}
+	 \infer{\vphantom{\dual P}}{
+	  \color{red}\infer{\seq{\dual Pss}{Pss}}{}
+       &&
+	  \color{blue}\infer{\seq{\dual Ptt}{Ptt}}{}
+	 }
+&\qquad\qquad&
+\scriptsize
+	\color{violet}
+	 \infer[\!\Qrr*]{\seq{\dual Puu}{Puu\*Puu}}{
+	  \color{black}\infer{\seq{\dual Puu}{Puu}}{}
+       &&
+	  \color{black}\infer{\seq{\dual Puu}{Puu}}{}
+	 }
+\end{array}
+\hfill
+\]
+The second difference is the coalescence step for additive conjunction, above right.
+Where strict coalescence requires both links to carry identical substitution maps, here we require both maps to be \emph{unifyable}, in the sense that both must have a common, more special (less general) substitution map.
+This is then applied to the new link.
+In the example, the terms $s$ and $t$ are unified to $u$, i.e.\ $u$ is a most general term that specializes both $s$ and $t$.
+Note that in the sequentialization, both subproofs also need to be specialized, from $s$ and $t$ to $u$.
+
+% ..................................................
+%
+%\begin{figure}[!t]
+%\[
+%\begin{array}{c}
+%\begin{array}{@{}c@{~}c@{\qquad}c@{}}
+%  \vc{
+%  \begin{tikzpicture}[net]
+%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+%	\Vlink[red,l,label={$\scriptstyle[f(x)/y\,,\,x/z]$~~}]{3,2}
+%	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
+%  \end{tikzpicture}}
+%&&
+%  \vc{
+%  \begin{tikzpicture}[net]
+%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+%	\Vlink[violet,l,label={$\scriptstyle\varnothing$~~}]{1,1}
+%  \end{tikzpicture}} 
+%\\ \\[-5pt] \downarrow\scriptstyle{\srr+1} && \uparrow\scriptstyle\srr! \\ \\[-5pt]
+%  \vc{
+%  \begin{tikzpicture}[net]
+%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+%	\Vlink[red,l,label={$\scriptstyle[f(x)/y\,,\,x/z]$~~~}]{4,2}
+%	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
+%  \end{tikzpicture}}
+%&&
+%  \vc{
+%  \begin{tikzpicture}[net]
+%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+%	\Vlink[violet,l,label={$\scriptstyle\varnothing$~~}]{2,1}
+%  \end{tikzpicture}} 
+%\\ \\[-5pt] \downarrow\scriptstyle\srr?,f(x) && \uparrow\scriptstyle\srr?,x \\ \\[-5pt]  
+%  \vc{
+%  \begin{tikzpicture}[net]
+%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+%	\Vlink[red,l,label={$\scriptstyle[x/z]$~~}]{2,2}
+%	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
+%  \end{tikzpicture}} 
+%&&  
+%  \vc{
+%  \begin{tikzpicture}[net]
+%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+%	\Vlink[violet,l,label={$\scriptstyle[x/z]$~~~}]{[2]2,3}
+%  \end{tikzpicture}}
+%\\ \\[-5pt] \downarrow\scriptstyle{\srr+2} && \uparrow\scriptstyle\srr* \\ \\[-5pt]
+%  \vc{
+%  \begin{tikzpicture}[net]
+%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+%	\Vlink[red,l,label={$\scriptstyle[x/z]$~~}]{2,2}
+%	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{4,4}
+%  \end{tikzpicture}}
+%& \stackrel{\srr?,t}\scoal & 
+%  \vc{
+%  \begin{tikzpicture}[net]
+%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
+%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
+%	\Vlink[red,l,label={$\scriptstyle[x/z]$~~}]{2,2}
+%	\Vlink[blue,r,label={~~~$\scriptstyle[x/z]$}]{[4]2,4}
+%  \end{tikzpicture}}
+%\end{array}
+%\\ \\[20pt]
+%	\color{violet}\infer[\color{black}\Qrr!]{\color{black}\Seq{\forall x.\exists y.\dual P(y)\+\dual Q(x,y)}{\exists z.P(f(z))\*Q(z,t)}}{
+%	 \color{violet}\infer[\color{black}\Qrr?x]{\color{black}\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{\exists z.P(f(z))\*Q(z,t)}}{
+%	  \color{violet}\infer[\color{black}\Qrr*]{\color{black}\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{P(f(x))\*Q(x,t)}}{
+%	   \color{red}\infer[\color{black}\Qrr?{f(x)}]{\color{black}\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{P(f(x))}}{
+%	    \color{red}\infer[\color{black}\Qrr+1]{\color{black}\Seq{\dual P(f(x))\+\dual Q(x,f(x))}{P(f(x))}}{
+%	     \color{red}\infer[\color{black}\Qrr1]{\color{black}\Seq{\dual P(f(x))}{P(f(x))}}{}
+%	   }}&
+%	   \color{blue}\infer[\color{black}\Qrr?t]{\color{black}\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{Q(x,t)}}{
+%	    \color{blue}\infer[\color{black}\Qrr+2]{\color{black}\Seq{\dual P(t)\+\dual Q(x,t)}{Q(x,t)}}{
+%	     \color{blue}\infer[\color{black}\Qrr1]{\color{black}\Seq{\dual Q(x,t)}{Q(x,t)}}{}
+%	}}}}}
+%\end{array}
+%\]
+%\caption{A coalescence and sequentialization example}
+%\label{fig:main example}
+%\end{figure}
+
+% ..................................................
+% ..................................................
+
+%\begin{figure}[!t]
+%
+%\caption{Coalescence with unification; $u$ is the smallest term unifying $s$ and $t$} 
+%\label{fig:unification example}
+%\end{figure}
+
+% ..................................................
 
@@
 
-Additive linear logic is combinatorially rich, yet well-behaved and tractable: proof search \cite{Galmiche-Marion-1995,Galmiche-2000} and proof net correctness \cite{Heijltjes-Hughes-2015} are linear in $|A|\times|B|$ (with $|A|$ the size of the syntax tree of $A$); proof nets remain canonical and equally tractable when extended with the two units \cite{Heijltjes-2011,Heijltjes-Hughes-2015}; and the first-order case is merely NP-complete \cite{Heijltjes-Hughes-2015}.
+Additive linear logic is combinatorially rich, yet well-behaved and tractable: proof search \cite{Galmiche-Marion-1995,Galmiche-2000} and proof net correctness \cite{Heijltjes-Hughes-2015} for a net over $\seq AB$ are linear in $|A|\times|B|$ (with $|A|$ the size of the syntax tree of $A$).
+Proof nets remain canonical and equally tractable when extended with the two units \cite{Heijltjes-2011,Heijltjes-Hughes-2015}, and the first-order case is merely NP-complete \cite{Heijltjes-Hughes-2015}.
 
@@
 To prepare the ground for the cut elimination of first-order \emph{combinatorial proofs} is one motivation for the current presentation.
+
+\subsection{Proof identity}
+
+At the heart of a theory of proof nets is the question of \emph{proof identity}: when are two proofs equivalent?
+The answer determines which proofs should map onto the same proof net.
+The introduction of quantifiers creates an interesting issue: if two proofs differ by an immaterial choice of existential witness, should they be equivalent?
+For example, to prove the sequent $\seq{\exists x.P(x)}{\exists y.\dual P(y)}$ both quantifiers must receive \emph{the same} witness, as in the following two proofs, but \emph{any} witness will do.
+\[
+	\vc{\infer={\seq{\exists x.P(x)}{\exists y.\dual P(y)}}{\infer{\seq{P(s)}{\dual P(s)}}{}}}
+	\quad
+	\stackrel?\equiv
+	\quad
+	\vc{\infer={\seq{\exists x.P(x)}{\exists y.\dual P(y)}}{\infer{\seq{P(t)}{\dual P(t)}}{}}}
+\]
+The issue is more pronounced where quantifiers are \emph{vacuous}, $\exists x.A$ where $x$ is not free in $A$.
+The proofs below left can only be distinguished even syntactically because the $\exists R$-rule makes the instantiating witness explicit.
+Below right is an interesting intermediate variant: the witness $s$ or $t$ can be observed without explicit annotation in the $\exists R$-rule, but the choice is equally immaterial to the content of the proof as when the quantifier were vacuous.
+\[
+	\vc{\infer[\!\!\scriptstyle{\qrr?s}]{\seq{\exists x.P}{\dual P}}{\infer{\seq P{\dual P}}{}}}
+	\quad
+	\stackrel?\equiv
+	\quad	
+	\vc{\infer[\!\!\scriptstyle{\qrr?t}]{\seq{\exists x.P}{\dual P}}{\infer{\seq P{\dual P}}{}}}\qquad
+	\vc{
+	 \infer[\!\!\scriptstyle{\qrr?s}]{\seq{\exists x.P\+Q(x)}{\dual P}}{
+	  \infer[\!\!\scriptstyle{\qrr+1}]{\seq{P\+Q(s)}{\dual P}}{\infer{\seq P{\dual P}}{}}
+	}}
+	\quad
+	\stackrel?\equiv
+	\quad	
+	\vc{
+	 \infer[\!\!\scriptstyle{\qrr?t}]{\seq{\exists x.P\+Q(x)}{\dual P}}{
+	  \infer[\!\!\scriptstyle{\qrr+1}]{\seq{P\+Q(t)}{\dual P}}{\infer{\seq P{\dual P}}{}}
+	}}
+\]
+In this paper we will not attempt to settle the question of proof identity.
+Rather, our two notions of proof net each represent a natural and coherent perspective, at either end of the spectrum.
+\emph{Witness nets} make all existential witnesses explicit, including those to vacuous quantifiers, rejecting all three equivalences above.
+\emph{Unification nets} leave all witnesses implicit, thus identifying all proofs modulo witness assignment, and validating all three equivalences.
 
@@
 
-\subsection{Proof identity}
-
-At the heart of a theory of proof nets is the question of \emph{proof identity}: when are two proofs equivalent?
-The answer determines which proofs should map onto the same proof net.
-The introduction of quantifiers creates an interesting issue: if two proofs differ by an immaterial choice of existential witness, should they be equivalent?
-For example, to prove the sequent $\seq{\exists x.P(x)}{\exists y.\dual P(y)}$ both quantifiers must receive \emph{the same} witness, as in the following two proofs, but any witness will do.
-\[
-	\vc{\infer={\seq{\exists x.P(x)}{\exists y.\dual P(y)}}{\infer{\seq{P(s)}{\dual P(s)}}{}}}
-	\quad
-	\stackrel?\equiv
-	\quad
-	\vc{\infer={\seq{\exists x.P(x)}{\exists y.\dual P(y)}}{\infer{\seq{P(t)}{\dual P(t)}}{}}}
-\]
-The issue is more pronounced where quantifiers are \emph{vacuous}, $\exists x.A$ where $x$ is not free in $A$.
-The proofs below left can only be distinguished even syntactically because the $\exists R$-rule makes the instantiating witness explicit.
-Below right is an interesting intermediate variant: the witness $s$ or $t$ can be observed without explicit annotation in the $\exists R$-rule, but the choice is equally immaterial to the content of the proof as when the quantifier were vacuous.
-\[
-	\vc{\infer[\!\!\scriptstyle{\qrr?s}]{\seq{\exists x.P}{\dual P}}{\infer{\seq P{\dual P}}{}}}
-	\quad
-	\stackrel?\equiv
-	\quad	
-	\vc{\infer[\!\!\scriptstyle{\qrr?t}]{\seq{\exists x.P}{\dual P}}{\infer{\seq P{\dual P}}{}}}\qquad
-	\vc{
-	 \infer[\!\!\scriptstyle{\qrr?s}]{\seq{\exists x.P\+Q(x)}{\dual P}}{
-	  \infer[\!\!\scriptstyle{\qrr+1}]{\seq{P\+Q(s)}{\dual P}}{\infer{\seq P{\dual P}}{}}
-	}}
-	\quad
-	\stackrel?\equiv
-	\quad	
-	\vc{
-	 \infer[\!\!\scriptstyle{\qrr?t}]{\seq{\exists x.P\+Q(x)}{\dual P}}{
-	  \infer[\!\!\scriptstyle{\qrr+1}]{\seq{P\+Q(t)}{\dual P}}{\infer{\seq P{\dual P}}{}}
-	}}
-\]
-In this paper we will not attempt to settle the question of proof identity.
-Rather, our two notions of proof net each represent a natural and coherent perspective, at either end of the spectrum.
-\emph{Witness nets} make all existential witnesses explicit, including those to vacuous quantifiers, rejecting all three equivalences above.
-\emph{Unification nets} leave all witnesses implicit, thus identifying all proofs modulo witness assignment, and validating all three equivalences.
-
 %$\seq{\,\exists x.P(x,x,s)\,}{\,\exists y.\dual P(t,y,y)}$
@@
 %
-For an example, we refer to Figure~\ref{fig:main example}: the de-sequentialization of the sequent proof is the first pre-net of the coalescence sequence.
+For an example, we refer to the introduction.
 
@@
 	}}
-\end{align*}
-%\\ \\[-8pt]
-\begin{align*}
+%\end{align*}
+\\ \\[-8pt]
+%\begin{align*}
 \tag{$\srr?$}
@@
 
-For an example of coalescence, see Figure~\ref{fig:main example} in the introduction.
+For an example of coalescence, see the introduction.
 
@@
 In the above definition, note that $\lambda_\star^\star=(\lambda_\star)^*$ is the initial proof labelling of $\lambda_\star$, which assigns an axiom rule to each axiom link.
-For a minimal example, see Figure~\ref{fig:unification example} in the introduction.
+For a minimal example, see the introduction.
 Observe also that unifying coalescence includes strict coalescence, $(\scoal)\subseteq(\ucoal)$.
@@
 \\\hline
-   Canonicity & \xmark & \vmark^\ast & \vmark & \vmark
+   Canonicity & \xmark & \vmark$^\ast$ & \vmark & \vmark
 \\ Generality & \xmark &\xmark&\xmark& \vmark
@@
 \\ Coalescence & ? & ? & \vmark & \vmark
-\\ Slicing &\vmark &\vmark^\ast& \vmark & ?
+\\ Slicing &\vmark &\vmark$^\ast$& \vmark & ?
 \end{tabular}  

### 2018-04-21 ALL1.tex
final?

@@
 
+In this paper we present proof nets for first-order additive linear logic (\all1).
+Our central challenge is to incorporate the essential content of first-order proof, the \defn{witness assignment} to existential quantifiers, into additive proof nets.
+In a standard approach, as in the sequent calculus rules below left, a witness to $\exists x.B$ is assigned by an immediate substitution $B[t/x]$.
+To assign different witnesses in different branches of a proof, the subformula may be duplicated first, giving $B[s/x]$ and $B[t/x]$, as below right.
+%
+\[
+\hspace*{\fill}
+\hspace*{-\parindent}
+	\vc{\infer[\Qrr?t]{\seq A{\exists x.B}}{\seq A{B[t/x]}}}
+%\qquad
+%	\vc{\infer[\Qrr!~(x\,\notin\,\fv(A))]{\seq A{\forall x.B}}{\seq AB}}
+\qquad\quad
+\vc{
+	\infer[\Qrr*]{\Seq{\exists x.\dual P(x)}{P(s)\*P(t)}}{
+	 \infer[\Qrr?s]{\Seq{\exists x.\dual P(x)}{P(s)}}{\infer{\Seq{\dual P(s)}{P(s)}}{}}
+	 &&
+	 \infer[\Qrr?t]{\Seq{\exists x.\dual P(x)}{P(t)}}{\infer{\Seq{\dual P(t)}{P(t)}}{}}
+   }}
+\hfill
+\]
+%
+This is incompatible with a \defn{sequent + links} proof net design, where the conclusion sequent remains intact, and a subformula $B$ cannot be the subject of substitution or duplication.
+Instead, we propose two alternative treatments of witnessing terms, embodied in two notions of proof net: \defn{witness nets} and \defn{unification nets}.
+Our solutions are based on the second author's recent \defn{unification nets} for first-order multiplicative linear logic \cite{Hughes-2018}.
+Their main feature is to omit existential witnesses altogether, and reconstruct them by unification.
+%
+\[
+\hspace*{\fill}
+\hspace*{-\parindent}
+\begin{array}{c@{\qquad\qquad\qquad\qquad\qquad}c}
+	\vc{\begin{tikzpicture}[net]
+		\formula[y=1.2]{\exists x.{\dual P}(x)}
+		\formula[y=0]{P(s)\*P(t)}
+		\Vlink[red,l,label={$\scriptstyle[s/x]~~$}]{[-3]4,1}
+		\Vlink[red,r,label={$~\scriptstyle[t/x]$}]{[1]4,6}
+	\end{tikzpicture}}
+&
+	\vc{\begin{tikzpicture}[net]
+		\formula[y=1.2]{\exists x.{\dual P}(x)}
+		\formula[y=0]{P(s)\*P(t)}
+		\Vlink[red]{[-3]4,1}
+		\Vlink[red]{[1]4,6}
+	\end{tikzpicture}}
+\\ \\[-5pt]
+	\text{\small a witness net}
+&	\text{\small a unification net}
+\end{array}
+\hfill
+\]
+
+\defn{Witness nets} record witness assignment in substitution maps attached to each link.
+The example above left shows the proof net for the sequent proof above.
+(We will assume a different variable for each quantifier, and we attach links to predicate letters, as the root connective of an atomic proposition.) Witness nets are canonical for \all1 sequent calculus permutations.
+Composition is direct, where the witness assignments of links are composed through a simple process of \emph{interaction + hiding} similar to that of game semantics \cite{Mimram-2011}.
+
+\defn{Unification nets} omit any witness information, as illustrated above right.
+In addition to canonicity, they embody a notion of \defn{generality}: where more than one witness could be assigned, unification nets do not require a definite choice, while witness nets do.
+Composition is direct, by straightforward relational composition.
+We compare further properties in Figure~\ref{fig:results}, in the conclusion, where we also discuss related work.
+
+\subsection{Background}
+
+Additive linear logic is combinatorially rich, yet well-behaved and tractable: proof search \cite{Galmiche-Marion-1995,Galmiche-2000} and proof net correctness \cite{Heijltjes-Hughes-2015} for a net over $\seq AB$ are linear in $|A|\times|B|$ (with $|A|$ the size of the syntax tree of $A$).
+Proof nets remain canonical and equally tractable when extended with the two units \cite{Heijltjes-2011,Heijltjes-Hughes-2015}, and the first-order case is merely NP-complete \cite{Heijltjes-Hughes-2015}.
+
+At the same time, the ubiquity of its main operations, product and sum, mean the ideas and results it garners are widely applicable.
+It serves as a microcosmos for important ideas and observations: it fostered the \emph{connections method} of proof search \cite{Galmiche-2000}; it demonstrated the \emph{Blass problem} \cite{Abramsky-2003} of game semantics, that sequential strategies do not in general have associative composition; and it is at the root of the study of fixed points in linear logic \cite{Santocanale-2002a}.
+The logic describes two-way communication~\cite{Cockett-Santocanale-2009}, and is a core part of \emph{session types}~\cite{Honda-1993}.
+
+{\all} is of course part of {\mall} (multiplicative-additive linear logic), and its lessons are clearly visible in the second author's canonical proof nets \cite{Hughes-vanGlabbeek-2005} for {\mall}, as well as the first and second author's locally canonical \emph{conflict nets}~\cite{Hughes-Heijltjes-2016}.
+Its proof nets also appear as the \emph{skew fibrations} in the second author's \emph{combinatorial proofs} for classical logic~\cite{Hughes-2006-proofs}, and in the third author's study of the \emph{medial rule} for classical logic~\cite{str:RTA07}.
+To prepare the ground for the cut elimination of first-order \emph{combinatorial proofs} is one motivation for the current presentation.
+
+\subsection{Proof identity}
+
+At the heart of a theory of proof nets is the question of \emph{proof identity}: when are two proofs equivalent?
+The answer determines which proofs should map onto the same proof net.
+The introduction of quantifiers creates an interesting issue: if two proofs differ by an immaterial choice of existential witness, should they be equivalent?
+For example, to prove the sequent $\seq{\exists x.P(x)}{\exists y.\dual P(y)}$ both quantifiers must receive \emph{the same} witness, as in the following two proofs, but \emph{any} witness will do.
+\[
+	\vc{\infer={\seq{\exists x.P(x)}{\exists y.\dual P(y)}}{\infer{\seq{P(s)}{\dual P(s)}}{}}}
+	\quad
+	\stackrel?\equiv
+	\quad
+	\vc{\infer={\seq{\exists x.P(x)}{\exists y.\dual P(y)}}{\infer{\seq{P(t)}{\dual P(t)}}{}}}
+\]
+The issue is more pronounced where quantifiers are \emph{vacuous}, $\exists x.A$ where $x$ is not free in $A$.
+The proofs below left can only be distinguished even syntactically because the $\exists R$-rule makes the instantiating witness explicit.
+Below right is an interesting intermediate variant: the witness $s$ or $t$ can be observed without explicit annotation in the $\exists R$-rule, but the choice is equally immaterial to the content of the proof as when the quantifier were vacuous.
+\[
+	\vc{\infer[\!\!\scriptstyle{\qrr?s}]{\seq{\exists x.P}{\dual P}}{\infer{\seq P{\dual P}}{}}}
+	\quad
+	\stackrel?\equiv
+	\quad	
+	\vc{\infer[\!\!\scriptstyle{\qrr?t}]{\seq{\exists x.P}{\dual P}}{\infer{\seq P{\dual P}}{}}}\qquad
+	\vc{
+	 \infer[\!\!\scriptstyle{\qrr?s}]{\seq{\exists x.P\+Q(x)}{\dual P}}{
+	  \infer[\!\!\scriptstyle{\qrr+1}]{\seq{P\+Q(s)}{\dual P}}{\infer{\seq P{\dual P}}{}}
+	}}
+	\quad
+	\stackrel?\equiv
+	\quad	
+	\vc{
+	 \infer[\!\!\scriptstyle{\qrr?t}]{\seq{\exists x.P\+Q(x)}{\dual P}}{
+	  \infer[\!\!\scriptstyle{\qrr+1}]{\seq{P\+Q(t)}{\dual P}}{\infer{\seq P{\dual P}}{}}
+	}}
+\]
+In this paper we will not attempt to settle the question of proof identity.
+Rather, our two notions of proof net each represent a natural and coherent perspective, at either end of the spectrum.
+\emph{Witness nets} make all existential witnesses explicit, including those to vacuous quantifiers, rejecting all three equivalences above.
+\emph{Unification nets} leave all witnesses implicit, thus identifying all proofs modulo witness assignment, and validating all three equivalences.
+
+\subsection{Correctness: coalescence and slicing}
+
 Additive proof nets have two natural correctness criteria.
-\defn{Coalescence} \cite{Heijltjes-Hughes-2015,Hughes-Heijltjes-2016}, a counterpart to multiplicative \emph{contractibility} \cite{Danos-1990}, provides efficient correctness and sequentialization via local rewriting: it asks that the steps below left result in a single link, connecting both formulas.
+\defn{Coalescence} \cite{Heijltjes-Hughes-2015,Hughes-Heijltjes-2016}, a counterpart to multiplicative \emph{contractibility} \cite{Danos-1990,Guerrini-Masini-2001}, provides efficient correctness and sequentialization via local rewriting: it asks that the steps below left result in a single link, connecting both formulas.
 \defn{Slicing} \cite{Hughes-vanGlabbeek-2005} is a global, geometric criterion: it asks that each \defn{slice}, a choice to remove one subformula of each product along with all connected links, retains a single link.
@@
 \]
-
-%In this paper we extend additive proof nets with first-order quantification. 
-In this paper we present proof nets for first-order additive linear logic (\all1).
-Our central challenge is to incorporate the essential content of first-order proof, the \defn{witness assignment} to existential quantifiers, into additive proof nets, while retaining their features and tools: canonicity, direct (relational) composition, coalescence, and slicing.
-
-In a standard approach, as in the sequent calculus rules below left, a witness to $\exists x.B$ is assigned by an immediate substitution $B[t/x]$.
-To assign different witnesses in different slices, the subformula may be duplicated first, giving $B[s/x]$ and $B[t/x]$, as below right.
-%
-\[
-\hspace*{\fill}
-\hspace*{-\parindent}
-	\vc{\infer[\Qrr?t]{\seq A{\exists x.B}}{\seq A{B[t/x]}}}
-\qquad
-	\vc{\infer[\Qrr!~(x\,\notin\,\fv(A))]{\seq A{\forall x.B}}{\seq AB}}
-\qquad\quad
-\vc{
-	\infer[\Qrr*]{\Seq{\exists x.\dual P(x)}{P(s)\*P(t)}}{
-	 \infer[\Qrr?s]{\Seq{\exists x.\dual P(x)}{P(s)}}{\infer{\Seq{\dual P(s)}{P(s)}}{}}
-	 &&
-	 \infer[\Qrr?t]{\Seq{\exists x.\dual P(x)}{P(t)}}{\infer{\Seq{\dual P(t)}{P(t)}}{}}
-   }}
-\hfill
-\]
-%
-This is incompatible with a \defn{sequent + links} proof net design, where the conclusion sequent remains intact, and a subformula $B$ cannot be the subject of substitution or duplication.
-Instead, we propose two alternative treatments of witnessing terms, embodied in two notions of proof net: \defn{witness nets} and \defn{unification nets}.
-% irrecoverably alters the subformula $B$ (since $B[t/x]$ may contain other occurrences of $t$, it is not possible to recover $B$)
-%
-Our solutions are based on the second author's recent \defn{unification nets} for first-order multiplicative linear logic \cite{Hughes-2018}.
-Their main feature is to omit existential witnesses altogether, and reconstruct them by unification.
-%
-\[
-\hspace*{\fill}
-\hspace*{-\parindent}
-\begin{array}{c@{\qquad\qquad\qquad\qquad\qquad}c}
-	\vc{\begin{tikzpicture}[net]
-		\formula[y=1.2]{\exists x.{\dual P}(x)}
-		\formula[y=0]{P(s)\*P(t)}
-		\Vlink[red,l,label={$\scriptstyle[s/x]~~$}]{[-3]4,1}
-		\Vlink[red,r,label={$~\scriptstyle[t/x]$}]{[1]4,6}
-	\end{tikzpicture}}
-&
-	\vc{\begin{tikzpicture}[net]
-		\formula[y=1.2]{\exists x.{\dual P}(x)}
-		\formula[y=0]{P(s)\*P(t)}
-		\Vlink[red]{[-3]4,1}
-		\Vlink[red]{[1]4,6}
-	\end{tikzpicture}}
-\\ \\[-5pt]
-	\text{\small a witness net}
-&	\text{\small a unification net}
-\end{array}
-\hfill
-\]
-
-\defn{Witness nets} record witness assignment in substitution maps attached to each link.
-The example above left shows the net corresponding to the sequent proof above.
-(We will assume a different variable for each quantifier, and we attach links to predicate letters, as the root connective of a propositional atom.) Witness nets are canonical for \all1 sequent calculus permutations, and we give two correctness criteria, one via coalescence and one via slicing.
-Composition is direct, where the witness assignments of links are composed through a simple process of \emph{interaction + hiding} similar to that of game semantics \cite{Mimram-2011}.
-
-\defn{Unification nets} omit any witness information, as illustrated above right.
-In addition to canonicity, they embody a notion of \defn{generality}: where more than one witness could be assigned, unification nets do not require a definite choice, while witness nets do.
-Composition remains by relational composition, and correctness is by coalescence.
-During this process witnesses are reconstructed by first-order unification.
-
-\defn{Coalescence}~\cite{Heijltjes-Hughes-2015,Hughes-Heijltjes-2016}, like multiplicative contractibility \cite{Danos-1990,Guerrini-Masini-2001}, is effectively top-down sequentialization.
+We extend slicing to witness nets, and coalescence to both witness nets and unification nets. Here, we illustrate the latter, and leave a discussion of slicing to the conclusion of the paper.
+
 We will distinguish \defn{strict coalescence} ($\scoal$) for witness nets and \defn{unifying coalescence} ($\ucoal$) for unification nets.
@@
 
-\subsection{Background}
-
-Additive linear logic is combinatorially rich, yet well-behaved and tractable: proof search \cite{Galmiche-Marion-1995,Galmiche-2000} and proof net correctness \cite{Heijltjes-Hughes-2015} for a net over $\seq AB$ are linear in $|A|\times|B|$ (with $|A|$ the size of the syntax tree of $A$).
-Proof nets remain canonical and equally tractable when extended with the two units \cite{Heijltjes-2011,Heijltjes-Hughes-2015}, and the first-order case is merely NP-complete \cite{Heijltjes-Hughes-2015}.
-
-At the same time, the ubiquity of its main operations, product and sum, mean the ideas and results it garners are widely applicable.
-It serves as a microcosmos for important ideas and observations: it fostered the \emph{connections method} of proof search \cite{Galmiche-2000}; it demonstrated the \emph{Blass problem} \cite{Abramsky-2003} of game semantics, that sequential strategies do not in general have associative composition; and it is at the root of the study of fixed points in linear logic \cite{Santocanale-2002a}.
-The logic describes two-way communication~\cite{Cockett-Santocanale-2009}, and is a core part of \emph{session types}~\cite{Honda-1993}.
-
-{\all} is of course part of {\mall} (multiplicative-additive linear logic), and its lessons are clearly visible in the second author's canonical proof nets \cite{Hughes-vanGlabbeek-2005} for {\mall}, as well as the first and second author's locally canonical \emph{conflict nets}~\cite{Hughes-Heijltjes-2016}.
-Its proof nets also appear as the \emph{skew fibrations} in the second author's \emph{combinatorial proofs} for classical logic~\cite{Hughes-2006-proofs}, and in the third author's study of the \emph{medial rule} for classical logic~\cite{str:RTA07}.
-To prepare the ground for the cut elimination of first-order \emph{combinatorial proofs} is one motivation for the current presentation.
-
-\subsection{Proof identity}
-
-At the heart of a theory of proof nets is the question of \emph{proof identity}: when are two proofs equivalent?
-The answer determines which proofs should map onto the same proof net.
-The introduction of quantifiers creates an interesting issue: if two proofs differ by an immaterial choice of existential witness, should they be equivalent?
-For example, to prove the sequent $\seq{\exists x.P(x)}{\exists y.\dual P(y)}$ both quantifiers must receive \emph{the same} witness, as in the following two proofs, but \emph{any} witness will do.
-\[
-	\vc{\infer={\seq{\exists x.P(x)}{\exists y.\dual P(y)}}{\infer{\seq{P(s)}{\dual P(s)}}{}}}
-	\quad
-	\stackrel?\equiv
-	\quad
-	\vc{\infer={\seq{\exists x.P(x)}{\exists y.\dual P(y)}}{\infer{\seq{P(t)}{\dual P(t)}}{}}}
-\]
-The issue is more pronounced where quantifiers are \emph{vacuous}, $\exists x.A$ where $x$ is not free in $A$.
-The proofs below left can only be distinguished even syntactically because the $\exists R$-rule makes the instantiating witness explicit.
-Below right is an interesting intermediate variant: the witness $s$ or $t$ can be observed without explicit annotation in the $\exists R$-rule, but the choice is equally immaterial to the content of the proof as when the quantifier were vacuous.
-\[
-	\vc{\infer[\!\!\scriptstyle{\qrr?s}]{\seq{\exists x.P}{\dual P}}{\infer{\seq P{\dual P}}{}}}
-	\quad
-	\stackrel?\equiv
-	\quad	
-	\vc{\infer[\!\!\scriptstyle{\qrr?t}]{\seq{\exists x.P}{\dual P}}{\infer{\seq P{\dual P}}{}}}\qquad
-	\vc{
-	 \infer[\!\!\scriptstyle{\qrr?s}]{\seq{\exists x.P\+Q(x)}{\dual P}}{
-	  \infer[\!\!\scriptstyle{\qrr+1}]{\seq{P\+Q(s)}{\dual P}}{\infer{\seq P{\dual P}}{}}
-	}}
-	\quad
-	\stackrel?\equiv
-	\quad	
-	\vc{
-	 \infer[\!\!\scriptstyle{\qrr?t}]{\seq{\exists x.P\+Q(x)}{\dual P}}{
-	  \infer[\!\!\scriptstyle{\qrr+1}]{\seq{P\+Q(t)}{\dual P}}{\infer{\seq P{\dual P}}{}}
-	}}
-\]
-In this paper we will not attempt to settle the question of proof identity.
-Rather, our two notions of proof net each represent a natural and coherent perspective, at either end of the spectrum.
-\emph{Witness nets} make all existential witnesses explicit, including those to vacuous quantifiers, rejecting all three equivalences above.
-\emph{Unification nets} leave all witnesses implicit, thus identifying all proofs modulo witness assignment, and validating all three equivalences.
-
 %Additive linear logic $(\all)$ is the logic of product $(\*)$ and sum $(\+)$, and their canonical morphisms: projections, injections, and diagonals.
@@
 % --------------------------------------------------
+%
+%\begin{figure}[!t]
+%\begin{center}
+%\begin{tabular}{lcccc}
+% &	Monomial nets & Expansion trees$^\ast$ & Witness nets & Unification nets
+%\\\hline
+%   Canonicity & \xmark & \vmark$^\ast$ & \vmark & \vmark
+%\\ Generality & \xmark &\xmark&\xmark& \vmark
+%\\ Direct composition &(\vmark) &\xmark& \vmark & \vmark
+%\\ Coalescence & ? & ? & \vmark & \vmark
+%\\ Slicing &\vmark &\vmark$^\ast$& \vmark & ?
+%\end{tabular}  
+%  \caption{Comparison of different notions of proof nets for quantifiers and additive connectives}
+%  \label{fig:results}
+%\end{center}
+%\end{figure}
 
@@
 \begin{center}
-\begin{tabular}{lcccc}
- &	Monomial nets & Expansion trees$^\ast$ & Witness nets & Unification nets
+\begin{tabular}{lccc}
+ &	Monomial nets & Witness nets & Unification nets
 \\\hline
-   Canonicity & \xmark & \vmark$^\ast$ & \vmark & \vmark
-\\ Generality & \xmark &\xmark&\xmark& \vmark
-\\ Direct composition &(\vmark) &\xmark& \vmark & \vmark
-\\ Coalescence & ? & ? & \vmark & \vmark
-\\ Slicing &\vmark &\vmark$^\ast$& \vmark & ?
+   Canonicity          &    ?   & \vmark & \vmark
+\\ Generality          & \xmark & \xmark & \vmark
+\\ Direct composition  & \xmark & \vmark & \vmark
+\\ Coalescence         &    ?   & \vmark & \vmark
+\\ Slicing             & \vmark & \vmark &   ?
 \end{tabular}  
@@
 
-%\subsection{Alternative approaches: monomial nets and expansion trees}
 We have presented two notions of first-order additive proof net, witness nets and unification nets, to canonically capture the two natural notions of proof identity for first-order additive linear logic.
-%
+The table in Figure~\ref{fig:results} summarizes the results of our paper, along with some observations we make below.
+
 Proof nets with additives and quantifiers existed before as \emph{monomial nets} \cite{Girard-1996}, where slices are managed explicitly with \emph{monomial weights}.
 These nets are not generally canonical: they admit the permutation (and duplication) of proof rules past implicit \emph{contractions}.
-%
-However, we do conjecture that additive monomial nets could be restricted to some notion of canonical form, which would be equivalent to the notion induced by \emph{expansion tree proofs}, provide another approach to first-order quantification for classical logic \cite{Miller-1987,Heijltjes-2010}.
-%
-But the details of this relation are clearly beyond the scope of our paper.
-
-%%\emph{Expansion trees} provide another approach to canonicity for first-order quantification for classical logic \cite{Miller-1987,Heijltjes-2010}.
-
-In the formulation of expansion trees, a formula $\exists x.A$ is interpreted as the sum (or classically, the \emph{disjunction}) over a fixed number of instantiations $A[t_1/x]\+\dots\+A[t_n/x]$.
+However, it is possible that additive monomial nets could be restricted to some notion of canonical form.
+Likewise, coalescence (or contractibility) has not been studied for first-order monomial nets, though it has been extended to a related form of MALL proof nets \cite{Maieli-2007}.
+
+Our slicing condition is closely related to a number of approaches to first-order classical logic.
+A formula $\exists x.A$ is interpreted as the sum (or classically, the \emph{disjunction}) over a fixed number of instantiations $A[t_1/x]\+\dots\+A[t_n/x]$.
 This can be traced back to Herbrand's Theorem \cite{Herbrand-1930}: $\exists x.A$ is equivalent to the infinite sum over $A[t/x]$ for all terms $t$ in the language, but for any given proof a finite set of terms suffices.
-%
-We used this idea implicitly for our geometric correctness condition for witness nets (Section~\ref{sec:correctness}), which generalizes the existing \emph{slice-based} criterion for multiplicative-additive proof nets \cite{Hughes-vanGlabbeek-2005}.
-In constructing the slices over a formula, we interpreted $\exists x.A$ by an \emph{expansion} $A[t_1/x]\+\dots\+A[t_n/x]$, where the witnesses $t_1$ through $t_n$ are collected from the substitution maps of the links in the proof net.
-
-However, for our definition of proof nets, we did not pursue this direction, and consider the choices made in this paper preferable.
-Witness nets and unification nets retain the original structure of \emph{formulas + links}, without requiring expansion trees.
-More importantly, as in the propositional case, they enable direct (non-inductive) composition by a relational composition of links.
-%
-%%Finally, available space does not permit a detailed exposition, which we defer to a journal version.
-%
-%We have presented two notions of first-order additive proof net, witness nets and unification nets, to canonically capture the two natural notions of proof identity for first-order additive linear logic.
-%
-The table in Figure~\ref{fig:results} summarizes the results of our paper and the observations in this section, where the column on expansion trees is speculative since they only exist for classical logic, and not (yet) exist for $\all$.
+\emph{Expansion tree proofs} \cite{Miller-1987,Heijltjes-2010} are a graphical proof formalism based on this idea.
+
+In our slicing condition, the witnesses $t_1,\dots,t_n$ for the expansion $A[t_1/x]\+\dots\+A[t_n/x]$ are collected from the substitutions recorded at the links of the proof net.
+Expansion trees, in contrast, record the expansion and its terms explicitly.
+This could be an interesting alternative approach to additive proof nets, which we will explore in future work.
+It is expected, though, that this would sacrifice \emph{generality} and \emph{direct composition}.
 

### 2018-08-07 ALL1.tex
addressing CSL referee comments

@@
 %
-%Additive linear logic $(\all)$ is the logic of product $(\*)$, sum $(\+)$, and their canonical morphisms: projections, injections, and diagonals.
-It is naturally captured in \defn{proof nets} \cite{Girard-1987,Hughes-vanGlabbeek-2005}, which describe a morphism $A\mathbin{\shortrightarrow}B$ by a sequent $\seq{\dual A}B$ plus a \defn{linking}, a relation between subformulas in $\dual A$ and in $B$.
-Proof nets are \defn{canonical}, factoring out the permutations of sequent calculus.
-%
-%Additive linear logic $(\all)$ is the logic of product $(\*)$ and sum $(\+)$.
-Proofs, over a two-sided sequent $A\vdash B$ or, here, a one-sided sequent $\seq{\dual A}B$, are built from the canonical morphisms: projections, injections, and diagonals.
-These are captured naturally in \emph{proof nets} \cite{Girard-1987,Hughes-vanGlabbeek-2005}, which consist of a set of \emph{links} between subformulas in $\dual A$ and in $B$, as illustrated below left.
 \[
 %\hspace*{9ex}% spacing hack to achieve central horizontal alignment
+% Behold my better spacing hack to achieve central horizontal alignment :)
 \hspace*{-\parindent}%
 \hspace*{\fill}%
-% Behold my better spacing hack to achieve central horizontal alignment :)
 \begin{array}{c@{\qquad\qquad}c}
@@
 	\vc{\infer[\Qrr?t]{\seq A{\exists x.B}}{\seq A{B[t/x]}}}
-%\qquad
-%	\vc{\infer[\Qrr!~(x\,\notin\,\fv(A))]{\seq A{\forall x.B}}{\seq AB}}
 \qquad\quad
@@
 In addition to canonicity, they embody a notion of \defn{generality}: where more than one witness could be assigned, unification nets do not require a definite choice, while witness nets do.
-Composition is direct, by straightforward relational composition.
-We compare further properties in Figure~\ref{fig:results}, in the conclusion, where we also discuss related work.
-
-\subsection{Background}
+Composition is direct, by relational composition.
+We compare further properties in Figure~\ref{fig:results} in the conclusion, where we also discuss related work and Lambek's notion of \defn{generality} \cite{Lambek-1968, Lambek-1969, Lambek-1972}.
+
+\paragraph*{Background}
 
@@
 
-\subsection{Proof identity}
+\paragraph*{Proof identity}
 
@@
 \]
-The issue is more pronounced where quantifiers are \emph{vacuous}, $\exists x.A$ where $x$ is not free in $A$.
+The issue is more pronounced where quantifiers are \emph{vacuous}, $\exists x.A$ with $x$ not free in $A$.
 The proofs below left can only be distinguished even syntactically because the $\exists R$-rule makes the instantiating witness explicit.
@@
 
-\subsection{Correctness: coalescence and slicing}
+\paragraph*{Correctness: coalescence and slicing}
 
@@
 \[
+\hspace*{-\parindent}
 \begin{array}{@{}c@{}c@{}c@{}c@{}c@{}}
@@
 \\ \\
-\scriptsize
+\text{\scriptsize
 	\color{white}
@@
 	  \color{blue}\infer{\seq{\dual P\xt}{P\xt}}{}
-	 }
-& \hspace*{32pt} &
-\scriptsize
+	 }}
+& \hspace*{26pt} &
+\text{\scriptsize
 	\color{red}\infer[\!\Qrr?s]{\seq{\exists y.\dual P\xy}{P\xs}}{\color{black}\infer{\seq{\dual P\xs}{P\xs}}{}}
 ~~
-	\color{white}\infer{\vphantom{\dual P}}{\color{blue}\infer{\seq{\dual P\xt}{P\xt}}{}}
-& \hspace*{32pt} &
-\scriptsize
+	\color{white}\infer{\vphantom{\dual P}}{\color{blue}\infer{\seq{\dual P\xt}{P\xt}}{}}}
+& \hspace*{26pt} &
+\text{\scriptsize
 	\color{red}\infer[\!\Qrr?s]{\seq{\exists y.\dual P\xy}{P\xs}}{\color{black}\infer{\seq{\dual P\xs}{P\xs}}{}}
 ~~
-	\color{blue}\infer[\!\Qrr?t]{\seq{\exists y.\dual P\xy}{P\xt}}{\color{black}\infer{\seq{\dual P\xt}{P\xt}}{}}
+	\color{blue}\infer[\!\Qrr?t]{\seq{\exists y.\dual P\xy}{P\xt}}{\color{black}\infer{\seq{\dual P\xt}{P\xt}}{}}}
 \end{array}
@@
 \\ \\
-\scriptsize
+\text{\scriptsize
 	\color{white}\infer{\dual P}{\infer{\dual P}{
@@
 	 }
-	}}
+	}}}
 & \hspace*{28pt} &
-\scriptsize
+\text{\scriptsize
 	\color{white}\infer{\dual P}{
@@
 	}}
-	}
+	}}
 & \hspace*{28pt} &
-\scriptsize
+\text{\scriptsize
 	\color{violet}
@@
 	   \infer{\seq{\exists y.\dual P\xy}{P\xt}}{\infer{\seq{\dual P\xt}{P\xt}}{}}
-	}}}
+	}}}}
 \end{array}
@@
 &\qquad\qquad&
-\scriptsize
+\text{\scriptsize
 	\color{white}
@@
 	  \color{blue}\infer{\seq{\dual Ptt}{Ptt}}{}
-	 }
+	 }}
 &\qquad\qquad&
-\scriptsize
+\text{\scriptsize
 	\color{violet}
@@
 	  \color{black}\infer{\seq{\dual Puu}{Puu}}{}
-	 }
+	 }}
 \end{array}
@@
 
-% ..................................................
-%
-%\begin{figure}[!t]
-%\[
-%\begin{array}{c}
-%\begin{array}{@{}c@{~}c@{\qquad}c@{}}
-%  \vc{
-%  \begin{tikzpicture}[net]
-%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-%	\Vlink[red,l,label={$\scriptstyle[f(x)/y\,,\,x/z]$~~}]{3,2}
-%	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
-%  \end{tikzpicture}}
-%&&
-%  \vc{
-%  \begin{tikzpicture}[net]
-%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-%	\Vlink[violet,l,label={$\scriptstyle\varnothing$~~}]{1,1}
-%  \end{tikzpicture}} 
-%\\ \\[-5pt] \downarrow\scriptstyle{\srr+1} && \uparrow\scriptstyle\srr! \\ \\[-5pt]
-%  \vc{
-%  \begin{tikzpicture}[net]
-%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-%	\Vlink[red,l,label={$\scriptstyle[f(x)/y\,,\,x/z]$~~~}]{4,2}
-%	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
-%  \end{tikzpicture}}
-%&&
-%  \vc{
-%  \begin{tikzpicture}[net]
-%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-%	\Vlink[violet,l,label={$\scriptstyle\varnothing$~~}]{2,1}
-%  \end{tikzpicture}} 
-%\\ \\[-5pt] \downarrow\scriptstyle\srr?,f(x) && \uparrow\scriptstyle\srr?,x \\ \\[-5pt]  
-%  \vc{
-%  \begin{tikzpicture}[net]
-%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-%	\Vlink[red,l,label={$\scriptstyle[x/z]$~~}]{2,2}
-%	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
-%  \end{tikzpicture}} 
-%&&  
-%  \vc{
-%  \begin{tikzpicture}[net]
-%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-%	\Vlink[violet,l,label={$\scriptstyle[x/z]$~~~}]{[2]2,3}
-%  \end{tikzpicture}}
-%\\ \\[-5pt] \downarrow\scriptstyle{\srr+2} && \uparrow\scriptstyle\srr* \\ \\[-5pt]
-%  \vc{
-%  \begin{tikzpicture}[net]
-%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-%	\Vlink[red,l,label={$\scriptstyle[x/z]$~~}]{2,2}
-%	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{4,4}
-%  \end{tikzpicture}}
-%& \stackrel{\srr?,t}\scoal & 
-%  \vc{
-%  \begin{tikzpicture}[net]
-%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-%	\Vlink[red,l,label={$\scriptstyle[x/z]$~~}]{2,2}
-%	\Vlink[blue,r,label={~~~$\scriptstyle[x/z]$}]{[4]2,4}
-%  \end{tikzpicture}}
-%\end{array}
-%\\ \\[20pt]
-%	\color{violet}\infer[\color{black}\Qrr!]{\color{black}\Seq{\forall x.\exists y.\dual P(y)\+\dual Q(x,y)}{\exists z.P(f(z))\*Q(z,t)}}{
-%	 \color{violet}\infer[\color{black}\Qrr?x]{\color{black}\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{\exists z.P(f(z))\*Q(z,t)}}{
-%	  \color{violet}\infer[\color{black}\Qrr*]{\color{black}\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{P(f(x))\*Q(x,t)}}{
-%	   \color{red}\infer[\color{black}\Qrr?{f(x)}]{\color{black}\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{P(f(x))}}{
-%	    \color{red}\infer[\color{black}\Qrr+1]{\color{black}\Seq{\dual P(f(x))\+\dual Q(x,f(x))}{P(f(x))}}{
-%	     \color{red}\infer[\color{black}\Qrr1]{\color{black}\Seq{\dual P(f(x))}{P(f(x))}}{}
-%	   }}&
-%	   \color{blue}\infer[\color{black}\Qrr?t]{\color{black}\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{Q(x,t)}}{
-%	    \color{blue}\infer[\color{black}\Qrr+2]{\color{black}\Seq{\dual P(t)\+\dual Q(x,t)}{Q(x,t)}}{
-%	     \color{blue}\infer[\color{black}\Qrr1]{\color{black}\Seq{\dual Q(x,t)}{Q(x,t)}}{}
-%	}}}}}
-%\end{array}
-%\]
-%\caption{A coalescence and sequentialization example}
-%\label{fig:main example}
-%\end{figure}
-
-% ..................................................
-% ..................................................
-
-%\begin{figure}[!t]
-%
-%\caption{Coalescence with unification; $u$ is the smallest term unifying $s$ and $t$} 
-%\label{fig:unification example}
-%\end{figure}
-
-% ..................................................
-
-%As illustrated by Herbrand's Theorem \cite{Herbrand-1930},
-
-%\[
-%\hspace*{\fill}%
-%\hspace*{-\parindent}%\hspace*{8ex}% spacing hack to achieve central horizontal alignment
-%\begin{tikzpicture}[net]
-%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-%	\Vlink[red,l,label={$\scriptstyle[f(x)/y\,,\,x/z]$~~}]{3,2}
-%	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
-%\end{tikzpicture}
-%\hspace*{16ex}
-%\begin{tikzpicture}[net]
-%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-%	\Vlink[red]{3,2}
-%	\Vlink[blue]{5,4}
-%\end{tikzpicture}
-%\hfill
-%\]
-%
-%Correctness and sequentialization for \all1 proof nets will be through \defn{coalescence}~\cite{Heijltjes-Hughes-2015,Hughes-Heijltjes-2016}, the additive counterpart to \defn{contractibility} for multiplicative linear logic~\cite{Danos-1990}.
-It is a simple graph rewrite relation that pushes links from the leaves towards the roots of a sequent,
-
-%We include the following results for our \all1 proof nets.
-Witness nets are \emph{canonical} for the permutations of the sequent calculus, and we provide a geometric correctness condition.
-\emph{Composition} of unification nets (over $\seq AB$ and $\seq{\dual BC}$ into one over $\seq AC$) is remarkedly simple, as the relational composition of both sets of links.
-For composition of witness nets, in addition
-%\end{document}
-
-%Additive linear logic $(\all)$ is the logic of product $(\*)$ and sum $(\+)$, and their canonical morphisms: projections, injections, and diagonals.
-It is captured naturally in \defn{additive proof nets} \cite{Girard-1987,Hughes-vanGlabbeek-2005}, consisting of a two-sided sequent $A\vdash B$ or, here, a one-sided sequent $\seq{\dual A}B$ plus a \defn{linking}, a relation between subformulas in $\dual A$ and in $B$.
-
-%\[
-%%\hspace*{9ex}% spacing hack to achieve central horizontal alignment
-%\hspace*{-\parindent}%
-%\hspace*{\fill}%
-%% Behold my better spacing hack to achieve central horizontal alignment :)
-%\begin{array}{c@{\qquad\qquad}c@{\qquad\qquad}c@{\qquad\qquad}c}
-%	\begin{tikzpicture}[net]
-%		\formula[y=1]{{\dual a}}
-%		\formula[y=0]{a\*a}
-%		\Vlink[red]{[-2]1,1}
-%		\Vlink[red]{[2]1,3}
-%	\end{tikzpicture}
-%&
-%	\begin{tikzpicture}[net]
-%		\formula[y=1]{{\dual a}}
-%		\formula[y=0]{a\+b}
-%		\Vlink[red]{1,1}
-%	\end{tikzpicture}
-%&
-%	\begin{tikzpicture}[net]
-%		\formula[y=1]{{\dual a}\+{\dual b}}
-%		\formula[y=0]{b\*a}
-%		\Vlink[red]{1,3}
-%		\Vlink[red]{3,1}
-%	\end{tikzpicture}
-%&
-%	\begin{tikzpicture}[net]
-%		\formula[y=1]{*{\phantom(}{\dual a}*{\phantom)}
-%		 {{\+}}*({\dual b}*{\phantom)}
-%		 {{\+}}*{\phantom(}{\dual c}*)}
-%		\formula[y=0]{*(a*{\phantom)}
-%		{{\*}}*{\phantom(}b*)
-%		{{\*}}*{\phantom(}c*{\phantom)}}
-%		\Vlink[red]{1,1}
-%		\Vlink[red]{3,3}
-%		\Vlink[red]{5,5}
-%	\end{tikzpicture}
-%\\
-%	\text{\small diagonal}
-%&	\text{\small injection}
-%&	\text{\small symmetry}
-%&	\text{\small associativity}
-%\end{array}
-%\hfill
-%\]
-
-%A companion paper \cite{Hughes-2018} explores unification nets for first-order \emph{multiplicative} linear logic, reporting drastic complexity improvements and equally straightforward proof net composition.
-
-% Hyland-Ong-2000,Abramsky-Jagadeesan-Malacaria-2000
+% ==================================================
+
+\section{Proof nets for first-order additive linear logic}
 
 % --------------------------------------------------
-
-%$\seq{\,\exists x.P(x,x,s)\,}{\,\exists y.\dual P(t,y,y)}$
-
-% --------------------------------------------------
-
-%\subsection{Background and related work}
-
-%
-%\cite{Whitman-1941}
-%\cite{Girard-1987}
-%\cite{Galmiche-Marion-1995} % ALL proof search
-%\cite{Girard-1996}
-%\cite{Hu-1999}
-%\cite{Galmiche-2000} % ALL connection net (Def 6.11.)
-%\cite{Cockett-Seely-2001}
-%\cite{Hughes-VanGlabbeek-2005}
-%%\cite{Cockett-Santocanale-2009}
-%\cite{Heijltjes-2011, Heijltjes-2012}
-%\cite{Heijltjes-Hughes-2015}
-%
-%\cite{Danos-1990}
-%\cite{Guerrini-Masini-2001}
-%\cite{Guerrini-2011}
-%
-%\cite{Herbrand-1930}
-%\cite{Heijltjes-2010}
-
-% ==================================================
-
-\section{Proof nets for first-order additive linear logic}
-
-% --------------------------------------------------
-
-\subsection{First-order additive linear logic}
 
@@
 
-% ..................................................
-
-\begin{figure}[!t]
-\[
-	\infer[\Qrr1]{\vphantom B\seq a{\dual a}}{}
-\quad
-	\infer[\Qrr+i]{\seq A{B_1\+B_2}}{\seq A{B_i}}
-\quad
-	\infer[\Qrr*]{\seq A{B\*C}}{\seq AB & \seq AC}
-\quad
-	\infer[\Qrr?t]{\seq A{\exists x.B}}{\seq A{B[t/x]}}
-\quad
-	\infer[\Qrr!~(x\,\notin\,\textsc{fv}(A))]{\seq A{\forall x.B}}{\seq AB}
-\]
-\caption{A sequent calculus for $\all1$}
-\label{fig:sequent calculus}
-\end{figure}
-
-% ..................................................
-
 By a \defn{subformula} we will mean a subformula \defn{occurrence}.
@@
 
+Since we will be working with a graphical representation, we will adopt \defn{Barendregt's convention}, that bound variable names are globally unique identifiers, in the following form.
+In a sequent $\seq AB$, we assume all quantifiers to have a unique binding variable, distinct from any free variable.
+In a proof $\pi$ over $\seq AB$, a variable $x$ that is universally quantified as $\forall x.C$ in $\seq AB$ is an \defn{eigenvariable}.
+A $\qrr!$ rule on $\forall x.C$ is considered to bind all free occurrences of the eigenvariable $x$ in its direct subproof.
+Accordingly, we assume that $x$ does not occur free outside these subproofs (which can be guaranteed by globally renaming $x$).
+We take variable names to be persistent throughout a proof, in the sense that we don't admit alpha-conversion between proof rules.
+We thus have unique bound variable names in $\seq AB$, but in $\pi$ all rules on the subformula $\forall x.C$ share the same eigenvariable $x$.
+
+% ..................................................
+
+\begin{figure}[!t]
+$
+	\infer[\Qrr1]{\vphantom B\seq a{\dual a}}{}
+\hspace*{\fill}
+	\infer[\Qrr+i]{\seq A{B_1\+B_2}}{\seq A{B_i}}
+\hspace*{\fill}
+	\infer[\Qrr*]{\seq A{B\*C}}{\seq AB & \seq AC}
+\hspace*{\fill}
+	\infer[\Qrr?t]{\seq A{\exists x.B}}{\seq A{B[t/x]}}
+\hspace*{\fill}
+	\infer[\Qrr!~(x\,\notin\,\textsc{fv}(A))]{\seq A{\forall x.B}}{\seq AB}
+$
+\medskip
+\caption{A sequent calculus for $\all1$}
+\label{fig:sequent calculus}
+\end{figure}
+
+% ..................................................
+
 A \defn{link} $(C,D)$ on a sequent $\seq AB$ is a pair of subformulas $C\leq A$ and $D\leq B$. 
@@
 
-\subsection{Witness maps}
-
-A \defn{witness map} $\sigma\colon\var\rightharpoonup\terms$ is a substitution map which assigns terms to variables, given as a (finite) partial function.
-We define it as $\sigma=[t_1/x_1,\dots,t_n/x_n]$, where its \defn{domain} $\dom\sigma$ is $\{x_1,\dots,x_n\}$.
-We abbreviate by $y\in\sigma$ that a variable $y$ occurs free in the range of~$\sigma$, i.e., $y\in\fv(t_i)$ for some $i\leq n$.
-The map $\sigma\minus x$ is undefined on $x$ and otherwise as $\sigma$, we write $\sigma\res V$ for the restriction of $\sigma$ to a set of variables $V$, and $\varnothing$ for the empty witness map.
-%
-We write $A\sigma$ for the application of the substitutions in $\sigma$ to the formula $A$, and $\pi\sigma$ for its application to the proof $\pi$, where it is applied to each formula in the proof, and to each existential witness $t$ recorded with a rule $\qrr?t$.
-The \defn{composition} of two maps is written $\sigma\tau$, where $A(\sigma\tau)=(A\sigma)\tau$.
-
-%\[
-%\begin{tabular}{@{}ll@{}} 
-%	$\varnothing$ & is the empty witness map \\
-%	$\sigma\minus x$ & is the witness map that is undefined on $x$ and otherwise as $\sigma$ \\
-%	$\sigma\res V$ & is the restriction of $\sigma$ to a set of variables $V$\\
-%	$y\in\sigma$ & abbreviates $y\in\fv(\sigma(x))$ for some $x$ ($y$ occurs in the range of $\sigma$) \\
-%	$A\sigma$ & is the application of $\sigma$ as a substitution map to a formula $A$ \\
-%	$\pi\sigma$ & is the application of $\sigma$ to a proof $\pi$ (applied to all its formulas) \\
-%\end{tabular}
-%\]
+\paragraph*{Witness maps}
+
+We will record the witnessing terms to existential quantifiers as (explicit) substitutions at each link.
+A \defn{witness map} $\sigma\colon\var\rightharpoonup\terms$ is a substitution map which assigns terms to variables, given as a (finite) partial function $\sigma=[t_1/x_1,\dots,t_n/x_n]$.
+Its \defn{domain} $\dom\sigma$ is $\{x_1,\dots,x_n\}$.
+We abbreviate by $y\in\sigma$ that a variable $y$ occurs free in the range of~$\sigma$  ($y\in\fv(t_i)$ for some $i\leq n$).
+The map $\sigma\minus x$ is undefined on $x$ and as $\sigma$ otherwise; $\sigma\res V$ is the restriction of $\sigma$ to a set of variables $V$, and $\varnothing$ is the empty witness map.
+We write $A\sigma$ for the application of the substitutions in $\sigma$ to the formula $A$, and $\sigma\tau$ is the \defn{composition} of two maps, where $A(\sigma\tau)=(A\sigma)\tau$.
+We apply $\sigma$ to a proof $\pi$, written $\pi\sigma$, by applying it to each formula in the proof and to each existential witness $t$ recorded with a rule $\qrr?t$.
 
 A \defn{witness linking} $\lambda_\Sigma$ is a linking $\lambda$ with a \defn{witness labelling} $\Sigma\colon\lambda\to\var\rightharpoonup\terms$ that assigns each link $(C,D)$ a witness map.
-We may use and define $\lambda_\Sigma$ as a set of \defn{witness links} $\link CD$, where $(C,D)\in\lambda$ and $\Sigma(C,D)=\sigma$.
+We may use and define $\lambda_\Sigma$ as a set of \defn{witness links} $\link CD$ where $(C,D)\in\lambda$ and $\Sigma(C,D)=\sigma$.
+A witness link $\link ab$ on atomic formulas is an \defn{axiom link} if $\dual a\sigma=b\sigma$.
+An \defn{axiom} witness linking is one consisting of axiom links.
 
@@
 
-We will assume the following variable naming conventions.
-%
-\begin{description}
-	\item
-[Barendregt's convention] All quantifiers in a sequent $\seq AB$ have a distinct binding variable, and no bound variable shares a name with a free one.
-
-	\item[Eigenvariables not free]
-For a link $\link CD$ over $\seq AB$, if a variable $x$ in the range of $\sigma$ is universally quantified as $\forall x.X$ in $\seq AB$ (an \emph{eigenvariable}), then $C\leq X$ or $D\leq X$.
-
-	\item[Freshness]
-For a link $\link CD$ over $\seq AB$, other variables in the range of $\sigma$ are \emph{fresh}: distinct from existentially quantified variables in $\seq AB$, and from those of other links.
-\end{description}
+%We will assume that all quantifiers in a sequent $\seq AB$ have a distinct binding variable, and no bound variable shares a name with a free one (\defn{Barendregt's convention}).
+In a proof $\pi$ or linking $\lambda_\Sigma$ over $\seq AB$, a variable $x$ is an \defn{eigenvariable} if it is universally quantified ($\forall x.X$) in $\seq AB$, an \defn{existential variable} if existentially quantified ($\exists x.X$), and a \defn{global variable} if free in $\seq AB$.
+A variable $x$ introduced by a witnessing term $t$ in $\pi$ (in a rule $\qrr?t$) or in $\lambda_\Sigma$ (in the range of $\Sigma$) that is not an eigenvariable or global variable is a \defn{term variable}.
+We will assume the following \defn{freshness} convention: term variables are distinct from existential variables.
+Observe that both conventions are readily applied to proofs and linkings by renaming (\emph{$\alpha$-converting}) quantified variables in the conclusion.
 
@@
 A function call $\deseq{\prf\pi AB}{A'}{B'}$ expects that $A=A'\sigma$ and $B=B'\sigma$: the translation separates a sequent $\seq AB$ into subformulas $A'$, $B'$ of the ultimate conclusion of the proof, and the accumulated existential witnesses $\sigma$.
-%While a sequent proof instantiates existential witnesses immedately into the premise of the existential quantifier rule, for proof nets we delay the substitutions $\sigma$.
-Hence we need to maintain the separation of the conclusion $\seq AB$ into the substitutions $\sigma$ and the subformulas $A'$ and $B'$ of the conclusion of the proof net.
-%
 For an example, we refer to the introduction.
-
-We will conclude this section by discussing two further essential notions.
-First, a witness link $\link ab$ on two atomic formulas $a$ and $b$ is an \defn{axiom} link if $a\sigma=\dual b\sigma$.
+%
+%To conclude this section we will identify three aspects of sequent proofs, arising from the local nature of the rules, that need to be enforced explicitly in proof nets.
+%
+%\begin{description}
+%	\item[Axiom links]
+%A sequent proof axiom connects dual atoms, $\seq a{\dual a}$.
+Correspondingly, a witness link $\link ab$ on atomic formulas $a$ and $b$ is an \defn{axiom link} if $a\sigma=\dual b\sigma$.
+An \defn{axiom} witness linking is one consisting solely of axiom links.
+%	\item[Local eigenvariables]
+%The side-condition on the $\forall R$-rule, that the eigenvariable is not free in the context, means that eigenvariables are \emph{local} to the subproof of the $\forall R$-rule.
+Correspondingly, a link $\link CD$ on $\seq AB$ has \defn{local eigenvariables} if for any variable $x\in\sigma$, if $x$ is an eigenvariable quantified as $\forall x.X$ in $\seq AB$, then $C\leq X$ or $D\leq X$.
+%A witness linking or pre-net has \defn{local eigenvariables} if all its links do.
+%	\item[Exact coverage]
+%The local witness substitution $[t/x]$ in a rule instance $\qrr?t$ will have been applied exactly to the axioms $\seq a{\dual a}$ in the subproof of that rule.
+Correspondingly, for a link $\link CD$ on $\seq AB$ we expect the domain of $\sigma$ to be exactly the existential variables in $A$ and $B$ in whose scope $C$ and $D$ occur.
+For a subformula $C$ of $A$, let the \defn{existential variables of $C$ in $A$} be the set $\ex[A]C = \{\,x \mid C < \exists x.X \sub A\,\}$.
+A link $\link CD$ on $\seq AB$ then has \defn{exact coverage} if $\dom\sigma = \ex[A]C\cup\ex[B]D$.
+If it does, $\sigma$ consists of two components, $\sigma\res{\ex[A]C}$ and $\sigma\res{\ex[B]D}$, which we abbreviate as $\sigma_C$ and $\sigma_D$ respectively.
+%A witness linking or pre-net has \defn{exact coverage} if all its links do.
+%\end{description}
+%
+%\noindent
+%Observe that a de-sequentialization $[\pi]$ has all three properties.
+
+%\begin{definition}[Local correctness]
+%A witness linking or pre-net has \emph{local eigenvariables/exact coverage} if all its links do.
+%It is \defn{locally correct} if it satisfies both.
+%\end{definition}
+
+%First, a witness link $\link ab$ on two atomic formulas $a$ and $b$ is an \defn{axiom} link if $a\sigma=\dual b\sigma$.
 A witness \defn{axiom} linking is one where every link is an axiom link.
@@
 
-Second, given a link $\link CD$ in a pre-net $\net\lambda AB$, we expect the domain of $\sigma$ to be exactly the existentially quantified variables in $A$ and $B$ in whose scope $C$ and $D$ occur. 
-%That is, any variable $x$ such that there is a subformula $\exists x.X$ in $A$ that in turn has $C$ as a subformula, and likewise for $B$ and $D$. We will now make this precise. 
-For a subformula $C$ of $A$, let the \defn{existential variables} $\ex[A]C$ of $C$ in $A$ be the set
-\[
-	\ex[A]C = \{\,x \mid C < \exists x.X \sub A\,\}~.
-\]
-
-% ..................................................
-
-\begin{definition}
-A witness pre-net $\net{\lambda_\Sigma}AB$ has \defn{exact coverage} if for every link $\link CD$ in $\lambda_\Sigma$ the domain of $\sigma$ is exactly the existential variables of $C$ and $D$:
-\[
-	\dom\sigma = \ex[A]C\cup\ex[B]D~.
-\]
-\end{definition}
-%
-% ..................................................
-%
-The witness map $\sigma$ of a link $\link CD$ then has two natural, disjoint components, $\sigma\res{\ex[A]C}$ and $\sigma\res{\ex[B]D}$, which we will abbreviate by $\sigma_C$ and $\sigma_D$ respectively.
-
-Finally, note that a de-sequentialization $[\pi]$ has exact coverage.
-
-%Note that the property is carefully formulated, using the \emph{exisential cover} rather than simply the free existential variables in a formula, to account for vacuous quantifiers.
-% ($\exists x.C$ where $x$ is not free in $C$).
-The issue becomes even more pertinent for a link $\link CD$ where $C$ occurs in $\exists x.C{\+}C'$ and $x$ is free in $C'$ but not $C$, where we still would like an explicit witness for $x$ in $\sigma$.
+%Second, in a sequent proof, the side-condition on the $\forall R$-rule, that the eigenvariable is not free in the context, means that eigenvariables are \emph{local} to the subproof of the $\forall R$-rule.
+We capture this in pre-nets as the \defn{local eigenvariables} condition: for a link $\link CD$ on $\seq AB$, if $x\in\sigma$ is an eigenvariable quantified as $\forall x.X$ in $\seq AB$, then $C\leq X$ or $D\leq X$.
+%
+%Third, for a link $\link CD$ on $\seq AB$ we expect the domain of $\sigma$ to be exactly the existential variables in $A$ and $B$ in whose scope $C$ and $D$ occur.
+For a subformula $C$ of $A$, let the \defn{existential variables of $C$ in $A$} be the set $\ex[A]C$:
+%\[
+%	\ex[A]C = \{\,x \mid C < \exists x.X \sub A\,\}~.
+%\]
+%
+%% ..................................................
+%
+%\begin{definition}
+%A witness pre-net $\net{\lambda_\Sigma}AB$ has \defn{exact coverage} if for every link $\link CD$ in $\lambda_\Sigma$ the domain of $\sigma$ is exactly the existential variables of $C$ and $D$:
+%\[
+%	\dom\sigma = \ex[A]C\cup\ex[B]D~.
+%\]
+%\end{definition}
+%
+% ..................................................
+%
+%The witness map $\sigma$ of a link $\link CD$ then has two natural, disjoint components, $\sigma\res{\ex[A]C}$ and $\sigma\res{\ex[B]D}$, which we will abbreviate by $\sigma_C$ and $\sigma_D$ respectively.
 
@@
 
-\subsection{Correctness and sequentialization}
+\paragraph*{Correctness and sequentialization by coalescence}
 
@@
 \tag{$\srr*$}
-	%\{\link C{D_1}^\pi\,,\,\link C{D_2}^\phi\}
 	\left.\begin{array}{@{}l@{\,}}\link C{D_1}^\pi \\ \link C{D_2}^\phi\end{array}\right\}
@@
 	}}
-%\end{align*}
 \\ \\[-8pt]
-%\begin{align*}
 \tag{$\srr?$}
@@
 
+We will first identify two aspects of sequent proofs, arising from the local nature of the rules, that need to be enforced explicitly in a geometric correctness condition.
+
+\begin{description}
+	\item[Local eigenvariables]
+The side-condition on the $\forall R$-rule, that the eigenvariable is not free in the context, means that eigenvariables are \emph{local} to the subproof of the $\forall R$-rule.
+Correspondingly, a link $\link CD$ on $\seq AB$ has \defn{local eigenvariables} if for any variable $x\in\sigma$, if $x$ is an eigenvariable quantified as $\forall x.X$ in $\seq AB$, then $C\leq X$ or $D\leq X$.
+A witness linking or pre-net has \defn{local eigenvariables} if all its links do.
+
+	\item[Exact coverage]
+The local witness substitution $[t/x]$ in a rule instance $\qrr?t$ will have been applied exactly to the axioms $\seq a{\dual a}$ in the subproof of that rule.
+Correspondingly, for a link $\link CD$ on $\seq AB$ we expect the domain of $\sigma$ to be exactly the existential variables in $A$ and $B$ in whose scope $C$ and $D$ occur.
+For a subformula $C$ of $A$, let the \defn{existential variables of $C$ in $A$} be the set $\ex[A]C = \{\,x \mid C < \exists x.X \sub A\,\}$.
+A link $\link CD$ on $\seq AB$ then has \defn{exact coverage} if $\dom\sigma = \ex[A]C\cup\ex[B]D$.
+If it does, $\sigma$ consists of two components, $\sigma\res{\ex[A]C}$ and $\sigma\res{\ex[B]D}$, which we abbreviate as $\sigma_C$ and $\sigma_D$ respectively.
+A witness linking or pre-net has \defn{exact coverage} if all its links do.
+\end{description}
+
+\noindent
+Both conditions are captured naturally by coalescence, as can be observed from the rules.
+
+\paragraph*{Slices}
+
 A \defn{slice} is the fraction of a proof that depends on a given choice of one branch (or projection) on each product formula $A\*B$.
@@
 We will here use slices for the latter purpose.
-
+%
 As in the propositional case \cite{Hughes-vanGlabbeek-2005}, we define a \defn{slice} of a sequent $\seq AB$ as a set of potential links, of which exactly one must be realized in a proof net $\net{\lambda_\Sigma}AB$.
 We extend the propositional criterion in two ways:
-\begin{itemize}
-	\item
+
+\begin{description}
+	\item[Expansion]
 When defining slices, we interpret an existential quantification $\exists x.A$ as a sum over all witnesses $t_i$ to $x$ that occur in the pre-net, $A[t_1/x]\+\dots\+A[t_n/x]$.
-This captures the non-permutability of a product rule over distinct existential instantiations, as below left.
-
-	\item
-We define a \defn{dependency} relation between a universal quantification $\forall x.A$ and an instantiation $B[t/y]$ of $\exists x.B$ where the \defn{eigenvariable} $x$ occurs free in $t$ (a standard approach to first-order quantification \cite{Miller-1987,Girard-1996,Heijltjes-2010,Mimram-2011}).
-For each link, we require the dependency to be \emph{acyclic}, which amounts to \emph{slice-wise} first-order correctness.
-It captures the non-permutability of universal and existential sequent rules due to the \emph{eigenvariable condition} of the former, as below right.
-\end{itemize}
-
+This captures the non-permutability of a product rule over distinct instantiations, as below left.
+	\item[]
 \[
@@
 \]
-
-For a witness linking $\lambda_\Sigma$ and variable $x$, write $\Sigma(x)\subseteq\terms$ for the \defn{witness set} of $x$, which collects the terms assigned to $x$ by the witness maps in $\Sigma$ for every link in $\lambda$:
+	\item[Dependency]
+We define a \defn{dependency} relation between a universal quantification $\forall x.A$ and an instantiation $B[t/y]$ of $\exists x.B$ where the \defn{eigenvariable} $x$ occurs free in $t$ (a standard approach to first-order quantification \cite{Miller-1987,Girard-1996,Heijltjes-2010,Mimram-2011}).
+For each link, we require the dependency to be \emph{acyclic}, which amounts to \emph{slice-wise} first-order correctness.
+It captures the non-permutability of universal and existential sequent rules due to the \emph{eigenvariable condition} of the former, as below right.
+\end{description}
+
+\noindent
+Formalizing this, for a witness linking $\lambda_\Sigma$ and variable $x$, write $\Sigma(x)\subseteq\terms$ for the \defn{witness set} of $x$, which collects the terms assigned to $x$ by the witness maps in $\Sigma$ for every link in $\lambda$:
 \[
@@
 \begin{definition}
-A witness pre-net is \defn{correct} if
+A witness pre-net is \defn{correct} if:
 \begin{itemize}
-\item it has exact coverage,
+\item it has local eigenvariables and exact coverage,
 \item it is \defn{slice-correct}: every slice is a singleton, and
@@
 \label{thm:correctness}
-A witness pre-net is correct if and only if it strict-coalesces. 
+\label{cor:strong coalescence}
+A witness pre-net that strict-coalesces is correct, and a correct witness pre-net strongly strict-coalesces. 
 \end{theorem}
@@
 \begin{proof}
-From right to left, we proceed by induction on the coalescence path from $\net{\lambda_\Sigma}AB$ to $\net{\{\link[\varnothing]AB\}}AB$, with the end result as the base case.
+For the first statement, we proceed by induction on the coalescence path from $\net{\lambda_\Sigma}AB$ to $\net{\{\link[\varnothing]AB\}}AB$, with the end result as the base case.
 It is slice-correct: every slice of $\seq AB$ contains $\link[\varnothing]AB$, so every slice of $\net{\{\link[\varnothing]AB\}}AB$ is the singleton $\{\link[\varnothing]AB\}$.
@@
 
-From left to right, let $\net{\lambda_\Sigma}AB$ be correct.
+For the second statement, let $\net{\lambda_\Sigma}AB$ be correct.
+%We proceed by induction on the \emph{depth} of the links in $\net{\lambda_\Sigma}AB$, their distance to the roots of $A$ and $B$, and observe that this measure strictly decreases for any coalescence step.
 By Lemma~\ref{lem:coalescence applies} either the net has coalesced, or a coalescence step applies.
-By Lemma~\ref{lem:correct} the result of this coalescence step is again correct.
-It follows that the pre-net $\net{\lambda_\Sigma}AB$ strict-coalesces.
+By Lemma~\ref{lem:correct} the result of any coalescence step is again correct.
+Since links strictly move towards the roots of both formula trees, it follows that this process terminates, and the pre-net $\net{\lambda_\Sigma}AB$ strongly strict-coalesces.
 \end{proof}
@@
 
-\begin{corollary}
-\label{cor:strong coalescence}
-A correct witness pre-net strongly strict-coalesces.
-\end{corollary}
-
-\begin{proof}
-By Theorem~\ref{thm:correctness} a correct pre-net coalesces, and by Lemma~\ref{lem:correct} any coalescence step preserves correctness.
-\end{proof}
+%\begin{corollary}
+%\label{cor:strong coalescence}
+%A correct witness pre-net strongly strict-coalesces.
+%\end{corollary}
+%
+%\begin{proof}
+%By Theorem~\ref{thm:correctness} a correct pre-net coalesces, and by Lemma~\ref{lem:correct} any coalescence step preserves correctness.
+AAs links strictly move towards the formula roots, this process terminates.
+%\end{proof}
 
@@
 \begin{theorem}
-Proof nets are canonical: $[\pi]=[\phi]$ if and only if $\pi\sim\phi$.
+Witness nets are canonical: $[\pi]=[\phi]$ if and only if $\pi\sim\phi$.
 \end{theorem}
@@
 	\formula[right,y=0]{*{\forall x.\exists y.\forall z.\,}P}
-	\Vlink[red,l,label={$\scriptstyle[v/z,f(x)/y]$~~}]{1,1}
+	\Vlink[red,l,label={$\scriptstyle[f(x)/y,z/v]$~~}]{1,1}
 	\formula[right,y=-.5]{*{\exists x.\forall y.\exists z.\,}{\dual P}}
@@
 The latter is the shortest sequence $\fix\sigma=\sigma\sigma\dots\sigma$ such that no variable is both in the domain and range of $\fix\sigma$.
-This is not necessarily finite; in our composition operations, finiteness is ensured by the correctness conditions on proof nets.
+This is not necessarily finite; in our composition operations, finiteness is ensured by the correctness conditions on proof nets (see Theorem~\ref{thm:composition}).
 
@@
 \label{thm:composition}
-If proof nets $\net{\lambda_\Sigma}AB$ and $\net{\kappa_\Theta}{\dual B}C$ sequentialize to $\pi$ and $\phi$ respectively, then their composition $(\net{\lambda_\Sigma}AB)\comp(\net{\kappa_\Theta}{\dual B}C)$ sequentializes to a normal form $\psi$ of $\pi\comp\phi$.
-%the proof
-%\[
-%	\infer[\Qrr.]{\seq AC}{
-%	 \Prf\pi AB & \Prf\phi{\dual B}C
-%	}
-%\]
+If proof nets $\net{\lambda_\Sigma}AB$ and $\net{\kappa_\Theta}{\dual B}C$ sequentialize to $\pi$ and $\phi$ respectively, then their composition $(\net{\lambda_\Sigma}AB)\comp(\net{\kappa_\Theta}{\dual B}C)$ is well-defined (i.e.\ all fixed points are finite), and sequentializes to a normal form $\psi$ of $\pi\comp\phi$.
 \end{theorem}
@@
 
+\noindent
 To reconstruct witnesses by unification, we define the following operations.
@@
 \]
-Observe that the initial witness pre-net satisfies the \emph{exact coverage} condition.
+An initial witness pre-net has \emph{exact coverage}, while coalescence will give \emph{local eigenvariables}.
 
@@
 Expansion trees, in contrast, record the expansion and its terms explicitly.
-This could be an interesting alternative approach to additive proof nets, which we will explore in future work.
+This could be an interesting alternative approach to additive proof nets, which we may explore in future work.
 It is expected, though, that this would sacrifice \emph{generality} and \emph{direct composition}.
+
+%\paragraph*{Generality}
+
+The idea of using \emph{generality} as a basis for proof identity originates with Lambek \cite{Lambek-1968,Lambek-1969,Lambek-1972}, who observed that the two canonical proofs of $\seq{A{\+}A}{\dual A}$ can be distinguished by casting each as a specialization (by substituting into propositional variables) of the more general proofs of $\seq{\,a{\+}b}{\dual a}$ and $\seq{\,a{\+}b}{\dual b}$.
+Curiously, how this extends to the first-order setting is not obvious.
+
+The natural first-order analogue of $\seq{A{\+}A}{\dual A}$ would be $\seq{\exists x.A}{\dual A}$ where the quantifier is vacuous, as $\exists x.A$ represents the infinite sum over $A$ (for all terms $t$).
+Where Lambek's generality \emph{distinguishes} the two proofs of $\seq{A{\+}A}{\dual A}$, ours \emph{identifies} the proofs of $\seq{\exists x.A}{\dual A}$: the sequent has one unification net, but infinitely many witness nets (one for each $t$).
+Interestingly, then, if existential quantification is indeed analogous to a sum, Lambek's notion of generality is more faithfully captured by witness nets than unification nets.
 
@@
 Then $S\cap \lambda_\Sigma$ is the singleton $\{\link CD\}$ if and only if $S\cap\kappa_\Theta$ is $\{\link[\sigma\minus x]C{\exists x.D}\}$, where it should be observed that if $t$ is also a witness to $x$ in some other slice of $R$, then $t\in\Theta(x)$ and in fact $S=S'$.
-
-%\lutz{?}
-%\todo{Explain the witness sets better; refer to 1st case above; }
 
@@
 The path along the top and right of this diagram sequentializes $L$ to $\pi'$ and $R$ to $\phi'$ (equivalent to $\pi$ and $\phi$ respectively), and then composes to $L_n\comp R_n = \net{\{\link[\varnothing]AC^{\pi'\comp\phi'}\}}AC$.
-%with
-%\[
-%	\psi' = \vc{\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq AC}{\Prf{\pi'}AB & \Prf{\phi'}{\dual B}C}}~.
-%\]
 
@@
 Then $L\comp R$ is a proof net (it has an axiom linking and it coalesces), and it sequentializes to a normal form of $\psi$.
-%
-%which sequentialize respectively to. 
-%\[
-%	\infer{\seq{a\sigma}{b\sigma}}{} 
-%	\qquad\text{and}\qquad
-%	\infer{\seq{\dual b\tau}{c\tau}}{}~.
-%\]
-%We have the link 
 \end{proof}
@@
 \end{document}
-
-\begin{lemma}
-If a labelled pre-net $\net{\lambda_\Sigma^\Pi}AB$ strict-sequentializes to $\pi$, then $(\net{\lambda_\Sigma^\Pi}AB)\rho$ strict-sequentializes to $\pi\rho$.
-\end{lemma}
-
-\begin{proof}
-By induction on the sequentialization sequence.
-\end{proof}
-
-NORMALIZATION PROBLEM
-
-\begin{lemma}
-For $\link ab$ with $\sigma=\mgu(a,\dual b)$ in a proof net $\net{\lambda_\star}AB$ and $\link[\tau]{\dual b}c$ with $\tau=\mgu(b,c)$ in $\net{\kappa_\star}{\dual B}C$ the composition $\sigma_a\tau_c\dcom\fix{\sigma_b\tau\subdual b}$ is $\mgu(a,\dual c)$.
-\end{lemma}
-
-%
-%\begin{lemma}
-%For $\link ab$ in a proof net $\net{\lambda_\star}AB$ and $\link[\tau]{\dual b}c$ in $\net{\kappa_\star}{\dual B}C$ the composition $\sigma_a\tau_c\dcom\fix{\sigma_b\tau\subdual b}=\mgu(a,c)$.
-%\end{lemma}
-%
-%\begin{proof}
-%Let $\rho=\mgu(a,c)$ and $\rho'=\sigma_a\tau_c\dcom\fix{\sigma_b\tau\subdual b}$.
-Define the \defn{basis} $\floor{s,t}$ of the $\mgu$ of $s$ and $t$ to be the substitution map defined by $\floor{x,t}=\floor{t,x} = [t/x]$ and
-%\[
-%	\floor{P(s_1,\dots,s_n),P(t_1,\dots,t_n)} =
-%	\floor{f(s_1,\dots,s_n),f(t_1,\dots,t_n)} =
-%	\floor{s_1,t_1}\dots\floor{s_n,t_n}~.
-%\]
-%Write $\floor\sigma$ for the basis $\floor{a,b}$ of $\sigma$, $\floor\tau$ for that of $\tau$, and $\floor\rho$ for that of $\rho$.
-%\end{proof}
-%
-%\end{document}
-%
-
-\begin{figure}
-\hrule
-\par\bigskip
-\[
-\begin{array}{ccc}
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{P}
-    	\formula[y=1]{Q}
-    	\Vlink[blue]{1,1}
-    \end{tikzpicture}}
-&\rightsquigarrow&    
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{P}
-    	\formula[y=1]{Q}
-    	\Vlink[red,label={$~\scriptstyle{\sigma(P,\dual Q)}$}]{1,1}
-    \end{tikzpicture}}
-\\ \\
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{A}
-    	\formula[y=1]{B\+C}
-    	\Vlink[red,label={$\scriptstyle\sigma~$},l]{1,1}
-    \end{tikzpicture}}
-&\rightsquigarrow& 
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{A}
-    	\formula[y=1]{B\+C}
-    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,2}
-    \end{tikzpicture}}
-\\ \\   
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{A}
-    	\formula[y=1]{B\*C}
-    	\Vlink[red,label={$\scriptstyle\sigma~$},l]{[-1]1,1}
-    	\Vlink[red,label={~$\scriptstyle\tau$}]{[1]1,3}
-    \end{tikzpicture}}
-&\stackrel{\sigma\coh\tau}\rightsquigarrow&   
-	\vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{A}
-    	\formula[y=1]{B\*C}
-    	\Vlink[red,label={~$\scriptstyle{\sigma\cup\tau}$}]{1,2}
-    \end{tikzpicture}}
-
-\\ \\
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{A}
-    	\formula[y=1]{\exists x.B}
-    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,4}
-    \end{tikzpicture}}
-&\rightsquigarrow&
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{A}
-    	\formula[y=1]{\exists x.B}
-    	\Vlink[red,label={~$\scriptstyle{\sigma\minus x}$}]{1,1}
-    \end{tikzpicture}}
-\\ \\
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{A}
-    	\formula[y=1]{\forall a.B}
-    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,4}
-    \end{tikzpicture}}
-&\stackrel{a\,\notin\,\fv(A\sigma)}\rightsquigarrow&
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{A}
-    	\formula[y=1]{\forall a.B}
-    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,1}
-    \end{tikzpicture}}
-\end{array}
-\]
-\caption{Coalescence rules}
-\label{fig:coalescence}
-\end{figure}
-
-\begin{equation}
-  	\net{\{\link A{B_i}^\pi\}}A{B_1\+B_2} 
- ~\scoal~
-	\net{\{\link A{B_1\+B_2} ^\psi\}}A{B_1\+B_2}
-\tag{$\srr+i$}
-\end{equation}
-
-\hfill $\text{where}\quad \psi=~
-  \vc{\infer  {\seq{A\sigma}{B_1\sigma\,\+\,B_2\sigma}}  {\Prf \pi {A\sigma} {B_i\sigma}}}
-$ \hspace*{20pt}
-
-\begin{equation}
-	\net{\{\link AB^\pi,\link AC^\phi\}}A{B\*C}
- ~\scoal~ 
-	\net{\{\link A{B\*C}^\psi\}}A{B\*C}
-\tag{$\srr*$}
-\end{equation}
-
-\hfill $\text{where}\quad \psi=~
-  \vc{
-   \infer  {\seq{A\sigma}{B\sigma\,\*\,C\sigma}}  {
-    \Prf \pi {A\sigma} {B\sigma}
-    &
-    \Prf \phi {A\sigma} {C\sigma}    
-  }}$ \hspace*{20pt}
-
-\begin{equation}
-	\net{\{\link AB^\pi\}}A{\exists x.B}
- ~\scoal~ 
-	\net{\{\link[\sigma\minus x]A{\exists x.B}^\psi\}}A{\exists x.B}
-\tag{$\srr?$}
-\end{equation}
-
-\hfill $\text{if}\quad\sigma(x)\,\neq\,\bot~,
-		\quad
-		\text{where}\quad \tau=\sigma\minus x
-		\quad
-		\text{and}\quad \psi=~
-  \vc{
-   \infer  {\seq{A\tau}{\exists x.B\tau}}  {
-    \Prf \pi {A\sigma} {B\sigma}
-  }}
-$ \hspace*{20pt}
-
-\begin{equation}
-	\net{\{\link AB\}}A{\forall a.B}
- ~\scoal~
-	\net{\{\link A{\forall a.B}\}}A{\forall a.B}
-\tag{$\srr!$}
-\end{equation}
-
-\hfill $\text{if}\quad a\notin\sigma~,
-		\quad
-		\text{where}\quad \psi=~
-  \vc{
-   \infer  {\seq{A\sigma}{\forall a.B\sigma}}  {
-    \Prf \pi {A\sigma} {B\sigma}
-  }}
-$ \hspace*{20pt}
-
-\begin{proposition}
-If $\net{\lambda_\Sigma}AB$ and $\net{\kappa_\Theta}{\dual B}C$ both coalesce, so does their composition.
-\end{proposition}
-
-\begin{proof}
-By induction on both coalescence sequences.
-In the base case, $\lambda_\Sigma=\{\link[\varnothing]AB\}$ and $\kappa_\Theta=\{\link[\varnothing]{\dual B}C\}$, and the composition is $\net{\{\link[\varnothing]AC\}}AC$.
-
-If
-\todo{}
-\end{proof}
-
-\[
-\begin{array}{@{}ccccc@{}}
-  \vc{
-  \begin{tikzpicture}[net]
-	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-	\Vlink[red,l,label={$\scriptstyle[f(x)/y\,,\,x/z]$~~}]{3,2}
-	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
-  \end{tikzpicture}}
-& \scoal &
-  \vc{
-  \begin{tikzpicture}[net]
-	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-	\Vlink[red,l,label={$\scriptstyle[f(x)/y\,,\,x/z]$~~~}]{4,2}
-	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
-  \end{tikzpicture}}
-& \scoal &
-  \vc{
-  \begin{tikzpicture}[net]
-	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-	\Vlink[red,l,label={$\scriptstyle[x/z]$~~}]{2,2}
-	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
-  \end{tikzpicture}}
-\\ \\[-10pt] &&&& \downarrow \\ \\[-10pt]
-  \vc{
-  \begin{tikzpicture}[net]
-	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-	\Vlink[violet,l,label={$\scriptstyle[x/z]$~~~}]{[2]2,3}
-  \end{tikzpicture}}
-& \leftarrow &
-  \vc{
-  \begin{tikzpicture}[net]
-	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-	\Vlink[red,l,label={$\scriptstyle[x/z]$~~}]{2,2}
-	\Vlink[blue,r,label={~~~$\scriptstyle[x/z]$}]{[4]2,4}
-  \end{tikzpicture}}
-& \leftarrow &
-  \vc{
-  \begin{tikzpicture}[net]
-	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-	\Vlink[red,l,label={$\scriptstyle[x/z]$~~}]{2,2}
-	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{4,4}
-  \end{tikzpicture}}
-\\ \\[-10pt] \downarrow &&&& \\ \\[-10pt]
-  \vc{
-  \begin{tikzpicture}[net]
-	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-	\Vlink[violet,l,label={$\scriptstyle\varnothing$~~}]{2,1}
-  \end{tikzpicture}}
-& \scoal &
-  \vc{
-  \begin{tikzpicture}[net]
-	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-	\Vlink[violet,l,label={$\scriptstyle\varnothing$~~}]{1,1}
-  \end{tikzpicture}}
-\end{array}
-\]
-
-%\vc{\scalebox{0.5}{$
-%	\infer[\Qrr!]{\Seq{\forall x.\exists y.\dual P(y)\+\dual Q(x,y)}{\exists z.P(f(z))\*Q(z,t)}}{
-%	 \infer[\Qrr?,x]{\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{\exists z.P(f(z))\*Q(z,t)}}{
-%	  \infer[\Qrr*]{\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{P(f(x))\*Q(x,t)}}{
-%	   \infer[\Qrr?{f(x)}]{\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{P(f(x))}}{
-%	    \infer[\Qrr+1]{\Seq{\dual P(f(x))\+\dual Q(x,f(x))}{P(f(x))}}{
-%	     \infer[\Qrr1]{\Seq{\dual P(f(x))}{P(f(x))}}{}
-%	   }}&
-%	   \infer[\Qrr?t]{\Seq{\exists y.\dual P(y)\+\dual Q(x,y)}{Q(x,t)}}{
-%	    \infer[\Qrr+2]{\Seq{\dual P(t)\+\dual Q(x,t)}{Q(x,t)}}{
-%	     \infer[\Qrr1]{\Seq{\dual Q(x,t)}{Q(x,t)}}{}
-%	}}}}}
-
-%
-%\[
-%\begin{array}{@{}ccc@{}}
-%  \vc{
-%  \begin{tikzpicture}[net]
-%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-%	\Vlink[red,l,label={$\scriptstyle[f(x)/y\,,\,x/z]$~~}]{3,2}
-%	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
-%  \end{tikzpicture}}
-%& \stackrel{\srr+1}\scoal &
-%  \vc{
-%  \begin{tikzpicture}[net]
-%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-%	\Vlink[red,l,label={$\scriptstyle[f(x)/y\,,\,x/z]$~~~}]{4,2}
-%	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
-%  \end{tikzpicture}}
-%\\ \\[-5pt] && \downarrow\scriptstyle\srr?,f(x) \\ \\[-5pt]
-%  \vc{
-%  \begin{tikzpicture}[net]
-%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-%	\Vlink[red,l,label={$\scriptstyle[x/z]$~~}]{2,2}
-%	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{4,4}
-%  \end{tikzpicture}}
-%& \stackrel{\srr+2}\leftarrow &
-%  \vc{
-%  \begin{tikzpicture}[net]
-%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-%	\Vlink[red,l,label={$\scriptstyle[x/z]$~~}]{2,2}
-%	\Vlink[blue,r,label={~$\scriptstyle[t/y\,,\,x/z]$}]{5,4}
-%  \end{tikzpicture}}
-%\\ \\[-5pt] \downarrow\scriptstyle\srr?,t \\ \\[-5pt]  
-%  \vc{
-%  \begin{tikzpicture}[net]
-%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-%	\Vlink[red,l,label={$\scriptstyle[x/z]$~~}]{2,2}
-%	\Vlink[blue,r,label={~~~$\scriptstyle[x/z]$}]{[4]2,4}
-%  \end{tikzpicture}}
-%& \stackrel{\srr*}\scoal & 
-%  \vc{
-%  \begin{tikzpicture}[net]
-%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-%	\Vlink[violet,l,label={$\scriptstyle[x/z]$~~~}]{[2]2,3}
-%  \end{tikzpicture}}
-%\\ \\[-5pt] && \downarrow\scriptstyle\srr?,x \\ \\[-5pt]
-%  \vc{
-%  \begin{tikzpicture}[net]
-%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-%	\Vlink[violet,l,label={$\scriptstyle\varnothing$~~}]{1,1}
-%  \end{tikzpicture}}
-%& \stackrel{\srr!}\leftarrow &
-%  \vc{
-%  \begin{tikzpicture}[net]
-%	\formula[y=1.2]{\forall*{x.}\exists*{y.~}{\dual P}*{(y)}\+{\dual Q}*{(x,y)}}
-%	\formula[y=0]{\exists*{z.~}P*{(f(z))}\*Q*{(z,t)}}
-%	\Vlink[violet,l,label={$\scriptstyle\varnothing$~~}]{2,1}
-%  \end{tikzpicture}}
-%\end{array}
-%\]
-
-%\[
-%	\vc{
-%	 \infer[\Qrr*]{\seq{A\*B}{\exists x.C}}{
-%	  \infer[\Qrr?y]{\seq A{\exists x.C}}{\seq AC}
-%	  &
-%	  \infer[\Qrr?z]{\seq B{\exists x.C}}{\seq BC}
-%	}}
-%	\quad\sim\quad
-%	\vc{
-%	 \infer[\Qrr?y]{\seq{A\*B}C}{
-%	  \infer[\Qrr*]{\seq{A\*B}{\exists x.C}}{
-%	   \seq AC
-%	   &
-%	   \seq BC
-%	}}}
-%\]

### 2018-08-07 ALL1.tex
update theorem also in appendix

@@
 \label{thm:composition}
-If proof nets $\net{\lambda_\Sigma}AB$ and $\net{\kappa_\Theta}{\dual B}C$ sequentialize to $\pi$ and $\phi$ respectively, then their composition $(\net{\lambda_\Sigma}AB)\comp(\net{\kappa_\Theta}{\dual B}C)$ is well-defined (i.e.\ all fixed points are finite), and sequentializes to a normal form $\psi$ of $\pi\comp\phi$.
+If proof nets $\net{\lambda_\Sigma}AB$ and $\net{\kappa_\Theta}{\dual B}C$ sequentialize to $\pi$ and $\phi$ respectively, then their composition $(\net{\lambda_\Sigma}AB)\comp(\net{\kappa_\Theta}{\dual B}C)$ is well-defined (i.e.\ all fixed points are finite) and sequentializes to a normal form $\psi$ of $\pi\comp\phi$.
 \end{theorem}
@@
 \begin{theorem}[Restatement]
-If proof nets $\net{\lambda_\Sigma}AB$ and $\net{\kappa_\Theta}{\dual B}C$ sequentialize to $\pi$ and $\phi$ respectively, then their composition $(\net{\lambda_\Sigma}AB)\comp(\net{\kappa_\Theta}{\dual B}C)$ sequentializes to a normal form $\psi$ of $\pi\comp\phi$.
+If proof nets $\net{\lambda_\Sigma}AB$ and $\net{\kappa_\Theta}{\dual B}C$ sequentialize to $\pi$ and $\phi$ respectively, then their composition $(\net{\lambda_\Sigma}AB)\comp(\net{\kappa_\Theta}{\dual B}C)$ is well-defined (i.e.\ all fixed points are finite) and sequentializes to a normal form $\psi$ of $\pi\comp\phi$.
 \end{theorem}

### 2018-08-07 ALL1.tex
minor typo stuff

@@
 The issue is more pronounced where quantifiers are \emph{vacuous}, $\exists x.A$ with $x$ not free in $A$.
-The proofs below left can only be distinguished even syntactically because the $\exists R$-rule makes the instantiating witness explicit.
-Below right is an interesting intermediate variant: the witness $s$ or $t$ can be observed without explicit annotation in the $\exists R$-rule, but the choice is equally immaterial to the content of the proof as when the quantifier were vacuous.
+The proofs below left can only be distinguished even syntactically because the $\exists\mathrm R$ rule makes the instantiating witness explicit.
+Below right is an interesting intermediate variant: the witness $s$ or $t$ can be observed without explicit annotation in the $\exists\mathrm R$ rule, but the choice is equally immaterial to the content of the proof as when the quantifier were vacuous.
 \[
@@
 \]
-The first two steps (above middle and right) move both links from the subformula $\dual Pxy$ to $\exists y.\dual Pxy$, removing the substitutions $[s/y]$ and $[t/y]$ on $y$, and corresponding to sequent rules $\exists R,s$ and $\exists R,t$.
+The first two steps (above middle and right) move both links from the subformula $\dual Pxy$ to $\exists y.\dual Pxy$, removing the substitutions $[s/y]$ and $[t/y]$ on $y$, and corresponding to sequent rules $\qrr?s$ and $\qrr?t$.
 Observe that we maintain the domain of the substitutions on a link as the variables of those existential quantifiers that either linked subformula is (strictly) in scope of.
@@
 Since we will be working with a graphical representation, we will adopt \defn{Barendregt's convention}, that bound variable names are globally unique identifiers, in the following form.
-In a sequent $\seq AB$, we assume all quantifiers to have a unique binding variable, distinct from any free variable.
+In a sequent $\seq AB$ we assume all quantifiers to have a unique binding variable, distinct from any free variable.
 In a proof $\pi$ over $\seq AB$, a variable $x$ that is universally quantified as $\forall x.C$ in $\seq AB$ is an \defn{eigenvariable}.
@@
 We take variable names to be persistent throughout a proof, in the sense that we don't admit alpha-conversion between proof rules.
-We thus have unique bound variable names in $\seq AB$, but in $\pi$ all rules on the subformula $\forall x.C$ share the same eigenvariable $x$.
+We thus have unique bound variable names in $\seq AB$, but in $\pi$ all $\qrr!$ rules on the subformula $\forall x.C$ share the same eigenvariable $x$.
 

### 2018-08-07 ALL1.tex
roar fixes, combined Lambek citations into one

@@
 Composition is direct, by relational composition.
-We compare further properties in Figure~\ref{fig:results} in the conclusion, where we also discuss related work and Lambek's notion of \defn{generality} \cite{Lambek-1968, Lambek-1969, Lambek-1972}.
+We compare further properties in Figure~\ref{fig:results} in the conclusion, where we also discuss related work and Lambek's notion of \defn{generality} \cite{Lambek-1968-1972}.
+%\cite{Lambek-1968, Lambek-1969, Lambek-1972}.
 
@@
 This captures the non-permutability of a product rule over distinct instantiations, as below left.
+	\item[Dependency]
+We define a \defn{dependency} relation between a universal quantification $\forall x.A$ and an instantiation $B[t/y]$ of $\exists x.B$ where the \defn{eigenvariable} $x$ occurs free in $t$ (a standard approach to first-order quantification \cite{Miller-1987,Girard-1996,Heijltjes-2010,Mimram-2011}).
+For each link, we require the dependency to be \emph{acyclic}, which amounts to \emph{slice-wise} first-order correctness.
+It captures the non-permutability of universal and existential sequent rules due to the \emph{eigenvariable condition} of the former, as below right.
 	\item[]
@@
 \]
-	\item[Dependency]
-We define a \defn{dependency} relation between a universal quantification $\forall x.A$ and an instantiation $B[t/y]$ of $\exists x.B$ where the \defn{eigenvariable} $x$ occurs free in $t$ (a standard approach to first-order quantification \cite{Miller-1987,Girard-1996,Heijltjes-2010,Mimram-2011}).
-For each link, we require the dependency to be \emph{acyclic}, which amounts to \emph{slice-wise} first-order correctness.
-It captures the non-permutability of universal and existential sequent rules due to the \emph{eigenvariable condition} of the former, as below right.
 \end{description}
@@
 
-The idea of using \emph{generality} as a basis for proof identity originates with Lambek \cite{Lambek-1968,Lambek-1969,Lambek-1972}, who observed that the two canonical proofs of $\seq{A{\+}A}{\dual A}$ can be distinguished by casting each as a specialization (by substituting into propositional variables) of the more general proofs of $\seq{\,a{\+}b}{\dual a}$ and $\seq{\,a{\+}b}{\dual b}$.
+The idea of using \emph{generality} as a basis for proof identity originates with Lambek \cite{Lambek-1968-1972}, 
+%\cite{Lambek-1968,Lambek-1969,Lambek-1972}, 
+who observed that the two canonical proofs of $\seq{A{\+}A}{\dual A}$ can be distinguished by casting each as a specialization (by substituting into propositional variables) of the more general proofs of $\seq{\,a{\+}b}{\dual a}$ and $\seq{\,a{\+}b}{\dual b}$.
 Curiously, how this extends to the first-order setting is not obvious.

### 2018-08-07 ALL1.tex
minor terminology refinement

@@
 The local witness substitution $[t/x]$ in a rule instance $\qrr?t$ will have been applied exactly to the axioms $\seq a{\dual a}$ in the subproof of that rule.
-Correspondingly, for a link $\link CD$ on $\seq AB$ we expect the domain of $\sigma$ to be exactly the existential variables in $A$ and $B$ in whose scope $C$ and $D$ occur.
-For a subformula $C$ of $A$, let the \defn{existential variables of $C$ in $A$} be the set $\ex[A]C = \{\,x \mid C < \exists x.X \sub A\,\}$.
+Correspondingly, for a link $\link CD$ on $\seq AB$ we expect the domain of $\sigma$ to be exactly the existential variables in $A$ and $B$ that are free in $C$ and $D$.
+For a subformula $C$ of $A$, let the \defn{free existential variables} of $C$ in $A$ be the set $\ex[A]C = \{\,x \mid C < \exists x.X \sub A\,\}$.
 A link $\link CD$ on $\seq AB$ then has \defn{exact coverage} if $\dom\sigma = \ex[A]C\cup\ex[B]D$.
@@
 \\
-Since the existential covers of $B$ and $B_1$ are the same, $\sigma_B\tau\subdual B = \sigma_{B_1}\tau\subdual{B_1}$ and $\rho=\rho'$.
+Since the free existential variables of $B$ and $B_1$ are the same, $\sigma_B\tau\subdual B = \sigma_{B_1}\tau\subdual{B_1}$ and $\rho=\rho'$.
 It then follows that $\psi'$ cut-eliminates in one step to $\psi$.
@@
 The column of $\link AD$ contains $(D,\sigma_D)$ and $(\forall x.D,\tau)$ where $\tau=\sigma\res{\ex[B]{\forall x.D}}$.
-By the exact coverage condition, $\sigma=\sigma_A\cup\sigma_D$, and since the existential variables in $D$ and $\forall x.D$ are the same, $\ex[B]D=\ex[B]{\forall x.D}$, so that $\tau=\sigma_D$.
+By the exact coverage condition, $\sigma=\sigma_A\cup\sigma_D$, and since the free existential variables in $D$ and $\forall x.D$ are the same, $\ex[B]D=\ex[B]{\forall x.D}$, so that $\tau=\sigma_D$.
 (Note that since $\sigma_A=\varnothing$, we get $\sigma=\sigma_D=\tau$, but this is not essential to the argument.) Since $x\in\sigma$ we have $x\in\tau$, and in the column of $\link AD$ we have $(\forall x.D,\tau)\dep(D,\tau)$ since $D$ occurs as $\forall x.D$.

### 2018-08-07 ALL1.tex
subtle

@@
 The local witness substitution $[t/x]$ in a rule instance $\qrr?t$ will have been applied exactly to the axioms $\seq a{\dual a}$ in the subproof of that rule.
-Correspondingly, for a link $\link CD$ on $\seq AB$ we expect the domain of $\sigma$ to be exactly the existential variables in $A$ and $B$ that are free in $C$ and $D$.
+Correspondingly, for a link $\link CD$ on $\seq AB$ we expect the domain of $\sigma$ to be exactly the existential variables in $A$ and $B$ that (could) occur free in $C$ and $D$.
 For a subformula $C$ of $A$, let the \defn{free existential variables} of $C$ in $A$ be the set $\ex[A]C = \{\,x \mid C < \exists x.X \sub A\,\}$.

### 2018-08-07 ALL1.tex
further referee-induced changes

@@
 
-We conclude this section by establishing that sequentialization and de-sequentialization for witness nets are inverses.
+We conclude this section by establishing that sequentialization and de-sequentialization for witness nets are inverses, and that witness nets are canonical.
 
@@
 % ..................................................
+
+\begin{theorem}
+Witness nets are canonical: $[\pi]=[\phi]$ if and only if $\pi\sim\phi$.
+\end{theorem}
+
+\begin{proof}
+From left to right is by inspection of the critical pairs of sequentialization ($\scoal$).
+From right to left is by inspection of the rule permutations in Figure~\ref{fig:permutations} in Appendix~\ref{sec:permutations}.
+\end{proof}
 
@@
 We will here use slices for the latter purpose.
-%
 As in the propositional case \cite{Hughes-vanGlabbeek-2005}, we define a \defn{slice} of a sequent $\seq AB$ as a set of potential links, of which exactly one must be realized in a proof net $\net{\lambda_\Sigma}AB$.
@@
 This captures the non-permutability of a product rule over distinct instantiations, as below left.
+(Technically, a slice of $\exists x.A$ will correspond to an infinite sum over $A[t/x]$ for every term $t$, but only the actually occurring terms $t_i$ will ever be relevant.)
+
 	\item[Dependency]
-We define a \defn{dependency} relation between a universal quantification $\forall x.A$ and an instantiation $B[t/y]$ of $\exists x.B$ where the \defn{eigenvariable} $x$ occurs free in $t$ (a standard approach to first-order quantification \cite{Miller-1987,Girard-1996,Heijltjes-2010,Mimram-2011}).
-For each link, we require the dependency to be \emph{acyclic}, which amounts to \emph{slice-wise} first-order correctness.
+We define a \defn{dependency} relation between a universal quantification $\forall x.A$ and an instantiation $B[t/y]$ of $\exists y.B$ where the eigenvariable $x$ occurs free in $t$ (a standard approach to first-order quantification \cite{Miller-1987,Girard-1996,Heijltjes-2010,Mimram-2011}).
+For each link, we will require this dependency relation to be \emph{acyclic}, which amounts to \emph{slice-wise} first-order correctness.
 It captures the non-permutability of universal and existential sequent rules due to the \emph{eigenvariable condition} of the former, as below right.
@@
 
-\noindent
-Formalizing this, for a witness linking $\lambda_\Sigma$ and variable $x$, write $\Sigma(x)\subseteq\terms$ for the \defn{witness set} of $x$, which collects the terms assigned to $x$ by the witness maps in $\Sigma$ for every link in $\lambda$:
-\[
-	\Sigma(x) = \{~\sigma(x)~\mid~\link CD\in\lambda_\Sigma~\}~.
-\]
+%\noindent
+%Formalizing this, for a witness linking $\lambda_\Sigma$ and variable $x$, write $\Sigma(x)\subseteq\terms$ for the \defn{witness set} of $x$, which collects the terms assigned to $x$ by the witness maps in $\Sigma$ for every link in $\lambda$:
+%\[
+%	\Sigma(x) = \{~\sigma(x)~\mid~\link CD\in\lambda_\Sigma~\}~.
+%\]
 
@@
 \begin{definition}[Slice]
-Given a witness linking $\lambda_\Sigma$, a \defn{slice} $S$ of a formula $A$ and a witness map $\sigma$ is a set of pairs $(A',\sigma')$, where $A'\leq A$ and $\sigma'\supseteq\sigma$, given by $S=\{(A,\sigma)\}\cup S'$ where:
+A \defn{slice} $S$ of a formula $A$ and a witness map $\sigma$ is a set of pairs $(A',\sigma')$, where $A'\leq A$ and $\sigma'\supseteq\sigma$, given by $S=\{(A,\sigma)\}\cup S'$ where:
 %
@@
 	\item
-\makebox[65pt][l]{If $A = \exists x.B$}	then $S'=\uplus_{t\,\in\,\Sigma(x)}S_t$ where each $S_t$ is a slice of $B$ and $\sigma[t/x]$.
+\makebox[65pt][l]{If $A = \exists x.B$}	then $S'=\uplus_{t\,\in\,\terms}S_t$ where each $S_t$ is a slice of $B$ and $\sigma[t/x]$.
 	\item
@@
 \]
-with a \defn{dependency} order $(\dep)$: $(X,\rho)\dep(Y,\tau)$ if $X\leq Y$ or $Y$ occurs as $\forall x.Y$ and $x\in\rho$.
+with a \defn{dependency} relation $(\dep)$: $(X,\rho)\dep(Y,\tau)$ if $X\leq Y$ or $Y$ occurs as $\forall x.Y$ and $x\in\rho$.
 \end{definition}
@@
 % ..................................................
-
-\begin{theorem}
-Witness nets are canonical: $[\pi]=[\phi]$ if and only if $\pi\sim\phi$.
-\end{theorem}
-
-\begin{proof}
-From left to right is by inspection of the critical pairs of sequentialization ($\scoal$).
-From right to left is by inspection of the rule permutations in Figure~\ref{fig:permutations} in Appendix~\ref{sec:permutations}.
-\end{proof}
 
@@
 	 &&
-	 \infer[\!\!\scriptstyle{\qrr+i}]{\Seq {\dual B_1\+\dual B_2}C}{\Prf\phi{B_i}C}
+	 \infer[\!\!\scriptstyle{\qrr+i}]{\Seq {\dual B_1\+\dual B_2}C}{\Prf\phi{\dual B_i}C}
 	}}
@@
 %
-A link $\link[]ab$ on two atomic formulas is an \defn{axiom} link if there exists a witness map $\sigma$ such that $a\sigma=\dual b\sigma$.
-To an axiom link $\link[]ab$ over $\seq AB$ we assign an \defn{initial witness map}, which is the least witness map $\sigma$ over the domain $\ex[\!A]a\cup\ex[\!B]b$ such that $a\sigma=\dual b\sigma$.
-In other words, $\sigma$ is the most general unifier of $a$ and $\dual b$, over the given domain, written $\init ab$.
+A link $\link[]ab$ on two atomic formulas is an \defn{axiom} link if there exists a witness map $\sigma$ such that $\dual a\sigma=b\sigma$.
+To an axiom link $\link[]ab$ over $\seq AB$ we assign an \defn{initial witness map}, which is the least witness map $\sigma$ over the domain $\ex[\!A]a\cup\ex[\!B]b$ such that $\dual a\sigma=b\sigma$.
+In other words, $\sigma$ is the most general unifier of $\dual a$ and $b$, over the given domain, written $\init{\dual a}b$.
 For an axiom linking $\lambda$ over $\seq AB$ the \defn{initial witness pre-net} $\net{\lambda_\star}AB$ is given by
 \[
-	\lambda_\star = \{~\link ab~\mid~\link[]ab\in\lambda~,~\sigma=\init ab~\}~.
+	\lambda_\star = \{~\link ab~\mid~\link[]ab\in\lambda~,~\sigma=\init{\dual a}b~\}~.
 \]
@@
 
-In the above definition, note that $\lambda_\star^\star=(\lambda_\star)^*$ is the initial proof labelling of $\lambda_\star$, which assigns an axiom rule to each axiom link.
+In the above definition, note that $\lambda_\star^\star=(\lambda_\star)^\star$ is the initial proof labelling of $\lambda_\star$, which assigns an axiom rule to each axiom link.
 For a minimal example, see the introduction.
@@
 
-Our slicing condition is closely related to a number of approaches to first-order classical logic.
+Our slicing condition is loosely related to a number of approaches to first-order classical logic.
 A formula $\exists x.A$ is interpreted as the sum (or classically, the \emph{disjunction}) over a fixed number of instantiations $A[t_1/x]\+\dots\+A[t_n/x]$.
@@
 
-In our slicing condition, the witnesses $t_1,\dots,t_n$ for the expansion $A[t_1/x]\+\dots\+A[t_n/x]$ are collected from the substitutions recorded at the links of the proof net.
-Expansion trees, in contrast, record the expansion and its terms explicitly.
-This could be an interesting alternative approach to additive proof nets, which we may explore in future work.
-It is expected, though, that this would sacrifice \emph{generality} and \emph{direct composition}.
+In our slicing condition, the interpretation of $\exists x.A$ is an infinite sum of which only a finite part $A[t_1/x]\+\dots\+A[t_n/x]$ is relevant, over the witnesses $t_1,\dots,t_n$ actually assigned to $x$ in the proof net.
+An interesting alternative approach to additive proof nets, which we may explore in future work, could be to take the expansion of $\exists x.A$ to $A[t_1/x]\+\dots\+A[t_n/x]$ as primary, and record it explicitly in the syntax, as expansion tree proofs do for classical logic.
+It is expected, however, that this would sacrifice \emph{generality} and \emph{direct composition}.
 
@@
 Let $L=\net{\lambda_\Sigma}AB$ and $R=\net{\kappa_\Theta}AB$.
-In each case, exact coverage is immediately preserved and reflected.
+In each case, exact coverage and local eigenvariables are immediately preserved and reflected.
 For slice-correctness, we will demonstrate that the left-hand side and right-hand side of each rule belong to the same slice of $\seq AB$, or in the case of $\srr?$, naturally corresponding slices.
@@
 \\
-The witness sets $\Sigma(x)$ and $\Theta(x)$ for $L$ and $R$ need not be the same, since $L$ has $\sigma$ where $R$ has $\sigma\minus x$.
+A slice $S$ of $\seq AB$ contains $\link[\tau] C{\exists x.D}$ if and only if it contains all links $\link[\tau{[t/x]}]CD$ for any term $t$.
+Letting $\tau[t/x]=\sigma$, then $S\cap \lambda_\Sigma$ is the singleton $\{\link CD\}$ if and only if $S\cap\kappa_\Theta$ is $\{\link[\sigma\minus x]C{\exists x.D}\}$.
+%
+%The witnesses sets $\Sigma(x)$ and $\Theta(x)$ for $L$ and $R$ need not be the same, since $L$ has $\sigma$ where $R$ has $\sigma\minus x$.
 Let $\Sigma(x)=\{t,t_1,\dots,t_n\}$ and $\Theta(x)=\{t_1,\dots,t_n\}$, where $\sigma(x)=t$.

### 2018-08-13 ALL1.tex
fixes re: Dominic's comments

@@
  {University of Bath, United Kingdom}
- {{http://willem.heijltj.es/}} %{w.b.heijltjes@bath.ac.uk}
+ {{http://willem.heijltj.es}} %{w.b.heijltjes@bath.ac.uk}
  {}
@@
  {Logic Group, UC Berkeley, USA}
- {{http://boole.stanford.edu/\textasciitilde dominic/}} %{dominich@theory.stanford.edu}
+ {{http://boole.stanford.edu/\textasciitilde dominic}} %{dominich@theory.stanford.edu}
  {}
@@
  {Inria Saclay \&\ LIX/\'Ecole Polytechnique, Palaiseau, France}
- {{http://www.lix.polytechnique.fr/Labo/Lutz.Strassburger/}} %{lutz.strassburger@inria.fr}
+ {{http://www.lix.polytechnique.fr/Labo/Lutz.Strassburger}}
+ %{lutz.strassburger@inria.fr}
  {}
@@
 Unification nets in addition factor out any inessential choice for existential witnesses.
-Both notions of proof net are defined through coalescence, the additive version of multiplicative contractibility, and for witness nets an additional geometric correctness criterion is provided.
-Both feature a global composition operation.
+Both notions of proof net are defined through coalescence, an additive counterpart to multiplicative contractibility, and for witness nets an additional geometric correctness criterion is provided.
+% 
+Both capture sequent calculus cut-elimination as a one-step global composition operation.
 \end{abstract}
@@
 It is naturally captured in \defn{proof nets} \cite{Girard-1987,Hughes-vanGlabbeek-2005}, which describe a morphism $A\to B$ by a sequent $\seq{\dual A}B$ plus a \defn{linking}, a relation between the propositional atoms of $\dual A$ and those of $B$.
+Four examples are illustrated below left.
 %
 Additive proof nets are \defn{canonical}: they factor out the permutations of sequent calculus, and correspond 1--1 to morphisms of the free category.
-%
-\[
+\defn{Composition}, of proof nets over $\seq{\dual A}B$ and $\seq{\dual B}C$ to one over $\seq{\dual A}C$, is by the relational composition of their linkings along the dual formulas $B$ and $\dual B$ (as illustrated below right), and captures sequent-calculus cut-elimination.
+%
+%\[
 %\hspace*{9ex}% spacing hack to achieve central horizontal alignment
 % Behold my better spacing hack to achieve central horizontal alignment :)
+%\hspace*{-\parindent}%
+%\hspace*{\fill}%
+%\begin{array}{c@{\qquad\qquad}c}
+%	\begin{tikzpicture}[net]
+%		\formula[y=1]{{\dual a}}
+%		\formula[y=0]{a\*a}
+%		\Vlink[red]{[-2]1,1}
+%		\Vlink[red]{[2]1,3}
+%	\end{tikzpicture}
+%&
+%	\begin{tikzpicture}[net]
+%		\formula[y=1]{{\dual a}}
+%		\formula[y=0]{a\+b}
+%		\Vlink[red]{1,1}
+%	\end{tikzpicture}
+%\\
+%	\text{\small diagonal}
+%&	\text{\small injection}	
+%\\ \\ \\[-10pt]
+%	\begin{tikzpicture}[net]
+%		\formula[y=1]{{\dual a}\+{\dual b}}
+%		\formula[y=0]{b\*a}
+%		\Vlink[red]{1,3}
+%		\Vlink[red]{3,1}
+%	\end{tikzpicture}
+%&
+%	\begin{tikzpicture}[net]
+%		\formula[y=1]{*{\phantom(}{\dual a}*{\phantom)}
+%		 {{\+}}*({\dual b}*{\phantom)}
+%		 {{\+}}*{\phantom(}{\dual c}*)}
+%		\formula[y=0]{*(a*{\phantom)}
+%		{{\*}}*{\phantom(}b*)
+%		{{\*}}*{\phantom(}c*{\phantom)}}
+%		\Vlink[red]{1,1}
+%		\Vlink[red]{3,3}
+%		\Vlink[red]{5,5}
+%	\end{tikzpicture}
+%\\
+%	\text{\small symmetry}
+%&	\text{\small associativity}
+%\end{array}
+%\qquad\qquad\qquad
+%\begin{array}{c}
+%    \vc{\begin{tikzpicture}[net]
+%        \formula[y=2.5]{{\dual b}*\+{\dual a}}
+%        \formula[y=1.5]{a*\**(b*\+b*)}
+%            \Vlink[red]{1,2}
+%            \Vlink[red]{2,1}
+%        \formula[y=1]{{\dual a}*\+*({\dual b}*\*{\dual b}*)}
+%        \formula[y=0]{b*\*b}
+%            \Vlink[blue]{[-1]2,[-1]1}
+%            \Vlink[blue]{[1]2,[-1]2}
+%            \Vlink[blue]{[-1]3,[1]1}
+%            \Vlink[blue]{[1]3,[1]2}
+%    \end{tikzpicture}}
+%\quad\Rightarrow\quad
+%    \vc{\begin{tikzpicture}[net]
+%        \formula[y=2.5]{{\dual b}*\+{\dual a}}
+%        \formula[y=0]{b*\*b}
+%            \Vlink[violet]{[-1]1,1}
+%            \Vlink[violet]{[1]1,2}
+%    \end{tikzpicture}}
+%\\ \\[-5pt]
+%	\text{\small composition}
+%\end{array}
+%\hfill
+%\]
+\[
 \hspace*{-\parindent}%
 \hspace*{\fill}%
-\begin{array}{c@{\qquad\qquad}c}
-	\begin{tikzpicture}[net]
+\begin{array}{@{}rc@{\qquad}rc@{}}
+	\text{\small diagonal:}
+&	\vc{\begin{tikzpicture}[net]
 		\formula[y=1]{{\dual a}}
@@
 		\Vlink[red]{[2]1,3}
-	\end{tikzpicture}
-&
-	\begin{tikzpicture}[net]
+	\end{tikzpicture}}
+&	\text{\small injection:}	
+&   \vc{\begin{tikzpicture}[net]
 		\formula[y=1]{{\dual a}}
@@
 		\Vlink[red]{1,1}
-	\end{tikzpicture}
-\\
-	\text{\small diagonal}
-&	\text{\small injection}	
-\\ \\ \\[-10pt]
-	\begin{tikzpicture}[net]
+	\end{tikzpicture}}
+\\ \\
+	\text{\small symmetry:}
+&	\vc{\begin{tikzpicture}[net]
 		\formula[y=1]{{\dual a}\+{\dual b}}
@@
 		\Vlink[red]{3,1}
-	\end{tikzpicture}
-&
-	\begin{tikzpicture}[net]
+	\end{tikzpicture}}
+&	\text{\small associativity:}
+&	\vc{\begin{tikzpicture}[net]
 		\formula[y=1]{*{\phantom(}{\dual a}*{\phantom)}
@@
 		\Vlink[red]{5,5}
-	\end{tikzpicture}
-\\
-	\text{\small symmetry}
-&	\text{\small associativity}
+	\end{tikzpicture}}
 \end{array}
-\qquad\qquad\qquad
-\begin{array}{c}
+\qquad
+	\text{\small composition:}
+	\quad
     \vc{\begin{tikzpicture}[net]
@@
     \end{tikzpicture}}
-\quad\Rightarrow\quad
+~~\Rightarrow~~
     \vc{\begin{tikzpicture}[net]
@@
     \end{tikzpicture}}
-\\ \\[-5pt]
-	\text{\small composition}
-\end{array}
 \hfill
-\]
-\defn{Composition}, of proof nets over $\seq{\dual A}B$ and $\seq{\dual B}C$ to one over $\seq{\dual A}C$, is by the relational composition of their linkings along the dual formulas $B$ and $\dual B$, as illustrated above right.
+% Tightening the text and spacing the 
+\rule[-55pt]{0pt}{110pt}
+\]
+
+% ALTERNATIVE (cuts one line) 
+%
+%We present proof nets for first-order additive linear logic (\all1).
+Our main challenge is to incorporate the essential content of first-order proof, the \defn{witness assignment} to existential quantifiers, into additive proof nets.
+Commonly, as in the sequent rule below left, a witness to $\exists x.B$ is assigned by a substitution $B[t/x]$.
+To assign different witnesses in different branches of a proof, the subformula is copied first, giving $B[s/x]$ and $B[t/x]$, as below right.
 
@@
 Our central challenge is to incorporate the essential content of first-order proof, the \defn{witness assignment} to existential quantifiers, into additive proof nets.
-In a standard approach, as in the sequent calculus rules below left, a witness to $\exists x.B$ is assigned by an immediate substitution $B[t/x]$.
+In a standard approach, as in the sequent calculus rule below left, a witness to $\exists x.B$ is assigned by an immediate substitution $B[t/x]$.
 To assign different witnesses in different branches of a proof, the subformula may be duplicated first, giving $B[s/x]$ and $B[t/x]$, as below right.
@@
 	\vc{\infer[\Qrr?t]{\seq A{\exists x.B}}{\seq A{B[t/x]}}}
-\qquad\quad
+\hfill
 \vc{
@@
 %
-This is incompatible with a \defn{sequent + links} proof net design, where the conclusion sequent remains intact, and a subformula $B$ cannot be the subject of substitution or duplication.
+This is incompatible with a \defn{sequent\,+\,links} proof net design, where the conclusion sequent remains intact, and a subformula $B$ cannot be the subject of substitution or duplication.
 Instead, we propose two alternative treatments of witnessing terms, embodied in two notions of proof net: \defn{witness nets} and \defn{unification nets}.
@@
 %
+
+\defn{Witness nets} record witness assignment in substitution maps attached to each link.
+The example below left shows the proof net for the sequent proof earlier.
+(We will assume a different variable for each quantifier, and we attach links to predicate letters, as the root connective of an atomic proposition.) Witness nets are canonical for \all1 sequent calculus permutations.
+Composition is direct, where the witness assignments of links are composed through a simple process of \emph{interaction\,+\,hiding} similar to that of game semantics \cite{Mimram-2011}.
+
+\defn{Unification nets} omit any witness information, as illustrated below right.
+In addition to canonicity, they embody a notion of \defn{generality}: where more than one witness could be assigned, unification nets do not require a definite choice, while witness nets do.
+Composition is direct, by relational composition.
+We compare further properties in Figure~\ref{fig:results} in the conclusion, where we also discuss related work and Lambek's notion of \defn{generality} \cite{Lambek-1968-1972}.
+%\cite{Lambek-1968, Lambek-1969, Lambek-1972}.
+%
 \[
@@
 \hspace*{-\parindent}
-\begin{array}{c@{\qquad\qquad\qquad\qquad\qquad}c}
+	\text{\small a witness net:}
+	\quad
 	\vc{\begin{tikzpicture}[net]
@@
 	\end{tikzpicture}}
-&
+\hfill
+	\text{\small a unification net:}
+	\quad
 	\vc{\begin{tikzpicture}[net]
@@
 	\end{tikzpicture}}
-\\ \\[-5pt]
-	\text{\small a witness net}
-&	\text{\small a unification net}
-\end{array}
 \hfill
 \]
-
-\defn{Witness nets} record witness assignment in substitution maps attached to each link.
-The example above left shows the proof net for the sequent proof above.
-(We will assume a different variable for each quantifier, and we attach links to predicate letters, as the root connective of an atomic proposition.) Witness nets are canonical for \all1 sequent calculus permutations.
-Composition is direct, where the witness assignments of links are composed through a simple process of \emph{interaction + hiding} similar to that of game semantics \cite{Mimram-2011}.
-
-\defn{Unification nets} omit any witness information, as illustrated above right.
-In addition to canonicity, they embody a notion of \defn{generality}: where more than one witness could be assigned, unification nets do not require a definite choice, while witness nets do.
-Composition is direct, by relational composition.
-We compare further properties in Figure~\ref{fig:results} in the conclusion, where we also discuss related work and Lambek's notion of \defn{generality} \cite{Lambek-1968-1972}.
-%\cite{Lambek-1968, Lambek-1969, Lambek-1972}.
-
+%
 \paragraph*{Background}
-
+%
 Additive linear logic is combinatorially rich, yet well-behaved and tractable: proof search \cite{Galmiche-Marion-1995,Galmiche-2000} and proof net correctness \cite{Heijltjes-Hughes-2015} for a net over $\seq AB$ are linear in $|A|\times|B|$ (with $|A|$ the size of the syntax tree of $A$).
@@
 
-{\all} is of course part of {\mall} (multiplicative-additive linear logic), and its lessons are clearly visible in the second author's canonical proof nets \cite{Hughes-vanGlabbeek-2005} for {\mall}, as well as the first and second author's locally canonical \emph{conflict nets}~\cite{Hughes-Heijltjes-2016}.
+{\all} is of course part of {\mall} (multiplicative-additive linear logic), and its lessons are clearly visible in the second author's canonical proof nets for {\mall}~\cite{Hughes-vanGlabbeek-2005}, as well as the first and second author's locally canonical \emph{conflict nets}~\cite{Hughes-Heijltjes-2016}.
 Its proof nets also appear as the \emph{skew fibrations} in the second author's \emph{combinatorial proofs} for classical logic~\cite{Hughes-2006-proofs}, and in the third author's study of the \emph{medial rule} for classical logic~\cite{str:RTA07}.
@@
 \]
-We extend slicing to witness nets, and coalescence to both witness nets and unification nets. Here, we illustrate the latter, and leave a discussion of slicing to the conclusion of the paper.
+We extend coalescence to both witness nets and unification nets, and slicing to witness nets. Here, we illustrate the former, and leave a discussion of slicing to the conclusion of the paper.
 
@@
 
-We have presented two notions of first-order additive proof net, witness nets and unification nets, to canonically capture the two natural notions of proof identity for first-order additive linear logic.
-The table in Figure~\ref{fig:results} summarizes the results of our paper, along with some observations we make below.
-
-Proof nets with additives and quantifiers existed before as \emph{monomial nets} \cite{Girard-1996}, where slices are managed explicitly with \emph{monomial weights}.
-These nets are not generally canonical: they admit the permutation (and duplication) of proof rules past implicit \emph{contractions}.
-However, it is possible that additive monomial nets could be restricted to some notion of canonical form.
+We have presented two notions of first-order additive proof net, \emph{witness nets} and \emph{unification nets}, to canonically capture the two natural notions of proof identity for first-order additive linear logic.
+Figure~\ref{fig:results} summarizes our results, along with some observations we make below.
+
+Proof nets with additives and quantifiers existed before as \emph{monomial nets} \cite{Girard-1996}.
+These are not generally canonical: they admit the permutation (and duplication) of proof rules past implicit \emph{contractions} (that is, the shared context of the additive conjunction rule).
+However, it might possible that additive monomial nets could be restricted to some notion of canonical form.
 Likewise, coalescence (or contractibility) has not been studied for first-order monomial nets, though it has been extended to a related form of MALL proof nets \cite{Maieli-2007}.
@@
 A formula $\exists x.A$ is interpreted as the sum (or classically, the \emph{disjunction}) over a fixed number of instantiations $A[t_1/x]\+\dots\+A[t_n/x]$.
-This can be traced back to Herbrand's Theorem \cite{Herbrand-1930}: $\exists x.A$ is equivalent to the infinite sum over $A[t/x]$ for all terms $t$ in the language, but for any given proof a finite set of terms suffices.
+This can be traced to Herbrand's Theorem \cite{Herbrand-1930}: $\exists x.A$ is equivalent to the infinite sum over $A[t/x]$ for all terms $t$ in the language, but for any given proof a finite set of terms suffices.
 \emph{Expansion tree proofs} \cite{Miller-1987,Heijltjes-2010} are a graphical proof formalism based on this idea.
-
+%
 In our slicing condition, the interpretation of $\exists x.A$ is an infinite sum of which only a finite part $A[t_1/x]\+\dots\+A[t_n/x]$ is relevant, over the witnesses $t_1,\dots,t_n$ actually assigned to $x$ in the proof net.
@@
 %\paragraph*{Generality}
-
-The idea of using \emph{generality} as a basis for proof identity originates with Lambek \cite{Lambek-1968-1972}, 
+%
+%The idea of using \emph{generality} as a basis for proof identity originates with Lambek \cite{Lambek-1968-1972}, 
 %\cite{Lambek-1968,Lambek-1969,Lambek-1972}, 
-who observed that the two canonical proofs of $\seq{A{\+}A}{\dual A}$ can be distinguished by casting each as a specialization (by substituting into propositional variables) of the more general proofs of $\seq{\,a{\+}b}{\dual a}$ and $\seq{\,a{\+}b}{\dual b}$.
-Curiously, how this extends to the first-order setting is not obvious.
-
+%who observed that the two canonical proofs of $\seq{A{\+}A}{\dual A}$ can be distinguished by casting each as a specialization (by substituting into propositional variables) of the more general proofs of $\seq{\,a{\+}b}{\dual a}$ and $\seq{\,a{\+}b}{\dual b}$.
+%
+Lambek observed that the two canonical proofs of $\seq{A{\+}A}{\dual A}$ can be distinguished by casting each as a specialization (by substituting into propositional variables) of the more general proofs of $\seq{\,a{\+}b}{\dual a}$ and $\seq{\,a{\+}b}{\dual b}$ (corresponding to the two injections of a sum).
+He proposed to use this idea of \emph{generality} as the basis for a notion of \emph{proof identity}: two proofs are equivalent if their most general forms are isomorphic \cite{Lambek-1968-1972}.
+How this extends to first order is not obvious.
 The natural first-order analogue of $\seq{A{\+}A}{\dual A}$ would be $\seq{\exists x.A}{\dual A}$ where the quantifier is vacuous, as $\exists x.A$ represents the infinite sum over $A$ (for all terms $t$).
-Where Lambek's generality \emph{distinguishes} the two proofs of $\seq{A{\+}A}{\dual A}$, ours \emph{identifies} the proofs of $\seq{\exists x.A}{\dual A}$: the sequent has one unification net, but infinitely many witness nets (one for each $t$).
-Interestingly, then, if existential quantification is indeed analogous to a sum, Lambek's notion of generality is more faithfully captured by witness nets than unification nets.
+Where Lambek's generality \emph{distinguishes} the two proofs of $\seq{A{\+}A}{\dual A}$, ours \emph{identifies} the proofs of $\seq{\exists x.A}{\dual A}$: the sequent has one unification net, but infinitely many witness nets (one for each term $t$).
+If existential quantification is indeed analogous to a sum, Lambek's notion of generality is more faithfully captured by witness nets than unification nets.
 

### 2018-09-03 ALL1-RR.tex
new intro; some variable comments

--- 2018-08-13 ALL1.tex
@@
-\documentclass[UKenglish]{lipics-v2018}
+\documentclass{article}
 
 %\usepackage {etex}
+\usepackage{geometry}
 
@@
 
-\theoremstyle{plain}
-\newtheorem{proposition}[theorem]{Proposition}
+\makeTheoremDefs
 
@@
 
+%\author
+% {Willem B.\ Heijltjes$^1$,
+%  Dominic J.D.\ Hughes$^2$, and 
+%  Lutz Stra\ss burger$^3$}
+
 \author
- {Willem B.\ Heijltjes}
- {University of Bath, United Kingdom}
- {{http://willem.heijltj.es}} %{w.b.heijltjes@bath.ac.uk}
- {}
- {}
-\author
- {Dominic J.D.\ Hughes}
- {Logic Group, UC Berkeley, USA}
- {{http://boole.stanford.edu/\textasciitilde dominic}} %{dominich@theory.stanford.edu}
- {}
- {} 
-\author
- {Lutz Stra\ss burger}
- {Inria Saclay \&\ LIX/\'Ecole Polytechnique, Palaiseau, France}
- {{http://www.lix.polytechnique.fr/Labo/Lutz.Strassburger}}
- %{lutz.strassburger@inria.fr}
- {}
- {}
-
-\authorrunning{W.B.\ Heijltjes, D.J.D.\ Hughes, and L.\ Stra\ss burger}
-
-\Copyright{Willem B.\ Heijltjes, Dominic J.D.\ Hughes, and Lutz Stra\ss burger}
-
-\subjclass{F.4.1: Mathematical logic--Proof theory}
-\keywords{Linear logic, First-order logic, Proof nets, Herbrand's Theorem}
+{
+\begin{tabular}{c}
+	Willem B.\ Heijltjes\\
+	\normalsize University of Bath, United Kingdom\\
+	\normalsize \texttt{http://willem.heijltj.es}\\
+	\\
+	Dominic J.D.\ Hughes\\
+	\normalsize Logic Group, UC Berkeley, USA\\
+	\normalsize \texttt{http://boole.stanford.edu/\textasciitilde dominic}\\
+	\\
+	Lutz Stra\ss burger\\
+	\normalsize Inria Saclay \&\ LIX/\'Ecole Polytechnique, Palaiseau, France\\
+	\normalsize \texttt{http://www.lix.polytechnique.fr/Labo/Lutz.Strassburger}\\
+\end{tabular}
+}
+
+\date{}
+
+% {}
+% {{http://willem.heijltj.es}} %{w.b.heijltjes@bath.ac.uk}
+% {}
+% {}
+% {}
+% {Logic Group, UC Berkeley, USA}
+% {{http://boole.stanford.edu/\textasciitilde dominic}} %{dominich@theory.stanford.edu}
+% {}
+% {} 
+%\author
+% {}
+% {Inria Saclay \&\ LIX/\'Ecole Polytechnique, Palaiseau, France}
+% {{http://www.lix.polytechnique.fr/Labo/Lutz.Strassburger}}
+% %{lutz.strassburger@inria.fr}
+% {}
+% {}
+
+%\authorrunning{W.B.\ Heijltjes, D.J.D.\ Hughes, and L.\ Stra\ss burger}
+
+%\Copyright{Willem B.\ Heijltjes, Dominic J.D.\ Hughes, and Lutz Stra\ss burger}
+
+%\subjclass{F.4.1: Mathematical logic--Proof theory}
+%\keywords{Linear logic, First-order logic, Proof nets, Herbrand's Theorem}
 
@@
 
-Additive linear logic $(\all)$ is the logic of product $(\*)$, sum $(\+)$, and their canonical morphisms: projections, injections, and diagonals.
+Additive linear logic (\all) is the logic of sum, product, and their canonical morphisms: projections, injections, and diagonals.
+Semantically, the logic represents parallel communication between two parties (with sum and product as respectively the sending and receiving of a binary choice) \cite{Joyal-1995, Cockett-Santocanale-2009}, and as such is a core part of \emph{session types} for process calculi \cite{Honda-Vasconcelos-Kubo-1998, Caires-Pfenning-2010, Wadler-2014}.
+
+A microcosm of parallellism, \all\ already demonstrates the \emph{Blass problem} of game semantics \cite{Abramsky-2003}, that sequential strategies do not in general have associative composition.
+This is resolved by \emph{proof nets} \cite{Girard-1987,Hughes-vanGlabbeek-2005}, which are a canonical, \emph{true-concurrency} presentation of \all.
+
+Here, we extend proof nets to first-order additive linear logic (\all1).
+Beyond the solution to the proof-net problem, a main contribution is the (further) development of the two techniques we consider: \emph{explicit substitutions} for witness assignment, and reconstruction of witness information through \emph{unification}, as pioneered for MLL by the second author \cite{Hughes-2018}.
+We expect to apply these to first-order logics more generally.
+
+%Additive linear logic $(\all)$ is the logic of product $(\*)$, sum $(\+)$, and their canonical morphisms: projections, injections, and diagonals.
 It is naturally captured in \defn{proof nets} \cite{Girard-1987,Hughes-vanGlabbeek-2005}, which describe a morphism $A\to B$ by a sequent $\seq{\dual A}B$ plus a \defn{linking}, a relation between the propositional atoms of $\dual A$ and those of $B$.
@@
 %
-Additive proof nets are \defn{canonical}: they factor out the permutations of sequent calculus, and correspond 1--1 to morphisms of the free category.
+%Additive proof nets are \defn{canonical}: they factor out the permutations of sequent calculus, and correspond 1--1 to morphisms of the free category.
 \defn{Composition}, of proof nets over $\seq{\dual A}B$ and $\seq{\dual B}C$ to one over $\seq{\dual A}C$, is by the relational composition of their linkings along the dual formulas $B$ and $\dual B$ (as illustrated below right), and captures sequent-calculus cut-elimination.
@@
 %\]
+
+\subsubsection*{Additive proof nets}
+%
+\all\ proof nets \cite[Section 4.10]{Hughes-vanGlabbeek-2005} represent a morphism $A\to B$ by a sequent $\seq{\dual A}B$ plus a \defn{linking}, a relation between the propositional atoms of $\dual A$ (the dual of $A$) and those of $B$.
+They are \defn{canonical}: they factor out the permutations of sequent calculus, and correspond 1--1 to morphisms of the free category with binary sums and products.
+\defn{Composition}, of proof nets over $\seq{\dual A}B$ and $\seq{\dual B}C$ to one over $\seq{\dual A}C$, is by the relational composition of their linkings along the dual formulas $B$ and $\dual B$ and captures sequent-calculus cut-elimination.
+Below are examples of proof nets and their composition.
+%
 \[
@@
 \]
-
+%
 % ALTERNATIVE (cuts one line) 
@@
 To assign different witnesses in different branches of a proof, the subformula is copied first, giving $B[s/x]$ and $B[t/x]$, as below right.
-
-In this paper we present proof nets for first-order additive linear logic (\all1).
-Our central challenge is to incorporate the essential content of first-order proof, the \defn{witness assignment} to existential quantifiers, into additive proof nets.
-In a standard approach, as in the sequent calculus rule below left, a witness to $\exists x.B$ is assigned by an immediate substitution $B[t/x]$.
-To assign different witnesses in different branches of a proof, the subformula may be duplicated first, giving $B[s/x]$ and $B[t/x]$, as below right.
+%
+We extend additive proof nets with first-order quantification.
+Our central challenge is to incorporate the essential content of first-order proof, the \defn{witness assignment} to existential quantifiers.
+Commonly, as in the sequent calculus rule below left, a witness to $\exists x.B$ is given by an immediate substitution $B[t/x]$.
+To assign different witnesses in different branches of a proof, the subformula is duplicated first, giving $B[s/x]$ and $B[t/x]$, as below right.
 %
@@
 %
-\paragraph*{Background}
-%
-Additive linear logic is combinatorially rich, yet well-behaved and tractable: proof search \cite{Galmiche-Marion-1995,Galmiche-2000} and proof net correctness \cite{Heijltjes-Hughes-2015} for a net over $\seq AB$ are linear in $|A|\times|B|$ (with $|A|$ the size of the syntax tree of $A$).
+\subsubsection*{Background}
+%
+Additive linear logic is combinatorially rich, yet well-behaved and tractable: proof search \cite{Galmiche-Marion-1995} and proof net correctness \cite{Heijltjes-Hughes-2015} for a net over $\seq AB$ are linear in $|A|\times|B|$ (with $|A|$ the size of the syntax tree of $A$).
 Proof nets remain canonical and equally tractable when extended with the two units \cite{Heijltjes-2011,Heijltjes-Hughes-2015}, and the first-order case is merely NP-complete \cite{Heijltjes-Hughes-2015}.
 
-At the same time, the ubiquity of its main operations, product and sum, mean the ideas and results it garners are widely applicable.
+%At the same time, the ubiquity of its main operations, product and sum, mean the ideas and results it garners are widely applicable.
 It serves as a microcosmos for important ideas and observations: it fostered the \emph{connections method} of proof search \cite{Galmiche-2000}; it demonstrated the \emph{Blass problem} \cite{Abramsky-2003} of game semantics, that sequential strategies do not in general have associative composition; and it is at the root of the study of fixed points in linear logic \cite{Santocanale-2002a}.
@@
 
-{\all} is of course part of {\mall} (multiplicative-additive linear logic), and its lessons are clearly visible in the second author's canonical proof nets for {\mall}~\cite{Hughes-vanGlabbeek-2005}, as well as the first and second author's locally canonical \emph{conflict nets}~\cite{Hughes-Heijltjes-2016}.
-Its proof nets also appear as the \emph{skew fibrations} in the second author's \emph{combinatorial proofs} for classical logic~\cite{Hughes-2006-proofs}, and in the third author's study of the \emph{medial rule} for classical logic~\cite{str:RTA07}.
-To prepare the ground for the cut elimination of first-order \emph{combinatorial proofs} is one motivation for the current presentation.
-
-\paragraph*{Proof identity}
+{\all} is of course part of {\mall} (multiplicative-additive linear logic), and its lessons are clearly visible in the second author's canonical {\mall} proof nets~\cite{Hughes-vanGlabbeek-2005}, as well as the first and second author's locally canonical \emph{conflict nets}~\cite{Hughes-Heijltjes-2016}.
+Its proof nets also appear in the third author's study of the \emph{medial rule} for classical logic~\cite{str:RTA07}, and as the \emph{skew fibrations} in the second author's \emph{combinatorial proofs} for classical logic~\cite{Hughes-2006-proofs}.
+To prepare the ground for cut elimination in first-order \emph{combinatorial proofs} is a further motivation for the present work.
+
+\subsubsection*{Proof identity}
 
@@
 
-\paragraph*{Correctness: coalescence and slicing}
+\subsubsection*{Correctness: coalescence and slicing}
 
@@
 
-\paragraph*{Witness maps}
+\subsubsection*{Witness maps}
 
@@
 
-\paragraph*{Correctness and sequentialization by coalescence}
+\subsubsection*{Correctness and sequentialization by coalescence}
 
@@
 
-\paragraph*{Slices}
+\subsubsection*{Slices}
 
@@
 % ..................................................
-\newcounter{lemcorrect}
-\setcounter{lemcorrect}{\thetheorem}
+
 \begin{lemma}
@@
 \begin{proof}
-See the appendix.
+For a strict coalescence step $L\scoal R$, we will show that the witness pre-net $L$ is correct if and only if $R$ is.
+Let $L=\net{\lambda_\Sigma}AB$ and $R=\net{\kappa_\Theta}AB$.
+In each case, exact coverage and local eigenvariables are immediately preserved and reflected.
+For slice-correctness, we will demonstrate that the left-hand side and right-hand side of each rule belong to the same slice of $\seq AB$, or in the case of $\srr?$, naturally corresponding slices.
+For dependency-correctness, we will briefly show how acyclicity of the columns of the involved links is preserved.
+
+\begin{itemize}
+	\item
+$\link C{D_i}\scoal\link C{D_1{\+}D_2}$
+\\
+A slice $S_B$ of $B$ and $\varnothing$ containing one of $(D_1,\tau)$, $(D_2,\tau)$, and $(D_1\+D_2,\tau)$ must also contain the other two.
+A slice $S$ of $\seq AB$ then contains all three of $\link C{D_1}$, $\link C{D_2}$, and $\link C{D_1{\+}D_2}$, or none.
+It follows that $S\cap \lambda_\Sigma$ is a singleton if and only if $S\cap\kappa_\Theta$ is.
+Since other slices are unaffected, $L$ is slice-correct if and only if $R$ is.
+
+For dependency-correctness, the column of $\link C{D_i}$ is that of $\link C{D_1{\+}D_2}$ plus the pair $(D_i,\sigma\res{\ex[B]{D_i}})$ itself, which is minimal in the order $\dep$.
+
+	\item
+$\link C{D_1},\link C{D_2}\scoal\link C{D_1{\*}D_2}$
+\\
+A slice $S$ of $\seq AB$ contains $\link C{D_1{\*}D_2}$ if and only if it contains either of $\link C{D_1}$ or $\link C{D_2}$, and cannot contain both.
+Then $S\cap \lambda_\Sigma$ is a singleton if and only if $S\cap\kappa_\Theta$ is.
+
+Dependency-correctness is immediate, as above.
+
+	\item
+$\link CD\scoal\link[\sigma\minus x]C{\exists x.D}$
+\\
+A slice $S$ of $\seq AB$ contains $\link[\tau] C{\exists x.D}$ if and only if it contains all links $\link[\tau{[t/x]}]CD$ for any term $t$.
+Letting $\tau[t/x]=\sigma$, then $S\cap \lambda_\Sigma$ is the singleton $\{\link CD\}$ if and only if $S\cap\kappa_\Theta$ is $\{\link[\sigma\minus x]C{\exists x.D}\}$.
+
+For dependency-correctness, the column of $\link CD$ is that of $\link[\sigma\minus x]C{\exists x.D}$ plus a pair $(D,\tau)$, which is minimal in $(\dep)$.
+
+	\item
+$\link CD\scoal\link C{\forall x.D}$
+\\
+A slice $S$ of $\seq AB$ contains $\link CD$ if and only if it contains also $\link C{\forall x.D}$, and hence $S\cap\lambda_\Sigma$ is a singleton if and only if $S\cap\kappa_\Theta$ is.
+
+For dependency-correctness, the column of $\link CD$ is that of $\link C{\forall x.D}$ plus a pair $(D,\tau)$.
+The side-condition of the coalescence step is that $x\notin\sigma$; then $x$ does not occur free in any $(X,\rho)$, and $(D,\tau)$ is minimal in $(\dep)$.
+\qedhere
+\end{itemize}
 \end{proof}
@@
 
-\newcounter{lemcoalescenceapplies}
-\setcounter{lemcoalescenceapplies}{\thetheorem}
 \begin{lemma}
@@
 \begin{proof}
-See the appendix.
+Let the \defn{depth} of a link $\link CD$ be a pair of integers $(n,m)$, where $n$ is the distance from $C$ to the root of $A$, and $m$ that from $D$ to $B$.
+We order link depth in the product order: $(i,j)\leq(n,m)$ if and only if $i\leq n$ and $j\leq m$.
+We will demonstrate that a link at maximal depth may always be coalesced, unless it is the unique link $\link[\varnothing]AB$ at $(0,0)$.
+
+To see that a maximally deep link coalesces, first note that a link $\link C{D_i}$ where $D_i$ occurs in $D_0{\+}D_1$ may always coalesce, as may a link $\link CD$ where $D$ occurs in $\exists x.D$.
+This leaves the following cases:
+\begin{itemize}
+	\item 
+$\link A{D_i}$ with $D_i$ occurring in $D=D_1\*D_2$.
+\\ 
+Without loss of generality, let $i=1$.
+A slice $S_1$ of $\seq AB$ containing $\link A{D_1}$ has a counterpart $S_2$ containing $\link A{D_2}$.
+The depth of $\link A{D_2}$ is the same as that of $\link A{D_1}$.
+By correctness $S_2\cap \lambda_\Sigma$ is a singleton; by the assumption of maximality it may not contain a deeper link than $\link A{D_2}$; and it may not contain a shallower one since that would be shared with $S_1\cap\lambda_\Sigma$.
+Then $\net{\lambda_\Sigma}AB$ contains both $\link A{D_1}$ and $\link A{D_2}$, and these contract to $\link AD$.
+
+	\item 
+$\link AD$ with $D$ in $\forall x.D$. 
+\\
+The step $\link AD\scoal\link A{\forall x.D}$ applies if $x\notin\sigma$.
+By way of contradiction, assume $x\in\sigma$.
+The column of $\link AD$ contains $(D,\sigma_D)$ and $(\forall x.D,\tau)$ where $\tau=\sigma\res{\ex[B]{\forall x.D}}$.
+By the exact coverage condition, $\sigma=\sigma_A\cup\sigma_D$, and since the free existential variables in $D$ and $\forall x.D$ are the same, $\ex[B]D=\ex[B]{\forall x.D}$, so that $\tau=\sigma_D$.
+(Note that since $\sigma_A=\varnothing$, we get $\sigma=\sigma_D=\tau$, but this is not essential to the argument.) Since $x\in\sigma$ we have $x\in\tau$, and in the column of $\link AD$ we have $(\forall x.D,\tau)\dep(D,\tau)$ since $D$ occurs as $\forall x.D$.
+But we already have $(D,\tau)\dep(\forall x.D,\tau)$ because $D\sub\forall x.D$, contradicting antisymmetry of $(\dep)$.
+Then $x\notin\sigma$, and the step $\link AD\scoal\link A{\forall x.D}$ applies.
+
+	\item
+$\link{C_i}{D_j}$ in $C=C_1\*C_2$ and $D=D_1\*D_2$.
+\\
+Without loss of generality, let $i=j=1$. By minimal depth and using similar reasoning to the first case above, the pre-net must contain one of the following three configurations.\\
+\begin{tabular}[c]{ll}
+	1. & $\link{C_1}{D_1},\link{C_1}{D_2},\link{C_2}{D_1},\link{C_2}{D_2}$
+\\	2. & $\link{C_1}{D_1},\link{C_1}{D_2},\link{C_2}{D}$
+\\	3. & $\link{C_1}{D_1},\link{C_2}{D_1},\link{C}{D_2}$
+\end{tabular}
+\hfill
+$
+\scriptstyle
+1:~\vc{
+\begin{tikzpicture}[net]
+	\formula[y=1]{C*{_1}{{\*}}C*{_2}}
+	\formula[y=0]{D*{_1}{{\*}}D*{_2}}
+	\Vlink[red]{[-2]1,[-2]1}\Vlink[red]{[2]1,[-2]3}\Vlink[red]{[-2]3,[2]1}\Vlink[red]{[2]3,[2]3}
+\end{tikzpicture}}
+\qquad
+2:~\vc{
+\begin{tikzpicture}[net]
+	\formula[y=1]{C*{_1}{{\*}}C*{_2}}
+	\formula[y=0]{D*{_1}{{\*}}D*{_2}}
+	\Vlink[red]{[-2]1,[-2]1}\Vlink[red]{[2]1,[-2]3}\Vlink[red]{3,2}
+\end{tikzpicture}}
+\qquad
+3:~\vc{
+\begin{tikzpicture}[net]
+	\formula[y=1]{C*{_1}{{\*}}C*{_2}}
+	\formula[y=0]{D*{_1}{{\*}}D*{_2}}
+	\Vlink[red]{[-2]1,[-2]1}\Vlink[red]{[-2]3,[2]1}\Vlink[red]{2,3}
+\end{tikzpicture}}
+\quad
+$
+In the second case, the step $\link{C_1}{D_1},\link{C_1}{D_2}\scoal\link{C_1}D$ applies; in the third case, $\link{C_1}{D_1},\link{C_2}{D_1}\scoal\link C{D_1}$; and in the first case, both.
+
+	\item 
+$\link{C_i}D$ in $C=C_1\*C_2$ and $\forall x.D$.
+\\
+Without loss of generality let $i=1$.
+If $x\notin\sigma$ the rewrite step $\link{C_1}D\scoal\link{C_1}{\forall x.D}$ applies.
+Otherwise, let $x\in\sigma$.
+The slice $S_1$ of $\seq AB$ containing $\link{C_1}D$ has a counterpart $S_2$ containing $\link{C_2}D$, which must include exactly one link of $\lambda_\Sigma$.
+By the assumption of minimal depth, it cannot have greater depth than $\link{C_2}D$.
+It cannot be $\link CD$ or any shallower link, since that would be shared with the slice $S_1$ which already contains $\link{C_1}D$.
+It cannot be $\link{C_2}{\forall x.D}$ or any shallower link $\link[\tau]{C_2}{X}$ (i.e.\ with $\forall x.D\leq X$) because $x\in\sigma$.
+This would mean either $x\in\tau$ which contradicts the \emph{eigenvariables not free} convention, or $x\in\fv(\sigma(y))$ where $\forall x.D<\exists y.Y\leq X$ which creates a cyclic column, as in the second case above.
+It follows that $S_2\cap\lambda_\Sigma=\{\link{C_2}{D}\}$, so that the rewrite step $\link{C_1}D,\link{C_2}D\scoal\link CD$ applies.
+
+	\item 
+$\link CD$ in $\forall x.C$ and $\forall y.D$.
+\\
+A rewrite step $\link CD\scoal\link{\forall x.C}D$ or $\link CD\scoal\link C{\forall y.D}$ applies unless $x,y\in\sigma$.
+But that would generate a cycle in the column of $\link CD$, in one of three ways.
+If $x\in\sigma_C$ or $y\in\sigma_D$ then, since $\sigma_C=\sigma_{\forall x.C}$ and $\sigma_D=\sigma_{\forall y.D}$, respectively:
+\[
+	(C,\sigma_C)\dep(\forall x.C,\sigma_C)\dep(C,\sigma_C)
+\qquad\quad
+	(D,\sigma_D)\dep(\forall y.D,\sigma_D)\dep(D,\sigma_D)~.
+\]
+Otherwise, if $x\in\sigma_D$ and $y\in\sigma_C$ then
+\[
+	(C,\sigma_C)\dep(\forall x.C,\sigma_C)\dep(D,\sigma_D)\dep(\forall x.D,\sigma_D)\dep(C,\sigma_C)~.
+\qedhere
+\]
+\end{itemize}
 \end{proof}
@@
 \\	
-Since $x$ is not free in the range of $\tau$, and (by the freshness convention) nor in the range of $\sigma$, we have that $\fix{\sigma_B\tau\subdual B}$ is $\fix[1pt]{(\sigma_B\minus x)\tau\subdual B}$ plus the substitution $[\sigma(x)/x]$.
+Since $x$ is not free in the range of $\tau$, nor in the range of $\sigma$ (by Barendregt's convention), we have that $\fix{\sigma_B\tau\subdual B}$ is $\fix[1pt]{(\sigma_B\minus x)\tau\subdual B}$ plus the substitution $[\sigma(x)/x]$.
 Then $\rho=\rho'$ (as $x$ does not occur in the range of $\sigma_A\tau_C$) and $\psi'$ reduces to $\psi$ in a single cut-elimination step.
@@
 \begin{proof}
-See the appendix.
+By Corollary~\ref{cor:strong coalescence} the proof nets $L=\net{\lambda_\Sigma}AB$ and $R=\net{\kappa_\Theta}{\dual B}C$ strongly coalesce.
+We may then interleave their coalescence sequences as follows: if a synchronized step in $L$ and $R$ on the interface $B$ and $\dual B$ is available, apply it; otherwise perform steps in $L$ on $A$ and in $R$ on $C$ until it is.
+This gives the following combined sequence.
+\[
+\begin{array}{c@{~}c@{~}c@{~}l@{~}c@{~}l@{~}c@{~}l@{~}c}
+	L &{}={}& L_1 & ~\scoal^?~ & L_2 & ~\scoal^?~ & \dots & ~\scoal^?~ & L_n 
+\\
+	R &{}={}& R_1 & ~\scoal^?~ & R_2 & ~\scoal^?~ & \dots & ~\scoal^?~ & R_n 
+\\[5pt]
+	\Downarrow && \Downarrow && \Downarrow &&&& \Downarrow 
+\\[5pt]
+	L\comp R & = & L_1\comp R_1 & ~\scoal~ & L_2\comp R_2 & ~\scoal~ & \dots & ~\scoal~ & L_n\comp R_n
+\end{array}
+\]
+(Here, $(\scoal^?)$ is the relation $(\scoal)\cup(=)$, but we assume that at least $L_i\scoal L_{i+1}$ or $R_i\scoal R_{i+1}$.)
+%
+The path along the top and right of this diagram sequentializes $L$ to $\pi'$ and $R$ to $\phi'$ (equivalent to $\pi$ and $\phi$ respectively), and then composes to $L_n\comp R_n = \net{\{\link[\varnothing]AC^{\pi'\comp\phi'}\}}AC$.
+
+Each square of the diagram converges as one of the critical pairs of sequentialization and composition discussed above.
+Then each path along the diagram from top left ($L$ and $R$) to bottom right $(L_n\comp R_n)$ gives a sequentialization, with cuts, of $L_n\comp R_n$.
+Let the path taking the vertical step from $L_i$ and $R_i$ to $L_i\comp R_i$ sequentialize to $\psi_i$, so that $\psi_n=\psi'$.
+By the way each square converges, we have that $\psi_i$ is reached from $\psi_{i+1}$ by a cut-elimination or permutation step.
+
+Finally, in $L$ and $R$ every link is an axiom link.
+Any link in $L\comp R$ is composed from two links $\link ab$ in $L$ and $\link[\tau]{\dual b}c$ in $R$, which yields $\link[\rho]ac$ where $\rho = \sigma_a\tau_c\dcom\fix{\sigma_b\tau\subdual b}$.
+This sequentializes to the axiom $\infer{\seq{a\rho}{c\rho}}{}$, which is in normal form.
+Then $L\comp R$ is a proof net (it has an axiom linking and it coalesces), and it sequentializes to a normal form of $\psi$.
 \end{proof}
@@
 An initial witness pre-net has \emph{exact coverage}, while coalescence will give \emph{local eigenvariables}.
+Note that eigenvariables are constants for the purpose of unification (they are not substituted into), and substitution maps of different links use different variables.
 
@@
 
-%\paragraph*{Generality}
+%\subsubsection*{Generality}
 %
@@
 \appendix
-
-\section{Postponed proofs}
-
-% ..................................................
-
-\setcounter{theorem}{\thelemcorrect}
-\begin{lemma}[Restatement]
-Strict coalescence preserves and reflects correctness.
-\end{lemma}
-
-\begin{proof}
-For a strict coalescence step $L\scoal R$, we will show that the witness pre-net $L$ is correct if and only if $R$ is.
-Let $L=\net{\lambda_\Sigma}AB$ and $R=\net{\kappa_\Theta}AB$.
-In each case, exact coverage and local eigenvariables are immediately preserved and reflected.
-For slice-correctness, we will demonstrate that the left-hand side and right-hand side of each rule belong to the same slice of $\seq AB$, or in the case of $\srr?$, naturally corresponding slices.
-For dependency-correctness, we will briefly show how acyclicity of the columns of the involved links is preserved.
-
-\begin{itemize}
-	\item
-$\link C{D_i}\scoal\link C{D_1{\+}D_2}$
-\\
-A slice $S_B$ of $B$ and $\varnothing$ containing one of $(D_1,\tau)$, $(D_2,\tau)$, and $(D_1\+D_2,\tau)$ must also contain the other two.
-A slice $S$ of $\seq AB$ then contains all three of $\link C{D_1}$, $\link C{D_2}$, and $\link C{D_1{\+}D_2}$, or none.
-It follows that $S\cap \lambda_\Sigma$ is a singleton if and only if $S\cap\kappa_\Theta$ is.
-Since other slices are unaffected, $L$ is slice-correct if and only if $R$ is.
-
-For dependency-correctness, the column of $\link C{D_i}$ is that of $\link C{D_1{\+}D_2}$ plus the pair $(D_i,\sigma\res{\ex[B]{D_i}})$ itself, which is minimal in the order $\dep$.
-
-	\item
-$\link C{D_1},\link C{D_2}\scoal\link C{D_1{\*}D_2}$
-\\
-A slice $S$ of $\seq AB$ contains $\link C{D_1{\*}D_2}$ if and only if it contains either of $\link C{D_1}$ or $\link C{D_2}$, and cannot contain both.
-Then $S\cap \lambda_\Sigma$ is a singleton if and only if $S\cap\kappa_\Theta$ is.
-
-Dependency-correctness is immediate, as above.
-
-	\item
-$\link CD\scoal\link[\sigma\minus x]C{\exists x.D}$
-\\
-A slice $S$ of $\seq AB$ contains $\link[\tau] C{\exists x.D}$ if and only if it contains all links $\link[\tau{[t/x]}]CD$ for any term $t$.
-Letting $\tau[t/x]=\sigma$, then $S\cap \lambda_\Sigma$ is the singleton $\{\link CD\}$ if and only if $S\cap\kappa_\Theta$ is $\{\link[\sigma\minus x]C{\exists x.D}\}$.
-%
-%The witnesses sets $\Sigma(x)$ and $\Theta(x)$ for $L$ and $R$ need not be the same, since $L$ has $\sigma$ where $R$ has $\sigma\minus x$.
-Let $\Sigma(x)=\{t,t_1,\dots,t_n\}$ and $\Theta(x)=\{t_1,\dots,t_n\}$, where $\sigma(x)=t$.
-For every slice $S_B$ of $B$ over $\Sigma$ there is a corresponding slice $S'_B$ over $\Theta$, both (or neither) containing $(\exists x.D,\tau)$ and $(D,\tau[t_i/x])$ for $i\leq n$, but the former in addition having $(D,\tau[t/x])$.
-Then $S\cap \lambda_\Sigma$ is the singleton $\{\link CD\}$ if and only if $S\cap\kappa_\Theta$ is $\{\link[\sigma\minus x]C{\exists x.D}\}$, where it should be observed that if $t$ is also a witness to $x$ in some other slice of $R$, then $t\in\Theta(x)$ and in fact $S=S'$.
-
-For dependency-correctness, the column of $\link CD$ is that of $\link[\sigma\minus x]C{\exists x.D}$ plus a pair $(D,\tau)$, which is minimal in $(\dep)$.
-
-	\item
-$\link CD\scoal\link C{\forall x.D}$
-\\
-A slice $S$ of $\seq AB$ contains $\link CD$ if and only if it contains also $\link C{\forall x.D}$, and hence $S\cap\lambda_\Sigma$ is a singleton if and only if $S\cap\kappa_\Theta$ is.
-
-For dependency-correctness, the column of $\link CD$ is that of $\link C{\forall x.D}$ plus a pair $(D,\tau)$.
-The side-condition of the coalescence step is that $x\notin\sigma$; then $x$ does not occur free in any $(X,\rho)$, and $(D,\tau)$ is minimal in $(\dep)$.
-\qedhere
-\end{itemize}
-\end{proof}
-
-% ..................................................
-
-\setcounter{theorem}{\thelemcoalescenceapplies}
-\begin{lemma}[Restatement]
-To a correct witness pre-net $\net{\lambda_\Sigma}AB$ a coalescence step applies, unless it is fully coalesced already, $\lambda_\Sigma=\{\link[\varnothing]AB\}$.
-\end{lemma}
-
-\begin{proof}
-Let the \defn{depth} of a link $\link CD$ be a pair of integers $(n,m)$, where $n$ is the distance from $C$ to the root of $A$, and $m$ that from $D$ to $B$.
-We order link depth in the product order: $(i,j)\leq(n,m)$ if and only if $i\leq n$ and $j\leq m$.
-We will demonstrate that a link at maximal depth may always be coalesced, unless it is the unique link $\link[\varnothing]AB$ at $(0,0)$.
-
-To see that a maximally deep link coalesces, first note that a link $\link C{D_i}$ where $D_i$ occurs in $D_0{\+}D_1$ may always coalesce, as may a link $\link CD$ where $D$ occurs in $\exists x.D$.
-This leaves the following cases:
-\begin{itemize}
-	\item 
-$\link A{D_i}$ with $D_i$ occurring in $D=D_1\*D_2$.
-\\ 
-Without loss of generality, let $i=1$.
-A slice $S_1$ of $\seq AB$ containing $\link A{D_1}$ has a counterpart $S_2$ containing $\link A{D_2}$.
-The depth of $\link A{D_2}$ is the same as that of $\link A{D_1}$.
-By correctness $S_2\cap \lambda_\Sigma$ is a singleton; by the assumption of maximality it may not contain a deeper link than $\link A{D_2}$; and it may not contain a shallower one since that would be shared with $S_1\cap\lambda_\Sigma$.
-Then $\net{\lambda_\Sigma}AB$ contains both $\link A{D_1}$ and $\link A{D_2}$, and these contract to $\link AD$.
-
-	\item 
-$\link AD$ with $D$ in $\forall x.D$. 
-\\
-The step $\link AD\scoal\link A{\forall x.D}$ applies if $x\notin\sigma$.
-By way of contradiction, assume $x\in\sigma$.
-The column of $\link AD$ contains $(D,\sigma_D)$ and $(\forall x.D,\tau)$ where $\tau=\sigma\res{\ex[B]{\forall x.D}}$.
-By the exact coverage condition, $\sigma=\sigma_A\cup\sigma_D$, and since the free existential variables in $D$ and $\forall x.D$ are the same, $\ex[B]D=\ex[B]{\forall x.D}$, so that $\tau=\sigma_D$.
-(Note that since $\sigma_A=\varnothing$, we get $\sigma=\sigma_D=\tau$, but this is not essential to the argument.) Since $x\in\sigma$ we have $x\in\tau$, and in the column of $\link AD$ we have $(\forall x.D,\tau)\dep(D,\tau)$ since $D$ occurs as $\forall x.D$.
-But we already have $(D,\tau)\dep(\forall x.D,\tau)$ because $D\sub\forall x.D$, contradicting antisymmetry of $(\dep)$.
-Then $x\notin\sigma$, and the step $\link AD\scoal\link A{\forall x.D}$ applies.
-
-	\item
-$\link{C_i}{D_j}$ in $C=C_1\*C_2$ and $D=D_1\*D_2$.
-\\
-Without loss of generality, let $i=j=1$. By minimal depth and using similar reasoning to the first case above, the pre-net must contain one of the following three configurations.\\
-\begin{tabular}[c]{ll}
-	1. & $\link{C_1}{D_1},\link{C_1}{D_2},\link{C_2}{D_1},\link{C_2}{D_2}$
-\\	2. & $\link{C_1}{D_1},\link{C_1}{D_2},\link{C_2}{D}$
-\\	3. & $\link{C_1}{D_1},\link{C_2}{D_1},\link{C}{D_2}$
-\end{tabular}
-\hfill
-$
-\scriptstyle
-1:~\vc{
-\begin{tikzpicture}[net]
-	\formula[y=1]{C*{_1}{{\*}}C*{_2}}
-	\formula[y=0]{D*{_1}{{\*}}D*{_2}}
-	\Vlink[red]{[-2]1,[-2]1}\Vlink[red]{[2]1,[-2]3}\Vlink[red]{[-2]3,[2]1}\Vlink[red]{[2]3,[2]3}
-\end{tikzpicture}}
-\qquad
-2:~\vc{
-\begin{tikzpicture}[net]
-	\formula[y=1]{C*{_1}{{\*}}C*{_2}}
-	\formula[y=0]{D*{_1}{{\*}}D*{_2}}
-	\Vlink[red]{[-2]1,[-2]1}\Vlink[red]{[2]1,[-2]3}\Vlink[red]{3,2}
-\end{tikzpicture}}
-\qquad
-3:~\vc{
-\begin{tikzpicture}[net]
-	\formula[y=1]{C*{_1}{{\*}}C*{_2}}
-	\formula[y=0]{D*{_1}{{\*}}D*{_2}}
-	\Vlink[red]{[-2]1,[-2]1}\Vlink[red]{[-2]3,[2]1}\Vlink[red]{2,3}
-\end{tikzpicture}}
-\quad
-$
-In the second case, the step $\link{C_1}{D_1},\link{C_1}{D_2}\scoal\link{C_1}D$ applies; in the third case, $\link{C_1}{D_1},\link{C_2}{D_1}\scoal\link C{D_1}$; and in the first case, both.
-
-	\item 
-$\link{C_i}D$ in $C=C_1\*C_2$ and $\forall x.D$.
-\\
-Without loss of generality let $i=1$.
-If $x\notin\sigma$ the rewrite step $\link{C_1}D\scoal\link{C_1}{\forall x.D}$ applies.
-Otherwise, let $x\in\sigma$.
-The slice $S_1$ of $\seq AB$ containing $\link{C_1}D$ has a counterpart $S_2$ containing $\link{C_2}D$, which must include exactly one link of $\lambda_\Sigma$.
-By the assumption of minimal depth, it cannot have greater depth than $\link{C_2}D$.
-It cannot be $\link CD$ or any shallower link, since that would be shared with the slice $S_1$ which already contains $\link{C_1}D$.
-It cannot be $\link{C_2}{\forall x.D}$ or any shallower link $\link[\tau]{C_2}{X}$ (i.e.\ with $\forall x.D\leq X$) because $x\in\sigma$.
-This would mean either $x\in\tau$ which contradicts the \emph{eigenvariables not free} convention, or $x\in\fv(\sigma(y))$ where $\forall x.D<\exists y.Y\leq X$ which creates a cyclic column, as in the second case above.
-It follows that $S_2\cap\lambda_\Sigma=\{\link{C_2}{D}\}$, so that the rewrite step $\link{C_1}D,\link{C_2}D\scoal\link CD$ applies.
-
-	\item 
-$\link CD$ in $\forall x.C$ and $\forall y.D$.
-\\
-A rewrite step $\link CD\scoal\link{\forall x.C}D$ or $\link CD\scoal\link C{\forall y.D}$ applies unless $x,y\in\sigma$.
-But that would generate a cycle in the column of $\link CD$, in one of three ways.
-If $x\in\sigma_C$ or $y\in\sigma_D$ then, since $\sigma_C=\sigma_{\forall x.C}$ and $\sigma_D=\sigma_{\forall y.D}$, respectively:
-\[
-	(C,\sigma_C)\dep(\forall x.C,\sigma_C)\dep(C,\sigma_C)
-\qquad\quad
-	(D,\sigma_D)\dep(\forall y.D,\sigma_D)\dep(D,\sigma_D)~.
-\]
-Otherwise, if $x\in\sigma_D$ and $y\in\sigma_C$ then
-\[
-	(C,\sigma_C)\dep(\forall x.C,\sigma_C)\dep(D,\sigma_D)\dep(\forall x.D,\sigma_D)\dep(C,\sigma_C)~.
-\qedhere
-\]
-\end{itemize}
-\end{proof}
-
-% ..................................................
-
-\setcounter{theorem}{\thethmcomposition}
-\begin{theorem}[Restatement]
-If proof nets $\net{\lambda_\Sigma}AB$ and $\net{\kappa_\Theta}{\dual B}C$ sequentialize to $\pi$ and $\phi$ respectively, then their composition $(\net{\lambda_\Sigma}AB)\comp(\net{\kappa_\Theta}{\dual B}C)$ is well-defined (i.e.\ all fixed points are finite) and sequentializes to a normal form $\psi$ of $\pi\comp\phi$.
-\end{theorem}
-
-\begin{proof}
-By Corollary~\ref{cor:strong coalescence} the proof nets $L=\net{\lambda_\Sigma}AB$ and $R=\net{\kappa_\Theta}{\dual B}C$ strongly coalesce.
-We may then interleave their coalescence sequences as follows: if a synchronized step in $L$ and $R$ on the interface $B$ and $\dual B$ is available, apply it; otherwise perform steps in $L$ on $A$ and in $R$ on $C$ until it is.
-This gives the following combined sequence.
-\[
-\begin{array}{c@{~}c@{~}c@{~}l@{~}c@{~}l@{~}c@{~}l@{~}c}
-	L &{}={}& L_1 & ~\scoal^?~ & L_2 & ~\scoal^?~ & \dots & ~\scoal^?~ & L_n 
-\\
-	R &{}={}& R_1 & ~\scoal^?~ & R_2 & ~\scoal^?~ & \dots & ~\scoal^?~ & R_n 
-\\[5pt]
-	\Downarrow && \Downarrow && \Downarrow &&&& \Downarrow 
-\\[5pt]
-	L\comp R & = & L_1\comp R_1 & ~\scoal~ & L_2\comp R_2 & ~\scoal~ & \dots & ~\scoal~ & L_n\comp R_n
-\end{array}
-\]
-(Here, $(\scoal^?)$ is the relation $(\scoal)\cup(=)$, but we assume that at least $L_i\scoal L_{i+1}$ or $R_i\scoal R_{i+1}$.)
-%
-The path along the top and right of this diagram sequentializes $L$ to $\pi'$ and $R$ to $\phi'$ (equivalent to $\pi$ and $\phi$ respectively), and then composes to $L_n\comp R_n = \net{\{\link[\varnothing]AC^{\pi'\comp\phi'}\}}AC$.
-
-Each square of the diagram converges as one of the critical pairs of sequentialization and composition discussed above.
-Then each path along the diagram from top left ($L$ and $R$) to bottom right $(L_n\comp R_n)$ gives a sequentialization, with cuts, of $L_n\comp R_n$.
-Let the path taking the vertical step from $L_i$ and $R_i$ to $L_i\comp R_i$ sequentialize to $\psi_i$, so that $\psi_n=\psi'$.
-By the way each square converges, we have that $\psi_i$ is reached from $\psi_{i+1}$ by a cut-elimination or permutation step.
-
-Finally, in $L$ and $R$ every link is an axiom link.
-Any link in $L\comp R$ is composed from two links $\link ab$ in $L$ and $\link[\tau]{\dual b}c$ in $R$, which yields $\link[\rho]ac$ where $\rho = \sigma_a\tau_c\dcom\fix{\sigma_b\tau\subdual b}$.
-This sequentializes to the axiom $\infer{\seq{a\rho}{c\rho}}{}$, which is in normal form.
-Then $L\comp R$ is a proof net (it has an axiom linking and it coalesces), and it sequentializes to a normal form of $\psi$.
-\end{proof}
 

### 2018-09-04 ALL1-RR.tex
spacing in figures
made it into an RR

@@
-\documentclass{article}
+\documentclass[twoside,a4paper]{article}
 
@@
 \newcommand{\willem}[1]{{\color{green!50!black}     \noindent[\![\![{\bf Willem: }#1]\!]\!]}}
+
+% ============================== for RR
+
+\usepackage{RR}
+
+\RRNo{9201}
+\RRdate{September 2018}
+\RRauthor{Willem B.\ Heijltjes \and Dominic J.D.\ Hughes \and Lutz Stra\ss burger}
+\RRtitle{Reseaux de preuves pour la logique linéaire additive de premier ordre}
+\RRetitle{Proof nets for first-order additive linear logic}
+\RRprojet{Parsifal}
+\RCSaclay
+\RRabstract{
+We present canonical proof nets for first-order additive linear logic, the fragment of linear logic with sum, product, and first-order universal and existential quantification. 
+%
+We present two versions of our proof nets.
+One, \emph{witness nets}, retains explicit witnessing information to existential quantification.
+For the other, \emph{unification nets}, this information is absent but can be reconstructed through unification.
+Unification nets embody a central contribution of the paper: first-order witness information can be left implicit, and reconstructed as needed.
+%
+Witness nets are canonical for first-order additive sequent calculus.
+Unification nets in addition factor out any inessential choice for existential witnesses.
+Both notions of proof net are defined through coalescence, an additive counterpart to multiplicative contractibility, and for witness nets an additional geometric correctness criterion is provided.
+% 
+Both capture sequent calculus cut-elimination as a one-step global composition operation.
+}
+
+\RRkeyword{proof nets, additive linear logic, first-order, unification}
+
+\RRresume{%%
+Nous présentons des réseaux de preuve canoniques pour la logique linéaire additive du premier ordre, le fragment de la logique linéaire avec somme, produit et quantificateurs du premier ordre.
+%
+Nous présentons deux versions de nos réseaux de preuves.
+Pour l'un, \emph{r\'eseaux \`a témoin}, conserve une information de témoin explicite à la quantification existentielle.
+Pour l'autre, \emph {r\'eseaux d'unification}, cette information est absente mais peut être reconstruite par l'unification.
+Les r\'esaeux d'unification incarnent une contribution centrale de l'article: les informations sur les témoins de premier ordre peuvent être implicites et reconstruites selon les besoins.
+%
+Les r\'eseaux à témoin sont canoniques pour le calcul des séquents additifs de premier ordre.
+Les réseaux d’unification excluent en outre tout choix inessentiel pour les témoins existentiels.
+Les deux notions de réseau de preuve sont définies par la coalescence, un complément additif à la contractibilité multiplicative, et pour les réseaux de témoins, un critère supplémentaire de correction géométrique est fourni.
+%
+Tous deux capturent l'élimination des coupures comme une opération de composition globale en une étape.
+}
+
+\RRmotcle{reseaux de preuves, logique linéaire additive, premier ordre, unification}
+
+\authorhead{Heijltjes \& Hughes \& Stra{\ss}burger}
+\titlehead{Proof nets for first-order additive linear logic}
 
@@
 
+\makeRR
+
 \maketitle
 
-\begin{abstract}
-We present canonical proof nets for first-order additive linear logic, the fragment of linear logic with sum, product, and first-order universal and existential quantification. 
-%
-We present two versions of our proof nets.
+%% \begin{abstract}
+
+%%   We present canonical proof nets for first-order additive linear logic, the fragment of linear logic with sum, product, and first-order universal and existential quantification. 
+%% %
+%% We present two versions of our proof nets.
 One, \emph{witness nets}, retains explicit witnessing information to existential quantification.
@@
 Unification nets embody a central contribution of the paper: first-order witness information can be left implicit, and reconstructed as needed.
-%
-Witness nets are canonical for first-order additive sequent calculus.
+%% %
+%% Witness nets are canonical for first-order additive sequent calculus.
 Unification nets in addition factor out any inessential choice for existential witnesses.
 Both notions of proof net are defined through coalescence, an additive counterpart to multiplicative contractibility, and for witness nets an additional geometric correctness criterion is provided.
-% 
-Both capture sequent calculus cut-elimination as a one-step global composition operation.
-\end{abstract}
+%% % 
+%% Both capture sequent calculus cut-elimination as a one-step global composition operation.
+%% \end{abstract}
 
@@
 \[
-\hspace*{-\parindent}%
-\hspace*{\fill}%
 \begin{array}{@{}rc@{\qquad}rc@{}}
@@
     \end{tikzpicture}}
-\hfill
 % Tightening the text and spacing the 
@@
 \[
-\hspace*{\fill}
-\hspace*{-\parindent}
 	\vc{\infer[\Qrr?t]{\seq A{\exists x.B}}{\seq A{B[t/x]}}}
-\hfill
+\qquad\qquad
 \vc{
@@
    }}
-\hfill
 \]
@@
 \[
-\hspace*{\fill}
-\hspace*{-\parindent}
 	\text{\small a witness net:}
@@
 	\end{tikzpicture}}
-\hfill
+\qquad\qquad
 	\text{\small a unification net:}
@@
 	\end{tikzpicture}}
-\hfill
 \]

### 2018-09-04 ALL1-RR.tex
fixed accents

@@
 \RRresume{%%
-Nous présentons des réseaux de preuve canoniques pour la logique linéaire additive du premier ordre, le fragment de la logique linéaire avec somme, produit et quantificateurs du premier ordre.
-%
-Nous présentons deux versions de nos réseaux de preuves.
-Pour l'un, \emph{r\'eseaux \`a témoin}, conserve une information de témoin explicite à la quantification existentielle.
-Pour l'autre, \emph {r\'eseaux d'unification}, cette information est absente mais peut être reconstruite par l'unification.
-Les r\'esaeux d'unification incarnent une contribution centrale de l'article: les informations sur les témoins de premier ordre peuvent être implicites et reconstruites selon les besoins.
-%
-Les r\'eseaux à témoin sont canoniques pour le calcul des séquents additifs de premier ordre.
-Les réseaux d’unification excluent en outre tout choix inessentiel pour les témoins existentiels.
-Les deux notions de réseau de preuve sont définies par la coalescence, un complément additif à la contractibilité multiplicative, et pour les réseaux de témoins, un critère supplémentaire de correction géométrique est fourni.
-%
-Tous deux capturent l'élimination des coupures comme une opération de composition globale en une étape.
+Nous pr\'esentons des r\'eseaux de preuve canoniques pour la logique lin\'eaire additive du premier ordre, le fragment de la logique lin\'eaire avec somme, produit et quantificateurs du premier ordre.
+%
+Nous pr\'esentons deux versions de nos r\'eseaux de preuves.
+Pour l'un, \emph{r\'eseaux \`a témoin}, conserve une information de t\'emoin explicite \`a la quantification existentielle.
+Pour l'autre, \emph {r\'eseaux d'unification}, cette information est absente mais peut \^etre reconstruite par l'unification.
+Les r\'esaeux d'unification incarnent une contribution centrale de l'article: les informations sur les t\'emoins de premier ordre peuvent \^etre implicites et reconstruites selon les besoins.
+%
+Les r\'eseaux \`a t\'emoin sont canoniques pour le calcul des s\'equents additifs de premier ordre.
+Les r\'eseaux d’unification excluent en outre tout choix inessentiel pour les t\'emoins existentiels.
+Les deux notions de r\'eseau de preuve sont d\'efinies par la coalescence, un compl\'ement additif \`a la contractibilit\'e multiplicative, et pour les r\'eseaux de t\'emoins, un crit\`ere suppl\'ementaire de correction g\'eom\'etrique est fourni.
+%
+Tous deux capturent l'\'elimination des coupures comme une op\'eration de composition globale en une \'etape.
 }
 
-\RRmotcle{reseaux de preuves, logique linéaire additive, premier ordre, unification}
+\RRmotcle{reseaux de preuves, logique lin\'eaire additive, premier ordre, unification}
 

### 2018-09-05 ALL1.tex
typo

@@
 
-Additive linear logic $(\all)$ is the logic of product $(\*)$, sum $(\+)$, and their canonical morphisms: projections, injections, and diagonals.
+Additive linear logic (\all) is the logic of sum, product, and their canonical morphisms: projections, injections, and diagonals.
+Semantically, the logic represents parallel communication between two parties, with sum and product as respectively the sending and receiving of a binary choice \cite{Joyal-1995, Cockett-Santocanale-2009}, and as such is a core part of \emph{session types} for process calculi \cite{Honda-Vasconcelos-Kubo-1998, Caires-Pfenning-2010, Wadler-2014}.
+
+A microcosm of parallellism, \all\ already demonstrates the \emph{Blass problem} of game semantics \cite{Abramsky-2003}, that sequential strategies do not in general have associative composition.
+This is resolved by \emph{proof nets} \cite{Girard-1987,Hughes-vanGlabbeek-2005}, which are a canonical, \emph{true-concurrency} presentation of \all.
+
+Here, we extend proof nets to first-order additive linear logic (\all1).
+Beyond the solution to the proof-net problem, a main contribution is the (further) development of the two techniques we consider: \emph{explicit substitutions} for witness assignment, and reconstruction of witness information through \emph{unification}, as pioneered for MLL by the second author \cite{Hughes-2018}.
+We expect to apply these to first-order logics more generally.
+
+%Additive linear logic $(\all)$ is the logic of product $(\*)$, sum $(\+)$, and their canonical morphisms: projections, injections, and diagonals.
 It is naturally captured in \defn{proof nets} \cite{Girard-1987,Hughes-vanGlabbeek-2005}, which describe a morphism $A\to B$ by a sequent $\seq{\dual A}B$ plus a \defn{linking}, a relation between the propositional atoms of $\dual A$ and those of $B$.
@@
 %\]
+
+\paragraph*{Additive proof nets}
+%
+\all\ proof nets \cite[Section 4.10]{Hughes-vanGlabbeek-2005} represent a morphism $A\to B$ by a sequent $\seq{\dual A}B$ plus a \defn{linking}, a relation between the propositional atoms of $\dual A$ (the dual of $A$) and those of $B$.
+They are \defn{canonical}: they factor out the permutations of sequent calculus, and correspond 1--1 to morphisms of the free category with binary sums and products.
+\defn{Composition}, of proof nets over $\seq{\dual A}B$ and $\seq{\dual B}C$ to one over $\seq{\dual A}C$, is by the relational composition of their linkings along the dual formulas $B$ and $\dual B$ and captures sequent-calculus cut-elimination.
+Below are examples of proof nets and their composition.
+%
 \[
@@
 %
-Additive linear logic is combinatorially rich, yet well-behaved and tractable: proof search \cite{Galmiche-Marion-1995,Galmiche-2000} and proof net correctness \cite{Heijltjes-Hughes-2015} for a net over $\seq AB$ are linear in $|A|\times|B|$ (with $|A|$ the size of the syntax tree of $A$).
+Additive linear logic is combinatorially rich, yet well-behaved and tractable: proof search \cite{Galmiche-Marion-1995} and proof net correctness \cite{Heijltjes-Hughes-2015} for a net over $\seq AB$ are linear in $|A|\times|B|$ (with $|A|$ the size of the syntax tree of $A$).
 Proof nets remain canonical and equally tractable when extended with the two units \cite{Heijltjes-2011,Heijltjes-Hughes-2015}, and the first-order case is merely NP-complete \cite{Heijltjes-Hughes-2015}.
 
-At the same time, the ubiquity of its main operations, product and sum, mean the ideas and results it garners are widely applicable.
+%At the same time, the ubiquity of its main operations, product and sum, mean the ideas and results it garners are widely applicable.
 It serves as a microcosmos for important ideas and observations: it fostered the \emph{connections method} of proof search \cite{Galmiche-2000}; it demonstrated the \emph{Blass problem} \cite{Abramsky-2003} of game semantics, that sequential strategies do not in general have associative composition; and it is at the root of the study of fixed points in linear logic \cite{Santocanale-2002a}.
@@
 
-{\all} is of course part of {\mall} (multiplicative-additive linear logic), and its lessons are clearly visible in the second author's canonical proof nets for {\mall}~\cite{Hughes-vanGlabbeek-2005}, as well as the first and second author's locally canonical \emph{conflict nets}~\cite{Hughes-Heijltjes-2016}.
-Its proof nets also appear as the \emph{skew fibrations} in the second author's \emph{combinatorial proofs} for classical logic~\cite{Hughes-2006-proofs}, and in the third author's study of the \emph{medial rule} for classical logic~\cite{str:RTA07}.
-To prepare the ground for the cut elimination of first-order \emph{combinatorial proofs} is one motivation for the current presentation.
+{\all} is of course part of {\mall} (multiplicative-additive linear logic), and its lessons are clearly visible in the second author's canonical {\mall} proof nets~\cite{Hughes-vanGlabbeek-2005}, as well as the first and second author's locally canonical \emph{conflict nets}~\cite{Hughes-Heijltjes-2016}.
+Its proof nets also appear in the third author's study of the \emph{medial rule} for classical logic~\cite{str:RTA07}, and as the \emph{skew fibrations} in the second author's \emph{combinatorial proofs} for classical logic~\cite{Hughes-2006-proofs}.
+To prepare the ground for cut elimination in first-order \emph{combinatorial proofs} is a further motivation for the present work.
 
@@
 		\Vlink[red,l,label={$\scriptstyle[x/z,s/y]~~$}]{[-3]3,2}
-		\Vlink[blue,r,label={$~~\scriptstyle[x/z,s/y]$}]{[1]3,4}
+		\Vlink[blue,r,label={$~~\scriptstyle[x/z,t/y]$}]{[1]3,4}
 	\end{tikzpicture}}
@@
 		\Vlink[red,l,label={$\scriptstyle[x/z]~$}]{[-2]2,2}
-		\Vlink[blue,r,label={$~~\scriptstyle[x/z,s/y]$}]{[1]3,4}
+		\Vlink[blue,r,label={$~~\scriptstyle[x/z,t/y]$}]{[1]3,4}
 	\end{tikzpicture}}

### 2019-01-21 ALL1.tex
typo, emphasis

@@
 These are not generally canonical: they admit the permutation (and duplication) of proof rules past implicit \emph{contractions} (that is, the shared context of the additive conjunction rule).
-However, it might possible that additive monomial nets could be restricted to some notion of canonical form.
+However, it might be possible to restrict additive monomial nets to some notion of canonical form.
 Likewise, coalescence (or contractibility) has not been studied for first-order monomial nets, though it has been extended to a related form of MALL proof nets \cite{Maieli-2007}.
 
-Our slicing condition is loosely related to a number of approaches to first-order classical logic.
+Our slicing condition is loosely related to a number of approaches to first-order \emph{classical} logic.
 A formula $\exists x.A$ is interpreted as the sum (or classically, the \emph{disjunction}) over a fixed number of instantiations $A[t_1/x]\+\dots\+A[t_n/x]$.

### 2019-02-11 ALL1.tex
FSCD 2019 + messing with folders

@@
-\documentclass[UKenglish]{lipics-v2018}
+\documentclass[UKenglish]{lipics-v2019}
 
@@
 \usepackage{proof}
+\usepackage{refcount}
 \usepackage{stmaryrd}
@@
 
-\theoremstyle{plain}
-\newtheorem{proposition}[theorem]{Proposition}
+%\theoremstyle{plain}
+%\newtheorem{proposition}[theorem]{Proposition}
 
@@
 
-\subjclass{F.4.1: Mathematical logic--Proof theory}
+%\subjclass{F.4.1: Mathematical logic--Proof theory}
+% Theory of computation - Logic - Proof theory
+% Theory of computation - Logic - Linear logic
+\ccsdesc[500]{Theory of computation~Proof theory}
+\ccsdesc[300]{Theory of computation~Linear logic}
 \keywords{Linear logic, First-order logic, Proof nets, Herbrand's Theorem}
@@
 
+%We present two solutions to the \emph{proof-net problem}, finding a canonical representation of proofs, for additive linear logic (\all) extended with first-order quantification (\all1).
+
+%\all is the fragment of linear logic \cite{Girard-1987} that describes sums and products, and their canonical morphisms: projections, injections, and diagonals.
+The logic represents a rich but tractable microcosm in which to explore important semantic ideas.
+By the duality between sum and product
+
 Additive linear logic (\all) is the logic of sum, product, and their canonical morphisms: projections, injections, and diagonals.
-Semantically, the logic represents parallel communication between two parties, with sum and product as respectively the sending and receiving of a binary choice \cite{Joyal-1995, Cockett-Santocanale-2009}, and as such is a core part of \emph{session types} for process calculi \cite{Honda-Vasconcelos-Kubo-1998, Caires-Pfenning-2010, Wadler-2014}.
+Semantically, the logic represents parallel communication between two parties, with sum and product as respectively the sending and receiving of a binary choice \cite{Joyal-1995, Cockett-Santocanale-2009}.
+As such it is a core part of \emph{session types} for process calculi \cite{Honda-Vasconcelos-Kubo-1998, Caires-Pfenning-2010, Wadler-2014}.
 
@@
 We expect to apply these to first-order logics more generally.
+
+Proofs have been relegated to the appendix---for a full version see the report \cite{Heijltjes-Hughes-Strassburger-2018}.
 
@@
 %
-% ALTERNATIVE (cuts one line) 
-%
-%We present proof nets for first-order additive linear logic (\all1).
-Our main challenge is to incorporate the essential content of first-order proof, the \defn{witness assignment} to existential quantifiers, into additive proof nets.
-Commonly, as in the sequent rule below left, a witness to $\exists x.B$ is assigned by a substitution $B[t/x]$.
-To assign different witnesses in different branches of a proof, the subformula is copied first, giving $B[s/x]$ and $B[t/x]$, as below right.
-%
 We extend additive proof nets with first-order quantification.
@@
 }
-%
 \begin{align*}
@@
 \end{align*}
+%
+%\begin{align*}
+%	\XDeseq{\,\infer[\Qrr1]{\seq a{\dual a}}{}}bc &\quad=\quad \{\link bc\}
+%\\ \\[-5pt]
+%	\XDeseq{\infer[\Qrr+i]{\seq A {B_1\+B_2}}{\prf \pi A{B_i}}} {A'} {B_1'\+B'_2} 
+%	& \quad=\quad 
+%	\deseq{\prf\pi A{B_i}} {A'} {B_i'}
+%\\ \\[-5pt]
+%	\XDeseq{\infer[\Qrr*]{\seq A{B\*C}}{
+%	 \prf\pi AB && \prf{\pi'}AC 
+%	}}{A'}{B'\*C'}
+%	& \quad=\quad 
+%	  \deseq{\prf\pi AB}{A'}{B'}
+%	  \cup
+%	  \deseq{\prf{\pi'}AC}{A'}{C'}
+%\\ \\[-5pt]
+%	\XDeseq{\infer[\Qrr?t]{\seq A{\exists x.B}}{\prf\pi A{B[t/x]}}}{A'}{\exists x.B'}
+%	& \quad=\quad 
+%	 \deseq[{\sigma[t/x]}]{\prf\pi A{B[t/x]}} {A'} {B'}
+%\\ \\[-5pt]
+%	\XDeseq{\infer[\Qrr!]
+%	  {\seq A{\forall x.B}}{\prf\pi AB}} {A'} {\forall x.B'}
+%	& \quad=\quad 
+%	  \deseq{\prf\pi AB}{A'}{B'}
+%\end{align*}
 \end{definition}
@@
 
-\begin{proof}
-It follows by induction on $\pi$ that if $\lambda_\Sigma=\deseq{\prf\pi AB}{A'}{B'}$ where $A'\sigma=A$ and $B'\sigma=B$, then $\net{\lambda^\star_\Sigma}AB$ reduces in $(\scoal)$ to $\net{\{\link{A'}{B'}^\pi\}}AB$.
+%\begin{proof}
+%It follows by induction on $\pi$ that if $\lambda_\Sigma=\deseq{\prf\pi AB}{A'}{B'}$ where $A'\sigma=A$ and $B'\sigma=B$, then $\net{\lambda^\star_\Sigma}AB$ reduces in $(\scoal)$ to $\net{\{\link{A'}{B'}^\pi\}}AB$.
 The statement is the case $\sigma=\varnothing$.
-\end{proof}
+%\end{proof}
 % ..................................................
@@
 
-\begin{proof}
-By induction on the sequentialization path 
-$\net{\lambda_\Sigma^\star}AB\scoal^*\net{\{\link[\varnothing]AB^\pi\}}AB$
-it follows that in every pre-net $\net{\kappa_\Theta^\Phi}AB$ on this path, $\lambda_\Sigma$ is equal to the union over the de-sequentialization of all proof labels $\phi$ in $\Phi$:
-\[
-	\lambda_\Sigma=\bigcup~\{\,\deseq\phi CD \mid \link CD^\phi \in \kappa_\Theta^\Phi\,\}~.
-\]
-The statement is then the case $\kappa_\Theta^\Phi=\{\link[\varnothing]AB^\pi\}$.
-\end{proof}
+%\begin{proof}
+%By induction on the sequentialization path 
+%$\net{\lambda_\Sigma^\star}AB\scoal^*\net{\{\link[\varnothing]AB^\pi\}}AB$
+%it follows that in every pre-net $\net{\kappa_\Theta^\Phi}AB$ on this path, $\lambda_\Sigma$ is equal to the union over the de-sequentialization of all proof labels $\phi$ in $\Phi$:
+%\[
+%	\lambda_\Sigma=\bigcup~\{\,\deseq\phi CD \mid \link CD^\phi \in \kappa_\Theta^\Phi\,\}~.
+%\]
+%The statement is then the case $\kappa_\Theta^\Phi=\{\link[\varnothing]AB^\pi\}$.
+%\end{proof}
 % ..................................................
@@
 \begin{theorem}
+\label{thm:canonical}
 Witness nets are canonical: $[\pi]=[\phi]$ if and only if $\pi\sim\phi$.
@@
 
-\begin{proof}
-From left to right is by inspection of the critical pairs of sequentialization ($\scoal$).
+%\begin{proof}
+%From left to right is by inspection of the critical pairs of sequentialization ($\scoal$).
 From right to left is by inspection of the rule permutations in Figure~\ref{fig:permutations} in Appendix~\ref{sec:permutations}.
-\end{proof}
+%\end{proof}
 
@@
 It captures the non-permutability of universal and existential sequent rules due to the \emph{eigenvariable condition} of the former, as below right.
-	\item[]
+	%\item[]
 \[
@@
 
-In the remainder of this section we will establish that the two correctness conditions, by coalescence and by slicing, are equivalent.
+%In the remainder of this section we will establish that the two correctness conditions, by coalescence and by slicing, are equivalent.
 The geometric condition further gives \emph{strong} coalescence: since it is preserved, no coalescence step yields an incorrect, and thus non-coalescing, pre-net.
@@
 
-% ..................................................
-\newcounter{lemcorrect}
-\setcounter{lemcorrect}{\thetheorem}
-\begin{lemma}
-\label{lem:correct}
-Strict coalescence preserves and reflects correctness.
-\end{lemma}
-
-\begin{proof}
-See the appendix.
-\end{proof}
-
-% ..................................................
-
-\newcounter{lemcoalescenceapplies}
-\setcounter{lemcoalescenceapplies}{\thetheorem}
-\begin{lemma}
-\label{lem:coalescence applies}
-To a correct witness pre-net $\net{\lambda_\Sigma}AB$ a coalescence step applies, unless it is fully coalesced already, $\lambda_\Sigma=\{\link[\varnothing]AB\}$.
-\end{lemma}
-
-\begin{proof}
-See the appendix.
-\end{proof}
+To conclude this section we will establish that both correctness conditions, by coalescence and by slicing, are equivalent. Moreover, both are equivalent to \emph{strong} coalescence.
+
+% ..................................................
+%\newcounter{lemcorrect}
+%\setcounter{lemcorrect}{\thetheorem}
+%\begin{lemma}
+%\label{lem:correct}
+%Strict coalescence preserves and reflects correctness.
+%\end{lemma}
+
+%\begin{proof}
+%See the appendix.
+%\end{proof}
+
+% ..................................................
+
+%\newcounter{lemcoalescenceapplies}
+%\setcounter{lemcoalescenceapplies}{\thetheorem}
+%\begin{lemma}
+%\label{lem:coalescence applies}
+%To a correct witness pre-net $\net{\lambda_\Sigma}AB$ a coalescence step applies, unless it is fully coalesced already, $\lambda_\Sigma=\{\link[\varnothing]AB\}$.
+%\end{lemma}
+
+%\begin{proof}
+%See the appendix.
+%\end{proof}
 
@@
 
-\begin{proof}
-For the first statement, we proceed by induction on the coalescence path from $\net{\lambda_\Sigma}AB$ to $\net{\{\link[\varnothing]AB\}}AB$, with the end result as the base case.
+%\begin{proof}
+%For the first statement, we proceed by induction on the coalescence path from $\net{\lambda_\Sigma}AB$ to $\net{\{\link[\varnothing]AB\}}AB$, with the end result as the base case.
 It is slice-correct: every slice of $\seq AB$ contains $\link[\varnothing]AB$, so every slice of $\net{\{\link[\varnothing]AB\}}AB$ is the singleton $\{\link[\varnothing]AB\}$.
@@
 For the inductive step, by Lemma~\ref{lem:correct} coalescence reflects correctness, so that any pre-net along the coalescence path is correct, in particular $\net{\lambda_\Sigma}AB$.
-
-For the second statement, let $\net{\lambda_\Sigma}AB$ be correct.
+%
+%For the second statement, let $\net{\lambda_\Sigma}AB$ be correct.
 %We proceed by induction on the \emph{depth} of the links in $\net{\lambda_\Sigma}AB$, their distance to the roots of $A$ and $B$, and observe that this measure strictly decreases for any coalescence step.
-By Lemma~\ref{lem:coalescence applies} either the net has coalesced, or a coalescence step applies.
+%By Lemma~\ref{lem:coalescence applies} either the net has coalesced, or a coalescence step applies.
 By Lemma~\ref{lem:correct} the result of any coalescence step is again correct.
 Since links strictly move towards the roots of both formula trees, it follows that this process terminates, and the pre-net $\net{\lambda_\Sigma}AB$ strongly strict-coalesces.
-\end{proof}
+%\end{proof}
 
@@
 
-%\begin{corollary}
-%\label{cor:strong coalescence}
-%A correct witness pre-net strongly strict-coalesces.
-%\end{corollary}
-%
-%\begin{proof}
-%By Theorem~\ref{thm:correctness} a correct pre-net coalesces, and by Lemma~\ref{lem:correct} any coalescence step preserves correctness.
-AAs links strictly move towards the formula roots, this process terminates.
-%\end{proof}
-
+% ..................................................
+\begin{figure}[!t]
+\[
+\begin{array}{ccc}
+	\vc{
+	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\Seq AC}{
+	 \infer[\!\!\scriptstyle{\qrr*}]{\Seq A{B_1\*B_2}\vphantom{\dual B}}{\Prf{\pi_1}A{B_1} & \Prf{\pi_2}A{B_2}}
+	 &&
+	 \infer[\!\!\scriptstyle{\qrr+i}]{\Seq {\dual B_1\+\dual B_2}C}{\Prf\phi{\dual B_i}C}
+	}}
+	&\Rightarrow&
+	\vc{\infer[\!\!\scriptstyle{\mathrm{cut}}]{\Seq AC}{\Prf{\pi_i}A{B_i} && \Prf\phi{\dual B_i}C}}
+\\ \\
+	\vc{
+	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\Seq AC}{
+	 \infer[\!\!\scriptstyle{\qrr?t}]{\Seq A{\exists x.B}}{\Prf\pi A{B[t/x]}}
+	 &&
+	 \infer[\!\!\scriptstyle{\qrr!}]{\Seq {\forall x.\dual B}C}{\Prf\phi{\dual B}C}
+	}}
+	&\Rightarrow&
+	\vc{\infer[\!\!\scriptstyle{\mathrm{cut}}]{\Seq AC}{\Prf\pi A{B[t/x]} && \Prf{\phi[t/x]}{\dual B[t/x]}C}}
+\end{array}
+\]
+\caption{\all1 cut-elimination steps}
+\label{fig:cut-elim}
+\end{figure}
 % ..................................................
@@
 % ..................................................
-
-% ..................................................
-\begin{figure}[!t]
-\[
-\begin{array}{ccc}
-	\vc{
-	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\Seq AC}{
-	 \infer[\!\!\scriptstyle{\qrr*}]{\Seq A{B_1\*B_2}\vphantom{\dual B}}{\Prf{\pi_1}A{B_1} & \Prf{\pi_2}A{B_2}}
-	 &&
-	 \infer[\!\!\scriptstyle{\qrr+i}]{\Seq {\dual B_1\+\dual B_2}C}{\Prf\phi{\dual B_i}C}
-	}}
-	&\Rightarrow&
-	\vc{\infer[\!\!\scriptstyle{\mathrm{cut}}]{\Seq AC}{\Prf{\pi_i}A{B_i} && \Prf\phi{\dual B_i}C}}
-\\ \\
-	\vc{
-	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\Seq AC}{
-	 \infer[\!\!\scriptstyle{\qrr?t}]{\Seq A{\exists x.B}}{\Prf\pi A{B[t/x]}}
-	 &&
-	 \infer[\!\!\scriptstyle{\qrr!}]{\Seq {\forall x.\dual B}C}{\Prf\phi{\dual B}C}
-	}}
-	&\Rightarrow&
-	\vc{\infer[\!\!\scriptstyle{\mathrm{cut}}]{\Seq AC}{\Prf\pi A{B[t/x]} && \Prf{\phi[t/x]}{\dual B[t/x]}C}}
-\end{array}
-\]
-\caption{\all1 cut-elimination steps}
-\label{fig:cut-elim}
-\end{figure}
-% ..................................................
-
-The composition of two links is strongly related to composition of strategies in game semantics.
-There, two strategies on $\seq AB$ and $\seq{\dual B}C$ are composed by \emph{interaction} on the interface of $B$ and $\dual B$, and subsequently \emph{hiding} that interaction.
-
-In the following we will demonstrate that composition gives the desired result: if a net $L$ sequentializes to $\pi$ and $R$ to $\phi$, then $L\comp R$ sequentializes to a normal form of the composition of $\pi$ and $\phi$ with a cut.
-To this end we will explore how composition and sequentialization interact.
-We will consider the critical pairs of sequentialization $(\scoal)$ with composition $(\Rightarrow)$ given in Figures~\ref{fig:crit1}--\ref{fig:crit3}, and demonstrate how they are resolved.
 
@@
 
+The composition of two links is strongly related to composition of strategies in game semantics.
+There, two strategies on $\seq AB$ and $\seq{\dual B}C$ are composed by \emph{interaction} on the interface of $B$ and $\dual B$, and subsequently \emph{hiding} that interaction.
+
+In the following we will demonstrate that composition gives the desired result: if a net $L$ sequentializes to $\pi$ and $R$ to $\phi$, then $L\comp R$ sequentializes to a normal form of the composition of $\pi$ and $\phi$ with a cut.
+To this end we will explore how composition and sequentialization interact.
+We will consider the critical pairs of sequentialization $(\scoal)$ with composition $(\Rightarrow)$ given in Figures~\ref{fig:crit1}--\ref{fig:crit3}, and demonstrate how they are resolved.
+
 \begin{itemize}
@@
 % ..................................................
-\newcounter{thmcomposition}
-\setcounter{thmcomposition}{\thetheorem}
+
 \begin{theorem}
@@
 
-\begin{proof}
-See the appendix.
-\end{proof}
+%\begin{proof}
+%See the appendix.
+%\end{proof}
 
@@
 
-\begin{proof}
-The sequentialization path
-$
-	\net{\lambda_\Sigma^\star}AB = 
-	L_1 \ucoal L_2 \ucoal \dots \ucoal L_n = 
-	\net{\link[\varnothing]AB^\pi}AB
-$
-has a corresponding path
-$
-	\net{\lambda_\star^\star}AB = 
-	R_1 \ucoal R_2 \ucoal \dots \ucoal R_n =
-	\net{\link[\varnothing]AB^{\pi'}}AB
-$
-where the same links (but with potentially different witness maps) are coalesced.
+%\begin{proof}
+%The sequentialization path
+%$
+%	\net{\lambda_\Sigma^\star}AB = 
+%	L_1 \ucoal L_2 \ucoal \dots \ucoal L_n = 
+%	\net{\link[\varnothing]AB^\pi}AB
+%$
+%has a corresponding path
+%$
+%	\net{\lambda_\star^\star}AB = 
+%	R_1 \ucoal R_2 \ucoal \dots \ucoal R_n =
+%	\net{\link[\varnothing]AB^{\pi'}}AB
+%$
+%where the same links (but with potentially different witness maps) are coalesced.
 It follows by induction on this path (where the base case is $L_1$ and $R_1$) that for every corresponding pair of links $\link CD^\phi$ in $L_i$ and $\link[\tau]CD^\psi$ in $R_i$ we have $\tau\leq\sigma$ and $\psi\leq\phi$.
-\end{proof}
+%\end{proof}
 % ..................................................
@@
 
-\begin{proof}
-By induction on the sequentialization path $\net{\lambda_\star}AB\ucoal^*\net{\link[\varnothing]AB^\pi}AB$.
+%\begin{proof}
+%By induction on the sequentialization path $\net{\lambda_\star}AB\ucoal^*\net{\link[\varnothing]AB^\pi}AB$.
 For the end result, the statement holds with $\rho=\varnothing$.
@@
 We show the case ($\urr*$); the other cases are immediate.
-%
-\begin{itemize}
-	\item
-$\link C{D_1},\link[\tau]C{D_2}\ucoal\link[\sigma\join\tau]C{D_1{\*}D_2}$
-\\
-By the inductive hypothesis, $R\rho'$ strict-sequentializes to $\pi$. Let $\sigma\join\tau=\sigma\rho''=\tau\rho''$ and let $\rho=\rho''\rho'$. Then $L\rho$ strict-sequentializes to $\pi$ by 
-\[
-	\link[\sigma\rho]C{D_1},\link[\tau\rho]C{D_2}\scoal\link[(\sigma\join\tau)\rho']C{D_1{\*}D_2}~.
-\qedhere
-\]
-\end{itemize}
-\end{proof}
+%%
+%\begin{itemize}
+%	\item
+%$\link C{D_1},\link[\tau]C{D_2}\ucoal\link[\sigma\join\tau]C{D_1{\*}D_2}$
+%\\
+%By the inductive hypothesis, $R\rho'$ strict-sequentializes to $\pi$. Let $\sigma\join\tau=\sigma\rho''=\tau\rho''$ and let $\rho=\rho''\rho'$. Then $L\rho$ strict-sequentializes to $\pi$ by 
+%\[
+%	\link[\sigma\rho]C{D_1},\link[\tau\rho]C{D_2}\scoal\link[(\sigma\join\tau)\rho']C{D_1{\*}D_2}~.
+%\qedhere
+%\]
+%\end{itemize}
+%\end{proof}
 % ..................................................
@@
 \begin{theorem}
+\label{thm:unet deseq-seq}
 If $[\prf\pi AB]$ is $\net{\lambda_\Sigma}AB$ then $\net\lambda AB$ unifying-sequentializes to $\pi'\leq \pi$.
@@
 
-\begin{proof}
-By Theorem~\ref{thm:proof->net->proof}, $\net{\lambda_\Sigma}AB$ sequentializes to $\pi$ in $(\scoal)$, and hence also in $(\ucoal)$.
+%\begin{proof}
+%By Theorem~\ref{thm:proof->net->proof}, $\net{\lambda_\Sigma}AB$ sequentializes to $\pi$ in $(\scoal)$, and hence also in $(\ucoal)$.
 Then by Lemma~\ref{lem:ucoal generality} $\net{\lambda_\star}AB$ sequentializes to $\pi'\leq\pi$.
-\end{proof}
+%\end{proof}
 % ..................................................
@@
 \begin{theorem}
+\label{thm:unet seq-deseq}
 If $\net\lambda AB$ sequentializes to $\pi$, then $[\pi]=\net{\lambda_\Sigma} AB$ for some $\Sigma$.
@@
 
-\begin{proof}
-By Lemma~\ref{lem:unifying implies strict coalescence}, since $\net\lambda AB$ sequentializes to $\pi$ there is a net $\net{\lambda_\Sigma} AB$ that sequentializes to $\pi$.
+%\begin{proof}
+%By Lemma~\ref{lem:unifying implies strict coalescence}, since $\net\lambda AB$ sequentializes to $\pi$ there is a net $\net{\lambda_\Sigma} AB$ that sequentializes to $\pi$.
 By Theorem~\ref{thm:net->proof->net}, $[\pi]=\net{\lambda_\Sigma} AB$.
-\end{proof}
+%\end{proof}
 % ..................................................
@@
 \begin{theorem}
+\label{thm:unet composition}
 If $\net\lambda AB$ sequentializes to $\pi$ and $\net\kappa{\dual B}C$ to $\phi$ then their composition $\net{\lambda\comp\kappa}AC$ sequentializes to a proof $\psi'\leq\psi$ where $\psi$ is a normal form of $\pi\comp\phi$.
-%\[
-%	\psi~=~
-%	\vc{\infer[\Qrr.]{\seq AC}{
-%	 \Prf\pi AB & \Prf\phi{\dual B}C
-%	}}~.
-%\]
 \end{theorem}
 
-\begin{proof}
-By Lemma~\ref{lem:unifying implies strict coalescence} there are witness labellings $\Sigma$ and $\Theta$ such that $\net{\lambda_\Sigma}AB$ strict-sequentializes to $\pi$ and $\net{\kappa_\Theta}{\dual B}C$ to $\phi$.
+%\begin{proof}
+%By Lemma~\ref{lem:unifying implies strict coalescence} there are witness labellings $\Sigma$ and $\Theta$ such that $\net{\lambda_\Sigma}AB$ strict-sequentializes to $\pi$ and $\net{\kappa_\Theta}{\dual B}C$ to $\phi$.
 By Theorem~\ref{thm:composition} their composition $(\net{\lambda_\Sigma\comp\kappa_\Theta)}AC$ strict-sequentializes to a normal form $\psi$ of $\pi\comp\phi$.
 By Lemma~\ref{lem:ucoal generality} the net $\net{(\lambda\comp\kappa)_\star}AC$ unifying-sequentializes to $\psi'\leq\psi$.
-\end{proof}
+%\end{proof}
 
 % --------------------------------------------------
-%
-%\begin{figure}[!t]
-%\begin{center}
-%\begin{tabular}{lcccc}
-% &	Monomial nets & Expansion trees$^\ast$ & Witness nets & Unification nets
-%\\\hline
-%   Canonicity & \xmark & \vmark$^\ast$ & \vmark & \vmark
-%\\ Generality & \xmark &\xmark&\xmark& \vmark
-%\\ Direct composition &(\vmark) &\xmark& \vmark & \vmark
-%\\ Coalescence & ? & ? & \vmark & \vmark
-%\\ Slicing &\vmark &\vmark$^\ast$& \vmark & ?
-%\end{tabular}  
-%  \caption{Comparison of different notions of proof nets for quantifiers and additive connectives}
-%  \label{fig:results}
-%\end{center}
-%\end{figure}
 
@@
 \end{center}
+\vskip-8pt
 \end{figure}
@@
 
-We have presented two notions of first-order additive proof net, \emph{witness nets} and \emph{unification nets}, to canonically capture the two natural notions of proof identity for first-order additive linear logic.
+We have presented two notions of first-order additive proof net, \emph{witness nets} and \emph{unification nets}, to canonically capture two natural notions of proof identity for first-order additive linear logic.
 Figure~\ref{fig:results} summarizes our results, along with some observations we make below.
@@
 In our slicing condition, the interpretation of $\exists x.A$ is an infinite sum of which only a finite part $A[t_1/x]\+\dots\+A[t_n/x]$ is relevant, over the witnesses $t_1,\dots,t_n$ actually assigned to $x$ in the proof net.
-An interesting alternative approach to additive proof nets, which we may explore in future work, could be to take the expansion of $\exists x.A$ to $A[t_1/x]\+\dots\+A[t_n/x]$ as primary, and record it explicitly in the syntax, as expansion tree proofs do for classical logic.
+An interesting alternative approach to additive proof nets, which we may explore in future work, is to take the expansion of $\exists x.A$ to $A[t_1/x]\+\dots\+A[t_n/x]$ as primary, and record it explicitly in the syntax, as expansion tree proofs do for classical logic.
 It is expected, however, that this would sacrifice \emph{generality} and \emph{direct composition}.
+
+Hetzl \cite{Hetzl-2010} explores \emph{explicit substitution} for first-order classical sequent calculus.
 
@@
 
-\subsection*{Acknowledgements}
-
-We would like to thank the anonymous referees for their constructive feedback. Dominic would like to thank his host, Wes Holliday, at the UC Berkeley Logic Group.
+%\subsection*{Acknowledgements}
+%
+%We would like to thank the anonymous referees for their constructive feedback.
+Dominic would like to thank his host, Wes Holliday, at the UC Berkeley Logic Group.
+The first author was supported by EPSRC Project EP/R029121/1.
 
@@
 % ==================================================
+
+%\end{document}
 
@@
 
-\section{Postponed proofs}
-
-% ..................................................
-
-\setcounter{theorem}{\thelemcorrect}
-\begin{lemma}[Restatement]
+\theoremstyle{theorem}
+\newtheorem{retheorem}{Theorem}
+\newtheorem{relemma}[retheorem]{Lemma}
+
+\section{Proofs}
+
+In this appendix we restate and prove all theorems, and add two supporting lemmata.
+
+% .................................................
+\setcounterref{retheorem}{thm:proof->net->proof}
+\addtocounter{retheorem}{-1}
+\begin{retheorem}
+For any \all1 proof $\pi$, the witness net $[\pi]$ sequentializes to $\pi$. 
+\end{retheorem}
+
+\begin{proof}
+It follows by induction on $\pi$ that if $\lambda_\Sigma=\deseq{\prf\pi AB}{A'}{B'}$ where $A'\sigma=A$ and $B'\sigma=B$, then $\net{\lambda^\star_\Sigma}AB$ reduces in $(\scoal)$ to $\net{\{\link{A'}{B'}^\pi\}}AB$.
+The statement is the case $\sigma=\varnothing$.
+\end{proof}
+% ..................................................
+
+% ..................................................
+\setcounterref{retheorem}{thm:net->proof->net}
+\addtocounter{retheorem}{-1}
+\begin{retheorem}
+If $\net{\lambda_\Sigma}AB$ sequentializes to $\pi$, then $[\pi]$ is $\net{\lambda_\Sigma}AB$. 
+\end{retheorem}
+
+\begin{proof}
+By induction on the sequentialization path 
+$\net{\lambda_\Sigma^\star}AB\scoal^*\net{\{\link[\varnothing]AB^\pi\}}AB$
+it follows that in every pre-net $\net{\kappa_\Theta^\Phi}AB$ on this path, $\lambda_\Sigma$ is equal to the union over the de-sequentialization of all proof labels $\phi$ in $\Phi$:
+\[
+	\lambda_\Sigma=\bigcup~\{\,\deseq\phi CD \mid \link CD^\phi \in \kappa_\Theta^\Phi\,\}~.
+\]
+The statement is then the case $\kappa_\Theta^\Phi=\{\link[\varnothing]AB^\pi\}$.
+\end{proof}
+% ..................................................
+
+% ..................................................
+\setcounterref{retheorem}{thm:canonical}
+\addtocounter{retheorem}{-1}
+\begin{retheorem}
+Witness nets are canonical: $[\pi]=[\phi]$ if and only if $\pi\sim\phi$.
+\end{retheorem}
+
+\begin{proof}
+From left to right is by inspection of the critical pairs of sequentialization ($\scoal$).
+From right to left is by inspection of the rule permutations in Figure~\ref{fig:permutations} in Appendix~\ref{sec:permutations}.
+\end{proof}
+% ..................................................
+
+% ..................................................
+\begin{lemma}
+\label{lem:correct}
 Strict coalescence preserves and reflects correctness.
@@
 \end{proof}
-
-% ..................................................
-
-\setcounter{theorem}{\thelemcoalescenceapplies}
-\begin{lemma}[Restatement]
+% ..................................................
+
+% ..................................................
+\begin{lemma}
+\label{lem:coalescence applies}
 To a correct witness pre-net $\net{\lambda_\Sigma}AB$ a coalescence step applies, unless it is fully coalesced already, $\lambda_\Sigma=\{\link[\varnothing]AB\}$.
@@
 \end{proof}
-
-% ..................................................
-
-\setcounter{theorem}{\thethmcomposition}
-\begin{theorem}[Restatement]
+% ..................................................
+
+% ..................................................
+\setcounterref{retheorem}{thm:correctness}
+\addtocounter{retheorem}{-1}
+\begin{retheorem}
+A witness pre-net that strict-coalesces is correct, and a correct witness pre-net strongly strict-coalesces. 
+\end{retheorem}
+
+\begin{proof}
+For the first statement, we proceed by induction on the coalescence path from $\net{\lambda_\Sigma}AB$ to $\net{\{\link[\varnothing]AB\}}AB$, with the end result as the base case.
+It is slice-correct: every slice of $\seq AB$ contains $\link[\varnothing]AB$, so every slice of $\net{\{\link[\varnothing]AB\}}AB$ is the singleton $\{\link[\varnothing]AB\}$.
+It is also dependency-correct: the column of $\link[\varnothing]AB$ is the set $\{(A,\varnothing),(B,\varnothing)\}$, where $A$ and $B$ are unrelated in $(\dep)$.
+For the inductive step, by Lemma~\ref{lem:correct} coalescence reflects correctness, so that any pre-net along the coalescence path is correct, in particular $\net{\lambda_\Sigma}AB$.
+
+For the second statement, let $\net{\lambda_\Sigma}AB$ be correct.
+By Lemma~\ref{lem:coalescence applies} either the net has coalesced, or a coalescence step applies.
+By Lemma~\ref{lem:correct} the result of any coalescence step is again correct.
+Since links strictly move towards the roots of both formula trees, it follows that this process terminates, and the pre-net $\net{\lambda_\Sigma}AB$ strongly strict-coalesces.
+\end{proof}
+% ..................................................
+
+% ..................................................
+\setcounterref{retheorem}{thm:composition}
+\addtocounter{retheorem}{-1}
+\begin{retheorem}
 If proof nets $\net{\lambda_\Sigma}AB$ and $\net{\kappa_\Theta}{\dual B}C$ sequentialize to $\pi$ and $\phi$ respectively, then their composition $(\net{\lambda_\Sigma}AB)\comp(\net{\kappa_\Theta}{\dual B}C)$ is well-defined (i.e.\ all fixed points are finite) and sequentializes to a normal form $\psi$ of $\pi\comp\phi$.
-\end{theorem}
+\end{retheorem}
 
@@
 \end{proof}
+% ..................................................
+
+% ..................................................
+\setcounterref{retheorem}{lem:ucoal generality}
+\addtocounter{retheorem}{-1}
+\begin{relemma}
+In ($\ucoal$), if $\net{\lambda_\Sigma}AB$ sequentializes to $\pi$ then $\net{\lambda_\star}AB$ sequentializes to $\pi'\leq\pi$.
+\end{relemma}
+
+\begin{proof}
+The sequentialization path
+$
+	\net{\lambda_\Sigma^\star}AB = 
+	L_1 \ucoal L_2 \ucoal \dots \ucoal L_n = 
+	\net{\link[\varnothing]AB^\pi}AB
+$
+has a corresponding path
+$
+	\net{\lambda_\star^\star}AB = 
+	R_1 \ucoal R_2 \ucoal \dots \ucoal R_n =
+	\net{\link[\varnothing]AB^{\pi'}}AB
+$
+where the same links (but with potentially different witness maps) are coalesced.
+It follows by induction on this path (where the base case is $L_1$ and $R_1$) that for every corresponding pair of links $\link CD^\phi$ in $L_i$ and $\link[\tau]CD^\psi$ in $R_i$ we have $\tau\leq\sigma$ and $\psi\leq\phi$.
+\end{proof}
+% ..................................................
+
+% ..................................................
+\setcounterref{retheorem}{lem:unifying implies strict coalescence}
+\addtocounter{retheorem}{-1}
+\begin{relemma}
+If $\net{\lambda_\star}AB$ unifying-sequentializes to $\pi$ then there exists a witness assignment $\Sigma$ and substitution $\rho$ such that $\net{\lambda_\Sigma}AB$ strict-sequentializes to $\pi$ and $\lambda_\Sigma=\lambda_\star\rho$.
+\end{relemma}
+
+\begin{proof}
+By induction on the sequentialization path $\net{\lambda_\star}AB\ucoal^*\net{\link[\varnothing]AB^\pi}AB$.
+For the end result, the statement holds with $\rho=\varnothing$.
+For the inductive step, consider a step $L\ucoal R$.
+We show the case ($\urr*$); the other cases are immediate.
+%
+\begin{itemize}
+	\item
+$\link C{D_1},\link[\tau]C{D_2}\ucoal\link[\sigma\join\tau]C{D_1{\*}D_2}$
+\\
+By the inductive hypothesis, $R\rho'$ strict-sequentializes to $\pi$. Let $\sigma\join\tau=\sigma\rho''=\tau\rho''$ and let $\rho=\rho''\rho'$. Then $L\rho$ strict-sequentializes to $\pi$ by 
+\[
+	\link[\sigma\rho]C{D_1},\link[\tau\rho]C{D_2}\scoal\link[(\sigma\join\tau)\rho']C{D_1{\*}D_2}~.
+\qedhere
+\]
+\end{itemize}
+\end{proof}
+% ..................................................
+
+% ..................................................
+\setcounterref{retheorem}{thm:unet deseq-seq}
+\addtocounter{retheorem}{-1}
+\begin{retheorem}
+If $[\prf\pi AB]$ is $\net{\lambda_\Sigma}AB$ then $\net\lambda AB$ unifying-sequentializes to $\pi'\leq \pi$.
+\end{retheorem}
+
+\begin{proof}
+By Theorem~\ref{thm:proof->net->proof}, $\net{\lambda_\Sigma}AB$ sequentializes to $\pi$ in $(\scoal)$, and hence also in $(\ucoal)$.
+Then by Lemma~\ref{lem:ucoal generality} $\net{\lambda_\star}AB$ sequentializes to $\pi'\leq\pi$.
+\end{proof}
+% ..................................................
+
+% ..................................................
+\setcounterref{retheorem}{thm:unet seq-deseq}
+\addtocounter{retheorem}{-1}
+\begin{retheorem}
+If $\net\lambda AB$ sequentializes to $\pi$, then $[\pi]=\net{\lambda_\Sigma} AB$ for some $\Sigma$.
+\end{retheorem}
+
+\begin{proof}
+By Lemma~\ref{lem:unifying implies strict coalescence}, since $\net\lambda AB$ sequentializes to $\pi$ there is a net $\net{\lambda_\Sigma} AB$ that sequentializes to $\pi$.
+By Theorem~\ref{thm:net->proof->net}, $[\pi]=\net{\lambda_\Sigma} AB$.
+\end{proof}
+% ..................................................
+
+% ..................................................
+\setcounterref{retheorem}{thm:unet composition}
+\addtocounter{retheorem}{-1}
+\begin{retheorem}
+If $\net\lambda AB$ sequentializes to $\pi$ and $\net\kappa{\dual B}C$ to $\phi$ then their composition $\net{\lambda\comp\kappa}AC$ sequentializes to a proof $\psi'\leq\psi$ where $\psi$ is a normal form of $\pi\comp\phi$.
+\end{retheorem}
+
+\begin{proof}
+By Lemma~\ref{lem:unifying implies strict coalescence} there are witness labellings $\Sigma$ and $\Theta$ such that $\net{\lambda_\Sigma}AB$ strict-sequentializes to $\pi$ and $\net{\kappa_\Theta}{\dual B}C$ to $\phi$.
+By Theorem~\ref{thm:composition} their composition $(\net{\lambda_\Sigma\comp\kappa_\Theta)}AC$ strict-sequentializes to a normal form $\psi$ of $\pi\comp\phi$.
+By Lemma~\ref{lem:ucoal generality} the net $\net{(\lambda\comp\kappa)_\star}AC$ unifying-sequentializes to $\psi'\leq\psi$.
+\end{proof}
+% ..................................................
 
 % --------------------------------------------------
-
+\newpage
 \section{Permutations}\label{sec:permutations}
 
-% ..................................................
-
-\begin{figure}[!ht]
-\[
-\renewcommand\+{{+}}
-\renewcommand\*{{\times}}
-\scalebox{0.85}{$
-\begin{array}{c@{\qquad}c}
-	\permAC   & \permEC   
-\\	\downperm & \downperm \\
-	\permCA   & \permCE
-\\ \\[20pt]
-	\permPC   & \permXC 
-\\	\downperm & \downperm \\
-	\permCP   & \permCX
-\end{array}
-\begin{array}{c}
-	\permCD \\ \downperm \\ \permDC
-\end{array}
-$}
-\]
-\caption{Cut-permutations}
-\label{fig:cut-permutations}
-\end{figure}
+In this section we give the rule permutations of {\all1} sequent calculus.
 
@@
 
+% ..................................................
+
+\begin{figure}[!ht]
+\[
+\renewcommand\+{{+}}
+\renewcommand\*{{\times}}
+\scalebox{0.85}{$
+\begin{array}{c@{\qquad}c}
+	\permAC   & \permEC   
+\\	\downperm & \downperm \\
+	\permCA   & \permCE
+\\ \\[20pt]
+	\permPC   & \permXC 
+\\	\downperm & \downperm \\
+	\permCP   & \permCX
+\end{array}
+\begin{array}{c}
+	\permCD \\ \downperm \\ \permDC
+\end{array}
+$}
+\]
+\caption{Cut-permutations}
+\label{fig:cut-permutations}
+\end{figure}
+
 \end{document}

### 2019-02-12 6-MLA2019/mla-abstract.tex
MLA stuff

%% FIRST RENAME THIS FILE <yoursurname>.tex. 
%% BEFORE COMPLETING THIS TEMPLATE, SEE THE "READ ME" SECTION 
%% BELOW FOR INSTRUCTIONS. 
%% TO PROCESS THIS FILE YOU WILL NEED TO DOWNLOAD asl.cls from 
%% http://aslonline.org/abstractresources.html.

\documentclass[a4paper,11pt]{article}

\pagestyle{plain}

\def\urladdr#1{\endgraf\noindent{\it URL Address}: {\tt #1}.}

\newcommand{\NP}{}
%\usepackage{verbatim}

\begin{document}
\thispagestyle{empty}

\title{Proof nets for first-order additive linear logic}

\author{Willem Heijltjes \and Dominic Hughes \and Lutz Stra{\ss}burger}

\maketitle
%% % First author's affiliation
%% \affil{Dept.\ Computer Science, University of Bath, UK}
%% %\meetemail{w.b.heijltjes@bath.ac.uk}
%% \urladdr{http://willem.heijltj.es}
%% %
%% % Second author's affiliation
%% \affil{Logic Group, U.C.\ Berkeley, USA}
%% \urladdr{http://boole.stanford.edu/\textasciitilde dominic}
%% %
%% % Third author's affiliation
%% \affil{Parsifal, Inria, France}
%% \urladdr{http://www.lix.polytechnique.fr/Labo/Lutz.Strassburger}

%% INSERT TEXT OF ABSTRACT DIRECTLY BELOW
In this talk we will present canonical proof nets for first-order additive linear logic, the fragment of linear logic with sum, product, and first-order universal and existential quantification. The central challenge is to combine the witnessing information to existential quantifiers with the behaviour of the additive conjunction. The latter creates multiple "slices", each containing a different version of the same quantifier, with a potentially different witness.

The challenge is met by upending the traditional evaluation of an existential quantifier by an immediate substitution: instead, the substitution is recorded separately, at each axiom link in the proof net. The result is a canonical notion of proof nets for this logic. The main thrust of the work resolves the technical consequences of the design. Efficient and intuitive correctness and sequentialization are given by "coalescence", an additive version of multiplicative contractibility; in essence, this is top-down sequentialization by simple graph rewriting. A main contribution is an intricate geometric correctness condition, which subtly combines "slicing" correctness for propositional additives with "dependency" correctness for quantification. Cut-elimination involves the composition of the witnessing substitutions in two proof nets by "composition + hiding" in the style of game semantics.

A further contribution is the observation --- following recent work by Dominic Hughes for first-order multiplicative linear logic --- that witnessing information can be omitted from first-order additive proof nets altogether, and reconstructed via unification. This yields a further, coarser notion of proof net that factors out any inessential choice in witness assignment.

Details can be found in the technical report \cite{HHS}.
%This is joint work with Dominic Hughes and Lutz Strassburger.

\begin{thebibliography}{10}

\bibitem{HHS}
Willem B.\ Heijltjes, Dominic J.\,D.\ Hughes, and Lutz Stra{\ss}burger.
\emph{Proof nets for first-order additive linear logic.}
Inria Research Report RR-9201,
2018

%% INSERT YOUR BIBLIOGRAPHIC ENTRIES HERE; 
%% SEE (4) BELOW FOR PROPER FORMAT.
%% EACH ENTRY MUST BEGIN WITH \bibitem{citation key}
%%
%% IF THERE ARE NO ENTRIES  
%% DELETE THE LINE ABOVE (\begin{thebibliography}{20}) 
%% AND THE LINE BELOW (\end{thebibliography})

\end{thebibliography}

%\vspace*{-0.5\baselineskip}
% this space adjustment is usually necessary after a bibliography

\end{document}

%% READ ME
%% READ ME
%% READ ME

INSTRUCTIONS FOR SUPPLYING INFORMATION IN THE CORRECT FORMAT:

1. Author names are listed as First Last, First Last, and First Last.

\absauth{FirstName1 LastName1, FirstName2 LastName2, and FirstName3 LastName3}

2. Titles of abstracts have ONLY the first letter capitalized,
except for Proper Nouns.

\meettitle{Title of abstract with initial capital letter only, except for
Proper Nouns}

3. Affiliations and email addresses for authors of abstracts are
  listed separately.

% First author's affiliation
\affil{Department, University, Street Address, Country}
\meetemail{First author's email}
%%% NOTE: email required for at least one author
\urladdr{OPTIONAL}
%
% Second author's affiliation
\affil{Department, University, Street Address, Country}
\meetemail{Second author's email}
\urladdr{OPTIONAL}
%
% Third author's affiliation
\affil{Department, University, Street Address, Country}
% Second author's email
\meetemail{Third author's email}
\urladdr{OPTIONAL}

4. Bibliographic Entries

%%%% IF references are submitted with abstract,
%%%% please use the following formats

%%% For a Journal article
\bibitem{cite1}
{\scshape Author's Name},
{\itshape Title of article},
{\bfseries\itshape Journal name spelled out, no abbreviations},
vol.~XX (XXXX), no.~X, pp.~XXX--XXX.

%%% For a Journal article by the same authors as above,
%%% i.e., authors in cite1 are the same for cite2
\bibitem{cite2}
\bysame
{\itshape Title of article},
{\bfseries\itshape Journal},
vol.~XX (XXXX), no.~X, pp.~XX--XXX.

%%% For a book
\bibitem{cite3}
{\scshape Author's Name},
{\bfseries\itshape Title of book},
Name of series,
Publisher,
Year.

%%% For an article in proceedings
\bibitem{cite4}
{\scshape Author's Name},
{\itshape Title of article},
{\bfseries\itshape Name of proceedings}
(Address of meeting),
(First Last and First2 Last2, editors),
vol.~X,
Publisher,
Year,
pp.~X--XX.

%%% For an article in a collection
\bibitem{cite5}
{\scshape Author's Name},
{\itshape Title of article},
{\bfseries\itshape Book title}
(First Last and First2 Last2, editors),
Publisher,
Publisher's address,
Year,
pp.~X--XX.

%%% An edited book
\bibitem{cite6}
Author's name, editor. % No special font used here
{\bfseries\itshape Title of book},
Publisher,
Publisher's address,
Year.

### 2019-03-29 5 - FSCD 2019 - Submitted/Reviews/rebuttal v1.txt
reviews, rebuttal, reorganise

Review 1:

(A) Why isn't there any **leap** edge?

The purpose of a leap edge is to explicitly record the dependency between quantifiers: when the eigenvariable (x) of a universal quantifier is used in the witnessing term (t{x}) to an existential quantifier. This corresponds to our "dependency" relation (Definition 10). The relevant part can be paraphrased: if (x) is the eigenvariable for a quantification "forall x.Y", and an explicit substitution [t{x}/y] ranges over a formula X, then there is a dependence (a "leap" or "jump") between Y and X.

We do not need leap edges for coalescence; we believe that likewise, contractibility for MLL1 unification nets would not need them.

(B) Is there a mismatch between slicing and unification?

Yes. For geometric correctness, it seems essential to reconstruct the dependencies (or "leaps", or "jumps") globally. In MLL1, where there are no slices, a single global unifier (for all links) can be constructed, from which the dependency is then derived.

With slices, the situation is much more involved. Dependencies (leaps) must be made explicit between existential quantifiers and products (see "Expansion", pages 8--9) as well as universal quantifiers. These interact in highly intricate ways, which the unifying coalescence algorithm resolves incrementally and locally. To do so globally, as a geometric criterion would, is a huge combinatorial challenge, beyond the scope of this paper.

==============================

Review 2:

(C) Is the equivalence generated by unification a form of observational equivalence?

We believe, yes, but none of us is an expert.

(D) Both proofs and witness nets are not considered up to alpha-equivalence.

In fact, we may alpha-convert at the level of proofs and proof nets; but for the sanity of the translations both ways, not at the level of individual formulas in a sequent proof.

Normally, indeed, every universal instantiation must have a unique eigenvariable. But for our proof nets, we only need (and have) this property for each slice individually.

==============================

Reviews 2 and 3:

(E) Can this be extended to MALL1?

The situation is mixed. There are two ways forward that are likely to succeed:
 - combine witness nets and MALL slice nets [Hughes & Van
   Glabbeek 2005], using a slicing criterion;
 - combine unification nets and MALL conflict nets [Hughes &
   Heijltjes 2016], using a coalescence criterion.
For both, there are still significant combinatorial challenges (e.g. because coalescence for MALL is not a straightforward extension of that for ALL). Other combinations are unlikely to work, or the groundwork is still incomplete: slice nets do not support coalescence (this looks fundamentally problematic), and conflict nets do not yet have a slicing criterion (work in progress).

### 2019-03-29 Archive/graveyard.tex
reviews, rebuttal, reorganise

--- 2017-12-19 ALL1-backup-2.tex
@@
-\documentclass{article}
+\newcommand\qrr[1]{
+  \ifx#1+\expandafter\@qrr\else
+  \ifx#1*[\*]\else
+  \ifx#1![\forall]\else
+  \ifx#1?[\exists]\else 
+  \ifx#11[a]\else
+  (#1)
+  \fi\fi\fi\fi\fi
+}
+\newcommand\@qrr[1]{[+_{#1}]}
+\newcommand\srr[1]{
+  \ifx#1+\expandafter\@srr\else
+  \ifx#1*(\*)\else
+  \ifx#1!(\forall)\else
+  \ifx#1?(\exists)\else
+  \ifx#11(a)\else
+  (#1)
+  \fi\fi\fi\fi
+}
+\newcommand\@srr[1]{(+_{#1})}
+\newcommand\urr[1]{
+  \ifx#1+\expandafter\@urr\else
+  \ifx#1*\langle\*\rangle\else
+  \ifx#1!\langle\forall\rangle\else
+  \ifx#1?\langle\exists\rangle\else
+  \ifx#11\langle a\rangle\else
+  \langle#1\rangle
+  \fi\fi\fi\fi\fi
+}
+\newcommand\@urr[1]{\langle+_{#1}\rangle}
 
-\usepackage{amsmath,amssymb,amsthm}
-\usepackage{proof}
-\usepackage{stmaryrd}
-\usepackage{xargs}
+% A \defn{unifying} witness map $\sigma$ for two atomic formulas $A$ and $B$ is one such that $A\sigma=B\sigma$.
+Note that these will substitute only the free existential variables, but not bound ones or universal variables.
+For instance, the only unifying witness map of $p(x,y)$ and $p(a,a)$ is $\{x\mapsto a,y\mapsto a\}$, while $\exists y.p(x,x)$ and $\exists y.p(a,y)$ have no unifier.
 
-\usepackage{graphicx}
+%\begin{figure}
+%\[
+%\begin{array}{cc}
+%	\infer[\!\!\scriptstyle{Q\sigma=\dual R\sigma}]{\ujg{\clink QR}QR}{}
+%&	\infer[\!\!\scriptstyle{\sigma\,=\,\sigma(Q,R)}]{\vjg{\clink[]QR}QR}{}
+%\\ \\
+%	\infer{\ujg\lambda A{B_0\+B_1}}{\ujg\lambda A{B_i}}
+%&	\infer{\vjg\lambda A{B_0\+B_1}}{\vjg\lambda A{B_i}}
+%\\ \\
+%	\infer{\ujg{\lambda\cup\kappa}A{B\*C}}{\ujg\lambda AB && \ujg\kappa AC}
+%&	\infer[\!\!\scriptstyle{\sigma\,\vco\,\tau}\vphantom)]{\vjg{\lambda\cup\kappa}[\sigma\vjn\tau]A{B\*C}}{\vjg\lambda[\sigma]AB && \vjg\kappa[\tau]AC}
+%\\ \\
+%	\infer[\!\!\scriptstyle{\sigma(x)=t}]{\ujg\lambda[\sigma\!\minus\!x]A{\exists x.B}}{\ujg\lambda AB}
+%&	\infer{\vjg\lambda[\sigma\!\minus\!x]A{\exists x.B}}{\vjg\lambda AB}
+%\\ \\
+%	\infer[\!\!\scriptstyle{a\,\notin\,\sigma}]{\ujg\lambda A{\forall a.B}}{\ujg\lambda AB}
+%&	\infer[\!\!\scriptstyle{a\,\notin\,\sigma}]{\vjg\lambda A{\forall a.B}}{\vjg\lambda AB}
+%\end{array}
+%\]
+%\caption{Derivation rules for (de-)sequentialization}
+%\label{fig:derivations}
+%\end{figure}
 
-\usepackage{willemtools}
-\usepackage{proofnet}
-
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
-\theoremstyle{plain}
-\newtheorem{lemma}[definition]{Lemma}
-
-% ===== Definitions
-
-\newcommand\defn[1]{\textit{\textbf{#1}}}
-
-% ===== General maths
-
-\newcommand\floor[1]{\lfloor#1\rfloor}
-
-% ===== Sets
-
-\newcommand\varA{\textsc{var}^\forall}
-\newcommand\varE{\textsc{var}^\exists}
-\newcommand\terms{\textsc{term}}
-\newcommand\termsA{\textsc{term}^\forall}
-\newcommand\atom{\textsc{atom}}
-\newcommand\all{\textsc{all}}
-
-\newcommand\subs[1]{\textsc{sub}(#1)}
-
-% ===== Formulas
-
-\newcommand\+{+}
-\renewcommand\*{\times}
-\newcommand\dual[1]{\overline{#1}}
-
-\newcommand\sub{\leq}
-\newcommand\seq[3][]{{\vdash_{#1}}#2,#3}
-\newcommand\fv{\textsc{fv}}
-
-% ===== Proofs
-
-\newcommand\prf[3]{#1\vdash\!#2,#3}
-
-% ===== Nets
-
-\newcommand\net[3]{#1\triangleright #2,#3}
-
-\newcommand\deseq[4][\sigma]{[#2]^{#1}_{#3,#4}}
-\newcommand\Deseq[4][\sigma]{\left[\vcenter{#2}\right]^{#1}_{#3,#4}}
-
-%\newcommandx\deseq[4][2=\sigma]{\floor{#1}_{#2}^{#3,#4}}
-%\newcommandx\Deseq[4][2=\sigma]{\left\lfloor\vcenter{#1}\right\rfloor_{#2}^{#3,#4}}
-
-% ===== Witness maps
-
-\newcommand\join\bowtie
-
-\newcommand\comp\frown
-%\newcommand\ubot\sqcup
-
-%\newlength{\cuplength}
-%\settowidth{\cuplength}{$\cup$}
-%\newcommand\ubot{\mathbin{\ooalign{$\cup$\cr\hss\scalebox{.9}{\raisebox{0.6ex}{\tiny$\mathbf\bot$}}\hss}}}
-
-%\newcommand\inst[1]{\llparenthesis#1\rrparenthesis}
-
-% ===== Slices
-
-% ===== Coalescence
-
-\newcommand\clink[3][\sigma]{(#2,#3)_{#1}}
-\newcommand\minus{\mathop{/\mathchoice{\kern-3pt}{\kern-3pt}{\kern-2.5pt}{\kern-2pt}/}}
-
-\newcommand\coals{\rightsquigarrow}
-\newcommand\coal{\coals}%{\stackrel1\rightsquigarrow}
-
-\newcommandx\crule[4][1=\sigma,2=\lambda]{#2\coals(#3,#4)_{#1}}
-
-%\newcommandx\xlink[4][1=\sigma,2=\lambda]{#2\triangleright(#3,#4)_{#1}}
-
-\begin{document}
-
-%\end{document}
-
-% ==================================================
-
-\section{Proof nets for first-order additive linear logic}
-
-% ..................................................
-
-\begin{figure}
-\hrule
-\par\bigskip
-\[
-	\infer{\seq P{\dual P}}{}
-\qquad
-	\infer{\seq A{B_0\+B_1}}{\seq A{B_i}}
-\qquad
-	\infer{\seq A{B\*C}}{\seq AB && \seq AC}
-\]
-\par
-\[
-	\infer{\seq A{\exists x.B}}{\seq A{B[t/x]}}
-\qquad
-	\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]{\seq A{\forall a.B}}{\seq AB}
-\]
-\par
 \[
@@
 \]
-\par\bigskip\hrule
-\caption{A sequent calculus for $\all1$}
-\label{fig:sequent calculus}
-\end{figure}
 
-% ..................................................
+The \defn{initial witness map} $\sigma(A,B)$ is the most general unifying witness map for the formulas $A$ and $B$, if it exists; if it does, $A$ and $B$ are \defn{compatible}.
+An unlabelled axiom link $(P,Q)$ is \defn{compatible} if $P$ and $\dual Q$ are compatible; a labelled one $\clink PQ$ is \defn{compatible} if $\sigma$ is a unifier for $P$ and $\dual Q$.
+A (labelled) linking or pre-net is \defn{compatible} if all links are compatible axiom links.
+The \defn{initial labelling} of a compatible linking $\lambda$ or pre-net $\net\lambda AB$ is the labelled linking $\lambda_\star$ or labelled pre-net $\net{\lambda_\star}AB$ given by
+\[
+	\lambda_\star = \{~\clink[\sigma(P,\dual Q)]PQ~\mid~(P,Q)\in\lambda~\}~.
+\]
 
-% --------------------------------------------------
+\[
+	\{~\clink[\varnothing]AB~\mid~\clink AB\in\lambda~\}
+\]
 
-\subsection{First-order additive linear logic}
+A linking (or pre-net) is a \defn{unification linking} if
 
-First-order terms and the formulas of first-order $\all$ are generated by the following grammars.
-%
-\setMidspace{5pt}
-\[
-\begin{array}{l@{}l}
-	t &\Coloneqq a \Mid x \Mid f(t_1,\dots,t_n)
-\\[10pt]
-	P &\Coloneqq p(t_1,\dots,t_n) \Mid \dual p(t_1,\dots,t_n)
-\\[10pt]
-	A &\Coloneqq P \Mid A\+A \Mid A\*A \Mid \exists x.A \Mid \forall a.A
-\end{array}
-\]
-%
-Negation $(\dual{\,\cdot\,})$ is applied to predicate symbols, $\dual p$, as a matter of convenience.
-The \defn{dual} $\dual A$ of an arbitrary formula $A$ is given by DeMorgan.
-We use the following notational conventions.
-%
-\\[2\itemsep]
-%
-\begin{tabular}{@{}lll@{}}
-	$a,b,c$ & $\in \varA$ 		& universally quantified variables (and free variables)\\
-	$x,y,z$ & $\in \varE$		& existentially quantified variables \\
-	$f,g,h$ & $\in \Sigma_f$	& $n$-ary $(n\geq 0)$ function symbols from a fixed alphabet $\Sigma_f$\\
-	$p,q,r$ & $\in \Sigma_p$	& $n$-ary $(n\geq 0)$ predicate symbols from a fixed alphabet $\Sigma_p$ \\
-	$s,t,u$ & $\in \terms$ 		& first-order terms over $\varA$, $\varE$, $\Sigma_f$, and $\Sigma_p$ \\
-	$P,Q,R$ & $\in \atom$		& atomic propositions \\
-	$A,B,C$ & $\in \all1$		& formulas \\
-\end{tabular}
-%
-\\[2\itemsep]
-%
-A \defn{sequent} $\seq AB$ is an ordered pair of formulas $A$ and $B$.
-A sequent calculus for \all1 is given in Figure~\ref{fig:sequent calculus}, where each rule has a symmetric counterpart that applies to the first formula in the sequent.
-We write $\prf\Pi AB$ for a proof $\Pi$ with conclusion sequent $\seq AB$.
-Anticipating the requirements of proof nets, we will assume the following convention for \all1 proofs.
+A link is an \defn{axiom link} if both formulas are atomic propositions.%It is an \defn{axiom linking} if all links are axiom links.
 
-\begin{description}
-	\item
-[\defn{Barendregt's convention}] All quantifiers in a sequent $\seq AB$ have a distinct binding variable, and no bound variable shares a name with a free one.
-%	\item
-%% ALTERNATIVE: "STATIC WITNESSING"
-%[\defn{Universal witnessing}] All existential witnesses in a proof are \defn{universal terms} $\termsA\subset\terms$, generated by the following grammar.
-%\[
-%	\termsA: \qquad t \Coloneqq a \Mid f(t_1,\dots,t_n)
-%\]
-\end{description}
-
-% --------------------------------------------------
-
-\subsection{Proof nets}
-
-By a \defn{subformula} we will mean a subformula \defn{occurrence}.
-For instance, a formula $A\*A$ has two subformulas $A$, one on the left and one on the right.
-The \defn{subformulas} $\subs A$ of a formula are given by
-\[
-	\subs A = \{A\} \cup
-	\left\{\begin{array}{ll}
-		\subs B\uplus\subs C	& \text{if $A=B\+C$ or $A=B\*C$} \\[5pt]
-		\subs B					& \text{if $A=\exists x.B$ or $A=\forall a.B$}
-	\end{array}\right.
-\]
-We will write $B\sub A$ if $B$ is a subformula of $A$.
-In the context of a sequent $\seq AB$, a \defn{link} $(A',B')$ is a pair of subformulas $A'\leq A$ and $B'\leq B$.
-A link is an \defn{axiom link} if both formulas are atomic propositions.
-A \defn{linking} $\lambda$ on the sequent $\seq AB$ is a set of links on $\seq AB$.
-%It is an \defn{axiom linking} if all links are axiom links.
-
-\begin{definition}
-A \defn{pre-net} $\net\lambda AB$ is a sequent $\seq AB$ with a linking $\lambda$ on it.
-\end{definition}
+The \defn{domain} $\dom\sigma$ of $\sigma$ are those variables on which it is not the identity, $\{~x\in\varE~\mid~\sigma(x)\neq x~\}$. We write $\varnothing$ for the empty map (the identity).
 
@@
 
-A \defn{labelled link} $\clink AB$ is a link carrying a witness map $\sigma$.
-A \defn{labelled linking} respectively a \defn{labelled pre-net} is a linking or pre-net where every link is labelled.
-A labelled linking $\lambda$ reverts to an unlabelled one, written $\floor\lambda$, by dropping the label of each link.
-
-\begin{definition}
-The \defn{labelled de-sequentialization} of a sequent proof $\prf\Pi AB$ is the labelled pre-net $\net{\deseq[\varnothing]\Pi AB} AB$ where $\deseq-AB$ is defined as follows.
-%
-\[
-\begin{array}{ccl}
-	\Deseq{\infer{\seq P{\dual P}}{}}QR &=& \{\clink QR\}
-\\ \\
-	\Deseq{\infer {\seq A {B_0\+B_1}} {\deduce [\rule{0pt}{1pt}] {\seq A{B_i}} \Pi }}
-	  {A'}{B_0'\+B'_1} 
-	&=& \Deseq{\deduce[\rule{0pt}{1pt}]{\seq A{B_i}}\Pi}{A'}{B_i'}
-\\ \\
-	\Deseq{\infer{\seq A{B\*C}}{
-	  \deduce[\rule{0pt}{1pt}]{\seq AB}\Pi 
-	  && 
-	  \deduce[\rule{0pt}{1pt}]{\seq AC}\Sigma}}{A'}{B'\*C'}
-	&=& \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AB}\Pi}{A'}{B'}
-	  \cup
-	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AC}\Sigma}{A'}{C'}
-\\ \\
-	\Deseq{\infer{\seq A{\exists x.B}}{\deduce[\rule{0pt}{1pt}]{\seq A{B[t/x]}}\Pi}}
-	  {A'}{\exists x.B'}
-	&=&
-	 \Deseq[{\sigma[x\mapsto t]}]{\deduce[\rule{0pt}{1pt}]{\seq A{B[t/x]}}\Pi}
-	  {A'}{B'}
-\\ \\
-	\Deseq{\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]
-	  {\seq A{\forall a.B}}{\deduce[\rule{0pt}{1pt}]{\seq AB}\Pi}}{A'}{\forall a.B'}
-	&=&
-	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AB}\Pi}{A'}{B'}
-\end{array}
-\]
-The \defn{(unlabelled) de-sequentialization} of $\Pi$ is $\net{\floor\Pi_{A,B}}AB$ where $\floor\Pi_{A,B}$ is $\floor{\deseq[\varnothing]\Pi AB}$.
-\end{definition}
-
 To generate witness maps for an unlabelled linking, we will be using unification.
@@
 For instance, the only unifying witness map of $p(x,y)$ and $p(a,a)$ is $\{x\mapsto a,y\mapsto a\}$, while $\exists y.p(x,x)$ and $\exists y.p(a,y)$ have no unifier.
-
-A witness map $\sigma$ is \defn{more general} than $\tau$, witten $\sigma\leq\tau$, if there is a $\rho$ such that $(A\sigma)\rho = A\tau$ for any $A$.
-The \defn{join} $\sigma\join\tau$ of two maps $\sigma$ and $\tau$ is the least map $\rho$ such that $\sigma\leq\rho$ and $\tau\leq\rho$, if it exists.
-If it does, we call $\sigma$ and $\tau$ \defn{compatible}, written $\sigma\comp\tau$.
 
@@
 
-\subsection{Geometric correctness}
+% ..................................................
 
-For a labelled linking $\lambda$ and an existential variable $x$, write $\lambda(x)\subseteq\terms$ for the \defn{witness set} of $x$, which collects the terms assigned to $x$ by the links in $\lambda$:
+\begin{figure}
 \[
-	\lambda(x) = \{~t~\mid~\sigma(x) = t~,~\clink AB\in\lambda~\}~.
+\begin{array}{rcl@{\hspace{40pt}}rcl} 
+    \vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{A}
+    	\formula[y=1]{B\+C}
+    	\Vlink[red,label={$\scriptstyle\sigma~$},l]{1,1}
+    \end{tikzpicture}}
+&\rightsquigarrow& 
+    \vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{A}
+    	\formula[y=1]{B\+C}
+    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,2}
+    \end{tikzpicture}}
+&    
+    \vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{A}
+    	\formula[y=1]{\exists x.B}
+    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,4}
+    \end{tikzpicture}}
+&\rightsquigarrow&
+    \vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{A}
+    	\formula[y=1]{\exists x.B}
+    	\Vlink[red,label={~$\scriptstyle{\sigma\!\minus\!x}$}]{1,1}
+    \end{tikzpicture}}
+\\ \\    
+    \vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{A}
+    	\formula[y=1]{B\*C}
+    	\Vlink[red,label={$\scriptstyle\sigma~$},l]{[-1]1,1}
+    	\Vlink[red,label={~$\scriptstyle\tau$}]{[1]1,3}
+    \end{tikzpicture}}
+&\stackrel{\sigma\comp\tau}\rightsquigarrow&   
+	\vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{A}
+    	\formula[y=1]{B\*C}
+    	\Vlink[red,label={~$\scriptstyle{\sigma\cup\tau}$}]{1,2}
+    \end{tikzpicture}}
+&  
+    \vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{A}
+    	\formula[y=1]{\forall a.B}
+    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,4}
+    \end{tikzpicture}}
+&\stackrel{a\,\notin\,\fv(A\sigma)}\rightsquigarrow&
+    \vc{\begin{tikzpicture}[net]
+    	\formula[y=2]{A}
+    	\formula[y=1]{\forall a.B}
+    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,1}
+    \end{tikzpicture}}
+\end{array}
 \]
-%
-Given a labelled linking $\lambda$, a \defn{slice} $S$ of a formula $A$ is a set of formulas given by: $S=\{A\}\cup S'$ where $S'$ is as follows; if $A$ is of the form
-%
-\begin{itemize}
-	\item
-\makebox[40pt][l]{$P$:}				$S'=\varnothing$.
-	\item
-\makebox[40pt][l]{$B\+C$:} 			$S'=S_B\cup S_C$ where $S_B$ is a slice of $B$ and $S_C$ a slice of $C$.
-	\item
-\makebox[40pt][l]{$B\*C$:}			$S'$ is a slice of $B$ or a slice of $C$.
-	\item
-\makebox[40pt][l]{$\exists x.B$:}	$S'$ is a slice of $B$ if the quantifier is vacuous, $x\notin\fv(B)$, and
-	\\[\itemsep]
-	\hspace*{40pt}					$S'=\uplus_{t\,\in\,\lambda(x)}S_t$ where each $S_t$ is a slice of $B[t/x]$ otherwise.
-	\item
-\makebox[40pt][l]{$\forall a.B$:}	$S'$ is a slice of $B$.
-\end{itemize}
-%
-A \defn{slice} of a labelled pre-net $\net\lambda AB$ is a set of links
-\[
-	\{~(C\sigma,D\sigma)~\mid~\clink CD\in \lambda~,~(C\sigma,D\sigma)\in S_A\times S_B~\}
-\]
-where $S_A$ is a slice of $A$ and $S_B$ a slice of $B$.
-A labelled pre-net is \defn{correct} if every slice is a singleton.
-A compatible pre-net $\net\lambda AB$ is \defn{correct} if its initial labelling $\net{\lambda_\star}AB$ is.
-Observe that for a \emph{labelled} pre-net correctness and compatibility are independent, while a non-labelled pre-net must be compatible to be correct, since $\lambda_\star$ is otherwise not defined.
+\caption{Coalescence rules}
+\label{fig:coalescence}
+\end{figure}
 
-\begin{definition}
-An \all1 \defn{proof net} is a correct pre-net. An \all1 \defn{labelled proof net} is a correct and compatible labelled pre-net.
-\end{definition}
-
-% --------------------------------------------------
-
-\subsection{Coalescence}
-
-\begin{definition}
-\defn{Coalescence} ($\coals$) is the rewrite relation on labelled pre-nets generated by the following rewrite rules, and their symmetric variants.
-%
-\renewcommand{\+}{{+}}
-\renewcommand{\*}{{\times}}
-\begin{align}
-  	\net{\{\clink AB\}}A{B\+C} 
-& ~\coal~
-	\net{\{\clink A{B\+C}\}}A{B\+C}
-\tag{$\+_1$}
-\\[5pt]
-        \net{\{\clink AC\}}A{B\+C}
-& ~\coal~  
-	\net{\{\clink A{B\+C}\}}A{B\+C}
-\tag{$\+_2$}
-\\[5pt]
-	\net{\{\clink AB,\clink[\tau]AC\}}A{B\*C}
-& ~\coal~ 
-	\net{\{\clink[\sigma\join\tau]A{B\*C}\}}A{B\*C}\quad\text{if }\sigma\comp\tau
-\tag{$\*$}
-\\[5pt]	
-	\net{\{\clink AB\}}A{\exists x.B}
-& ~\coal~ 
-	\net{\{\clink[\sigma\!\minus\!x]A{\exists x.B}\}}A{\exists x.B}
-\tag{$\exists$}
-\\[5pt]
-	\net{\{\clink AB\}}A{\forall a.B}
-& ~\coal~ 
-	\net{\clink A{\forall a.B}}A{\forall a.B} \quad \text{if }a\,\notin\,\fv(A\sigma)
-\tag{$\forall$}
-\end{align}
+% ..................................................
 %\[
@@
 %\end{itemize}
-%
-A labelled pre-net $\net\lambda AB$ \defn{coalesces} if it coalesces to a single link $\clink[\varnothing]AB$.
-A compatible pre-net \defn{coalesces} if $\net{\lambda_\star}AB$ coalesces.
-A pre-net \defn{strongly coalesces} if every coalescence sequence terminates at $\clink[\varnothing]AB$.
-\end{definition}
-
-To be explicit, generating coalescence as a rewrite relation means the following: $\net\lambda AB\coal \net{\lambda'}AB$ if and only if there is a rewrite rule $\net\kappa CD\coal\net{\kappa'} CD$ such that $C\leq A$, $D\leq B$, $\kappa\subseteq\lambda$, and $\lambda'=\lambda\cup\kappa'-\kappa$.
-
-\begin{lemma}
-If a labelled pre-net coalesces, it is correct. 
-\end{lemma}
-
-\begin{proof}
-By induction on the coalescence path.
-Let $\net\lambda AB$ coalesce to $\net\kappa AB$ where $\kappa=\{\clink AB\}$.
-First, we show that the result is correct.
-For each $x$ the witness set $\kappa(x)$ is $\{\sigma x\}$.
-the only slice of $\seq AB$ is $(A,B)$,
-\end{proof}
-
-Coalescence is effectively sequentialization. We will make this explicit by organising the rewrite rules as inference rules.
-
-%
-%As an intermediary between the sequent calculus and labelled proof nets, we will introduce a \defn{labelled sequent calculus}. A \defn{labelled sequent}
-%\[
-%	\xlink AB
-%\]
-%is a sequent that carries a linking $\lambda$ and a witness map $\sigma$. 
-%
-%
-%for the statement that $\lambda\seq{A\sigma}{B\sigma}$ coalesces to a single labelled 
-%
-
-\begin{figure}
-\hrule
-\par\bigskip
-\[
-\begin{array}{c@{\hspace{40pt}}ccc}
-	\vc{\infer{\crule [\sigma(P,\dual Q)] [\{(P,Q)\}] P Q}{}}
-&    
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{P}
-    	\formula[y=1]{Q}
-    	\Vlink[blue]{1,1}
-    \end{tikzpicture}}
-&\rightsquigarrow&    
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{P}
-    	\formula[y=1]{Q}
-    	\Vlink[red,label={$~\scriptstyle{\sigma(P,\dual Q)}$}]{1,1}
-    \end{tikzpicture}}
-\\ \\
-	\vc{\infer{\crule A {B\+C}} {\crule AB}}
-&   
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{A}
-    	\formula[y=1]{B\+C}
-    	\Vlink[red,label={$\scriptstyle\sigma~$},l]{1,1}
-    \end{tikzpicture}}
-&\rightsquigarrow& 
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{A}
-    	\formula[y=1]{B\+C}
-    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,2}
-    \end{tikzpicture}}
-\\ \\ 
-    \vc{\infer[\!\!\scriptstyle{\sigma\comp\tau}]
-    		{\crule [\sigma\cup\tau] [\lambda\cup\kappa] A {B\*C}}
-    		{\crule AB && \crule[\tau][\kappa]AC}}
-&     
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{A}
-    	\formula[y=1]{B\*C}
-    	\Vlink[red,label={$\scriptstyle\sigma~$},l]{[-1]1,1}
-    	\Vlink[red,label={~$\scriptstyle\tau$}]{[1]1,3}
-    \end{tikzpicture}}
-&\stackrel{\sigma\comp\tau}\rightsquigarrow&   
-	\vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{A}
-    	\formula[y=1]{B\*C}
-    	\Vlink[red,label={~$\scriptstyle{\sigma\cup\tau}$}]{1,2}
-    \end{tikzpicture}}
-
-\\ \\
-    \vc{\infer{\crule[\sigma\minus x]A{\exists x.B}}{\crule AB}}
-&
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{A}
-    	\formula[y=1]{\exists x.B}
-    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,4}
-    \end{tikzpicture}}
-&\rightsquigarrow&
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{A}
-    	\formula[y=1]{\exists x.B}
-    	\Vlink[red,label={~$\scriptstyle{\sigma\!\minus\!x}$}]{1,1}
-    \end{tikzpicture}}
-\\ \\
-    \vc{\infer[\!\!\scriptstyle{a\,\notin\,\fv(A\sigma)}]{\crule A{\forall a.B}}{\crule AB}}
-&    
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{A}
-    	\formula[y=1]{\forall a.B}
-    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,4}
-    \end{tikzpicture}}
-&\stackrel{a\,\notin\,\fv(A\sigma)}\rightsquigarrow&
-    \vc{\begin{tikzpicture}[net]
-    	\formula[y=2]{A}
-    	\formula[y=1]{\forall a.B}
-    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,1}
-    \end{tikzpicture}}
-\end{array}
-\]
-\par\bigskip\hrule
-\caption{Coalescence derivation rules}
-\label{fig:coalescence}
-\end{figure}
-
-\begin{lemma}
-Given a proof $\prf\Pi AB$, formulas $A'$, $B'$, and a witness map $\sigma$ such that $A'\sigma=A$ and $B'\sigma=B$, the de-sequentialization $\net{\deseq\Pi{A'}{B'}}AB$ coalesces to $\net{\{\clink AB\}}AB$.
-\end{lemma}
-
-\begin{lemma}
-Given a proof $\prf\Pi AB$ and formulas $A'$ and $B'$, if a smallest witness map $\tau$ exists such that $A=A'\tau$ and $B=B'\tau$, then $\deseq\Pi{A'}{B'}$ coalesces to $\clink{A'}{B'}$ with $\sigma\leq\tau$.
-\end{lemma}
-
-\begin{proof}
-By induction on $\Pi$.
-
-\newlength\prooftablewidth
-\setlength\prooftablewidth{-80pt}
-\addtolength\prooftablewidth{\textwidth}
-
-\noindent
-\begin{tabular}{@{}p{80pt}@{}p{\prooftablewidth}@{}}
-	\hfill \raisebox{-20pt}{\infer{\seq P{\dual P}}{\vphantom B}} \hfill\hfill
-&
-	Let $A'=Q$ and $B'=R$, and suppose $\tau$ is the smallest witness map such that $Q\tau=P$ and $R\tau=\dual P$.
-The desequentialization $\deseq\Pi QR$ is the $\net{\{Q,R\}}QR$, which coalesces to $\clink QR$ if $\sigma=\sigma(Q,{\dual R})$ exists.
-Since $\tau$ is a unifier of $Q$ and $\dual R$, $\sigma\leq\tau$.
-\\ \\
-%	$\infer{\seq A{B_0\+B_1}}{\seq A{B_i}}$
-%&
-%\\ \\
-	\hfill \raisebox{-20pt}{\infer{\seq A{B\*C}}{\seq AB && \seq AC}}\hfill\hfill
-&
-	Let $\seq{\prf\Pi AB}{A'}{B'}$ coalesce to the two subproofs coalesce to $\clink{A'}{B'}$ and $\clink[\rho]{A'}{B'}$ 
-%	\infer{\seq A{\exists x.B}}{\seq A{B[t/x]}}
-%	\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]{\seq A{\forall a.B}}{\seq AB}
-\end{tabular}
-
-\end{proof}
-
-\end{document}
-
-%\[
-%	\infer{\xlink [\sigma(P,Q)] [\{(P,Q)\}] P Q}{}
-%\]
-%\par
-%\[
-%	\infer{\xlink A {B_0\+B_1}} {\xlink A {B_i}}
-%\]
-%\par
-%\[
-%	\infer[\!\!\scriptstyle{\sigma\comp\tau}]
-%		{\xlink [\sigma\cup\tau] [\lambda\cup\kappa] A {B\*C}}
-%		{\xlink AB && \xlink[\tau][\kappa]AC}
-%\]
-%\par
-%\[
-%	\infer{\xlink[\sigma\minus x]A{\exists x.B}}{\xlink AB}
-%\]
-%\par
-%\[
-%	\infer[\!\!\scriptstyle{a\,\notin\,\fv(A\sigma)}]{\xlink A{\forall a.B}}{\xlink AB}
-%\]
-
-% --------------------------------------------------
-
-%\subsection{Existential witnesses}
-
-%
-%
-%For two first-order terms $s$ and $t$, and a set of variables $V$, let a $V$-\defn{unifier} be a unifying substitution map
-%\[
-%	\sigma\colon V\rightharpoonup \terms
-%\]
-%(that is, $s\sigma=t\sigma$). A $V$-unifier for atomic propositions $P$ and $Q$ is defined analogously. For example, 
-%
-%
-%The \defn{most general $V$-unifier} $\sigma_V(P,Q)$ of $P$ and $Q$ is the most general unifying
-%
-%let the \defn{initial witness map} $\sigma(P,Q)$ be the most general unifier of $P$ and $Q$, if it exists, where only existential variables can be substituted for, and universal variables are considered constant.
-That is, the only unifier of $p(x,y)$ and $p(a,a)$ is $\{x\mapsto a,y\mapsto a\}$, while $p(x,x)$ and $p(a,b)$ have no unifier.
-%
-%Let $\sigma\join\tau$ denote the combination of two witness maps $\sigma$ and $\tau$ as unifiers, if it exists.
-If it does, we call $\sigma$ and $\tau$ \defn{compatible}, expressed by $\sigma\comp\tau$.
-The initial witness map $\sigma(A,B)$ of two formulae $A$ and $B$, if it exists, is then given by:
-%
-%\begin{align}
-%	\left.\begin{array}{r}
-%		\sigma_V(\,A\+B\,,\,C\+D\,) \\
-%		\sigma_V(\,A\*B\,,\,C\*D\,)
-%	\end{array}\right\}
-%	& = \sigma_V(A,C)\join\sigma_V(B,D)
-%\\	
-%	\sigma_V(\,\forall a.A\,,\,\forall a.B\,)
-%		 \kern12.5pt & = \sigma_V(A,B)
-%\\	\sigma_V(\,\exists x.A\,,\,\exists x.B\,)
-%		 \kern12.5pt & = \sigma_{V-\{x\}}(A,B)
-%\end{align*}
-%
-%
-%Two witness maps $\sigma$ and $\tau$ are \defn{compatible}, written $\sigma\comp\tau$, if they agree wherever they are defined:
-%\[
-%	\sigma\comp\tau \quad\iff\quad \forall x\in\varE.~\big(\sigma(x)\neq\bot~\wedge~\tau(x)\neq\bot\big)~\Rightarrow~\sigma(x)=\tau(x)~.
-%\]
-%Two compatible witness maps can be combined into the map $\sigma\cup\tau$ that sends $x$ to $\sigma(x)$ or $\tau(x)$, whichever is defined, and is undefined when both are.
-To combine witness maps that may not be compatible we will write $\sigma\ubot\tau$, which is $\sigma\cup\tau$ if they are, and undefined ($\bot$) otherwise; if either $\sigma$ or $\tau$ is already undefined, $\sigma\ubot\tau$ also reverts to $\bot$.
-%\[
-%	\sigma\ubot\tau\quad=\quad
-%	\left\{\begin{array}{ll}
-%		\sigma\cup\tau	& \text{if $\sigma\neq\bot$, $\tau\neq\bot$, and $\sigma\comp\tau$} \\
-%		\bot			& \text{otherwise} \\
-%	\end{array}\right.
-%\] 
-%Note that $\bot$ is not a witness map, and different from the empty substitution map, $\sigma(x)=\bot$ for all $x$.
-For two atomic formulas $P,Q$ (or terms $s,t$) the \defn{initial witness map} $\sigma(P,Q)$ is the smallest witness map $\sigma$ such that $P\sigma=\dual Q\sigma$ and $P\sigma$ has no free existential variables.
-If it exists, it is defined inductively as follows (omitting the symmetric case for $\dual p$ and $p$).
-%
-%\begin{align*}
-%	\left.\begin{array}{r}
-%		\sigma(\,x\,,\,t\,) \\
-%	 	\sigma(\,t\,,\,x\,)
-%	\end{array}\right\}
-%	& = \{ x\mapsto t \}\quad \text{if $t\in\termsA$}
-% \\
-%	\left.\begin{array}{r}
-%		\sigma(\,p(s_1,\dots,s_n)\,,\,\dual p(t_1,\dots,t_n)\,) \\
-%		\sigma(\,f(s_1,\dots,s_n)\,,\,f(t_1,\dots,t_n)\,)
-%	\end{array}\right\}
-%	& = \sigma(s_1,t_1)\ubot\dots\ubot\sigma(s_n,t_n)
-%\end{align*}
-%
-%\begin{lemma}
-%\label{lem:minimal witness map}
-%For first-order terms $s$ and $t$ the witness map $\sigma(s,t)$ is the smallest such that $s\sigma=t\sigma$ and $s\sigma$ contains no existential variables.
-%\end{lemma}
-%
-%\begin{proof}
-%By induction on $s$ and $t$. If $s=x$ then $\sigma(x,t)$ exists if and only if $t\in\termsA$, 
-%\end{proof}
-
-%\begin{align*}
-%	\sigma_V(\,a\,,\,a\,) \kern12.5pt & = \varnothing
-%\\	\sigma_V(\,x\,,\,x\,) \kern12.5pt & = \varnothing\quad \text{if $x\in V$}
-%\\
-%	\left.\begin{array}{r}
-%		\sigma_V(\,x\,,\,t\,) \\
-%	 	\sigma_V(\,t\,,\,x\,)
-%	\end{array}\right\}
-%	& = \{ x\mapsto t \}\quad \text{if $x\notin V$ and $t\in\termsA$}
-% \\
-%	\left.\begin{array}{r}
-%		\sigma_V(\,p(s_1,\dots,s_n)\,,\,p(t_1,\dots,t_n)\,) \\
-%		\sigma_V(\,f(s_1,\dots,s_n)\,,\,f(t_1,\dots,t_n)\,)
-%	\end{array}\right\}
-%	& = \sigma_V(s_1,t_1)\ubot\dots\ubot\sigma_V(s_n,t_n)
-%\\	
-%	\left.\begin{array}{r}
-%		\sigma_V(\,A\+B\,,\,C\+D\,) \\
-%		\sigma_V(\,A\*B\,,\,C\*D\,)
-%	\end{array}\right\}
-%	& = \sigma_V(A,C)\ubot\sigma_V(B,D)
-%\\	
-%	\sigma_V(\,\forall a.A\,,\,\forall a.B\,)
-%		 \kern12.5pt & = \sigma_V(A,B)
-%\\	\sigma_V(\,\exists x.A\,,\,\exists x.B\,)
-%		 \kern12.5pt & = \sigma_{V\cup\{x\}}(A,B)
-%\end{align*}
-%
-%Observe that if the witness map $\sigma=\sigma(A,B)$ exists then $A\sigma=B\sigma$.
-
-% --------------------------------------------------
-
-\begin{lemma}
-Given a proof $\prf\Pi AB$ and formulas $A'$ and $B'$, if a smallest witness map $\tau$ exists such that $A=A'\tau$ and $B=B'\tau$, then $\deseq\Pi{A'}{B'}$ coalesces to $\clink{A'}{B'}$ with $\sigma\leq\tau$.
-\end{lemma}
-
-\begin{proof}
-By induction on $\Pi$.
-
-\newlength\prooftablewidth
-\setlength\prooftablewidth{-80pt}
-\addtolength\prooftablewidth{\textwidth}
-
-\noindent
-\begin{tabular}{@{}p{80pt}@{}p{\prooftablewidth}@{}}
-	\hfill \raisebox{-20pt}{\infer{\seq P{\dual P}}{\vphantom B}} \hfill\hfill
-&
-	Let $A'=Q$ and $B'=R$, and suppose $\tau$ is the smallest witness map such that $Q\tau=P$ and $R\tau=\dual P$.
-The desequentialization $\deseq\Pi QR$ is the $\net{\{Q,R\}}QR$, which coalesces to $\clink QR$ if $\sigma=\sigma(Q,{\dual R})$ exists.
-Since $\tau$ is a unifier of $Q$ and $\dual R$, $\sigma\leq\tau$.
-\\ \\
-%	$\infer{\seq A{B_0\+B_1}}{\seq A{B_i}}$
-%&
-%\\ \\
-	\hfill \raisebox{-20pt}{\infer{\seq A{B\*C}}{\seq AB && \seq AC}}\hfill\hfill
-&
-	Let $\seq{\prf\Pi AB}{A'}{B'}$ coalesce to the two subproofs coalesce to $\clink{A'}{B'}$ and $\clink[\rho]{A'}{B'}$ 
-%	\infer{\seq A{\exists x.B}}{\seq A{B[t/x]}}
-%	\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]{\seq A{\forall a.B}}{\seq AB}
-\end{tabular}
-
-\end{proof}

### 2019-03-29 5 - FSCD 2019 - Submitted/Reviews/rebuttal v1.txt
polishing rebuttal

@@
 
-In fact, we may alpha-convert at the level of proofs and proof nets; but for the sanity of the translations both ways, not at the level of individual formulas in a sequent proof.
+In fact, we may alpha-convert at the level of proofs and proof nets; but for the sanity of the translations between them, not at the level of individual formulas in a sequent proof.
 
-Normally, indeed, every universal instantiation must have a unique eigenvariable. But for our proof nets, we only need (and have) this property for each slice individually.
+Normally in proof nets, indeed, every universal instantiation should have a unique eigenvariable. But here we only need this property for each slice individually.
 
@@
 Other combinations are unlikely to work, or the groundwork is still incomplete: slice nets do not support coalescence (this looks fundamentally problematic), and conflict nets do not yet have a slicing criterion (work in progress).
+
+==============================
+
+Review 3:
+
+(F) Unification seems to break the variable naming convention.
+
+Indeed - a naive unification algorithm would.
+We should stipulate explicitly that an "initial witness map" (the MGU for a link) uses fresh variables in its range, distinct from any existentially quantified ones (which occur in its domain); then all is well.

### 2019-03-29 5 - FSCD 2019 - Submitted/Reviews/rebuttal v1.txt
more polish
polish polish

@@
 
+There are! We formulate these as a "dependency" relation, which is standard practice for graphical first-order proofs (see e.g. Miller's Expansion Tree Proofs).
+
 The purpose of a leap edge is to explicitly record the dependency between quantifiers: when the eigenvariable (x) of a universal quantifier is used in the witnessing term (t{x}) to an existential quantifier.
-This corresponds to our "dependency" relation (Definition 10).
-The relevant part can be paraphrased: if (x) is the eigenvariable for a quantification "forall x.Y", and an explicit substitution [t{x}/y] ranges over a formula X, then there is a dependence (a "leap" or "jump") between Y and X.
+We capture this in our "dependency" relation (Definition 10).
+The relevant part can be paraphrased: if (x) is the eigenvariable for a quantification "forall x.Y", and an explicit substitution [t{x}/y] ranges over a formula X, then there is a dependence (i.e.
+a "leap", or a "jump") between Y and X.
 
@@
 Yes.
-For geometric correctness, it seems essential to reconstruct the dependencies (or "leaps", or "jumps") globally.
-In MLL1, where there are no slices, a single global unifier (for all links) can be constructed, from which the dependency is then derived.
+For geometric correctness, it seems essential to reconstruct dependencies globally.
+In MLL1, where there are no slices, a single global unifier (for all links) can be constructed, from which the dependency is then derived (as "leap" edges).
 
 With slices, the situation is much more involved.
-Dependencies (leaps) must be made explicit between existential quantifiers and products (see "Expansion", pages 8--9) as well as universal quantifiers.
+Dependencies must be made explicit between existential quantifiers and products (see "Expansion", pages 8--9) as well as universal quantifiers.
 These interact in highly intricate ways, which the unifying coalescence algorithm resolves incrementally and locally.
-To do so globally, as a geometric criterion would, is a huge combinatorial challenge, beyond the scope of this paper.
+To do so globally, as would be necessary for a geometric criterion, is a huge combinatorial challenge, beyond the scope of this paper.
 
@@
 
-Indeed - a naive unification algorithm would.
+Indeed - the standard unification algorithm would.
 We should stipulate explicitly that an "initial witness map" (the MGU for a link) uses fresh variables in its range, distinct from any existentially quantified ones (which occur in its domain); then all is well.

### 2019-03-31 5 - FSCD 2019 - Submitted/Reviews/rebuttal v1.txt
rebuttal polish

@@
 
-There are! We formulate these as a "dependency" relation, which is standard practice for graphical first-order proofs (see e.g. Miller's Expansion Tree Proofs).
+There are! We have these in the form of a "dependency" relation. (This is standard for graphical first-order proofs; see e.g. Miller's Expansion Tree Proofs.)
 
@@
 a "leap", or a "jump") between Y and X.
+
+Just like the "leaps" in Hughes's MLL1 nets, our dependency is not explicit, but derived from the data structure (from the occurrences of eigenvariables in the explicit substitutions).
 
@@
 With slices, the situation is much more involved.
-Dependencies must be made explicit between existential quantifiers and products (see "Expansion", pages 8--9) as well as universal quantifiers.
-These interact in highly intricate ways, which the unifying coalescence algorithm resolves incrementally and locally.
+Dependencies must be made explicit between existential quantifiers and products (see "Expansion", pages 8--9) as well as existential and universal quantifiers.
+These interact in highly intricate ways - which the unifying coalescence algorithm resolves incrementally and locally.
 To do so globally, as would be necessary for a geometric criterion, is a huge combinatorial challenge, beyond the scope of this paper.

### 2019-04-01 5 - FSCD 2019 - Submitted/Reviews/rebuttal v1.txt
updated

@@
 
-(A) Why isn't there any **leap** edge?
+(A) Why isn't there any **leap** edge in the slicing criterion?
 
-There are! We have these in the form of a "dependency" relation. (This is standard for graphical first-order proofs; see e.g. Miller's Expansion Tree Proofs.)
+There are!
+We have these in the form of a "dependency" relation, part of the geometric correctness criterion.
+(This is standard for graphical first-order proofs; see e.g.
+Miller's Expansion Tree Proofs.)
 
@@
 Just like the "leaps" in Hughes's MLL1 nets, our dependency is not explicit, but derived from the data structure (from the occurrences of eigenvariables in the explicit substitutions).
+But note that in MLL1, the derived leaps are explicitly part of the "switching graphs" of the correctness criterion, so that they can interact with tensors to create cycles.
+In ALL1 there are no tensors to interact with leaps, so we can have a completely separate “dependency acyclicity” condition (our "dependency-correct" condition).
 
-We do not need leap edges for coalescence; we believe that likewise, contractibility for MLL1 unification nets would not need them.
+In contrast with geometric correctness, we do not need leap edges for coalescence; we believe that likewise, contractibility for MLL1 unification nets would not need them.
 
@@
 
-The situation is mixed. There are two ways forward that are likely to succeed:
+The situation is mixed. There are two ways forward that could succeed:
  - combine witness nets and MALL slice nets [Hughes & Van
@@
 because coalescence for MALL is not a straightforward extension of that for ALL).
-Other combinations are unlikely to work, or the groundwork is still incomplete: slice nets do not support coalescence (this looks fundamentally problematic), and conflict nets do not yet have a slicing criterion (work in progress).
+Other combinations are unlikely to work, or the groundwork is still incomplete: MALL slice nets do not support coalescence (this looks fundamentally problematic), and MALL conflict nets do not yet have a slicing criterion (work in progress).
 

### 2019-04-01 5 - FSCD 2019 - Submitted/Reviews/rebuttal v2.txt
rebuttal v2

--- 2019-04-01 5 - FSCD 2019 - Submitted/Reviews/rebuttal v1.txt
@@
+Review 1 is overall very positive but makes the vote for acceptance
+dependent on two technical questions that we address in (A) and (B)
+below.
+
+Review 2 and 3 both ask about MALL1, which we discuss in (C) below.
+
+Further minor questions by Review 2 and 3 are addressed in (D), (E),
+and (F).
+
+=====================================
 Review 1:
@@
 
-There are!
-We have these in the form of a "dependency" relation, part of the geometric correctness criterion.
-(This is standard for graphical first-order proofs; see e.g.
-Miller's Expansion Tree Proofs.)
+There are! However, they are not explicit. They occur in the form of a
+"dependency" relation, as part of the geometric correctness
+criterion. (This is standard for graphical first-order proofs; see
+e.g. Miller's Expansion Tree Proofs.)
 
-The purpose of a leap edge is to explicitly record the dependency between quantifiers: when the eigenvariable (x) of a universal quantifier is used in the witnessing term (t{x}) to an existential quantifier.
-We capture this in our "dependency" relation (Definition 10).
-The relevant part can be paraphrased: if (x) is the eigenvariable for a quantification "forall x.Y", and an explicit substitution [t{x}/y] ranges over a formula X, then there is a dependence (i.e.
-a "leap", or a "jump") between Y and X.
+The purpose of a leap edge in other proof net like presentations is to
+explicitly record the dependency between quantifiers: when the
+eigenvariable (x) of a universal quantifier is used in the witnessing
+term (t{x}) to an existential quantifier.
 
-Just like the "leaps" in Hughes's MLL1 nets, our dependency is not explicit, but derived from the data structure (from the occurrences of eigenvariables in the explicit substitutions).
-But note that in MLL1, the derived leaps are explicitly part of the "switching graphs" of the correctness criterion, so that they can interact with tensors to create cycles.
-In ALL1 there are no tensors to interact with leaps, so we can have a completely separate “dependency acyclicity” condition (our "dependency-correct" condition).
+We capture this in our "dependency" relation (Definition 10). The
+relevant part can be paraphrased: if (x) is the eigenvariable for a
+quantification "forall x.Y", and an explicit substitution [t{x}/y]
+ranges over a formula X, then there is a dependence (i.e. a "leap", or
+a "jump") between Y and X.
 
-In contrast with geometric correctness, we do not need leap edges for coalescence; we believe that likewise, contractibility for MLL1 unification nets would not need them.
+Just like the "leaps" in Hughes's MLL1 nets, our dependency is not
+explicit, but derived from the data structure (from the occurrences of
+eigenvariables in the explicit substitutions). But note that in MLL1,
+the derived leaps are explicitly part of the "switching graphs" of the
+correctness criterion, so that they can interact with tensors to
+create cycles. In ALL1 there are no tensors to interact with leaps, so
+we can have a completely separate “dependency acyclicity” condition
+(our "dependency-correct" condition).
+
+In contrast with geometric correctness, we do not need leap edges for
+coalescence; we believe that likewise, contractibility for MLL1
+unification nets would not need them.
 
@@
 
-Yes.
-For geometric correctness, it seems essential to reconstruct dependencies globally.
-In MLL1, where there are no slices, a single global unifier (for all links) can be constructed, from which the dependency is then derived (as "leap" edges).
+Yes. For geometric correctness, it seems essential to reconstruct
+dependencies globally. In MLL1, where there are no slices, a single
+global unifier (for all links) can be constructed, from which the
+dependency is then derived (as "leap" edges).
 
-With slices, the situation is much more involved.
-Dependencies must be made explicit between existential quantifiers and products (see "Expansion", pages 8--9) as well as existential and universal quantifiers.
-These interact in highly intricate ways - which the unifying coalescence algorithm resolves incrementally and locally.
-To do so globally, as would be necessary for a geometric criterion, is a huge combinatorial challenge, beyond the scope of this paper.
+With slices, the situation is much more involved. Dependencies must be
+made explicit between existential quantifiers and products (see
+"Expansion", pages 8--9) as well as existential and universal
+quantifiers. These interact in highly intricate ways - which the
+unifying coalescence algorithm resolves incrementally and locally. To
+do so globally, as would be necessary for a geometric criterion, is a
+huge combinatorial challenge, beyond the scope of this paper.
 
-==============================
+=====================================
+Review 2 and 3:
 
+(C) Can this be extended to MALL1?
+
+The situation is mixed. There are two ways forward that could succeed:
+
+ - combine witness nets and MALL slice nets [Hughes & Van
+   Glabbeek 2005], using a slicing criterion;
+
+- combine unification nets and MALL conflict nets [Hughes &
+   Heijltjes 2016], using a coalescence criterion.
+
+For both, there are still significant combinatorial challenges
+(e.g. because coalescence for MALL is not a straightforward extension
+of that for ALL). Other combinations are unlikely to work, or the
+groundwork is still incomplete: MALL slice nets do not support
+coalescence (this looks fundamentally problematic), and MALL conflict
+nets do not yet have a slicing criterion (work in progress).
+
+=====================================
 Review 2:
 
-(C) Is the equivalence generated by unification a form of observational equivalence?
+(D) Is the equivalence generated by unification a form of observational equivalence?
 
@@
 
-(D) Both proofs and witness nets are not considered up to alpha-equivalence.
+(E) Both proofs and witness nets are not considered up to alpha-equivalence.
 
@@
 
-==============================
-
-Reviews 2 and 3:
-
-(E) Can this be extended to MALL1?
-
-The situation is mixed. There are two ways forward that could succeed:
- - combine witness nets and MALL slice nets [Hughes & Van
-   Glabbeek 2005], using a slicing criterion;
- - combine unification nets and MALL conflict nets [Hughes &
-   Heijltjes 2016], using a coalescence criterion.
-For both, there are still significant combinatorial challenges (e.g.
-because coalescence for MALL is not a straightforward extension of that for ALL).
-Other combinations are unlikely to work, or the groundwork is still incomplete: MALL slice nets do not support coalescence (this looks fundamentally problematic), and MALL conflict nets do not yet have a slicing criterion (work in progress).
-
-==============================
-
+=====================================
 Review 3:
@@
 Indeed - the standard unification algorithm would.
-We should stipulate explicitly that an "initial witness map" (the MGU for a link) uses fresh variables in its range, distinct from any existentially quantified ones (which occur in its domain); then all is well.
+But we can stipulate explicitly that an "initial witness map" (the MGU for a link) uses fresh variables in its range, distinct from any existentially quantified ones (which occur in its domain); then all is well.

### 2019-04-16 7 - FSCD 2019 - Final/ALL1.tex
reviews, rebuttal, reorganise
prep for final submission

--- 2019-02-11 ALL1.tex
@@
 \documentclass[UKenglish]{lipics-v2019}
+
+\nolinenumbers
 
@@
 \makeatletter
-
-%\theoremstyle{plain}
-%\newtheorem{proposition}[theorem]{Proposition}
 
@@
 
+%\relatedversion{http://hal.inria.fr/hal-01867625/}
+
+\EventEditors{Herman Geuvers}
+\EventNoEds{1}
+\EventLongTitle{4th International Conference on Formal Structures for Computation and Deduction (FSCD 2019)}
+\EventShortTitle{FSCD 2019}
+\EventAcronym{FSCD}
+\EventYear{2019}
+\EventDate{June 24--30, 2019}
+\EventLocation{Dortmund, Germany}
+\EventLogo{}
+\SeriesVolume{131}
+\ArticleNo{22}
+
 % ============================== CONTENT
@@
 
-%We present two solutions to the \emph{proof-net problem}, finding a canonical representation of proofs, for additive linear logic (\all) extended with first-order quantification (\all1).
-
-%\all is the fragment of linear logic \cite{Girard-1987} that describes sums and products, and their canonical morphisms: projections, injections, and diagonals.
-The logic represents a rich but tractable microcosm in which to explore important semantic ideas.
-By the duality between sum and product
+%We investigate the \emph{proof-net problem}, finding a canonical representation of proofs, for additive linear logic (\all) extended with first-order quantification (\all1).
+\all\ is the fragment of linear logic \cite{Girard-1987} that describes sums and products, and their canonical morphisms: projections, injections, and diagonals.
+It is rich, well-behaved, and compact: an ideal microcosm in which to explore semantic and proof-theoretic ideas.
+Here, we explore two techniques to account for the witness information that is essential to first-order proof: \emph{explicit substitution} and first-order \emph{unification}.
 
@@
 We write $\prf\pi AB$ for a proof $\pi$ with conclusion sequent $\seq AB$.
-Two proofs are \defn{equivalent} $\pi\sim\pi'$ if one is obtained from the other by rule permutations (Appendix~\ref{sec:permutations}, Figure~\ref{fig:permutations}).
+Two proofs are \defn{equivalent} $\pi\sim\pi'$ if one is obtained from the other by rule permutations, given in Figure~\ref{fig:permutations}.
 
@@
 
+\begin{figure}[!ht]
+\[
+\renewcommand\+{{+}}
+\renewcommand\*{{\times}}
+\scalebox{0.85}{$
+\begin{array}{@{}c@{\qquad}c@{\qquad}c@{\qquad}c@{}}
+	\permAB   & \permAE   & \permAP   & \permAX 
+\\	\downperm & \downperm & \downperm & \downperm \\
+	\permBA   & \permEA   & \permPA   & \permXA
+\\ \\[20pt]
+ 			  & \permEF   & \permEP   & \permEX
+\\			  & \downperm & \downperm & \downperm \\
+ 			  & \permFE   & \permPE   & \permXE
+\\ \\[20pt]
+ 			  &			  & \permPQ   & \permPX
+\\			  &			  & \downperm & \downperm \\
+ 			  &			  & \permQP   & \permXP
+\\ \\[20pt]
+ 			  &			  &			  & \permXY
+\\			  &			  &			  & \downperm \\
+ 			  &			  &			  & \permYX
+\end{array}$}
+\]
+\caption{Cut-free rule permutations}
+\label{fig:permutations}
+\end{figure}
+
+% ..................................................
+
 A \defn{link} $(C,D)$ on a sequent $\seq AB$ is a pair of subformulas $C\leq A$ and $D\leq B$. 
@@
 \begin{definition}
-The \defn{de-sequentialization} $[\pi]$ of a sequent proof $\prf\pi AB$ is the witness pre-net $\net{\deseq[\varnothing]\pi AB}AB$ where the function $\deseq-AB$ is defined inductively as follows.
+The \defn{de-sequentialization} $[\pi]$ of a sequent proof $\prf\pi AB$ is the witness pre-net $\net{\deseq[\varnothing]\pi AB}AB$ where the function $\deseq-AB$ is defined inductively as follows (symmetric cases are omitted).
 %
@@
 \]
+
+% ..................................................
+
 \begin{definition}
@@
 %
-\defn{Strict sequentialization} ($\scoal$) is the rewrite relation on labelled pre-nets generated by the following rules, that replace one or two links by another in a pre-net $\net{\lambda_\Sigma^\Pi}AB$ (where $B$ has a subformula $D_1\+D_2$, $D_1\*D_2$, $\exists x.D$, and $\forall x.D$ respectively).
+\defn{Strict sequentialization} ($\scoal$) is the rewrite relation on labelled pre-nets generated by the following rules, that replace one or two links by another in a pre-net $\net{\lambda_\Sigma^\Pi}AB$ where $B$ has a subformula $D_1\+D_2$, $D_1\*D_2$, $\exists x.D$, and $\forall x.D$ respectively.
+Symmetric cases are omitted.
 %
@@
 \end{definition}
+
 % ..................................................
@@
 % ..................................................
+
 \begin{definition}
@@
 % ..................................................
+
 \begin{theorem}
@@
 
-%\begin{proof}
-%It follows by induction on $\pi$ that if $\lambda_\Sigma=\deseq{\prf\pi AB}{A'}{B'}$ where $A'\sigma=A$ and $B'\sigma=B$, then $\net{\lambda^\star_\Sigma}AB$ reduces in $(\scoal)$ to $\net{\{\link{A'}{B'}^\pi\}}AB$.
-The statement is the case $\sigma=\varnothing$.
-%\end{proof}
-% ..................................................
-
-% ..................................................
+% ..................................................
+
 \begin{theorem}
@@
 
-%\begin{proof}
-%By induction on the sequentialization path 
-%$\net{\lambda_\Sigma^\star}AB\scoal^*\net{\{\link[\varnothing]AB^\pi\}}AB$
-%it follows that in every pre-net $\net{\kappa_\Theta^\Phi}AB$ on this path, $\lambda_\Sigma$ is equal to the union over the de-sequentialization of all proof labels $\phi$ in $\Phi$:
-%\[
-%	\lambda_\Sigma=\bigcup~\{\,\deseq\phi CD \mid \link CD^\phi \in \kappa_\Theta^\Phi\,\}~.
-%\]
-%The statement is then the case $\kappa_\Theta^\Phi=\{\link[\varnothing]AB^\pi\}$.
-%\end{proof}
 % ..................................................
@@
 \end{theorem}
-
-%\begin{proof}
-%From left to right is by inspection of the critical pairs of sequentialization ($\scoal$).
-From right to left is by inspection of the rule permutations in Figure~\ref{fig:permutations} in Appendix~\ref{sec:permutations}.
-%\end{proof}
 
@@
 
+% ..................................................
+
 \paragraph*{Slices}
@@
 It captures the non-permutability of universal and existential sequent rules due to the \emph{eigenvariable condition} of the former, as below right.
-	%\item[]
+\end{description}
+
 \[
@@
 \]
-\end{description}
-
-%\noindent
-%Formalizing this, for a witness linking $\lambda_\Sigma$ and variable $x$, write $\Sigma(x)\subseteq\terms$ for the \defn{witness set} of $x$, which collects the terms assigned to $x$ by the witness maps in $\Sigma$ for every link in $\lambda$:
-%\[
-%	\Sigma(x) = \{~\sigma(x)~\mid~\link CD\in\lambda_\Sigma~\}~.
-%\]
-
-% ..................................................
+
+\noindent
+\emph{Expansion} covers the interaction between existential quantifiers and products, and \emph{dependency} that between existential and universal quantifiers.
+Note that in proof nets that include the multiplicatives (e.g.\ \cite{Girard-1996,Hughes-2018}), instead of a dependency as a \emph{partial order} it is common to consider the underlying graph, created by adding a \emph{jump} or \emph{leap} edge when an existential instantiation $B[t/y]$ of $\exists y.B$ contains the eigenvariable $x$ of $\forall x.A$.
+These edges participate in the \emph{switching} condition \cite{Danos-Regnier-1989}, to capture the interaction between quantifiers and tensors.
+Without the tensor, here, the dependency as a partial order suffices.
+
+% ..................................................
+
 \begin{definition}[Slice]
@@
 
-%As in the propositional case, for correctness we will require that each slice is a singleton.
-In addition, within each slice we need to ensure that the order in which quantifiers are instantiated is sound.
-That is, we need to have an analogue of the \emph{eigenvariable condition} on the $\qrr!$-rule of sequent calculus, that the quantified variable $x$ of the formula $\forall x.A$ does not occur free in the context.
-We will define a \defn{dependency} condition to this effect.
-For simplicity we will define the dependency condition on individual links rather than on slices.
+% ..................................................
 
@@
 \end{definition}
-% ..................................................
-
-%In the remainder of this section we will establish that the two correctness conditions, by coalescence and by slicing, are equivalent.
-The geometric condition further gives \emph{strong} coalescence: since it is preserved, no coalescence step yields an incorrect, and thus non-coalescing, pre-net.
-Finally, canonicity follows by inspecting the critical pairs of sequentialization.
+
+% ..................................................
 
 To conclude this section we will establish that both correctness conditions, by coalescence and by slicing, are equivalent. Moreover, both are equivalent to \emph{strong} coalescence.
-
-% ..................................................
-%\newcounter{lemcorrect}
-%\setcounter{lemcorrect}{\thetheorem}
-%\begin{lemma}
-%\label{lem:correct}
-%Strict coalescence preserves and reflects correctness.
-%\end{lemma}
-
-%\begin{proof}
-%See the appendix.
-%\end{proof}
-
-% ..................................................
-
-%\newcounter{lemcoalescenceapplies}
-%\setcounter{lemcoalescenceapplies}{\thetheorem}
-%\begin{lemma}
-%\label{lem:coalescence applies}
-%To a correct witness pre-net $\net{\lambda_\Sigma}AB$ a coalescence step applies, unless it is fully coalesced already, $\lambda_\Sigma=\{\link[\varnothing]AB\}$.
-%\end{lemma}
-
-%\begin{proof}
-%See the appendix.
-%\end{proof}
 
@@
 \end{theorem}
-
-%\begin{proof}
-%For the first statement, we proceed by induction on the coalescence path from $\net{\lambda_\Sigma}AB$ to $\net{\{\link[\varnothing]AB\}}AB$, with the end result as the base case.
-It is slice-correct: every slice of $\seq AB$ contains $\link[\varnothing]AB$, so every slice of $\net{\{\link[\varnothing]AB\}}AB$ is the singleton $\{\link[\varnothing]AB\}$.
-It is also dependency-correct: the column of $\link[\varnothing]AB$ is the set $\{(A,\varnothing),(B,\varnothing)\}$, where $A$ and $B$ are unrelated in $(\dep)$.
-For the inductive step, by Lemma~\ref{lem:correct} coalescence reflects correctness, so that any pre-net along the coalescence path is correct, in particular $\net{\lambda_\Sigma}AB$.
-%
-%For the second statement, let $\net{\lambda_\Sigma}AB$ be correct.
-%We proceed by induction on the \emph{depth} of the links in $\net{\lambda_\Sigma}AB$, their distance to the roots of $A$ and $B$, and observe that this measure strictly decreases for any coalescence step.
-%By Lemma~\ref{lem:coalescence applies} either the net has coalesced, or a coalescence step applies.
-By Lemma~\ref{lem:correct} the result of any coalescence step is again correct.
-Since links strictly move towards the roots of both formula trees, it follows that this process terminates, and the pre-net $\net{\lambda_\Sigma}AB$ strongly strict-coalesces.
-%\end{proof}
 
@@
 
+% ..................................................
+\begin{figure}[!ht]
+\[
+\renewcommand\+{{+}}
+\renewcommand\*{{\times}}
+\scalebox{0.85}{$
+\begin{array}{c@{\qquad}c}
+	\permAC   & \permEC   
+\\	\downperm & \downperm \\
+	\permCA   & \permCE
+\\ \\[20pt]
+	\permPC   & \permXC 
+\\	\downperm & \downperm \\
+	\permCP   & \permCX
+\end{array}
+\begin{array}{c}
+	\permCD \\ \downperm \\ \permDC
+\end{array}
+$}
+\]
+\caption{Cut-permutations}
+\label{fig:cut-permutations}
+\end{figure}
+% ..................................................
+
 % --------------------------------------------------
@@
 \indent
-Cut-elimination rules for \all1 are given in Figure~\ref{fig:cut-elim}; the needed permutations are in Appendix~\ref{sec:permutations}, Figure~\ref{fig:cut-permutations}.
+Cut-elimination rules for \all1 are given in Figure~\ref{fig:cut-elim}; the needed permutations are in Figure~\ref{fig:cut-permutations}.
 }
@@
 \end{definition}
+% ..................................................
+
+The composition of two links is strongly related to composition of strategies in game semantics.
+There, two strategies on $\seq AB$ and $\seq{\dual B}C$ are composed by \emph{interaction} on the interface of $B$ and $\dual B$, and subsequently \emph{hiding} that interaction.
+
+In the following we will demonstrate that composition gives the desired result: if a net $L$ sequentializes to $\pi$ and $R$ to $\phi$, then $L\comp R$ sequentializes to a normal form of the composition of $\pi$ and $\phi$ with a cut.
+To this end we will explore how composition and sequentialization interact.
+We will consider the critical pairs of sequentialization $(\scoal)$ with composition $(\Rightarrow)$ given in Figures~\ref{fig:crit1}--\ref{fig:crit3}, and demonstrate how they are resolved.
+
+\begin{itemize}
+	\item 
+$\seq A{B_1{\*}B_2}$ ; $\seq{\dual B_1{\+}\dual B_2}C$\quad (Figure~\ref{fig:crit1})
+\\
+Since the free existential variables of $B$ and $B_1$ are the same, $\sigma_B\tau\subdual B = \sigma_{B_1}\tau\subdual{B_1}$ and $\rho=\rho'$.
+It then follows that $\psi'$ cut-eliminates in one step to $\psi$.
+
+	\item
+$\seq A{\exists x.B}$ ; $\seq{\forall x.\dual B}C$\quad (Figure~\ref{fig:crit2})
+\\	
+Since $x$ is not free in the range of $\tau$, nor in the range of $\sigma$ (by Barendregt's convention), we have that $\fix{\sigma_B\tau\subdual B}$ is $\fix[1pt]{(\sigma_B\minus x)\tau\subdual B}$ plus the substitution $[\sigma(x)/x]$.
+Then $\rho=\rho'$ (as $x$ does not occur in the range of $\sigma_A\tau_C$) and $\psi'$ reduces to $\psi$ in a single cut-elimination step.
+
+	\item
+\parbox[t]{0.72\columnwidth}{
+$\seq AB$ ; $\seq{\dual B}{\exists x.C}$\quad (Figure~\ref{fig:crit3})
+\\
+Observe that since $x$ occurs in $C$ but not $B$, it is not in the domain of $\tau_B$, so that $\tau_B\minus x$ is just $\tau_B$.
+Then $\rho'=\rho\minus x$, and the diagram is closed by a sequentialization step (from left to right) that extends $\psi$ with an existential introduction rule, to a proof equivalent to $\psi'$:
+}\hfill
+\raisebox{-40pt}{$
+	\infer[\!\!\scriptstyle{\qrr?{\rho(x)}}]{\Seq{A\rho'}{\exists x.C\rho'}}{
+	 \Prf\psi{A\rho}{C\rho}
+	}
+$}
+\end{itemize}
+
+\noindent
+There are three further critical pairs, for a proof net on $\seq AB$ composed with one on $\seq {\dual B}{C_1{\+}C_2}$, one on $\seq {\dual B}{C_1{\*}C_2}$, and one on $\seq {\dual B}{\forall x.C}$.
+These converge as the one above.
+%
+Resolving these critical pairs gives the soundness of the composition operation, per the following theorem. We abbreviate a cut on proofs $\prf\pi AB$ and $\prf\phi{\dual B}C$ by $\pi\comp\phi$.
+
+% ..................................................
+\begin{theorem}
+\label{thm:composition}
+If proof nets $\net{\lambda_\Sigma}AB$ and $\net{\kappa_\Theta}{\dual B}C$ sequentialize to $\pi$ and $\phi$ respectively, then their composition $(\net{\lambda_\Sigma}AB)\comp(\net{\kappa_\Theta}{\dual B}C)$ is well-defined (i.e.\ all fixed points are finite) and sequentializes to a normal form $\psi$ of $\pi\comp\phi$.
+\end{theorem}
 % ..................................................
@@
 
-The composition of two links is strongly related to composition of strategies in game semantics.
-There, two strategies on $\seq AB$ and $\seq{\dual B}C$ are composed by \emph{interaction} on the interface of $B$ and $\dual B$, and subsequently \emph{hiding} that interaction.
-
-In the following we will demonstrate that composition gives the desired result: if a net $L$ sequentializes to $\pi$ and $R$ to $\phi$, then $L\comp R$ sequentializes to a normal form of the composition of $\pi$ and $\phi$ with a cut.
-To this end we will explore how composition and sequentialization interact.
-We will consider the critical pairs of sequentialization $(\scoal)$ with composition $(\Rightarrow)$ given in Figures~\ref{fig:crit1}--\ref{fig:crit3}, and demonstrate how they are resolved.
-
-\begin{itemize}
-	\item 
-$\seq A{B_1{\*}B_2}$ ; $\seq{\dual B_1{\+}\dual B_2}C$\quad (Figure~\ref{fig:crit1})
-\\
-Since the free existential variables of $B$ and $B_1$ are the same, $\sigma_B\tau\subdual B = \sigma_{B_1}\tau\subdual{B_1}$ and $\rho=\rho'$.
-It then follows that $\psi'$ cut-eliminates in one step to $\psi$.
-
-	\item
-$\seq A{\exists x.B}$ ; $\seq{\forall x.\dual B}C$\quad (Figure~\ref{fig:crit2})
-\\	
-Since $x$ is not free in the range of $\tau$, nor in the range of $\sigma$ (by Barendregt's convention), we have that $\fix{\sigma_B\tau\subdual B}$ is $\fix[1pt]{(\sigma_B\minus x)\tau\subdual B}$ plus the substitution $[\sigma(x)/x]$.
-Then $\rho=\rho'$ (as $x$ does not occur in the range of $\sigma_A\tau_C$) and $\psi'$ reduces to $\psi$ in a single cut-elimination step.
-
-	\item
-$\seq AB$ ; $\seq{\dual B}{\exists x.C}$\quad (Figure~\ref{fig:crit3})
-\\
-Observe that since $x$ occurs in $C$ but not $B$, it is not in the domain of $\tau_B$, so that $\tau_B\minus x$ is just $\tau_B$.
-Then $\rho'=\rho\minus x$, and the diagram is closed by a sequentialization step (from left to right) that extends $\psi$ with an existential introduction rule, to a proof equivalent to $\psi'$:
-\[
-	\infer[\!\!\scriptstyle{\qrr?{\rho(x)}}]{\Seq{A\rho'}{\exists x.C\rho'}}{
-	 \Prf\psi{A\rho}{C\rho}
-	}
-\]
-\end{itemize}
-There are three further critical pairs, for a proof net on $\seq AB$ composed with one on $\seq {\dual B}{C_1{\+}C_2}$, one on $\seq {\dual B}{C_1{\*}C_2}$, and one on $\seq {\dual B}{\forall x.C}$.
-These converge as the one above.
-
-Resolving these critical pairs gives the soundness of the composition operation, per the following theorem. We abbreviate a cut on proofs $\prf\pi AB$ and $\prf\phi{\dual B}C$ by $\pi\comp\phi$.
-
-% ..................................................
-
-\begin{theorem}
-\label{thm:composition}
-If proof nets $\net{\lambda_\Sigma}AB$ and $\net{\kappa_\Theta}{\dual B}C$ sequentialize to $\pi$ and $\phi$ respectively, then their composition $(\net{\lambda_\Sigma}AB)\comp(\net{\kappa_\Theta}{\dual B}C)$ is well-defined (i.e.\ all fixed points are finite) and sequentializes to a normal form $\psi$ of $\pi\comp\phi$.
-\end{theorem}
-
-%\begin{proof}
-%See the appendix.
-%\end{proof}
-
 % --------------------------------------------------
@@
 	\vc{
-	 \infer[\Qrr?u]{\seq{A\*B}C}{
-	  \infer[\Qrr*]{\seq{A\*B}{\exists x.C}}{
+	 \infer[\Qrr?u]{\seq{A\*B}{\exists x.C}}{
+	  \infer[\Qrr*]{\seq{A\*B}C}{
 	   \seq AC
@@
 
-%\[
-%\begin{tabular}{@{}p{.08\textwidth}@{}p{.92\textwidth}@{}}
-%	$\sigma\gen\tau$
-%&
-%	A witness map $\sigma$ is \defn{more general} than $\tau$,  
-%	$\sigma\gen\tau$, if there is a map $\rho$ such that 
-%	$\sigma\rho=\tau$.
-%\\%[4pt]	
-%	$\sigma\coh\tau$
-%&
-%	Two witness maps $\sigma$ and $\tau$ are \defn{coherent}, $\sigma\coh\tau$,
-%	if there is a map $\rho$ such that $\sigma\rho=\tau\rho$.
-%\\%[4pt]
-%	$\sigma\join\tau$
-%&
-%	The \defn{join} $\sigma\join\tau$ of two coherent witness maps is the least map $\rho$ such that $\sigma\gen\rho$ and $\tau\gen\rho$.
-%\end{tabular}%
-%\]
-
-%
 A link $\link[]ab$ on two atomic formulas is an \defn{axiom} link if there exists a witness map $\sigma$ such that $\dual a\sigma=b\sigma$.
@@
 An initial witness pre-net has \emph{exact coverage}, while coalescence will give \emph{local eigenvariables}.
-Note that eigenvariables are constants for the purpose of unification (they are not substituted into), and substitution maps of different links use different variables.
+Note that eigenvariables are constants for the purpose of unification (they are not substituted into).
+For Barendregt's convention, that free variables have distinct names from bound ones, we should assume that variables in the domain of a witness map are fresh; for example, the most general unifier of existential variables $x$ and $y$ should be $[z/x,z/y]$ for a fresh variable~$z$, and not $[y/x]$ or $[x/y]$.
 
@@
 \end{lemma}
-
-%\begin{proof}
-%The sequentialization path
-%$
-%	\net{\lambda_\Sigma^\star}AB = 
-%	L_1 \ucoal L_2 \ucoal \dots \ucoal L_n = 
-%	\net{\link[\varnothing]AB^\pi}AB
-%$
-%has a corresponding path
-%$
-%	\net{\lambda_\star^\star}AB = 
-%	R_1 \ucoal R_2 \ucoal \dots \ucoal R_n =
-%	\net{\link[\varnothing]AB^{\pi'}}AB
-%$
-%where the same links (but with potentially different witness maps) are coalesced.
-It follows by induction on this path (where the base case is $L_1$ and $R_1$) that for every corresponding pair of links $\link CD^\phi$ in $L_i$ and $\link[\tau]CD^\psi$ in $R_i$ we have $\tau\leq\sigma$ and $\psi\leq\phi$.
-%\end{proof}
 % ..................................................
@@
 \end{lemma}
-
-%\begin{proof}
-%By induction on the sequentialization path $\net{\lambda_\star}AB\ucoal^*\net{\link[\varnothing]AB^\pi}AB$.
-For the end result, the statement holds with $\rho=\varnothing$.
-For the inductive step, consider a step $L\ucoal R$.
-We show the case ($\urr*$); the other cases are immediate.
-%%
-%\begin{itemize}
-%	\item
-%$\link C{D_1},\link[\tau]C{D_2}\ucoal\link[\sigma\join\tau]C{D_1{\*}D_2}$
-%\\
-%By the inductive hypothesis, $R\rho'$ strict-sequentializes to $\pi$. Let $\sigma\join\tau=\sigma\rho''=\tau\rho''$ and let $\rho=\rho''\rho'$. Then $L\rho$ strict-sequentializes to $\pi$ by 
-%\[
-%	\link[\sigma\rho]C{D_1},\link[\tau\rho]C{D_2}\scoal\link[(\sigma\join\tau)\rho']C{D_1{\*}D_2}~.
-%\qedhere
-%\]
-%\end{itemize}
-%\end{proof}
 % ..................................................
@@
 \end{theorem}
-
-%\begin{proof}
-%By Theorem~\ref{thm:proof->net->proof}, $\net{\lambda_\Sigma}AB$ sequentializes to $\pi$ in $(\scoal)$, and hence also in $(\ucoal)$.
-Then by Lemma~\ref{lem:ucoal generality} $\net{\lambda_\star}AB$ sequentializes to $\pi'\leq\pi$.
-%\end{proof}
 % ..................................................
@@
 \end{theorem}
-
-%\begin{proof}
-%By Lemma~\ref{lem:unifying implies strict coalescence}, since $\net\lambda AB$ sequentializes to $\pi$ there is a net $\net{\lambda_\Sigma} AB$ that sequentializes to $\pi$.
-By Theorem~\ref{thm:net->proof->net}, $[\pi]=\net{\lambda_\Sigma} AB$.
-%\end{proof}
 % ..................................................
@@
 \end{theorem}
-
-%\begin{proof}
-%By Lemma~\ref{lem:unifying implies strict coalescence} there are witness labellings $\Sigma$ and $\Theta$ such that $\net{\lambda_\Sigma}AB$ strict-sequentializes to $\pi$ and $\net{\kappa_\Theta}{\dual B}C$ to $\phi$.
-By Theorem~\ref{thm:composition} their composition $(\net{\lambda_\Sigma\comp\kappa_\Theta)}AC$ strict-sequentializes to a normal form $\psi$ of $\pi\comp\phi$.
-By Lemma~\ref{lem:ucoal generality} the net $\net{(\lambda\comp\kappa)_\star}AC$ unifying-sequentializes to $\psi'\leq\psi$.
-%\end{proof}
-
-% --------------------------------------------------
-
+% ..................................................
+
+% ..................................................
 \begin{figure}[!t]
@@
 \emph{Expansion tree proofs} \cite{Miller-1987,Heijltjes-2010} are a graphical proof formalism based on this idea.
-%
 In our slicing condition, the interpretation of $\exists x.A$ is an infinite sum of which only a finite part $A[t_1/x]\+\dots\+A[t_n/x]$ is relevant, over the witnesses $t_1,\dots,t_n$ actually assigned to $x$ in the proof net.
@@
 
-%\paragraph*{Generality}
-%
-%The idea of using \emph{generality} as a basis for proof identity originates with Lambek \cite{Lambek-1968-1972}, 
-%\cite{Lambek-1968,Lambek-1969,Lambek-1972}, 
-%who observed that the two canonical proofs of $\seq{A{\+}A}{\dual A}$ can be distinguished by casting each as a specialization (by substituting into propositional variables) of the more general proofs of $\seq{\,a{\+}b}{\dual a}$ and $\seq{\,a{\+}b}{\dual b}$.
-%
 Lambek observed that the two canonical proofs of $\seq{A{\+}A}{\dual A}$ can be distinguished by casting each as a specialization (by substituting into propositional variables) of the more general proofs of $\seq{\,a{\+}b}{\dual a}$ and $\seq{\,a{\+}b}{\dual b}$ (corresponding to the two injections of a sum).
@@
 
+For future work, there are a few natural questions.
+First is that of a geometric criterion for unification nets.
+For this, it seems essential to reconstruct dependencies between products and exitential quantifiers globally, as the \emph{expansion} condition provides for witness nets.
+These interact in highly intricate ways, which the unifying coalescence algorithm resolves incrementally and locally.
+To do so globally, as would be necessary for a geometric criterion, is a major combinatorial challenge.
+
+A second is whether coalescence (or \emph{contractibility} \cite{Danos-1990}) applies to MLL1 unification nets \cite{Hughes-2018}.
+We believe it would, straightforwardly (without requiring a dependency or leap edges).
+
+A final question is whether the current approach can be extended to obtain proof nets for MALL1.
+We see two ways forward that could succeed: (i) combine witness nets with MALL slice nets \cite{Hughes-vanGlabbeek-2005} using a slicing criterion; (ii) combine witness nets or unification nets with MALL conflict nets \cite{Hughes-Heijltjes-2016} using a coalescence criterion.
+For both, there are still significant combinatorial challenges, for example because coalescence for MALL is not a straightforward extension of that for ALL.
+Other approaches are much less certain: MALL conflict nets do not yet have a slicing criterion (though this looks feasible), and MALL slice nets do not support coalescence (this looks fundamentally problematic).
+
 % --------------------------------------------------
 
-%\subsection*{Acknowledgements}
-%
-%We would like to thank the anonymous referees for their constructive feedback.
+\section*{Acknowledgements}
+
+We would like to thank the anonymous referees for their constructive feedback.
 Dominic would like to thank his host, Wes Holliday, at the UC Berkeley Logic Group.
-The first author was supported by EPSRC Project EP/R029121/1.
+Willem was supported by EPSRC Project EP/R029121/1 \emph{Typed Lambda-Calculi with Sharing and Unsharing}.
 
@@
 % ==================================================
-
-%\end{document}
 
@@
 
-\theoremstyle{theorem}
+\theoremstyle{plain}
 \newtheorem{retheorem}{Theorem}
@@
 \begin{proof}
-From left to right is by inspection of the critical pairs of sequentialization ($\scoal$).
-From right to left is by inspection of the rule permutations in Figure~\ref{fig:permutations} in Appendix~\ref{sec:permutations}.
+From left to right is by inspection of the critical pairs of sequentialization ($\scoal$). From right to left is by inspection of the rule permutations in Figure~\ref{fig:permutations}.
 \end{proof}
@@
 Letting $\tau[t/x]=\sigma$, then $S\cap \lambda_\Sigma$ is the singleton $\{\link CD\}$ if and only if $S\cap\kappa_\Theta$ is $\{\link[\sigma\minus x]C{\exists x.D}\}$.
-%
-%The witnesses sets $\Sigma(x)$ and $\Theta(x)$ for $L$ and $R$ need not be the same, since $L$ has $\sigma$ where $R$ has $\sigma\minus x$.
-Let $\Sigma(x)=\{t,t_1,\dots,t_n\}$ and $\Theta(x)=\{t_1,\dots,t_n\}$, where $\sigma(x)=t$.
-For every slice $S_B$ of $B$ over $\Sigma$ there is a corresponding slice $S'_B$ over $\Theta$, both (or neither) containing $(\exists x.D,\tau)$ and $(D,\tau[t_i/x])$ for $i\leq n$, but the former in addition having $(D,\tau[t/x])$.
-Then $S\cap \lambda_\Sigma$ is the singleton $\{\link CD\}$ if and only if $S\cap\kappa_\Theta$ is $\{\link[\sigma\minus x]C{\exists x.D}\}$, where it should be observed that if $t$ is also a witness to $x$ in some other slice of $R$, then $t\in\Theta(x)$ and in fact $S=S'$.
 
@@
 
-% --------------------------------------------------
-\newpage
-\section{Permutations}\label{sec:permutations}
-
-In this section we give the rule permutations of {\all1} sequent calculus.
-
-% ..................................................
-
-\begin{figure}[!ht]
-\[
-\renewcommand\+{{+}}
-\renewcommand\*{{\times}}
-\scalebox{0.85}{$
-\begin{array}{@{}c@{\qquad}c@{\qquad}c@{\qquad}c@{}}
-	\permAB   & \permAE   & \permAP   & \permAX 
-\\	\downperm & \downperm & \downperm & \downperm \\
-	\permBA   & \permEA   & \permPA   & \permXA
-\\ \\[20pt]
- 			  & \permEF   & \permEP   & \permEX
-\\			  & \downperm & \downperm & \downperm \\
- 			  & \permFE   & \permPE   & \permXE
-\\ \\[20pt]
- 			  &			  & \permPQ   & \permPX
-\\			  &			  & \downperm & \downperm \\
- 			  &			  & \permQP   & \permXP
-\\ \\[20pt]
- 			  &			  &			  & \permXY
-\\			  &			  &			  & \downperm \\
- 			  &			  &			  & \permYX
-\end{array}$}
-\]
-\caption{Cut-free rule permutations}
-\label{fig:permutations}
-\end{figure}
-
-% ..................................................
-
-\begin{figure}[!ht]
-\[
-\renewcommand\+{{+}}
-\renewcommand\*{{\times}}
-\scalebox{0.85}{$
-\begin{array}{c@{\qquad}c}
-	\permAC   & \permEC   
-\\	\downperm & \downperm \\
-	\permCA   & \permCE
-\\ \\[20pt]
-	\permPC   & \permXC 
-\\	\downperm & \downperm \\
-	\permCP   & \permCX
-\end{array}
-\begin{array}{c}
-	\permCD \\ \downperm \\ \permDC
-\end{array}
-$}
-\]
-\caption{Cut-permutations}
-\label{fig:cut-permutations}
-\end{figure}
-
 \end{document}

### 2019-04-22 7 - FSCD 2019 - Final/ALL1.tex
tweaks upon proof reading

@@
 For example, to prove the sequent $\seq{\exists x.P(x)}{\exists y.\dual P(y)}$ both quantifiers must receive \emph{the same} witness, as in the following two proofs, but \emph{any} witness will do.
-\[
+\begin{center}\(
 	\vc{\infer={\seq{\exists x.P(x)}{\exists y.\dual P(y)}}{\infer{\seq{P(s)}{\dual P(s)}}{}}}
@@
 	\vc{\infer={\seq{\exists x.P(x)}{\exists y.\dual P(y)}}{\infer{\seq{P(t)}{\dual P(t)}}{}}}
-\]
+\)\end{center}
 The issue is more pronounced where quantifiers are \emph{vacuous}, $\exists x.A$ with $x$ not free in $A$.
@@
 Below right is an interesting intermediate variant: the witness $s$ or $t$ can be observed without explicit annotation in the $\exists\mathrm R$ rule, but the choice is equally immaterial to the content of the proof as when the quantifier were vacuous.
-\[
+\begin{center}\(
 	\vc{\infer[\!\!\scriptstyle{\qrr?s}]{\seq{\exists x.P}{\dual P}}{\infer{\seq P{\dual P}}{}}}
@@
 	}}
-\]
+\)\end{center}
 In this paper we will not attempt to settle the question of proof identity.
@@
 We will distinguish \defn{strict coalescence} ($\scoal$) for witness nets and \defn{unifying coalescence} ($\ucoal$) for unification nets.
-We first give an example of the former (writing $Pxy$ for $P(x,y)$ to conserve space).
+We first give an example of the former (abbreviating $P(x,y)$ to $Pxy$).
+%(writing $Pxy$ for $P(x,y)$ to conserve space). 
 In the initial witness net, below left, each link corresponds to a sequent calculus axiom between both linked subformulas, with the substitutions applied.
@@
 Negation $(\dual{\,\cdot\,})$ is applied to predicate symbols, $\dual P$ as a matter of convenience.
-The \defn{dual} $\dual A$ of an arbitrary formula $A$ is given by DeMorgan.
+The \defn{dual} $\dual A$ of an arbitrary formula $A$ is given by De Morgan.
 We use the following notational conventions.
@@
 Since we will be working with a graphical representation, we will adopt \defn{Barendregt's convention}, that bound variable names are globally unique identifiers, in the following form.
-In a sequent $\seq AB$ we assume all quantifiers to have a unique binding variable, distinct from any free variable.
+In a sequent $\seq AB$ we assume all quantifiers have a unique binding variable, distinct from any free variable.
 In a proof $\pi$ over $\seq AB$, a variable $x$ that is universally quantified as $\forall x.C$ in $\seq AB$ is an \defn{eigenvariable}.
@@
 Accordingly, we assume that $x$ does not occur free outside these subproofs (which can be guaranteed by globally renaming $x$).
-We take variable names to be persistent throughout a proof, in the sense that we don't admit alpha-conversion between proof rules.
+We take variable names to be persistent throughout a proof, in the sense that we don't admit alpha-conversion (renaming of bound variables) between proof rules.
 We thus have unique bound variable names in $\seq AB$, but in $\pi$ all $\qrr!$ rules on the subformula $\forall x.C$ share the same eigenvariable $x$.
@@
 A \defn{link} $(C,D)$ on a sequent $\seq AB$ is a pair of subformulas $C\leq A$ and $D\leq B$. 
-A \defn{linking} $\lambda$ on the sequent $\seq AB$ is a set of links on it.
+A \defn{linking} $\lambda$ on the sequent $\seq AB$ is a set of links on $\seq AB$.
 
@@
 
-A \defn{witness linking} $\lambda_\Sigma$ is a linking $\lambda$ with a \defn{witness labelling} $\Sigma\colon\lambda\to\var\rightharpoonup\terms$ that assigns each link $(C,D)$ a witness map.
+A \defn{witness linking} $\lambda_\Sigma$ is a linking $\lambda$ with a \defn{witness label\hspace{-.1pt}ling} $\Sigma\colon\lambda\to\var\rightharpoonup\terms$ that assigns each link $(C,D)$ a witness map.
 We may use and define $\lambda_\Sigma$ as a set of \defn{witness links} $\link CD$ where $(C,D)\in\lambda$ and $\Sigma(C,D)=\sigma$.
 A witness link $\link ab$ on atomic formulas is an \defn{axiom link} if $\dual a\sigma=b\sigma$.
-An \defn{axiom} witness linking is one consisting of axiom links.
+An \defn{axiom} witness linking is one comprising axiom links.
 
@@
 For sequentialization, the links in a pre-net will be labelled with a sequent proof.
-An axiom link will carry an axiom, and each coalescence step introduces one proof rule.
+An axiom link will carry an axiom, and each coalescence step will introduce one proof rule.
 Formalizing this, a \defn{proof linking} $\lambda_\Sigma^\Pi$ is a witness linking $\lambda_\Sigma$ with a \defn{proof labelling} $\Pi\colon \lambda\to\proofs$ assigning a sequent proof to each link.
@@
 %
-Then to recap, we have accumulated the following further notational conventions.
+So far we have accumulated the following notational conventions:
 %
@@
 %
-\defn{Strict sequentialization} ($\scoal$) is the rewrite relation on labelled pre-nets generated by the following rules, that replace one or two links by another in a pre-net $\net{\lambda_\Sigma^\Pi}AB$ where $B$ has a subformula $D_1\+D_2$, $D_1\*D_2$, $\exists x.D$, and $\forall x.D$ respectively.
+\defn{Strict sequentialization} ($\scoal$) is the rewrite relation on labelled pre-nets generated by the following rules, which replace one or two links by another in a pre-net $\net{\lambda_\Sigma^\Pi}AB$ where $B$ has a subformula $D_1\+D_2$, $D_1\*D_2$, $\exists x.D$, and $\forall x.D$ respectively.
 Symmetric cases are omitted.
@@
 \begin{definition}
-An \all1 \defn{witness proof net} or \defn{witness net} is a witness pre-net $\net{\lambda_\Sigma}AB$ with $\lambda_\Sigma$ an axiom linking, that strict-coalesces.
+An \all{\textnormal 1} \defn{witness proof net} or \defn{witness net} is a witness pre-net $\net{\lambda_\Sigma}AB$ with $\lambda_\Sigma$ an axiom linking, that strict-coalesces.
 It \defn{sequentializes} to a proof $\pi$ if its initial labelling $\net{\lambda_\Sigma^\star}AB$ reduces in $(\scoal)$ to $\net{\{\link[\varnothing]AB^\pi\}}AB$.
@@
 \label{thm:proof->net->proof}
-For any \all1 proof $\pi$, the witness net $[\pi]$ sequentializes to $\pi$. 
+For any \all{\textnormal 1} proof $\pi$, the witness net $[\pi]$ sequentializes to $\pi$. 
 \end{theorem}
@@
 
-We will first identify two aspects of sequent proofs, arising from the local nature of the rules, that need to be enforced explicitly in a geometric correctness condition.
+We will first identify two aspects of sequent proofs, arising from the local nature of the rules, which need to be enforced explicitly in a geometric correctness condition.
 
 \begin{description}
-	\item[Local eigenvariables]
+	\item[Local eigenvariables.]
 The side-condition on the $\forall R$-rule, that the eigenvariable is not free in the context, means that eigenvariables are \emph{local} to the subproof of the $\forall R$-rule.
@@
 
-	\item[Exact coverage]
+	\item[Exact coverage.]
 The local witness substitution $[t/x]$ in a rule instance $\qrr?t$ will have been applied exactly to the axioms $\seq a{\dual a}$ in the subproof of that rule.
@@
 \begin{description}
-	\item[Expansion]
+	\item[Expansion.]
 When defining slices, we interpret an existential quantification $\exists x.A$ as a sum over all witnesses $t_i$ to $x$ that occur in the pre-net, $A[t_1/x]\+\dots\+A[t_n/x]$.
@@
 
-	\item[Dependency]
+	\item[Dependency.]
 We define a \defn{dependency} relation between a universal quantification $\forall x.A$ and an instantiation $B[t/y]$ of $\exists y.B$ where the eigenvariable $x$ occurs free in $t$ (a standard approach to first-order quantification \cite{Miller-1987,Girard-1996,Heijltjes-2010,Mimram-2011}).
@@
 \indent
-Cut-elimination rules for \all1 are given in Figure~\ref{fig:cut-elim}; the needed permutations are in Figure~\ref{fig:cut-permutations}.
+Cut-elimination rules for \all1 are given in Figure~\ref{fig:cut-elim}; the requisite permutations are in Figure~\ref{fig:cut-permutations}.
 }
@@
 Observe that since $x$ occurs in $C$ but not $B$, it is not in the domain of $\tau_B$, so that $\tau_B\minus x$ is just $\tau_B$.
-Then $\rho'=\rho\minus x$, and the diagram is closed by a sequentialization step (from left to right) that extends $\psi$ with an existential introduction rule, to a proof equivalent to $\psi'$:
+Then $\rho'=\rho\minus x$, and the diagram is closed by a sequentialization step (from left to right) which extends $\psi$ with an existential introduction rule, to a proof equivalent to $\psi'$:
 }\hfill
@@
 There are three further critical pairs, for a proof net on $\seq AB$ composed with one on $\seq {\dual B}{C_1{\+}C_2}$, one on $\seq {\dual B}{C_1{\*}C_2}$, and one on $\seq {\dual B}{\forall x.C}$.
-These converge as the one above.
+These converge like the one above.
 %
@@
 \begin{definition}
-An \all1 \defn{unification proof net} or \defn{unification net} is a pre-net $\net\lambda AB$ with axiom linking $\lambda$ such that the initial witness pre-net $\net{\lambda_\star}AB$ unifying-coalesces.
+An \all{\textnormal 1} \defn{unification proof net} or \defn{unification net} is a pre-net $\net\lambda AB$ with axiom linking $\lambda$ such that the initial witness pre-net $\net{\lambda_\star}AB$ unifying-coalesces.
 It \defn{sequentializes} to $\pi$ if $\net{\lambda^\star_\star}AB$ reduces in $(\ucoal)$ to $\net{\{\link[\varnothing]AB^\pi\}}AB$.
@@
 In the above definition, note that $\lambda_\star^\star=(\lambda_\star)^\star$ is the initial proof labelling of $\lambda_\star$, which assigns an axiom rule to each axiom link.
-For a minimal example, see the introduction.
+For a minimal example, see the Introduction.
 Observe also that unifying coalescence includes strict coalescence, $(\scoal)\subseteq(\ucoal)$.
@@
 
-We have presented two notions of first-order additive proof net, \emph{witness nets} and \emph{unification nets}, to canonically capture two natural notions of proof identity for first-order additive linear logic.
+We have presented two notions of first-order additive proof net, \emph{witness nets} and \emph{unification nets}, to capture canonically two natural notions of proof identity for first-order additive linear logic.
 Figure~\ref{fig:results} summarizes our results, along with some observations we make below.
@@
 First is that of a geometric criterion for unification nets.
-For this, it seems essential to reconstruct dependencies between products and exitential quantifiers globally, as the \emph{expansion} condition provides for witness nets.
+For this, it seems essential to reconstruct dependencies between products and existential quantifiers globally, as the \emph{expansion} condition provides for witness nets.
 These interact in highly intricate ways, which the unifying coalescence algorithm resolves incrementally and locally.
@@
 For both, there are still significant combinatorial challenges, for example because coalescence for MALL is not a straightforward extension of that for ALL.
-Other approaches are much less certain: MALL conflict nets do not yet have a slicing criterion (though this looks feasible), and MALL slice nets do not support coalescence (this looks fundamentally problematic).
+Other approaches are much less certain: MALL conflict nets do not yet have a slicing criterion (though this looks feasible), and MALL slice nets do not support coalescence (which seems fundamentally problematic).
 

### 2019-04-22 7 - FSCD 2019 - Final/ALL1.tex
tweaks

@@
 Unlike for proof nets, this notion is not so natural for sequent proofs: in the permutation of existential and product rules below, from left to right $u$ must be generated as the least term more general than $s$ and $t$; from right to left, $s$ and $t$ cannot be reconstructed from $u$, and must be retrieved from their respective subproofs.
-\[
+\begin{center}\(
 	\vc{
@@
 	}}}
-\]
+\)\end{center}
 
@@
 For an axiom linking $\lambda$ over $\seq AB$ the \defn{initial witness pre-net} $\net{\lambda_\star}AB$ is given by
-\[
+\begin{center}\(
 	\lambda_\star = \{~\link ab~\mid~\link[]ab\in\lambda~,~\sigma=\init{\dual a}b~\}~.
-\]
+\)\end{center}
 An initial witness pre-net has \emph{exact coverage}, while coalescence will give \emph{local eigenvariables}.
@@
 it follows that in every pre-net $\net{\kappa_\Theta^\Phi}AB$ on this path, $\lambda_\Sigma$ is equal to the union over the de-sequentialization of all proof labels $\phi$ in $\Phi$:
-\[
+\begin{center}\(
 	\lambda_\Sigma=\bigcup~\{\,\deseq\phi CD \mid \link CD^\phi \in \kappa_\Theta^\Phi\,\}~.
-\]
+\)\end{center}
 The statement is then the case $\kappa_\Theta^\Phi=\{\link[\varnothing]AB^\pi\}$.

### 2019-04-22 7 - FSCD 2019 - Final/ALL1.tex
changed acknowledgements

--- 2019-04-16 7 - FSCD 2019 - Final/ALL1.tex
@@
 We would like to thank the anonymous referees for their constructive feedback.
-Dominic would like to thank his host, Wes Holliday, at the UC Berkeley Logic Group.
-Willem was supported by EPSRC Project EP/R029121/1 \emph{Typed Lambda-Calculi with Sharing and Unsharing}.
+Dominic Hughes would like to thank his host, Wes Holliday, at the UC Berkeley Logic Group.
+Willem Heijltjes was supported by EPSRC Project EP/R029121/1 \emph{Typed Lambda-Calculi with Sharing and Unsharing}, and Lutz Stra{\ss}burger was supported by the ANR-FWF international
+grant ANR-5-CE25-0014 \emph{The Fine Structure of Formal Proof
+Systems and their Computational Interpretations (FISP)}.
 

### 2019-04-22 7 - FSCD 2019 - Final/ALL1.tex
one exists missing
one all1 in the appendix

@@
 
-%We investigate the \emph{proof-net problem}, finding a canonical representation of proofs, for additive linear logic (\all) extended with first-order quantification (\all1).
+%We investigate the \emph{proof-net problem}, finding a canonical representation of proofs, for additive linear logic (\all) extended with first-order quantification (\all{\textnormal 1}).
 \all\ is the fragment of linear logic \cite{Girard-1987} that describes sums and products, and their canonical morphisms: projections, injections, and diagonals.
@@
 
-Here, we extend proof nets to first-order additive linear logic (\all1).
+Here, we extend proof nets to first-order additive linear logic (\all{\textnormal 1}).
 Beyond the solution to the proof-net problem, a main contribution is the (further) development of the two techniques we consider: \emph{explicit substitutions} for witness assignment, and reconstruction of witness information through \emph{unification}, as pioneered for MLL by the second author \cite{Hughes-2018}.
@@
 The example below left shows the proof net for the sequent proof earlier.
-(We will assume a different variable for each quantifier, and we attach links to predicate letters, as the root connective of an atomic proposition.) Witness nets are canonical for \all1 sequent calculus permutations.
+(We will assume a different variable for each quantifier, and we attach links to predicate letters, as the root connective of an atomic proposition.) Witness nets are canonical for \all{\textnormal 1} sequent calculus permutations.
 Composition is direct, where the witness assignments of links are composed through a simple process of \emph{interaction\,+\,hiding} similar to that of game semantics \cite{Mimram-2011}.
@@
 	\vc{
-	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq{A\rho'}{C\rho'}}{
+	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq{A\rho'}{\exists x.C\rho'}}{
 	 \left(\vc{
@@
 \begin{retheorem}
-For any \all1 proof $\pi$, the witness net $[\pi]$ sequentializes to $\pi$. 
+For any \all{\textnormal 1} proof $\pi$, the witness net $[\pi]$ sequentializes to $\pi$. 
 \end{retheorem}

### 2019-04-22 7 - FSCD 2019 - Final/ALL1.tex

@@
 \begin{proof}
-By Corollary~\ref{cor:strong coalescence} the proof nets $L=\net{\lambda_\Sigma}AB$ and $R=\net{\kappa_\Theta}{\dual B}C$ strongly coalesce.
+By Theorem~\ref{cor:strong coalescence} the proof nets $L=\net{\lambda_\Sigma}AB$ and $R=\net{\kappa_\Theta}{\dual B}C$ strongly coalesce.
 We may then interleave their coalescence sequences as follows: if a synchronized step in $L$ and $R$ on the interface $B$ and $\dual B$ is available, apply it; otherwise perform steps in $L$ on $A$ and in $R$ on $C$ until it is.

### 2019-04-23 7 - FSCD 2019 - Final/ALL1.tex
final edit
tweaked spacing to make \relatedversion work --- now everything up to last reference is within the first 17 pages; submitted to server

@@
 \author
- {Dominic J.D.\ Hughes}
+ {Dominic J.\ D.\ Hughes}
  {Logic Group, UC Berkeley, USA}
@@
 
-%\subjclass{F.4.1: Mathematical logic--Proof theory}
-% Theory of computation - Logic - Proof theory
-% Theory of computation - Logic - Linear logic
 \ccsdesc[500]{Theory of computation~Proof theory}
@@
 
-%\relatedversion{http://hal.inria.fr/hal-01867625/}
+\relatedversion{A full version \cite{Heijltjes-Hughes-Strassburger-2018} is available at \url{http://hal.inria.fr/hal-01867625/}}
 
@@
 
-%We investigate the \emph{proof-net problem}, finding a canonical representation of proofs, for additive linear logic (\all) extended with first-order quantification (\all{\textnormal 1}).
-\all\ is the fragment of linear logic \cite{Girard-1987} that describes sums and products, and their canonical morphisms: projections, injections, and diagonals.
-It is rich, well-behaved, and compact: an ideal microcosm in which to explore semantic and proof-theoretic ideas.
-Here, we explore two techniques to account for the witness information that is essential to first-order proof: \emph{explicit substitution} and first-order \emph{unification}.
-
 Additive linear logic (\all) is the logic of sum, product, and their canonical morphisms: projections, injections, and diagonals.
@@
 Proofs have been relegated to the appendix---for a full version see the report \cite{Heijltjes-Hughes-Strassburger-2018}.
-
-%Additive linear logic $(\all)$ is the logic of product $(\*)$, sum $(\+)$, and their canonical morphisms: projections, injections, and diagonals.
-It is naturally captured in \defn{proof nets} \cite{Girard-1987,Hughes-vanGlabbeek-2005}, which describe a morphism $A\to B$ by a sequent $\seq{\dual A}B$ plus a \defn{linking}, a relation between the propositional atoms of $\dual A$ and those of $B$.
-Four examples are illustrated below left.
-%
-%Additive proof nets are \defn{canonical}: they factor out the permutations of sequent calculus, and correspond 1--1 to morphisms of the free category.
-\defn{Composition}, of proof nets over $\seq{\dual A}B$ and $\seq{\dual B}C$ to one over $\seq{\dual A}C$, is by the relational composition of their linkings along the dual formulas $B$ and $\dual B$ (as illustrated below right), and captures sequent-calculus cut-elimination.
-%
-%\[
-%\hspace*{9ex}% spacing hack to achieve central horizontal alignment
-% Behold my better spacing hack to achieve central horizontal alignment :)
-%\hspace*{-\parindent}%
-%\hspace*{\fill}%
-%\begin{array}{c@{\qquad\qquad}c}
-%	\begin{tikzpicture}[net]
-%		\formula[y=1]{{\dual a}}
-%		\formula[y=0]{a\*a}
-%		\Vlink[red]{[-2]1,1}
-%		\Vlink[red]{[2]1,3}
-%	\end{tikzpicture}
-%&
-%	\begin{tikzpicture}[net]
-%		\formula[y=1]{{\dual a}}
-%		\formula[y=0]{a\+b}
-%		\Vlink[red]{1,1}
-%	\end{tikzpicture}
-%\\
-%	\text{\small diagonal}
-%&	\text{\small injection}	
-%\\ \\ \\[-10pt]
-%	\begin{tikzpicture}[net]
-%		\formula[y=1]{{\dual a}\+{\dual b}}
-%		\formula[y=0]{b\*a}
-%		\Vlink[red]{1,3}
-%		\Vlink[red]{3,1}
-%	\end{tikzpicture}
-%&
-%	\begin{tikzpicture}[net]
-%		\formula[y=1]{*{\phantom(}{\dual a}*{\phantom)}
-%		 {{\+}}*({\dual b}*{\phantom)}
-%		 {{\+}}*{\phantom(}{\dual c}*)}
-%		\formula[y=0]{*(a*{\phantom)}
-%		{{\*}}*{\phantom(}b*)
-%		{{\*}}*{\phantom(}c*{\phantom)}}
-%		\Vlink[red]{1,1}
-%		\Vlink[red]{3,3}
-%		\Vlink[red]{5,5}
-%	\end{tikzpicture}
-%\\
-%	\text{\small symmetry}
-%&	\text{\small associativity}
-%\end{array}
-%\qquad\qquad\qquad
-%\begin{array}{c}
-%    \vc{\begin{tikzpicture}[net]
-%        \formula[y=2.5]{{\dual b}*\+{\dual a}}
-%        \formula[y=1.5]{a*\**(b*\+b*)}
-%            \Vlink[red]{1,2}
-%            \Vlink[red]{2,1}
-%        \formula[y=1]{{\dual a}*\+*({\dual b}*\*{\dual b}*)}
-%        \formula[y=0]{b*\*b}
-%            \Vlink[blue]{[-1]2,[-1]1}
-%            \Vlink[blue]{[1]2,[-1]2}
-%            \Vlink[blue]{[-1]3,[1]1}
-%            \Vlink[blue]{[1]3,[1]2}
-%    \end{tikzpicture}}
-%\quad\Rightarrow\quad
-%    \vc{\begin{tikzpicture}[net]
-%        \formula[y=2.5]{{\dual b}*\+{\dual a}}
-%        \formula[y=0]{b*\*b}
-%            \Vlink[violet]{[-1]1,1}
-%            \Vlink[violet]{[1]1,2}
-%    \end{tikzpicture}}
-%\\ \\[-5pt]
-%	\text{\small composition}
-%\end{array}
-%\hfill
-%\]
 
@@
 %
-\[
-\hspace*{-\parindent}%
-\hspace*{\fill}%
+\begin{center}\vspace{-.5ex}\(
 \begin{array}{@{}rc@{\qquad}rc@{}}
@@
     \end{tikzpicture}}
-\hfill
-% Tightening the text and spacing the 
 \rule[-55pt]{0pt}{110pt}
-\]
+\)\vspace{-.5ex}\end{center}
 %
@@
 %
-\[
-\hspace*{\fill}
-\hspace*{-\parindent}
+\begin{center}\(
+%\hspace*{\fill}
+%\hspace*{-\parindent}
 	\vc{\infer[\Qrr?t]{\seq A{\exists x.B}}{\seq A{B[t/x]}}}
-\hfill
+\hspace{10ex}
 \vc{
@@
    }}
-\hfill
-\]
+%\hfill
+\)\end{center}
 %
@@
 We compare further properties in Figure~\ref{fig:results} in the conclusion, where we also discuss related work and Lambek's notion of \defn{generality} \cite{Lambek-1968-1972}.
-%\cite{Lambek-1968, Lambek-1969, Lambek-1972}.
-%
-\[
-\hspace*{\fill}
-\hspace*{-\parindent}
+%
+\begin{center}\(
 	\text{\small a witness net:}
@@
 	\end{tikzpicture}}
-\hfill
+\hspace{11ex}
 	\text{\small a unification net:}
@@
 	\end{tikzpicture}}
-\hfill
-\]
+\)\vspace{-1ex}\end{center}
 %
@@
 
-%At the same time, the ubiquity of its main operations, product and sum, mean the ideas and results it garners are widely applicable.
-It serves as a microcosmos for important ideas and observations: it fostered the \emph{connections method} of proof search \cite{Galmiche-2000}; it demonstrated the \emph{Blass problem} \cite{Abramsky-2003} of game semantics, that sequential strategies do not in general have associative composition; and it is at the root of the study of fixed points in linear logic \cite{Santocanale-2002a}.
-The logic describes two-way communication~\cite{Cockett-Santocanale-2009}, and is a core part of \emph{session types}~\cite{Honda-1993}.
-
 {\all} is of course part of {\mall} (multiplicative-additive linear logic), and its lessons are clearly visible in the second author's canonical {\mall} proof nets~\cite{Hughes-vanGlabbeek-2005}, as well as the first and second author's locally canonical \emph{conflict nets}~\cite{Hughes-Heijltjes-2016}.
 Its proof nets also appear in the third author's study of the \emph{medial rule} for classical logic~\cite{str:RTA07}, and as the \emph{skew fibrations} in the second author's \emph{combinatorial proofs} for classical logic~\cite{Hughes-2006-proofs}.
-To prepare the ground for cut elimination in first-order \emph{combinatorial proofs} is a further motivation for the present work.
+To prepare the ground for cut elimination in first-order combinatorial proofs~\cite{Hughes-2019-fopws} is further motivation for the present work.
 
@@
 We first give an example of the former (abbreviating $P(x,y)$ to $Pxy$).
-%(writing $Pxy$ for $P(x,y)$ to conserve space). 
 In the initial witness net, below left, each link corresponds to a sequent calculus axiom between both linked subformulas, with the substitutions applied.
 %
-\newcommand\xs{xs} %{(\kern-1ptx\kern-1pt,\kern-2pts\kern-1pt)}
-\newcommand\xt{xt} %{(\kern-1ptx\kern-1pt,\kern-2ptt\kern-1pt)}
-\newcommand\xy{xy} %(\kern-1ptx\kern-1pt,\kern-2pty\kern-1pt)}
-\newcommand\zs{zs}
-\newcommand\zt{zt}
-\[
+\newcommand\xs{xs}%
+\newcommand\xt{xt}%
+\newcommand\xy{xy}%
+\newcommand\zs{zs}%
+\newcommand\zt{zt}%
+\begin{center}\vspace{1pt}\(
 \hspace*{-\parindent}
@@
 \scoal\cdots
-\\ \\
+\\[6ex]
 \text{\scriptsize
@@
 \end{array}
-\]
+\)\vspace{-3pt}\end{center}
 The first two steps (above middle and right) move both links from the subformula $\dual Pxy$ to $\exists y.\dual Pxy$, removing the substitutions $[s/y]$ and $[t/y]$ on $y$, and corresponding to sequent rules $\qrr?s$ and $\qrr?t$.
@@
 We require that both substitutions agree (their domains are the same by the above observation); hence this step could not have been performed before the previous two, corresponding to the non-permutability of the generated inference rules.
-\[
+\begin{center}\(
 \begin{array}{@{}c@{}c@{}c@{}c@{}c@{}}
@@
 	\end{tikzpicture}}
-\\ \\
+\\[6ex]
 \text{\scriptsize
@@
 \end{array}
-\]
+\)\end{center}
 The final steps introduce an inference $\exists R,x$ and one $\forall R$.
@@
 Both links now correspond to sequent axioms.
-\[
+\begin{center}\vspace{0pt}\(
 \hspace*{-\parindent}
@@
     \end{tikzpicture}}
-\\ \\
+\\[6ex]
 &\qquad\qquad&
@@
 \hfill
-\]
+\)\vspace{-2pt}\end{center}
 The second difference is the coalescence step for additive conjunction, above right.
@@
 %
-\setMidspace{5pt}
-\[
+\setMidspace{5pt}%
+\begin{center}\vspace{-.5ex}\(
 \begin{array}{@{}l@{}l}
 	t &\Coloneqq x \Mid f(t_1,\dots,t_n)
-\\[10pt]
+\\[8pt]
 	a &\Coloneqq P(t_1,\dots,t_n) \Mid \dual P(t_1,\dots,t_n)
-\\[10pt]
+\\[8pt]
 	A &\Coloneqq a \Mid A\+A \Mid A\*A \Mid \exists x.A \Mid \forall x.A
 \end{array}
-\]
-%
+\)\vspace{-.5ex}\end{center}
+%
+%\vspace{-.5ex}
 Negation $(\dual{\,\cdot\,})$ is applied to predicate symbols, $\dual P$ as a matter of convenience.
 The \defn{dual} $\dual A$ of an arbitrary formula $A$ is given by De Morgan.
-We use the following notational conventions.
-%
+We use the following notational conventions:
+%
+%\begin{center}\vspace{-1ex}\(
 \[
@@
 \]
+%\)\vspace{-.8ex}\end{center}
 %
@@
 
-By a \defn{subformula} we will mean a subformula \defn{occurrence}.
-For instance, a formula $A\*A$ has two subformulas $A$, one on the left and one on the right.
-The \defn{subformulas} $\subs A$ of a formula are defined as follows; we write $B\sub A$ if $B$ is a subformula of $A$, i.e.\ if $B\in\subs A$.
-\[
-	\subs A = \{A\} \cup
-	\left\{\begin{array}{ll}
-		\subs B\uplus\subs C	& \text{if $A=B\+C$ or $A=B\*C$} \\[5pt]
-		\subs B					& \text{if $A=\exists x.B$ or $A=\forall x.B$}
-	\end{array}\right.
-\]
-
-Since we will be working with a graphical representation, we will adopt \defn{Barendregt's convention}, that bound variable names are globally unique identifiers, in the following form.
-In a sequent $\seq AB$ we assume all quantifiers have a unique binding variable, distinct from any free variable.
-In a proof $\pi$ over $\seq AB$, a variable $x$ that is universally quantified as $\forall x.C$ in $\seq AB$ is an \defn{eigenvariable}.
-A $\qrr!$ rule on $\forall x.C$ is considered to bind all free occurrences of the eigenvariable $x$ in its direct subproof.
-Accordingly, we assume that $x$ does not occur free outside these subproofs (which can be guaranteed by globally renaming $x$).
-We take variable names to be persistent throughout a proof, in the sense that we don't admit alpha-conversion (renaming of bound variables) between proof rules.
-We thus have unique bound variable names in $\seq AB$, but in $\pi$ all $\qrr!$ rules on the subformula $\forall x.C$ share the same eigenvariable $x$.
-
-% ..................................................
-
-\begin{figure}[!t]
+% ..................................................
+
+\begin{figure}[!p]
 $
@@
 
-\begin{figure}[!ht]
+\begin{figure}[!p]
 \[
@@
 
+By a \defn{subformula} we will mean a subformula \defn{occurrence}.
+For instance, a formula $A\*A$ has two subformulas $A$, one on the left and one on the right.
+The \defn{subformulas} $\subs A$ of a formula are defined as follows; we write $B\sub A$ if $B$ is a subformula of $A$, i.e.\ if $B\in\subs A$.
+\begin{center}\vspace{-1ex}\(
+	\subs A = \{A\} \cup
+	\left\{\begin{array}{ll}
+		\subs B\uplus\subs C	& \text{if $A=B\+C$ or $A=B\*C$} \\[5pt]
+		\subs B					& \text{if $A=\exists x.B$ or $A=\forall x.B$}
+	\end{array}\right.
+\)\vspace{-1ex}\end{center}
+
+Since we will be working with a graphical representation, we will adopt \defn{Barendregt's convention}, that bound variable names are globally unique identifiers, in the following form.
+In a sequent $\seq AB$ we assume all quantifiers have a unique binding variable, distinct from any free variable.
+In a proof $\pi$ over $\seq AB$, a variable $x$ that is universally quantified as $\forall x.C$ in $\seq AB$ is an \defn{eigenvariable}.
+A $\qrr!$ rule on $\forall x.C$ is considered to bind all free occurrences of the eigenvariable $x$ in its direct subproof.
+Accordingly, we assume that $x$ does not occur free outside these subproofs (which can be guaranteed by globally renaming $x$).
+We take variable names to be persistent throughout a proof, in the sense that we don't admit alpha-conversion (renaming of bound variables) between proof rules.
+We thus have unique bound variable names in $\seq AB$, but in $\pi$ all $\qrr!$ rules on the subformula $\forall x.C$ share the same eigenvariable $x$.
+
+% ..................................................
+
 A \defn{link} $(C,D)$ on a sequent $\seq AB$ is a pair of subformulas $C\leq A$ and $D\leq B$. 
@@
 
-%We will assume that all quantifiers in a sequent $\seq AB$ have a distinct binding variable, and no bound variable shares a name with a free one (\defn{Barendregt's convention}).
-In a proof $\pi$ or linking $\lambda_\Sigma$ over $\seq AB$, a variable $x$ is an \defn{eigenvariable} if it is universally quantified ($\forall x.X$) in $\seq AB$, an \defn{existential variable} if existentially quantified ($\exists x.X$), and a \defn{global variable} if free in $\seq AB$.
-A variable $x$ introduced by a witnessing term $t$ in $\pi$ (in a rule $\qrr?t$) or in $\lambda_\Sigma$ (in the range of $\Sigma$) that is not an eigenvariable or global variable is a \defn{term variable}.
-We will assume the following \defn{freshness} convention: term variables are distinct from existential variables.
-Observe that both conventions are readily applied to proofs and linkings by renaming (\emph{$\alpha$-converting}) quantified variables in the conclusion.
-
-% ..................................................
-
-\begin{definition}
-The \defn{de-sequentialization} $[\pi]$ of a sequent proof $\prf\pi AB$ is the witness pre-net $\net{\deseq[\varnothing]\pi AB}AB$ where the function $\deseq-AB$ is defined inductively as follows (symmetric cases are omitted).
-%
+\begin{figure}
 \newcommand\XDeseq[4][\sigma]{
- \left[\vcenter{#2}\right]%
+ \left[\vc{#2}\right]%
  _{\makebox[0pt][l]{$\scriptstyle{#1}$}}%
@@
 \begin{align*}
-	\XDeseq{\,\infer[\Qrr1]{\seq a{\dual a}}{}}bc &\quad=\quad \{\link bc\}
+	\XDeseq{\,\infer[\Qrr1]{\seq a{\dual a}}{\rule{0pt}{3pt}}}bc &\quad=\quad \{\link bc\}
 \\ \\[-5pt]
@@
 \end{align*}
-%
-%\begin{align*}
-%	\XDeseq{\,\infer[\Qrr1]{\seq a{\dual a}}{}}bc &\quad=\quad \{\link bc\}
-%\\ \\[-5pt]
-%	\XDeseq{\infer[\Qrr+i]{\seq A {B_1\+B_2}}{\prf \pi A{B_i}}} {A'} {B_1'\+B'_2} 
-%	& \quad=\quad 
-%	\deseq{\prf\pi A{B_i}} {A'} {B_i'}
-%\\ \\[-5pt]
-%	\XDeseq{\infer[\Qrr*]{\seq A{B\*C}}{
-%	 \prf\pi AB && \prf{\pi'}AC 
-%	}}{A'}{B'\*C'}
-%	& \quad=\quad 
-%	  \deseq{\prf\pi AB}{A'}{B'}
-%	  \cup
-%	  \deseq{\prf{\pi'}AC}{A'}{C'}
-%\\ \\[-5pt]
-%	\XDeseq{\infer[\Qrr?t]{\seq A{\exists x.B}}{\prf\pi A{B[t/x]}}}{A'}{\exists x.B'}
-%	& \quad=\quad 
-%	 \deseq[{\sigma[t/x]}]{\prf\pi A{B[t/x]}} {A'} {B'}
-%\\ \\[-5pt]
-%	\XDeseq{\infer[\Qrr!]
-%	  {\seq A{\forall x.B}}{\prf\pi AB}} {A'} {\forall x.B'}
-%	& \quad=\quad 
-%	  \deseq{\prf\pi AB}{A'}{B'}
-%\end{align*}
+\caption{De-sequentialization}
+\label{fig:deseq}
+\end{figure}
+
+% ..................................................
+
+\begin{definition}
+The \defn{de-sequentialization} $[\pi]$ of a sequent proof $\prf\pi AB$ is the witness pre-net $\net{\deseq[\varnothing]\pi AB}AB$ where the function $\deseq-AB$ is defined inductively in Figure~\ref{fig:deseq} (symmetric cases are omitted).
 \end{definition}
@@
 For an example, we refer to the introduction.
-%
-%To conclude this section we will identify three aspects of sequent proofs, arising from the local nature of the rules, that need to be enforced explicitly in proof nets.
-%
-%\begin{description}
-%	\item[Axiom links]
-%A sequent proof axiom connects dual atoms, $\seq a{\dual a}$.
-Correspondingly, a witness link $\link ab$ on atomic formulas $a$ and $b$ is an \defn{axiom link} if $a\sigma=\dual b\sigma$.
-An \defn{axiom} witness linking is one consisting solely of axiom links.
-%	\item[Local eigenvariables]
-%The side-condition on the $\forall R$-rule, that the eigenvariable is not free in the context, means that eigenvariables are \emph{local} to the subproof of the $\forall R$-rule.
-Correspondingly, a link $\link CD$ on $\seq AB$ has \defn{local eigenvariables} if for any variable $x\in\sigma$, if $x$ is an eigenvariable quantified as $\forall x.X$ in $\seq AB$, then $C\leq X$ or $D\leq X$.
-%A witness linking or pre-net has \defn{local eigenvariables} if all its links do.
-%	\item[Exact coverage]
-%The local witness substitution $[t/x]$ in a rule instance $\qrr?t$ will have been applied exactly to the axioms $\seq a{\dual a}$ in the subproof of that rule.
-Correspondingly, for a link $\link CD$ on $\seq AB$ we expect the domain of $\sigma$ to be exactly the existential variables in $A$ and $B$ in whose scope $C$ and $D$ occur.
-For a subformula $C$ of $A$, let the \defn{existential variables of $C$ in $A$} be the set $\ex[A]C = \{\,x \mid C < \exists x.X \sub A\,\}$.
-A link $\link CD$ on $\seq AB$ then has \defn{exact coverage} if $\dom\sigma = \ex[A]C\cup\ex[B]D$.
-If it does, $\sigma$ consists of two components, $\sigma\res{\ex[A]C}$ and $\sigma\res{\ex[B]D}$, which we abbreviate as $\sigma_C$ and $\sigma_D$ respectively.
-%A witness linking or pre-net has \defn{exact coverage} if all its links do.
-%\end{description}
-%
-%\noindent
-%Observe that a de-sequentialization $[\pi]$ has all three properties.
-
-%\begin{definition}[Local correctness]
-%A witness linking or pre-net has \emph{local eigenvariables/exact coverage} if all its links do.
-%It is \defn{locally correct} if it satisfies both.
-%\end{definition}
-
-%First, a witness link $\link ab$ on two atomic formulas $a$ and $b$ is an \defn{axiom} link if $a\sigma=\dual b\sigma$.
-A witness \defn{axiom} linking is one where every link is an axiom link.
-Observe that the de-sequentialization $[\pi]$ is a witness pre-net with axiom linking $\deseq[\varnothing]\pi AB$.
-
-%Second, in a sequent proof, the side-condition on the $\forall R$-rule, that the eigenvariable is not free in the context, means that eigenvariables are \emph{local} to the subproof of the $\forall R$-rule.
-We capture this in pre-nets as the \defn{local eigenvariables} condition: for a link $\link CD$ on $\seq AB$, if $x\in\sigma$ is an eigenvariable quantified as $\forall x.X$ in $\seq AB$, then $C\leq X$ or $D\leq X$.
-%
-%Third, for a link $\link CD$ on $\seq AB$ we expect the domain of $\sigma$ to be exactly the existential variables in $A$ and $B$ in whose scope $C$ and $D$ occur.
-For a subformula $C$ of $A$, let the \defn{existential variables of $C$ in $A$} be the set $\ex[A]C$:
-%\[
-%	\ex[A]C = \{\,x \mid C < \exists x.X \sub A\,\}~.
-%\]
-%
-%% ..................................................
-%
-%\begin{definition}
-%A witness pre-net $\net{\lambda_\Sigma}AB$ has \defn{exact coverage} if for every link $\link CD$ in $\lambda_\Sigma$ the domain of $\sigma$ is exactly the existential variables of $C$ and $D$:
-%\[
-%	\dom\sigma = \ex[A]C\cup\ex[B]D~.
-%\]
-%\end{definition}
-%
-% ..................................................
-%
-%The witness map $\sigma$ of a link $\link CD$ then has two natural, disjoint components, $\sigma\res{\ex[A]C}$ and $\sigma\res{\ex[B]D}$, which we will abbreviate by $\sigma_C$ and $\sigma_D$ respectively.
 
@@
 
-\begin{definition}
-%
+\begin{figure}
 \renewcommand{\+}{{+}}
 \renewcommand{\*}{{\times}}
-%
-\defn{Strict sequentialization} ($\scoal$) is the rewrite relation on labelled pre-nets generated by the following rules, which replace one or two links by another in a pre-net $\net{\lambda_\Sigma^\Pi}AB$ where $B$ has a subformula $D_1\+D_2$, $D_1\*D_2$, $\exists x.D$, and $\forall x.D$ respectively.
-Symmetric cases are omitted.
-%
 \begin{align*}
@@
 \end{align*}
+\caption{Strict coalescence}
+\label{fig:strict}
+\end{figure}
+
+% ..................................................
+
+\begin{definition}
+%
+\renewcommand{\+}{{+}}
+\renewcommand{\*}{{\times}}
+%
+\defn{Strict sequentialization} ($\scoal$) is the rewrite relation on labelled pre-nets generated by the rules in Figure~\ref{fig:strict}, which replace one or two links by another in a pre-net $\net{\lambda_\Sigma^\Pi}AB$ where $B$ has a subformula $D_1\+D_2$, $D_1\*D_2$, $\exists x.D$, and $\forall x.D$ respectively.
+Symmetric cases are omitted.
 %
@@
 \end{description}
-
-\[
+\begin{center}\vspace{-.8ex}\(\quad\quad
 \vc{
@@
    \quad\text{where }x\in\fv(t)
-\]
-
+\)\vspace{.5ex}\end{center}
+%
 \noindent
@@
 % ..................................................
-\begin{figure}[!tp]
+\begin{figure}[!p]
 \[
@@
 We would like to thank the anonymous referees for their constructive feedback.
-Dominic Hughes would like to thank his host, Wes Holliday, at the UC Berkeley Logic Group.
-Willem Heijltjes was supported by EPSRC Project EP/R029121/1 \emph{Typed Lambda-Calculi with Sharing and Unsharing}, and Lutz Stra{\ss}burger was supported by the ANR-FWF international
+Dominic Hughes thanks his hosts, Wes Holliday and Dana Scott, at the UC Berkeley Logic Group.
+Willem Heijltjes was supported by EPSRC Project EP/R029121/1 \emph{Typed Lambda-Calculi with Sharing and Unsharing}.
+Lutz Stra{\ss}burger was supported by the ANR-FWF international
 grant ANR-5-CE25-0014 \emph{The Fine Structure of Formal Proof

### 2019-05-31 7 - FSCD 2019 - Final/ALL1.tex
trying to match editor's version

@@
-\documentclass[UKenglish]{lipics-v2019}
+\documentclass[a4paper,UKenglish]{lipics-v2019}
 
@@
 \usepackage{amsmath,amssymb,amsthm}
-\usepackage{latexsym}
+%\usepackage{latexsym}
 \usepackage{microtype}
 \usepackage{proof}
-\usepackage{refcount}
-\usepackage{stmaryrd}
-\usepackage{xargs}
+%\usepackage{refcount}
+%\usepackage{stmaryrd}
+%\usepackage{xargs}
 
@@
 
-\newcommand\defn[1]{\textit{\textbf{#1}}}
+\newcommand\defn[1]{\textbf{#1}}
 
@@
 \newcommand\join{\vee}
-\newcommand\minus{\mathop{\!/\mathchoice{\kern-3pt}{\kern-3pt}{\kern-2.5pt}{\kern-2pt}/\!}}
+%\newcommand\minus{\mathop{\!/\mathchoice{\kern-3pt}{\kern-3pt}{\kern-2.5pt}{\kern-2pt}/\!}}
+\newcommand\minus{-}
 
@@
  {Willem B.\ Heijltjes}
- {University of Bath, United Kingdom}
- {{http://willem.heijltj.es}} %{w.b.heijltjes@bath.ac.uk}
+ {University of Bath, United Kingdom\and\url{http://willem.heijltj.es}}
+ {} %{w.b.heijltjes@bath.ac.uk}
  {}
- {}
+ {was supported by EPSRC Project EP/R029121/1 \emph{Typed Lambda-Calculi with Sharing and Unsharing}.}
 \author
  {Dominic J.\ D.\ Hughes}
- {Logic Group, UC Berkeley, USA}
- {{http://boole.stanford.edu/\textasciitilde dominic}} %{dominich@theory.stanford.edu}
+ {Logic Group, UC Berkeley, USA\and\url{http://boole.stanford.edu/~dominic}}
+ {} %{dominich@theory.stanford.edu}
  {}
@@
  {Lutz Stra\ss burger}
- {Inria Saclay \&\ LIX/\'Ecole Polytechnique, Palaiseau, France}
- {{http://www.lix.polytechnique.fr/Labo/Lutz.Strassburger}}
+ {Inria Saclay, Palaiseau, France\and LIX, \'Ecole Polytechnique, Palaiseau, France\and \url{http://www.lix.polytechnique.fr/Labo/Lutz.Strassburger}}
+ {}
  %{lutz.strassburger@inria.fr}
  {}
- {}
+ {was supported by the ANR-FWF international grant ANR-5-CE25-0014 \emph{The Fine Structure of Formal Proof Systems and their Computational Interpretations (FISP)}.}
 
@@
 \relatedversion{A full version \cite{Heijltjes-Hughes-Strassburger-2018} is available at \url{http://hal.inria.fr/hal-01867625/}}
+
+\acknowledgements{We would like to thank the anonymous referees for their constructive feedback. Dominic Hughes thanks his hosts, Wes Holliday and Dana Scott, at the UC Berkeley Logic Group. }
+
+\funding{}
+
+%\section*{Acknowledgements}
+%
+%We would like to thank the anonymous referees for their constructive feedback.
+Dominic Hughes thanks his hosts, Wes Holliday and Dana Scott, at the UC Berkeley Logic Group.
+Willem Heijltjes was supported by EPSRC Project EP/R029121/1 \emph{Typed Lambda-Calculi with Sharing and Unsharing}.
+Lutz Stra{\ss}burger was supported by the ANR-FWF international
+%grant ANR-5-CE25-0014 \emph{The Fine Structure of Formal Proof
+%Systems and their Computational Interpretations (FISP)}.
 
@@
 %
-\begin{center}\vspace{-.5ex}\(
+\[
 \begin{array}{@{}rc@{\qquad}rc@{}}
@@
     \end{tikzpicture}}
-\rule[-55pt]{0pt}{110pt}
-\)\vspace{-.5ex}\end{center}
+%\rule[-55pt]{0pt}{110pt}
+~~
+\]
 %
@@
 %
-\begin{center}\(
-%\hspace*{\fill}
-%\hspace*{-\parindent}
+\[
 	\vc{\infer[\Qrr?t]{\seq A{\exists x.B}}{\seq A{B[t/x]}}}
@@
    }}
-%\hfill
-\)\end{center}
+\]
 %
@@
 We compare further properties in Figure~\ref{fig:results} in the conclusion, where we also discuss related work and Lambek's notion of \defn{generality} \cite{Lambek-1968-1972}.
-%
-\begin{center}\(
+
+\[
 	\text{\small a witness net:}
@@
 	\end{tikzpicture}}
-\)\vspace{-1ex}\end{center}
-%
+\]
+
 \paragraph*{Background}
-%
+
 Additive linear logic is combinatorially rich, yet well-behaved and tractable: proof search \cite{Galmiche-Marion-1995} and proof net correctness \cite{Heijltjes-Hughes-2015} for a net over $\seq AB$ are linear in $|A|\times|B|$ (with $|A|$ the size of the syntax tree of $A$).
@@
 For example, to prove the sequent $\seq{\exists x.P(x)}{\exists y.\dual P(y)}$ both quantifiers must receive \emph{the same} witness, as in the following two proofs, but \emph{any} witness will do.
-\begin{center}\(
+\[
 	\vc{\infer={\seq{\exists x.P(x)}{\exists y.\dual P(y)}}{\infer{\seq{P(s)}{\dual P(s)}}{}}}
@@
 	\vc{\infer={\seq{\exists x.P(x)}{\exists y.\dual P(y)}}{\infer{\seq{P(t)}{\dual P(t)}}{}}}
-\)\end{center}
+\]
 The issue is more pronounced where quantifiers are \emph{vacuous}, $\exists x.A$ with $x$ not free in $A$.
@@
 Below right is an interesting intermediate variant: the witness $s$ or $t$ can be observed without explicit annotation in the $\exists\mathrm R$ rule, but the choice is equally immaterial to the content of the proof as when the quantifier were vacuous.
-\begin{center}\(
+\[
 	\vc{\infer[\!\!\scriptstyle{\qrr?s}]{\seq{\exists x.P}{\dual P}}{\infer{\seq P{\dual P}}{}}}
@@
 	}}
-\)\end{center}
+\]
 In this paper we will not attempt to settle the question of proof identity.
@@
 \defn{Slicing} \cite{Hughes-vanGlabbeek-2005} is a global, geometric criterion: it asks that each \defn{slice}, a choice to remove one subformula of each product along with all connected links, retains a single link.
-%
-\[
-\hspace*{-\parindent}
-\hspace*{\fill}
+\[
 \begin{array}{c@{\qquad\qquad\qquad}c}
@@
 \end{array}
-\hfill
 \]
@@
 \newcommand\zt{zt}%
-\begin{center}\vspace{1pt}\(
-\hspace*{-\parindent}
+\[
 \begin{array}{@{}c@{}c@{}c@{}c@{}c@{}}
@@
 \end{array}
-\)\vspace{-3pt}\end{center}
+\]
 The first two steps (above middle and right) move both links from the subformula $\dual Pxy$ to $\exists y.\dual Pxy$, removing the substitutions $[s/y]$ and $[t/y]$ on $y$, and corresponding to sequent rules $\qrr?s$ and $\qrr?t$.
@@
 We require that both substitutions agree (their domains are the same by the above observation); hence this step could not have been performed before the previous two, corresponding to the non-permutability of the generated inference rules.
-\begin{center}\(
+\[
 \begin{array}{@{}c@{}c@{}c@{}c@{}c@{}}
@@
 \end{array}
-\)\end{center}
+\]
 The final steps introduce an inference $\exists R,x$ and one $\forall R$.
@@
 Both links now correspond to sequent axioms.
-\begin{center}\vspace{0pt}\(
-\hspace*{-\parindent}
-\hspace*{\fill}
+\[
 \begin{array}{@{}ccccc@{}}
@@
 \end{array}
-\hfill
-\)\vspace{-2pt}\end{center}
+\]
 The second difference is the coalescence step for additive conjunction, above right.
@@
 First-order terms and the formulas of first-order $\all$ are generated by the following grammars.
-%
-\setMidspace{5pt}%
-\begin{center}\vspace{-.5ex}\(
+\[
+\setMidspace{5pt}
 \begin{array}{@{}l@{}l}
@@
 \end{array}
-\)\vspace{-.5ex}\end{center}
-%
-%\vspace{-.5ex}
+\]
 Negation $(\dual{\,\cdot\,})$ is applied to predicate symbols, $\dual P$ as a matter of convenience.
@@
 We use the following notational conventions:
-%
-%\begin{center}\vspace{-1ex}\(
 \[
@@
 \]
-%\)\vspace{-.8ex}\end{center}
-%
 A \defn{sequent} $\seq AB$ is a pair of formulas $A$ and $B$.
@@
 A $\qrr!$ rule on $\forall x.C$ is considered to bind all free occurrences of the eigenvariable $x$ in its direct subproof.
-Accordingly, we assume that $x$ does not occur free outside these subproofs (which can be guaranteed by globally renaming $x$).
+Accordingly, we assume that $x$ does not occur free outside these subproofs (which can be guaranteed by globally renaming~$x$).
 We take variable names to be persistent throughout a proof, in the sense that we don't admit alpha-conversion (renaming of bound variables) between proof rules.
@@
 It captures the non-permutability of universal and existential sequent rules due to the \emph{eigenvariable condition} of the former, as below right.
-\end{description}
-\begin{center}\vspace{-.8ex}\(\quad\quad
+\[
 \vc{
@@
    \quad\text{where }x\in\fv(t)
-\)\vspace{.5ex}\end{center}
+\]
+\end{description}
 %
@@
 
-\newlength\seriously
-\setlength\seriously\parindent
-\parbox[b]{.6\columnwidth}{
 We will describe the composition of two witness nets by a global operation.
@@
 
-\setlength\parindent\seriously
-\indent
 Cut-elimination rules for \all1 are given in Figure~\ref{fig:cut-elim}; the requisite permutations are in Figure~\ref{fig:cut-permutations}.
-}
-\quad
+
+\[
 \begin{tikzpicture}[net]
@@
 \end{tikzpicture}
-
-We use the example on the right to illustrate the composition of links.
+\]
+
+%
+%\newlength\seriously
+%\setlength\seriously\parindent
+%\parbox[b]{.6\columnwidth}{
+%
+%\setlength\parindent\seriously
+%\indent
+%}
+%\quad
+
+We use the example above to illustrate the composition of links.
 To eliminate the central cut, on $\forall x.\exists y.\forall z.P$ and $\exists x.\forall y.\exists z.\dual P$, the explicit substitutions for both formulas must be effectuated.
@@
 Unlike for proof nets, this notion is not so natural for sequent proofs: in the permutation of existential and product rules below, from left to right $u$ must be generated as the least term more general than $s$ and $t$; from right to left, $s$ and $t$ cannot be reconstructed from $u$, and must be retrieved from their respective subproofs.
-\begin{center}\(
+\[
 	\vc{
@@
 	}}}
-\)\end{center}
+\]
 
@@
 For an axiom linking $\lambda$ over $\seq AB$ the \defn{initial witness pre-net} $\net{\lambda_\star}AB$ is given by
-\begin{center}\(
+\[
 	\lambda_\star = \{~\link ab~\mid~\link[]ab\in\lambda~,~\sigma=\init{\dual a}b~\}~.
-\)\end{center}
+\]
 An initial witness pre-net has \emph{exact coverage}, while coalescence will give \emph{local eigenvariables}.
 Note that eigenvariables are constants for the purpose of unification (they are not substituted into).
-For Barendregt's convention, that free variables have distinct names from bound ones, we should assume that variables in the domain of a witness map are fresh; for example, the most general unifier of existential variables $x$ and $y$ should be $[z/x,z/y]$ for a fresh variable~$z$, and not $[y/x]$ or $[x/y]$.
+For Barendregt's convention, that free variables have distinct names from bound ones, we should assume that variables in the range of a witness map are fresh; for example, the most general unifier of existential variables $x$ and $y$ should be $[z/x,z/y]$ for a fresh variable~$z$, and not $[y/x]$ or $[x/y]$.
 
@@
 
-\section*{Acknowledgements}
-
-We would like to thank the anonymous referees for their constructive feedback.
-Dominic Hughes thanks his hosts, Wes Holliday and Dana Scott, at the UC Berkeley Logic Group.
-Willem Heijltjes was supported by EPSRC Project EP/R029121/1 \emph{Typed Lambda-Calculi with Sharing and Unsharing}.
-Lutz Stra{\ss}burger was supported by the ANR-FWF international
-grant ANR-5-CE25-0014 \emph{The Fine Structure of Formal Proof
-Systems and their Computational Interpretations (FISP)}.
-
 \bibliography{ALL1}
